### 2019-04-04 frame.tex
setting it up

\documentclass[11pt]{amsart}

\usepackage{macros}
\usepackage[bbgreekl]{mathbbol}

\linespread{1.25}

%\usepackage[final]{pdfpages}

\setcounter{tocdepth}{2}
\numberwithin{equation}{section}

\def\brian{\textcolor{blue}{BW: }\textcolor{blue}}
\def\owen{\textcolor{magenta}{OG: }\textcolor{magenta}}

\begin{document}
\title{Large $N$ limits of higher enveloping algebras}

%\author{Owen Gwilliam}
%\address{Department of Mathematics and Statistics \\
%Lederle Graduate Research Tower, 1623D \\
%University of Massachusetts Amherst \\
%710 N. Pleasant Street}
%\email{gwilliam@math.umass.edu}
%
%\author{Brian Williams}
%\address{Department of Mathematics, 
%Northeastern University \\ 
%567 Lake Hall \\ 
%Boston, MA 02115 \\ U.S.A.}
%\email{br.williams@northeastern.edu}

\maketitle
\thispagestyle{empty}

\tableofcontents

Recently there has emerged a systematic generalization of the enveloping algebra $U\fg$ of a Lie algebra $\fg$ to {\em higher} enveloping algebras:
each dg Lie algebra $\fg$ has an enveloping $E_n$ algebra $\UU_n\fg$.
Building on prior work \cite{BD, AF}, Knudsen \cite{Knudsen} has developed these ideas extensively and offered useful models as factorization algebras.
Our central goal here is to develop close cousins of two important results about enveloping algebras of Lie algebras: 
\begin{enumerate}
\item[(1)] the (underived) center of $U\sl_{N+1}$ is isomorphic to $(\Sym(\CC^{N}))^{S_N}$, where we view $\CC^{N}$ as the Cartan subalgebra of $\sl_{N+1}$ and $S_N$ as the Weyl group of $SL_{N+1}$, and
\item[(2)] the derived center of the enveloping algebra $U\fg$ is given by derived invariants of the adjoint action of $\fg$ on $U\fg$:
\[
Hoch^*(U\fg,U\fg) \simeq \clies(\fg, Ug),
\]
\end{enumerate}
but in a way that works uniformly for these higher enveloping algebras.

Our results are cousins, and not exact analogues, because we are interested in varying (1) by taking the limit as $N \to \infty$ and in varying (2) by studying the derived {\em centralizer} of a map $\UU_n\sl_\infty \hookrightarrow \UU_n\gl_\infty$, where $A$ is a dg algebra.
(The derived center is the centralizer of the identity map $\UU_n\fg \to \UU_n\fg$.)
These notions will be reviewed and explained in the next section below,
where we also describe our results in detail.
When $n=1$, however, note that we find that \owen{state the classical thing!}

Our main tool is the Loday-Quillen-Tsygan (LQT) theorem,
which describes the large $N$ limit of Lie algebra homology of $\gl_N(A)$ for $A$ a dg algebra.
Experts will know that enveloping $E_n$ algebras can be constructed using Chevalley-Eilenberg chains
(i.e., that they are shifted versions of $\cliels$, in a precise sense),
and hence will recognize the relevance of the LQT theorem in this context.
From this perspective, our main result can be understood as an $E_n$ generalization of the LQT theorem.

We hope these constructions and ideas have interesting applications to other large $N$ phenomena,
such as in quantum field theory and random matrix theory.

\section{Our main results}

Our primary result is the following.

\begin{thm}
Let $A$ be a unital dg algebra over a field $k$ of characteristic zero. 
Then the centralizer of the Lie algebra map 
\[
u_A: \sl_\infty(k) \hookrightarrow \gl_\infty(A)
\]
\end{thm}

\section{A variant of the Loday-Quillen-Tsygan theorem}

Throughout this section, let $A$ be a dg algebra over a field $k$ of characteristic zero.
We do not assume $A$ is unital; whenever unitality leads to a stronger result, we will explicitly add it as a hypothesis.
(It is possible to work with $A_\infty$ algebras rather than dg algebras, 
but it changes nothing structurally essential while adding a distracting layer of notational complexity.)

\begin{dfn}
Let $\cC(A)$ denote the cochain complex $\Cyc_*(A)[1]$, which may be viewed as an abelian Lie algebra. 
Let $\cL(A)$ denote the dg Lie algebra $\gl_\infty(A)$.
\end{dfn}

Let $\sl_\infty$ denote $\sl_\infty(k)$, the trace-zero matrices of rank infinity with only finitely many nonzero entries in~$k$.
Let $\gl_\infty$ denote $\gl_\infty(k)$, the matrices of rank infinity with only finitely many nonzero entries in~$k$.
Let $\gl_\infty(A)$ denote the matrices of rank infinity with only finitely many nonzero entries in~$A$.
There is a natural action of $\sl_\infty$ on $\gl_\infty(A)$, 
and hence on its Chevalley-Eilenberg chains $\cliels(\cL(A))$.
A key step in the LQT theorem is the construction of a quasi-isomorphism
\beqn\label{lqtco}
\lambda^{co}_A: \cliels(\cL(A))_{\sl_\infty} \xto{\cong} \Sym(\cC(A)).
\eeqn
When $A$ is unital, the inclusion of the identity $k \hookrightarrow A$ means the action of $\sl_\infty$ on $\gl_\infty(A)$ is inner, 
and hence the projection $\cliels(\cL(A)) \to \cliels(\cL(A))_{\sl_\infty}$ is a quasi-isomorphism.
The standard statement of the LQT theorem composes these two maps.

\begin{thm}
For $A$ a unital dg algebra over a characteristic zero field $k$,
there is a quasi-isomorphism
\beqn\label{lqt}
\lambda_A: \cliels(\cL(A)) \xto{\simeq} \Sym(\cC(A))
\eeqn
of dg cocommutative Hopf algebras.
\end{thm}

For us it is the coalgebra structure that is particularly important, although the full Hopf algebra structure is typically emphasized.

As the constructions are natural in the algebra $A$, one can phrase a stronger but more abstract statement.

\begin{cor}
There is a natural transformation
\[
\lambda: \cliels(\cL(-)) \Longrightarrow \Sym(\cC(-))
\]
between these two functors from the dg category of unital dg algebras to the dg category of dg cocommutative Hopf algebras over~$k$.
It is a quasi-isomorphism on every algebra.
\end{cor}

For our purposes, a variant is more useful, but this variant follows by easy, formal arguments.

\def\lqt{{\bblambda}}

\begin{thm}
There is a natural transformation
\[
\lqt: \clies(\sl_\infty, \cliels(\cL(-)))  \Longrightarrow \clies(\sl_\infty) \otimes \Sym(\cC(-))
\]
between these two functors from the dg category of {\em non}unital dg algebras to the dg category of dg Hopf algebras over~$k$.
For each nonunital dg algebra $A$, the map
\beqn\label{lqtinv}
\lqt_A: \clies(\sl_\infty, \cliels(\cL(A))) \xto{\simeq} \clies(\sl_\infty) \otimes \Sym(\cC(A))
\eeqn
is a quasi-isomorphism.
\end{thm}

\begin{proof}
We take for granted that the reader is familiar with the proof of the LQT theorem as articulated in \cite{LQ, Weibel, Loday}.
Our primary modification is to replace the coinvariants $\cliels(\cL(A))_{\sl_\infty}$ by the invariants $\cliels(\cL(A))^{\sl_\infty}$.
Note that there is a canonical map
\beqn\label{invtoco}
\cliels(\cL(A))^{\sl_\infty} \hookrightarrow \cliels(\cL(A)) \to \cliels(\cL(A))_{\sl_\infty},
\eeqn
and in fact this map is an isomorphism, which we now show.

To see this claim, we need to understand how $\sl_\infty$ acts on the underlying graded module of $\cliels(\cL(A))$. Note that as a $k$-module, $\cL(A) \cong \gl_\infty \otimes A$, which is a free $k$-module. 
Each $n$th tensor power thus factors as
\[
(\cL(A)[1])^{\otimes n} \cong (\gl_\infty[1])^{\otimes n} \otimes A^{\otimes n}.
\]
Taking the coinvariants under the action of the symmetric group $S_n$
(which acts diagonally on the $\gl_\infty$ factor and the $A$ factor),
we obtain
\[
\Sym^n (\gl_\infty[1]) \otimes A.
\]
But the action of $\sl_\infty$ is then wholly on the left hand factor, leaving $A$ independent.

There is a natural decomposition of $\Sym^n (\gl_\infty[1])$ into a direct sum $T_n \oplus T_n^\perp$ of representations of $\sl_\infty$, where $T_n$ is trivial and the complement $T_n^\perp$ has no trivial components.
If we replace $\gl_\infty$ with the finite-dimensional Lie algebra $\gl_m$, 
the analogous decomposition of $\Sym^n (\gl_m[1])$ exists by semisimplicity. 
In fact, with $m > n$, invariant theory implies
\[
(\gl_m^{\otimes n})^{\sl_m} = (\gl_m^{\otimes n})_{\sl_m} \cong k S_n,
\]  
the group algebra of the symmetric group $S_n$.
A stabilization phenomenon then implies the decomposition as $m \to \infty$.
We note that we see here the equivalence of the $\sl_m$-invariants with the $\sl_m$-coinvariants,
which holds for every degree $n$ and hence yields the desired isomorphism~(\ref{invtoco}).

We thus conclude that there is a decomposition
\[
\cliels(\cL(A)) = T(A) \oplus T^\perp(A)
\]
into a direct sum of cochain complexes,
where the first summand is a trivial $\sl_\infty$-module and the second has no trivial components.
We will not unravel explicitly how to construct $T(A)$ from the algebra $A$ and the modules~$T_n$,
but the reader should recognize that $T(A) = \cliels(\cL(A))^{\sl_\infty}$.

We now recall two familiars fact about the Lie algebra cohomology of a semisimple Lie algebra~$\fg$:
\begin{itemize}
\item the Lie algebra cohomology of an irreducible, nontrivial, finite-dimensional module $M$ is zero, and
\item for any trivial module $N$, there is a natural isomorphism $H^*_\Lie( \fg,N) \cong H^*_\Lie(\fg) \otimes N$.
\end{itemize}
Thus, we have a decomposition
\[
\clies(\sl_\infty,\cliels(\cL(A))) = \clies(\sl_\infty,T(A)) \oplus \clies(\sl_\infty,T^\perp(A)), 
\]
and there is a split surjection
\[
\bbsigma_A: \clies(\sl_\infty,\cliels(\cL(A))) \to \clies(\sl_\infty,T(A)) \cong \clies(\sl_\infty) \otimes T(A) 
\]
that is a quasi-isomorphism.

We define our desired map $\lqt$ as the composite
\[
\lqt_A = \left(\id_{\clies(\sl_\infty)} \otimes \lambda^{co}_A \right) \circ \bbsigma_A,
\]
which is a quasi-isomorphism by construction.

Our arguments, like those for the LQT theorem, are natural in the algebra~$A$ and hence we have constructed the natural transformation $\lqt$ implicitly.
\end{proof}

%\bibliographystyle{alpha}
%%\bibliographystyle{spmpsci}  
%\bibliography{hic}

\end{document}

### 2019-04-22 frame.tex
b edits

@@
 \def\owen{\textcolor{magenta}{OG: }\textcolor{magenta}}
+\def\mahmoud{\textcolor{green}{MZ: }\textcolor{green}}
 
 \begin{document}
-\title{Large $N$ limits of higher enveloping algebras}
+\title{Centralizers of higher enveloping algebras and their large $N$ limits}
 
@@
 Building on prior work \cite{BD, AF}, Knudsen \cite{Knudsen} has developed these ideas extensively and offered useful models as factorization algebras.
-Our central goal here is to develop close cousins of two important results about enveloping algebras of Lie algebras: 
+Our central goal here is to document generalizations of two important results about enveloping algebras of Lie algebras: 
 \begin{enumerate}
@@
 \[
-Hoch^*(U\fg,U\fg) \simeq \clies(\fg, Ug),
+\Hoch^*(U\fg,U\fg) \simeq \clies(\fg, U\fg),
 \]
@@
 
-Our results are cousins, and not exact analogues, because we are interested in varying (1) by taking the limit as $N \to \infty$ and in varying (2) by studying the derived {\em centralizer} of a map $\UU_n\sl_\infty \hookrightarrow \UU_n\gl_\infty$, where $A$ is a dg algebra.
+Our results include a cousin of these results where we vary (1) by taking the limit as $N \to \infty$ and vary (2) by studying the derived {\em centralizer} of a map $\UU_n\sl_\infty \hookrightarrow \UU_n\gl_\infty(A)$, where $A$ is a dg algebra.
 (The derived center is the centralizer of the identity map $\UU_n\fg \to \UU_n\fg$.)
@@
 
-Our main tool is the Loday-Quillen-Tsygan (LQT) theorem,
+Our main tool for this result is the Loday-Quillen-Tsygan (LQT) theorem,
 which describes the large $N$ limit of Lie algebra homology of $\gl_N(A)$ for $A$ a dg algebra.
@@
 
+\begin{rmk}
+Throughout this document, we will work with differential graded vector spaces over a field $k$ of characteristic zero.
+When we write ``Lie algebra,'' we mean a dg Lie algebra; if we mean an ordinary Lie algebra (such as $\sl_2(\CC)$), we say so explicitly.
+Similarly, ``algebra'' means ``dg algebra'' unless stated otherwise.
+Our theorems will be stated in terms of the stable $\infty$-category of such cochain complexes (one is free to work with the appropriate stable model or pretriangulated dg category, as one wishes).
+Many of our constructions involve, however, explicit manipulations with standard, explicit complexes.
+To minimize confusion, we try to indicate the level at which we are working but that may be left implicit in some places.
+\end{rmk}
+
 \section{Our main results}
 
-Our primary result is the following.
+See section~\ref{sec: enveloping} for a summary of the enveloping $E_n$ algebra construction, 
+and see section~\ref{sec: centralizer} for a summary of centralizers of maps of $E_n$ algebras.
 
 \begin{thm}
-Let $A$ be a unital dg algebra over a field $k$ of characteristic zero. 
-Then the centralizer of the Lie algebra map 
+\label{thm: centralizer}
+Let $f: \UU_n \fg \to B$ denote a map of $E_n$ algebras, where $\UU_n \fg$ is the enveloping $E_n$ algebra of a dg Lie algebra $\fg$.
+In particular, $B$ is an $E_n$ algebra in $\fg$-modules via the map~$f$.
+
+The centralizer ${\frak Z}_{E_n}(f)$ is the $E_n$ algebra $\clies(\fg, B)$.
+\end{thm}
+
+By using Knudsen's results, we have the following consequence.
+
+\begin{cor}
+Let $\rho: \fg \to \fh$ be a map of dg Lie algebras, and let $\UU_n \rho$ denote the associated map of enveloping $E_n$ algebras.
+When $k$ is $\RR$ or $\CC$, 
+the centralizer ${\frak Z}_{E_n}(\UU_n \rho)$ is modeled by the locally constant factorization algebra that assigns
 \[
-u_A: \sl_\infty(k) \hookrightarrow \gl_\infty(A)
+\clies(\fg \otimes \Omega^*(U), \cliels( \fh \otimes \Omega^*_c(U)))
 \]
+to each open set $U \subset \RR^n$.
+\end{cor}
+
+An immediate corollary, by taking the identity map, is the following.
+
+\begin{cor}
+\label{thm: center}
+The center of the enveloping $E_n$ algebra $\UU_n\fg$ is the $E_n$ algebra $\clies(\fg, \UU_n\fg)$.
+(It has, of course, a natural $E_{n+1}$ algebra structure.)
+
+When $k$ is $\RR$ or $\CC$, 
+it is modeled by the locally constant factorization algebra that assigns
+\[
+\clies(\fg \otimes \Omega^*(U), \cliels( \fg \otimes \Omega^*_c(U)))
+\]
+to each open set $U \subset \RR^n$.
+\end{cor}
+
+This result generalizes the fact that $\Hoch^*(U\fg,U\fg) \simeq \clies(\fg, U\fg)$, since the associative algebra $U\fg$ is modeled by the locally constant one-dimensional factorization algebra that assigns $\cliels (\fg \otimes \Omega^*_c(U))$ to each open $U \subset \RR$.
+
+Having an explicit presentation for the centralizer of a map of $E_n$ algebras allows for immediate calculations of factorization homology.
+Indeed, for $M$ a closed $n$-dimensional manifold,
+\[
+\int_M {\frak Z}_{E_n}(\UU_n \rho) \simeq \clies(\fg \otimes \Omega^*(M), \cliels( \fh \otimes \Omega^*(M))).
+\]
+When $M = S^n$, we thus see
+\[
+\int_{S^n} {\frak Z}_{E_n}(\UU_n \rho) \simeq \clies(\fg[\epsilon_n], \cliels( \fh[\epsilon_n]))
+\]
+as $\Omega^*(S^n) \simeq \CC[\epsilon_n]$ where $\epsilon_n$ is a formal variable with $|\epsilon_n| = n$ and $\epsilon_n^2 = 0$.
+In the case that $n=1$, this recovers a theorem of Tamarkin-Tsygan \cite{TT} on the Hochschild cohomology of differential operators in the case of a group $G$ (see Example \ref{eg: TT}).
+
+\begin{rmk}
+The preceding results are well-known to experts in factorization homology (we discussed it with several, including Francis and Knudsen),
+since they are quick consequences of published work, as will be seen below.
+But these statements seem not to have be documented yet in the literature, 
+and so we record them here.
+\end{rmk}
+
+Our primary large $N$ result is the following, which is the novel contribution of this paper.
+
+\begin{thm}
+\label{thm: large N}
+Let $A$ be a unital algebra over a field $k$ of characteristic zero. 
+The map of Lie algebras
+\[
+u_A: \sl_\infty(k) \hookrightarrow \gl_\infty(A),
+\]
+induced by the unit in $A$, determines a map 
+\[
+\UU_nu_A: \UU_n\sl_\infty(k) \to \UU_n\gl_\infty(A).
+\]
+In particular, $\UU_n\gl_\infty(A)$ is an $E_n$ algebra in $\sl_\infty(k)$-representations.
+
+The centralizer ${\frak Z}_{E_n}(\UU_nu_A)$ of this map is the $E_n$ algebra obtained by forgetting the dg commutative algebra
+\[
+\clies(\sl_\infty(k)) \otimes \Sym(\Cyc_*(A)[1-n])
+\]
+down to an $E_n$ algebra.
+
+When $k$ is $\RR$ or $\CC$, 
+it is modeled by the locally constant factorization algebra that assigns
+\[
+\clies(\sl_\infty(\Omega^*(U)))\otimes \Sym(\Cyc_*(A \otimes \Omega^*_c(U))[1])
+\]
+to each open set $U \subset \RR^n$.
 \end{thm}
+
+\owen{We should write explicitly what happens in the case $A = k$, and maybe $n=1$.}
+
+The explicit factorization algebras provide convenient methods for computing factorization homology.
+As shown in \owen{exact reference} in \cite{Knudsen}, 
+the enveloping $E_n$ algebras are homotopy $O(n)$-fixed points and hence determine factorization algebras on unoriented $n$-dimensional manifolds.
+
+\section{Enveloping $E_n$ algebras of Lie algebras}
+
+Although \cite{Knudsen} develops an adjunction between Lie and $E_n$ algebras in any presentable stable symmetric monoidal $\infty$-category $\cC$,
+we need his result only in the setting of chain complexes over a field $k$ of characteristic zero $\Mod_k$ with tensor product~$\otimes_k$.
+We summarize his result in that setting as follows.
+
+\def\oblv{{\rm oblv}}
+\def\Free{{\rm Free}}
+
+\begin{thm}
+There is a commuting square of adjunctions
+\[
+\begin{tikzcd}
+\Alg_\Lie(\Mod_k) \arrow[r, bend left=20, shift left=.5ex,"\UU_n"] \arrow[dd] & \Alg_{E_n}(\Mod_k) \arrow[l, shift left=.5ex, "\oblv"] \arrow[dd]\\
+&\\
+\Mod_k \arrow[r, bend left=20, shift left=.5ex, "\Sigma^{1-n}"] \arrow[uu, bend left=20, shift left=.5ex, "\Free_\Lie"] & \Mod_k \arrow[l, shift left=.5ex,"\Sigma^{n-1}"] \arrow[uu, bend right=20, shift right=.5ex, "\Free_{E_n}"']
+\end{tikzcd}
+\]
+where $\Sigma$ denotes suspension \owen{because tikzcd does weird things with ``[1-n]'' instead}.
+(Curving arrows denote left adjoints.)
+
+When $k$ is $\RR$ or $\CC$, 
+the enveloping $E_n$ algebra $\UU_n \fg$ of a dg Lie algebra $\fg$ is modeled by the locally constant factorization algebra that assigns
+\[
+\cliels(\Omega^*_c(U) \otimes \fg)
+\]
+to each open set $U \subset \RR^n$.
+\end{thm}
+
+The second part of this result implies the explicit models in our theorems.
+
+\section{Centralizers of maps of $E_n$ algebras and the derived center}
+\label{sec: centralizer}
+
+We provide a gloss of the main notions here but refer the reader to Section 5.3 of \cite{LurieHA} and \cite{FrancisHH} for extensive and detailed discussions.
+
+Let $\cC^\otimes$ denote a presentable stable symmetric monoidal $\infty$-category (for us, chain complexes over a field $k$ of characteristic zero with~$\otimes_k$).
+
+\begin{dfn}
+For a map $f: A \to B$ of $E_n$ algebras in $\cC$, 
+the {\em centralizer} ${\frak Z}_{E_n}(f)$ is the $E_n$ algebra in $\cC$ that is universal among those that sit in a commuting diagram
+\[
+\begin{tikzcd}
+& {\frak Z}_{E_n}(f) \otimes A \arrow[dr] & \\
+A \arrow[ur, "u"] \arrow[rr, "f"] && B
+\end{tikzcd}
+\]
+where $u$ is induced by the identity map $1_\cC \to {\frak Z}_{E_n}(f)$.
+
+The {\em center} of an $E_n$ algebra $A$ is the centralizer of its identity morphism $\id_A: A \to A$.
+\end{dfn}
+
+When $n=1$ and $\cC$ just ordinary vector spaces, the centralizer of $f: A \to B$ thus consists of the subspace of elements of $B$ that commute with the image $f(A)$ inside~$B$.
+The center of $A$ thus recovers the traditional notion.
+
+An alternative characterization is found in Theorem 5.3.1.30 of~\cite{LurieHA}.
+
+\begin{prp}
+The centralizer ${\frak Z}_{E_n}(f)$ can be identified with the classifying object for maps from $A$ to $B$ in the $\infty$-category $\Mod^{E_n}_A(\cC)$.
+\end{prp}
+
+When $n=1$ and $\cC$ is chain complexes over the field $k$, 
+then $\Mod^{E_1}_A(\cC)$ is equivalent to $A-A$-bimodules and hence ${\frak Z}_{E_1}(f) \simeq \HH^*(A,B_f)$,
+where $B_f$ denotes $B$ viewed as an $A-A$-bimodule via the map~$f$.
+
+We record a key fact drawn from \cite{LurieHA} and~\cite{FrancisHH}, which generalizes this situation.
+
+\begin{prp}
+Let $\cC^\otimes$ be a presentable symmetric monoidal stable $\infty$-category whose tensor product preserves colimits in each variable separately.
+For $A$ be an $E_n$ algebra in $\cC$,
+the $\infty$-category $\Mod^{E_n}_A(\cC)$ is equivalent to the $\infty$-category $\LMod_{\int_{S^{n-1} A}}(\cC)$.
+\end{prp}
+
+See Remark 7.3.5.3 of \cite{LurieHA} and Section 2 of \cite{FrancisHH}.
+Concretely, this claim arises from the fact that as a module over $A$ as an $E_n$ algebra, 
+$M \in \Mod^{E_n}_A(\cC)$ is equipped with a commuting family of actions by $A$ parametrized by $\RR^n \setminus \{0\}$.
+This action factors through the left action of the $E_1$ algebra $\int_{S^{n-1} \times \RR} A$ arising from factorization homology over the complement of the origin,
+which integrates all those actions and through which they all factor.
+As shown in Theorem 7.5.3.1 of \cite{LurieHA} and earlier in Proposition 3.16 of \cite{FrancisHH}, 
+this algebra $\int_{S^{n-1} \times \RR} A$ is equivalent to ${\rm Free}(1_\cC)$, 
+the image of the unit object $1_\cC \in \cC$ under the left adjoint ${\rm Free}$ to the forgetful functor $\Mod^{E_n}_A(\cC) \to \cC$.
+
+We now use these results to prove the central claim of Theorem~\ref{thm: centralizer}.
+
+\section{Proof of Theorem \ref{thm: centralizer}}
+
+Let $\fg$ be a dg Lie algebra, let $B$ be an $E_n$ algebra, and let $f: \UU_n \fg \to B$ be a map of $E_n$ algebras.
+Then the results of the preceding section imply
+\begin{align*}
+{\frak Z}_{E_n}(f) &\simeq {{\rm Mor}}_{\Mod^{E_n}_{\UU_n}}(\UU_n \fg, B_f) \\
+&\simeq {\rm Mor}_{\LMod_{\int_{S^{n-1}} \UU_n}}(\UU_n \fg, B_f)
+\end{align*}
+where 
+\begin{itemize}
+\item $B_f$ denotes the object in $\Mod^{E_n}_{\UU_n}$ or, equivalently, in $\LMod_{\int_{S^{n-1}}\UU_n}$ determined by~$f$,
+\item ${\rm Mor}_{\Mod^{E_n}_{\UU_n}}(\UU_n \fg, B)$ denotes the classifying object for maps from $\UU_n$ to $B_f$ in the $\infty$-category $\Mod^{E_n}_{\UU_n}$ (i.e., an internal mapping object),
+\item and ${\rm Mor}_{\LMod_{\int_{S^{n-1}} \UU_n}} (\UU_n \fg, B_f)$ denotes the classifying object for maps from ${\UU_n}$ to $B$ in the $\infty$-category $\LMod_{\int_{S^{n-1}}\UU_n}$.
+\end{itemize}
+Observe now that $\int_{S^{n-1}}\UU_n$ is an $E_1$ algebra equivalent to the dg algebra $U(\fg \otimes k[\epsilon_{n-1}])$.
+This is because the rational $(n-1)$-sphere is formal, and hence its cochains are quasi-isomorphic to its cohomology $k[\epsilon_{n-1}]$.
+Using the canonical inclusion $i: U\fg \to U(\fg \otimes k[\epsilon_{n-1}])$,
+we find
+\[
+k \otimes_{U\fg} U(\fg \otimes k[\epsilon_{n-1}]) \simeq \Sym(\fg[1-n]).
+\]
+Recall now that $\UU_n \fg \simeq \Sym(\fg[1-n])$ as $\fg$-modules.
+Base change thus implies
+\[
+{\rm Mor}_{\LMod_{\int_{S^{n-1}} \UU_n}} (\UU_n \fg, B_f)  \simeq {\rm Mor}_{U\fg} (k, B_f).
+\]
+The right hand side is precisely Lie algebra cochains of $\fg$ with coefficients in~$B_f$, as desired.
+
+\brian{do you like this example?}
+\begin{eg}\label{eg: TT}
+Consider the case $n=1$ and $B = U \fg$ where $f$ is simply the identity map. 
+The Hochschild cohomology of $U \fg$ can be expressed in terms of Lie algebra cohomology as $\Hoch^*(U\fg,U\fg) \simeq \clies(\fg, U\fg)$. 
+On the other hand, our model for the derived center ${\frak Z}(U(\fg))$ of $U \fg$ is the one-dimensional factorization algebra assigning 
+\[
+\clies(\fg \otimes \Omega^*(U), \cliels( \fg \otimes \Omega^*_c(U)))
+\]
+to each open set $U \subset \RR$.
+In particular, the factorization homology of the derived center along the closed manifold $S^1$ can be computed as
+\[
+\int_{S^1} {\frak Z}(U(\fg)) \simeq \clies(\fg[\epsilon], \cliels( \fg[\epsilon])),
+\]
+where $\epsilon$ is a formal variable of degree $+1$. 
+\brian{let's talk about this.}
+\end{eg}
 
@@
 \begin{thm}
+\label{thm: variant LQT}
 There is a natural transformation
@@
 
+This result yields the central claim of Theorem~\ref{thm: large N}, about the large $N$ limit of the centralizer.
+
+\begin{rmk}
+Loday and Procesi proved versions of the Loday-Quillen-Tsygan theorem for the Lie algebras $\mathfrak{o}_n$ and $\mathfrak{sp}_{2n}$,
+in which cyclic homology of the algebra is replaced by its dihedral homology.
+As nothing substantive changes in proving analogous versions of our results above, 
+we do not spell out the details here.
+\end{rmk}
+
 \begin{proof}
-We take for granted that the reader is familiar with the proof of the LQT theorem as articulated in \cite{LQ, Weibel, Loday}.
+We take for granted that the reader is familiar with the proof of the LQT theorem as articulated in \cite{LQ, Weibel, LodayCyclic}.
 Our primary modification is to replace the coinvariants $\cliels(\cL(A))_{\sl_\infty}$ by the invariants $\cliels(\cL(A))^{\sl_\infty}$.
@@
 which holds for every degree $n$ and hence yields the desired isomorphism~(\ref{invtoco}).
+\owen{MZ points out we should show the filtered colimit here commutes with taking invariants (which is a limit), 
+which should be true since filtered colimits commute with finite limits.}
 
@@
 
-We now recall two familiars fact about the Lie algebra cohomology of a semisimple Lie algebra~$\fg$:
+We now recall two familiar facts about the Lie algebra cohomology of a semisimple Lie algebra~$\fg$:
 \begin{itemize}
@@
 \end{itemize}
+Together these imply that for an arbitrary finite-dimensional module~$M$,
+\[
+\clies(\fg,M) \simeq \clies(\fg) \otimes M^\fg.
+\]
 Thus, we have a decomposition
@@
 
-%\bibliographystyle{alpha}
+\section{A factorization algebra arising from cyclic homology}
+
+We explain here how to construct a factorization algebra using cyclic homology,
+much as Lie algebra homology leads to an explicit factorization Lodayalgebra modeling the enveloping $E_n$ algebra. 
+Throughout this section, let $k$ denote the field $\RR$ or $\CC$; 
+by mimicking \cite{Knudsen}, one could also produce an explicit model over~$\QQ$.
+
+\begin{dfn}
+Let $A$ be a dg algebra over $k$, and let $\cA = A \otimes \Omega^*_c$ denote the associated cosheaf of dg algebras on~$\RR^n$.
+Let $\cC_A$ denote the precosheaf $\Cyc_*(\cA)[1]$ of cochain complexes on $\RR^n$,
+which assigns to each open set $U$, the 1-shifted cyclic chains on $\cA(U)$.
+\end{dfn}
+
+Note that for two algebras $B$ and $B'$,
+\[
+\Cyc_*(B) \oplus \Cyc_*(B') \simeq \Cyc_*(B \times B') .
+\] 
+The corresponding statement for ordinary Hochschild homology is induced by the projections $B \leftarrow B \times B' \to B'$, and any map of algebras that induces a quasi-isomorphism on Hochschild homology induces one on cyclic homology as well.
+See, for instance, 2.2.12 of \cite{LodayCyclic}. 
+Hence, for any finite collection of disjoint opens $U_1$, \dots, $U_k$, 
+we have
+\[
+\cC_A(U_1 \sqcup \cdots \sqcup U_k) \simeq \cC_A(U_1) \oplus \cdots \oplus \cC_A(U_k).
+\]
+(In this sense $\cC_A$ behaves like a cosheaf, up to quasi-isomorphism. 
+\owen{Does cyclic homology preserve filtered colimits? If so, I think $\cC_A$ may be a homotopy cosheaf.}
+\brian{Yes, see E.2.1.1 of \cite{LodayCyclic} on p. 59.}
+This property underlies the following claim.
+
+\begin{lmm}
+\label{lem: cycfact}
+The functor $\Sym(\cC_A)$ sending an open set $U \subset \RR^n$ to $\Sym(\cC_A(U))$ is a locally constant prefactorization algebra.
+\end{lmm}
+
+%\begin{rmk}
+%We note that, as with the definition of the Chevalley-Eilenberg chains of a local Lie algebra,
+%we use here a construction of cyclic chains that plays nicely with the kind of vector spaces relevant to this situation,
+%namely smooth sections of vector bundles.
+%Where the cyclic quotient $A^{\otimes n}/C_n$ would appear for an ordinary algebra in complex vector spaces,
+%we take the $\Omega^{0,*}(X^n)/C_n$ and so on.
+%\owen{I need to check that the $\Sym$ doesn't lead to issues \dots If we must, we can ignore the quasi-isomorphism and focus on the map just to cyclic homology.}
+%\end{rmk}
+
+\begin{proof}
+It remains to provide the structure maps of the putative prefactorization algebra.
+We need to provide a multilinear structure map 
+\beqn
+\label{eqn: desiredmap}
+\cC(U_1) \times \cdots \times \cC(U_n) \to \cC(V)
+\eeqn
+for any finite set of pairwise disjoint opens $U_1,\ldots, U_n$ inside a larger open $V$.
+For the cosheaf $\Omega^{0,*}_c$ on pairwise disjoint opens $U_1,\ldots, U_n$,
+the isomorphism of dg algebras
+\[
+\Omega^{*}_c(U_1) \oplus \cdots \oplus \Omega^{*}_c(U_n) \cong \Omega^{*}_c(U_1 \sqcup \cdots \sqcup U_n),
+\]
+determines a quasi-isomorphism
+\beqn
+\label{eqn:cyccosheaf}
+\Cyc_*(A \otimes \Omega^{*}_c(U_1)) \oplus \cdots \oplus \Cyc_*(A \otimes \Omega^{*}_c(U_n)) \xto{\simeq} \Cyc_*(A \otimes \Omega^{*}_c(U_1 \sqcup \cdots \sqcup U_n)).
+\eeqn
+The inclusion $U_1 \sqcup \cdots \sqcup U_n \hookrightarrow V$ then provides a map
+\[
+\Cyc_*(A \otimes \Omega^{*}_c(U_1 \sqcup \cdots \sqcup U_n)) \to \Cyc_*(A \otimes \Omega^{*}(V)),
+\]
+and so determines a map
+\beqn
+\label{eqn:map2}
+\Sym(\cC_A(U_1 \sqcup \cdots \sqcup U_n)) \to \Sym(\cC_A(V)).
+\eeqn
+Likewise, applying $\Sym$ to map~\eqref{eqn:cyccosheaf} provides
+\[
+\Sym(\cC_A(U_1)) \otimes \cdots \otimes \Sym(\cC_A(U_n)) \to \Sym(\cC_A(U_1 \sqcup \cdots \sqcup U_n)).
+\]
+We thus obtain the desired map \eqref{eqn: desiredmap} as a composite.
+This construction is automatically associative for nested inclusions of pairwise disjoint opens,
+and so $\Sym(\cC_A)$ is a prefactorization algebra.
+\end{proof}
+
+\begin{cor}
+For $A$ a dg algebra over $k$, Theorem~\ref{thm: variant LQT} provides a weak equivalence of prefactorization algebras
+\[
+\lqt: \clies(\sl_\infty(\Omega^*), \cliels(\cL(\cA))) \xto{\simeq} \clies(\sl_\infty(\Omega^*)) \otimes \Sym(\cC_A).
+\]
+Hence, the functor $\Sym(\cC_A)$ determines a locally constant factorization algebra on $\RR^n$, and hence an $E_n$ algebra.
+\end{cor}
+
+This result yields the latter part of Theorem~\ref{thm: large N}, about an explicit factorization algebra.
+
+\begin{rmk}
+As remarked earlier, the Loday-Procesi theorem for the Lie algebras $\mathfrak{o}_n$ and $\mathfrak{sp}_{2n}$,
+in which cyclic homology of the algebra is replaced by its dihedral homology,
+lead to an analogous class of factorization algebras.
+\end{rmk}
+
+%\section{Proof of Theorem~\ref{thm: large N}}
+
+\bibliographystyle{alpha}  
+\bibliography{centralize}
+
 %%\bibliographystyle{spmpsci}
-%\bibliography{hic}
 

### 2019-04-22 frame.tex
test of git
twisted

@@
 
+\begin{rmk}
+We briefly remark on a natural modification of the prefactorization algebra $\Sym(\cC_A)$. 
+For simplicity, suppose $A$ is an ordinary (non dg) algebra, and let $\chi \in \Cyc^m(A, A^\vee)$ be a cyclic {\em cocycle} of degree $m$.
+Consider, for each open $U \subset \RR^n$ the cochain complex
+\[
+\Tilde{\cC}_{A,\chi} (U) = \left(\Cyc_*(A \tensor \Omega^*_c(U))[1] \oplus \CC \cdot K , \d_{\rm Cyc} + K \cdot \chi \right) 
+\]
+where $K$ is a formal parameter of degree $-m+n+1$.
+Also, $\d_{\rm Cyc}$ is the cyclic differential and $\chi$ is defined on $m$-chains by the pairing between cyclic chains and cochains, together with integration along $U$:
+\[
+\chi (\alpha_1 \tensor \cdots \tensor \alpha_m) = \int_U \<\chi, \alpha_1 \tensor \cdots \tensor \alpha_m\> .
+\]
+The differential is extended to the entire cochain complex by the graded Leibniz rule. 
+By similar arguments as above, the assignment $U \subset \Tilde{\cC}_{A, \chi}$ is a precosheaf of cochain complexes and $\Sym\left(\Tilde{\cC}_{A,\chi}\right)$ is a prefactorization algebra. 
+As a precosheaf of graded vectors spaces one has $\Tilde{\cC}_{A, \chi} = \cC_A \oplus \ul{\CC}[m-n-1]$, where $\ul{\CC}$ is the constant precosheaf, so that we may think of $\Sym\left(\Tilde{\cC}_{A,\chi}\right)$ as a twisted version of $\Sym(\cC_A)$.
+These types of twisted \brian{what to say? check my degrees!}
+\end{rmk}
+
 \begin{cor}

### 2019-05-07 frame.tex
merge

@@
 where we also describe our results in detail.
-When $n=1$, however, note that we find that \owen{state the classical thing!}
+When $n=1$, however, note that we find that \owen{state the classical thing here!}
 
@@
 By similar arguments as above, the assignment $U \subset \Tilde{\cC}_{A, \chi}$ is a precosheaf of cochain complexes and $\Sym\left(\Tilde{\cC}_{A,\chi}\right)$ is a prefactorization algebra. 
-As a precosheaf of graded vectors spaces one has $\Tilde{\cC}_{A, \chi} = \cC_A \oplus \ul{\CC}[m-n-1]$, where $\ul{\CC}$ is the constant precosheaf, so that we may think of $\Sym\left(\Tilde{\cC}_{A,\chi}\right)$ as a twisted version of $\Sym(\cC_A)$.
+As a precosheaf of graded vectors spaces one has $\Tilde{\cC}_{A, \chi} = \cC_A \oplus \ul{k}[m-n-1]$, where $\ul{k}$ is the constant precosheaf with costalk $k$, so that we may think of $\Sym\left(\Tilde{\cC}_{A,\chi}\right)$ as a twisted version of $\Sym(\cC_A)$.
 These types of twisted \brian{what to say? check my degrees!}

### 2019-05-07 frame.tex

--- 2019-04-22 frame.tex
@@
 When $n=1$ and $\cC$ is chain complexes over the field $k$, 
-then $\Mod^{E_1}_A(\cC)$ is equivalent to $A-A$-bimodules and hence ${\frak Z}_{E_1}(f) \simeq \HH^*(A,B_f)$,
+then $\Mod^{E_1}_A(\cC)$ is equivalent to $A-A$-bimodules and hence ${\frak Z}_{E_1}(f) \simeq {\rm Hoch}^*(A,B_f)$,
 where $B_f$ denotes $B$ viewed as an $A-A$-bimodule via the map~$f$.
@@
 Recall now that $\UU_n \fg \simeq \Sym(\fg[1-n])$ as $\fg$-modules.
-Base change thus implies
+Base change thus implies that we have an equivalence
 \[
-{\rm Mor}_{\LMod_{\int_{S^{n-1}} \UU_n}} (\UU_n \fg, B_f)  \simeq {\rm Mor}_{U\fg} (k, B_f).
+{\rm Mor}_{\LMod_{\int_{S^{n-1}} \UU_n}} (\UU_n \fg, B_f)  \simeq {\rm Mor}_{U\fg} (k, B_f)
 \]
+of underlying chain complexes.
+(That is, we have an equivalence after applying forgetful functors.)
 The right hand side is precisely Lie algebra cochains of $\fg$ with coefficients in~$B_f$, as desired.
@@
 \]
-where $\epsilon$ is a formal variable of degree $+1$. 
-\brian{let's talk about this.}
+where $\epsilon$ is a formal variable of degree~$1$. 
+\brian{We should compare with Tamarkin-Tsygan's noncommutative claculus (cf. section 2.6).
+We could exhibit Theorem 2.7.1 explicitly in this case for the $E_n$ case with enveloping algebras.}
 \end{eg}
@@
 The corresponding statement for ordinary Hochschild homology is induced by the projections $B \leftarrow B \times B' \to B'$, and any map of algebras that induces a quasi-isomorphism on Hochschild homology induces one on cyclic homology as well.
-See, for instance, 2.2.12 of \cite{LodayCyclic}. 
+(See, for instance, \S2.2.12 of \cite{LodayCyclic}.)
 Hence, for any finite collection of disjoint opens $U_1$, \dots, $U_k$, 
@@
 \]
-(In this sense $\cC_A$ behaves like a cosheaf, up to quasi-isomorphism. 
-\owen{Does cyclic homology preserve filtered colimits? If so, I think $\cC_A$ may be a homotopy cosheaf.}
-\brian{Yes, see E.2.1.1 of \cite{LodayCyclic} on p. 59.}
+Moreover, for any nested sequence of inclusions $V_1 \subset V_2 \subset \cdots$ with $V = \bigcup_i V_i$,
+there is a quasi-isomorphism
+\[
+{\rm hocolim}(\cC_A(V_1) \to \cC_A(V_2) \to \cdots) \simeq \cC_A(V).
+\]
+(See E.2.1.1 of \cite{LodayCyclic}.)
+In this sense $\cC_A$ behaves like a cosheaf, up to quasi-isomorphism. 
 This property underlies the following claim.
@@
 
-%\section{Proof of Theorem~\ref{thm: large N}}
+\section{\owen{A stub about a twisted version of LQT}}
+
+\owen{Brian and I will later insert an expansion of the following.}
+
+Let $\chi \in \Cyc^m(A)$ is a cyclic cocycle of degree $m$. 
+Then $\chi$ determines a central extension $\cC(A)_\chi$ of $\Cyc_*(A)[1]$ as an abelian Lie algebra (cf. Heisenberg Lie algebras),
+but $\chi$ also maps to Lie algebra cochains $\clies(\gl_N(A))$ for every $N$ via the LQT map,
+and hence determines a central extension $\gl_N(A)_\chi$ of $\gl_N(A)$ as well.
+There is thus a $\chi$-twisted version of the LQT map
+\[
+\lqt_\chi: \Sym(\cC(A)_\chi) \to \cliels(\gl_N(A)_\chi)
+\]
+which is a quasi-isomorphism in the large $N$ limit.
+
+This induces $\chi$-twisted versions of all our enveloping $E_n$ algebra theorems (in large $N$ limit).
+
+%We briefly remark on a natural modification of the prefactorization algebra $\Sym(\cC_A)$. 
+%For simplicity, suppose $A$ is an ordinary (non dg) algebra, and let $\chi \in \Cyc^m(A)$ be a cyclic {\em cocycle} of degree $m$.
+%Consider for each open $U \subset \RR^n$ the cochain complex
+%\[
+%\Tilde{\cC}_{A,\chi} (U) = \left(\Cyc_*(A \tensor \Omega^*_c(U))[1] \oplus \CC \cdot K , \d_{\rm Cyc} + K \cdot \chi \right) 
+%\]
+%where $K$ is a formal parameter of degree $-m+n+1$.
+%Also, $\d_{\rm Cyc}$ is the cyclic differential and $\chi$ is defined on $m$-chains by the pairing between cyclic chains and cochains, together with integration along $U$:
+%\[
+%\chi ((a_1 \otimes \alpha_1) \tensor \cdots \tensor (a_m \otimes \alpha_m)) = \int_U \<\chi, a_1 \tensor \cdots \tensor a_m\> \alpha_1 \wedge \cdots \wedge \alpha_m.
+%\]
+%The differential is extended to the entire cochain complex by the graded Leibniz rule. 
+%By similar arguments as above, the assignment $U \subset \Tilde{\cC}_{A, \chi}$ is a precosheaf of cochain complexes and $\Sym\left(\Tilde{\cC}_{A,\chi}\right)$ is a prefactorization algebra. 
+%As a precosheaf of graded vectors spaces one has $\Tilde{\cC}_{A, \chi} = \cC_A \oplus \ul{\CC}[m-n-1]$, where $\ul{\CC}$ is the constant precosheaf, so that we may think of $\Sym\left(\Tilde{\cC}_{A,\chi}\right)$ as a twisted version of $\Sym(\cC_A)$.
+%These types of twisted \brian{what to say? check my degrees!}
+%
 

### 2019-05-07 frame.tex
Greg's edit

@@
 \def\mahmoud{\textcolor{green}{MZ: }\textcolor{green}}
+\def\greg{\textcolor{red}{GG: }\textcolor{red}}
 
@@
 \end{thm}
-
+\greg{shall explain/remind somewhere what is the $E_n$-structure there: namely induced by $E_n$-structure of $B$ and com mutliplication in $\clies$, namely convolution between an $E_\infty$-coalgebra and an $E_n$-algebra}
 By using Knudsen's results, we have the following consequence.
@@
 \end{cor}
-
+\greg{shall relate this to $P_n$-center of $\fg$. that shall also (but I have to think to the proof more), at least up to formality gives the $P_{n+1}$-structure on it. }
 This result generalizes the fact that $\Hoch^*(U\fg,U\fg) \simeq \clies(\fg, U\fg)$, since the associative algebra $U\fg$ is modeled by the locally constant one-dimensional factorization algebra that assigns $\cliels (\fg \otimes \Omega^*_c(U))$ to each open $U \subset \RR$.
@@
 Having an explicit presentation for the centralizer of a map of $E_n$ algebras allows for immediate calculations of factorization homology.
-Indeed, for $M$ a closed $n$-dimensional manifold,
+
+Indeed, as shown  in \cite{Knudsen}, 
+the enveloping $E_n$ algebras are homotopy $O(n)$-fixed points (in other words $\mathrm{Disk}_n$-algebras in the sense of~\cite{AF}) and hence determine factorization algebras on unoriented $n$-dimensional manifolds.
+
+Therefore, for $M$ a closed $n$-dimensional manifold, one has 
 \[
@@
 
-The explicit factorization algebras provide convenient methods for computing factorization homology.
-As shown in \owen{exact reference} in \cite{Knudsen}, 
-the enveloping $E_n$ algebras are homotopy $O(n)$-fixed points and hence determine factorization algebras on unoriented $n$-dimensional manifolds.
+Again, the explicit factorization algebras provide convenient methods for computing factorization homology.
 
+\greg{need to add a notation/convention somewhere including that $\Sigma^n$ will be shift functor, convention for grading and so on}
 \section{Enveloping $E_n$ algebras of Lie algebras}
@@
 
-An alternative characterization is found in Theorem 5.3.1.30 of~\cite{LurieHA}.
+An alternative characterization is found in Theorem 5.3.1.30 of~\cite{LurieHA} or Proposition 6.22 in~\cite{GTZ3}.
 
@@
 
-We record a key fact drawn from \cite{LurieHA} and~\cite{FrancisHH}, which generalizes this situation.
+We record a key fact drawn from \cite{LurieHA},~\cite{FrancisHH}  and \cite{GG-Notes}, which generalizes this situation.
 
@@
 
-See Remark 7.3.5.3 of \cite{LurieHA} and Section 2 of \cite{FrancisHH}.
+See Remark 7.3.5.3 of \cite{LurieHA}, Coroallary 13 in~\cite{GG-Notes} and Section 2 of \cite{FrancisHH}.
 Concretely, this claim arises from the fact that as a module over $A$ as an $E_n$ algebra, 
@@
 \]
-Recall now that $\UU_n \fg \simeq \Sym(\fg[1-n])$ as $\fg$-modules.
+Recall now that $\UU_n \fg \simeq \Sym(\fg[1-n])$ as $\fg$-modules \greg{shall we also need that it is true as $E_n$-algebra one we see right hand side as a $P_n$-algebra in the natrual way and use formality ?
+I feel we need to say something more to recover the $E_n$-structure below-something like the $E_n$-structure on Lie algebra cochains realizes teh moduel map structure after all equivalences we use}.
 Base change thus implies that we have an equivalence
@@
 
-\brian{do you like this example?}
+\brian{do you like this example?} \greg{I do !}
 \begin{eg}\label{eg: TT}
@@
 
-\begin{thm}
+\begin{thm}[\cite{LQ}]
 For $A$ a unital dg algebra over a characteristic zero field $k$,
@@
 \end{cor}
-
+\greg{why not state (in a remark) this corollary and the next one as syaing this is an equivalence in the $\infty$-categories of functor ?}
 For our purposes, a variant is more useful, but this variant follows by easy, formal arguments.
@@
 We explain here how to construct a factorization algebra using cyclic homology,
-much as Lie algebra homology leads to an explicit factorization Lodayalgebra modeling the enveloping $E_n$ algebra. 
+much as Lie algebra homology leads to an explicit factorization algebra modeling the enveloping $E_n$ algebra. 
 Throughout this section, let $k$ denote the field $\RR$ or $\CC$; 
@@
 \end{dfn}
-
+\greg{Here we shall either recall our model for cyclic chains, or first define the $\infty$-categorical universal statement and then precise a nice model.
+By the universal model, I mean define cyclic as the homotopy $S^1$-fixed point for the action on Hochschild chains.
+This will make the construction more transparent ?}
 Note that for two algebras $B$ and $B'$,

### 2019-05-13 frame.tex
mz's edit

@@
 
-Recently there has emerged a systematic generalization of the enveloping algebra $U\fg$ of a Lie algebra $\fg$ to {\em higher} enveloping algebras:
-each dg Lie algebra $\fg$ has an enveloping $E_n$ algebra $\UU_n\fg$.
-Building on prior work \cite{BD, AF}, Knudsen \cite{Knudsen} has developed these ideas extensively and offered useful models as factorization algebras.
-Our central goal here is to document generalizations of two important results about enveloping algebras of Lie algebras: 
+Recently, a generalization of the concept of the enveloping algebra of a Lie algebra has emerged: each dg Lie algebra $\fg$ has an $E_n$-enveloping algebra $\UU_n\fg$, for every $n$, so that $\UU_1\fg$ is the usual enveloping algebra $U\fg$.
+Building on prior work \cite{BD, AF} [Owen's thesis?], Knudsen \cite{Knudsen} developed these ideas extensively and offered a useful factorization algebra model for the $E_n$ enveloping algebra.
+Our central goal here is to generalize the following results about the enveloping algebra to all $n$.
+
 \begin{enumerate}
-\item[(1)] the (underived) center of $U\sl_{N+1}$ is isomorphic to $(\Sym(\CC^{N}))^{S_N}$, where we view $\CC^{N}$ as the Cartan subalgebra of $\sl_{N+1}$ and $S_N$ as the Weyl group of $SL_{N+1}$, and
-\item[(2)] the derived center of the enveloping algebra $U\fg$ is given by derived invariants of the adjoint action of $\fg$ on $U\fg$:
-\[
-\Hoch^*(U\fg,U\fg) \simeq \clies(\fg, U\fg),
-\]
+\item[(1)] the (underived) center of $U\sl_{N+1}$ is isomorphic to $(\Sym(\CC^{N}))^{S_N}$, where $\CC^{N}$ denotes the Cartan subalgebra of $\sl_{N+1}$ and $S_N$ is the Weyl group of $SL_{N+1}$, and
+\item[(2)] the derived center of the enveloping algebra $U\fg$ is given by derived invariants of the adjoint action of $\fg$ on $U\fg$. That is to say $\Hoch^*(U\fg,U\fg) \simeq \clies(\fg, U\fg)$.
 \end{enumerate}
-but in a way that works uniformly for these higher enveloping algebras.
 
-Our results include a cousin of these results where we vary (1) by taking the limit as $N \to \infty$ and vary (2) by studying the derived {\em centralizer} of a map $\UU_n\sl_\infty \hookrightarrow \UU_n\gl_\infty(A)$, where $A$ is a dg algebra.
-(The derived center is the centralizer of the identity map $\UU_n\fg \to \UU_n\fg$.)
-These notions will be reviewed and explained in the next section below,
-where we also describe our results in detail.
-When $n=1$, however, note that we find that \owen{state the classical thing here!}
+Our results pertains to (1) by taking $N \to \infty$, and to (2) through the derived {\em centralizer} of the map $\UU_n\sl_\infty \hookrightarrow \UU_n\gl_\infty(A)$, where $A$ is a dg algebra.
+Note that the usual derived center is the centralizer of the identity map $\UU_n\fg \to \UU_n\fg$.
 
-Our main tool for this result is the Loday-Quillen-Tsygan (LQT) theorem,
-which describes the large $N$ limit of Lie algebra homology of $\gl_N(A)$ for $A$ a dg algebra.
-Experts will know that enveloping $E_n$ algebras can be constructed using Chevalley-Eilenberg chains
-(i.e., that they are shifted versions of $\cliels$, in a precise sense),
-and hence will recognize the relevance of the LQT theorem in this context.
-From this perspective, our main result can be understood as an $E_n$ generalization of the LQT theorem.
+We will review these notions and describe our results in detail in the next section. When $n=1$,  \owen{state the classical thing here!}
 
-We hope these constructions and ideas have interesting applications to other large $N$ phenomena,
-such as in quantum field theory and random matrix theory.
+Our primary tool here is the Loday-Quillen-Tsygan (LQT) theorem, which describes the large $N$ limit of the Lie algebra homology of $\gl_N(A)$, for a dg associative algebra $A$.
+Since the $E_n$ enveloping algebra of a Lie algebra can be constructed as a locally constant factorization algebra that is made out of the shifted Chevalley-Eilenberg chains \cite{}, the relevance of the LQT theorem in this context becomes apparent.
+Thus, one can think of our main result as an $E_n$ generalization of the LQT theorem.
+We hope these ideas have exciting applications in quantum field theory and random matrix theory, as well as to other large $N$ limit phenomena.
 
@@
 Throughout this document, we will work with differential graded vector spaces over a field $k$ of characteristic zero.
-When we write ``Lie algebra,'' we mean a dg Lie algebra; if we mean an ordinary Lie algebra (such as $\sl_2(\CC)$), we say so explicitly.
-Similarly, ``algebra'' means ``dg algebra'' unless stated otherwise.
-Our theorems will be stated in terms of the stable $\infty$-category of such cochain complexes (one is free to work with the appropriate stable model or pretriangulated dg category, as one wishes).
-Many of our constructions involve, however, explicit manipulations with standard, explicit complexes.
-To minimize confusion, we try to indicate the level at which we are working but that may be left implicit in some places.
+We refer to dg Lie algebras simply as Lie algebra, and refer to those without grading and a differential, such as $\sl_2(\CC)$, as ordinary Lie algebras.
+Similarly, the term algebra means dg algebra unless stated otherwise.
+\end{rmk}
+
+\begin{rmk}
+We state our theorems in terms of the stable $\infty$-category cochain complexes instead of the appropriate stable model or pre-triangulated dg categories.
+Many of our constructions, however, involve explicit manipulations of standard complexes.
+We indicate the level at which we are working, when it is helpful.
 \end{rmk}
@@
 
-See section~\ref{sec: enveloping} for a summary of the enveloping $E_n$ algebra construction, 
-and see section~\ref{sec: centralizer} for a summary of centralizers of maps of $E_n$ algebras.
+See section~\ref{sec: enveloping} for a summary of the enveloping $E_n$ algebra construction, and see section~\ref{sec: centralizer} for a summary of centralizers of maps of $E_n$ algebras.
 
@@
 \label{thm: centralizer}
-Let $f: \UU_n \fg \to B$ denote a map of $E_n$ algebras, where $\UU_n \fg$ is the enveloping $E_n$ algebra of a dg Lie algebra $\fg$.
-In particular, $B$ is an $E_n$ algebra in $\fg$-modules via the map~$f$.
+Let $\UU_n \fg$ is the enveloping $E_n$ algebra of a dg Lie algebra $\fg$ and $f: \UU_n \fg \to B$ a map of $E_n$ algebras, which gives $B$ the structure of an $E_n$ algebra in $\fg$-modules.
+Then, the centralizer ${\frak Z}_{E_n}(f)$ is the $E_n$ algebra $\clies(\fg, B)$.
+\end{thm}
 
-The centralizer ${\frak Z}_{E_n}(f)$ is the $E_n$ algebra $\clies(\fg, B)$.
-\end{thm}
-\greg{shall explain/remind somewhere what is the $E_n$-structure there: namely induced by $E_n$-structure of $B$ and com mutliplication in $\clies$, namely convolution between an $E_\infty$-coalgebra and an $E_n$-algebra}
-By using Knudsen's results, we have the following consequence.
+\greg{shall explain/remind somewhere what is the $E_n$-structure there: namely induced by $E_n$-structure of $B$ and commutative multiplication in $\clies$, namely convolution between an $E_\infty$-coalgebra and an $E_n$-algebra}
+
+By Knudsen's results \cite{Knudsen}, we have the following consequence.
 
 \begin{cor}
-Let $\rho: \fg \to \fh$ be a map of dg Lie algebras, and let $\UU_n \rho$ denote the associated map of enveloping $E_n$ algebras.
-When $k$ is $\RR$ or $\CC$, 
-the centralizer ${\frak Z}_{E_n}(\UU_n \rho)$ is modeled by the locally constant factorization algebra that assigns
+Let $k$ is $\RR$ or $\CC$, and $\UU_n \rho:  \UU_n \fg \to \UU_n \fh$ be the induced by a map of Lie algebras $\rho: \fg \to \fh$.
+Then, the centralizer ${\frak Z}_{E_n}(\UU_n \rho)$ is modeled by the locally constant factorization algebra that assigns
 \[
@@
 \]
-to each open set $U \subset \RR^n$.
+to each open set $U \subset \RR^n$, where $\Omega^*_c(U)$ denoted the commutative differential graded algebra (cdga) of compactly supported forms on $U$.
 \end{cor}
 
-An immediate corollary, by taking the identity map, is the following.
+When $\rho: \fg \to \fg$ is the identity map, we have the following immediate corollary.
 
@@
 \label{thm: center}
-The center of the enveloping $E_n$ algebra $\UU_n\fg$ is the $E_n$ algebra $\clies(\fg, \UU_n\fg)$.
-(It has, of course, a natural $E_{n+1}$ algebra structure.)
-
-When $k$ is $\RR$ or $\CC$, 
-it is modeled by the locally constant factorization algebra that assigns
+The center of the enveloping $E_n$ algebra $\UU_n\fg$ is the $E_n$ algebra $\clies(\fg, \UU_n\fg)$, which by Dunn's additivity theorem has in fact a natural $E_{n+1}$ algebra structure.
+When $k$ is $\RR$ or $\CC$, the
+center is modeled by the locally constant factorization algebra that assigns
 \[
@@
 
-Having an explicit presentation for the centralizer of a map of $E_n$ algebras allows for immediate calculations of factorization homology.
-
-Indeed, as shown  in \cite{Knudsen}, 
-the enveloping $E_n$ algebras are homotopy $O(n)$-fixed points (in other words $\mathrm{Disk}_n$-algebras in the sense of~\cite{AF}) and hence determine factorization algebras on unoriented $n$-dimensional manifolds.
-
-Therefore, for $M$ a closed $n$-dimensional manifold, one has 
+Having an explicit presentation for the centralizer of a map of $E_n$ algebras leads to a calculations of factorization homology.
+The enveloping $E_n$ algebras are homotopy $O(n)$-fixed points, or a $\mathrm{Disk}_n$-algebras in the sense of~\cite{AF}, and hence determine factorization algebras on un-oriented $n$-dimensional manifolds \cite{Knudsen}.
+Therefore, for a closed $n$-dimensional manifold $M$, one has
 \[
@@
 \]
-When $M = S^n$, we thus see
+Since $\Omega^*(S^n) \simeq \CC[\epsilon_n]$, where $\epsilon_n$ is a formal variable with $|\epsilon_n| = n$ and $\epsilon_n^2 = 0$, we have
 \[
@@
 \]
-as $\Omega^*(S^n) \simeq \CC[\epsilon_n]$ where $\epsilon_n$ is a formal variable with $|\epsilon_n| = n$ and $\epsilon_n^2 = 0$.
-In the case that $n=1$, this recovers a theorem of Tamarkin-Tsygan \cite{TT} on the Hochschild cohomology of differential operators in the case of a group $G$ (see Example \ref{eg: TT}).
+
+For $n=1$, this recovers a theorem of Tamarkin and Tsygan \cite{TT} on the Hochschild cohomology of differential operators on a Lie group $G$; see Example \ref{eg: TT}.
 
 \begin{rmk}
-The preceding results are well-known to experts in factorization homology (we discussed it with several, including Francis and Knudsen),
-since they are quick consequences of published work, as will be seen below.
-But these statements seem not to have be documented yet in the literature, 
-and so we record them here.
+The preceding results are quick consequences of published work and are well-known to experts we spoke to, including John Francis and Ben Knudsen.
+Nevertheless, we record these results so they are documented in the literature.
 \end{rmk}
 
-Our primary large $N$ result is the following, which is the novel contribution of this paper.
+Our novel contribution in this paper is the following large $N$ result.
+Let $A$ be a unital algebra over a field $k$ of characteristic zero, and $u_A: \sl_\infty(k) \hookrightarrow \gl_\infty(A)$, the map of Lie algebras induced by the unit in $A$.
+The induced map $\UU_nu_A: \UU_n\sl_\infty(k) \to \UU_n\gl_\infty(A)$ makes $\UU_n\gl_\infty(A)$ is an $E_n$ algebra in $\sl_\infty(k)$-modules.
 
@@
 \label{thm: large N}
-Let $A$ be a unital algebra over a field $k$ of characteristic zero. 
-The map of Lie algebras
-\[
-u_A: \sl_\infty(k) \hookrightarrow \gl_\infty(A),
-\]
-induced by the unit in $A$, determines a map 
-\[
-\UU_nu_A: \UU_n\sl_\infty(k) \to \UU_n\gl_\infty(A).
-\]
-In particular, $\UU_n\gl_\infty(A)$ is an $E_n$ algebra in $\sl_\infty(k)$-representations.
 
-The centralizer ${\frak Z}_{E_n}(\UU_nu_A)$ of this map is the $E_n$ algebra obtained by forgetting the dg commutative algebra
+The centralizer ${\frak Z}_{E_n}(\UU_nu_A)$ of the map $\UU_nu_A$ is the $E_n$ algebra obtained by forgetting the dg commutative algebra
 \[
@@
 
-When $k$ is $\RR$ or $\CC$, 
-it is modeled by the locally constant factorization algebra that assigns
+When $k$ is $\RR$ or $\CC$, this centralizer is modeled by the locally constant factorization algebra that assigns
 \[
@@
 
-Although \cite{Knudsen} develops an adjunction between Lie and $E_n$ algebras in any presentable stable symmetric monoidal $\infty$-category $\cC$,
-we need his result only in the setting of chain complexes over a field $k$ of characteristic zero $\Mod_k$ with tensor product~$\otimes_k$.
-We summarize his result in that setting as follows.
+Although \cite{Knudsen} develops an adjunction between Lie and $E_n$ algebras in any presentable symmetric monoidal stable $\infty$-category $\cC$,
+we need his result only for that of chain complexes $(\Mod_k, \otimes_k)$, where $k$ is a field of characteristic zero. We summarize Knudsen's result in this setting as follows.
 
@@
 \]
-where $\Sigma$ denotes suspension \owen{because tikzcd does weird things with ``[1-n]'' instead}.
+where $\Sigma$ denotes suspension \owen{because tikzcd does weird things with ``[1-n]'' instead}, \mahmoud{earlier we denoted the shift by [n]. should we change that?}.
 (Curving arrows denote left adjoints.)
@@
 
-We provide a gloss of the main notions here but refer the reader to Section 5.3 of \cite{LurieHA} and \cite{FrancisHH} for extensive and detailed discussions.
-
+We briefly review some of the main notions and refer the reader to \cite{LurieHA} Section 5.3 and \cite{FrancisHH} for detailed discussions.
 Let $\cC^\otimes$ denote a presentable stable symmetric monoidal $\infty$-category (for us, chain complexes over a field $k$ of characteristic zero with~$\otimes_k$).
@@
 \]
-where $u$ is induced by the identity map $1_\cC \to {\frak Z}_{E_n}(f)$.
-
-The {\em center} of an $E_n$ algebra $A$ is the centralizer of its identity morphism $\id_A: A \to A$.
+where $u$ is induced by the identity map $1_\cC \to {\frak Z}_{E_n}(f)$. The {\em center} of an $E_n$ algebra $A$ is the centralizer of its identity morphism $\id_A: A \to A$.
 \end{dfn}
-
-When $n=1$ and $\cC$ just ordinary vector spaces, the centralizer of $f: A \to B$ thus consists of the subspace of elements of $B$ that commute with the image $f(A)$ inside~$B$.
-The center of $A$ thus recovers the traditional notion.
-
-An alternative characterization is found in Theorem 5.3.1.30 of~\cite{LurieHA} or Proposition 6.22 in~\cite{GTZ3}.
+When $n=1$ and $\cC$ is the category of vector spaces, the centralizer of $f: A \to B$ thus consists of the subspace of elements of $B$ that commute with the image $f(A)$ inside~$B$.
+Thus, the center of $A$ agrees with the traditional notion.
+See Theorem 5.3.1.30 of~\cite{LurieHA}, or Proposition 6.22 in~\cite{GTZ3}, for an alternative characterization.
 
@@
 
-When $n=1$ and $\cC$ is chain complexes over the field $k$, 
-then $\Mod^{E_1}_A(\cC)$ is equivalent to $A-A$-bimodules and hence ${\frak Z}_{E_1}(f) \simeq {\rm Hoch}^*(A,B_f)$,
-where $B_f$ denotes $B$ viewed as an $A-A$-bimodule via the map~$f$.
+When $n=1$ and $\cC$ is chain complexes over the field $k$, then $\Mod^{E_1}_A(\cC)$ is equivalent to $A\otimes A^{op}$-modules and hence ${\frak Z}_{E_1}(f) \simeq {\rm Hoch}^*(A,B_f)$,
+where $B_f$ denotes $B$ viewed as an $A\otimes A^{op}$-modules via the map~$f$.
 
@@
 Throughout this section, let $A$ be a dg algebra over a field $k$ of characteristic zero.
-We do not assume $A$ is unital; whenever unitality leads to a stronger result, we will explicitly add it as a hypothesis.
-(It is possible to work with $A_\infty$ algebras rather than dg algebras, 
-but it changes nothing structurally essential while adding a distracting layer of notational complexity.)
-
-\begin{dfn}
-Let $\cC(A)$ denote the cochain complex $\Cyc_*(A)[1]$, which may be viewed as an abelian Lie algebra. 
-Let $\cL(A)$ denote the dg Lie algebra $\gl_\infty(A)$.
-\end{dfn}
-
-Let $\sl_\infty$ denote $\sl_\infty(k)$, the trace-zero matrices of rank infinity with only finitely many nonzero entries in~$k$.
-Let $\gl_\infty$ denote $\gl_\infty(k)$, the matrices of rank infinity with only finitely many nonzero entries in~$k$.
-Let $\gl_\infty(A)$ denote the matrices of rank infinity with only finitely many nonzero entries in~$A$.
-There is a natural action of $\sl_\infty$ on $\gl_\infty(A)$, 
-and hence on its Chevalley-Eilenberg chains $\cliels(\cL(A))$.
-A key step in the LQT theorem is the construction of a quasi-isomorphism
+We do not assume $A$ is unital, unless we state otherwise.
+Also, it is possible to work with $A_\infty$ algebras rather than dg algebras, but it changes nothing structurally essential while it adds a distracting layer of complexity.
+Let $\cL(A)$ denote the dg Lie algebra $\gl_\infty(A)$ and $\cC(A)$ denote the cochain complex $\Cyc_*(A)[1]$ thought of as an abelian differential graded algebra.
+Let $\gl_\infty(A)$ denotes the infinite matrices with only finitely many nonzero entries in~$A$.
+Let $\gl_\infty$ stand for $\gl_\infty(k)$ and $\sl_\infty=\sl_\infty(k)$ denote the sub Lie algebra of the elements of trace is zero.
+There is a natural action of $\sl_\infty$ on $\gl_\infty(A)$, and hence on its Chevalley-Eilenberg chains $\cliels(\cL(A))$.
+A key step in the LQT theorem is the construction of an isomorphism
 \beqn\label{lqtco}
@@
 between these two functors from the dg category of unital dg algebras to the dg category of dg cocommutative Hopf algebras over~$k$.
-It is a quasi-isomorphism on every algebra.
+Furthermore, the induced natural transformation on the homotopy categories is a natural isomorphism.
 \end{cor}
-\greg{why not state (in a remark) this corollary and the next one as syaing this is an equivalence in the $\infty$-categories of functor ?}
-For our purposes, a variant is more useful, but this variant follows by easy, formal arguments.
+\greg{why not state (in a remark) this corollary and the next one as saying this is an equivalence in the $\infty$-categories of functor ?}
+For our purposes, the following variant, which follows easy by formal arguments, is more useful.
 
@@
 \]
-between these two functors from the dg category of {\em non}unital dg algebras to the dg category of dg Hopf algebras over~$k$.
+between these two functors from the dg category of {\em non-unital} dg algebras to the dg category of dg Hopf algebras over~$k$.
 For each nonunital dg algebra $A$, the map
@@
 \begin{rmk}
-Loday and Procesi proved versions of the Loday-Quillen-Tsygan theorem for the Lie algebras $\mathfrak{o}_n$ and $\mathfrak{sp}_{2n}$,
-in which cyclic homology of the algebra is replaced by its dihedral homology.
-As nothing substantive changes in proving analogous versions of our results above, 
-we do not spell out the details here.
+Loday and Procesi proved versions of the LQT theorem for the Lie algebras $\mathfrak{o}_n$ and $\mathfrak{sp}_{2n}$, in which cyclic homology is replaced by dihedral homology.
+As nothing substantive changes in proving analogous versions of our results above, we do not spell out the details here.
 \end{rmk}
@@
 \eeqn
-and in fact this map is an isomorphism, which we now show.
+which we now show is an isomorphism.
 
-To see this claim, we need to understand how $\sl_\infty$ acts on the underlying graded module of $\cliels(\cL(A))$.
+To see this, we need to understand how $\sl_\infty$ acts on the underlying graded module of $\cliels(\cL(A))$.
 Note that as a $k$-module, $\cL(A) \cong \gl_\infty \otimes A$, which is a free $k$-module.
@@
 \]
-Taking the coinvariants under the action of the symmetric group $S_n$
-(which acts diagonally on the $\gl_\infty$ factor and the $A$ factor),
+Taking the coinvariants under the action of the symmetric group $S_n$, which acts diagonally on the $\gl_\infty$ factor and the $A$ factor, 
 we obtain
@@
 \]
-But the action of $\sl_\infty$ is then wholly on the left hand factor, leaving $A$ independent.
+But the action of $\sl_\infty$ is then solely on the left hand factor, leaving $A$ untouched.
 
@@
 This will make the construction more transparent ?}
+\mahmoud{cyclic is the homotopy quotient and negative cyclic the homotopy fixed points}
 Note that for two algebras $B$ and $B'$,

### 2019-05-14 frame.tex
Add files via upload

@@
 
-Recently, a generalization of the concept of the enveloping algebra of a Lie algebra has emerged: each dg Lie algebra $\fg$ has an $E_n$-enveloping algebra $\UU_n\fg$, for every $n$, so that $\UU_1\fg$ is the usual enveloping algebra $U\fg$.
-Building on prior work \cite{BD, AF} [Owen's thesis?], Knudsen \cite{Knudsen} developed these ideas extensively and offered a useful factorization algebra model for the $E_n$ enveloping algebra.
-Our central goal here is to generalize the following results about the enveloping algebra to all $n$.
+Recently, a generalization of the concept of the enveloping algebra of a Lie algebra has emerged: each dg Lie algebra $\fg$ has an enveloping $E_n$ algebra $\UU_n\fg$, for every $n$, so that $\UU_1\fg$ is the usual enveloping algebra $U\fg$.
+Building on prior work \cite{BD, AF} [Owen's thesis?], Knudsen \cite{Knudsen} developed these ideas extensively and offered a useful factorization algebra model for the enveloping $E_n$ algebra.
+Our central goal here is to generalize the following results about the enveloping algebra $U\fg$ to $\UU_n\fg$, for all $n$.
 
@@
 
-Our primary tool here is the Loday-Quillen-Tsygan (LQT) theorem, which describes the large $N$ limit of the Lie algebra homology of $\gl_N(A)$, for a dg associative algebra $A$.
-Since the $E_n$ enveloping algebra of a Lie algebra can be constructed as a locally constant factorization algebra that is made out of the shifted Chevalley-Eilenberg chains \cite{}, the relevance of the LQT theorem in this context becomes apparent.
-Thus, one can think of our main result as an $E_n$ generalization of the LQT theorem.
+Our primary tool here is the Loday-Quillen-Tsygan (LQT) theorem which describes the large $N$ limit of the Lie algebra homology of $\gl_N(A)$, for a dg associative algebra $A$.
+Since the enveloping $E_n$ algebra of a Lie algebra can be constructed as a locally constant factorization algebra made out of the shifted Chevalley-Eilenberg chains \cite{}, the relevance of the LQT theorem in this context  should be apparent.
+From this point of view, one can think of our main result as an $E_n$ generalization of the LQT theorem.
 We hope these ideas have exciting applications in quantum field theory and random matrix theory, as well as to other large $N$ limit phenomena.
@@
 \begin{rmk}
-We state our theorems in terms of the stable $\infty$-category cochain complexes instead of the appropriate stable model or pre-triangulated dg categories.
-Many of our constructions, however, involve explicit manipulations of standard complexes.
-We indicate the level at which we are working, when it is helpful.
+We state our theorems in terms of the stable $\infty$-category cochain complexes instead of the appropriate stable model categories or pre-triangulated dg categories.
+Many of our constructions, however, involve explicit manipulations of standard complexes, and when it is helpful, we indicate the level at which we are working.
 \end{rmk}
@@
 \label{thm: centralizer}
-Let $\UU_n \fg$ is the enveloping $E_n$ algebra of a dg Lie algebra $\fg$ and $f: \UU_n \fg \to B$ a map of $E_n$ algebras, which gives $B$ the structure of an $E_n$ algebra in $\fg$-modules.
+Let $\UU_n \fg$ be the enveloping $E_n$ algebra of a dg Lie algebra $\fg$ and $f: \UU_n \fg \to B$ a map of $E_n$ algebras which gives $B$ the structure of an $E_n$ algebra in $\fg$-modules.
 Then, the centralizer ${\frak Z}_{E_n}(f)$ is the $E_n$ algebra $\clies(\fg, B)$.
@@
 \begin{cor}
-Let $k$ is $\RR$ or $\CC$, and $\UU_n \rho:  \UU_n \fg \to \UU_n \fh$ be the induced by a map of Lie algebras $\rho: \fg \to \fh$.
+Let $k$ is $\RR$ or $\CC$, and assume $\UU_n \rho:  \UU_n \fg \to \UU_n \fh$ is induced by a map of Lie algebras $\rho: \fg \to \fh$.
 Then, the centralizer ${\frak Z}_{E_n}(\UU_n \rho)$ is modeled by the locally constant factorization algebra that assigns
@@
 \]
-to each open set $U \subset \RR^n$, where $\Omega^*_c(U)$ denoted the commutative differential graded algebra (cdga) of compactly supported forms on $U$.
+to each open set $U \subset \RR^n$. Here, $\Omega^*_c(U)$ denotes the commutative differential graded algebra (cdga) of compactly supported forms on $U$.
 \end{cor}
 
-When $\rho: \fg \to \fg$ is the identity map, we have the following immediate corollary.
+If $\rho: \fg \to \fg$ is the identity map, we get the following immediate corollary.
 
@@
 \end{cor}
-\greg{shall relate this to $P_n$-center of $\fg$. that shall also (but I have to think to the proof more), at least up to formality gives the $P_{n+1}$-structure on it. }
+\greg{shall relate this to $P_n$-center of $\fg$. that shall also (but I have to think about the proof more), at least up to formality gives the $P_{n+1}$-structure on it. }
 This result generalizes the fact that $\Hoch^*(U\fg,U\fg) \simeq \clies(\fg, U\fg)$, since the associative algebra $U\fg$ is modeled by the locally constant one-dimensional factorization algebra that assigns $\cliels (\fg \otimes \Omega^*_c(U))$ to each open $U \subset \RR$.
 
-Having an explicit presentation for the centralizer of a map of $E_n$ algebras leads to a calculations of factorization homology.
-The enveloping $E_n$ algebras are homotopy $O(n)$-fixed points, or a $\mathrm{Disk}_n$-algebras in the sense of~\cite{AF}, and hence determine factorization algebras on un-oriented $n$-dimensional manifolds \cite{Knudsen}.
+Having an explicit presentation for the centralizer of a map of $E_n$ algebras leads to a calculation of factorization homology.
+The enveloping $E_n$ algebra is the homotopy $O(n)$-fixed points, or a $\mathrm{Disk}_n$-algebra in the sense of~\cite{AF}, and hence determines a factorization algebra on any un-oriented $n$-dimensional manifold \cite{Knudsen}.
 Therefore, for a closed $n$-dimensional manifold $M$, one has
@@
 Our novel contribution in this paper is the following large $N$ result.
-Let $A$ be a unital algebra over a field $k$ of characteristic zero, and $u_A: \sl_\infty(k) \hookrightarrow \gl_\infty(A)$, the map of Lie algebras induced by the unit in $A$.
+Let $A$ be a unital algebra over a field $k$ of characteristic zero, and $u_A: \sl_\infty(k) \hookrightarrow \gl_\infty(A)$ be the map of Lie algebras determined by the unit in $A$.
 The induced map $\UU_nu_A: \UU_n\sl_\infty(k) \to \UU_n\gl_\infty(A)$ makes $\UU_n\gl_\infty(A)$ is an $E_n$ algebra in $\sl_\infty(k)$-modules.
@@
 
-Again, the explicit factorization algebras provide convenient methods for computing factorization homology.
+We can calculate the factorization homology of this factorization algebra explicitly.
 
@@
 
-Although \cite{Knudsen} develops an adjunction between Lie and $E_n$ algebras in any presentable symmetric monoidal stable $\infty$-category $\cC$,
-we need his result only for that of chain complexes $(\Mod_k, \otimes_k)$, where $k$ is a field of characteristic zero. We summarize Knudsen's result in this setting as follows.
+Although \cite{Knudsen} develops an adjunction between Lie and $E_n$ algebras \mahmoud{non-unital?} in any presentable symmetric monoidal stable $\infty$-category $\cC$,
+we only work in the infinity category of chain complexes $(\Mod_k, \otimes_k)$, where $k$ is a field of characteristic zero. We summarize Knudsen's result in this setting as follows.
 
@@
 \]
-where $\Sigma$ denotes suspension \owen{because tikzcd does weird things with ``[1-n]'' instead}, \mahmoud{earlier we denoted the shift by [n]. should we change that?}.
+
+\mahmoud{explain what oblv stands for}
+where $\Sigma$ denotes suspension \owen{because tikzcd does weird things with ``[1-n]'' instead}, \mahmoud{earlier we denoted the shift by [n]. should we use $\Sigma^n$ everywhere?}.
 (Curving arrows denote left adjoints.)
@@
 
-The second part of this result implies the explicit models in our theorems.
+The second part of this result leads to the explicit models in our theorems.
 
@@
 For a map $f: A \to B$ of $E_n$ algebras in $\cC$, 
-the {\em centralizer} ${\frak Z}_{E_n}(f)$ is the $E_n$ algebra in $\cC$ that is universal among those that sit in a commuting diagram
+the {\em centralizer} ${\frak Z}_{E_n}(f)$ is the $E_n$ algebra in $\cC$ that is universal among those that fit in a commuting diagram
 \[
@@
 \end{dfn}
-When $n=1$ and $\cC$ is the category of vector spaces, the centralizer of $f: A \to B$ thus consists of the subspace of elements of $B$ that commute with the image $f(A)$ inside~$B$.
+When $n=1$ and $\cC$ is the category of vector spaces, the centralizer of $f: A \to B$ consists of the subspace of elements of $B$ that commute with the image $f(A)$ inside~$B$.
 Thus, the center of $A$ agrees with the traditional notion.
@@
 The centralizer ${\frak Z}_{E_n}(f)$ can be identified with the classifying object for maps from $A$ to $B$ in the $\infty$-category $\Mod^{E_n}_A(\cC)$.
+\mahmoud{we should probably spell out the meaning of the classifying object in this case to make it obvious that the centralizer is the classifying object}
 \end{prp}
@@
 which integrates all those actions and through which they all factor.
+\mahmoud{i think the picture of why it is a one-sided action is clearer if we use $S^{n-1} \times \RR^+$ istead of $S^{n-1} \times \RR$}
 As shown in Theorem 7.5.3.1 of \cite{LurieHA} and earlier in Proposition 3.16 of \cite{FrancisHH}, 
@@
 
-Let $\fg$ be a dg Lie algebra, let $B$ be an $E_n$ algebra, and let $f: \UU_n \fg \to B$ be a map of $E_n$ algebras.
-Then the results of the preceding section imply
+Let $f: \UU_n \fg \to B$ denote a map of $E_n$ algebras between the enveloping $E_n$ algebra of a dg Lie algebra $\fg$ and an $E_n$ algebra $B$.
+The results of the preceding section imply
 \begin{align*}
-{\frak Z}_{E_n}(f) &\simeq {{\rm Mor}}_{\Mod^{E_n}_{\UU_n}}(\UU_n \fg, B_f) \\
-&\simeq {\rm Mor}_{\LMod_{\int_{S^{n-1}} \UU_n}}(\UU_n \fg, B_f)
+{\frak Z}_{E_n}(f) &\simeq {{\rm Mor}}_{\Mod^{E_n}_{\UU_n\fg}}(\UU_n \fg, B_f) \\
+&\simeq {\rm Mor}_{\LMod_{\int_{S^{n-1}} \UU_n\fg}}(\UU_n \fg, B_f)
 \end{align*}
@@
 \begin{itemize}
-\item $B_f$ denotes the object in $\Mod^{E_n}_{\UU_n}$ or, equivalently, in $\LMod_{\int_{S^{n-1}}\UU_n}$ determined by~$f$,
-\item ${\rm Mor}_{\Mod^{E_n}_{\UU_n}}(\UU_n \fg, B)$ denotes the classifying object for maps from $\UU_n$ to $B_f$ in the $\infty$-category $\Mod^{E_n}_{\UU_n}$ (i.e., an internal mapping object),
-\item and ${\rm Mor}_{\LMod_{\int_{S^{n-1}} \UU_n}} (\UU_n \fg, B_f)$ denotes the classifying object for maps from ${\UU_n}$ to $B$ in the $\infty$-category $\LMod_{\int_{S^{n-1}}\UU_n}$.
+\item[-] $B_f$ denotes the object in $\Mod^{E_n}_{\UU_n\fg}$, as well as in $\LMod_{\int_{S^{n-1}}\UU_n}$, determined by~$f$, 
+\item[-] ${\rm Mor}_{\Mod^{E_n}_{\UU_n\fg}}(\UU_n \fg, B)$ denotes the classifying object for maps from $\UU_n\fg$ to $B_f$ in the $\infty$-category $\Mod^{E_n}_{\UU_n\fg}$ (i.e.
+an internal mapping object), and
+\item[-] ${\rm Mor}_{\LMod_{\int_{S^{n-1}} \UU_n\fg}} (\UU_n \fg, B_f)$ denotes the classifying object for maps from ${\UU_n\fg}$ to $B$ in the $\infty$-category $\LMod_{\int_{S^{n-1}}\UU_n\fg}$.
 \end{itemize}
-Observe now that $\int_{S^{n-1}}\UU_n$ is an $E_1$ algebra equivalent to the dg algebra $U(\fg \otimes k[\epsilon_{n-1}])$.
+Note that $\int_{S^{n-1}}\UU_n\fg$ is an $E_1$ algebra equivalent to the dg algebra $U(\fg \otimes k[\epsilon_{n-1}])$.
 This is because the rational $(n-1)$-sphere is formal, and hence its cochains are quasi-isomorphic to its cohomology $k[\epsilon_{n-1}]$.
@@
 \]
-Recall now that $\UU_n \fg \simeq \Sym(\fg[1-n])$ as $\fg$-modules \greg{shall we also need that it is true as $E_n$-algebra one we see right hand side as a $P_n$-algebra in the natrual way and use formality ?
-I feel we need to say something more to recover the $E_n$-structure below-something like the $E_n$-structure on Lie algebra cochains realizes teh moduel map structure after all equivalences we use}.
-Base change thus implies that we have an equivalence
+Recall now that $\UU_n \fg \simeq \Sym(\fg[1-n])$ as $\fg$-modules \greg{shall we also need that it is true as $E_n$-algebra one we see right hand side as a $P_n$-algebra in the natural way and use formality ?
+I feel we need to say something more to recover the $E_n$-structure below ...
+something like the $E_n$-structure on Lie algebra cochains realizes the module map structure after all equivalences we use}.
+Thus, base change \mahmoud{which is a map of $E_n$ algebras?} gives rise to an equivalence 
 \[
@@
 \]
-of underlying chain complexes.
-(That is, we have an equivalence after applying forgetful functors.)
-The right hand side is precisely Lie algebra cochains of $\fg$ with coefficients in~$B_f$, as desired.
+of underlying chain complexes, i.e. an equivalence after applying forgetful functor. The right hand side is precisely Lie algebra cochains of $\fg$ with coefficients in~$B_f$, as desired.
 
@@
 where $\epsilon$ is a formal variable of degree~$1$. 
-\brian{We should compare with Tamarkin-Tsygan's noncommutative claculus (cf. section 2.6).
+\brian{We should compare with Tamarkin-Tsygan's noncommutative calculus (cf. section 2.6).
 We could exhibit Theorem 2.7.1 explicitly in this case for the $E_n$ case with enveloping algebras.}
@@
 We do not assume $A$ is unital, unless we state otherwise.
-Also, it is possible to work with $A_\infty$ algebras rather than dg algebras, but it changes nothing structurally essential while it adds a distracting layer of complexity.
-Let $\cL(A)$ denote the dg Lie algebra $\gl_\infty(A)$ and $\cC(A)$ denote the cochain complex $\Cyc_*(A)[1]$ thought of as an abelian differential graded algebra.
-Let $\gl_\infty(A)$ denotes the infinite matrices with only finitely many nonzero entries in~$A$.
-Let $\gl_\infty$ stand for $\gl_\infty(k)$ and $\sl_\infty=\sl_\infty(k)$ denote the sub Lie algebra of the elements of trace is zero.
+More generally, it possible to work with $A_\infty$ algebras, which changes nothing essentially, while it adds a distracting layer of complexity.
+Let $\cL(A)$ stand for the dg Lie algebra $\gl_\infty(A)$ of infinite matrices with only finitely many nonzero entries in~$A$, and $\cC(A)$ the cochain complex $\Cyc_*(A)[1]$ thought of as an abelian differential graded algebra.
+Let $\gl_\infty$ stand for $\gl_\infty(k)$ and $\sl_\infty=\sl_\infty(k)$ denote the sub Lie algebra of those elements that have trace zero.
 There is a natural action of $\sl_\infty$ on $\gl_\infty(A)$, and hence on its Chevalley-Eilenberg chains $\cliels(\cL(A))$.
-A key step in the LQT theorem is the construction of an isomorphism
+A key step in the LQT theorem is the construction of an isomorphism of graded vector spaces
 \beqn\label{lqtco}
@@
 \begin{thm}[\cite{LQ}]
-For $A$ a unital dg algebra over a characteristic zero field $k$,
-there is a quasi-isomorphism
+For $A$ a unital dg algebra over a field $k$ of characteristic zero, there is a quasi-isomorphism
 \beqn\label{lqt}
@@
 
-For us it is the coalgebra structure that is particularly important, although the full Hopf algebra structure is typically emphasized.
+While the full Hopf algebra structure is typically emphasized, it is the coalgebra structure that is of particularly importance to us.
 
-As the constructions are natural in the algebra $A$, one can phrase a stronger but more abstract statement.
+The naturality of the above constructions in $A$, leads to the following more abstract yet stronger statement.
 
@@
 
-This result yields the central claim of Theorem~\ref{thm: large N}, about the large $N$ limit of the centralizer.
+This result yields the central claim of Theorem~\ref{thm: large N} about the large $N$ limit of the centralizer.
 
@@
 \begin{rmk}
-As remarked earlier, the Loday-Procesi theorem for the Lie algebras $\mathfrak{o}_n$ and $\mathfrak{sp}_{2n}$,
-in which cyclic homology of the algebra is replaced by its dihedral homology,
-lead to an analogous class of factorization algebras.
+The Loday and Procesi theorem for the Lie algebras $\mathfrak{o}_n$ and $\mathfrak{sp}_{2n}$ replaces cyclic homology with the dihedral homology and leads to an analogous class of factorization algebras.
 \end{rmk}
@@
 
-%%\bibliographystyle{spmpsci}
+%\bibliographystyle{spmpsci}
 

### 2019-05-14 frame.tex
small reminders for stuff for o to do

@@
 \def\owen{\textcolor{magenta}{OG: }\textcolor{magenta}}
-\def\mahmoud{\textcolor{green}{MZ: }\textcolor{green}}
+\def\mahmoud{\textcolor{olive}{MZ: }\textcolor{olive}}
 \def\greg{\textcolor{red}{GG: }\textcolor{red}}
@@
 \label{thm: center}
-The center of the enveloping $E_n$ algebra $\UU_n\fg$ is the $E_n$ algebra $\clies(\fg, \UU_n\fg)$, which by Dunn's additivity theorem has in fact a natural $E_{n+1}$ algebra structure.
+The center of the enveloping $E_n$ algebra $\UU_n\fg$ is the $E_n$ algebra $\clies(\fg, \UU_n\fg)$. 
 When $k$ is $\RR$ or $\CC$, the 
@@
 \end{cor}
+
+\owen{Add remark for ", which by Dunn's additivity theorem has in fact a natural $E_{n+1}$ algebra structure."}
+
 \greg{shall relate this to $P_n$-center of $\fg$. that shall also (but I have to think about the proof more), at least up to formality gives the $P_{n+1}$-structure on it. }
@@
 Concretely, this claim arises from the fact that as a module over $A$ as an $E_n$ algebra, 
-$M \in \Mod^{E_n}_A(\cC)$ is equipped with a commuting family of actions by $A$ parametrized by $\RR^n \setminus \{0\}$.
+$M \in \Mod^{E_n}_A(\cC)$ is equipped with a commuting family of actions by $A$ parametrized by $\RR^n \setminus \{0\}\cong S^{n-1} \times \RR_{>0}$.
 This action factors through the left action of the $E_1$ algebra $\int_{S^{n-1} \times \RR} A$ arising from factorization homology over the complement of the origin,

### 2019-05-17 frame.tex
my changs

@@
 \label{thm: center}
-The center of the enveloping $E_n$ algebra $\UU_n\fg$ is the $E_n$ algebra $\clies(\fg, \UU_n\fg)$. 
+The center ${\frak Z}_{E_n}(\UU_n\fg)$ of the enveloping $E_n$ algebra $\UU_n\fg$ is the $E_n$ algebra $\clies(\fg, \UU_n\fg)$. 
 When $k$ is $\RR$ or $\CC$, the 
@@
 
-\owen{Add remark for ", which by Dunn's additivity theorem has in fact a natural $E_{n+1}$ algebra structure."}
+In fact, ${\frak Z}_{E_n}(\UU_n\fg)$ has a natural $E_{n+1}$ algebra structure, 
+as shown in \cite{LurieHA, GTZ}, 
+but we will not examine it here.
 
@@
 This result generalizes the fact that $\Hoch^*(U\fg,U\fg) \simeq \clies(\fg, U\fg)$, since the associative algebra $U\fg$ is modeled by the locally constant one-dimensional factorization algebra that assigns $\cliels (\fg \otimes \Omega^*_c(U))$ to each open $U \subset \RR$.
+
+As another consequence of the theorem, we note that we recover an explicit model for the Koszul dual to the enveloping algebra. 
+Namely, take $B$ to be the unit $E_n$ algebra $k$ (alternatively, take the enveloping $E_n$ algebra of the trivial Lie algebra $\fh = 0$).
+
+\begin{cor}
+\label{thm: koszul}
+The $E_n$ Koszul dual of the enveloping $E_n$ algebra $\UU_n\fg$ is the underlying $E_n$ algebra of the $\clies(\fg)$. 
+When $k$ is $\RR$ or $\CC$, the 
+center is modeled by the locally constant factorization algebra that assigns
+\[
+\clies(\fg \otimes \Omega^*(U)))
+\]
+to each open set $U \subset \RR^n$.
+\end{cor}
 
@@
 \begin{tikzcd}
-\Alg_\Lie(\Mod_k) \arrow[r, bend left=20, shift left=.5ex,"\UU_n"] \arrow[dd] & \Alg_{E_n}(\Mod_k) \arrow[l, shift left=.5ex, "\oblv"] \arrow[dd]\\
+\Alg_\Lie(\Mod_k) \arrow[r, bend left=20, shift left=.5ex,"\UU_n"] \arrow[dd, "\oblv"] & \Alg_{E_n}(\Mod_k) \arrow[l, shift left=.5ex, "\oblv"] \arrow[dd, swap, "\oblv"]\\
 &\\
-\Mod_k \arrow[r, bend left=20, shift left=.5ex, "\Sigma^{1-n}"] \arrow[uu, bend left=20, shift left=.5ex, "\Free_\Lie"] & \Mod_k \arrow[l, shift left=.5ex,"\Sigma^{n-1}"] \arrow[uu, bend right=20, shift right=.5ex, "\Free_{E_n}"']
+\Mod_k \arrow[r, bend left=20, shift left=.5ex, "\text{$[1-n]$}"] \arrow[uu, bend left=20, shift left=.5ex, "\Free_\Lie"] & \Mod_k \arrow[l, shift left=.5ex, "\text{$[n-1]$}"] \arrow[uu, bend right=20, shift right=.5ex, "\Free_{E_n}"']
 \end{tikzcd}
 \]
-
-\mahmoud{explain what oblv stands for}
-where $\Sigma$ denotes suspension \owen{because tikzcd does weird things with ``[1-n]'' instead}, \mahmoud{earlier we denoted the shift by [n]. should we use $\Sigma^n$ everywhere?}.
+where $\oblv$ denotes a forgetful functor.
 (Curving arrows denote left adjoints.)
@@
 Thus, the center of $A$ agrees with the traditional notion.
-See Theorem 5.3.1.30 of~\cite{LurieHA}, or Proposition 6.22 in~\cite{GTZ3}, for an alternative characterization.
+See Theorem 5.3.1.30 of~\cite{LurieHA}, or Proposition 6.22 in~\cite{GTZ3}, for an alternative characterization,
+as follows.
 
 \begin{prp}
-The centralizer ${\frak Z}_{E_n}(f)$ can be identified with the classifying object for maps from $A$ to $B$ in the $\infty$-category $\Mod^{E_n}_A(\cC)$.
-\mahmoud{we should probably spell out the meaning of the classifying object in this case to make it obvious that the centralizer is the classifying object}
+The centralizer ${\frak Z}_{E_n}(f)$ can be identified with the classifying object for maps from $A$ to $B$ in the $\infty$-category~$\Mod^{E_n}_A(\cC)$.
 \end{prp}
+
+Here ``classifying object'' means an internal hom object, so that a map from $M$ to ${\frak Z}_{E_n}(f)$ in $\Mod^{E_n}_A(\cC)$ corresponds to a map from $M \otimes A$ to $B$ in $\Mod^{E_n}_A(\cC)$. 
+(More carefully, there is an equivalence of the appropriate mapping spaces in that category.)
+\owen{We should double check this.}
 

### 2019-05-19 frame.tex
twisted

--- 2019-05-14 frame.tex
@@
 
-Recently, a generalization of the concept of the enveloping algebra of a Lie algebra has emerged: each dg Lie algebra $\fg$ has an enveloping $E_n$ algebra $\UU_n\fg$, for every $n$, so that $\UU_1\fg$ is the usual enveloping algebra $U\fg$.
-Building on prior work \cite{BD, AF} [Owen's thesis?], Knudsen \cite{Knudsen} developed these ideas extensively and offered a useful factorization algebra model for the enveloping $E_n$ algebra.
-Our central goal here is to generalize the following results about the enveloping algebra $U\fg$ to $\UU_n\fg$, for all $n$.
+Recently there has emerged a systematic generalization of the enveloping algebra $U\fg$ of a Lie algebra $\fg$ to {\em higher} enveloping algebras:
+each dg Lie algebra $\fg$ has an enveloping $E_n$ algebra $\UU_n\fg$.
+Building on prior work \cite{BD, AF}, Knudsen \cite{Knudsen} has developed these ideas extensively and offered useful models as factorization algebras.
+Our central goal here is to document generalizations of two important results about enveloping algebras of Lie algebras: 
+\begin{enumerate}
+\item[(1)] the (underived) center of $U\sl_{N+1}$ is isomorphic to $(\Sym(\CC^{N}))^{S_N}$, where we view $\CC^{N}$ as the Cartan subalgebra of $\sl_{N+1}$ and $S_N$ as the Weyl group of $SL_{N+1}$, and
+\item[(2)] the derived center of the enveloping algebra $U\fg$ is given by derived invariants of the adjoint action of $\fg$ on $U\fg$:
+\[
+\Hoch^*(U\fg,U\fg) \simeq \clies(\fg, U\fg),
+\]
+\end{enumerate}
+but in a way that works uniformly for these higher enveloping algebras.
 
-\begin{enumerate}
-\item[(1)] the (underived) center of $U\sl_{N+1}$ is isomorphic to $(\Sym(\CC^{N}))^{S_N}$, where $\CC^{N}$ denotes the Cartan subalgebra of $\sl_{N+1}$ and $S_N$ is the Weyl group of $SL_{N+1}$, and
-\item[(2)] the derived center of the enveloping algebra $U\fg$ is given by derived invariants of the adjoint action of $\fg$ on $U\fg$. That is to say $\Hoch^*(U\fg,U\fg) \simeq \clies(\fg, U\fg)$.
-\end{enumerate}
+Our results include a cousin of these results where we vary (1) by taking the limit as $N \to \infty$ and vary (2) by studying the derived {\em centralizer} of a map $\UU_n\sl_\infty \hookrightarrow \UU_n\gl_\infty(A)$, where $A$ is a dg algebra.
+(The derived center is the centralizer of the identity map $\UU_n\fg \to \UU_n\fg$.)
+These notions will be reviewed and explained in the next section below,
+where we also describe our results in detail.
+When $n=1$, however, note that we find that \owen{state the classical thing here!}
 
-Our results pertains to (1) by taking $N \to \infty$, and to (2) through the derived {\em centralizer} of the map $\UU_n\sl_\infty \hookrightarrow \UU_n\gl_\infty(A)$, where $A$ is a dg algebra.
-Note that the usual derived center is the centralizer of the identity map $\UU_n\fg \to \UU_n\fg$.
+Our main tool for this result is the Loday-Quillen-Tsygan (LQT) theorem,
+which describes the large $N$ limit of Lie algebra homology of $\gl_N(A)$ for $A$ a dg algebra.
+Experts will know that enveloping $E_n$ algebras can be constructed using Chevalley-Eilenberg chains
+(i.e., that they are shifted versions of $\cliels$, in a precise sense),
+and hence will recognize the relevance of the LQT theorem in this context.
+From this perspective, our main result can be understood as an $E_n$ generalization of the LQT theorem.
 
-We will review these notions and describe our results in detail in the next section. When $n=1$,  \owen{state the classical thing here!}
-
-Our primary tool here is the Loday-Quillen-Tsygan (LQT) theorem which describes the large $N$ limit of the Lie algebra homology of $\gl_N(A)$, for a dg associative algebra $A$.
-Since the enveloping $E_n$ algebra of a Lie algebra can be constructed as a locally constant factorization algebra made out of the shifted Chevalley-Eilenberg chains \cite{}, the relevance of the LQT theorem in this context  should be apparent.
-From this point of view, one can think of our main result as an $E_n$ generalization of the LQT theorem.
-We hope these ideas have exciting applications in quantum field theory and random matrix theory, as well as to other large $N$ limit phenomena.
+We hope these constructions and ideas have interesting applications to other large $N$ phenomena,
+such as in quantum field theory and random matrix theory.
 
@@
 Throughout this document, we will work with differential graded vector spaces over a field $k$ of characteristic zero.
-We refer to dg Lie algebras simply as Lie algebra, and refer to those without grading and a differential, such as $\sl_2(\CC)$, as ordinary Lie algebras.
-Similarly, the term algebra means dg algebra unless stated otherwise.
-\end{rmk}
-
-\begin{rmk}
-We state our theorems in terms of the stable $\infty$-category cochain complexes instead of the appropriate stable model categories or pre-triangulated dg categories.
-Many of our constructions, however, involve explicit manipulations of standard complexes, and when it is helpful, we indicate the level at which we are working.
+When we write ``Lie algebra,'' we mean a dg Lie algebra; if we mean an ordinary Lie algebra (such as $\sl_2(\CC)$), we say so explicitly.
+Similarly, ``algebra'' means ``dg algebra'' unless stated otherwise.
+Our theorems will be stated in terms of the stable $\infty$-category of such cochain complexes (one is free to work with the appropriate stable model or pretriangulated dg category, as one wishes).
+Many of our constructions involve, however, explicit manipulations with standard, explicit complexes.
+To minimize confusion, we try to indicate the level at which we are working but that may be left implicit in some places.
 \end{rmk}
@@
 
-See section~\ref{sec: enveloping} for a summary of the enveloping $E_n$ algebra construction, and see section~\ref{sec: centralizer} for a summary of centralizers of maps of $E_n$ algebras.
+See section~\ref{sec: enveloping} for a summary of the enveloping $E_n$ algebra construction, 
+and see section~\ref{sec: centralizer} for a summary of centralizers of maps of $E_n$ algebras.
 
@@
 \label{thm: centralizer}
-Let $\UU_n \fg$ be the enveloping $E_n$ algebra of a dg Lie algebra $\fg$ and $f: \UU_n \fg \to B$ a map of $E_n$ algebras which gives $B$ the structure of an $E_n$ algebra in $\fg$-modules.
-Then, the centralizer ${\frak Z}_{E_n}(f)$ is the $E_n$ algebra $\clies(\fg, B)$.
+Let $f: \UU_n \fg \to B$ denote a map of $E_n$ algebras, where $\UU_n \fg$ is the enveloping $E_n$ algebra of a dg Lie algebra $\fg$.
+In particular, $B$ is an $E_n$ algebra in $\fg$-modules via the map~$f$.
+
+The centralizer ${\frak Z}_{E_n}(f)$ is the $E_n$ algebra $\clies(\fg, B)$.
 \end{thm}
-
-\greg{shall explain/remind somewhere what is the $E_n$-structure there: namely induced by $E_n$-structure of $B$ and commutative multiplication in $\clies$, namely convolution between an $E_\infty$-coalgebra and an $E_n$-algebra}
-
-By Knudsen's results \cite{Knudsen}, we have the following consequence.
+\greg{shall explain/remind somewhere what is the $E_n$-structure there: namely induced by $E_n$-structure of $B$ and com mutliplication in $\clies$, namely convolution between an $E_\infty$-coalgebra and an $E_n$-algebra}
+By using Knudsen's results, we have the following consequence.
 
 \begin{cor}
-Let $k$ is $\RR$ or $\CC$, and assume $\UU_n \rho:  \UU_n \fg \to \UU_n \fh$ is induced by a map of Lie algebras $\rho: \fg \to \fh$.
-Then, the centralizer ${\frak Z}_{E_n}(\UU_n \rho)$ is modeled by the locally constant factorization algebra that assigns
+Let $\rho: \fg \to \fh$ be a map of dg Lie algebras, and let $\UU_n \rho$ denote the associated map of enveloping $E_n$ algebras.
+When $k$ is $\RR$ or $\CC$, 
+the centralizer ${\frak Z}_{E_n}(\UU_n \rho)$ is modeled by the locally constant factorization algebra that assigns
 \[
@@
 \]
-to each open set $U \subset \RR^n$. Here, $\Omega^*_c(U)$ denotes the commutative differential graded algebra (cdga) of compactly supported forms on $U$.
+to each open set $U \subset \RR^n$.
 \end{cor}
 
-If $\rho: \fg \to \fg$ is the identity map, we get the following immediate corollary.
+An immediate corollary, by taking the identity map, is the following.
 
@@
 \label{thm: center}
-The center of the enveloping $E_n$ algebra $\UU_n\fg$ is the $E_n$ algebra $\clies(\fg, \UU_n\fg)$, which by Dunn's additivity theorem has in fact a natural $E_{n+1}$ algebra structure.
-When $k$ is $\RR$ or $\CC$, the
-center is modeled by the locally constant factorization algebra that assigns
+The center of the enveloping $E_n$ algebra $\UU_n\fg$ is the $E_n$ algebra $\clies(\fg, \UU_n\fg)$.
+(It has, of course, a natural $E_{n+1}$ algebra structure.)
+
+When $k$ is $\RR$ or $\CC$, 
+it is modeled by the locally constant factorization algebra that assigns
 \[
@@
 \end{cor}
-\greg{shall relate this to $P_n$-center of $\fg$. that shall also (but I have to think about the proof more), at least up to formality gives the $P_{n+1}$-structure on it. }
+\greg{shall relate this to $P_n$-center of $\fg$. that shall also (but I have to think to the proof more), at least up to formality gives the $P_{n+1}$-structure on it. }
 This result generalizes the fact that $\Hoch^*(U\fg,U\fg) \simeq \clies(\fg, U\fg)$, since the associative algebra $U\fg$ is modeled by the locally constant one-dimensional factorization algebra that assigns $\cliels (\fg \otimes \Omega^*_c(U))$ to each open $U \subset \RR$.
 
-Having an explicit presentation for the centralizer of a map of $E_n$ algebras leads to a calculation of factorization homology.
-The enveloping $E_n$ algebra is the homotopy $O(n)$-fixed points, or a $\mathrm{Disk}_n$-algebra in the sense of~\cite{AF}, and hence determines a factorization algebra on any un-oriented $n$-dimensional manifold \cite{Knudsen}.
-Therefore, for a closed $n$-dimensional manifold $M$, one has
+Having an explicit presentation for the centralizer of a map of $E_n$ algebras allows for immediate calculations of factorization homology.
+
+Indeed, as shown  in \cite{Knudsen}, 
+the enveloping $E_n$ algebras are homotopy $O(n)$-fixed points (in other words $\mathrm{Disk}_n$-algebras in the sense of~\cite{AF}) and hence determine factorization algebras on unoriented $n$-dimensional manifolds.
+
+Therefore, for $M$ a closed $n$-dimensional manifold, one has 
 \[
@@
 \]
-Since $\Omega^*(S^n) \simeq \CC[\epsilon_n]$, where $\epsilon_n$ is a formal variable with $|\epsilon_n| = n$ and $\epsilon_n^2 = 0$, we have
+When $M = S^n$, we thus see
 \[
@@
 \]
-
-For $n=1$, this recovers a theorem of Tamarkin and Tsygan \cite{TT} on the Hochschild cohomology of differential operators on a Lie group $G$; see Example \ref{eg: TT}.
+as $\Omega^*(S^n) \simeq \CC[\epsilon_n]$ where $\epsilon_n$ is a formal variable with $|\epsilon_n| = n$ and $\epsilon_n^2 = 0$.
+In the case that $n=1$, this recovers a theorem of Tamarkin-Tsygan \cite{TT} on the Hochschild cohomology of differential operators in the case of a group $G$ (see Example \ref{eg: TT}).
 
 \begin{rmk}
-The preceding results are quick consequences of published work and are well-known to experts we spoke to, including John Francis and Ben Knudsen.
-Nevertheless, we record these results so they are documented in the literature.
+The preceding results are well-known to experts in factorization homology (we discussed it with several, including Francis and Knudsen),
+since they are quick consequences of published work, as will be seen below.
+But these statements seem not to have be documented yet in the literature, 
+and so we record them here.
 \end{rmk}
 
-Our novel contribution in this paper is the following large $N$ result.
-Let $A$ be a unital algebra over a field $k$ of characteristic zero, and $u_A: \sl_\infty(k) \hookrightarrow \gl_\infty(A)$ be the map of Lie algebras determined by the unit in $A$.
-The induced map $\UU_nu_A: \UU_n\sl_\infty(k) \to \UU_n\gl_\infty(A)$ makes $\UU_n\gl_\infty(A)$ is an $E_n$ algebra in $\sl_\infty(k)$-modules.
+Our primary large $N$ result is the following, which is the novel contribution of this paper.
 
@@
 \label{thm: large N}
+Let $A$ be a unital algebra over a field $k$ of characteristic zero. 
+The map of Lie algebras
+\[
+u_A: \sl_\infty(k) \hookrightarrow \gl_\infty(A),
+\]
+induced by the unit in $A$, determines a map 
+\[
+\UU_nu_A: \UU_n\sl_\infty(k) \to \UU_n\gl_\infty(A).
+\]
+In particular, $\UU_n\gl_\infty(A)$ is an $E_n$ algebra in $\sl_\infty(k)$-representations.
 
-The centralizer ${\frak Z}_{E_n}(\UU_nu_A)$ of the map $\UU_nu_A$ is the $E_n$ algebra obtained by forgetting the dg commutative algebra
+The centralizer ${\frak Z}_{E_n}(\UU_nu_A)$ of this map is the $E_n$ algebra obtained by forgetting the dg commutative algebra
 \[
@@
 
-When $k$ is $\RR$ or $\CC$, this centralizer is modeled by the locally constant factorization algebra that assigns
+When $k$ is $\RR$ or $\CC$, 
+it is modeled by the locally constant factorization algebra that assigns
 \[
@@
 
-We can calculate the factorization homology of this factorization algebra explicitly.
+Again, the explicit factorization algebras provide convenient methods for computing factorization homology.
 
@@
 
-Although \cite{Knudsen} develops an adjunction between Lie and $E_n$ algebras \mahmoud{non-unital?} in any presentable symmetric monoidal stable $\infty$-category $\cC$,
-we only work in the infinity category of chain complexes $(\Mod_k, \otimes_k)$, where $k$ is a field of characteristic zero. We summarize Knudsen's result in this setting as follows.
+Although \cite{Knudsen} develops an adjunction between Lie and $E_n$ algebras in any presentable stable symmetric monoidal $\infty$-category $\cC$,
+we need his result only in the setting of chain complexes over a field $k$ of characteristic zero $\Mod_k$ with tensor product~$\otimes_k$.
+We summarize his result in that setting as follows.
 
@@
 \]
-
-\mahmoud{explain what oblv stands for}
-where $\Sigma$ denotes suspension \owen{because tikzcd does weird things with ``[1-n]'' instead}, \mahmoud{earlier we denoted the shift by [n]. should we use $\Sigma^n$ everywhere?}.
+where $\Sigma$ denotes suspension \owen{because tikzcd does weird things with ``[1-n]'' instead}.
 (Curving arrows denote left adjoints.)
@@
 
-The second part of this result leads to the explicit models in our theorems.
+The second part of this result implies the explicit models in our theorems.
 
@@
 
-We briefly review some of the main notions and refer the reader to \cite{LurieHA} Section 5.3 and \cite{FrancisHH} for detailed discussions.
+We provide a gloss of the main notions here but refer the reader to Section 5.3 of \cite{LurieHA} and \cite{FrancisHH} for extensive and detailed discussions.
+
 Let $\cC^\otimes$ denote a presentable stable symmetric monoidal $\infty$-category (for us, chain complexes over a field $k$ of characteristic zero with~$\otimes_k$).
@@
 For a map $f: A \to B$ of $E_n$ algebras in $\cC$, 
-the {\em centralizer} ${\frak Z}_{E_n}(f)$ is the $E_n$ algebra in $\cC$ that is universal among those that fit in a commuting diagram
+the {\em centralizer} ${\frak Z}_{E_n}(f)$ is the $E_n$ algebra in $\cC$ that is universal among those that sit in a commuting diagram
 \[
@@
 \]
-where $u$ is induced by the identity map $1_\cC \to {\frak Z}_{E_n}(f)$. The {\em center} of an $E_n$ algebra $A$ is the centralizer of its identity morphism $\id_A: A \to A$.
+where $u$ is induced by the identity map $1_\cC \to {\frak Z}_{E_n}(f)$.
+
+The {\em center} of an $E_n$ algebra $A$ is the centralizer of its identity morphism $\id_A: A \to A$.
 \end{dfn}
-When $n=1$ and $\cC$ is the category of vector spaces, the centralizer of $f: A \to B$ consists of the subspace of elements of $B$ that commute with the image $f(A)$ inside~$B$.
-Thus, the center of $A$ agrees with the traditional notion.
-See Theorem 5.3.1.30 of~\cite{LurieHA}, or Proposition 6.22 in~\cite{GTZ3}, for an alternative characterization.
+
+When $n=1$ and $\cC$ just ordinary vector spaces, the centralizer of $f: A \to B$ thus consists of the subspace of elements of $B$ that commute with the image $f(A)$ inside~$B$.
+The center of $A$ thus recovers the traditional notion.
+
+An alternative characterization is found in Theorem 5.3.1.30 of~\cite{LurieHA} or Proposition 6.22 in~\cite{GTZ3}.
 
@@
 The centralizer ${\frak Z}_{E_n}(f)$ can be identified with the classifying object for maps from $A$ to $B$ in the $\infty$-category $\Mod^{E_n}_A(\cC)$.
-\mahmoud{we should probably spell out the meaning of the classifying object in this case to make it obvious that the centralizer is the classifying object}
 \end{prp}
 
-When $n=1$ and $\cC$ is chain complexes over the field $k$, then $\Mod^{E_1}_A(\cC)$ is equivalent to $A\otimes A^{op}$-modules and hence ${\frak Z}_{E_1}(f) \simeq {\rm Hoch}^*(A,B_f)$,
-where $B_f$ denotes $B$ viewed as an $A\otimes A^{op}$-modules via the map~$f$.
+When $n=1$ and $\cC$ is chain complexes over the field $k$, 
+then $\Mod^{E_1}_A(\cC)$ is equivalent to $A-A$-bimodules and hence ${\frak Z}_{E_1}(f) \simeq {\rm Hoch}^*(A,B_f)$,
+where $B_f$ denotes $B$ viewed as an $A-A$-bimodule via the map~$f$.
 
@@
 which integrates all those actions and through which they all factor.
-\mahmoud{i think the picture of why it is a one-sided action is clearer if we use $S^{n-1} \times \RR^+$ istead of $S^{n-1} \times \RR$}
 As shown in Theorem 7.5.3.1 of \cite{LurieHA} and earlier in Proposition 3.16 of \cite{FrancisHH}, 
@@
 
-Let $f: \UU_n \fg \to B$ denote a map of $E_n$ algebras between the enveloping $E_n$ algebra of a dg Lie algebra $\fg$ and an $E_n$ algebra $B$.
-The results of the preceding section imply
+Let $\fg$ be a dg Lie algebra, let $B$ be an $E_n$ algebra, and let $f: \UU_n \fg \to B$ be a map of $E_n$ algebras.
+Then the results of the preceding section imply
 \begin{align*}
-{\frak Z}_{E_n}(f) &\simeq {{\rm Mor}}_{\Mod^{E_n}_{\UU_n\fg}}(\UU_n \fg, B_f) \\
-&\simeq {\rm Mor}_{\LMod_{\int_{S^{n-1}} \UU_n\fg}}(\UU_n \fg, B_f)
+{\frak Z}_{E_n}(f) &\simeq {{\rm Mor}}_{\Mod^{E_n}_{\UU_n}}(\UU_n \fg, B_f) \\
+&\simeq {\rm Mor}_{\LMod_{\int_{S^{n-1}} \UU_n}}(\UU_n \fg, B_f)
 \end{align*}
@@
 \begin{itemize}
-\item[-] $B_f$ denotes the object in $\Mod^{E_n}_{\UU_n\fg}$, as well as in $\LMod_{\int_{S^{n-1}}\UU_n}$, determined by~$f$, 
-\item[-] ${\rm Mor}_{\Mod^{E_n}_{\UU_n\fg}}(\UU_n \fg, B)$ denotes the classifying object for maps from $\UU_n\fg$ to $B_f$ in the $\infty$-category $\Mod^{E_n}_{\UU_n\fg}$ (i.e.
-an internal mapping object), and
-\item[-] ${\rm Mor}_{\LMod_{\int_{S^{n-1}} \UU_n\fg}} (\UU_n \fg, B_f)$ denotes the classifying object for maps from ${\UU_n\fg}$ to $B$ in the $\infty$-category $\LMod_{\int_{S^{n-1}}\UU_n\fg}$.
+\item $B_f$ denotes the object in $\Mod^{E_n}_{\UU_n}$ or, equivalently, in $\LMod_{\int_{S^{n-1}}\UU_n}$ determined by~$f$,
+\item ${\rm Mor}_{\Mod^{E_n}_{\UU_n}}(\UU_n \fg, B)$ denotes the classifying object for maps from $\UU_n$ to $B_f$ in the $\infty$-category $\Mod^{E_n}_{\UU_n}$ (i.e., an internal mapping object),
+\item and ${\rm Mor}_{\LMod_{\int_{S^{n-1}} \UU_n}} (\UU_n \fg, B_f)$ denotes the classifying object for maps from ${\UU_n}$ to $B$ in the $\infty$-category $\LMod_{\int_{S^{n-1}}\UU_n}$.
 \end{itemize}
-Note that $\int_{S^{n-1}}\UU_n\fg$ is an $E_1$ algebra equivalent to the dg algebra $U(\fg \otimes k[\epsilon_{n-1}])$.
+Observe now that $\int_{S^{n-1}}\UU_n$ is an $E_1$ algebra equivalent to the dg algebra $U(\fg \otimes k[\epsilon_{n-1}])$.
 This is because the rational $(n-1)$-sphere is formal, and hence its cochains are quasi-isomorphic to its cohomology $k[\epsilon_{n-1}]$.
@@
 \]
-Recall now that $\UU_n \fg \simeq \Sym(\fg[1-n])$ as $\fg$-modules \greg{shall we also need that it is true as $E_n$-algebra one we see right hand side as a $P_n$-algebra in the natural way and use formality ?
-I feel we need to say something more to recover the $E_n$-structure below ...
-something like the $E_n$-structure on Lie algebra cochains realizes the module map structure after all equivalences we use}.
-Thus, base change \mahmoud{which is a map of $E_n$ algebras?} gives rise to an equivalence 
+Recall now that $\UU_n \fg \simeq \Sym(\fg[1-n])$ as $\fg$-modules \greg{shall we also need that it is true as $E_n$-algebra one we see right hand side as a $P_n$-algebra in the natrual way and use formality ?
+I feel we need to say something more to recover the $E_n$-structure below-something like the $E_n$-structure on Lie algebra cochains realizes teh moduel map structure after all equivalences we use}.
+Base change thus implies that we have an equivalence
 \[
@@
 \]
-of underlying chain complexes, i.e. an equivalence after applying forgetful functor. The right hand side is precisely Lie algebra cochains of $\fg$ with coefficients in~$B_f$, as desired.
+of underlying chain complexes.
+(That is, we have an equivalence after applying forgetful functors.)
+The right hand side is precisely Lie algebra cochains of $\fg$ with coefficients in~$B_f$, as desired.
 
@@
 where $\epsilon$ is a formal variable of degree~$1$. 
-\brian{We should compare with Tamarkin-Tsygan's noncommutative calculus (cf. section 2.6).
+\brian{We should compare with Tamarkin-Tsygan's noncommutative claculus (cf. section 2.6).
 We could exhibit Theorem 2.7.1 explicitly in this case for the $E_n$ case with enveloping algebras.}
@@
 Throughout this section, let $A$ be a dg algebra over a field $k$ of characteristic zero.
-We do not assume $A$ is unital, unless we state otherwise.
-More generally, it possible to work with $A_\infty$ algebras, which changes nothing essentially, while it adds a distracting layer of complexity.
-Let $\cL(A)$ stand for the dg Lie algebra $\gl_\infty(A)$ of infinite matrices with only finitely many nonzero entries in~$A$, and $\cC(A)$ the cochain complex $\Cyc_*(A)[1]$ thought of as an abelian differential graded algebra.
-Let $\gl_\infty$ stand for $\gl_\infty(k)$ and $\sl_\infty=\sl_\infty(k)$ denote the sub Lie algebra of those elements that have trace zero.
-There is a natural action of $\sl_\infty$ on $\gl_\infty(A)$, and hence on its Chevalley-Eilenberg chains $\cliels(\cL(A))$.
-A key step in the LQT theorem is the construction of an isomorphism of graded vector spaces
+We do not assume $A$ is unital; whenever unitality leads to a stronger result, we will explicitly add it as a hypothesis.
+(It is possible to work with $A_\infty$ algebras rather than dg algebras, 
+but it changes nothing structurally essential while adding a distracting layer of notational complexity.)
+
+\begin{dfn}
+Let $\cC(A)$ denote the cochain complex $\Cyc_*(A)[1]$, which may be viewed as an abelian Lie algebra. 
+Let $\cL(A)$ denote the dg Lie algebra $\gl_\infty(A)$.
+\end{dfn}
+
+Let $\sl_\infty$ denote $\sl_\infty(k)$, the trace-zero matrices of rank infinity with only finitely many nonzero entries in~$k$.
+Let $\gl_\infty$ denote $\gl_\infty(k)$, the matrices of rank infinity with only finitely many nonzero entries in~$k$.
+Let $\gl_\infty(A)$ denote the matrices of rank infinity with only finitely many nonzero entries in~$A$.
+There is a natural action of $\sl_\infty$ on $\gl_\infty(A)$, 
+and hence on its Chevalley-Eilenberg chains $\cliels(\cL(A))$.
+A key step in the LQT theorem is the construction of a quasi-isomorphism
 \beqn\label{lqtco}
@@
 \begin{thm}[\cite{LQ}]
-For $A$ a unital dg algebra over a field $k$ of characteristic zero, there is a quasi-isomorphism
+For $A$ a unital dg algebra over a characteristic zero field $k$,
+there is a quasi-isomorphism
 \beqn\label{lqt}
@@
 
-While the full Hopf algebra structure is typically emphasized, it is the coalgebra structure that is of particularly importance to us.
+For us it is the coalgebra structure that is particularly important, although the full Hopf algebra structure is typically emphasized.
 
-The naturality of the above constructions in $A$, leads to the following more abstract yet stronger statement.
+As the constructions are natural in the algebra $A$, one can phrase a stronger but more abstract statement.
 
@@
 between these two functors from the dg category of unital dg algebras to the dg category of dg cocommutative Hopf algebras over~$k$.
-Furthermore, the induced natural transformation on the homotopy categories is a natural isomorphism.
+It is a quasi-isomorphism on every algebra.
 \end{cor}
-\greg{why not state (in a remark) this corollary and the next one as saying this is an equivalence in the $\infty$-categories of functor ?}
-For our purposes, the following variant, which follows easy by formal arguments, is more useful.
+\greg{why not state (in a remark) this corollary and the next one as syaing this is an equivalence in the $\infty$-categories of functor ?}
+For our purposes, a variant is more useful, but this variant follows by easy, formal arguments.
 
@@
 \]
-between these two functors from the dg category of {\em non-unital} dg algebras to the dg category of dg Hopf algebras over~$k$.
+between these two functors from the dg category of {\em non}unital dg algebras to the dg category of dg Hopf algebras over~$k$.
 For each nonunital dg algebra $A$, the map
@@
 
-This result yields the central claim of Theorem~\ref{thm: large N} about the large $N$ limit of the centralizer.
+This result yields the central claim of Theorem~\ref{thm: large N}, about the large $N$ limit of the centralizer.
 
 \begin{rmk}
-Loday and Procesi proved versions of the LQT theorem for the Lie algebras $\mathfrak{o}_n$ and $\mathfrak{sp}_{2n}$, in which cyclic homology is replaced by dihedral homology.
-As nothing substantive changes in proving analogous versions of our results above, we do not spell out the details here.
+Loday and Procesi proved versions of the Loday-Quillen-Tsygan theorem for the Lie algebras $\mathfrak{o}_n$ and $\mathfrak{sp}_{2n}$,
+in which cyclic homology of the algebra is replaced by its dihedral homology.
+As nothing substantive changes in proving analogous versions of our results above, 
+we do not spell out the details here.
 \end{rmk}
@@
 \eeqn
-which we now show is an isomorphism.
+and in fact this map is an isomorphism, which we now show.
 
-To see this, we need to understand how $\sl_\infty$ acts on the underlying graded module of $\cliels(\cL(A))$.
+To see this claim, we need to understand how $\sl_\infty$ acts on the underlying graded module of $\cliels(\cL(A))$.
 Note that as a $k$-module, $\cL(A) \cong \gl_\infty \otimes A$, which is a free $k$-module.
@@
 \]
-Taking the coinvariants under the action of the symmetric group $S_n$, which acts diagonally on the $\gl_\infty$ factor and the $A$ factor, 
+Taking the coinvariants under the action of the symmetric group $S_n$
+(which acts diagonally on the $\gl_\infty$ factor and the $A$ factor),
 we obtain
@@
 \]
-But the action of $\sl_\infty$ is then solely on the left hand factor, leaving $A$ untouched.
+But the action of $\sl_\infty$ is then wholly on the left hand factor, leaving $A$ independent.
 
@@
 
-\begin{dfn}
+\begin{dfn}\label{dfn: CA}
 Let $A$ be a dg algebra over $k$, and let $\cA = A \otimes \Omega^*_c$ denote the associated cosheaf of dg algebras on~$\RR^n$.
@@
 This will make the construction more transparent ?}
-\mahmoud{cyclic is the homotopy quotient and negative cyclic the homotopy fixed points}
 Note that for two algebras $B$ and $B'$,
@@
 \begin{rmk}
-The Loday and Procesi theorem for the Lie algebras $\mathfrak{o}_n$ and $\mathfrak{sp}_{2n}$ replaces cyclic homology with the dihedral homology and leads to an analogous class of factorization algebras.
+As remarked earlier, the Loday-Procesi theorem for the Lie algebras $\mathfrak{o}_n$ and $\mathfrak{sp}_{2n}$,
+in which cyclic homology of the algebra is replaced by its dihedral homology,
+lead to an analogous class of factorization algebras.
 \end{rmk}
 
-\section{\owen{A stub about a twisted version of LQT}}
+\section{A twisted version of LQT}
 
-\owen{Brian and I will later insert an expansion of the following.}
-
+We step aside from the main body of the paper to describe a natural modification of the prefactorization algebra $\Sym(\cC_A)$. 
 Let $\chi \in \Cyc^m(A)$ is a cyclic cocycle of degree $m$. 
-Then $\chi$ determines a central extension $\cC(A)_\chi$ of $\Cyc_*(A)[1]$ as an abelian Lie algebra (cf. Heisenberg Lie algebras),
+Then $\chi$ determines a central extension $\cC(A)_\chi$ of $\Cyc_*(A)[1]$ as an abelian dg Lie algebra (cf. Heisenberg Lie algebras),
 but $\chi$ also maps to Lie algebra cochains $\clies(\gl_N(A))$ for every $N$ via the LQT map,
@@
 
-This induces $\chi$-twisted versions of all our enveloping $E_n$ algebra theorems (in large $N$ limit).
+This induces $\chi$-twisted versions of all our enveloping $E_n$ algebra theorems (in large $N$ limit) which we can describe using the models prescribed in the main part of the text. 
+For simplicity, suppose $A$ is an ordinary (non dg) algebra, and let $\chi \in \Cyc^m(A)$ be a cyclic {\em cocycle} of degree $m$.
 
-%We briefly remark on a natural modification of the prefactorization algebra $\Sym(\cC_A)$. 
-%For simplicity, suppose $A$ is an ordinary (non dg) algebra, and let $\chi \in \Cyc^m(A)$ be a cyclic {\em cocycle} of degree $m$.
-%Consider for each open $U \subset \RR^n$ the cochain complex
-%\[
-%\Tilde{\cC}_{A,\chi} (U) = \left(\Cyc_*(A \tensor \Omega^*_c(U))[1] \oplus \CC \cdot K , \d_{\rm Cyc} + K \cdot \chi \right) 
-%\]
-%where $K$ is a formal parameter of degree $-m+n+1$.
+\begin{dfn}
+Define the precosheaf $\Tilde{\cC}_{A,\chi}$ on $\RR^n$ which assigns to the open $U \subset \RR^n$ the cochain complex
+\[
+ (U) = \left(\Cyc_*(A \tensor \Omega^*_c(U))[1] \oplus \CC \cdot K , \d_{\rm Cyc} + K \cdot \chi \right) 
+\]
+where $K$ is a formal parameter of degree $-m+n+1$.
+\end{dfn}
+
+Note that when $\chi = 0$, this precosheaf is equivalent to the precosheaf $\cC_A \oplus \ul{\CC}[m-n-1]$, where $\cC_A$ is as in Definition \ref{dfn: CA} and $\ul{\CC}[m-n-1]$ denotes the shifted constant precosheaf.
+
 %Also, $\d_{\rm Cyc}$ is the cyclic differential and $\chi$ is defined on $m$-chains by the pairing between cyclic chains and cochains, together with integration along $U$:
@@
 
-%\bibliographystyle{spmpsci}
+%%\bibliographystyle{spmpsci}
 

### 2019-05-19 frame.tex

--- 2019-05-17 frame.tex
@@
 
-\section{\owen{A stub about a twisted version of LQT}}
+\section{A twisted version of LQT}
 
-\owen{Brian and I will later insert an expansion of the following.}
-
+We step aside from the main body of the paper to describe a natural modification of the prefactorization algebra $\Sym(\cC_A)$. 
 Let $\chi \in \Cyc^m(A)$ is a cyclic cocycle of degree $m$. 
-Then $\chi$ determines a central extension $\cC(A)_\chi$ of $\Cyc_*(A)[1]$ as an abelian Lie algebra (cf. Heisenberg Lie algebras),
+Then $\chi$ determines a central extension $\cC(A)_\chi$ of $\Cyc_*(A)[1]$ as an abelian dg Lie algebra (cf. Heisenberg Lie algebras),
 but $\chi$ also maps to Lie algebra cochains $\clies(\gl_N(A))$ for every $N$ via the LQT map,

### 2020-01-28 draft.tex
outlining strategy

\documentclass[11pt]{amsart}

\usepackage{macros}
\usepackage[bbgreekl]{mathbbol}

\linespread{1.25}

%\usepackage[final]{pdfpages}

\setcounter{tocdepth}{2}
\numberwithin{equation}{section}

\def\brian{\textcolor{blue}{BW: }\textcolor{blue}}
\def\owen{\textcolor{magenta}{OG: }\textcolor{magenta}}
\def\mahmoud{\textcolor{olive}{MZ: }\textcolor{olive}}
\def\greg{\textcolor{red}{GG: }\textcolor{red}}

\begin{document}
\title{Centralizers of higher enveloping algebras of Lie algebras}

%\author{Owen Gwilliam}
%\address{Department of Mathematics and Statistics \\
%Lederle Graduate Research Tower, 1623D \\
%University of Massachusetts Amherst \\
%710 N. Pleasant Street}
%\email{gwilliam@math.umass.edu}
%
%\author{Brian Williams}
%\address{Department of Mathematics, 
%Northeastern University \\ 
%567 Lake Hall \\ 
%Boston, MA 02115 \\ U.S.A.}
%\email{br.williams@northeastern.edu}

\maketitle
\thispagestyle{empty}

\tableofcontents

%Recently, a generalization of the concept of the enveloping algebra of a Lie algebra has emerged: each dg Lie algebra $\fg$ has an enveloping $E_n$ algebra $\UU_n\fg$, for every $n$, so that $\UU_1\fg$ is the usual enveloping algebra $U\fg$. Building on prior work \cite{BD, AF} [Owen's thesis?], Knudsen \cite{Knudsen} developed these ideas extensively and offered a useful factorization algebra model for the enveloping $E_n$ algebra. Our central goal here is to generalize the following results about the enveloping algebra $U\fg$ to $\UU_n\fg$, for all $n$.
%
%\begin{enumerate}
%\item[(1)] the (underived) center of $U\sl_{N+1}$ is isomorphic to $(\Sym(\CC^{N}))^{S_N}$, where $\CC^{N}$ denotes the Cartan subalgebra of $\sl_{N+1}$ and $S_N$ is the Weyl group of $SL_{N+1}$, and
%\item[(2)] the derived center of the enveloping algebra $U\fg$ is given by derived invariants of the adjoint action of $\fg$ on $U\fg$. That is to say $\Hoch^*(U\fg,U\fg) \simeq \clies(\fg, U\fg)$.
%\end{enumerate}
%
%Our results pertains to (1) by taking $N \to \infty$, and to (2) through the derived {\em centralizer} of the map $\UU_n\sl_\infty \hookrightarrow \UU_n\gl_\infty(A)$, where $A$ is a dg algebra. Note that the usual derived center is the centralizer of the identity map $\UU_n\fg \to \UU_n\fg$.
%
%We will review these notions and describe our results in detail Min the next section. When $n=1$,  \owen{state the classical thing here!}
%
%Our primary tool here is the Loday-Quillen-Tsygan (LQT) theorem which describes the large $N$ limit of the Lie algebra homology of $\gl_N(A)$, for a dg associative algebra $A$. Since the enveloping $E_n$ algebra of a Lie algebra can be constructed as a locally constant factorization algebra made out of the shifted Chevalley-Eilenberg chains \cite{}, the relevance of the LQT theorem in this context  should be apparent. From this point of view, one can think of our main result as an $E_n$ generalization of the LQT theorem. We hope these ideas have exciting applications in quantum field theory and random matrix theory, as well as to other large $N$ limit phenomena.

\begin{rmk}
Throughout this document, we will work with differential graded vector spaces over a field $k$ of characteristic zero. We refer to dg Lie algebras simply as Lie algebra, and refer to those without grading and a differential, such as $\sl_2(\CC)$, as ordinary Lie algebras. Similarly, the term algebra means dg algebra unless stated otherwise.
\end{rmk}

\begin{rmk}
We state our theorems in terms of the stable $\infty$-category of cochain complexes 
instead of the stable model categories or pre-triangulated dg categories. 
Many of our constructions, however, involve explicit manipulations of standard complexes, 
and when it is helpful, we indicate the level at which we are working.
\end{rmk}

\section{Our main results}

See section~\ref{sec: enveloping} for a brief discussion of the enveloping $E_n$ algebra construction, and see section~\ref{sec: centralizer} 
for a brief discussion about centralizers to maps of $E_n$ algebras.

\owen{An approximate version of our main theorem. It's not terrible but I'd like to make the statement more accurate and perhaps punchier.}

\begin{thm}
\label{thm: centralizer}
Let $\UU_n \fg$ be the enveloping $E_n$ algebra of a dg Lie algebra $\fg$ and $f: \UU_n \fg \to B$ a map of augmented $E_n$ algebras that gives $B$
the structure of an $E_n$ algebra in $\fg$-modules\footnote{see Proposition~\ref{P:inducedEngModStruct}}. 
The centralizer ${\frak Z}_{E_n}(f)$ is an $E_n$-algebra modeled by the Chevalley-Eilenberg 
cochains $\clies(\fg, B)$ equipped with the convolution $E_n$-product.
\end{thm}

\owen{Here is an outline of the proof strategy, with ingredients indicated:}

Existing work gives us some insight into the situation:
\begin{itemize}
\item Lurie and Francis give a characterization of the centralizer of any map $f: A \to B$ as the ``internal hom'' in left $\int_{S^{n-1}}A$ -modules from $A$ to $B_f$, where $B_f$ denotes $B$ viewed as a left module via the map~$f$.
\item Knudsen verifies that we can model the enveloping $E_n$ algebra by a strict prefactorization algebra $\cliel(\Omega_c \otimes \fg)$ on $\RR^n$, which is weakly locally constant.
\item In combination, we have an explicit characterization of the centralizer up to quasi-isomorphism, 
since it is easy to compute the factorization homology of the enveloping algebra $\UU_n \fg$ over a sphere.
\end{itemize}

Our approach has the following steps:
\begin{enumerate}
\item Transfer the question to the setting of strict prefactorization algebras on $\RR^n$ that are weakly locally constant. (First use Lurie to explain that we can work with the homotopy coherent version, and then invoke strictification theorems from the model category literature on operads.) 
\item In particular, explain why $B$ determines some prefactorization algebra that I'll also call~$B$. Explain how the map $f: \UU_n \fg \to B$ determines a $\fg$-action on $B$. That is, we can obtain a prefactorization algebra $B_f$ taking values in the 1-category of $\fg$-representations.
\item Construct an explicit strict prefactorization algebra $\clies(\Omega \otimes \fg, B_f)$ as a kind of ``convolution algebra.'' Explain why it canonically fits into a centralizer diagram: there is a map
\[
\clies(\Omega \otimes \fg, B_f) \otimes \UU_n \fg \to B_f
\]
such that precomposing with the map $1 \otimes \id_{\UU_n \fg}$ is the map~$f$.
\item Fitting into such a diagram guarantees a canonical map $\clies(\Omega \otimes \fg, B_f) \to \cZ_f$ as strict prefactorization algebras.
\item Verify that this map is a quasi-isomorphism on disks. 
Hence it induces a weak equivalence of the associated $E_n$ algebras. 
\end{enumerate}

Some easy but important situations to examine:
\begin{itemize}
\item When $n=0$, we see naive endomorphisms arise.
\item When $n=1$, we recover standard Koszul duality and Hochschild cohomology examples.
\item Consider $\fg$ {\em abelian} for arbitrary $n$ and compare to the $E_n$ HKR theorem.
\item Compare with $E_n$ HKR theorem for $\clies(\fg)$ via $E_n$ Koszul duality.
\item Use these facts to compute factorization homology of centralizers on manifolds with boundary --- kind of like Chern-Simons states!
\end{itemize}

\owen{End of strategy}

To any $\fg$-module $M$ (wether $\fg$ is a dg Lie algebra or an $L_\infty$-algebra), 
we can associate its Chevalley-Eilenberg cochain complex defined 
by 
\begin{equation}
 \clies(\fg, M) = \Hom (Sym(\fg[-1]), M)
\end{equation}
with its classical differential. 
\greg{recall....quickly. AT least for dg-part. Say something for $L_\infty$ too}
We have the evaluation map 
\begin{equation}
 \label{eq:defev} ev: \clies(\fg, M) \otimes Sym(\fg[-1])\to M
\end{equation}
given by applying a function on a given tensor in $Sym(\fg[-1])$.

\begin{dfn}\label{D:convolutionalgebraCE}Let $\fg$ be a dg Lie (or $L_\infty$)-algebra and $B$ be an $E_n$-algebra in $\fg$-modules,
that is an object of the $\infty$-category 
$E_n-Alg(Mod_{\fg})$. Its associated convolution $E_n$-algebra structure on  $\clies(\fg, B) = \Hom (Sym(\fg[-1]), B)$ is obtained by 
 taking the \emph{convolution} between the cocommutative symmetric coalgebra $Sym(\fg[-1])$ (forgetted to an $E_n$-coalgebra) and the $E_n$-algebra $B$.
\end{dfn}
\greg{Probably need somewhere to say what means $E_n-Alg(Mod_{\fg})$ and find a less ugly notation for it}
Precisely, given an explicit $E_n$-operad $D_n$ in chain complexes and $(B, \mu^B)$ a $D_n$-algebra, 
the convolution structure is given by the following composition
\begin{multline}
 \Big(D_n(r)\otimes \clies(\fg, B)^{\otimes r} \Big)\otimes Sym(\fg[-1])\\ \stackrel{id\otimes id \otimes\Delta^{(r-1)}}\longrightarrow 
 D_n(r)\otimes \clies(\fg, B)^{\otimes r} \otimes Sym(\fg[-1])^{\otimes r} 
 \stackrel{id \otimes (ev^{\otimes r})}\longrightarrow D_n(r)\otimes B^{\otimes r} 
 \stackrel{\mu_\sigma^B}\longrightarrow B.
\end{multline}
where $\Delta$ is the cocommutative comultiplication.
In plain formula,
for any $\sigma \in D_n(r)$ and $\phi_1,\dots, \phi_r \in 
\clies(\fg, B)$, their multiplication (parametrized by $\sigma$) is  given by 
\begin{equation}
 \mu_\sigma (\phi_1,\dots, \phi_r): Sym(\fg[-1]) \ni x \mapsto \pm \mu^B_{\sigma} \big(\phi_1(x^{(1)}), \dots, \phi_r(x^{(r)})\big)
\end{equation}
where $x\mapsto x^{(1)}\otimes \cdots x^{(r)}$ is the usual $r$-fold cocommutative comultiplication.
Note that here, we are using the usual Koszul sign  convention.

\begin{lmm}
 $\clies(\fg, M) = \Hom (Sym(\fg[-1]), B)$ is a $E_n$-algebra, naturally in $\fg$ and $B$.
\end{lmm}

By Knudsen's results \cite{Knudsen}, we have the following explicit interpretation of our main theorem~\ref{thm: center}, which is the second part of our main theorem.

\begin{cor}\label{cor:centerfactorization}
Let $k$ is $\RR$ or $\CC$, and assume $\UU_n \rho:  \UU_n \fg \to \UU_n \fh$ is induced by a map of Lie algebras $\rho: \fg \to \fh$. 
Then, the centralizer ${\frak Z}_{E_n}(\UU_n \rho)$ is modeled by the locally constant factorization algebra that assigns
\[
\clies(\fg \otimes \Omega^*(U), \cliels( \fh \otimes \Omega^*_c(U)))
\]
to each open set $U \subset \RR^n$. Here, $\Omega^*_c(U)$ denotes the commutative differential graded algebra (cdga) of compactly supported forms on $U$.
\end{cor}

If $\rho: \fg \to \fg$ is the identity map, we get the following immediate corollary.

\begin{cor}
\label{thm: center}
The center of the enveloping $E_n$ algebra $\UU_n\fg$ is the $E_n$ algebra $\clies(\fg, \UU_n\fg)$. 
When $k$ is $\RR$ or $\CC$, the 
center is modeled by the locally constant factorization algebra that assigns
\[
\clies(\fg \otimes \Omega^*(U), \cliels( \fg \otimes \Omega^*_c(U)))
\]
to each open set $U \subset \RR^n$.
\end{cor}
\greg{I will add stuff and rewrite that latter, hopefully to explain ``how'' to see the $E_{n+1}$-structure}
\owen{Add remark for ", which by Dunn's additivity theorem has in fact a natural $E_{n+1}$ algebra structure."}

\greg{shall relate this to $P_n$-center of $\fg$. that shall also (but I have to think about the proof more), 
at least up to formality gives the $P_{n+1}$-structure on it. }
This result generalizes the fact that $\Hoch^*(U\fg,U\fg) \simeq \clies(\fg, U\fg)$, 
since the associative algebra $U\fg$ is modeled by the locally constant one-dimensional factorization algebra that assigns
$\cliels (\fg \otimes \Omega^*_c(U))$ to each open $U \subset \RR$.

\greg{somewhere recall that $\UU_n$ and center i that case are unoriented $E_n$-algebras and defined factorization algebras over any manifold which came from the formula}
Having an explicit presentation for the centralizer of a map of $E_n$ algebras leads to a calculation of factorization homology.
The enveloping $E_n$ algebra is the homotopy $O(n)$-fixed points, or a $\mathrm{Disk}_n$-algebra in the sense of~\cite{AF},
and hence determines a factorization algebra on any un-oriented $n$-dimensional manifold \cite{Knudsen}.
Therefore, for a closed $n$-dimensional manifold $M$, one has
\[
\int_M {\frak Z}_{E_n}(\UU_n \rho) \simeq \clies(\fg \otimes \Omega^*(M), \cliels( \fh \otimes \Omega^*(M))).
\]
Since $\Omega^*(S^n) \simeq \CC[\epsilon_n]$, where $\epsilon_n$ is a formal variable with $|\epsilon_n| = n$ and $\epsilon_n^2 = 0$, we have
\[
\int_{S^n} {\frak Z}_{E_n}(\UU_n \rho) \simeq \clies(\fg[\epsilon_n], \cliels( \fh[\epsilon_n]))
\]

For $n=1$, this recovers a theorem of Tamarkin and Tsygan \cite{TT} on the Hochschild cohomology of differential operators on a Lie group $G$;
see Example \ref{eg: TT}.

\begin{rmk}
The preceding results are quick consequences of published work and are well-known to experts we spoke to, including John Francis and Ben Knudsen. 
Nevertheless, we record these results so they are documented in the literature.
\end{rmk}

Our novel contribution in this paper is the following large $N$ result. Let $A$ be a unital algebra over a field $k$ of characteristic zero, 
and $u_A: \sl_\infty(k) \hookrightarrow \gl_\infty(A)$ be the map of Lie algebras determined by the unit in $A$. 
The induced map $\UU_nu_A: \UU_n\sl_\infty(k) \to \UU_n\gl_\infty(A)$ makes $\UU_n\gl_\infty(A)$ is an $E_n$ algebra in $\sl_\infty(k)$-modules.

\begin{thm}
\label{thm: large N}

The centralizer ${\frak Z}_{E_n}(\UU_nu_A)$ of the map $\UU_nu_A$ is the $E_n$ algebra obtained by forgetting the dg commutative algebra
\[
\clies(\sl_\infty(k)) \otimes \Sym(\Cyc_*(A)[1-n])
\]
down to an $E_n$ algebra.

When $k$ is $\RR$ or $\CC$, this centralizer is modeled by the locally constant factorization algebra that assigns
\[
\clies(\sl_\infty(\Omega^*(U)))\otimes \Sym(\Cyc_*(A \otimes \Omega^*_c(U))[1])
\]
to each open set $U \subset \RR^n$.
\end{thm}
\greg{Shall we keep these examples which uses/but are the easy part/ of LQT theorem ?}
\owen{We should write explicitly what happens in the case $A = k$, and maybe $n=1$.}

We can calculate the factorization homology of this factorization algebra explicitly.

\greg{need to add a notation/convention somewhere including that $\Sigma^n$ will be shift functor, convention for grading and so on}
\section{Enveloping $E_n$ algebras of Lie algebras}

Although \cite{Knudsen} develops an adjunction between Lie and $E_n$ algebras \mahmoud{non-unital?}\greg{Both I think}
in any presentable symmetric monoidal stable $\infty$-category $\cC$,
we only work in the infinity category of chain complexes $(\Mod_k, \otimes_k)$, where $k$ is a field of characteristic zero.
We summarize Knudsen's result in this setting as follows.

\begin{thm}\label{T:UnofLie}
There is a commuting square of adjunctions
\[
\begin{tikzcd}
\Alg_\Lie(\Mod_k) \arrow[r, bend left=20, shift left=.5ex,"\UU_n"] \arrow[dd] & \Alg_{E_n}(\Mod_k) \arrow[l, shift left=.5ex, "\oblv_n"] \arrow[dd]\\
&\\
\Mod_k \arrow[r, bend left=20, shift left=.5ex, "\Sigma^{1-n}"] \arrow[uu, bend left=20, shift left=.5ex, "\Free_\Lie"] & \Mod_k \arrow[l, shift left=.5ex,"\Sigma^{n-1}"] \arrow[uu, bend right=20, shift right=.5ex, "\Free_{E_n}"']
\end{tikzcd}
\]
\greg{Also explains what commutatrive means here ? Meaning the curved arrow diagram and the straight arrow diagram only; not combos of such}
\mahmoud{explain what oblv stands for}
where $\Sigma$ denotes suspension \owen{because tikzcd does weird things with ``[1-n]'' instead}, \mahmoud{earlier we denoted the shift by [n]. should we use $\Sigma^n$ everywhere?}.
(Curving arrows denote left adjoints.)

When $k$ is $\RR$ or $\CC$, 
the enveloping $E_n$ algebra $\UU_n \fg$ of a dg Lie algebra $\fg$ is modeled by the locally constant factorization algebra that assigns
\[
\cliels(\Omega^*_c(U) \otimes \fg)
\]
to each open set $U \subset \RR^n$.
\end{thm}

The second part of this result leads to the explicit models in our theorems.
Note that in the theorem we use the following equivalence due to Lurie~\cite{LurieHA}. 
\begin{thm}\label{T:En=Fac} there is an equivalence of $\infty$-categories between $E_n$-algebras and locally constant factorization algebras.
\end{thm}
\begin{rmk}
 It follows from theorem~\ref{T:UnofLie} that for any $E_n$-algebra $B$, the underlying complex of the $L_\infty$-algebra $\oblv_n(B)$ is naturally quasi-isomorphic to 
 $\Sigma^{n-1}B = B[n-1]$. Henceforth in this paper, we will simply use the notation  $B[n-1]$ for $\oblv_n(B)$, that is tacitly assume 
 $B[n-1]$ is endowed with the $L_\infty$structure induced by its $E_n$ algebra structure.
\end{rmk}

Let  $f:\UU_n \fg \to B$ be an $E_n$-algebra map. Then the adjunction 
$\xymatrix{\Alg_\Lie(\Mod_k) \ar@/^/[r]^{\UU_n} & \ar[l]^{\oblv_n}  \Alg_{E_n}(\Mod_k)}$
gives a $L_\infty$-algebra morphism 
\begin{equation}
 \tilde{f}: \fg \, \longrightarrow \, \oblv(B)\cong B[n-1]
\end{equation}
which makes $B[n-1]$ into a $\fg$-module and therefore its shift $B$ inherits a  $\fg$-module structure as well from $f$.
\begin{prp}\label{P:inducedEngModStruct} Let $f:\UU_n \fg \to B$ be an $E_n$-algebra morphism. The induced  
 $\fg$ $L_\infty$-module on $B$ lifts canonically to make  $B$ into an $E_n$-algebra in $\fg$-module. 
\end{prp}
\begin{proof}

\end{proof}
Proposition~\ref{P:inducedEngModStruct} has an easy realization in the factorization algebra setting.
Indeed, applying the equivalence of $E_n$-algebras with locally constant factorization algebras (Theorem~\ref{T:En=Fac}), 
we obtain an induced map of factorization 
algebras 
\begin{equation}\label{eq:DefofFonFaclevel}
 \mathbf{f}: \cliels( \fg \otimes \Omega^*_c(-)) \longrightarrow B(-)
\end{equation}
 where $B(-)$ is the factorization algebra associated to $B$.
\begin{lmm}\label{L:inducedFacgModstruct} The factorization algebra map  $\mathbf{f}$ makes $B(-)$ into an homotopy cosheaf of $L_\infty$-modules over 
 $\fg \otimes \Omega^*_c(-)$.
\end{lmm}
\begin{proof}

\end{proof}
The lemma allows us to define the factorization algebra given on any open $U$ by  the Chevalley-Eilenberg chain complexes
$ \cliels\big(\fg \otimes \Omega^*_c(U), B(U) \big)$ (with their standard differential)
of $\fg \otimes \Omega^*_c(U)$ with value on $B(U)$ whose structure maps are given, for any $(U_i)_{i\in I}$ 
a finite family of pairwise disjoint open subsets of an open $V$, by 
\begin{multline}\label{eq:transClieFac}
 \bigotimes_{i\in I} \cliels\big(\fg \otimes \Omega^*_c(U_i), B(U_i) \big) \cong Sym\Big(
 \fg\otimes (\bigoplus_{i\in I}  \Omega^*_c(U_i))[-1]  \Big) \otimes \Big( \bigotimes_{i\in I} B(U_i)\Big) \\ 
 \cong Sym\Big(\fg\otimes \Omega_c\big(\coprod U_i\big)[-1] \Big) \otimes \Big( \bigotimes_{i\in I} B(U_i)\Big)  
 \stackrel{\omega^*\otimes \mu_B}\longrightarrow Sym(\fg\otimes \Omega_c(V)[-1] ) \otimes B(V) \\ 
 = \cliels(\fg\otimes \Omega_c(V), B(V))
\end{multline}
where $\omega$ is induced by the cosheaf structure of compactly supported form and $\mu_B$ is the factorization algebra structure of $B(-)$.

\smallskip

The (homotopy) sheaf structure of forms also gives us structure maps
\begin{multline}\label{eq:transClieFacCochain}
 \bigotimes_{i\in I} \clies\big(\fg \otimes \Omega^*(U_i), B(U_i) \big) \longrightarrow
  \Hom\Big(Sym\big(\fg\otimes (\bigoplus_{i\in I}  \Omega^*(U_i))[-1]\big),  \bigotimes\limits_{i\in I} B(U_i) \Big) \\
 \cong \Hom\Big(Sym\big(\fg\otimes \Omega^*(\coprod U_i)[-1]\big), \bigotimes\limits_{i\in I} B(U_i) \Big) \\
 \stackrel{\rho}\longrightarrow \Hom\Big(Sym\big(\fg\otimes \Omega^*(V)[-1]\big), \bigotimes\limits_{i\in I} B(U_i) \Big) \\
 \stackrel{\mu_B}\longrightarrow 
  \clies(\fg\otimes \Omega (V), B(V))
\end{multline}
where $\rho$ is given by the restriction of forms onto a subspace. 
\begin{lmm}\label{L:ClieFacDef} For any (resp. locally constant) factorization algebra $B(-)$ and factorization algebra map $\mathbf{f}:\UU_n(\fg) \to B(-)$, 
 the structure maps~\eqref{eq:transClieFac} makes $ \cliels\big(\fg \otimes \Omega^*_c(-), B(-) \big)$ a (resp. locally constant) factorization algebra.
 Similarly, the structure maps~\eqref{eq:transClieFacCochain} makes 
 $ \clies\big(\fg \otimes \Omega^*(-), B(-) \big)$ a (resp. locally constant) factorization algebra.
\end{lmm}
\begin{dfn}\label{dfn:CEofFact}
We {call   $\cliels\big(\fg \otimes \Omega^*_c(-), B(-) \big)$ the Chevalley-Eilenberg chain factorization algebra of $\fg$ with value in $B(-)$} 
and $\clies\big(\fg \otimes \Omega^*(-), B(-) \big)$ the Chevalley-Eilenberg cochain factorization algebra.
\end{dfn}
\begin{proof}

\end{proof}

A special but very interesting case is of course when $B$ is itself an enveloping algebra. 
\begin{cor}
 Let $\fg$, $\fh$ be dg-Lie algebras and $f:\fg\to \fh$ be a dg-Lie algebra morphism. 
 Then the induced factorization algebra map $\mathbf{\UU_n f}:  \cliels( \fg \otimes \Omega^*_c(-)) \longrightarrow  \cliels( \fh \otimes \Omega^*_c(-)) $
 is the standard map $\cliels(f)$ induced by $f$ and the action of $\fg  \otimes \Omega^*_c(-)$ is obtained from the $\fg$-action on $\fh$ by Leibniz rule.
\end{cor}
\begin{rmk}\greg{Extends to $L_\infty$ case in a sentence or too}
\end{rmk}

\section{Centralizers of maps of $E_n$ algebras and the derived center}
\label{sec: centralizer}

We briefly review some of the main notions and refer the reader to \cite{LurieHA} Section 5.3 and \cite{FrancisHH} for detailed discussions. Let $\cC^\otimes$ denote a presentable stable symmetric monoidal $\infty$-category (for us, chain complexes over a field $k$ of characteristic zero with~$\otimes_k$).

\begin{dfn}\label{D:centralizer}
For a map $f: A \to B$ of $E_n$ algebras in $\cC$, 
the {\em centralizer} ${\frak Z}_{E_n}(f)$ is the $E_n$ algebra in $\cC$ that is universal among those that fit in a commuting diagram
\[
\begin{tikzcd}
& {\frak Z}_{E_n}(f) \otimes A \arrow[dr] & \\
A \arrow[ur, "u"] \arrow[rr, "f"] && B
\end{tikzcd}
\]
where $u$ is induced by the identity map $1_\cC \to {\frak Z}_{E_n}(f)$.
The {\em center} of an $E_n$ algebra $A$ is the centralizer of its identity morphism $\id_A: A \to A$. We will denote it ${\frak Z}_{E_n}(A) 
:= {\frak Z}_{E_n}(\id_A)$.
\end{dfn}
When $n=1$ and $\cC$ is the category of vector spaces, the centralizer of $f: A \to B$ consists of the subspace of elements of $B$ that commute with the image $f(A)$ inside~$B$. Thus, the center of $A$ agrees with the traditional notion. See Theorem 5.3.1.30 of~\cite{LurieHA}, or Proposition 6.22 in~\cite{GTZ3}, for an alternative characterization.

\begin{prp}\label{T:centralizer=inthom} 
The centralizer ${\frak Z}_{E_n}(f)$ exists and can be identified with the classifying object for maps from $A$ to $B$ in the $\infty$-category $\Mod^{E_n}_A(\cC)$. \mahmoud{we should probably spell out the meaning of the classifying object in this case to make it obvious that the centralizer is the classifying object}
\end{prp}

When $n=1$ and $\cC$ is chain complexes over the field $k$, then $\Mod^{E_1}_A(\cC)$ is equivalent to $A\otimes A^{op}$-modules and hence ${\frak Z}_{E_1}(f) \simeq {\rm Hoch}^*(A,B_f)$,
where $B_f$ denotes $B$ viewed as an $A\otimes A^{op}$-modules via the map~$f$.

\smallskip

We record a key fact drawn from \cite{LurieHA},~\cite{FrancisHH}  and \cite{GG-Notes}, which generalizes this situation.

\begin{prp}\label{P:ModentoModSn}
Let $\cC^\otimes$ be a presentable symmetric monoidal stable $\infty$-category whose tensor product preserves colimits in each variable separately.
For $A$ be an $E_n$ algebra in $\cC$,
the $\infty$-category $\Mod^{E_n}_A(\cC)$ is equivalent to the $\infty$-category $\LMod_{\int_{S^{n-1} A}}(\cC)$.
\end{prp}

See Remark 7.3.5.3 of \cite{LurieHA}, Coroallary 13 in~\cite{GG-Notes} and Section 2 of \cite{FrancisHH}.
Concretely, this claim arises from the fact that as a module over $A$ as an $E_n$ algebra, 
$M \in \Mod^{E_n}_A(\cC)$ is equipped with a commuting family of actions by $A$ parametrized by $\RR^n \setminus \{0\}\cong S^{n-1} \times \RR_{>0}$.
This action factors through the left action of the $E_1$ algebra $\int_{S^{n-1} \times \RR} A$ arising from factorization homology over the complement of the origin,
which integrates all those actions and through which they all factor. \mahmoud{i think the picture of why it is a one-sided action is clearer if we use $S^{n-1} \times \RR^+$ istead of $S^{n-1} \times \RR$}
As shown in Theorem 7.5.3.1 of \cite{LurieHA} and earlier in Proposition 3.16 of \cite{FrancisHH}, 
this algebra $\int_{S^{n-1} \times \RR} A$ is equivalent to ${\rm Free}(1_\cC)$, 
the image of the unit object $1_\cC \in \cC$ under the left adjoint ${\rm Free}$ to the forgetful functor $\Mod^{E_n}_A(\cC) \to \cC$.

\medskip

There is an immediate analogue of the notion of centralizers for factorization algebras.
\begin{dfn}\label{D:centralizerFacAlgebra}
 Let $X$ be a manifold and  $f: A(-) \to B(-)$ be a map of locally constant factorization algebras over $X$.  
The {\em centralizer} ${\frak Z}(\mathbf{f})(-)$ is the locally constant factorization
algebra over $X$ in $\cC$ that is universal among those that fit in a commuting diagram
\[
\begin{tikzcd}
& {\frak Z}(\mathbf{f}) \otimes A(-) \arrow[dr] & \\
A(-) \arrow[ur, "u"] \arrow[rr, "f"] && B(-)
\end{tikzcd}
\]
where $u$ is induced by the canonical map $1_\cC= {\frak Z}(\mathbf{f})(\emptyset) \to {\frak Z}(\mathbf{f})(-)$ induced by the inclusion of the emptyset. The {\em center} of a locally constant  factorization algebra
$A(-)$ is the centralizer of its identity morphism $\id: A(-) \to A(-)$.
\end{dfn}
By Theorem~\ref{T:En=Fac} and Proposition~\ref{T:centralizer=inthom} (also see~\cite{GTZ3}) we get
\begin{lmm}\label{L:faccentralizerexists}
 Let $X=\RR^n$. Then a centralizer of $f: A(-)\to B(-)$ exists for any morphism of locally constant factorization algebras over $X$. Further, if the above map is induced by 
 an $E_n$-algebra morphism $f:A\to B$, then 
 ${\frak Z}(\mathbf{f})(-)$ is the locally constant factorization algebra over $\RR^n$ associated to 
 the $E_n$-algebra ${\frak Z}_{E_n}(f)$.
\end{lmm}

\smallskip

We now use these results to prove the central claim of Theorem~\ref{thm: centralizer}.

\section{Proof of Theorem \ref{thm: centralizer}}

Let us start by summarizing the proof. The idea, using theorem~\ref{T:En=Fac}, 
is that we only have to prove the factorization algebra part of the main theorem. 
To do so, we first use the universal property of the centralizer to obtain 
a canonical factorization algebra map 
\[\Theta_f: \clies\big(\fg\otimes \Omega (-), B(-) \big) \longrightarrow  {\frak Z}(\mathbf{f})(-)\]
where ${\frak Z}(\mathbf{f})(-)$ is the centralizer of locally constant factorization algebras (\ref{D:centralizerFacAlgebra}).

Using the fundamental properties of universal $E_n$-enveloping algebra, we then prove that 
this map is a weak-equivalence.

\smallskip

We thus let $\mathbf{f}: \cliels\big(\fg \otimes \Omega^* (-)) \to B(-)$ be a factorization algebra map (see~\eqref{eq:DefofFonFaclevel}). We can 
assume that the structural (natural) quasi-isomorphism
$$\bigotimes_{i\in I} B(U_i) 
\stackrel{\simeq}\longrightarrow B(\coprod  U_i)$$ are chain complexes isomorphisms by replacing $B(-)$ by the prefactorization algebra 
given, on any $V=\coprod_{j\in J} V_j$, where the $V_j$ are the connected components of $V$, by   $\mathop{\bigotimes}\limits_{j\in J} B(V_j)$. 
The structural maps of $B$ are then a quasi-isomorphism of prefactorization algebras between it and $B(-)$. The map $\mathbf{f}$ is lifted similary using 
the isomorphism $\bigotimes_{i\in I} \cliels\big(\fg \otimes \Omega_c^* (U_i)\big) \cong
\cliels\big(\fg \otimes \Omega_c^* (U)\big)$ as well. We assume we have this property in the rest of this section.
\greg{Technically we may need to replace the latter by a quasi-isomorphic one satisfying the same property to ensure we do have a strict fact algebra map. 
Not sure if we should elaborate on it more since in the end we only need that to obtain lemma~\ref{L:inducedFacgModstruct} to make the construction valid 
and therefore only use the induced sym on the cosheaf of $L_\infty$-module maps}
\subsection{Construction of the universal pairing in factorization algebras}\label{SS:constuctionthetaf}
We start by defining a pairing between the factorization algebras of Chevalley-Eilenberg (co)chains in order to use the universal property of centralizers.

\smallskip

First note that compactly supported form embedds in all forms, therefore we can apply 
any element of $\cliels\big(\fg \otimes \Omega^* (-), B(-)\big)$ 
to any element of $\cliels\big(\fg \otimes \Omega_c^* (-)\big)$. Therefore, for any  $p\in \bN$, we have an evaluation 
\begin{equation} \label{eqdef:ev} \begin{array}{c}\ev: Sym^p \big( \fg \otimes \Omega^* (U)[-1] ,B(U)\big)
\otimes  Sym^p( \fg\otimes \Omega^*_c(U) [1]) \stackrel{ev}\longrightarrow B(U)  
  \\
 (x,\Phi) \,\longmapsto\, (-1)^{p(|x|+p) } \Phi (x)\end{array}
\end{equation} induced by this embedding  in all forms followed by evaluating on a function.

\smallskip

Second, the augmentation of $B$ makes $B(-)$ augmented as well (in the obvious sense of~\cite{Gi-NotesFactorization}) and this induces an augmentation on
$\clies\big(\fg\otimes \Omega (-), B(-) \big)$ as well as follows. 
We have the canonical factorization algebra map  $\mathbf{1}$  defined, for any open $U$, by 
\[\xymatrix{ k(U)=k  \ar[r]^{\quad \cong}& 
B(\emptyset) \ar[r] & B(U)  } 
 \] where the last map is given by the factorization algebra structure of $B(-)$. This gives the canonical element element 
 $\mathbf{1}\in \clies(\fg\otimes \Omega^*(-), B(-)) )$ which is the unit $k(-)\to \clies(\fg\otimes \Omega^*(-), B(-)) )$
 of the factorization structure of 
 the Chevalley-Eilenberg cochain factorization algebras~\ref{dfn:CEofFact}.  
 The augmentation map is given by $\varphi\mapsto \varepsilon \circ \varphi \circ 
 \iota$ where $\iota: k(U) \cong k \hookrightarrow Sym(\fg \otimes \Omega (U) [1]) $ is the inclusion and $\varepsilon B(U)\to k(U)$ is the augmentation of 
 $B(-)$. We therefore obtain a canonical splitting of factorization algebras 
 \begin{equation}\label{eq:splittingbyaugm}
   \clies\big(\fg\otimes \Omega^*(-), B(-)\big)  \, \cong \, k(-) \oplus \overline{ \clies(\fg\otimes \Omega^*(-), B(-)) )}
 \end{equation}
given by the augmentation. Below~\ref{Rmk:defgraduationclie}, we refine  this splitting, using it  freely  on each-connected component, to obtain 
a natural grading on it.

\smallskip

We use the splitting and~\eqref{eqdef:ev} to define our pairing as follows. First for a \emph{connected} open subset $W$ of $\RR^n$, we define 
\begin{multline}\label{eq:defevforconnected}
 \ev_f^W:   \clies (\fg\otimes \Omega (W), B(W)) \otimes \cliels\big(\fg \otimes \Omega_c^* (W)) 
 \\ \cong \, \left( k(W) \oplus \overline{\clies (\fg\otimes \Omega (W), B(W))  }\right) 
 \otimes \cliels\big(\fg \otimes \Omega_c^* (W))  \\ \cong
 \cliels\big(\fg \otimes \Omega_c^* (W))  \oplus  \left(\overline{\clies (\fg\otimes \Omega (W), B(W))  }\otimes \cliels\big(\fg \otimes \Omega_c^* (W)) 
 \right) \\
 \stackrel{ \mathbf{f}\oplus \ev}\longrightarrow  
 B(W)
\end{multline}
where $\mathbf{f}$ is the factorization algebra morphism  we are given.
In other words, if $\varphi = \lambda \mathbf{1} \oplus \overline{\varphi}$ is the decomposition of $\varphi \in  \clies (\fg\otimes \Omega (W), B(W)) $,
we have 
\[ \ev_f^W(\varphi\otimes x)= \lambda \mathbf{f}(W)(x) + \overline{\varphi}(x). \]

\smallskip

We extend this construction  to any 
 open subset in $\RR^n$ using the \lq\lq{}Leibniz rule\rq\rq{}, that is on using it freely on every connected components. 
 More precisely, 
  write $U=\coprod_{i\in I} U_i$ the decomposition of an open into the  disjoint union 
of its connected components. Using, the natural isomorphisms of complexes 
\[Sym\big(\fg \otimes \Omega (U)[-1]\big) 
\cong \bigotimes\limits_{i\in I} Sym\big(\fg \otimes \Omega ( U_i)[-1]\big), \mbox{  } 
\bigotimes_{i\in I} \cliels\big(\fg \otimes \Omega_c^* (U_i)\big) \cong
\cliels\big(\fg \otimes \Omega_c^* (U)\big)\] and
$\bigotimes_{i\in I} B(U_i) 
\stackrel{\simeq}\longrightarrow B(U)$, we obtain the 
 (natural) decomposition 
\begin{multline}\label{eq:defgraduationoncentralizernonconnected}
 \clies\big(\fg\otimes \Omega^*(U), B(U)\big)  \, \cong \, 
 \Hom\left(\bigotimes\limits_{i\in I} Sym\Big(\fg\otimes \Omega (U_i)[-1]), 
 \bigotimes\limits_{i\in I} B(U_i)\right) \\ \cong \, 
 \bigotimes\limits_{i\in I}\left( k(U_i) \oplus \overline{\clies (\fg\otimes \Omega (U_i), B(U_i))  }\right).
\end{multline}
and we can therefore define 
\begin{multline}\label{eq:defineevf}
 \ev_f^U: \clies (\fg\otimes \Omega (U), B(U)) \otimes \cliels\big(\fg \otimes \Omega_c^* (U)) 
 \\ \stackrel{\simeq}\longrightarrow  
\bigotimes\limits_{i\in I}\left( k(U_i) \oplus \overline{\clies (\fg\otimes \Omega (U_i), B(U_i))  }\right) \otimes 
 \left(\bigotimes\limits_{i\in I}\cliels\big(\fg \otimes \Omega_c^* (U_i)\big)\right)  \\ 
 \stackrel{\bigotimes\limits_{i\in I}\ev^{U_i}_f}\longrightarrow  
 \bigotimes\limits_{i\in I} B(U_i) \stackrel{\mu_B}\longrightarrow B(U)
\end{multline}
where $\mu_B$ is the canonical structure map of the factorization algebra $B(-)$ and the other maps are given by~\eqref{eq:defgraduationoncentralizernonconnected} 
and~\eqref{eq:defevforconnected}.
\greg{In~\eqref{eq:defgraduationoncentralizernonconnected} and definition of Chevalley Eilneberg complexes, one shall explain/takes care of the appropriate 
things to do (like completion) for non-finitely dimensional Lie algebras}
\greg{The decomposition used to extend $\ev$ on non-connected open can be done with any augmented $B(-)$, simply by defining it onto the prefact alg obtained by tensoring 
out on non-connected components and using the quasi-isomorphism canonical map to $\clies(\fg, B(-))$ in that case. Not sure which way is easier to define/mention}

\begin{rmk}\label{Rmk:defgraduationclie} The decomposition~\eqref{eq:defgraduationoncentralizernonconnected} makes 
the Chevalley-Eilenberg cochain complex with value on an open $U$ naturally\footnote{The grading
is compatible (by the same argument as Lemma~\ref{L:pairingCE}) with the factorization algebra structure maps of
$\clies(\fg\otimes \Omega(-), B(-))$} graded by the subsets of its connected components:
 \begin{equation}\label{eq:defgraduationoncentralizernonconnected2}
 \clies\big(\fg\otimes \Omega^*(U), B(U)\big)  \, \cong \, \bigoplus\limits_{J\subset I} {\clies}^{(J)}\big(\fg\otimes \Omega^*(U), B(U)\big) 
\end{equation}
where $J$ runs through all the (possibly empty) subsets of $I$.  Precisely, the $J$-piece is
\begin{multline*}
{\clies}^{(J)}\big(\fg\otimes \Omega^*(U), B(U)\big) = 
\left(\bigotimes\limits_{j\in I\setminus J} k(U_j)\right) \otimes \left(\bigotimes\limits_{j\in J}
\overline{\clies (\fg\otimes \Omega (U_j), B(U_j))  }\right) \\ \cong 
\overline{\clies (\fg\otimes \Omega (\coprod\limits_{j\in_J}U_j), B(\coprod\limits_{j\in_J}U_j))  }.
\end{multline*}
We think of an element of ${\clies}^{(J)}\big(\fg\otimes \Omega^*(U), B(U)\big)$ has an element of ${\clies}\big(\fg\otimes \Omega^*(U), B(U)\big)$
\emph{with support $\coprod\limits_{j\in J} U_j$}.   
Note that the component $k(-)$ in the decomposition~\eqref{eq:splittingbyaugm} is precisely the component 
${\clies}^{(\emptyset)}\big(\fg\otimes \Omega^*(U), B(U)\big)$ corresponding to the empty family.
\end{rmk}
In other words, if $\varphi = \sum_{J\subset I} \varphi^{(J)}$ is the decomposition of $\varphi$ in its graded pieces, for all 
$X= \bigotimes\limits_{i\in I} X_i \in \bigotimes\limits_{I}\cliels(\fg\otimes \Omega_c^*(U_i)) \cong \cliels(\fg\otimes \Omega^*_c(U))$, we 
have the following formula generalizing the one for connected open  subsets:
\begin{equation} \ev_f^U(\varphi\otimes X)= \sum_{J\subset I} \mu_B\left(\mathbf{f}\Big(\bigotimes\limits_{i\in I\setminus J} 
X_i\Big)\otimes  \varphi^{(J)}\Big(\bigotimes\limits_{j\in J} 
X_j\Big)\right) \end{equation}
where $\mu_{B,J}: B\Big(\coprod\limits_{i\in I\setminus J}U_i\Big)\otimes B\Big(\coprod\limits_{j\in J}U_j\Big) \to B(U)$
is the  structure map of $B(-)$.

\begin{lmm}\label{L:pairingCE}
 The pairing morphism $\ev_f$ defined by formula~\eqref{eq:defineevf} extends to a factorization algebra morphism
 \[\ev_f:  \cliels\big(\fg \otimes \Omega^* (-), B(-)\big) \otimes \cliels\big(\fg \otimes \Omega_c^* (-)\big) 
 \longrightarrow B(-).\]
\end{lmm}
\begin{proof}

\end{proof}
We write, $1$ for the factorization algebra map defined, for any open $U$, by 
\[\xymatrix{ k(U)=k  \ar[r]^{\quad \cong}& 
B(\emptyset) \ar[r] & B(U)  } 
 \] where the last map is given by the factorization algebra structure of $B(-)$. This gives the canonical element element $\mathbf{1}\in \clies(\fg\otimes \Omega^*(-), B(-)) )$ which is the unit of the factorization structure of 
 the Chevalley-Eilenberg cochain factorization algebras.

\begin{lmm}\label{L:ComTriangCent} The triangle 
 $$ \xymatrix{
& \clies ( \fg\otimes \Omega^* (-), B(-)) \otimes \cliels(\fg\otimes \Omega^*_c  (-) )
\ar[dr]^{\ev_f} & \\
\cliels(\fg\otimes \Omega^*_c (-)) \ar[ur]^{\mathbf{1} \otimes \id} \ar[rr]^{\mathbf{f}}  & &  B(-).}
 $$
is a commutative triangle of factorization algebras maps.
\end{lmm}
\begin{proof}
 It follows from lemma~\ref{L:pairingCE} that this is a diagram of factorization algebras. Since the unit $\mathbf{1}:Sym(\fg \otimes \Omega(U)[1]) \to B(U)$ is induced, for all $U$, by the factorization structure from the empty set $\emptyset$, we obtain that its support $I_{\mathbf{1}}=\emptyset$. 
 Therefore, formula~\eqref{eq:defineevJ} yields that 
 \[\ev_{f} (\mathbf{1}\otimes X) = \ev_{\emptyset}(\tilde{\mathbf{1}}\otimes X) 
 = \mathbf{f}(X)\] which proves the commutativity.
\end{proof}

By universal property of the centralizer (definition~\ref{D:centralizerFacAlgebra}), lemma~\ref{L:ComTriangCent} implies that the pairing $\ev_f \,:\,\cliels\big(\fg \otimes \Omega^* (-), B(-)\big) \otimes \cliels\big(\fg \otimes \Omega_c^* (-)\big) 
 \longrightarrow B(-)$ induces 
a canonical morphism of factorization algebras
\begin{equation}\label{eq:canonicaltocenter}
\theta_f: \clies\big(\fg\otimes \Omega (-), B(-) \big) \longrightarrow  {\frak Z}(\mathbf{f})(-). 
\end{equation}

\subsection{The map $\theta_f$ is a weak equivalence.} 
We have defined a functorial (in $f$) factorization algebras map 
$\theta_f$.

\begin{lmm}\label{L:thetaquisondisk}Let $U$ be an open subset homeomorphic to $\RR^n$. 
 Then, the canonical map~\eqref{eq:canonicaltocenter}:
 \[\theta_f(U): \clies\big(\fg\otimes \Omega (U), B(U) \big) \longrightarrow 
 {\frak Z}(\mathbf{f})(U)\] is a quasi-isomorphism and is further quasi-isomorphic 
 to the Chevalley-Eilenberg cochain complex $\clies \big(\fg, B\big)$ 
 with value in the $E_n$-algebra $B\cong B(\RR^n)$.
\end{lmm}
\begin{proof}
Recall that $f: \UU_n \fg \to B$ denote a map of $E_n$ algebras between the enveloping $E_n$ algebra of a dg Lie algebra $\fg$ and an $E_n$ algebra $B$.
And that $\mathbf{f}$ is the associated map of factorization algebras.

Let $U\hookrightarrow \RR^n$ be the canonical inclusion. It induces a commutative diagram 
 \[ \xymatrix{ \clies\big(\fg\otimes \Omega (U), B(U) \big) \ar[d] \ar[r]^{\theta_f(U)} &
\ar[d] {\frak Z}(\mathbf{f})(U)\\
 \clies\big(\fg\otimes \Omega (\RR^n), B(\RR^n) \big)
 \ar[r]^{\theta_f(\RR^n)}& {\frak Z}(\mathbf{f})(\RR^n)}  \]
whose vertical maps (given by the factorization structure) are quasi-isomorphisms since the factorization algebras 
are locally constant. 
Therefore it is enough to prove the result for $U=\RR^n$. 
In that case $\Omega(\RR^n) \cong k$ since $\RR^n$ is contractible and therefore  $\clies\big(\fg\otimes \Omega (\RR^n), B(\RR^n) \big) \cong \clies \big(\fg, B\big)$ as a chain complex.

It therefore remains to prove that 
$\clies\big(\fg\otimes \Omega (\RR^n), B(\RR^n) \big) \longrightarrow 
 {\frak Z}(\mathbf{f})(\RR^n)\cong {\frak Z}_{E_n}(\mathbf{f})$ is a quasi-isomorphism.

 \smallskip

The results of the preceding section imply
\begin{align*}
{\frak Z}_{E_n}(f) &\simeq {{\rm Mor}}_{\Mod^{E_n}_{\UU_n\fg}}(\UU_n \fg, B_f) \\
&\simeq {\rm Mor}_{\LMod_{\int_{S^{n-1}} \UU_n\fg}}(\UU_n \fg, B_f)
\end{align*}
where 
\begin{itemize}
\item[-] $B_f$ denotes the object in $\Mod^{E_n}_{\UU_n\fg}$, as well as in $\LMod_{\int_{S^{n-1}}\UU_n}$, determined by~$f$, 
\item[-] ${\rm Mor}_{\Mod^{E_n}_{\UU_n\fg}}(\UU_n \fg, B_f)$ denotes the classifying object for maps from $\UU_n\fg$ to $B_f$ in the $\infty$-category $\Mod^{E_n}_{\UU_n\fg}$ (i.e. an internal mapping object), and
\item[-] ${\rm Mor}_{\LMod_{\int_{S^{n-1}} \UU_n\fg}} (\UU_n \fg, B_f)$ denotes the classifying object for maps from ${\UU_n\fg}$ to $B$ in the $\infty$-category $\LMod_{\int_{S^{n-1}}\UU_n\fg}$. 
\end{itemize}
Note that $\int_{S^{n-1}}\UU_n\fg$ is an $E_1$ algebra equivalent to the dg algebra $U(\fg \otimes k[\epsilon_{n-1}])$.
This is because the rational $(n-1)$-sphere is formal, and hence its cochains are quasi-isomorphic to its cohomology $k[\epsilon_{n-1}]$.

\smallskip

Using the canonical inclusion $i: U\fg \to U(\fg \otimes k[\epsilon_{n-1}])$,
we find
\[
k \otimes_{U\fg} U(\fg \otimes k[\epsilon_{n-1}]) \simeq \Sym(\fg[1-n]).
\]
Recall now that $\UU_n \fg \simeq \Sym(\fg[1-n])$ as $\fg$-modules 
since, as factorization algebras (see Theorem~\ref{T:UnofLie}),  $$\UU_n \fg \cong \cliels(\Omega^*_c(-) \otimes \fg) \cong \Sym((\fg[-n])[-1])$$ where the right hand side formula follows from the fact that the product of degree $n$ compactly supported forms is trivial and therefore $\fg[-n]$ is a trivial Lie algebra.   
Thus, base change  gives rise to an equivalence 
\[
{\rm Mor}_{\LMod_{\int_{S^{n-1}} \UU_n}} (\UU_n \fg, B_f)  \simeq {\rm Mor}_{U\fg} (k, B_f)
\]
of underlying chain complexes, i.e. an equivalence after applying forgetful functor. The right hand side is precisely Lie algebra cochains of $\fg$ with coefficients in~$B_f$, as desired.
\end{proof}
\greg{That proof shall still be polished but it's the idea.}

\begin{prp}\label{L:canonicaltocenterisquis} The morphism~\eqref{eq:canonicaltocenter}
\[\clies\big(\fg\otimes \Omega (-), B(-) \big) \longrightarrow  {\frak Z}(\mathbf{f})(-)\] is a weak-equivalence of factorization algebras. 
\end{prp}
\begin{proof}
By definition (and Lemma~\ref{L:ComTriangCent}) the map 
$\theta_f$ is a factorization algebra map between \emph{locally constant} factorization algebras. 
Therefore, in order to prove it is a weak-equivalence of factorization algebras, it is enough to prove that 
$\clies\big(\fg\otimes \Omega (U), B(U) \big) \longrightarrow  {\frak Z}(\mathbf{f})(U)$ is a quasi-isomorphism for every $U$ which is a disk, that is 
homeomorphic to $\RR^n$. This is given by lemma~\ref{L:thetaquisondisk}.
\end{proof}

\subsection{End of the proof}
Combining the result of the last two sections we obtain immediately the following factorization algebra model for our main theorem:
\begin{thm}\label{thm:centralizerfactorization}
Let $k$ be $\RR$ or $\CC$, and assume $\mathbf{f}:  \UU_n \fg \to B(-)$ is a map of augmented factorization algebras. 
Then, the centralizer ${\frak Z}(\mathbf{f})$ is modeled by the locally constant factorization algebra that assigns
\[
\clies(\fg \otimes \Omega^*(U), B(U))
\]
to each open set $U \subset \RR^n$. 
\end{thm}
\begin{proof}
 In section~\ref{SS:constuctionthetaf}, we have constructed a factorization algebra map 
 $\theta_f: \clies\big(\fg\otimes \Omega (-), B(-) \big) \longrightarrow  {\frak Z}(\mathbf{f})(-)$. Proposition~\ref{L:canonicaltocenterisquis} 
 states that this map is an equivalence he Chevalley-Eilenberg factorization algebra cochains and the factorization algebra center of $f$ as claimed.
\end{proof}
By Lurie's equivalence (Theorem~\ref{T:En=Fac}) between the $\infty$-categories of $E_n$-algebras and locally constant factorization algebras 
over $\RR^n$ (and the last part of lemma~\ref{L:thetaquisondisk}),
the main theorem~\ref{thm: centralizer} follows from its factorization algebra counterpart~\ref{thm:centralizerfactorization}, 
that is from Theorem~\ref{thm:centerfactorization}. This proves the theorem over $k=\RR$ (or $\CC$).

\smallskip

Corollary~\ref{cor:centerfactorization}  is a consequence of theorem~\ref{thm:centralizerfactorization} obtained from applyting the universal 
$E_n$-enveloping algebra functor to a (homotopy) Lie algebra homorphism.

\greg{Add a base change result to get the result over Q ? Add the center structure. I.E. write and check (!) that we can write a structure of $E_1$algebra in factorization algebra describing the higher $E_{n+1}$-structure for $f=id$}

\section{Factorization algebra description of the center}\label{S:centerinFacAlg}
The universal property of centralizer (definition~\ref{D:centralizer}) implies that, for any $E_n$-algebras maps $A\stackrel{f}\to B$ and
$B\stackrel{g}\to C$, there are natural morphisms
\begin{equation}\label{eqdef:canonicaltocentralizers} {\frak Z}_{E_n}(g) \otimes {\frak Z}_{E_n}(f) \longrightarrow {\frak Z}_{E_n}(g\circ f)
\end{equation}

in the $\infty$-catgeory of $E_n$-algebras which are given by the  
following commutative diagrams of $E_n$-algebras:
\[\begin{tikzcd}
&   {\frak Z}_{E_n}(g) \otimes  {\frak Z}_{E_n}(f) \otimes A \arrow[rr, "\id\otimes \ev_f"] &&  {\frak Z}_{E_n}(g) \otimes  B \arrow[dr, "\ev_g"]\\
A \arrow[ur, "1\otimes \id_A"] \arrow[rr, "f"] && B \arrow[rr, "g"] \arrow[ur, "1\otimes \id_B"] && C. 
\end{tikzcd}\]
 When $f=g=\id_A:A\to A$, we obtain a canonical morphism \begin{equation} \label{eq:dgAssofcenter}
 {\frak Z}_{E_n}(A){\otimes} {\frak Z}_{E_n}(A) \longrightarrow {\frak Z}_{E_n}(A).\end{equation}
 Lurie has proved that this multiplication makes the center into an (homotopy) dg-associative algebras in $E_n$-algebras 
 and therefore an $E_{n+1}$-algebra. Precisely: 
\begin{prp}[\cite{LurieHA} Section 5] \label{P:PtyCenter}
\begin{itemize}
 \item The canonical map~\eqref{eq:dgAssofcenter} makes the center ${\frak Z}_{E_n}(A)$ into an $E_1$-algebra in the symmetric monoidal category of 
 $E_n$-algebras.
 \item There is a canonical equivalence of the $\infty$-category $E_1\mathrm{-Alg}(E_n\mathrm{-Alg})$ with $E_{n+1}\mathrm{-Alg}$.
\end{itemize}
\end{prp}
When $A(-)$ is a factorization algebra model for $A$, in virtue of theorem~\ref{T:En=Fac} 
(and \greg{add reference for fac algebra in fac algebra maybe too}), in order to have a factorization algebra 
model of the center of $A$, it is sufficient to describe the induced map 
\[{\frak Z}(A(-)){\otimes} {\frak Z}(A(-)) \longrightarrow {\frak Z}(A(-))\]
as a factorization algebra homomorphism which makes it an associative object in the category of locally constant factorization algebras.

\smallskip

We now turn to the specific case   of enveloping algebras $\UU_n(\fg)$.

Let $f: \fg \to \fh$, $g: \fh \to \fl$ be  $L_\infty$-algebras morphisms; for instance a dg-Lie algebras morphisms. We write 
\[ \mathbf{f}:\cliels\big(\fg \otimes \Omega^*_c(-)\big) \to  \cliels\big(\fh \otimes \Omega^*_c(-)\big), \quad 
\mathbf{h}:\cliels\big(\fh \otimes \Omega^*_c(-)\big) \to  \cliels\big(\fl \otimes \Omega^*_c(-)\big)\]
for the induced morphisms on their enveloping factorization algebras over $\RR^n$.

The inclusion  of compactly supported forms on all forms induces, for any open $U$,  the  map
\begin{equation}
 \label{eq:incofcpctforms} 
\iota_U: \cliels\big(\fh \otimes \Omega^*_c(U)\big) \, \cong \, 
Sym\big( \fh\otimes  \Omega^*_c (U) [1]\big) \hookrightarrow  
Sym\big( \fh\otimes  \Omega^* (U) [1]\big).
\end{equation}
Recall from section~\ref{SS:constuctionthetaf} that the Chevalley Eilenberg cochain factorization algebras (with values in an augmented factorization 
algebras) 
are canonically pointed  by $\mathbf{1}\in \clies(\fg\otimes \Omega^*(-), B(-)) )$ which is induced by 
the unit $k(-)\to \clies(\fg\otimes \Omega^*(-), B(-)) )$
 of the factorization structures.  In particular, we have the canonical splitting~\eqref{eq:splittingbyaugm} 
of the  Chevalley-Eilenberg cochain factorization algebras, and an associated grading~\eqref{eq:defgraduationoncentralizernonconnected2} on each open
set. We denote $\varphi= \lambda_\varphi +\overline{\varphi}$ the induced decomposition given by the splitting~\eqref{eq:splittingbyaugm} . 
We use these gradings as in section~\ref{SS:constuctionthetaf} to construct a composition as follows. 
\begin{dfn}\label{def:comp}
For any \emph{connected} open set $W$, we define  the composition 
$$\clies\big(\fh \otimes \Omega(W), \cliels(\fl \otimes \Omega_c(W)  \big) \otimes 
\clie\big(\fg \otimes \Omega(W), \cliels(\fh \otimes \Omega_c(W)  \big)
\stackrel{(-\star-)}\longrightarrow 
\clies\big(\fg \otimes \Omega(W), \cliels(\fl \otimes \Omega_c(W)  \big)
$$ to be given, for any $$\psi=\lambda_\psi \mathbf{1} +\overline{\psi} \in \clies\big(\fg \otimes \Omega(W), \cliels(\fh \otimes \Omega_c(W)  \big)=
\Hom(Sym\big( \fh\otimes  \Omega (W) [1]\big), Sym\big( \fl\otimes  \Omega_c (W) [1]\big))$$
$$\mbox{and }\varphi =\lambda_\varphi \mathbf{1} +\overline{\varphi}\in \clies\big(\fg \otimes \Omega(W), \cliels(\fh \otimes \Omega_c(W)  \big)= 
\Hom(Sym\big( \fg\otimes  \Omega (W) [1]\big), Sym\big( \fh\otimes  \Omega_c (W) [1]\big)) $$ by 
$$ \psi \star \varphi \, := \, \lambda_{\psi} \lambda_{\varphi} \mathbf{1}+
\lambda_\psi g\circ \overline{\varphi} + \lambda_{\varphi} \overline{\psi} \circ \iota_W \circ f +\overline{\psi} \circ \iota_U \circ \overline{\varphi} . $$
For any open 
$U=\coprod\limits_{i\in I}U_i$, where the $U_i$ are the connected components of $U$,  we define  the composition 
$$\clies\big(\fh \otimes \Omega(U), \cliels(\fl \otimes \Omega_c(U)  \big) \otimes 
\clie\big(\fg \otimes \Omega(U), \cliels(\fh \otimes \Omega_c(U)  \big)
\stackrel{(-\star-)}\longrightarrow 
\clies\big(\fg \otimes \Omega(U), \cliels(\fl \otimes \Omega_c(U)  \big)
$$ as follows. For any $$\psi \in \clies\big(\fg \otimes \Omega(U), \cliels(\fh \otimes \Omega_c(U)  \big)=
\Hom(Sym\big( \fh\otimes  \Omega (U) [1]\big), Sym\big( \fl\otimes  \Omega_c (U) [1]\big))$$
$$\mbox{and }\varphi \in \clies\big(\fg \otimes \Omega(U), \cliels(\fh \otimes \Omega_c(U)  \big)= 
\Hom(Sym\big( \fg\otimes  \Omega (U) [1]\big), Sym\big( \fh\otimes  \Omega_c (U) [1]\big)), $$ we write 
$\varphi = \mathop{\bigotimes}\limits_{i\in I} \varphi_i$, $\psi= \mathop{\bigotimes}\limits_{i\in I} \psi_i$ 
(where $\varphi_i \in \clies\big(\fg \otimes \Omega(U_i), \cliels(\fh \otimes \Omega_c(U_i)  \big)$,
$\psi_i\in \clies\big(\fh \otimes \Omega(U_i), \cliels(\fl \otimes \Omega_c(U_i)  \big)$) 
 using the decomposition~\eqref{eq:defgraduationoncentralizernonconnected}. Then we define
\begin{equation} \label{eqdef:staronnonconnected}
\psi \star \varphi \, := \mu_{\fl} \circ \Big( \bigotimes\limits_{i\in I} (\psi_i \star \varphi_i)\Big) \end{equation}
where $\mu_{\fl}: \mathop{\bigotimes}\limits_{i\in I} \cliels(\fl\otimes \Omega^c(U_I)) \cong \cliels(\fl\otimes \Omega^c(U))$ 
is given by the factorization algebra 
structure. 
\end{dfn}
Since $\iota_U$ is an embeding for every $U$, in the rest of the paper, we will usually 
omit it in the formulas.

\begin{lmm}\label{L:compisfacmap} The composition $$\clies\big(\fh \otimes \Omega(-), \cliels(\fl \otimes \Omega_c(-)  \big) \otimes 
\clies\big(\fg \otimes \Omega(-), \cliels(\fh \otimes \Omega_c(-)  \big)
\stackrel{(-\star-)}\longrightarrow 
\clies\big(\fg \otimes \Omega(-), \cliels(\fl \otimes \Omega_c(-)  \big)
$$
 is a morphism of factorization algebras.
\end{lmm}
\begin{proof}

\end{proof}
The composition is compatible with the augmentation splitting. Precisely, we have
\begin{lmm}\label{L:compisaugmented} For any $\varphi \in \clies\big(\fg \otimes \Omega(-), \cliels(\fh \otimes \Omega_c(-)  \big)$,
$\psi \in \clies\big(\fh \otimes \Omega(-), \cliels(\fl \otimes \Omega_c(-)  \big)$
 One has the following equalities  :
 \begin{align}
  \overline{\psi\star \varphi} \;= \;\mathbf{1}\star \overline{\varphi} +\overline{\psi}\star \mathbf{1} +\overline{\psi}\star \overline{\varphi} 
  & \quad\mbox{ (in  $\clies\big(\fg \otimes \Omega(-), \cliels(\fl \otimes \Omega_c(-)  \big) $)}\\
 \mathbf{1}\star \varphi \;=\;  (\lambda_\varphi \mathbf{1}, g\circ \overline{\varphi})\qquad
  &\quad\mbox{ (in  $k(-)  \oplus \overline{\clies\big(\fg \otimes \Omega(-), \cliels(\fl \otimes \Omega_c(-)  \big)}$)}\\
  \psi \star \mathbf{1}\;=\; (\lambda_\psi \mathbf{1}, \overline{\psi} \circ f) \qquad
  &\quad\mbox{ (in  $k(-)  \oplus \overline{\clies\big(\fg \otimes \Omega(-), \cliels(\fl \otimes \Omega_c(-)  \big)}$).}
 \end{align}
 In particular, $\mathbf{1} \star \mathbf{1} =\mathbf{1}$.
\end{lmm}
\greg{maybe I shoudl use the notation $\mathbf{1}_{\mathbf{f}}$, $\mathbf{1}_{\mathbf{g}}$, $\mathbf{1}_{\mathbf{g\circ f}}$ to differentiate 
the various spaces in which leaves the units and avoid possible confusion...?}
\begin{proof}

\end{proof}
The composition is asscoiative in the following sense.
\begin{lmm}\label{L:compisassociative} Let $\fg \stackrel{f}\to \fh$, $\fh \stackrel{g}\to \fl$ and $\fl \stackrel{h}\to \fk$ be maps of $L_\infty$-algebras.
 Then, we have, for any $\varphi \in \clies\big(\fg\otimes \Omega(-), \cliels(\fh \otimes \Omega_c(-)) \big)$, 
  $\psi \in \clies\big(\fh\otimes \Omega(-), \cliels(\fl \otimes \Omega_c(-)) \big)$ and  
  $\gamma \in \clies\big(\fl\otimes \Omega(-), \cliels(\fk \otimes \Omega_c(-)) \big)$, the equality 
  \[ (\gamma\star \psi)\star \varphi \;=\; \gamma\star (\psi \star \varphi) \quad \mbox{ in 
  $\clies\big(\fg\otimes \Omega(-), \cliels(\fk \otimes \Omega_c(-)) \big)$.}  \]
\end{lmm}
\begin{proof}

\end{proof}

\begin{lmm}\label{L:NatPptyofComp}
 The following diagram of factorization algebras 
 \[\tiny \begin{tikzcd}
 \clies\big(\fh \otimes \Omega(-), \cliels(\fl \otimes \Omega_c(-)  \big) 
 \otimes  \clies\big(\fg \otimes \Omega(-), \cliels(\fh \otimes \Omega_c(-)  \big) 
 \otimes \cliels(\fg \otimes \Omega_c(-)  \big) \arrow[rd, "(-\star-)\otimes \id"]
 \arrow[dd, "\id\otimes \ev_ {\mathbf{f}}"]& \\ 
 & \clies\big(\fg \otimes \Omega(-), \cliels(\fl \otimes \Omega_c(-)  \big) 
 \otimes \cliels(\fg \otimes \Omega_c(-)  \big)
 \arrow[dd, "\ev_{\mathbf{g}\circ \mathbf{f}}"]\\
\clies\big(\fh \otimes \Omega(-), \cliels(\fl \otimes \Omega_c(-)  \big) 
 \otimes \cliels(\fh \otimes \Omega_c(-)  \big)  \arrow[rd, "\ev_{\mathbf{g}}"] & \\  & \cliels(\fl \otimes \Omega_c(-)  \big). 
\end{tikzcd}\]
 is commutative.
\end{lmm}
\begin{proof}

\end{proof}

\begin{thm}\label{T:compcentralizer}
 Let $f: \fg \to \fh$, $g: \fh \to \fl$ be  $L_\infty$-algebras morphisms.
\begin{enumerate} \item 
 The composition $(-\star-)$ of factorization algebras (definition~\ref{def:comp}) 
 is the canonical map 
\[{\frak Z}_{E_n}(g) \otimes {\frak Z}_{E_n}(f) \longrightarrow {\frak Z}_{E_n}(g\circ f).\] 
\item If $f= \fg \stackrel{\id}\to \fg$,  the composition $(-\star-)$ makes 
$\clies\big(\fg \otimes \Omega(-), \cliels(\fg \otimes \Omega_c(-)) \big)$ into an 
(augmented) associative algebra object in factorization algebra, with unit given by $\mathbf{1}$, 
which is equivalent to the structure of the center ${\frak Z} (\cliels(\fg \otimes \Omega_c(-)))$. 
\end{enumerate}
\end{thm}
\begin{proof}
By universal property of centralizers, the canonical map~\eqref{eqdef:canonicaltocentralizers}  
is the unique\footnote{it is unique in the $\infty$-categorical 
sense, that is there is a contractible space of choices for it} map 
\[ \Upsilon: {\frak Z}_{E_n}(\UU_n g) \otimes {\frak Z}_{E_n}(\UU_n f) \longrightarrow {\frak Z}_{E_n}\big(\UU_n (g\circ f)\big)\] 
of $E_n$-algebras which makes the following diagram
\begin{equation}\label{eq:comdiagforcentralizercomput}\small
 \xymatrix{
&   &&  
{\frak Z}_{E_n}\big(\UU_n (g\circ f) \big) \otimes  \UU_n \fg  \ar@/^{2pc}/[dddr]^{\ev_{\UU_n (g\circ f)}}\\
&{\frak Z}_{E_n}(\UU_n g) \otimes  {\frak Z}_{E_n}(\UU_n f) \otimes \UU_n \fg \ar@/^{1pc}/[rru]_{ \Upsilon \otimes \id_{\UU_n \fg}} \ar[rrd]_{\id\otimes \ev_{\UU_n f}}
&& (1)
& & \\
\UU_n \fg \ar[ur]_{1^{\otimes 2}\otimes \id_{\UU_n \fg}} \ar@/_{1pc}/[rrd]^{\UU_n f} \ar@/^{6pc}/[rrruu]_{1\otimes \id_{\UU_n \fg}} &&&
{\frak Z}_{E_n}(\UU_n g) \otimes \UU_n \fh \ar[rd]^{\ev_{\UU_n h}}  &\\
&& \UU_n \fh \ar[rr]^{\UU_n g} \ar[ur]^{1\otimes \id_{\UU_n \fh}} && \UU_n \fl .}
\end{equation}
commutative (since $\UU_n (g\circ f) = \UU_n g\, \circ \, \UU_n f $;  the commutativity of the lower part of the diagram being by definition of centralizers).

By Theorem~\ref{thm:centralizerfactorization}, we know that the factorization algebras models for the centralizers are given by the respective Chevalley-Eilenberg cochain factorizations algebras 
(Definition~\ref{dfn:CEofFact}) $\clies\big(\fg \otimes \Omega(-), \cliels(\fh \otimes \Omega_c(-)  \big) $, 
$\clies\big(\fh \otimes \Omega(-), \cliels(\fl \otimes \Omega_c(-)  \big) $ and $\clies\big(\fg \otimes \Omega(-), \cliels(\fl \otimes \Omega_c(-)  \big) $ 
equipped with the evaluations maps are given by $\ev_{\mathbf{f}}$, $\ev_{\mathbf{g}}$ and $\ev_{\mathbf{g}\circ \mathbf{f}}$. We are thus left 
to prove that the same  diagram as~\eqref{eq:comdiagforcentralizercomput}, where we replace the objects and maps by their factorization analogue and $\Upsilon$
by $(-\star-)$, is commutative in factorization algebras.

Thus the map $(-\star-)$ represents the canonical map of factorization algebras 
$ {\frak Z}(\mathbf{g}) \otimes {\frak Z}(\mathbf{f}) \longrightarrow {\frak Z}(\mathbf{g}\circ \mathbf{f})$ which by proposition~\ref{P:PtyCenter} lifts
into an $E_1$-algebra map. It remains to check that the structure is on the nose an augmented associative algebra structure.
The augmentation and unitality are provided by Lemma~\ref{L:compisaugmented} (since in our case $f=g=\id-A$). 
It remains to prove associativity. It follows from Lemma~\ref{L:compisassociative}. 
The commutativity of the lower square and triangle of the diagram follows from Lemma~\ref{L:ComTriangCent}.
\end{proof}

\greg{To add: remark taht it implies the corollary~\ref{thm: center} and so.}

\section{Examples}

\greg{Add the Koszul duality example. Add examples coming from topological spaces and abelian Lie algebras}

\brian{do you like this example?} \greg{I do !}
\begin{eg}\label{eg: TT}
Consider the case $n=1$ and $B = U \fg$ where $f$ is simply the identity map. 
The Hochschild cohomology of $U \fg$ can be expressed in terms of Lie algebra cohomology as $\Hoch^*(U\fg,U\fg) \simeq \clies(\fg, U\fg)$. 
On the other hand, our model for the derived center ${\frak Z}(U(\fg))$ of $U \fg$ is the one-dimensional factorization algebra assigning 
\[
\clies(\fg \otimes \Omega^*(U), \cliels( \fg \otimes \Omega^*_c(U)))
\]
to each open set $U \subset \RR$.
In particular, the factorization homology of the derived center along the closed manifold $S^1$ can be computed as
\[
\int_{S^1} {\frak Z}(U(\fg)) \simeq \clies(\fg[\epsilon], \cliels( \fg[\epsilon])),
\]
where $\epsilon$ is a formal variable of degree~$1$. 
\brian{We should compare with Tamarkin-Tsygan's noncommutative calculus (cf. section 2.6).
We could exhibit Theorem 2.7.1 explicitly in this case for the $E_n$ case with enveloping algebras.}
\end{eg}

%We briefly remark on a natural modification of the prefactorization algebra $\Sym(\cC_A)$. 
%For simplicity, suppose $A$ is an ordinary (non dg) algebra, and let $\chi \in \Cyc^m(A)$ be a cyclic {\em cocycle} of degree $m$.
%Consider for each open $U \subset \RR^n$ the cochain complex
%\[
%\Tilde{\cC}_{A,\chi} (U) = \left(\Cyc_*(A \tensor \Omega^*_c(U))[1] \oplus \CC \cdot K , \d_{\rm Cyc} + K \cdot \chi \right) 
%\]
%where $K$ is a formal parameter of degree $-m+n+1$.
%Also, $\d_{\rm Cyc}$ is the cyclic differential and $\chi$ is defined on $m$-chains by the pairing between cyclic chains and cochains, together with integration along $U$:
%\[
%\chi ((a_1 \otimes \alpha_1) \tensor \cdots \tensor (a_m \otimes \alpha_m)) = \int_U \<\chi, a_1 \tensor \cdots \tensor a_m\> \alpha_1 \wedge \cdots \wedge \alpha_m.
%\]
%The differential is extended to the entire cochain complex by the graded Leibniz rule. 
%By similar arguments as above, the assignment $U \subset \Tilde{\cC}_{A, \chi}$ is a precosheaf of cochain complexes and $\Sym\left(\Tilde{\cC}_{A,\chi}\right)$ is a prefactorization algebra. 
%As a precosheaf of graded vectors spaces one has $\Tilde{\cC}_{A, \chi} = \cC_A \oplus \ul{\CC}[m-n-1]$, where $\ul{\CC}$ is the constant precosheaf, so that we may think of $\Sym\left(\Tilde{\cC}_{A,\chi}\right)$ as a twisted version of $\Sym(\cC_A)$. 
%These types of twisted \brian{what to say? check my degrees!}
%

\bibliographystyle{alpha}  
\bibliography{centralize}

%\bibliographystyle{spmpsci}

\end{document}
We call $\ev_f$ the 
$g: Sym(\fg \otimes \Omega (U_J) [1]) \longrightarrow B(U_J) $
let $f\otimes X  $ be an 
element in $\cliels\big(\fg \otimes \Omega^* (-), B(-)\big) \otimes \cliels\big(\fg \otimes \Omega_c^* (-)\big)$.  
Let

, since

Recall that we have a factorization algebra map~\eqref{eq:DefofFonFaclevel}  $\mathbf{f}: \cliels(\fg \otimes \Omega_c^*(-) \to B(-)$.
The unital factorization algebra is given, for any open $U$, by $k(U)=k$.

which gives us,  for any integer $n$, maps 
\begin{multline}
 Sym^n\big(\fg \otimes \Omega^*_c(U)[1]\big) \otimes Sym^p \big( \fg \otimes \Omega^* (U)[-1] ,B(U)\big) \\
 \stackrel{\Delta \otimes id}\longrightarrow 
 \bigoplus_{q} Sym^{n-q}\big(\fg \otimes \Omega^*_c(U)[1]\big) \otimes  Sym^q\big(\fg \otimes \Omega^*_c(U)[1]\big) 
 \otimes Sym^p \big( \fg \otimes \Omega^* (U)[-1] , B(U)\big)
 \\ 
 \stackrel{\id \otimes ev}\longrightarrow Sym^{n-p}\big(\fg \otimes \Omega^*_c(U)\big) \otimes B(U)  \hookrightarrow
 \cliels\big(\fg \otimes \Omega_c^*(U), B(U) \big) 
\end{multline}

\smallskip

\def \Fac {\mathrm{Fac}}
We now need to express the $E_n$-structure on ${\rm Mor}_{\LMod_{\int_{S^{n-1}} \UU_n\fg}}(\UU_n \fg, B_f)$ induced by the equivalence of Proposition~\ref{P:ModentoModSn}, and then on the subsequent isomorphic hom spaces of modules morphisms.  Since we are going to take advantage of the factorization algebra presentation of $\UU_n( \fg)$, see~Theorem~\ref{T:UnofLie}, we recall the following factorization algebra description of the centralizer.
Let $\cA \stackrel{f}\to \cB$ be a morphism of locally constant factorization algebras on $\RR^n$ corresponding to an $E_n$-algebra map similarly denoted. Then by Theorems~\ref{T:En=Fac}, \ref{T:centralizer=inthom} the centralizer of $f$ is represented by the locally constant factorization algebra  
${\rm Mor}_{\Fac_{\cA}}(\cA, \cB_f)$ which is the internal mapping object  of maps from $\cA$ to $\cB_f$ in the $\infty$-category of locally constant factorization algebras on $\RR^n$ which are a $\cA$-module.

The factorization algebra structure is 
represented as follows, see~\cite{GTZ3}: let $\cU =\big((U_i)_{i=1\dots r}, V\big)$ be a collection pairwise disjoint open convex subdisks $U_i$ of a disk $V$ and $(\phi_i: \cA\to \cB_f)_{i=1\dots r}$ be $\cA$-module maps of factorization algebras. 
To this data we need to associate a factorization algebra map 
$$\rho_{\cU}^{(\phi_i)} : \cA \longrightarrow \cB .$$
First since $V$ is a disk, the structure maps $\cA(V) \to \cA(\RR^n)$ and $\cB(V)\to \cB(\RR^n)$ are equivalences so that it is sufficient to define $\rho_{\cU}^{(\phi_i)}$ on the restrictions $\cA_{V}$, $\cB_{V}$ of the factorization algebras to $V$ or equivalently to treat only the case where $V =\RR^n$  which we assume now.
Then $\rho_{\cU}^{(\phi_i)}$ is given by a chain complex map $\cA(W)\to \cB_f(W)$ for any open $W \subset \RR^n$.  
Now we use the fact that the data of $\cU$ gives us a natural way of computing $\cA(W)$, $\cB_f (W)$ using the Cech complex $\check{C}(-,\cW)$ of a factorization algebra with values in a factorizing cover. Namely, we have canonical equivalences 
$$\check{C}(\cA, W_\cU) \stackrel{\simeq}\to \cA(W), \qquad  \check{C}(\cB_f, W_\cU) \stackrel{\simeq}\to \cB_f(W)$$ 
where $\W_{\cU}$ is the cover of $W$ given by $W_1=W\cap U_1, \dots, W_r=W\cap U_r, W^c$ where $W^c$ is the intersection of $W$ with an open $U^c$ that contains the complement of the $U_i$'s but not any of the $U_i$. Note that by definition of a factorization algebra, $\check{C}(\cA, W_\cU)$ is  a direct sum of tensors of the form 
$\cA(W'_1) \otimes \cdots \cA(W_r') \otimes \cA((W')^c) $ where $W'_i$ are subsets of $U_i$, $(W')^c$ is a subset $U^c$.

Then the map $
\cA(W) \stackrel{\rho_{\cU}^{(\phi_i)}(W)}\longrightarrow \cB_f(W)$ is uniqueley determined by the commutative diagram 
\begin{equation}\label{eq:Cechassociatedtoconfofdisks}
\xymatrix{\cA(W) \ar[rr]^{\rho_{\cU}^{(\phi_i)}(W)}&& \cB_f(W) \\
\check{C}(\cA, W_\cU) \ar[u]_{\simeq}   \ar[rr]_{\check{\rho}_{\cU}^{(\phi_i)}}&& \check{C}(\cB_f, W_\cU) \ar[u]^{\simeq} } 
\end{equation}
where the lower map $\check{\rho}_{\cU}^{(\phi_i)}$ is given by $\phi_i(W'_i): \cA(W'_i) \to \cB_f(W'_i)$ on $W_i'$ and by $id: \cA((W')^c) \to \cA((W')^c)=\cB_f((W')^c)$ on $(W')^c$. Note that the fact that the $\phi_i$ are precisely $\cA$-module maps where the module structure of $\cB_f$ is induced by $f$ induced that $\rho_{\cU}^{(\phi_i)}$ is indepedent of the choice of $U^c$. Indeed, by definition of a map of $\cA$-modules in factorization algebras, we have that such a map computed on the complement of a compact set containing the isobarycenter of its domain  in $\RR^n$ is given by the identity evaluate on $\cA$ of this complement.  Further, for the same reason we have
\begin{lmm} \label{L:reductiontodisks}
 Let $\xymatrix{ \cB \ar[r]^{g} \ar[d]^{h} & \cB' \ar[d]_{h'} \\ \cC \ar[r]^{g'} & \cC'}$ be a diagramm in the $\infty$-category of $\cA$-modules. If the restriction 
 $$\xymatrix{ \cB_{\coprod U_i} \ar[r] \ar[d] & \cB'_{\coprod U_i} \ar[d] \\ 
 \cC_{\coprod U_i} \ar[r] & \cC'_{\coprod U_i}}$$ of this diagram  to the union $\coprod U_i$   is commutative then so is the original diagram.
\end{lmm}
\begin{proof}
 Using the diagramm~\eqref{eq:Cechassociatedtoconfofdisks}, it is equivalent to prove that the following diagram 
 \xymatrix{ \check{C}(\cB, (-)_\cU)\ar[r] \ar[d] & \check{C}(\cB', (-)_\cU) \ar[d] \\ \check{C}(\cC, (-)_\cU\ar[r] & \check{C}(\cC', (-)_\cU}
 is commutative. But the map $\check{C}(\cB, (-)_\cU) \to \check{C}(\cB', (-)_\cU)$ 
 is induced by the direct sums of tensors products of chain maps $ g(W_i): \cB(U_i)= \cB_{U_i}(W_i) \to \cB'_{U_i} (W_i)$ on each $i=1\dots r$ and 
 by $id: \cB(W^c) \to \cB'(W^c)$.
\end{proof}

We now apply this to the special case of $\UU_n(\fg)$, that is for $\cA(-)= \cliels(\Omega^*_c(-) \otimes \fg)$ as we have seen. 
\begin{lmm}
 There is a commutative diagram 
 \[ \xymatrix{ \Sym( \fg[1-n])^{\otimes r} \ar[r]^{\simeq}& \bigotimes_{i=1}^r\cliels(\Omega^*_c(U_i) \otimes \fg) \ar[d]^{\rho} \ar[r]^{\bigotimes \phi_i(U_i)}  & \cB_f(U_1)\otimes \cdots \otimes B_f(U_r) \ar[d]^{\rho} \\ 
\Sym( \fg[1-n]) \ar[u]^{\delta^{r}} \ar[r]^{\simeq} & \cliels(\Omega^*_c(V) \otimes \fg) \ar[r]_{\rho_{\cU}^{(\phi_i)}(V)}& \cB_f(V)  } \] where $\delta^r$ is the iterated cocommuative coproduct. 
\end{lmm}
\begin{proof}
 The commtativity of the right square follows from~\eqref{eq:Cechassociatedtoconfofdisks}. For the left square, note that the factorization algebra structure maps on $\cliels(\Omega^*_c(-) \otimes \fg)$ 
 are induced by applying the Chevalley-Eilenberg chain functor to the canonical maps of cosheaves of Lie algebras $\bigoplus_{i=1}^{r} (\Omega^*_c(U_i)\otimes \fg) \cong \Omega^*_c(\coprod U_i) \otimes \fg \longrightarrow  \Omega^*_c(V)\otimes \fg $. 
\end{proof}

### 2020-01-28 draftbygreg.tex
outlining strategy

--- 2020-01-28 draft.tex
@@
 
-%Recently, a generalization of the concept of the enveloping algebra of a Lie algebra has emerged: each dg Lie algebra $\fg$ has an enveloping $E_n$ algebra $\UU_n\fg$, for every $n$, so that $\UU_1\fg$ is the usual enveloping algebra $U\fg$.
+Recently, a generalization of the concept of the enveloping algebra of a Lie algebra has emerged: each dg Lie algebra $\fg$ has an enveloping $E_n$ algebra $\UU_n\fg$, for every $n$, so that $\UU_1\fg$ is the usual enveloping algebra $U\fg$.
 Building on prior work \cite{BD, AF} [Owen's thesis?], Knudsen \cite{Knudsen} developed these ideas extensively and offered a useful factorization algebra model for the enveloping $E_n$ algebra.
 Our central goal here is to generalize the following results about the enveloping algebra $U\fg$ to $\UU_n\fg$, for all $n$.
-%
-%\begin{enumerate}
-%\item[(1)] the (underived) center of $U\sl_{N+1}$ is isomorphic to $(\Sym(\CC^{N}))^{S_N}$, where $\CC^{N}$ denotes the Cartan subalgebra of $\sl_{N+1}$ and $S_N$ is the Weyl group of $SL_{N+1}$, and
-%\item[(2)] the derived center of the enveloping algebra $U\fg$ is given by derived invariants of the adjoint action of $\fg$ on $U\fg$. That is to say $\Hoch^*(U\fg,U\fg) \simeq \clies(\fg, U\fg)$.
-%\end{enumerate}
-%
-%Our results pertains to (1) by taking $N \to \infty$, and to (2) through the derived {\em centralizer} of the map $\UU_n\sl_\infty \hookrightarrow \UU_n\gl_\infty(A)$, where $A$ is a dg algebra.
+
+\begin{enumerate}
+\item[(1)] the (underived) center of $U\sl_{N+1}$ is isomorphic to $(\Sym(\CC^{N}))^{S_N}$, where $\CC^{N}$ denotes the Cartan subalgebra of $\sl_{N+1}$ and $S_N$ is the Weyl group of $SL_{N+1}$, and
+\item[(2)] the derived center of the enveloping algebra $U\fg$ is given by derived invariants of the adjoint action of $\fg$ on $U\fg$. That is to say $\Hoch^*(U\fg,U\fg) \simeq \clies(\fg, U\fg)$.
+\end{enumerate}
+
+Our results pertains to (1) by taking $N \to \infty$, and to (2) through the derived {\em centralizer} of the map $\UU_n\sl_\infty \hookrightarrow \UU_n\gl_\infty(A)$, where $A$ is a dg algebra.
 Note that the usual derived center is the centralizer of the identity map $\UU_n\fg \to \UU_n\fg$.
-%
-%We will review these notions and describe our results in detail Min the next section. When $n=1$,  \owen{state the classical thing here!}
-%
-%Our primary tool here is the Loday-Quillen-Tsygan (LQT) theorem which describes the large $N$ limit of the Lie algebra homology of $\gl_N(A)$, for a dg associative algebra $A$.
+
+We will review these notions and describe our results in detail Min the next section. When $n=1$,  \owen{state the classical thing here!}
+
+Our primary tool here is the Loday-Quillen-Tsygan (LQT) theorem which describes the large $N$ limit of the Lie algebra homology of $\gl_N(A)$, for a dg associative algebra $A$.
 Since the enveloping $E_n$ algebra of a Lie algebra can be constructed as a locally constant factorization algebra made out of the shifted Chevalley-Eilenberg chains \cite{}, the relevance of the LQT theorem in this context  should be apparent.
@@
 \begin{rmk}
-We state our theorems in terms of the stable $\infty$-category of cochain complexes 
-instead of the stable model categories or pre-triangulated dg categories. 
-Many of our constructions, however, involve explicit manipulations of standard complexes, 
-and when it is helpful, we indicate the level at which we are working.
+We state our theorems in terms of the stable $\infty$-category cochain complexes instead of the appropriate stable model categories or pre-triangulated dg categories.
+Many of our constructions, however, involve explicit manipulations of standard complexes, and when it is helpful, we indicate the level at which we are working.
 \end{rmk}
@@
 
-See section~\ref{sec: enveloping} for a brief discussion of the enveloping $E_n$ algebra construction, and see section~\ref{sec: centralizer} 
-for a brief discussion about centralizers to maps of $E_n$ algebras.
-
-\owen{An approximate version of our main theorem. It's not terrible but I'd like to make the statement more accurate and perhaps punchier.}
+See section~\ref{sec: enveloping} for a summary of the enveloping $E_n$ algebra construction, and see section~\ref{sec: centralizer} 
+for a summary of centralizers of maps of $E_n$ algebras.
 
@@
 \label{thm: centralizer}
-Let $\UU_n \fg$ be the enveloping $E_n$ algebra of a dg Lie algebra $\fg$ and $f: \UU_n \fg \to B$ a map of augmented $E_n$ algebras that gives $B$
+Let $\UU_n \fg$ be the enveloping $E_n$ algebra of a dg Lie algebra $\fg$ and $f: \UU_n \fg \to B$ a map of augmented $E_n$ algebras which gives $B$
 the structure of an $E_n$ algebra in $\fg$-modules\footnote{see Proposition~\ref{P:inducedEngModStruct}}. 
-The centralizer ${\frak Z}_{E_n}(f)$ is an $E_n$-algebra modeled by the Chevalley-Eilenberg 
-cochains $\clies(\fg, B)$ equipped with the convolution $E_n$-product.
+Then, the centralizer ${\frak Z}_{E_n}(f)$ is the $E_n$-algebra given by the Chevalley-Eilenberg 
+algebra $\clies(\fg, B)$ with the convolution $E_n$-product.
 \end{thm}
 
-\owen{Here is an outline of the proof strategy, with ingredients indicated:}
-
-Existing work gives us some insight into the situation:
-\begin{itemize}
-\item Lurie and Francis give a characterization of the centralizer of any map $f: A \to B$ as the ``internal hom'' in left $\int_{S^{n-1}}A$ -modules from $A$ to $B_f$, where $B_f$ denotes $B$ viewed as a left module via the map~$f$.
-\item Knudsen verifies that we can model the enveloping $E_n$ algebra by a strict prefactorization algebra $\cliel(\Omega_c \otimes \fg)$ on $\RR^n$, which is weakly locally constant.
-\item In combination, we have an explicit characterization of the centralizer up to quasi-isomorphism, 
-since it is easy to compute the factorization homology of the enveloping algebra $\UU_n \fg$ over a sphere.
-\end{itemize}
-
-Our approach has the following steps:
-\begin{enumerate}
-\item Transfer the question to the setting of strict prefactorization algebras on $\RR^n$ that are weakly locally constant.
-(First use Lurie to explain that we can work with the homotopy coherent version, and then invoke strictification theorems from the model category literature on operads.)
-\item In particular, explain why $B$ determines some prefactorization algebra that I'll also call~$B$.
-Explain how the map $f: \UU_n \fg \to B$ determines a $\fg$-action on $B$.
-That is, we can obtain a prefactorization algebra $B_f$ taking values in the 1-category of $\fg$-representations.
-\item Construct an explicit strict prefactorization algebra $\clies(\Omega \otimes \fg, B_f)$ as a kind of ``convolution algebra.'' Explain why it canonically fits into a centralizer diagram: there is a map
-\[
-\clies(\Omega \otimes \fg, B_f) \otimes \UU_n \fg \to B_f
-\]
-such that precomposing with the map $1 \otimes \id_{\UU_n \fg}$ is the map~$f$.
-\item Fitting into such a diagram guarantees a canonical map $\clies(\Omega \otimes \fg, B_f) \to \cZ_f$ as strict prefactorization algebras.
-\item Verify that this map is a quasi-isomorphism on disks. 
-Hence it induces a weak equivalence of the associated $E_n$ algebras. 
-\end{enumerate}
-
-Some easy but important situations to examine:
-\begin{itemize}
-\item When $n=0$, we see naive endomorphisms arise.
-\item When $n=1$, we recover standard Koszul duality and Hochschild cohomology examples.
-\item Consider $\fg$ {\em abelian} for arbitrary $n$ and compare to the $E_n$ HKR theorem.
-\item Compare with $E_n$ HKR theorem for $\clies(\fg)$ via $E_n$ Koszul duality.
-\item Use these facts to compute factorization homology of centralizers on manifolds with boundary --- kind of like Chern-Simons states!
-\end{itemize}
-
-\owen{End of strategy}
-
-To any $\fg$-module $M$ (wether $\fg$ is a dg Lie algebra or an $L_\infty$-algebra), 
-we can associate its Chevalley-Eilenberg cochain complex defined 
+To any $\fg$-module $M$ (wether $\fg$ is a dg Lie algebra or an $L_\infty$-algebra), we can associate its Chevalley-Eilenberg cochain complex defined 
 by 

### 2020-01-28 draft.tex
some rearrangment

@@
 \item When $n=1$, we recover standard Koszul duality and Hochschild cohomology examples.
+\item When $n=1$, unpack in detail how the convolution picture matches the classic view of Koszul duality for associative (co)algebras.
 \item Consider $\fg$ {\em abelian} for arbitrary $n$ and compare to the $E_n$ HKR theorem.
@@
 \owen{End of strategy}
-
-To any $\fg$-module $M$ (wether $\fg$ is a dg Lie algebra or an $L_\infty$-algebra), 
-we can associate its Chevalley-Eilenberg cochain complex defined 
-by 
-\begin{equation}
- \clies(\fg, M) = \Hom (Sym(\fg[-1]), M)
-\end{equation}
-with its classical differential. 
-\greg{recall....quickly. AT least for dg-part. Say something for $L_\infty$ too}
-We have the evaluation map 
-\begin{equation}
- \label{eq:defev} ev: \clies(\fg, M) \otimes Sym(\fg[-1])\to M
-\end{equation}
-given by applying a function on a given tensor in $Sym(\fg[-1])$.
-
-\begin{dfn}\label{D:convolutionalgebraCE}Let $\fg$ be a dg Lie (or $L_\infty$)-algebra and $B$ be an $E_n$-algebra in $\fg$-modules,
-that is an object of the $\infty$-category 
-$E_n-Alg(Mod_{\fg})$. Its associated convolution $E_n$-algebra structure on  $\clies(\fg, B) = \Hom (Sym(\fg[-1]), B)$ is obtained by 
- taking the \emph{convolution} between the cocommutative symmetric coalgebra $Sym(\fg[-1])$ (forgetted to an $E_n$-coalgebra) and the $E_n$-algebra $B$.
-\end{dfn}
-\greg{Probably need somewhere to say what means $E_n-Alg(Mod_{\fg})$ and find a less ugly notation for it}
-Precisely, given an explicit $E_n$-operad $D_n$ in chain complexes and $(B, \mu^B)$ a $D_n$-algebra, 
-the convolution structure is given by the following composition
-\begin{multline}
- \Big(D_n(r)\otimes \clies(\fg, B)^{\otimes r} \Big)\otimes Sym(\fg[-1])\\ \stackrel{id\otimes id \otimes\Delta^{(r-1)}}\longrightarrow 
- D_n(r)\otimes \clies(\fg, B)^{\otimes r} \otimes Sym(\fg[-1])^{\otimes r} 
- \stackrel{id \otimes (ev^{\otimes r})}\longrightarrow D_n(r)\otimes B^{\otimes r} 
- \stackrel{\mu_\sigma^B}\longrightarrow B.
-\end{multline}
-where $\Delta$ is the cocommutative comultiplication.
-In plain formula,
-for any $\sigma \in D_n(r)$ and $\phi_1,\dots, \phi_r \in 
-\clies(\fg, B)$, their multiplication (parametrized by $\sigma$) is  given by 
-\begin{equation}
- \mu_\sigma (\phi_1,\dots, \phi_r): Sym(\fg[-1]) \ni x \mapsto \pm \mu^B_{\sigma} \big(\phi_1(x^{(1)}), \dots, \phi_r(x^{(r)})\big)
-\end{equation}
-where $x\mapsto x^{(1)}\otimes \cdots x^{(r)}$ is the usual $r$-fold cocommutative comultiplication.
-Note that here, we are using the usual Koszul sign  convention.
-
-\begin{lmm}
- $\clies(\fg, M) = \Hom (Sym(\fg[-1]), B)$ is a $E_n$-algebra, naturally in $\fg$ and $B$.
-\end{lmm}
 
@@
 For $n=1$, this recovers a theorem of Tamarkin and Tsygan \cite{TT} on the Hochschild cohomology of differential operators on a Lie group $G$;
-see Example \ref{eg: TT}.
+see Example~\ref{eg: TT}.
 
 \begin{rmk}
-The preceding results are quick consequences of published work and are well-known to experts we spoke to, including John Francis and Ben Knudsen. 
-Nevertheless, we record these results so they are documented in the literature.
+The preceding results are known to experts we spoke to, including John Francis and Ben Knudsen. 
+Nevertheless, we record these results to document in the literature and for future use in mathematical physics,
+where such constructions already appear but lack proofs of their universal properties.
 \end{rmk}
+
+\owen{Below is an orphaned set of results. Perhaps we prove it, or perhaps we just reserve it for future projects.}
 
@@
 \label{thm: large N}
-
 The centralizer ${\frak Z}_{E_n}(\UU_nu_A)$ of the map $\UU_nu_A$ is the $E_n$ algebra obtained by forgetting the dg commutative algebra
@@
 \greg{need to add a notation/convention somewhere including that $\Sigma^n$ will be shift functor, convention for grading and so on}
+
 \section{Enveloping $E_n$ algebras of Lie algebras}
@@
 Note that in the theorem we use the following equivalence due to Lurie~\cite{LurieHA}.
-\begin{thm}\label{T:En=Fac} there is an equivalence of $\infty$-categories between $E_n$-algebras and locally constant factorization algebras.
+
+\begin{thm}
+\label{T:En=Fac} 
+There is an equivalence of $\infty$-categories between $E_n$-algebras and locally constant factorization algebras.
 \end{thm}
+
 \begin{rmk}
@@
 
+\owen{I'm not wild about Greg's phrasing below. Also, I'd prefer to move the explicit formulas later, when we've shifted our setting to strict prefactorization algebras.}
+
 Let  $f:\UU_n \fg \to B$ be an $E_n$-algebra map. Then the adjunction 
-$\xymatrix{\Alg_\Lie(\Mod_k) \ar@/^/[r]^{\UU_n} & \ar[l]^{\oblv_n}  \Alg_{E_n}(\Mod_k)}$
+\[
+\xymatrix{\Alg_\Lie(\Mod_k) \ar@/^/[r]^{\UU_n} & \ar[l]^{\oblv_n}  \Alg_{E_n}(\Mod_k)}
+\]
 gives a $L_\infty$-algebra morphism 
@@
 
-\smallskip
-
 We record a key fact drawn from \cite{LurieHA},~\cite{FrancisHH}  and \cite{GG-Notes}, which generalizes this situation.
@@
 the image of the unit object $1_\cC \in \cC$ under the left adjoint ${\rm Free}$ to the forgetful functor $\Mod^{E_n}_A(\cC) \to \cC$.
-
-\medskip
 
@@
 
-\smallskip
-
 We now use these results to prove the central claim of Theorem~\ref{thm: centralizer}.
+
+\section{Convolution algebras over colored operads}
+
+\def\conv{{\rm Conv}}
+
+\owen{For an ordinary colored operad $\cO$, describe how to produce a $\cO$-algebra $\conv(C,A)$ from any $\cO$-coalgebra $C$ and $\cO$-algebra $A$.}
+
+\owen{A special case to consider is how a cocycle $f \in \conv(C,A)$ encodes an $\cO$-algebra morphism $C^!
+\to A$ from $C^!
+= \conv(C,1)$, the ``Koszul dual'' $\cO$-algebra to the coalgebra $C$.
+This cocycle can be used to twist the differential of $\conv(C,A)$.
+Hopefully this admits an obvious deformation-theoretic interpretation.}
+
+\owen{If we do this correctly, we might find a model category-theoretic picture of how Koszul duality works for prefactorization algebras.}
 
@@
 
+\section{Leftover stuff}
+
+\owen{I took the following out of Greg's version of the "main theorem" section}
+
+To any $\fg$-module $M$ (wether $\fg$ is a dg Lie algebra or an $L_\infty$-algebra), 
+we can associate its Chevalley-Eilenberg cochain complex defined 
+by 
+\begin{equation}
+ \clies(\fg, M) = \Hom (Sym(\fg[-1]), M)
+\end{equation}
+with its classical differential. 
+\greg{recall....quickly. AT least for dg-part. Say something for $L_\infty$ too}
+We have the evaluation map 
+\begin{equation}
+ \label{eq:defev} ev: \clies(\fg, M) \otimes Sym(\fg[-1])\to M
+\end{equation}
+given by applying a function on a given tensor in $Sym(\fg[-1])$.
+
+\begin{dfn}\label{D:convolutionalgebraCE}Let $\fg$ be a dg Lie (or $L_\infty$)-algebra and $B$ be an $E_n$-algebra in $\fg$-modules,
+that is an object of the $\infty$-category 
+$E_n-Alg(Mod_{\fg})$. Its associated convolution $E_n$-algebra structure on  $\clies(\fg, B) = \Hom (Sym(\fg[-1]), B)$ is obtained by 
+ taking the \emph{convolution} between the cocommutative symmetric coalgebra $Sym(\fg[-1])$ (forgetted to an $E_n$-coalgebra) and the $E_n$-algebra $B$.
+\end{dfn}
+\greg{Probably need somewhere to say what means $E_n-Alg(Mod_{\fg})$ and find a less ugly notation for it}
+Precisely, given an explicit $E_n$-operad $D_n$ in chain complexes and $(B, \mu^B)$ a $D_n$-algebra, 
+the convolution structure is given by the following composition
+\begin{multline}
+ \Big(D_n(r)\otimes \clies(\fg, B)^{\otimes r} \Big)\otimes Sym(\fg[-1])\\ \stackrel{id\otimes id \otimes\Delta^{(r-1)}}\longrightarrow 
+ D_n(r)\otimes \clies(\fg, B)^{\otimes r} \otimes Sym(\fg[-1])^{\otimes r} 
+ \stackrel{id \otimes (ev^{\otimes r})}\longrightarrow D_n(r)\otimes B^{\otimes r} 
+ \stackrel{\mu_\sigma^B}\longrightarrow B.
+\end{multline}
+where $\Delta$ is the cocommutative comultiplication.
+In plain formula,
+for any $\sigma \in D_n(r)$ and $\phi_1,\dots, \phi_r \in 
+\clies(\fg, B)$, their multiplication (parametrized by $\sigma$) is  given by 
+\begin{equation}
+ \mu_\sigma (\phi_1,\dots, \phi_r): Sym(\fg[-1]) \ni x \mapsto \pm \mu^B_{\sigma} \big(\phi_1(x^{(1)}), \dots, \phi_r(x^{(r)})\big)
+\end{equation}
+where $x\mapsto x^{(1)}\otimes \cdots x^{(r)}$ is the usual $r$-fold cocommutative comultiplication.
+Note that here, we are using the usual Koszul sign  convention.
+
+\begin{lmm}
+ $\clies(\fg, M) = \Hom (Sym(\fg[-1]), B)$ is a $E_n$-algebra, naturally in $\fg$ and $B$.
+\end{lmm}
+
 \section{Examples}

### 2020-08-10 draft.tex
og beginning to reorganize

@@
 \label{thm: centralizer}
-Let $\UU_n \fg$ be the enveloping $E_n$ algebra of a dg Lie algebra $\fg$ and $f: \UU_n \fg \to B$ a map of augmented $E_n$ algebras that gives $B$
-the structure of an $E_n$ algebra in $\fg$-modules\footnote{see Proposition~\ref{P:inducedEngModStruct}}. 
-The centralizer ${\frak Z}_{E_n}(f)$ is an $E_n$-algebra modeled by the Chevalley-Eilenberg 
+Let $\UU_n \fg$ be the enveloping $E_n$ algebra of a dg Lie algebra $\fg$ and let $f: \UU_n \fg \to B$ a map of augmented $E_n$ algebras.
+Then
+\begin{itemize}
+\item $f$ equips $B$ with the structure of an $E_n$ algebra in $\fg$-modules and
+\item the centralizer ${\frak Z}_{E_n}(f)$ is an $E_n$-algebra modeled by the Chevalley-Eilenberg 
 cochains $\clies(\fg, B)$ equipped with the convolution $E_n$-product.
+\end{itemize}
 \end{thm}
@@
 
-Existing work gives us some insight into the situation:
+Existing work provides insight into and context for the situation:
 \begin{itemize}
 \item Lurie and Francis give a characterization of the centralizer of any map $f: A \to B$ as the ``internal hom'' in left $\int_{S^{n-1}}A$ -modules from $A$ to $B_f$, where $B_f$ denotes $B$ viewed as a left module via the map~$f$.
-\item Knudsen verifies that we can model the enveloping $E_n$ algebra by a strict prefactorization algebra $\cliel(\Omega_c \otimes \fg)$ on $\RR^n$, which is weakly locally constant.
-\item In combination, we have an explicit characterization of the centralizer up to quasi-isomorphism, 
+\item Knudsen verifies that we can model the enveloping $E_n$ algebra by a strict prefactorization algebra $\tt{U}_n \fg = \cliel(\Omega_c \otimes \fg)$ on $\RR^n$, which is weakly locally constant.
+\item In combination, the centralizer is characterized up to quasi-isomorphism, 
 since it is easy to compute the factorization homology of the enveloping algebra $\UU_n \fg$ over a sphere.
 \end{itemize}
-
-Our approach has the following steps:
+Our approach leverages these results as follows to prove the theorem.
 \begin{enumerate}
-\item Transfer the question to the setting of strict prefactorization algebras on $\RR^n$ that are weakly locally constant.
-(First use Lurie to explain that we can work with the homotopy coherent version, and then invoke strictification theorems from the model category literature on operads.)
-\item In particular, explain why $B$ determines some prefactorization algebra that I'll also call~$B$.
-Explain how the map $f: \UU_n \fg \to B$ determines a $\fg$-action on $B$.
-That is, we can obtain a prefactorization algebra $B_f$ taking values in the 1-category of $\fg$-representations.
-\item Construct an explicit strict prefactorization algebra $\clies(\Omega \otimes \fg, B_f)$ as a kind of ``convolution algebra.'' Explain why it canonically fits into a centralizer diagram: there is a map
-\[
-\clies(\Omega \otimes \fg, B_f) \otimes \UU_n \fg \to B_f
-\]
-such that precomposing with the map $1 \otimes \id_{\UU_n \fg}$ is the map~$f$.
-\item Fitting into such a diagram guarantees a canonical map $\clies(\Omega \otimes \fg, B_f) \to \cZ_f$ as strict prefactorization algebras.
-\item Verify that this map is a quasi-isomorphism on disks. 
+\item First, we transfer the question to the setting of strict prefactorization algebras on $\RR^n$ that are weakly locally constant.
+Lurie \cite{LurieHA} explains why we can work with the homotopy coherent version of prefactorization algebras, and then strictification theorems from the model category literature on operads say we can work with strict prefactorization algebras.
+\item  In particular, given an $E_n$ algebra $B$,  let $\tt{B}$ denote a strict prefactorization algebra modeling~$B$.
+Strictification lets us associate to the map $f: \UU_n \fg \to B$, a map $\tt{f}: \tt{U}_n \fg \to \tt{B}$ of strict prefactorization algebras. 
+\owen{It might be better to first use the adjunction to get a map of homotopy-coherent Lie algebras $\fg \to B$ but \dots}
+\item From the map $\tt{f}$, we read off an $\fg$-action on $\tt{B}$ intertwining with the structure maps of $\tt{B}$. 
+That is, we have a prefactorization algebra $\tt{B}_f$ taking values in the 1-category of chain complexes of $\fg$-representations.
+\item We then construct an explicit strict prefactorization algebra $\clies(\Omega \otimes \fg, B_f)$ as a kind of ``convolution algebra.'' 
+\item We show this object fits canonically into a centralizer diagram: there is a map
+\[
+\clies(\Omega \otimes \fg, \tt{B}_f) \otimes \tt{U}_n \fg \to \tt{B}_f
+\]
+such that precomposing with the map $1 \otimes \id_{\tt{U}_n \fg}$ is the map~$\tt{f}$.
+Fitting into such a diagram guarantees a canonical map $\clies(\Omega \otimes \fg, B_f) \to \tt{Z}_f$ as strict prefactorization algebras. 
+\item We then verify that this map is a quasi-isomorphism on disks. 
+\end{enumerate}
 Hence it induces a weak equivalence of the associated $E_n$ algebras.
-\end{enumerate}
-
-Some easy but important situations to examine:
+
+\owen{Some easy but important situations to examine:}
 \begin{itemize}
@@
 
-\owen{End of strategy}
-
-By Knudsen's results \cite{Knudsen}, we have the following explicit interpretation of our main theorem~\ref{thm: center}, which is the second part of our main theorem.
+By Knudsen's results \cite{Knudsen}, we have the following explicit applications of our main theorem~\ref{thm: center}.
+
+\owen{I think we should just work in $Ch(\RR)$ or $Ch(\CC)$ throughout.}
 
@@
 Let $k$ is $\RR$ or $\CC$, and assume $\UU_n \rho:  \UU_n \fg \to \UU_n \fh$ is induced by a map of Lie algebras $\rho: \fg \to \fh$. 
-Then, the centralizer ${\frak Z}_{E_n}(\UU_n \rho)$ is modeled by the locally constant factorization algebra that assigns
+Then the centralizer ${\frak Z}_{E_n}(\UU_n \rho)$ is modeled by the locally constant factorization algebra that assigns
 \[
@@
 
-\section{Enveloping $E_n$ algebras of Lie algebras}
-
-Although \cite{Knudsen} develops an adjunction between Lie and $E_n$ algebras \mahmoud{non-unital?}\greg{Both I think}
+\section{Background}
+
+\owen{Add overview}
+
+\subsection{Recollections on $E_n$ algebras and prefactorization algebras}
+
+\owen{Recall Jacob's results and what it means in conjunction with strictification}
+
+\subsection{Enveloping $E_n$ algebras of Lie algebras}
+
+Although \cite{Knudsen} develops an adjunction between Lie and $E_n$ algebras \mahmoud{non-unital?}\greg{Both I think}\owen{augmented is probably best for us}
 in any presentable symmetric monoidal stable $\infty$-category $\cC$,
@@
 \label{T:En=Fac} 
-There is an equivalence of $\infty$-categories between $E_n$-algebras and locally constant factorization algebras.
+There is an equivalence of $\infty$-categories between $E_n$-algebras and locally constant prefactorization algebras on~$\RR^n$.
 \end{thm}
@@
 
-\section{Centralizers of maps of $E_n$ algebras and the derived center}
+\subsection{Centralizers of maps of $E_n$ algebras and the derived center}
 \label{sec: centralizer}

### 2020-08-10 draft.tex
og getting confused

@@
 
-See section~\ref{sec: enveloping} for a brief discussion of the enveloping $E_n$ algebra construction, and see section~\ref{sec: centralizer} 
+See section~\ref{sec: en background} for a brief discussion of $E_n$ algebras and their relationship with locally constant factorization algebras on $\RR^n$, section~\ref{sec: enveloping} for a brief discussion of the enveloping $E_n$ algebra construction, and see section~\ref{sec: centralizer}
 for a brief discussion about centralizers to maps of $E_n$ algebras.
@@
 \begin{itemize}
-\item Lurie and Francis give a characterization of the centralizer of any map $f: A \to B$ as the ``internal hom'' in left $\int_{S^{n-1}}A$ -modules from $A$ to $B_f$, where $B_f$ denotes $B$ viewed as a left module via the map~$f$.
-\item Knudsen verifies that we can model the enveloping $E_n$ algebra by a strict prefactorization algebra $\tt{U}_n \fg = \cliel(\Omega_c \otimes \fg)$ on $\RR^n$, which is weakly locally constant.
+\item Lurie and Francis give a characterization of the centralizer ${\frak Z}_{E_n}(f)$ of any $E_n$ algebra map $f: A \to B$ as the ``internal hom'' in left $\int_{S^{n-1}}A$ -modules from $A$ to $B_f$, where $B_f$ denotes $B$ viewed as a left module via the map~$f$.
+\item Knudsen verifies that we can model the enveloping $E_n$ algebra by a strict prefactorization algebra ${\tt U}_n \fg = \cliel(\Omega_c \otimes \fg)$ on $\RR^n$, which is weakly locally constant.
 \item In combination, the centralizer is characterized up to quasi-isomorphism, 
@@
 Lurie \cite{LurieHA} explains why we can work with the homotopy coherent version of prefactorization algebras, and then strictification theorems from the model category literature on operads say we can work with strict prefactorization algebras.
-\item  In particular, given an $E_n$ algebra $B$,  let $\tt{B}$ denote a strict prefactorization algebra modeling~$B$.
-Strictification lets us associate to the map $f: \UU_n \fg \to B$, a map $\tt{f}: \tt{U}_n \fg \to \tt{B}$ of strict prefactorization algebras. 
-\owen{It might be better to first use the adjunction to get a map of homotopy-coherent Lie algebras $\fg \to B$ but \dots}
-\item From the map $\tt{f}$, we read off an $\fg$-action on $\tt{B}$ intertwining with the structure maps of $\tt{B}$. 
-That is, we have a prefactorization algebra $\tt{B}_f$ taking values in the 1-category of chain complexes of $\fg$-representations.
+\item  In particular, given an $E_n$ algebra $B$,  let ${\tt B}$ denote a strict prefactorization algebra modeling~$B$.
+Strictification lets us associate to the map $f: \UU_n \fg \to B$, a map ${\tt f}: {\tt U}_n \fg \to {\tt B}$ of strict prefactorization algebras. 
+\owen{It might be better to first use the adjunction to get a map of homotopy-coherent Lie algebras $\fg \to B$ but I'm not sure this plays nicely with the other strictification\dots}
+\item From the map ${\tt f}$, we read off an $\fg$-action on ${\tt B}$ intertwining with the structure maps of ${\tt B}$. 
+That is, we have a prefactorization algebra ${\tt B}_f$ taking values in the 1-category $\Ch(\Rep(\fg))$ of chain complexes of $\fg$-representations.
 \item We then construct an explicit strict prefactorization algebra $\clies(\Omega \otimes \fg, B_f)$ as a kind of ``convolution algebra.'' 
@@
 \[
-\clies(\Omega \otimes \fg, \tt{B}_f) \otimes \tt{U}_n \fg \to \tt{B}_f
-\]
-such that precomposing with the map $1 \otimes \id_{\tt{U}_n \fg}$ is the map~$\tt{f}$.
-Fitting into such a diagram guarantees a canonical map $\clies(\Omega \otimes \fg, B_f) \to \tt{Z}_f$ as strict prefactorization algebras. 
+\clies(\Omega \otimes \fg, {\tt B}_f) \otimes {\tt U}_n \fg \to {\tt B}_f
+\]
+such that precomposing with the map $1 \otimes \id_{{\tt U}_n \fg}$ is the map~${\tt f}$.
+Fitting into such a diagram guarantees a canonical map $\clies(\Omega \otimes \fg, {\tt B}_f) \to {\tt Z}_f$ as strict prefactorization algebras. 
 \item We then verify that this map is a quasi-isomorphism on disks. 
@@
 \subsection{Recollections on $E_n$ algebras and prefactorization algebras}
-
-\owen{Recall Jacob's results and what it means in conjunction with strictification}
+\label{sec: en background}
+
+\owen{Recall Jacob's results and what it means in conjunction with strictification.}
+
+\owen{I want to work with the colored operad of round disks (or rectilinear boxes) in $\RR^n$.}
+
+Note that in the theorem we use the following equivalence due to Lurie~\cite{LurieHA}.
+
+\begin{thm}
+\label{T:En=Fac} 
+There is an equivalence of $\infty$-categories between $E_n$-algebras and locally constant prefactorization algebras on~$\RR^n$.
+\end{thm}
 
 \subsection{Enveloping $E_n$ algebras of Lie algebras}
+\label{sec: enveloping}
 
@@
 The second part of this result leads to the explicit models in our theorems.
-Note that in the theorem we use the following equivalence due to Lurie~\cite{LurieHA}.
-
-\begin{thm}
-\label{T:En=Fac} 
-There is an equivalence of $\infty$-categories between $E_n$-algebras and locally constant prefactorization algebras on~$\RR^n$.
-\end{thm}
 
 \begin{rmk}
- It follows from theorem~\ref{T:UnofLie} that for any $E_n$-algebra $B$, the underlying complex of the $L_\infty$-algebra $\oblv_n(B)$ is naturally quasi-isomorphic to 
- $\Sigma^{n-1}B = B[n-1]$. Henceforth in this paper, we will simply use the notation  $B[n-1]$ for $\oblv_n(B)$, that is tacitly assume 
- $B[n-1]$ is endowed with the $L_\infty$structure induced by its $E_n$ algebra structure.
+It follows from theorem~\ref{T:UnofLie} that for any $E_n$-algebra $B$, 
+its underlying complex is equipped with a homotopy-coherent Lie algebra structure.
+Depending on one's preferences, one can work with an an $L_\infty$-algebra structure or strictify to a dg Lie algebra structure (at the cost of replacing the complex with something quasi-isomorphic but typically much larger).
 \end{rmk}
 
+\owen{\label{note on little model} Note that if we work with the colored operad of disks/boxes, then Poincar\'e lemma tells us that we can use the strict model $\cliel(\fg[-n])$ rather than the fatter model $\cliels(\Omega^*_c(U) \otimes \fg)$.
+I think Ben actually shows this too.
+This would be worth explaining because we can then use a much simpler strictification of $f$.}
+
+\subsection{Centralizers of maps of $E_n$ algebras and the derived center}
+\label{sec: centralizer}
+
+We briefly review some of the main notions and refer the reader to \cite{LurieHA} Section 5.3 and \cite{FrancisHH} for detailed discussions.
+Let $\cC^\otimes$ denote a presentable stable symmetric monoidal $\infty$-category (for us, chain complexes over a field $k$ of characteristic zero with~$\otimes_k$).
+
+\begin{dfn}\label{D:centralizer}
+For a map $f: A \to B$ of $E_n$ algebras in $\cC$, 
+the {\em centralizer} ${\frak Z}_{E_n}(f)$ is the $E_n$ algebra in $\cC$ that is universal among those that fit in a commuting diagram
+\[
+\begin{tikzcd}
+& {\frak Z}_{E_n}(f) \otimes A \arrow[dr] & \\
+A \arrow[ur, "u"] \arrow[rr, "f"] && B
+\end{tikzcd}
+\]
+where $u$ is induced by the identity map $1_\cC \to {\frak Z}_{E_n}(f)$.
+The {\em center} of an $E_n$ algebra $A$ is the centralizer of its identity morphism $\id_A: A \to A$. We will denote it ${\frak Z}_{E_n}(A) 
+:= {\frak Z}_{E_n}(\id_A)$.
+\end{dfn}
+When $n=1$ and $\cC$ is the category of vector spaces, the centralizer of $f: A \to B$ consists of the subspace of elements of $B$ that commute with the image $f(A)$ inside~$B$.
+Thus, the center of $A$ agrees with the traditional notion.
+See Theorem 5.3.1.30 of~\cite{LurieHA}, or Proposition 6.22 in~\cite{GTZ3}, for an alternative characterization.
+
+\begin{prp}\label{T:centralizer=inthom} 
+The centralizer ${\frak Z}_{E_n}(f)$ exists and can be identified with the classifying object for maps from $A$ to $B$ in the $\infty$-category $\Mod^{E_n}_A(\cC)$.
+\mahmoud{we should probably spell out the meaning of the classifying object in this case to make it obvious that the centralizer is the classifying object}
+\end{prp}
+
+When $n=1$ and $\cC$ is chain complexes over the field $k$, then $\Mod^{E_1}_A(\cC)$ is equivalent to $A\otimes A^{op}$-modules and hence ${\frak Z}_{E_1}(f) \simeq {\rm Hoch}^*(A,B_f)$,
+where $B_f$ denotes $B$ viewed as an $A\otimes A^{op}$-modules via the map~$f$.
+
+We record a key fact drawn from \cite{LurieHA},~\cite{FrancisHH}  and \cite{GG-Notes}, which generalizes this situation.
+
+\begin{prp}\label{P:ModentoModSn}
+Let $\cC^\otimes$ be a presentable symmetric monoidal stable $\infty$-category whose tensor product preserves colimits in each variable separately.
+For $A$ be an $E_n$ algebra in $\cC$,
+the $\infty$-category $\Mod^{E_n}_A(\cC)$ is equivalent to the $\infty$-category $\LMod_{\int_{S^{n-1} A}}(\cC)$.
+\end{prp}
+
+See Remark 7.3.5.3 of \cite{LurieHA}, Coroallary 13 in~\cite{GG-Notes} and Section 2 of \cite{FrancisHH}.
+Concretely, this claim arises from the fact that as a module over $A$ as an $E_n$ algebra, 
+$M \in \Mod^{E_n}_A(\cC)$ is equipped with a commuting family of actions by $A$ parametrized by $\RR^n \setminus \{0\}\cong S^{n-1} \times \RR_{>0}$.
+This action factors through the left action of the $E_1$ algebra $\int_{S^{n-1} \times \RR} A$ arising from factorization homology over the complement of the origin,
+which integrates all those actions and through which they all factor.
+\mahmoud{i think the picture of why it is a one-sided action is clearer if we use $S^{n-1} \times \RR^+$ istead of $S^{n-1} \times \RR$}
+As shown in Theorem 7.5.3.1 of \cite{LurieHA} and earlier in Proposition 3.16 of \cite{FrancisHH}, 
+this algebra $\int_{S^{n-1} \times \RR} A$ is equivalent to ${\rm Free}(1_\cC)$, 
+the image of the unit object $1_\cC \in \cC$ under the left adjoint ${\rm Free}$ to the forgetful functor $\Mod^{E_n}_A(\cC) \to \cC$.
+
+There is an immediate analogue of the notion of centralizers for factorization algebras.
+\begin{dfn}\label{D:centralizerFacAlgebra}
+ Let $X$ be a manifold and  $f: A(-) \to B(-)$ be a map of locally constant factorization algebras over $X$.  
+The {\em centralizer} ${\frak Z}(\mathbf{f})(-)$ is the locally constant factorization
+algebra over $X$ in $\cC$ that is universal among those that fit in a commuting diagram
+\[
+\begin{tikzcd}
+& {\frak Z}(\mathbf{f}) \otimes A(-) \arrow[dr] & \\
+A(-) \arrow[ur, "u"] \arrow[rr, "f"] && B(-)
+\end{tikzcd}
+\]
+where $u$ is induced by the canonical map $1_\cC= {\frak Z}(\mathbf{f})(\emptyset) \to {\frak Z}(\mathbf{f})(-)$ induced by the inclusion of the emptyset.
+The {\em center} of a locally constant  factorization algebra
+$A(-)$ is the centralizer of its identity morphism $\id: A(-) \to A(-)$.
+\end{dfn}
+By Theorem~\ref{T:En=Fac} and Proposition~\ref{T:centralizer=inthom} (also see~\cite{GTZ3}) we get
+\begin{lmm}\label{L:faccentralizerexists}
+ Let $X=\RR^n$. Then a centralizer of $f: A(-)\to B(-)$ exists for any morphism of locally constant factorization algebras over $X$. Further, if the above map is induced by 
+ an $E_n$-algebra morphism $f:A\to B$, then 
+ ${\frak Z}(\mathbf{f})(-)$ is the locally constant factorization algebra over $\RR^n$ associated to 
+ the $E_n$-algebra ${\frak Z}_{E_n}(f)$.
+\end{lmm}
+
+We now turn to proving Theorem~\ref{thm: centralizer}.
+
+\section{Strictifying the map $f: \UU_n \fg \to B$}
+
+As a first step, we analyze the strictification of the map $f: \UU_n \fg \to B$ and show how it lets us view $B$ as an $E_n$ algebra in~$\Ch(\Rep(\fg))$.
+
+By using the small model \owen{see my comment \ref{note on little model}}, we can strictify to obtain a map
+\[
+{\tt f}: \cliel(\fg[-n]) \to {\tt B}.
+\]
+
+\owen{And now I'm really confused.}
+
 \owen{I'm not wild about Greg's phrasing below. Also, I'd prefer to move the explicit formulas later, when we've shifted our setting to strict prefactorization algebras.}
+
+\begin{rmk}
+It follows from theorem~\ref{T:UnofLie} that for any $E_n$-algebra $B$, 
+the underlying complex of the $L_\infty$-algebra $\oblv_n(B)$ is naturally quasi-isomorphic to $\Sigma^{n-1}B = B[n-1]$. 
+Henceforth in this paper, we will simply use the notation $B[n-1]$ for $\oblv_n(B)$, 
+that is tacitly assume we $B[n-1]$ is endowed with the $L_\infty$structure induced by its $E_n$ algebra structure.
+\end{rmk}
 
@@
 \end{rmk}
-
-\subsection{Centralizers of maps of $E_n$ algebras and the derived center}
-\label{sec: centralizer}
-
-We briefly review some of the main notions and refer the reader to \cite{LurieHA} Section 5.3 and \cite{FrancisHH} for detailed discussions.
-Let $\cC^\otimes$ denote a presentable stable symmetric monoidal $\infty$-category (for us, chain complexes over a field $k$ of characteristic zero with~$\otimes_k$).
-
-\begin{dfn}\label{D:centralizer}
-For a map $f: A \to B$ of $E_n$ algebras in $\cC$, 
-the {\em centralizer} ${\frak Z}_{E_n}(f)$ is the $E_n$ algebra in $\cC$ that is universal among those that fit in a commuting diagram
-\[
-\begin{tikzcd}
-& {\frak Z}_{E_n}(f) \otimes A \arrow[dr] & \\
-A \arrow[ur, "u"] \arrow[rr, "f"] && B
-\end{tikzcd}
-\]
-where $u$ is induced by the identity map $1_\cC \to {\frak Z}_{E_n}(f)$.
-The {\em center} of an $E_n$ algebra $A$ is the centralizer of its identity morphism $\id_A: A \to A$. We will denote it ${\frak Z}_{E_n}(A) 
-:= {\frak Z}_{E_n}(\id_A)$.
-\end{dfn}
-When $n=1$ and $\cC$ is the category of vector spaces, the centralizer of $f: A \to B$ consists of the subspace of elements of $B$ that commute with the image $f(A)$ inside~$B$.
-Thus, the center of $A$ agrees with the traditional notion.
-See Theorem 5.3.1.30 of~\cite{LurieHA}, or Proposition 6.22 in~\cite{GTZ3}, for an alternative characterization.
-
-\begin{prp}\label{T:centralizer=inthom} 
-The centralizer ${\frak Z}_{E_n}(f)$ exists and can be identified with the classifying object for maps from $A$ to $B$ in the $\infty$-category $\Mod^{E_n}_A(\cC)$.
-\mahmoud{we should probably spell out the meaning of the classifying object in this case to make it obvious that the centralizer is the classifying object}
-\end{prp}
-
-When $n=1$ and $\cC$ is chain complexes over the field $k$, then $\Mod^{E_1}_A(\cC)$ is equivalent to $A\otimes A^{op}$-modules and hence ${\frak Z}_{E_1}(f) \simeq {\rm Hoch}^*(A,B_f)$,
-where $B_f$ denotes $B$ viewed as an $A\otimes A^{op}$-modules via the map~$f$.
-
-We record a key fact drawn from \cite{LurieHA},~\cite{FrancisHH}  and \cite{GG-Notes}, which generalizes this situation.
-
-\begin{prp}\label{P:ModentoModSn}
-Let $\cC^\otimes$ be a presentable symmetric monoidal stable $\infty$-category whose tensor product preserves colimits in each variable separately.
-For $A$ be an $E_n$ algebra in $\cC$,
-the $\infty$-category $\Mod^{E_n}_A(\cC)$ is equivalent to the $\infty$-category $\LMod_{\int_{S^{n-1} A}}(\cC)$.
-\end{prp}
-
-See Remark 7.3.5.3 of \cite{LurieHA}, Coroallary 13 in~\cite{GG-Notes} and Section 2 of \cite{FrancisHH}.
-Concretely, this claim arises from the fact that as a module over $A$ as an $E_n$ algebra, 
-$M \in \Mod^{E_n}_A(\cC)$ is equipped with a commuting family of actions by $A$ parametrized by $\RR^n \setminus \{0\}\cong S^{n-1} \times \RR_{>0}$.
-This action factors through the left action of the $E_1$ algebra $\int_{S^{n-1} \times \RR} A$ arising from factorization homology over the complement of the origin,
-which integrates all those actions and through which they all factor.
-\mahmoud{i think the picture of why it is a one-sided action is clearer if we use $S^{n-1} \times \RR^+$ istead of $S^{n-1} \times \RR$}
-As shown in Theorem 7.5.3.1 of \cite{LurieHA} and earlier in Proposition 3.16 of \cite{FrancisHH}, 
-this algebra $\int_{S^{n-1} \times \RR} A$ is equivalent to ${\rm Free}(1_\cC)$, 
-the image of the unit object $1_\cC \in \cC$ under the left adjoint ${\rm Free}$ to the forgetful functor $\Mod^{E_n}_A(\cC) \to \cC$.
-
-There is an immediate analogue of the notion of centralizers for factorization algebras.
-\begin{dfn}\label{D:centralizerFacAlgebra}
- Let $X$ be a manifold and  $f: A(-) \to B(-)$ be a map of locally constant factorization algebras over $X$.  
-The {\em centralizer} ${\frak Z}(\mathbf{f})(-)$ is the locally constant factorization
-algebra over $X$ in $\cC$ that is universal among those that fit in a commuting diagram
-\[
-\begin{tikzcd}
-& {\frak Z}(\mathbf{f}) \otimes A(-) \arrow[dr] & \\
-A(-) \arrow[ur, "u"] \arrow[rr, "f"] && B(-)
-\end{tikzcd}
-\]
-where $u$ is induced by the canonical map $1_\cC= {\frak Z}(\mathbf{f})(\emptyset) \to {\frak Z}(\mathbf{f})(-)$ induced by the inclusion of the emptyset.
-The {\em center} of a locally constant  factorization algebra
-$A(-)$ is the centralizer of its identity morphism $\id: A(-) \to A(-)$.
-\end{dfn}
-By Theorem~\ref{T:En=Fac} and Proposition~\ref{T:centralizer=inthom} (also see~\cite{GTZ3}) we get
-\begin{lmm}\label{L:faccentralizerexists}
- Let $X=\RR^n$. Then a centralizer of $f: A(-)\to B(-)$ exists for any morphism of locally constant factorization algebras over $X$. Further, if the above map is induced by 
- an $E_n$-algebra morphism $f:A\to B$, then 
- ${\frak Z}(\mathbf{f})(-)$ is the locally constant factorization algebra over $\RR^n$ associated to 
- the $E_n$-algebra ${\frak Z}_{E_n}(f)$.
-\end{lmm}
-
-We now use these results to prove the central claim of Theorem~\ref{thm: centralizer}.
 

### 2020-08-20 draft.tex
more rearrangment

@@
 \begin{itemize}
-\item Lurie and Francis give a characterization of the centralizer ${\frak Z}_{E_n}(f)$ of any $E_n$ algebra map $f: A \to B$ as the ``internal hom'' in left $\int_{S^{n-1}}A$ -modules from $A$ to $B_f$, where $B_f$ denotes $B$ viewed as a left module via the map~$f$.
+\item Lurie and Francis give a characterization of the centralizer ${\frak Z}_{E_n}(f)$ of any $E_n$ algebra map $f: A \to B$ as the ``internal hom'' in left $\int_{S^{n-1}}A$-modules from $A$ to $B_f$, where $B_f$ denotes $B$ viewed as a left module via the map~$f$.
+\item Their work shows, in fact, that $f$ equips $B$ with the structure of an $E_n$ algebra in $\fg$-representations,
+which we also denote $B_f$, as it relies on related arguments. \owen{Let's hope we can justify this!}
 \item Knudsen verifies that we can model the enveloping $E_n$ algebra by a strict prefactorization algebra ${\tt U}_n \fg = \cliel(\Omega_c \otimes \fg)$ on $\RR^n$, which is weakly locally constant.
@@
 Lurie \cite{LurieHA} explains why we can work with the homotopy coherent version of prefactorization algebras, and then strictification theorems from the model category literature on operads say we can work with strict prefactorization algebras.
-\item  In particular, given an $E_n$ algebra $B$,  let ${\tt B}$ denote a strict prefactorization algebra modeling~$B$.
-Strictification lets us associate to the map $f: \UU_n \fg \to B$, a map ${\tt f}: {\tt U}_n \fg \to {\tt B}$ of strict prefactorization algebras. 
-\owen{It might be better to first use the adjunction to get a map of homotopy-coherent Lie algebras $\fg \to B$ but I'm not sure this plays nicely with the other strictification\dots}
-\item From the map ${\tt f}$, we read off an $\fg$-action on ${\tt B}$ intertwining with the structure maps of ${\tt B}$. 
-That is, we have a prefactorization algebra ${\tt B}_f$ taking values in the 1-category $\Ch(\Rep(\fg))$ of chain complexes of $\fg$-representations.
-\item We then construct an explicit strict prefactorization algebra $\clies(\Omega \otimes \fg, B_f)$ as a kind of ``convolution algebra.'' 
+\item  In particular, given our $E_n$ algebra $B_f$ in $\fg$-modules,  model it by a strict prefactorization algebra ${\tt B}_f$ with values in a nice model category $\Mod_\fg(\Ch_k)$ of dg $\fg$-representations.
+The forgetful functor $\Mod_\fg(\Ch_k) \to \Ch_k$ lets us produce a strict prefactorization algebra ${\tt B}$ that models~$B$.
+\item By construction, the action of $\fg$ on ${\tt B}_f$ determines a map ${\tt f}:  {\tt U}_n \fg \to {\tt B}$ of strict prefactorization algebras.
+\owen{I'm not sure this is true ... but let's be optimistic.}
+\item We then construct an explicit strict prefactorization algebra $\clies(\Omega \otimes \fg, {\tt B}_f)$ as a kind of ``convolution algebra.'' 
 \item We show this object fits canonically into a centralizer diagram: there is a map
@@
 
+\owen{I might move the discussion of $E_n$-modules from near proposition~\ref{P:ModentoModSn} to here. 
+We can then sketch here the argument you explained about $E_n$-monoidal products to show that $B$ lifts to an $E_n$ algebra $B_f$ in $\fg$-modules.}
+
 \subsection{Enveloping $E_n$ algebras of Lie algebras}
@@
 
-\begin{prp}\label{P:ModentoModSn}
+\begin{prp}
+\label{P:ModentoModSn}
 Let $\cC^\otimes$ be a presentable symmetric monoidal stable $\infty$-category whose tensor product preserves colimits in each variable separately.
@@
 
-There is an immediate analogue of the notion of centralizers for factorization algebras.
-\begin{dfn}\label{D:centralizerFacAlgebra}
- Let $X$ be a manifold and  $f: A(-) \to B(-)$ be a map of locally constant factorization algebras over $X$.  
-The {\em centralizer} ${\frak Z}(\mathbf{f})(-)$ is the locally constant factorization
-algebra over $X$ in $\cC$ that is universal among those that fit in a commuting diagram
-\[
-\begin{tikzcd}
-& {\frak Z}(\mathbf{f}) \otimes A(-) \arrow[dr] & \\
-A(-) \arrow[ur, "u"] \arrow[rr, "f"] && B(-)
-\end{tikzcd}
-\]
-where $u$ is induced by the canonical map $1_\cC= {\frak Z}(\mathbf{f})(\emptyset) \to {\frak Z}(\mathbf{f})(-)$ induced by the inclusion of the emptyset.
+\owen{We need to track here how the $E_n$-monoidal product intertwines with these functors.
+If we can find a juicy comment in \cite{LurieHA} or \cite{FrancisHH}, 
+we can claim they've shown that the map $f: \UU_n \fg \to B$ allows us to ``forget'' $B$ to an $E_n$ algebra in $\fg$-modules.}
+
+\owen{I commented out a discussion of the factorization algebra version of centralizer, as I don't think it's relevant.}
+
+%
+%There is an immediate analogue of the notion of centralizers for factorization algebras.
+%\begin{dfn}\label{D:centralizerFacAlgebra}
+% Let $X$ be a manifold and  $f: A(-) \to B(-)$ be a map of locally constant factorization algebras over $X$.  
+%The {\em centralizer} ${\frak Z}(\mathbf{f})(-)$ is the locally constant factorization
+%algebra over $X$ in $\cC$ that is universal among those that fit in a commuting diagram
+%\[
+%\begin{tikzcd}
+%& {\frak Z}(\mathbf{f}) \otimes A(-) \arrow[dr] & \\
+%A(-) \arrow[ur, "u"] \arrow[rr, "f"] && B(-)
+%\end{tikzcd}
+%\]
+%where $u$ is induced by the canonical map $1_\cC= {\frak Z}(\mathbf{f})(\emptyset) \to {\frak Z}(\mathbf{f})(-)$ induced by the inclusion of the emptyset.
 The {\em center} of a locally constant  factorization algebra
-$A(-)$ is the centralizer of its identity morphism $\id: A(-) \to A(-)$.
-\end{dfn}
-By Theorem~\ref{T:En=Fac} and Proposition~\ref{T:centralizer=inthom} (also see~\cite{GTZ3}) we get
-\begin{lmm}\label{L:faccentralizerexists}
- Let $X=\RR^n$. Then a centralizer of $f: A(-)\to B(-)$ exists for any morphism of locally constant factorization algebras over $X$. Further, if the above map is induced by 
- an $E_n$-algebra morphism $f:A\to B$, then 
- ${\frak Z}(\mathbf{f})(-)$ is the locally constant factorization algebra over $\RR^n$ associated to 
- the $E_n$-algebra ${\frak Z}_{E_n}(f)$.
-\end{lmm}
+%$A(-)$ is the centralizer of its identity morphism $\id: A(-) \to A(-)$.
+%\end{dfn}
+%By Theorem~\ref{T:En=Fac} and Proposition~\ref{T:centralizer=inthom} (also see~\cite{GTZ3}) we get
+%\begin{lmm}\label{L:faccentralizerexists}
+% Let $X=\RR^n$. Then a centralizer of $f: A(-)\to B(-)$ exists for any morphism of locally constant factorization algebras over $X$. Further, if the above map is induced by 
+% an $E_n$-algebra morphism $f:A\to B$, then 
+% ${\frak Z}(\mathbf{f})(-)$ is the locally constant factorization algebra over $\RR^n$ associated to 
+% the $E_n$-algebra ${\frak Z}_{E_n}(f)$.
+%\end{lmm}
+%
 
@@
 \section{Strictifying the map $f: \UU_n \fg \to B$}
+
+\owen{If our new strategy works, then we can get rid of this section.}
 

### 2020-08-21 draft.tex
more rearrangemetns

@@
 
-\owen{I might move the discussion of $E_n$-modules from near proposition~\ref{P:ModentoModSn} to here. 
-We can then sketch here the argument you explained about $E_n$-monoidal products to show that $B$ lifts to an $E_n$ algebra $B_f$ in $\fg$-modules.}
-
 \subsection{Enveloping $E_n$ algebras of Lie algebras}
@@
 This would be worth explaining because we can then use a much simpler strictification of $f$.}
+
+\subsection{Maps out of enveloping $E_n$ algebras}
+
+\owen{I might move the discussion of $E_n$-modules from near proposition~\ref{P:ModentoModSn} to here. 
+We can then sketch here the argument you explained about $E_n$-monoidal products to show that $B$ lifts to an $E_n$ algebra $B_f$ in $\fg$-modules.}
+
+These results can be marshaled to prove the following.
+
+\begin{prp}
+Let $\Ch_k^{\otimes_k}$ be the symmetric monoidal $\infty$-category arising from cochain complexes of vector spaces over a characteristic zero field $k$.
+Let $\fg$ be a Lie algebra in $\Ch_k^{\otimes_k}$, i.e., a dg Lie algebra, 
+and let $B$ be an $E_n$ algebra in $\Ch_k^{\otimes_k}$.
+Then given a map of $E_n$ algebras $f: \UU_n \fg \to B$, 
+there exists a lift of $B$ to an $E_n$ algebra $B_f$ in $\Mod_\fg(\Ch_k^{\otimes_k})^{\otimes_k}$, the symmetric monoidal $\infty$-category of $\fg$-modules.
+\end{prp}
+
+That is, the forgetful functor $\Mod_\fg(\Ch_k^{\otimes_k})^{\otimes_k} \to \Ch_k^{\otimes_k}$ sends $B_f$ to~$B$.
+
+\begin{proof}
+\owen{Essentially, we verify that a bunch of "forgetful functors" are $E_n$-monoidal.}
+\end{proof}
+
+By the strictification results, $B_f$ admits a model ${\tt B}_f$ as a strict prefactorization algebra with values in the stable symmetric monoidal \owen{other adjectives} model category $\Alg_\Lie(\Ch_k^{\rm dg})$.
+As the forgetful functor $\Alg_\Lie(\Ch_k^{\rm dg}) \to \Alg_\Lie(\Ch_k^{\rm dg})$ is \owen{more adjectives},
+we obtain an underlying strict prefactorization algebra ${\tt B}$ with values in cochain complexes.
+Moreover, there is a canonical map $\cliel(\fg[-n]) \to {\tt B}$ of strict prefactorization algebras that models $f$, as desired.
+
+\owen{I'd love to say we can produce a map from our favorite model of the envelope, but we may not need it.}
 

### 2020-08-21 draft.tex
merge

--- 2020-08-10 draft.tex
@@
 
-See section~\ref{sec: en background} for a brief discussion of $E_n$ algebras and their relationship with locally constant factorization algebras on $\RR^n$, section~\ref{sec: enveloping} for a brief discussion of the enveloping $E_n$ algebra construction, and see section~\ref{sec: centralizer}
+See section~\ref{sec: enveloping} for a brief discussion of the enveloping $E_n$ algebra construction, and see section~\ref{sec: centralizer} 
 for a brief discussion about centralizers to maps of $E_n$ algebras.
@@
 \label{thm: centralizer}
-Let $\UU_n \fg$ be the enveloping $E_n$ algebra of a dg Lie algebra $\fg$ and let $f: \UU_n \fg \to B$ a map of augmented $E_n$ algebras.
-Then
+Let $\UU_n \fg$ be the enveloping $E_n$ algebra of a dg Lie algebra $\fg$ and $f: \UU_n \fg \to B$ a map of augmented $E_n$ algebras that gives $B$
+the structure of an $E_n$ algebra in $\fg$-modules\footnote{see Proposition~\ref{P:inducedEngModStruct}}. 
+The centralizer ${\frak Z}_{E_n}(f)$ is an $E_n$-algebra modeled by the Chevalley-Eilenberg 
+cochains $\clies(\fg, B)$ equipped with the convolution $E_n$-product.
+\end{thm}
+
+\owen{Here is an outline of the proof strategy, with ingredients indicated:}
+
+Existing work gives us some insight into the situation:
 \begin{itemize}
-\item $f$ equips $B$ with the structure of an $E_n$ algebra in $\fg$-modules and
-\item the centralizer ${\frak Z}_{E_n}(f)$ is an $E_n$-algebra modeled by the Chevalley-Eilenberg 
-cochains $\clies(\fg, B)$ equipped with the convolution $E_n$-product.
-\end{itemize}
-\end{thm}
-
-\owen{Here is an outline of the proof strategy, with ingredients indicated:}
-
-Existing work provides insight into and context for the situation:
-\begin{itemize}
-\item Lurie and Francis give a characterization of the centralizer ${\frak Z}_{E_n}(f)$ of any $E_n$ algebra map $f: A \to B$ as the ``internal hom'' in left $\int_{S^{n-1}}A$ -modules from $A$ to $B_f$, where $B_f$ denotes $B$ viewed as a left module via the map~$f$.
-\item Knudsen verifies that we can model the enveloping $E_n$ algebra by a strict prefactorization algebra ${\tt U}_n \fg = \cliel(\Omega_c \otimes \fg)$ on $\RR^n$, which is weakly locally constant.
-\item In combination, the centralizer is characterized up to quasi-isomorphism, 
+\item Lurie and Francis give a characterization of the centralizer of any map $f: A \to B$ as the ``internal hom'' in left $\int_{S^{n-1}}A$ -modules from $A$ to $B_f$, where $B_f$ denotes $B$ viewed as a left module via the map~$f$.
+\item Knudsen verifies that we can model the enveloping $E_n$ algebra by a strict prefactorization algebra $\cliel(\Omega_c \otimes \fg)$ on $\RR^n$, which is weakly locally constant.
+\item In combination, we have an explicit characterization of the centralizer up to quasi-isomorphism, 
 since it is easy to compute the factorization homology of the enveloping algebra $\UU_n \fg$ over a sphere.
 \end{itemize}
-Our approach leverages these results as follows to prove the theorem.
+
+Our approach has the following steps:
 \begin{enumerate}
-\item First, we transfer the question to the setting of strict prefactorization algebras on $\RR^n$ that are weakly locally constant.
-Lurie \cite{LurieHA} explains why we can work with the homotopy coherent version of prefactorization algebras, and then strictification theorems from the model category literature on operads say we can work with strict prefactorization algebras.
-\item  In particular, given an $E_n$ algebra $B$,  let ${\tt B}$ denote a strict prefactorization algebra modeling~$B$.
-Strictification lets us associate to the map $f: \UU_n \fg \to B$, a map ${\tt f}: {\tt U}_n \fg \to {\tt B}$ of strict prefactorization algebras. 
-\owen{It might be better to first use the adjunction to get a map of homotopy-coherent Lie algebras $\fg \to B$ but I'm not sure this plays nicely with the other strictification\dots}
-\item From the map ${\tt f}$, we read off an $\fg$-action on ${\tt B}$ intertwining with the structure maps of ${\tt B}$. 
-That is, we have a prefactorization algebra ${\tt B}_f$ taking values in the 1-category $\Ch(\Rep(\fg))$ of chain complexes of $\fg$-representations.
-\item We then construct an explicit strict prefactorization algebra $\clies(\Omega \otimes \fg, B_f)$ as a kind of ``convolution algebra.'' 
-\item We show this object fits canonically into a centralizer diagram: there is a map
-\[
-\clies(\Omega \otimes \fg, {\tt B}_f) \otimes {\tt U}_n \fg \to {\tt B}_f
-\]
-such that precomposing with the map $1 \otimes \id_{{\tt U}_n \fg}$ is the map~${\tt f}$.
-Fitting into such a diagram guarantees a canonical map $\clies(\Omega \otimes \fg, {\tt B}_f) \to {\tt Z}_f$ as strict prefactorization algebras. 
-\item We then verify that this map is a quasi-isomorphism on disks. 
+\item Transfer the question to the setting of strict prefactorization algebras on $\RR^n$ that are weakly locally constant.
+(First use Lurie to explain that we can work with the homotopy coherent version, and then invoke strictification theorems from the model category literature on operads.)
+\item In particular, explain why $B$ determines some prefactorization algebra that I'll also call~$B$.
+Explain how the map $f: \UU_n \fg \to B$ determines a $\fg$-action on $B$.
+That is, we can obtain a prefactorization algebra $B_f$ taking values in the 1-category of $\fg$-representations.
+See Lemma \ref{L:inducedFacgModstruct}. 
+\item Construct an explicit strict prefactorization algebra $\clies(\Omega \otimes \fg, B_f)$ as a kind of ``convolution algebra", Lemma \ref{L:ClieFacDef}.
+We then argue that it canonically fits into a centralizer diagram: there is a map of prefactorization algebras
+\[
+\clies(\Omega \otimes \fg, B_f) \otimes \UU_n \fg \to B_f
+\]
+such that precomposing with the map $1 \otimes \id_{\UU_n \fg}$ is the map~$f$, see Lemma \ref{L:ComTriangCent}.
+\item Fitting into such a diagram guarantees a canonical map $\clies(\Omega \otimes \fg, B_f) \to \cZ_f$ as strict prefactorization algebras.
+\item Verify that this map is a quasi-isomorphism on disks, Lemma \ref{L:thetaquisondisk}.
+Hence it induces a weak equivalence of the associated $E_n$ algebras. 
 \end{enumerate}
-Hence it induces a weak equivalence of the associated $E_n$ algebras.
-
-\owen{Some easy but important situations to examine:}
+
+Some easy but important situations to examine:
 \begin{itemize}
@@
 
-By Knudsen's results \cite{Knudsen}, we have the following explicit applications of our main theorem~\ref{thm: center}.
-
-\owen{I think we should just work in $Ch(\RR)$ or $Ch(\CC)$ throughout.}
+\owen{End of strategy}
+
+By Knudsen's results \cite{Knudsen}, we have the following explicit interpretation of our main theorem~\ref{thm: center}, which is the second part of our main theorem.
 
@@
 Let $k$ is $\RR$ or $\CC$, and assume $\UU_n \rho:  \UU_n \fg \to \UU_n \fh$ is induced by a map of Lie algebras $\rho: \fg \to \fh$. 
-Then the centralizer ${\frak Z}_{E_n}(\UU_n \rho)$ is modeled by the locally constant factorization algebra that assigns
+Then, the centralizer ${\frak Z}_{E_n}(\UU_n \rho)$ is modeled by the locally constant factorization algebra that assigns
 \[
@@
 
-\section{Background}
-
-\owen{Add overview}
-
-\subsection{Recollections on $E_n$ algebras and prefactorization algebras}
-\label{sec: en background}
-
-\owen{Recall Jacob's results and what it means in conjunction with strictification.}
-
-\owen{I want to work with the colored operad of round disks (or rectilinear boxes) in $\RR^n$.}
-
-Note that in the theorem we use the following equivalence due to Lurie~\cite{LurieHA}.
-
-\begin{thm}
-\label{T:En=Fac} 
-There is an equivalence of $\infty$-categories between $E_n$-algebras and locally constant prefactorization algebras on~$\RR^n$.
-\end{thm}
-
-\subsection{Enveloping $E_n$ algebras of Lie algebras}
-\label{sec: enveloping}
-
-Although \cite{Knudsen} develops an adjunction between Lie and $E_n$ algebras \mahmoud{non-unital?}\greg{Both I think}\owen{augmented is probably best for us}
+\section{Enveloping $E_n$ algebras of Lie algebras}
+
+Although \cite{Knudsen} develops an adjunction between Lie and $E_n$ algebras \mahmoud{non-unital?}\greg{Both I think}
 in any presentable symmetric monoidal stable $\infty$-category $\cC$,
@@
 The second part of this result leads to the explicit models in our theorems.
+Note that in the theorem we use the following equivalence due to Lurie~\cite{LurieHA}.
+
+\begin{thm}
+\label{T:En=Fac} 
+There is an equivalence of $\infty$-categories between $E_n$-algebras and locally constant factorization algebras.
+\end{thm}
 
 \begin{rmk}
-It follows from theorem~\ref{T:UnofLie} that for any $E_n$-algebra $B$, 
-its underlying complex is equipped with a homotopy-coherent Lie algebra structure.
-Depending on one's preferences, one can work with an an $L_\infty$-algebra structure or strictify to a dg Lie algebra structure (at the cost of replacing the complex with something quasi-isomorphic but typically much larger).
+ It follows from theorem~\ref{T:UnofLie} that for any $E_n$-algebra $B$, the underlying complex of the $L_\infty$-algebra $\oblv_n(B)$ is naturally quasi-isomorphic to 
+ $\Sigma^{n-1}B = B[n-1]$. Henceforth in this paper, we will simply use the notation  $B[n-1]$ for $\oblv_n(B)$, that is tacitly assume 
+ $B[n-1]$ is endowed with the $L_\infty$structure induced by its $E_n$ algebra structure.
 \end{rmk}
 
-\owen{\label{note on little model} Note that if we work with the colored operad of disks/boxes, then Poincar\'e lemma tells us that we can use the strict model $\cliel(\fg[-n])$ rather than the fatter model $\cliels(\Omega^*_c(U) \otimes \fg)$.
-I think Ben actually shows this too.
-This would be worth explaining because we can then use a much simpler strictification of $f$.}
-
-\subsection{Centralizers of maps of $E_n$ algebras and the derived center}
-\label{sec: centralizer}
-
-We briefly review some of the main notions and refer the reader to \cite{LurieHA} Section 5.3 and \cite{FrancisHH} for detailed discussions.
-Let $\cC^\otimes$ denote a presentable stable symmetric monoidal $\infty$-category (for us, chain complexes over a field $k$ of characteristic zero with~$\otimes_k$).
-
-\begin{dfn}\label{D:centralizer}
-For a map $f: A \to B$ of $E_n$ algebras in $\cC$, 
-the {\em centralizer} ${\frak Z}_{E_n}(f)$ is the $E_n$ algebra in $\cC$ that is universal among those that fit in a commuting diagram
-\[
-\begin{tikzcd}
-& {\frak Z}_{E_n}(f) \otimes A \arrow[dr] & \\
-A \arrow[ur, "u"] \arrow[rr, "f"] && B
-\end{tikzcd}
-\]
-where $u$ is induced by the identity map $1_\cC \to {\frak Z}_{E_n}(f)$.
-The {\em center} of an $E_n$ algebra $A$ is the centralizer of its identity morphism $\id_A: A \to A$. We will denote it ${\frak Z}_{E_n}(A) 
-:= {\frak Z}_{E_n}(\id_A)$.
-\end{dfn}
-When $n=1$ and $\cC$ is the category of vector spaces, the centralizer of $f: A \to B$ consists of the subspace of elements of $B$ that commute with the image $f(A)$ inside~$B$.
-Thus, the center of $A$ agrees with the traditional notion.
-See Theorem 5.3.1.30 of~\cite{LurieHA}, or Proposition 6.22 in~\cite{GTZ3}, for an alternative characterization.
-
-\begin{prp}\label{T:centralizer=inthom} 
-The centralizer ${\frak Z}_{E_n}(f)$ exists and can be identified with the classifying object for maps from $A$ to $B$ in the $\infty$-category $\Mod^{E_n}_A(\cC)$.
-\mahmoud{we should probably spell out the meaning of the classifying object in this case to make it obvious that the centralizer is the classifying object}
-\end{prp}
-
-When $n=1$ and $\cC$ is chain complexes over the field $k$, then $\Mod^{E_1}_A(\cC)$ is equivalent to $A\otimes A^{op}$-modules and hence ${\frak Z}_{E_1}(f) \simeq {\rm Hoch}^*(A,B_f)$,
-where $B_f$ denotes $B$ viewed as an $A\otimes A^{op}$-modules via the map~$f$.
-
-We record a key fact drawn from \cite{LurieHA},~\cite{FrancisHH}  and \cite{GG-Notes}, which generalizes this situation.
-
-\begin{prp}\label{P:ModentoModSn}
-Let $\cC^\otimes$ be a presentable symmetric monoidal stable $\infty$-category whose tensor product preserves colimits in each variable separately.
-For $A$ be an $E_n$ algebra in $\cC$,
-the $\infty$-category $\Mod^{E_n}_A(\cC)$ is equivalent to the $\infty$-category $\LMod_{\int_{S^{n-1} A}}(\cC)$.
-\end{prp}
-
-See Remark 7.3.5.3 of \cite{LurieHA}, Coroallary 13 in~\cite{GG-Notes} and Section 2 of \cite{FrancisHH}.
-Concretely, this claim arises from the fact that as a module over $A$ as an $E_n$ algebra, 
-$M \in \Mod^{E_n}_A(\cC)$ is equipped with a commuting family of actions by $A$ parametrized by $\RR^n \setminus \{0\}\cong S^{n-1} \times \RR_{>0}$.
-This action factors through the left action of the $E_1$ algebra $\int_{S^{n-1} \times \RR} A$ arising from factorization homology over the complement of the origin,
-which integrates all those actions and through which they all factor.
-\mahmoud{i think the picture of why it is a one-sided action is clearer if we use $S^{n-1} \times \RR^+$ istead of $S^{n-1} \times \RR$}
-As shown in Theorem 7.5.3.1 of \cite{LurieHA} and earlier in Proposition 3.16 of \cite{FrancisHH}, 
-this algebra $\int_{S^{n-1} \times \RR} A$ is equivalent to ${\rm Free}(1_\cC)$, 
-the image of the unit object $1_\cC \in \cC$ under the left adjoint ${\rm Free}$ to the forgetful functor $\Mod^{E_n}_A(\cC) \to \cC$.
-
-There is an immediate analogue of the notion of centralizers for factorization algebras.
-\begin{dfn}\label{D:centralizerFacAlgebra}
- Let $X$ be a manifold and  $f: A(-) \to B(-)$ be a map of locally constant factorization algebras over $X$.  
-The {\em centralizer} ${\frak Z}(\mathbf{f})(-)$ is the locally constant factorization
-algebra over $X$ in $\cC$ that is universal among those that fit in a commuting diagram
-\[
-\begin{tikzcd}
-& {\frak Z}(\mathbf{f}) \otimes A(-) \arrow[dr] & \\
-A(-) \arrow[ur, "u"] \arrow[rr, "f"] && B(-)
-\end{tikzcd}
-\]
-where $u$ is induced by the canonical map $1_\cC= {\frak Z}(\mathbf{f})(\emptyset) \to {\frak Z}(\mathbf{f})(-)$ induced by the inclusion of the emptyset.
-The {\em center} of a locally constant  factorization algebra
-$A(-)$ is the centralizer of its identity morphism $\id: A(-) \to A(-)$.
-\end{dfn}
-By Theorem~\ref{T:En=Fac} and Proposition~\ref{T:centralizer=inthom} (also see~\cite{GTZ3}) we get
-\begin{lmm}\label{L:faccentralizerexists}
- Let $X=\RR^n$. Then a centralizer of $f: A(-)\to B(-)$ exists for any morphism of locally constant factorization algebras over $X$. Further, if the above map is induced by 
- an $E_n$-algebra morphism $f:A\to B$, then 
- ${\frak Z}(\mathbf{f})(-)$ is the locally constant factorization algebra over $\RR^n$ associated to 
- the $E_n$-algebra ${\frak Z}_{E_n}(f)$.
-\end{lmm}
-
-We now turn to proving Theorem~\ref{thm: centralizer}.
-
-\section{Strictifying the map $f: \UU_n \fg \to B$}
-
-As a first step, we analyze the strictification of the map $f: \UU_n \fg \to B$ and show how it lets us view $B$ as an $E_n$ algebra in~$\Ch(\Rep(\fg))$.
-
-By using the small model \owen{see my comment \ref{note on little model}}, we can strictify to obtain a map
-\[
-{\tt f}: \cliel(\fg[-n]) \to {\tt B}.
-\]
-
-\owen{And now I'm really confused.}
-
 \owen{I'm not wild about Greg's phrasing below. Also, I'd prefer to move the explicit formulas later, when we've shifted our setting to strict prefactorization algebras.}
-
-\begin{rmk}
-It follows from theorem~\ref{T:UnofLie} that for any $E_n$-algebra $B$, 
-the underlying complex of the $L_\infty$-algebra $\oblv_n(B)$ is naturally quasi-isomorphic to $\Sigma^{n-1}B = B[n-1]$. 
-Henceforth in this paper, we will simply use the notation $B[n-1]$ for $\oblv_n(B)$, 
-that is tacitly assume we $B[n-1]$ is endowed with the $L_\infty$structure induced by its $E_n$ algebra structure.
-\end{rmk}
 
@@
 which makes $B[n-1]$ into a $\fg$-module and therefore its shift $B$ inherits a  $\fg$-module structure as well from $f$.
-\begin{prp}\label{P:inducedEngModStruct} Let $f:\UU_n \fg \to B$ be an $E_n$-algebra morphism. The induced  
- $\fg$ $L_\infty$-module on $B$ lifts canonically to make  $B$ into an $E_n$-algebra in $\fg$-module. 
+
+\brian{let's start with a strict representative $B$. 
+So we have an actual locally constant factorization algebra.}
+
+\begin{prp}\label{P:inducedEngModStruct} Let $f:\UU_n \fg \to B$ be an $E_n$-algebra morphism. 
+The induced $\fg$ $L_\infty$-module on $B$ lifts canonically to make  $B$ into an $E_n$-algebra in the category of $\fg$-modules that we denote by $B_f$. 
 \end{prp}
@@
  where $B(-)$ is the factorization algebra associated to $B$.
+ \brian{How about $\ul{B}$ instead?}
+
 \begin{lmm}\label{L:inducedFacgModstruct} The factorization algebra map  $\mathbf{f}$ makes $B(-)$ into an homotopy cosheaf of $L_\infty$-modules over 
@@
 where $\rho$ is given by the restriction of forms onto a subspace.
+
 \begin{lmm}\label{L:ClieFacDef} For any (resp. locally constant) factorization algebra $B(-)$ and factorization algebra map $\mathbf{f}:\UU_n(\fg) \to B(-)$, 
@@
 \end{rmk}
+
+\section{Centralizers of maps of $E_n$ algebras and the derived center}
+\label{sec: centralizer}
+
+We briefly review some of the main notions and refer the reader to \cite{LurieHA} Section 5.3 and \cite{FrancisHH} for detailed discussions.
+Let $\cC^\otimes$ denote a presentable stable symmetric monoidal $\infty$-category (for us, chain complexes over a field $k$ of characteristic zero with~$\otimes_k$).
+
+\begin{dfn}\label{D:centralizer}
+For a map $f: A \to B$ of $E_n$ algebras in $\cC$, 
+the {\em centralizer} ${\frak Z}_{E_n}(f)$ is the $E_n$ algebra in $\cC$ that is universal among those that fit in a commuting diagram
+\[
+\begin{tikzcd}
+& {\frak Z}_{E_n}(f) \otimes A \arrow[dr] & \\
+A \arrow[ur, "u"] \arrow[rr, "f"] && B
+\end{tikzcd}
+\]
+where $u$ is induced by the identity map $1_\cC \to {\frak Z}_{E_n}(f)$.
+The {\em center} of an $E_n$ algebra $A$ is the centralizer of its identity morphism $\id_A: A \to A$. We will denote it ${\frak Z}_{E_n}(A) 
+:= {\frak Z}_{E_n}(\id_A)$.
+\end{dfn}
+When $n=1$ and $\cC$ is the category of vector spaces, the centralizer of $f: A \to B$ consists of the subspace of elements of $B$ that commute with the image $f(A)$ inside~$B$.
+Thus, the center of $A$ agrees with the traditional notion.
+See Theorem 5.3.1.30 of~\cite{LurieHA}, or Proposition 6.22 in~\cite{GTZ3}, for an alternative characterization.
+
+\begin{prp}\label{T:centralizer=inthom} 
+The centralizer ${\frak Z}_{E_n}(f)$ exists and can be identified with the classifying object for maps from $A$ to $B$ in the $\infty$-category $\Mod^{E_n}_A(\cC)$.
+\mahmoud{we should probably spell out the meaning of the classifying object in this case to make it obvious that the centralizer is the classifying object}
+\end{prp}
+
+When $n=1$ and $\cC$ is chain complexes over the field $k$, then $\Mod^{E_1}_A(\cC)$ is equivalent to $A\otimes A^{op}$-modules and hence ${\frak Z}_{E_1}(f) \simeq {\rm Hoch}^*(A,B_f)$,
+where $B_f$ denotes $B$ viewed as an $A\otimes A^{op}$-modules via the map~$f$.
+
+We record a key fact drawn from \cite{LurieHA},~\cite{FrancisHH}  and \cite{GG-Notes}, which generalizes this situation.
+
+\begin{prp}\label{P:ModentoModSn}
+Let $\cC^\otimes$ be a presentable symmetric monoidal stable $\infty$-category whose tensor product preserves colimits in each variable separately.
+For $A$ be an $E_n$ algebra in $\cC$,
+the $\infty$-category $\Mod^{E_n}_A(\cC)$ is equivalent to the $\infty$-category $\LMod_{\int_{S^{n-1} A}}(\cC)$.
+\end{prp}
+
+See Remark 7.3.5.3 of \cite{LurieHA}, Coroallary 13 in~\cite{GG-Notes} and Section 2 of \cite{FrancisHH}.
+Concretely, this claim arises from the fact that as a module over $A$ as an $E_n$ algebra, 
+$M \in \Mod^{E_n}_A(\cC)$ is equipped with a commuting family of actions by $A$ parametrized by $\RR^n \setminus \{0\}\cong S^{n-1} \times \RR_{>0}$.
+This action factors through the left action of the $E_1$ algebra $\int_{S^{n-1} \times \RR} A$ arising from factorization homology over the complement of the origin,
+which integrates all those actions and through which they all factor.
+\mahmoud{i think the picture of why it is a one-sided action is clearer if we use $S^{n-1} \times \RR^+$ istead of $S^{n-1} \times \RR$}
+As shown in Theorem 7.5.3.1 of \cite{LurieHA} and earlier in Proposition 3.16 of \cite{FrancisHH}, 
+this algebra $\int_{S^{n-1} \times \RR} A$ is equivalent to ${\rm Free}(1_\cC)$, 
+the image of the unit object $1_\cC \in \cC$ under the left adjoint ${\rm Free}$ to the forgetful functor $\Mod^{E_n}_A(\cC) \to \cC$.
+
+There is an immediate analogue of the notion of centralizers for factorization algebras.
+\begin{dfn}\label{D:centralizerFacAlgebra}
+ Let $X$ be a manifold and  $f: A(-) \to B(-)$ be a map of locally constant factorization algebras over $X$.  
+The {\em centralizer} ${\frak Z}(\mathbf{f})(-)$ is the locally constant factorization
+algebra over $X$ in $\cC$ that is universal among those that fit in a commuting diagram
+\[
+\begin{tikzcd}
+& {\frak Z}(\mathbf{f}) \otimes A(-) \arrow[dr] & \\
+A(-) \arrow[ur, "u"] \arrow[rr, "f"] && B(-)
+\end{tikzcd}
+\]
+where $u$ is induced by the canonical map $1_\cC= {\frak Z}(\mathbf{f})(\emptyset) \to {\frak Z}(\mathbf{f})(-)$ induced by the inclusion of the emptyset.
+The {\em center} of a locally constant  factorization algebra
+$A(-)$ is the centralizer of its identity morphism $\id: A(-) \to A(-)$.
+\end{dfn}
+By Theorem~\ref{T:En=Fac} and Proposition~\ref{T:centralizer=inthom} (also see~\cite{GTZ3}) we get
+\begin{lmm}\label{L:faccentralizerexists}
+ Let $X=\RR^n$. Then a centralizer of $f: A(-)\to B(-)$ exists for any morphism of locally constant factorization algebras over $X$. Further, if the above map is induced by 
+ an $E_n$-algebra morphism $f:A\to B$, then 
+ ${\frak Z}(\mathbf{f})(-)$ is the locally constant factorization algebra over $\RR^n$ associated to 
+ the $E_n$-algebra ${\frak Z}_{E_n}(f)$.
+\end{lmm}
+
+We now use these results to prove the central claim of Theorem~\ref{thm: centralizer}.
 
@@
 Consider the case $n=1$ and $B = U \fg$ where $f$ is simply the identity map. 
-The Hochschild cohomology of $U \fg$ can be expressed in terms of Lie algebra cohomology as $\Hoch^*(U\fg,U\fg) \simeq \clies(\fg, U\fg)$. 
-On the other hand, our model for the derived center ${\frak Z}(U(\fg))$ of $U \fg$ is the one-dimensional factorization algebra assigning 
+A classic result of \cite{HochSerre} is that the Hochschild cohomology of $U \fg$ can be expressed in terms of Lie algebra cohomology as $\Hoch^*(U\fg,U\fg) \simeq \clies(\fg, U\fg^{ad})$. 
+On the right-hand side, we take the Chevalley--Eilenberg cochain complex with values in the module $U \fg$ equipped with the adjoint action.
+The algebra structure is given by a special case of the convolution product as in Section \ref{??}.
+
+On the other hand, our model for the derived center ${\frak Z}(U(\fg))$ of $U \fg$ is the one-dimensional factorization algebra assigning the cochain complex
 \[
@@
 to each open set $U \subset \RR$.
-In particular, the factorization homology of the derived center along the closed manifold $S^1$ can be computed as
+In the case that $U$ is an interval, this cochain complex is quasi-isomorphic to $\clies (\fg , U\fg^{ad})$.
+Furthermore, one can verify that the resulting $E_1$-algebra structure agrees with the one coming from convolution.
+
+Our model also gives us a simple description of the factorization homology of the derived center along the circle $S^1$.
 \[

### 2020-08-25 draft.tex
small edit

@@
 \begin{proof}
-\owen{Essentially, we verify that a bunch of "forgetful functors" are $E_n$-monoidal.}
+By Corollary 3.4.4.6 of \cite{LurieHA}, any $E_n$ algebra $B$ defines an $E_n$-monoidal category ${\rm Mod}_B^{E_n} (\Ch_k^{\otimes k})$ of $E_n$-$B$-modules. 
+Furthermore, by Corollary 3.4.1.7 \cite{LurieHA} (see also Example 3.4.4.7 of the same reference) $B$ can be viewed as an $E_n$-algebra in this $E_n$-monoidal category. 
+In other words, there is an object $\Bar{B} \in  {\rm Mod}_B^{E_n} (\Ch_k^{\otimes k})$ which gets sent to $B$ under the forgetful functor ${\rm Mod}_B^{E_n} (\Ch_k^{\otimes k}) \to \Ch_k^{\otimes_k}$.
+
+Given a map of $E_n$-algebras $f : A \to B$ there is an $E_n$-monoidal functor of $E_n$-module categories 
+\[
+f^* :  {\rm Mod}_B^{E_n} (\Ch_k^{\otimes_k}) \to  {\rm Mod}_A^{E_n} (\Ch_k^{\otimes_k}) .
+\]
+In particular, for $A = \UU_n \fg$, we see that the $E_n$-algebra $B$ defines an $E_n$-algebra object $f^*\Bar{B} \in {\rm Mod}_{\UU_n \fg}^{E_n} (\Ch_k^{\otimes k})$. 
+Again, the image of this object under the forgetful functor to $\Ch_k^{\otimes_k}$ is $B$.
+
+Now, for any $E_n$-algebra the factorization homology along the $(n-1)$-sphere $\int_{S^{n-1}} A$ is an $E_1$-algebra.
+By Proposition 3.33 of \cite{FrancisHH} (see also Example 5.5.4.16 of \cite{LurieHA}), there is an equivalence of $\infty$-categories ${\rm Mod}^{E_n}_A (\Ch_k^{\otimes_k}) \simeq {\rm LMod}_{\int_{S^{n-1}} A} (\Ch_k^{\otimes_k})$.
+For $A = \UU_n \fg$, the factorization homology along the $(n-1)$-sphere is $\int_{S^{n-1} A} \simeq \UU_1 \left(\fg[\epsilon] \right)$, where $\epsilon$ is a formal parameter of cohomological degree $n-1$.
+It follows that there is an equivalence of $\infty$-categories 
+\[
+{\rm Mod}_{\UU_n \fg}^{E_n} (\Ch_k^{\otimes_k}) \simeq {\rm LMod}_{\UU_1(\fg[\epsilon])} (\Ch_k^{\otimes_k}) = {\rm Mod}_{\fg[\epsilon]} (\Ch_k^{\otimes_k}) .
+\]
+\brian{The RHS has a symmetric monoidal structure with $\otimes_k$. 
+This does not agree with the tensor product on the LHS, but we hope there is a functor $\otimes_{\UU_n \fg} \to \otimes_k$.}
+
+Finally, restriction along the map of Lie algebras $i : \fg \hookrightarrow \fg[\epsilon]$ defines monoidal functor $i^* :  {\rm Mod}_{\fg[\epsilon]} (\Ch_k^{\otimes_k})  \to  {\rm Mod}_{\fg} (\Ch_k^{\otimes_k})$.
+The desired $E_n$-algebra object $B_f$ is $i^* f^* \Bar{B}$.
 \end{proof}

### 2020-08-27 draft.tex
bulk

@@
 \label{thm: centralizer}
-Let $\UU_n \fg$ be the enveloping $E_n$ algebra of a dg Lie algebra $\fg$ and let $f: \UU_n \fg \to B$ a map of augmented $E_n$ algebras.
+Let $\UU_n \fg$ be the enveloping $E_n$ algebra of a dg Lie algebra $\fg$ and let 
+\[
+f: \UU_n \fg \to B
+\]
+be a map of augmented $E_n$ algebras.
 Then
@@
 By Proposition 3.33 of \cite{FrancisHH} (see also Example 5.5.4.16 of \cite{LurieHA}), there is an equivalence of $\infty$-categories ${\rm Mod}^{E_n}_A (\Ch_k^{\otimes_k}) \simeq {\rm LMod}_{\int_{S^{n-1}} A} (\Ch_k^{\otimes_k})$.
-For $A = \UU_n \fg$, the factorization homology along the $(n-1)$-sphere is $\int_{S^{n-1} A} \simeq \UU_1 \left(\fg[\epsilon] \right)$, where $\epsilon$ is a formal parameter of cohomological degree $n-1$.
+For $A = \UU_n \fg$, the factorization homology along the $(n-1)$-sphere is $\int_{S^{n-1}} A \simeq \UU_1 \left(\fg[\epsilon] \right)$, where $\epsilon$ is a formal parameter of cohomological degree $n-1$.
 It follows that there is an equivalence of $\infty$-categories 
@@
 
-First note that compactly supported form embedds in all forms, therefore we can apply 
+First note that compactly supported form embeds in all forms, therefore we can apply 
 any element of $\cliels\big(\fg \otimes \Omega^* (-), B(-)\big)$ 
@@
 
-\brian{do you like this example?} \greg{I do !}
-\begin{eg}\label{eg: TT}
+\subsection{Koszul duality}
+\label{sec: Koszul}
+
+Consider the trivial $E_n$-algebra $k$ and suppose $\varepsilon : \UU_n \fg \to k$ is the natural augmentation. 
+Then, ${\frak Z}_n (\varepsilon)$ is the $E_n$-{\em Koszul dual} of the $E_n$-algebra $\UU_n \fg$. 
+Our results provide a model for this $E_n$-algebra as a locally constant factorization algebra on $\RR^n$ which assigns to an open set $U \subset \RR^n$ the cochain complex
+\[
+\clie \left(\fg \otimes \Omega(U) \right) .
+\]
+
+\subsection{Universal bulk TFT}
+\label{sec: TFT}
+
+Generally speaking, the local observables of a topological field theory on a manifold $M$ form a locally constant factorization algebra on $M$.
+
+Let $\fg$ be a dg Lie algebra and consider the $E_n$ algebra $\UU_n \fg$. 
+We have shown that a model for the $E_n$-center ${\frak Z}_n (\UU_n \fg) = {\frak Z}_n ({\rm id}_{\UU_n \fg})$ is the $n$-dimensional locally constant factorization algebra 
+\[
+\clie \left( \fg \otimes \Omega \; , \; \clieu (\fg \otimes \Omega_c) \right)  .
+\]
+
+Let us place this locally constant factorization algebra on the $n$-manifold $M$.
+This factorization algebra is equivalent to the pushforward of a factorization algebra $\cF_{\rm bulk}$ on the $(n+1)$-dimensional manifold $M \times \RR$ along the projection $\pi : M \times \RR \to M$.
+We proceed to construct this factorization algebra.
+
+For an open set $V \subset M \times I$ let $\cF^{\rm cl}_{\rm bulk} (V)$ be the cochain complex 
+\[
+\cF^{\rm cl}_{\rm bulk} (V) = \clie \bigg(\fg \otimes \Omega (V) \; , \; \Sym \left(\fg \otimes \Omega_c(V) [2] \right) \bigg) .
+\]
+The assignment $V \mapsto \cF^{\rm cl}_{\rm bulk}(V)$ defines a locally constant factorization algebra $\cF^{\rm cl}_{\rm bulk}$ on $M \times \RR$.
+
+The factorization algebra $\pi_* \cF^{\rm cl}_{\rm bulk}$ on $M$ is quasi-isomorphic to a certain limit, or ``deqauntization", of the $E_n$-center of $\UU_n \fg$. 
+To exhibit this quasi-isomorphism, we introduce the following cochain maps.
+For an open set $U \subset M$ let
+\[
+\int_\RR : \Omega_c(U \times \RR) \to \Omega_c (U) [1] 
+\] 
+be the map which integrates a compactly supported form on $U \times \RR$ along $\RR$. 
+This map is a quasi-isomorphism for any $U $ and admits the following explicit retract. 
+Let $\phi$ be a fixed compactly supported function on $\RR$ of mass $1$ and define
+\[
+r_\phi : \Omega_c(U) [1] \to \Omega_c (U \times \RR)
+\]
+by $r_\phi (\alpha) = \alpha \wedge \phi \, \d t$.
+
+The ``dequantization" of the $E_n$-center is defined using the following filtration of ${\frak Z}_n(\UU_n \fg)$.
+We for any Lie algebra $\fh$, let $\clieu_{\leq k} (\fh)$ be the subcomplex of Chevalley--Eilenberg chains which is $\Sym^{\leq k} (\fh[1])$ as an underlying graded vector space. 
+The increasing filtration for the $E_n$-center is defined by
+\[
+F^k {\frak Z}_n(\UU_n \fg) = \clie \bigg(\fg \otimes \Omega \; , \; \clieu_{\leq k} (\fg \otimes \Omega_c) \bigg) .
+\]
+This is a filtration of factorization algebras on $M$. 
+The associated graded factorization algebra is
+\[
+{\rm Gr} \;  {\frak Z}_n(\UU_n \fg)  = \clie \bigg(\fg \otimes \Omega \; , \; \Sym \left(\fg \otimes \Omega_c [1] \right) \bigg) .
+\]
+Notice this is similar to the model $E_n$-center except we have turned off the Chevalley--Eilenberg differential on chains.
+
+\begin{lmm}
+Integration along $\RR$ determines a quasi-isomorphism of factorization algebras on $M$:
+\[
+\int_\RR : \pi_* \cF^{\rm cl}_{\rm bulk} \xto{\simeq} {\rm Gr} \;  {\frak Z}_n(\UU_n \fg) .
+\]
+In fact, this is a deformation retraction with retract given by $r_\phi$. 
+\end{lmm}
+
+\brian{Maybe you can finesse this last part better than me.}
+
+%\begin{lmm}
+%Consider the locally constant factorization algebra $\cF_{\rm bulk}$ on $M \times \RR$ which assigns to an open set $U \subset M \times \RR$
+%\[
+%\cF_{\rm bulk} = \clie \left(\fg \otimes \Omega (U) \; , \; \clieu (\fg \otimes \Omega_c (U)[1]) \right) .
+%\]
+%Then, 
+%\end{lmm}
+%
+%\begin{proof}
+%For $V \subset M$, the integration of compactly supported de Rham forms along $\RR$ 
+%\[
+%\fg \otimes \Omega_c (\pi^{-1} (V)) = \fg \otimes \Omega_c (V \times \RR) \xto{\int_{\RR}} \fg \otimes \Omega_c (V) [-1] .
+%\]
+%is a quasi-isomorphism. 
+%
+%\end{proof}
+
+\subsection{$E_n$-calculus}
+\label{sec: TT}
+
+\brian{HKR}
+
 Consider the case $n=1$ and $B = U \fg$ where $f$ is simply the identity map. 
@@
 We could exhibit Theorem 2.7.1 explicitly in this case for the $E_n$ case with enveloping algebras.}
-\end{eg}
 

### 2020-08-30 draft.tex
rearrangments before cleaning up strictified stuff

@@
 
+\owen{We should collect here a list of notations, such as}
+
+Let $\Ch_k^{\otimes_k}$ be the symmetric monoidal stable $\infty$-category arising from cochain complexes of vector spaces over a characteristic zero field $k$.
+Let ${\tt Ch}_k^{\otimes_k}$ denote the symmetric monoidal stable model category of cochain complexes of vector spaces over a characteristic zero field $k$ ETC.
+
 \section{Our main results}
@@
 \begin{itemize}
-\item $f$ equips $B$ with the structure of an $E_n$ algebra in $\fg$-modules and
+\item $f$ lets us lift $B$ to an $E_n$ algebra $B_f$ in $\fg$-modules and
 \item the centralizer ${\frak Z}_{E_n}(f)$ is an $E_n$-algebra modeled by the Chevalley-Eilenberg 
-cochains $\clies(\fg, B)$ equipped with the convolution $E_n$-product.
+cochains $\clies(\fg, B_f)$ equipped with the convolution $E_n$-product.
 \end{itemize}
@@
 This would be worth explaining because we can then use a much simpler strictification of $f$.}
-
-\subsection{Maps out of enveloping $E_n$ algebras}
-
-\owen{I might move the discussion of $E_n$-modules from near proposition~\ref{P:ModentoModSn} to here. 
-We can then sketch here the argument you explained about $E_n$-monoidal products to show that $B$ lifts to an $E_n$ algebra $B_f$ in $\fg$-modules.}
-
-These results can be marshaled to prove the following.
-
-\begin{prp}
-Let $\Ch_k^{\otimes_k}$ be the symmetric monoidal $\infty$-category arising from cochain complexes of vector spaces over a characteristic zero field $k$.
-Let $\fg$ be a Lie algebra in $\Ch_k^{\otimes_k}$, i.e., a dg Lie algebra, 
-and let $B$ be an $E_n$ algebra in $\Ch_k^{\otimes_k}$.
-Then given a map of $E_n$ algebras $f: \UU_n \fg \to B$, 
-there exists a lift of $B$ to an $E_n$ algebra $B_f$ in $\Mod_\fg(\Ch_k^{\otimes_k})^{\otimes_k}$, the symmetric monoidal $\infty$-category of $\fg$-modules.
-\end{prp}
-
-That is, the forgetful functor $\Mod_\fg(\Ch_k^{\otimes_k})^{\otimes_k} \to \Ch_k^{\otimes_k}$ sends $B_f$ to~$B$.
-
-\begin{proof}
-By Corollary 3.4.4.6 of \cite{LurieHA}, any $E_n$ algebra $B$ defines an $E_n$-monoidal category ${\rm Mod}_B^{E_n} (\Ch_k^{\otimes k})$ of $E_n$-$B$-modules. 
-Furthermore, by Corollary 3.4.1.7 \cite{LurieHA} (see also Example 3.4.4.7 of the same reference) $B$ can be viewed as an $E_n$-algebra in this $E_n$-monoidal category. 
-In other words, there is an object $\Bar{B} \in  {\rm Mod}_B^{E_n} (\Ch_k^{\otimes k})$ which gets sent to $B$ under the forgetful functor ${\rm Mod}_B^{E_n} (\Ch_k^{\otimes k}) \to \Ch_k^{\otimes_k}$.
-
-Given a map of $E_n$-algebras $f : A \to B$ there is an $E_n$-monoidal functor of $E_n$-module categories 
-\[
-f^* :  {\rm Mod}_B^{E_n} (\Ch_k^{\otimes_k}) \to  {\rm Mod}_A^{E_n} (\Ch_k^{\otimes_k}) .
-\]
-In particular, for $A = \UU_n \fg$, we see that the $E_n$-algebra $B$ defines an $E_n$-algebra object $f^*\Bar{B} \in {\rm Mod}_{\UU_n \fg}^{E_n} (\Ch_k^{\otimes k})$. 
-Again, the image of this object under the forgetful functor to $\Ch_k^{\otimes_k}$ is $B$.
-
-Now, for any $E_n$-algebra the factorization homology along the $(n-1)$-sphere $\int_{S^{n-1}} A$ is an $E_1$-algebra.
-By Proposition 3.33 of \cite{FrancisHH} (see also Example 5.5.4.16 of \cite{LurieHA}), there is an equivalence of $\infty$-categories ${\rm Mod}^{E_n}_A (\Ch_k^{\otimes_k}) \simeq {\rm LMod}_{\int_{S^{n-1}} A} (\Ch_k^{\otimes_k})$.
-For $A = \UU_n \fg$, the factorization homology along the $(n-1)$-sphere is $\int_{S^{n-1}} A \simeq \UU_1 \left(\fg[\epsilon] \right)$, where $\epsilon$ is a formal parameter of cohomological degree $n-1$.
-It follows that there is an equivalence of $\infty$-categories 
-\[
-{\rm Mod}_{\UU_n \fg}^{E_n} (\Ch_k^{\otimes_k}) \simeq {\rm LMod}_{\UU_1(\fg[\epsilon])} (\Ch_k^{\otimes_k}) = {\rm Mod}_{\fg[\epsilon]} (\Ch_k^{\otimes_k}) .
-\]
-\brian{The RHS has a symmetric monoidal structure with $\otimes_k$. 
-This does not agree with the tensor product on the LHS, but we hope there is a functor $\otimes_{\UU_n \fg} \to \otimes_k$.}
-
-Finally, restriction along the map of Lie algebras $i : \fg \hookrightarrow \fg[\epsilon]$ defines monoidal functor $i^* :  {\rm Mod}_{\fg[\epsilon]} (\Ch_k^{\otimes_k})  \to  {\rm Mod}_{\fg} (\Ch_k^{\otimes_k})$.
-The desired $E_n$-algebra object $B_f$ is $i^* f^* \Bar{B}$.
-\end{proof}
-
-By the strictification results, $B_f$ admits a model ${\tt B}_f$ as a strict prefactorization algebra with values in the stable symmetric monoidal \owen{other adjectives} model category $\Alg_\Lie(\Ch_k^{\rm dg})$.
-As the forgetful functor $\Alg_\Lie(\Ch_k^{\rm dg}) \to \Alg_\Lie(\Ch_k^{\rm dg})$ is \owen{more adjectives},
-we obtain an underlying strict prefactorization algebra ${\tt B}$ with values in cochain complexes.
-Moreover, there is a canonical map $\cliel(\fg[-n]) \to {\tt B}$ of strict prefactorization algebras that models $f$, as desired.
-
-\owen{I'd love to say we can produce a map from our favorite model of the envelope, but we may not need it.}
 
@@
 
-\section{Strictifying the map $f: \UU_n \fg \to B$}
-
-\owen{If our new strategy works, then we can get rid of this section.}
-
-As a first step, we analyze the strictification of the map $f: \UU_n \fg \to B$ and show how it lets us view $B$ as an $E_n$ algebra in~$\Ch(\Rep(\fg))$.
-
-By using the small model \owen{see my comment \ref{note on little model}}, we can strictify to obtain a map
-\[
-{\tt f}: \cliel(\fg[-n]) \to {\tt B}.
-\]
-
-\owen{And now I'm really confused.}
-
-\owen{I'm not wild about Greg's phrasing below. Also, I'd prefer to move the explicit formulas later, when we've shifted our setting to strict prefactorization algebras.}
+\section{Lifting $B$ to an $E_n$ algebra $B_f$ in $\fg$-modules}
+
+A technical result is the key step.
+
+\def\obl{{\rm obl}}
+
+\begin{prp}
+\label{prp: def of obl}
+For $\fg$ a dg Lie algebra in $\Ch_k^{\otimes_k}$, i.e., a dg Lie algebra, 
+there is a forgetful functor $\obl: \Mod^{E_n}_{\UU_n \fg} \to \LMod_{U\fg}$ that is lax $E_n$-monoidal.
+\end{prp}
+
+\owen{I don't know if we need to include the adjective ``lax'' here, or if it's implicit in the usual discussions these days.}
+
+Concretely, we mean there is a natural morphism
+\[
+\obl(M) \otimes_k \obl \to \obl(M \otimes_{\UU_n \fg} N) 
+\]
+as left modules over $U\fg$, i.e., as $\fg$-representations.
+
+As a consequence, we obtain the following.
+
+\begin{cor}
+There is a functor 
+\[
+\Alg_{E_n}(\obl): \Alg_{E_n}({\Mod^{E_n}_{\UU_n \fg}}) \to \Alg_{E_n}(\LMod_{U\fg}).
+\]
+\end{cor}
+
+These results can be marshaled to prove the following.
+
+\begin{prp}
+Let $\fg$ be a Lie algebra in $\Ch_k^{\otimes_k}$, 
+and let $B$ be an $E_n$ algebra in $\Ch_k^{\otimes_k}$.
+Given a map of $E_n$ algebras $f: \UU_n \fg \to B$, 
+there exists a lift of $B$ to an $E_n$ algebra $B_f$ in $\Mod_\fg(\Ch_k^{\otimes_k})^{\otimes_k}$, the symmetric monoidal $\infty$-category of $\fg$-modules.
+\end{prp}
+
+That is, the forgetful functor $\Mod_\fg(\Ch_k^{\otimes_k})^{\otimes_k} \to \Ch_k^{\otimes_k}$ sends $B_f$ to~$B$.
+
+\begin{proof}
+By Corollary 3.4.4.6 of \cite{LurieHA}, any $E_n$ algebra $B$ defines an $E_n$-monoidal category ${\rm Mod}_B^{E_n} (\Ch_k^{\otimes k})$ of $E_n$-$B$-modules with monoidal structure $\otimes_B$. 
+Furthermore, by Corollary 3.4.1.7 \cite{LurieHA} $B$ can be viewed as an $E_n$-algebra in this $E_n$-monoidal category. 
+(See also Example 3.4.4.7 of the same reference.)
+In other words, there is an object $\Hat{B} \in  {\rm Mod}_B^{E_n} (\Ch_k^{\otimes k})$ sent to $B$ under the forgetful functor ${\rm Mod}_B^{E_n} (\Ch_k^{\otimes k}) \to \Ch_k^{\otimes_k}$.
+
+Given a map of $E_n$-algebras $f : A \to B$, 
+the forgetful functor of $E_n$-module categories 
+\[
+f^* :  {\rm Mod}_B^{E_n} (\Ch_k^{\otimes_k}) \to  {\rm Mod}_A^{E_n} (\Ch_k^{\otimes_k}) .
+\]
+admits a natural refinement to an $E_n$-monoidal functor.
+\owen{Any place to cite?}
+In particular, for $A = \UU_n \fg$, there is an $E_n$-algebra object $f^*\Hat{B} \in {\rm Mod}_{\UU_n \fg}^{E_n} (\Ch_k^{\otimes k})$, and it forgets to $B$ under the forgetful functor to $\Ch_k^{\otimes_k}$, by construction.
+
+Applying the $E_n$-monoidal functor $\obl$, we obtain an $E_n$ algebra $\obl(f^*\Hat{B})$ in $\Mod_\fg(\Ch_k^{\otimes_k})^{\otimes_k}$.
+Again, by construction, it forgets to $B$.
+We denote $\obl(f^*\Hat{B})$ by~$B_f$.
+\end{proof}
 
 \begin{rmk}
-It follows from theorem~\ref{T:UnofLie} that for any $E_n$-algebra $B$, 
-the underlying complex of the $L_\infty$-algebra $\oblv_n(B)$ is naturally quasi-isomorphic to $\Sigma^{n-1}B = B[n-1]$. 
-Henceforth in this paper, we will simply use the notation $B[n-1]$ for $\oblv_n(B)$, 
-that is tacitly assume we $B[n-1]$ is endowed with the $L_\infty$structure induced by its $E_n$ algebra structure.
+By the strictification results, $B_f$ admits a model ${\tt B}_f$ as a strict prefactorization algebra with values in the stable symmetric monoidal \owen{other adjectives} model category $\Alg_\Lie(\Ch_k^{\rm dg})$.
+As the forgetful functor $\Alg_\Lie({\tt Ch}_k) \to \Alg_\Lie({\tt Ch}_k)$ is \owen{more adjectives},
+we obtain an underlying strict prefactorization algebra ${\tt B}$ with values in cochain complexes.
+Moreover, there is a canonical map $\cliel(\fg[-n]) \to {\tt B}$ of strict prefactorization algebras that models $f$, as desired.
 \end{rmk}
 
-Let  $f:\UU_n \fg \to B$ be an $E_n$-algebra map. Then the adjunction 
-\[
-\xymatrix{\Alg_\Lie(\Mod_k) \ar@/^/[r]^{\UU_n} & \ar[l]^{\oblv_n}  \Alg_{E_n}(\Mod_k)}
-\]
-gives a $L_\infty$-algebra morphism 
-\begin{equation}
- \tilde{f}: \fg \, \longrightarrow \, \oblv(B)\cong B[n-1]
-\end{equation}
-which makes $B[n-1]$ into a $\fg$-module and therefore its shift $B$ inherits a  $\fg$-module structure as well from $f$.
-
-\brian{let's start with a strict representative $B$. 
-So we have an actual locally constant factorization algebra.}
-
-\begin{prp}\label{P:inducedEngModStruct} Let $f:\UU_n \fg \to B$ be an $E_n$-algebra morphism. 
-The induced $\fg$ $L_\infty$-module on $B$ lifts canonically to make  $B$ into an $E_n$-algebra in the category of $\fg$-modules that we denote by $B_f$. 
-\end{prp}
-\begin{proof}
-
+It remains to prove the technical result.
+
+\begin{proof}[Proof of proposition~\ref{prp: def of obl}]
+\owen{We are stuck on this point.}
+We construct the underlying functor of $\infty$-categories $\Mod^{E_n}_{\UU_n \fg} \to \LMod_{U\fg}$ 
+before lifting to a lax $E_n$-monoidal functor.
+
+For any $E_n$-algebra the factorization homology along the $(n-1)$-sphere $\int_{S^{n-1}} A$ is an $E_1$-algebra.
+By Proposition 3.33 of \cite{FrancisHH} (see also Example 5.5.4.16 of \cite{LurieHA}), 
+there is an equivalence of $\infty$-categories ${\rm Mod}^{E_n}_A (\Ch_k^{\otimes_k}) \simeq {\rm LMod}_{\int_{S^{n-1}} A} (\Ch_k^{\otimes_k})$.
+For $A = \UU_n \fg$, the factorization homology along the $(n-1)$-sphere is 
+\[
+\int_{S^{n-1}} A \simeq \UU_1 \left(\fg[\epsilon] \right),
+\] 
+where $\epsilon$ is a formal parameter of cohomological degree $n-1$.
+It follows that there is an equivalence of $\infty$-categories 
+\[
+{\rm Mod}_{\UU_n \fg}^{E_n} (\Ch_k^{\otimes_k}) \simeq {\rm LMod}_{\UU_1(\fg[\epsilon])} (\Ch_k^{\otimes_k}).
+% = {\rm Mod}_{\fg[\epsilon]} (\Ch_k^{\otimes_k}) .
+\]
+Consider now the map of Lie algebras $i : \fg \hookrightarrow \fg[\epsilon]$,
+which induces a forgetful functor $i^* :  {\rm Mod}_{\fg[\epsilon]} (\Ch_k^{\otimes_k})  \to  {\rm Mod}_{\fg} (\Ch_k^{\otimes_k})$. 
+The composite 
+\[
+{\rm Mod}_{\UU_n \fg}^{E_n} (\Ch_k^{\otimes_k}) \simeq {\rm LMod}_{\UU_1(\fg[\epsilon])} (\Ch_k^{\otimes_k}) \xto{i^*}  {\rm LMod}_{U\fg} (\Ch_k^{\otimes_k})
+\]
+is the desired forgetful functor.
+
+\owen{Now we need to explain why it is lax monoidal.}
 \end{proof}
-Proposition~\ref{P:inducedEngModStruct} has an easy realization in the factorization algebra setting.
-Indeed, applying the equivalence of $E_n$-algebras with locally constant factorization algebras (Theorem~\ref{T:En=Fac}), 
-we obtain an induced map of factorization 
-algebras 
-\begin{equation}\label{eq:DefofFonFaclevel}
- \mathbf{f}: \cliels( \fg \otimes \Omega^*_c(-)) \longrightarrow B(-)
-\end{equation}
- where $B(-)$ is the factorization algebra associated to $B$.
- \brian{How about $\ul{B}$ instead?}
-
-\begin{lmm}\label{L:inducedFacgModstruct} The factorization algebra map  $\mathbf{f}$ makes $B(-)$ into an homotopy cosheaf of $L_\infty$-modules over 
- $\fg \otimes \Omega^*_c(-)$.
-\end{lmm}
-\begin{proof}
-
-\end{proof}
-The lemma allows us to define the factorization algebra given on any open $U$ by  the Chevalley-Eilenberg chain complexes
-$ \cliels\big(\fg \otimes \Omega^*_c(U), B(U) \big)$ (with their standard differential)
-of $\fg \otimes \Omega^*_c(U)$ with value on $B(U)$ whose structure maps are given, for any $(U_i)_{i\in I}$ 
-a finite family of pairwise disjoint open subsets of an open $V$, by 
-\begin{multline}\label{eq:transClieFac}
- \bigotimes_{i\in I} \cliels\big(\fg \otimes \Omega^*_c(U_i), B(U_i) \big) \cong Sym\Big(
- \fg\otimes (\bigoplus_{i\in I}  \Omega^*_c(U_i))[-1]  \Big) \otimes \Big( \bigotimes_{i\in I} B(U_i)\Big) \\ 
- \cong Sym\Big(\fg\otimes \Omega_c\big(\coprod U_i\big)[-1] \Big) \otimes \Big( \bigotimes_{i\in I} B(U_i)\Big)  
- \stackrel{\omega^*\otimes \mu_B}\longrightarrow Sym(\fg\otimes \Omega_c(V)[-1] ) \otimes B(V) \\ 
- = \cliels(\fg\otimes \Omega_c(V), B(V))
-\end{multline}
-where $\omega$ is induced by the cosheaf structure of compactly supported form and $\mu_B$ is the factorization algebra structure of $B(-)$.
-
-\smallskip
-
-The (homotopy) sheaf structure of forms also gives us structure maps
-\begin{multline}\label{eq:transClieFacCochain}
- \bigotimes_{i\in I} \clies\big(\fg \otimes \Omega^*(U_i), B(U_i) \big) \longrightarrow
-  \Hom\Big(Sym\big(\fg\otimes (\bigoplus_{i\in I}  \Omega^*(U_i))[-1]\big),  \bigotimes\limits_{i\in I} B(U_i) \Big) \\
- \cong \Hom\Big(Sym\big(\fg\otimes \Omega^*(\coprod U_i)[-1]\big), \bigotimes\limits_{i\in I} B(U_i) \Big) \\
- \stackrel{\rho}\longrightarrow \Hom\Big(Sym\big(\fg\otimes \Omega^*(V)[-1]\big), \bigotimes\limits_{i\in I} B(U_i) \Big) \\
- \stackrel{\mu_B}\longrightarrow 
-  \clies(\fg\otimes \Omega (V), B(V))
-\end{multline}
-where $\rho$ is given by the restriction of forms onto a subspace.
-
-\begin{lmm}\label{L:ClieFacDef} For any (resp. locally constant) factorization algebra $B(-)$ and factorization algebra map $\mathbf{f}:\UU_n(\fg) \to B(-)$, 
- the structure maps~\eqref{eq:transClieFac} makes $ \cliels\big(\fg \otimes \Omega^*_c(-), B(-) \big)$ a (resp. locally constant) factorization algebra.
- Similarly, the structure maps~\eqref{eq:transClieFacCochain} makes 
- $ \clies\big(\fg \otimes \Omega^*(-), B(-) \big)$ a (resp. locally constant) factorization algebra.
-\end{lmm}
-\begin{dfn}\label{dfn:CEofFact}
-We {call   $\cliels\big(\fg \otimes \Omega^*_c(-), B(-) \big)$ the Chevalley-Eilenberg chain factorization algebra of $\fg$ with value in $B(-)$} 
-and $\clies\big(\fg \otimes \Omega^*(-), B(-) \big)$ the Chevalley-Eilenberg cochain factorization algebra.
-\end{dfn}
-\begin{proof}
-
-\end{proof}
-
-A special but very interesting case is of course when $B$ is itself an enveloping algebra. 
-\begin{cor}
- Let $\fg$, $\fh$ be dg-Lie algebras and $f:\fg\to \fh$ be a dg-Lie algebra morphism. 
- Then the induced factorization algebra map $\mathbf{\UU_n f}:  \cliels( \fg \otimes \Omega^*_c(-)) \longrightarrow  \cliels( \fh \otimes \Omega^*_c(-)) $
- is the standard map $\cliels(f)$ induced by $f$ and the action of $\fg  \otimes \Omega^*_c(-)$ is obtained from the $\fg$-action on $\fh$ by Leibniz rule.
-\end{cor}
-\begin{rmk}\greg{Extends to $L_\infty$ case in a sentence or too}
-\end{rmk}
+
+%\section{Strictifying the map $f: \UU_n \fg \to B$}
+%
+%
+%\owen{If our new strategy works, then we can get rid of this section.}
+%
+%As a first step, we analyze the strictification of the map $f: \UU_n \fg \to B$ and show how it lets us view $B$ as an $E_n$ algebra in~$\Ch(\Rep(\fg))$.
+%
+%By using the small model \owen{see my comment \ref{note on little model}}, we can strictify to obtain a map
+%\[
+%{\tt f}: \cliel(\fg[-n]) \to {\tt B}.
+%\]
+%
+%\owen{And now I'm really confused.}
+%
+%\owen{I'm not wild about Greg's phrasing below. Also, I'd prefer to move the explicit formulas later, when we've shifted our setting to strict prefactorization algebras.}
+%
+%
+%\begin{rmk}
+%It follows from theorem~\ref{T:UnofLie} that for any $E_n$-algebra $B$, 
+%the underlying complex of the $L_\infty$-algebra $\oblv_n(B)$ is naturally quasi-isomorphic to $\Sigma^{n-1}B = B[n-1]$. 
+%Henceforth in this paper, we will simply use the notation $B[n-1]$ for $\oblv_n(B)$, 
+%that is tacitly assume we $B[n-1]$ is endowed with the $L_\infty$structure induced by its $E_n$ algebra structure.
+%\end{rmk}
+%
+%Let  $f:\UU_n \fg \to B$ be an $E_n$-algebra map. Then the adjunction 
+%\[
+%\xymatrix{\Alg_\Lie(\Mod_k) \ar@/^/[r]^{\UU_n} & \ar[l]^{\oblv_n}  \Alg_{E_n}(\Mod_k)}
+%\]
+%gives a $L_\infty$-algebra morphism 
+%\begin{equation}
+% \tilde{f}: \fg \, \longrightarrow \, \oblv(B)\cong B[n-1]
+%\end{equation}
+%which makes $B[n-1]$ into a $\fg$-module and therefore its shift $B$ inherits a  $\fg$-module structure as well from $f$.
+%
+%\brian{let's start with a strict representative $B$. 
+%So we have an actual locally constant factorization algebra.}
+%
+%\begin{prp}\label{P:inducedEngModStruct} Let $f:\UU_n \fg \to B$ be an $E_n$-algebra morphism. 
+%The induced $\fg$ $L_\infty$-module on $B$ lifts canonically to make  $B$ into an $E_n$-algebra in the category of $\fg$-modules that we denote by $B_f$. 
+%\end{prp}
+%\begin{proof}
+% 
+%\end{proof}
+%Proposition~\ref{P:inducedEngModStruct} has an easy realization in the factorization algebra setting.
+%Indeed, applying the equivalence of $E_n$-algebras with locally constant factorization algebras (Theorem~\ref{T:En=Fac}), 
+%we obtain an induced map of factorization 
+%algebras 
+%\begin{equation}\label{eq:DefofFonFaclevel}
+% \mathbf{f}: \cliels( \fg \otimes \Omega^*_c(-)) \longrightarrow B(-)
+%\end{equation}
+% where $B(-)$ is the factorization algebra associated to $B$.
+% \brian{How about $\ul{B}$ instead?}
+% 
+%\begin{lmm}\label{L:inducedFacgModstruct} The factorization algebra map  $\mathbf{f}$ makes $B(-)$ into an homotopy cosheaf of $L_\infty$-modules over 
+% $\fg \otimes \Omega^*_c(-)$.
+%\end{lmm}
+%\begin{proof}
+% 
+%\end{proof}
+%The lemma allows us to define the factorization algebra given on any open $U$ by  the Chevalley-Eilenberg chain complexes
+%$ \cliels\big(\fg \otimes \Omega^*_c(U), B(U) \big)$ (with their standard differential)
+%of $\fg \otimes \Omega^*_c(U)$ with value on $B(U)$ whose structure maps are given, for any $(U_i)_{i\in I}$ 
+%a finite family of pairwise disjoint open subsets of an open $V$, by 
+%\begin{multline}\label{eq:transClieFac}
+% \bigotimes_{i\in I} \cliels\big(\fg \otimes \Omega^*_c(U_i), B(U_i) \big) \cong Sym\Big(
+% \fg\otimes (\bigoplus_{i\in I}  \Omega^*_c(U_i))[-1]  \Big) \otimes \Big( \bigotimes_{i\in I} B(U_i)\Big) \\ 
+% \cong Sym\Big(\fg\otimes \Omega_c\big(\coprod U_i\big)[-1] \Big) \otimes \Big( \bigotimes_{i\in I} B(U_i)\Big)  
+% \stackrel{\omega^*\otimes \mu_B}\longrightarrow Sym(\fg\otimes \Omega_c(V)[-1] ) \otimes B(V) \\ 
+% = \cliels(\fg\otimes \Omega_c(V), B(V))
+%\end{multline}
+%where $\omega$ is induced by the cosheaf structure of compactly supported form and $\mu_B$ is the factorization algebra structure of $B(-)$.
+%
+%\smallskip
+%
+%The (homotopy) sheaf structure of forms also gives us structure maps
+%\begin{multline}\label{eq:transClieFacCochain}
+% \bigotimes_{i\in I} \clies\big(\fg \otimes \Omega^*(U_i), B(U_i) \big) \longrightarrow
+%  \Hom\Big(Sym\big(\fg\otimes (\bigoplus_{i\in I}  \Omega^*(U_i))[-1]\big),  \bigotimes\limits_{i\in I} B(U_i) \Big) \\
+% \cong \Hom\Big(Sym\big(\fg\otimes \Omega^*(\coprod U_i)[-1]\big), \bigotimes\limits_{i\in I} B(U_i) \Big) \\
+% \stackrel{\rho}\longrightarrow \Hom\Big(Sym\big(\fg\otimes \Omega^*(V)[-1]\big), \bigotimes\limits_{i\in I} B(U_i) \Big) \\
+% \stackrel{\mu_B}\longrightarrow 
+%  \clies(\fg\otimes \Omega (V), B(V))
+%\end{multline}
+%where $\rho$ is given by the restriction of forms onto a subspace. 
+%
+%\begin{lmm}\label{L:ClieFacDef} For any (resp. locally constant) factorization algebra $B(-)$ and factorization algebra map $\mathbf{f}:\UU_n(\fg) \to B(-)$, 
+% the structure maps~\eqref{eq:transClieFac} makes $ \cliels\big(\fg \otimes \Omega^*_c(-), B(-) \big)$ a (resp. locally constant) factorization algebra.
+% Similarly, the structure maps~\eqref{eq:transClieFacCochain} makes 
+% $ \clies\big(\fg \otimes \Omega^*(-), B(-) \big)$ a (resp. locally constant) factorization algebra.
+%\end{lmm}
+%\begin{dfn}\label{dfn:CEofFact}
+%We {call   $\cliels\big(\fg \otimes \Omega^*_c(-), B(-) \big)$ the Chevalley-Eilenberg chain factorization algebra of $\fg$ with value in $B(-)$} 
+%and $\clies\big(\fg \otimes \Omega^*(-), B(-) \big)$ the Chevalley-Eilenberg cochain factorization algebra.
+%\end{dfn}
+%\begin{proof}
+% 
+%\end{proof}
+%
+%
+%A special but very interesting case is of course when $B$ is itself an enveloping algebra. 
+%\begin{cor}
+% Let $\fg$, $\fh$ be dg-Lie algebras and $f:\fg\to \fh$ be a dg-Lie algebra morphism. 
+% Then the induced factorization algebra map $\mathbf{\UU_n f}:  \cliels( \fg \otimes \Omega^*_c(-)) \longrightarrow  \cliels( \fh \otimes \Omega^*_c(-)) $
+% is the standard map $\cliels(f)$ induced by $f$ and the action of $\fg  \otimes \Omega^*_c(-)$ is obtained from the $\fg$-action on $\fh$ by Leibniz rule.
+%\end{cor}
+%\begin{rmk}\greg{Extends to $L_\infty$ case in a sentence or too}
+%\end{rmk}
+%
 

### 2020-08-30 draft.tex
finally starting to adjust gregs stuff

@@
 
+\greg{need to add a notation/convention somewhere including that $\Sigma^n$ will be shift functor, convention for grading and so on}
+
 \section{Our main results}
@@
 
-\owen{An approximate version of our main theorem. It's not terrible but I'd like to make the statement more accurate and perhaps punchier.}
+\subsection{The central theorem and its proof strategy}
+
+%\owen{An approximate version of our main theorem. It's not terrible but I'd like to make the statement more accurate and perhaps punchier.}
 
@@
 
-\owen{Here is an outline of the proof strategy, with ingredients indicated:}
+\def\Disk{{\rm Disk}}
 
@@
 \item Lurie and Francis give a characterization of the centralizer ${\frak Z}_{E_n}(f)$ of any $E_n$ algebra map $f: A \to B$ as the ``internal hom'' in left $\int_{S^{n-1}}A$-modules from $A$ to $B_f$, where $B_f$ denotes $B$ viewed as a left module via the map~$f$.
-\item Their work shows, in fact, that $f$ equips $B$ with the structure of an $E_n$ algebra in $\fg$-representations,
-which we also denote $B_f$, as it relies on related arguments. \owen{Let's hope we can justify this!}
-\item Knudsen verifies that we can model the enveloping $E_n$ algebra by a strict prefactorization algebra ${\tt U}_n \fg = \cliel(\Omega_c \otimes \fg)$ on $\RR^n$, which is weakly locally constant.
+\item Lurie \cite{LurieHA} explains why the $\infty$-category of $E_n$ algebras is equivalent to the homotopy-coherent version of locally constant prefactorization algebras on $\RR^n$.  
+In fact, he simplifies the situation a bit more. 
+Let $\Disk_n^\sqcup$ denote the colored operad whose colors are balls in $\RR^n$ and whose spaces of operations are either empty or a point, depending on whether the input balls are pairwise disjoint and subsets of the output ball.
+One can work with locally constant, homotopy-coherent algebras over $\Disk_n^\sqcup$.
+\item In particular, Knudsen verifies that we can model the enveloping $E_n$ algebra by a strict $\Disk_n$-algebra $\cliels(\fg[-n])$ that is strictly locally constant.
 \item In combination, the centralizer is characterized up to quasi-isomorphism, 
@@
 \begin{enumerate}
-\item First, we transfer the question to the setting of strict prefactorization algebras on $\RR^n$ that are weakly locally constant.
-Lurie \cite{LurieHA} explains why we can work with the homotopy coherent version of prefactorization algebras, and then strictification theorems from the model category literature on operads say we can work with strict prefactorization algebras.
-\item  In particular, given our $E_n$ algebra $B_f$ in $\fg$-modules,  model it by a strict prefactorization algebra ${\tt B}_f$ with values in a nice model category $\Mod_\fg(\Ch_k)$ of dg $\fg$-representations.
+\item By modest extensions of the works cited above, we show that  $f$ equips $B$ with the structure of an $E_n$ algebra in $\fg$-representations, which we also denote $B_f$.
+\owen{Let's hope we can justify this!}
+\item Next, we transfer the question to the setting of {\em strict} $\Disk_n$-algebras that are weakly locally constant. 
+Strictification theorems from the model category literature on operads say we can replace homotopy-coherent $\Disk_n$-algebras with strict ones. 
+\item  In particular, given our $E_n$ algebra $B_f$ in $\fg$-modules, model it by a strict $\Disk_n$-algebra ${\tt B}_f$ with values in a nice model category $\Mod_\fg(\Ch_k)$ of dg $\fg$-representations.
 The forgetful functor $\Mod_\fg(\Ch_k) \to \Ch_k$ lets us produce a strict prefactorization algebra ${\tt B}$ that models~$B$.
-\item By construction, the action of $\fg$ on ${\tt B}_f$ determines a map ${\tt f}:  {\tt U}_n \fg \to {\tt B}$ of strict prefactorization algebras.
-\owen{I'm not sure this is true ... but let's be optimistic.}
-\item We then construct an explicit strict prefactorization algebra $\clies(\Omega \otimes \fg, {\tt B}_f)$ as a kind of ``convolution algebra.'' 
+\item By construction, the action of $\fg$ on ${\tt B}_f$ determines a map ${\tt f}:  {\tt U}_n \fg \to {\tt B}$ of strict $\Disk_n$-algebras that models the original map~$f$.
+\item We then construct an explicit strict $\Disk_n$-algebra $\clies(\Omega \otimes \fg, {\tt B}_f)$ as a kind of ``convolution algebra.'' 
 \item We show this object fits canonically into a centralizer diagram: there is a map
@@
 such that precomposing with the map $1 \otimes \id_{{\tt U}_n \fg}$ is the map~${\tt f}$.
-Fitting into such a diagram guarantees a canonical map $\clies(\Omega \otimes \fg, {\tt B}_f) \to {\tt Z}_f$ as strict prefactorization algebras. 
-\item We then verify that this map is a quasi-isomorphism on disks. 
+Fitting into such a diagram guarantees a canonical map $\clies(\Omega \otimes \fg, {\tt B}_f) \to {\tt Z}_f$ as strict $\Disk_n$-algebras. 
+\item We then verify that this map is a quasi-isomorphism on disks, by the Lurie-Francis result mentioned above. 
 \end{enumerate}
 Hence it induces a weak equivalence of the associated $E_n$ algebras.
+
+\subsection{Consequences of the central result}
 
@@
 \end{cor}
-\greg{I will add stuff and rewrite that latter, hopefully to explain ``how'' to see the $E_{n+1}$-structure}
-\owen{Add remark for ", which by Dunn's additivity theorem has in fact a natural $E_{n+1}$ algebra structure."}
-
-\greg{shall relate this to $P_n$-center of $\fg$. that shall also (but I have to think about the proof more), 
+
+\owen{Add remark that by Dunn's additivity theorem, the center has a natural $E_{n+1}$ algebra structure.}
+\greg{I will add stuff and rewrite that later, hopefully to explain ``how'' to see the $E_{n+1}$-structure}
+
+\greg{We could relate this to $P_n$-center of $\fg$. That shall also (but I have to think about the proof more), 
 at least up to formality gives the $P_{n+1}$-structure on it. }
+
 This result generalizes the fact that $\Hoch^*(U\fg,U\fg) \simeq \clies(\fg, U\fg)$, 
@@
 
-\greg{somewhere recall that $\UU_n$ and center i that case are unoriented $E_n$-algebras and defined factorization algebras over any manifold which came from the formula}
 Having an explicit presentation for the centralizer of a map of $E_n$ algebras leads to a calculation of factorization homology.
@@
 
-\begin{rmk}
-The preceding results are known to experts we spoke to, including John Francis and Ben Knudsen. 
-Nevertheless, we record these results to document in the literature and for future use in mathematical physics,
-where such constructions already appear but lack proofs of their universal properties.
-\end{rmk}
-
-\owen{Below is an orphaned set of results. Perhaps we prove it, or perhaps we just reserve it for future projects.}
-
-Our novel contribution in this paper is the following large $N$ result. Let $A$ be a unital algebra over a field $k$ of characteristic zero, 
-and $u_A: \sl_\infty(k) \hookrightarrow \gl_\infty(A)$ be the map of Lie algebras determined by the unit in $A$. 
-The induced map $\UU_nu_A: \UU_n\sl_\infty(k) \to \UU_n\gl_\infty(A)$ makes $\UU_n\gl_\infty(A)$ is an $E_n$ algebra in $\sl_\infty(k)$-modules.
-
-\begin{thm}
-\label{thm: large N}
-The centralizer ${\frak Z}_{E_n}(\UU_nu_A)$ of the map $\UU_nu_A$ is the $E_n$ algebra obtained by forgetting the dg commutative algebra
-\[
-\clies(\sl_\infty(k)) \otimes \Sym(\Cyc_*(A)[1-n])
-\]
-down to an $E_n$ algebra.
-
-When $k$ is $\RR$ or $\CC$, this centralizer is modeled by the locally constant factorization algebra that assigns
-\[
-\clies(\sl_\infty(\Omega^*(U)))\otimes \Sym(\Cyc_*(A \otimes \Omega^*_c(U))[1])
-\]
-to each open set $U \subset \RR^n$.
-\end{thm}
-\greg{Shall we keep these examples which uses/but are the easy part/ of LQT theorem ?}
-\owen{We should write explicitly what happens in the case $A = k$, and maybe $n=1$.}
-
-We can calculate the factorization homology of this factorization algebra explicitly.
-
-\greg{need to add a notation/convention somewhere including that $\Sigma^n$ will be shift functor, convention for grading and so on}
+\greg{Somewhere we should recall that $\UU_n$ and its center are unoriented $E_n$-algebras and define factorization algebras over any manifold that came from the formula}
+
+\owen{Commented out below is an orphaned set of results. Perhaps we prove it, or perhaps we just reserve it for future projects.}
+%
+%Our novel contribution in this paper is the following large $N$ result. Let $A$ be a unital algebra over a field $k$ of characteristic zero, 
+%and $u_A: \sl_\infty(k) \hookrightarrow \gl_\infty(A)$ be the map of Lie algebras determined by the unit in $A$. 
+%The induced map $\UU_nu_A: \UU_n\sl_\infty(k) \to \UU_n\gl_\infty(A)$ makes $\UU_n\gl_\infty(A)$ is an $E_n$ algebra in $\sl_\infty(k)$-modules.
+%
+%\begin{thm}
+%\label{thm: large N}
+%The centralizer ${\frak Z}_{E_n}(\UU_nu_A)$ of the map $\UU_nu_A$ is the $E_n$ algebra obtained by forgetting the dg commutative algebra
+%\[
+%\clies(\sl_\infty(k)) \otimes \Sym(\Cyc_*(A)[1-n])
+%\]
+%down to an $E_n$ algebra.
+%
+%When $k$ is $\RR$ or $\CC$, this centralizer is modeled by the locally constant factorization algebra that assigns
+%\[
+%\clies(\sl_\infty(\Omega^*(U)))\otimes \Sym(\Cyc_*(A \otimes \Omega^*_c(U))[1])
+%\]
+%to each open set $U \subset \RR^n$.
+%\end{thm}
+%\greg{Shall we keep these examples which uses/but are the easy part/ of LQT theorem ?}
+%\owen{We should write explicitly what happens in the case $A = k$, and maybe $n=1$.}
+%
+%We can calculate the factorization homology of this factorization algebra explicitly.
+%
 
@@
 
+In fact, Knudsen shows a stronger version of the second part.
+if one restricts to working with open balls in $\RR^n$ (rather than arbitrary open sets)
+then there is a $\Disk_n$-algebra ${\tt U}_n \fg$ assigning $\cliels(\fg[-n])$ to each ball and it is manifestly locally constant.
+This algebra ${\tt U}_n \fg$ is a model for~$\UU_n \fg$.
+
 \begin{rmk}
@@
 \end{rmk}
-
-\owen{\label{note on little model} Note that if we work with the colored operad of disks/boxes, then Poincar\'e lemma tells us that we can use the strict model $\cliel(\fg[-n])$ rather than the fatter model $\cliels(\Omega^*_c(U) \otimes \fg)$.
-I think Ben actually shows this too.
-This would be worth explaining because we can then use a much simpler strictification of $f$.}
 
@@
 $M \in \Mod^{E_n}_A(\cC)$ is equipped with a commuting family of actions by $A$ parametrized by $\RR^n \setminus \{0\}\cong S^{n-1} \times \RR_{>0}$.
-This action factors through the left action of the $E_1$ algebra $\int_{S^{n-1} \times \RR} A$ arising from factorization homology over the complement of the origin,
+This action factors through the left action of the $E_1$ algebra $\int_{S^{n-1} \times \RR_{>0}} A$ arising from factorization homology over the complement of the origin,
 which integrates all those actions and through which they all factor. 
-\mahmoud{i think the picture of why it is a one-sided action is clearer if we use $S^{n-1} \times \RR^+$ istead of $S^{n-1} \times \RR$}
 As shown in Theorem 7.5.3.1 of \cite{LurieHA} and earlier in Proposition 3.16 of \cite{FrancisHH}, 
@@
 the image of the unit object $1_\cC \in \cC$ under the left adjoint ${\rm Free}$ to the forgetful functor $\Mod^{E_n}_A(\cC) \to \cC$.
-
-\owen{We need to track here how the $E_n$-monoidal product intertwines with these functors.
-If we can find a juicy comment in \cite{LurieHA} or \cite{FrancisHH}, 
-we can claim they've shown that the map $f: \UU_n \fg \to B$ allows us to ``forget'' $B$ to an $E_n$ algebra in $\fg$-modules.}
 
@@
 
-These results can be marshaled to prove the following.
+These results can be marshaled to prove the first bullet point of our main theorem.
 
@@
 we obtain an underlying strict prefactorization algebra ${\tt B}$ with values in cochain complexes.
-Moreover, there is a canonical map $\cliel(\fg[-n]) \to {\tt B}$ of strict prefactorization algebras that models $f$, as desired.
+Moreover, there is a canonical map ${\tt U}_n \fg \to {\tt B}$ of strict prefactorization algebras that models $f$, as desired.
 \end{rmk}
 
-It remains to prove the technical result.
+It remains to prove the technical result.\owen{We are stuck on this point.}
 
 \begin{proof}[Proof of proposition~\ref{prp: def of obl}]
-\owen{We are stuck on this point.}
 We construct the underlying functor of $\infty$-categories $\Mod^{E_n}_{\UU_n \fg} \to \LMod_{U\fg}$ 
@@
 
-\section{Convolution algebras over colored operads}
-
-\def\conv{{\rm Conv}}
-
-\owen{For an ordinary colored operad $\cO$, describe how to produce a $\cO$-algebra $\conv(C,A)$ from any $\cO$-coalgebra $C$ and $\cO$-algebra $A$.}
-
-\owen{A special case to consider is how a cocycle $f \in \conv(C,A)$ encodes an $\cO$-algebra morphism $C^!
+%\section{Convolution algebras over colored operads}
+%
+%\def\conv{{\rm Conv}}
+%
+%\owen{For an ordinary colored operad $\cO$, describe how to produce a $\cO$-algebra $\conv(C,A)$ from any $\cO$-coalgebra $C$ and $\cO$-algebra $A$.}
+%
+%\owen{A special case to consider is how a cocycle $f \in \conv(C,A)$ encodes an $\cO$-algebra morphism $C^!
 \to A$ from $C^!
@@
 Hopefully this admits an obvious deformation-theoretic interpretation.}
-
-\owen{If we do this correctly, we might find a model category-theoretic picture of how Koszul duality works for prefactorization algebras.}
+%
+%\owen{If we do this correctly, we might find a model category-theoretic picture of how Koszul duality works for prefactorization algebras.}
 
@@
 
-Let us start by summarizing the proof. The idea, using theorem~\ref{T:En=Fac}, 
-is that we only have to prove the factorization algebra part of the main theorem. 
-To do so, we first use the universal property of the centralizer to obtain 
-a canonical factorization algebra map 
-\[\Theta_f: \clies\big(\fg\otimes \Omega (-), B(-) \big) \longrightarrow  {\frak Z}(\mathbf{f})(-)\]
-where ${\frak Z}(\mathbf{f})(-)$ is the centralizer of locally constant factorization algebras (\ref{D:centralizerFacAlgebra}).
-
-Using the fundamental properties of universal $E_n$-enveloping algebra, we then prove that 
-this map is a weak-equivalence.
-
-\smallskip
-
-We thus let $\mathbf{f}: \cliels\big(\fg \otimes \Omega^* (-)) \to B(-)$ be a factorization algebra map (see~\eqref{eq:DefofFonFaclevel}). We can 
-assume that the structural (natural) quasi-isomorphism
-$$\bigotimes_{i\in I} B(U_i) 
-\stackrel{\simeq}\longrightarrow B(\coprod  U_i)$$ are chain complexes isomorphisms by replacing $B(-)$ by the prefactorization algebra 
-given, on any $V=\coprod_{j\in J} V_j$, where the $V_j$ are the connected components of $V$, by   $\mathop{\bigotimes}\limits_{j\in J} B(V_j)$. 
-The structural maps of $B$ are then a quasi-isomorphism of prefactorization algebras between it and $B(-)$. The map $\mathbf{f}$ is lifted similary using 
-the isomorphism $\bigotimes_{i\in I} \cliels\big(\fg \otimes \Omega_c^* (U_i)\big) \cong
-\cliels\big(\fg \otimes \Omega_c^* (U)\big)$ as well. We assume we have this property in the rest of this section.
-\greg{Technically we may need to replace the latter by a quasi-isomorphic one satisfying the same property to ensure we do have a strict fact algebra map. 
-Not sure if we should elaborate on it more since in the end we only need that to obtain lemma~\ref{L:inducedFacgModstruct} to make the construction valid 
-and therefore only use the induced sym on the cosheaf of $L_\infty$-module maps}
+We have implemented the first step in the proof strategy.
+This section is devoted to the remaining steps.
+First, we explain steps (2)-(4), which are rather formal.
+Next, we define the $\Disk_n$-algebra $\clies(\Omega^* \otimes \fg, {\tt B}_f)$ as a kind of convolution algebra.
+Finally, we get to the heart of the construction:
+we show that this convolution algebra naturally sits inside a centralizer diagram.
+By the universal property of the centralizer, we then obtain 
+a canonical map 
+\[
+\Theta_f: \clies\big(\fg\otimes \Omega (-), B(-) \big) \longrightarrow  {\frak Z}(\mathbf{f})(-)
+\]
+where ${\frak Z}(\mathbf{f})(-)$ is the centralizer of locally constant $\Disk_n$-algebras~(\ref{D:centralizerFacAlgebra}).
+\owen{Calibrate notations!}
+It is then a direct computation to verify $\Theta_f$ is a quasi-isomorphism.
+
+\owen{Commented below is Greg's summary of the proof.}
+
+%Let us start by summarizing the proof. The idea, using theorem~\ref{T:En=Fac}, 
+%is that we only have to prove the factorization algebra part of the main theorem. 
+%To do so, we first use the universal property of the centralizer to obtain 
+%a canonical factorization algebra map 
+%\[\Theta_f: \clies\big(\fg\otimes \Omega (-), B(-) \big) \longrightarrow  {\frak Z}(\mathbf{f})(-)\]
+%where ${\frak Z}(\mathbf{f})(-)$ is the centralizer of locally constant factorization algebras (\ref{D:centralizerFacAlgebra}).
+%
+%
+%Using the fundamental properties of universal $E_n$-enveloping algebra, we then prove that 
+%this map is a weak-equivalence. 
+%
+%\smallskip 
+%
+%We thus let $\mathbf{f}: \cliels\big(\fg \otimes \Omega^* (-)) \to B(-)$ be a factorization algebra map (see~\eqref{eq:DefofFonFaclevel}). We can 
+%assume that the structural (natural) quasi-isomorphism
+%$$\bigotimes_{i\in I} B(U_i) 
+%\stackrel{\simeq}\longrightarrow B(\coprod  U_i)$$ are chain complexes isomorphisms by replacing $B(-)$ by the prefactorization algebra 
+%given, on any $V=\coprod_{j\in J} V_j$, where the $V_j$ are the connected components of $V$, by   $\mathop{\bigotimes}\limits_{j\in J} B(V_j)$. 
+%The structural maps of $B$ are then a quasi-isomorphism of prefactorization algebras between it and $B(-)$. The map $\mathbf{f}$ is lifted similary using 
+%the isomorphism $\bigotimes_{i\in I} \cliels\big(\fg \otimes \Omega_c^* (U_i)\big) \cong
+%\cliels\big(\fg \otimes \Omega_c^* (U)\big)$ as well. We assume we have this property in the rest of this section.
+%\greg{Technically we may need to replace the latter by a quasi-isomorphic one satisfying the same property to ensure we do have a strict fact algebra map. 
+%Not sure if we should elaborate on it more since in the end we only need that to obtain lemma~\ref{L:inducedFacgModstruct} to make the construction valid 
+%and therefore only use the induced sym on the cosheaf of $L_\infty$-module maps}
+
+\subsection{Strictification}
+
+\owen{Recall the relevant strictification results.}
+
+\owen{Sketch of where ${\tt f}$ comes from.}
+Given a cochain complex $M$, every $\fg$-representation $\rho: \fg \to \End(M)$ determines a cocommutative coderivation $\cliels(\fg) \to M$.
+Conversely, such a coderivation determines an $L_\infty$ action of $\fg$ on $M$.
+\owen{\dots}
+Applying these observations to ${\tt B}_f$ disk-by-disk, we obtain the following.
+
+\begin{lmm}
+As ${\tt B}_f$ is a $\Disk_n$-algebra in $\fg$-representations,
+there is a map of $\Disk_n$-algebras in cochain complexes ${\tt f}:  {\tt U}_n \fg \to {\tt B}$.
+\end{lmm}
+
+\owen{I'm not sure how to prove the following, or even if we need to.}
+
+\begin{prp}
+The map ${\tt f}:  {\tt U}_n \fg \to {\tt B}$ of strict $\Disk_n$-algebras models the original map~$f$.
+\end{prp}
+
+\subsection{The convolution $\Disk_n$-algebra}
+
+\owen{Describe it.}
+
 \subsection{Construction of the universal pairing in factorization algebras}\label{SS:constuctionthetaf}
+
 We start by defining a pairing between the factorization algebras of Chevalley-Eilenberg (co)chains in order to use the universal property of centralizers.

### 2020-08-31 draft.tex
small things

@@
 
-\owen{I want to work with the colored operad of round disks (or rectilinear boxes) in $\RR^n$.}
+\owen{I want to work with a colored operad $\Disk_n$ of round disks (or rectilinear boxes) in $\RR^n$.}
 
@@
 \end{thm}
+
+\owen{Plus a version for $\Disk_n$ algebras}
 
@@
 \end{dfn}
-When $n=1$ and $\cC$ is the category of vector spaces, the centralizer of $f: A \to B$ consists of the subspace of elements of $B$ that commute with the image $f(A)$ inside~$B$.
-Thus, the center of $A$ agrees with the traditional notion.
+
+When $n=1$ and $\cC$ is the category of vector spaces, 
+the centralizer of $f: A \to B$ consists of elements in $B$ that commute with the image $f(A)$ inside~$B$. 
+In particular, taking $f$ as the identity map, 
+the center of $A$ defined above agrees with the traditional notion. 
 See Theorem 5.3.1.30 of~\cite{LurieHA}, or Proposition 6.22 in~\cite{GTZ3}, for an alternative characterization.
@@
 
-We now turn to proving Theorem~\ref{thm: centralizer}.
+%We now turn to proving Theorem~\ref{thm: centralizer}.
 

### 2020-08-31 draft.tex
rearrangements

@@
 \subsection{The convolution $\Disk_n$-algebra}
+
+\owen{Discussion of convolution fact algs commented out below}
+%
+%To any $\fg$-module $M$ (wether $\fg$ is a dg Lie algebra or an $L_\infty$-algebra), 
+%we can associate its Chevalley-Eilenberg cochain complex defined 
+%by 
+%\begin{equation}
+% \clies(\fg, M) = \Hom (Sym(\fg[-1]), M)
+%\end{equation}
+%with its classical differential. 
+%\greg{recall....quickly. AT least for dg-part. Say something for $L_\infty$ too}
+%We have the evaluation map 
+%\begin{equation}
+% \label{eq:defev} ev: \clies(\fg, M) \otimes Sym(\fg[-1])\to M
+%\end{equation}
+%given by applying a function on a given tensor in $Sym(\fg[-1])$.
+%
+%\begin{dfn}\label{D:convolutionalgebraCE}Let $\fg$ be a dg Lie (or $L_\infty$)-algebra and $B$ be an $E_n$-algebra in $\fg$-modules,
+%that is an object of the $\infty$-category 
+%$E_n-Alg(Mod_{\fg})$. Its associated convolution $E_n$-algebra structure on  $\clies(\fg, B) = \Hom (Sym(\fg[-1]), B)$ is obtained by 
+% taking the \emph{convolution} between the cocommutative symmetric coalgebra $Sym(\fg[-1])$ (forgetted to an $E_n$-coalgebra) and the $E_n$-algebra $B$.
+%\end{dfn}
+%\greg{Probably need somewhere to say what means $E_n-Alg(Mod_{\fg})$ and find a less ugly notation for it}
+%Precisely, given an explicit $E_n$-operad $D_n$ in chain complexes and $(B, \mu^B)$ a $D_n$-algebra, 
+%the convolution structure is given by the following composition
+%\begin{multline}
+% \Big(D_n(r)\otimes \clies(\fg, B)^{\otimes r} \Big)\otimes Sym(\fg[-1])\\ \stackrel{id\otimes id \otimes\Delta^{(r-1)}}\longrightarrow 
+% D_n(r)\otimes \clies(\fg, B)^{\otimes r} \otimes Sym(\fg[-1])^{\otimes r} 
+% \stackrel{id \otimes (ev^{\otimes r})}\longrightarrow D_n(r)\otimes B^{\otimes r} 
+% \stackrel{\mu_\sigma^B}\longrightarrow B.
+%\end{multline}
+%where $\Delta$ is the cocommutative comultiplication.
+%In plain formula,
+%for any $\sigma \in D_n(r)$ and $\phi_1,\dots, \phi_r \in 
+%\clies(\fg, B)$, their multiplication (parametrized by $\sigma$) is  given by 
+%\begin{equation}
+% \mu_\sigma (\phi_1,\dots, \phi_r): Sym(\fg[-1]) \ni x \mapsto \pm \mu^B_{\sigma} \big(\phi_1(x^{(1)}), \dots, \phi_r(x^{(r)})\big)
+%\end{equation}
+%where $x\mapsto x^{(1)}\otimes \cdots x^{(r)}$ is the usual $r$-fold cocommutative comultiplication.
+%Note that here, we are using the usual Koszul sign  convention. 
+%
+%\begin{lmm}
+% $\clies(\fg, M) = \Hom (Sym(\fg[-1]), B)$ is a $E_n$-algebra, naturally in $\fg$ and $B$.
+%\end{lmm}
 
@@
 \subsection{End of the proof}
+
 Combining the result of the last two sections we obtain immediately the following factorization algebra model for our main theorem:
@@
 \end{proof}
+
 By Lurie's equivalence (Theorem~\ref{T:En=Fac}) between the $\infty$-categories of $E_n$-algebras and locally constant factorization algebras 
@@
 Corollary~\ref{cor:centerfactorization}  is a consequence of theorem~\ref{thm:centralizerfactorization} obtained from applyting the universal 
-$E_n$-enveloping algebra functor to a (homotopy) Lie algebra homorphism.
+$E_n$-enveloping algebra functor to a (homotopy) Lie algebra homomorphism.
 
@@
 
-\section{Factorization algebra description of the center}\label{S:centerinFacAlg}
-The universal property of centralizer (definition~\ref{D:centralizer}) implies that, for any $E_n$-algebras maps $A\stackrel{f}\to B$ and
-$B\stackrel{g}\to C$, there are natural morphisms
-\begin{equation}\label{eqdef:canonicaltocentralizers} {\frak Z}_{E_n}(g) \otimes {\frak Z}_{E_n}(f) \longrightarrow {\frak Z}_{E_n}(g\circ f)
-\end{equation}
-
-in the $\infty$-catgeory of $E_n$-algebras which are given by the  
-following commutative diagrams of $E_n$-algebras:
-\[\begin{tikzcd}
-&   {\frak Z}_{E_n}(g) \otimes  {\frak Z}_{E_n}(f) \otimes A \arrow[rr, "\id\otimes \ev_f"] &&  {\frak Z}_{E_n}(g) \otimes  B \arrow[dr, "\ev_g"]\\
-A \arrow[ur, "1\otimes \id_A"] \arrow[rr, "f"] && B \arrow[rr, "g"] \arrow[ur, "1\otimes \id_B"] && C. 
-\end{tikzcd}\]
- When $f=g=\id_A:A\to A$, we obtain a canonical morphism \begin{equation} \label{eq:dgAssofcenter}
- {\frak Z}_{E_n}(A){\otimes} {\frak Z}_{E_n}(A) \longrightarrow {\frak Z}_{E_n}(A).\end{equation}
- Lurie has proved that this multiplication makes the center into an (homotopy) dg-associative algebras in $E_n$-algebras 
- and therefore an $E_{n+1}$-algebra. Precisely: 
-\begin{prp}[\cite{LurieHA} Section 5] \label{P:PtyCenter}
-\begin{itemize}
- \item The canonical map~\eqref{eq:dgAssofcenter} makes the center ${\frak Z}_{E_n}(A)$ into an $E_1$-algebra in the symmetric monoidal category of 
- $E_n$-algebras.
- \item There is a canonical equivalence of the $\infty$-category $E_1\mathrm{-Alg}(E_n\mathrm{-Alg})$ with $E_{n+1}\mathrm{-Alg}$.
-\end{itemize}
-\end{prp}
-When $A(-)$ is a factorization algebra model for $A$, in virtue of theorem~\ref{T:En=Fac} 
-(and \greg{add reference for fac algebra in fac algebra maybe too}), in order to have a factorization algebra 
-model of the center of $A$, it is sufficient to describe the induced map 
-\[{\frak Z}(A(-)){\otimes} {\frak Z}(A(-)) \longrightarrow {\frak Z}(A(-))\]
-as a factorization algebra homomorphism which makes it an associative object in the category of locally constant factorization algebras.
-
-\smallskip
-
-We now turn to the specific case   of enveloping algebras $\UU_n(\fg)$.
-
-Let $f: \fg \to \fh$, $g: \fh \to \fl$ be  $L_\infty$-algebras morphisms; for instance a dg-Lie algebras morphisms. We write 
-\[ \mathbf{f}:\cliels\big(\fg \otimes \Omega^*_c(-)\big) \to  \cliels\big(\fh \otimes \Omega^*_c(-)\big), \quad 
-\mathbf{h}:\cliels\big(\fh \otimes \Omega^*_c(-)\big) \to  \cliels\big(\fl \otimes \Omega^*_c(-)\big)\]
-for the induced morphisms on their enveloping factorization algebras over $\RR^n$.
-
-The inclusion  of compactly supported forms on all forms induces, for any open $U$,  the  map
-\begin{equation}
- \label{eq:incofcpctforms} 
-\iota_U: \cliels\big(\fh \otimes \Omega^*_c(U)\big) \, \cong \, 
-Sym\big( \fh\otimes  \Omega^*_c (U) [1]\big) \hookrightarrow  
-Sym\big( \fh\otimes  \Omega^* (U) [1]\big).
-\end{equation}
-Recall from section~\ref{SS:constuctionthetaf} that the Chevalley Eilenberg cochain factorization algebras (with values in an augmented factorization 
-algebras) 
-are canonically pointed  by $\mathbf{1}\in \clies(\fg\otimes \Omega^*(-), B(-)) )$ which is induced by 
-the unit $k(-)\to \clies(\fg\otimes \Omega^*(-), B(-)) )$
- of the factorization structures.  In particular, we have the canonical splitting~\eqref{eq:splittingbyaugm} 
-of the  Chevalley-Eilenberg cochain factorization algebras, and an associated grading~\eqref{eq:defgraduationoncentralizernonconnected2} on each open
-set. We denote $\varphi= \lambda_\varphi +\overline{\varphi}$ the induced decomposition given by the splitting~\eqref{eq:splittingbyaugm} . 
-We use these gradings as in section~\ref{SS:constuctionthetaf} to construct a composition as follows. 
-\begin{dfn}\label{def:comp}
-For any \emph{connected} open set $W$, we define  the composition 
-$$\clies\big(\fh \otimes \Omega(W), \cliels(\fl \otimes \Omega_c(W)  \big) \otimes 
-\clie\big(\fg \otimes \Omega(W), \cliels(\fh \otimes \Omega_c(W)  \big)
-\stackrel{(-\star-)}\longrightarrow 
-\clies\big(\fg \otimes \Omega(W), \cliels(\fl \otimes \Omega_c(W)  \big)
-$$ to be given, for any $$\psi=\lambda_\psi \mathbf{1} +\overline{\psi} \in \clies\big(\fg \otimes \Omega(W), \cliels(\fh \otimes \Omega_c(W)  \big)=
-\Hom(Sym\big( \fh\otimes  \Omega (W) [1]\big), Sym\big( \fl\otimes  \Omega_c (W) [1]\big))$$
-$$\mbox{and }\varphi =\lambda_\varphi \mathbf{1} +\overline{\varphi}\in \clies\big(\fg \otimes \Omega(W), \cliels(\fh \otimes \Omega_c(W)  \big)= 
-\Hom(Sym\big( \fg\otimes  \Omega (W) [1]\big), Sym\big( \fh\otimes  \Omega_c (W) [1]\big)) $$ by 
-$$ \psi \star \varphi \, := \, \lambda_{\psi} \lambda_{\varphi} \mathbf{1}+
-\lambda_\psi g\circ \overline{\varphi} + \lambda_{\varphi} \overline{\psi} \circ \iota_W \circ f +\overline{\psi} \circ \iota_U \circ \overline{\varphi} . $$
-For any open 
-$U=\coprod\limits_{i\in I}U_i$, where the $U_i$ are the connected components of $U$,  we define  the composition 
-$$\clies\big(\fh \otimes \Omega(U), \cliels(\fl \otimes \Omega_c(U)  \big) \otimes 
-\clie\big(\fg \otimes \Omega(U), \cliels(\fh \otimes \Omega_c(U)  \big)
-\stackrel{(-\star-)}\longrightarrow 
-\clies\big(\fg \otimes \Omega(U), \cliels(\fl \otimes \Omega_c(U)  \big)
-$$ as follows. For any $$\psi \in \clies\big(\fg \otimes \Omega(U), \cliels(\fh \otimes \Omega_c(U)  \big)=
-\Hom(Sym\big( \fh\otimes  \Omega (U) [1]\big), Sym\big( \fl\otimes  \Omega_c (U) [1]\big))$$
-$$\mbox{and }\varphi \in \clies\big(\fg \otimes \Omega(U), \cliels(\fh \otimes \Omega_c(U)  \big)= 
-\Hom(Sym\big( \fg\otimes  \Omega (U) [1]\big), Sym\big( \fh\otimes  \Omega_c (U) [1]\big)), $$ we write 
-$\varphi = \mathop{\bigotimes}\limits_{i\in I} \varphi_i$, $\psi= \mathop{\bigotimes}\limits_{i\in I} \psi_i$ 
-(where $\varphi_i \in \clies\big(\fg \otimes \Omega(U_i), \cliels(\fh \otimes \Omega_c(U_i)  \big)$,
-$\psi_i\in \clies\big(\fh \otimes \Omega(U_i), \cliels(\fl \otimes \Omega_c(U_i)  \big)$) 
- using the decomposition~\eqref{eq:defgraduationoncentralizernonconnected}. Then we define
-\begin{equation} \label{eqdef:staronnonconnected}
-\psi \star \varphi \, := \mu_{\fl} \circ \Big( \bigotimes\limits_{i\in I} (\psi_i \star \varphi_i)\Big) \end{equation}
-where $\mu_{\fl}: \mathop{\bigotimes}\limits_{i\in I} \cliels(\fl\otimes \Omega^c(U_I)) \cong \cliels(\fl\otimes \Omega^c(U))$ 
-is given by the factorization algebra 
-structure. 
-\end{dfn}
-Since $\iota_U$ is an embeding for every $U$, in the rest of the paper, we will usually 
-omit it in the formulas.
-
-\begin{lmm}\label{L:compisfacmap} The composition $$\clies\big(\fh \otimes \Omega(-), \cliels(\fl \otimes \Omega_c(-)  \big) \otimes 
-\clies\big(\fg \otimes \Omega(-), \cliels(\fh \otimes \Omega_c(-)  \big)
-\stackrel{(-\star-)}\longrightarrow 
-\clies\big(\fg \otimes \Omega(-), \cliels(\fl \otimes \Omega_c(-)  \big)
-$$
- is a morphism of factorization algebras.
-\end{lmm}
-\begin{proof}
-
-\end{proof}
-The composition is compatible with the augmentation splitting. Precisely, we have
-\begin{lmm}\label{L:compisaugmented} For any $\varphi \in \clies\big(\fg \otimes \Omega(-), \cliels(\fh \otimes \Omega_c(-)  \big)$,
-$\psi \in \clies\big(\fh \otimes \Omega(-), \cliels(\fl \otimes \Omega_c(-)  \big)$
- One has the following equalities  :
- \begin{align}
-  \overline{\psi\star \varphi} \;= \;\mathbf{1}\star \overline{\varphi} +\overline{\psi}\star \mathbf{1} +\overline{\psi}\star \overline{\varphi} 
-  & \quad\mbox{ (in  $\clies\big(\fg \otimes \Omega(-), \cliels(\fl \otimes \Omega_c(-)  \big) $)}\\
- \mathbf{1}\star \varphi \;=\;  (\lambda_\varphi \mathbf{1}, g\circ \overline{\varphi})\qquad
-  &\quad\mbox{ (in  $k(-)  \oplus \overline{\clies\big(\fg \otimes \Omega(-), \cliels(\fl \otimes \Omega_c(-)  \big)}$)}\\
-  \psi \star \mathbf{1}\;=\; (\lambda_\psi \mathbf{1}, \overline{\psi} \circ f) \qquad
-  &\quad\mbox{ (in  $k(-)  \oplus \overline{\clies\big(\fg \otimes \Omega(-), \cliels(\fl \otimes \Omega_c(-)  \big)}$).}
- \end{align}
- In particular, $\mathbf{1} \star \mathbf{1} =\mathbf{1}$.
-\end{lmm}
-\greg{maybe I shoudl use the notation $\mathbf{1}_{\mathbf{f}}$, $\mathbf{1}_{\mathbf{g}}$, $\mathbf{1}_{\mathbf{g\circ f}}$ to differentiate 
-the various spaces in which leaves the units and avoid possible confusion...?}
-\begin{proof}
-
-\end{proof}
-The composition is asscoiative in the following sense.
-\begin{lmm}\label{L:compisassociative} Let $\fg \stackrel{f}\to \fh$, $\fh \stackrel{g}\to \fl$ and $\fl \stackrel{h}\to \fk$ be maps of $L_\infty$-algebras.
- Then, we have, for any $\varphi \in \clies\big(\fg\otimes \Omega(-), \cliels(\fh \otimes \Omega_c(-)) \big)$, 
-  $\psi \in \clies\big(\fh\otimes \Omega(-), \cliels(\fl \otimes \Omega_c(-)) \big)$ and  
-  $\gamma \in \clies\big(\fl\otimes \Omega(-), \cliels(\fk \otimes \Omega_c(-)) \big)$, the equality 
-  \[ (\gamma\star \psi)\star \varphi \;=\; \gamma\star (\psi \star \varphi) \quad \mbox{ in 
-  $\clies\big(\fg\otimes \Omega(-), \cliels(\fk \otimes \Omega_c(-)) \big)$.}  \]
-\end{lmm}
-\begin{proof}
-
-\end{proof}
-
-\begin{lmm}\label{L:NatPptyofComp}
- The following diagram of factorization algebras 
- \[\tiny \begin{tikzcd}
- \clies\big(\fh \otimes \Omega(-), \cliels(\fl \otimes \Omega_c(-)  \big) 
- \otimes  \clies\big(\fg \otimes \Omega(-), \cliels(\fh \otimes \Omega_c(-)  \big) 
- \otimes \cliels(\fg \otimes \Omega_c(-)  \big) \arrow[rd, "(-\star-)\otimes \id"]
- \arrow[dd, "\id\otimes \ev_ {\mathbf{f}}"]& \\ 
- & \clies\big(\fg \otimes \Omega(-), \cliels(\fl \otimes \Omega_c(-)  \big) 
- \otimes \cliels(\fg \otimes \Omega_c(-)  \big)
- \arrow[dd, "\ev_{\mathbf{g}\circ \mathbf{f}}"]\\
-\clies\big(\fh \otimes \Omega(-), \cliels(\fl \otimes \Omega_c(-)  \big) 
- \otimes \cliels(\fh \otimes \Omega_c(-)  \big)  \arrow[rd, "\ev_{\mathbf{g}}"] & \\  & \cliels(\fl \otimes \Omega_c(-)  \big). 
-\end{tikzcd}\]
- is commutative.
-\end{lmm}
-\begin{proof}
-
-\end{proof}
-
-\begin{thm}\label{T:compcentralizer}
- Let $f: \fg \to \fh$, $g: \fh \to \fl$ be  $L_\infty$-algebras morphisms.
-\begin{enumerate} \item 
- The composition $(-\star-)$ of factorization algebras (definition~\ref{def:comp}) 
- is the canonical map 
-\[{\frak Z}_{E_n}(g) \otimes {\frak Z}_{E_n}(f) \longrightarrow {\frak Z}_{E_n}(g\circ f).\] 
-\item If $f= \fg \stackrel{\id}\to \fg$,  the composition $(-\star-)$ makes 
-$\clies\big(\fg \otimes \Omega(-), \cliels(\fg \otimes \Omega_c(-)) \big)$ into an 
-(augmented) associative algebra object in factorization algebra, with unit given by $\mathbf{1}$, 
-which is equivalent to the structure of the center ${\frak Z} (\cliels(\fg \otimes \Omega_c(-)))$. 
-\end{enumerate}
-\end{thm}
-\begin{proof}
-By universal property of centralizers, the canonical map~\eqref{eqdef:canonicaltocentralizers}  
-is the unique\footnote{it is unique in the $\infty$-categorical 
-sense, that is there is a contractible space of choices for it} map 
-\[ \Upsilon: {\frak Z}_{E_n}(\UU_n g) \otimes {\frak Z}_{E_n}(\UU_n f) \longrightarrow {\frak Z}_{E_n}\big(\UU_n (g\circ f)\big)\] 
-of $E_n$-algebras which makes the following diagram
-\begin{equation}\label{eq:comdiagforcentralizercomput}\small
- \xymatrix{
-&   &&  
-{\frak Z}_{E_n}\big(\UU_n (g\circ f) \big) \otimes  \UU_n \fg  \ar@/^{2pc}/[dddr]^{\ev_{\UU_n (g\circ f)}}\\
-&{\frak Z}_{E_n}(\UU_n g) \otimes  {\frak Z}_{E_n}(\UU_n f) \otimes \UU_n \fg \ar@/^{1pc}/[rru]_{ \Upsilon \otimes \id_{\UU_n \fg}} \ar[rrd]_{\id\otimes \ev_{\UU_n f}}
-&& (1)
-& & \\
-\UU_n \fg \ar[ur]_{1^{\otimes 2}\otimes \id_{\UU_n \fg}} \ar@/_{1pc}/[rrd]^{\UU_n f} \ar@/^{6pc}/[rrruu]_{1\otimes \id_{\UU_n \fg}} &&&
-{\frak Z}_{E_n}(\UU_n g) \otimes \UU_n \fh \ar[rd]^{\ev_{\UU_n h}}  &\\
-&& \UU_n \fh \ar[rr]^{\UU_n g} \ar[ur]^{1\otimes \id_{\UU_n \fh}} && \UU_n \fl .}
-\end{equation}
-commutative (since $\UU_n (g\circ f) = \UU_n g\, \circ \, \UU_n f $;  the commutativity of the lower part of the diagram being by definition of centralizers).
-
-By Theorem~\ref{thm:centralizerfactorization}, we know that the factorization algebras models for the centralizers are given by the respective Chevalley-Eilenberg cochain factorizations algebras 
-(Definition~\ref{dfn:CEofFact}) $\clies\big(\fg \otimes \Omega(-), \cliels(\fh \otimes \Omega_c(-)  \big) $, 
-$\clies\big(\fh \otimes \Omega(-), \cliels(\fl \otimes \Omega_c(-)  \big) $ and $\clies\big(\fg \otimes \Omega(-), \cliels(\fl \otimes \Omega_c(-)  \big) $ 
-equipped with the evaluations maps are given by $\ev_{\mathbf{f}}$, $\ev_{\mathbf{g}}$ and $\ev_{\mathbf{g}\circ \mathbf{f}}$. We are thus left 
-to prove that the same  diagram as~\eqref{eq:comdiagforcentralizercomput}, where we replace the objects and maps by their factorization analogue and $\Upsilon$
-by $(-\star-)$, is commutative in factorization algebras.
-
-Thus the map $(-\star-)$ represents the canonical map of factorization algebras 
-$ {\frak Z}(\mathbf{g}) \otimes {\frak Z}(\mathbf{f}) \longrightarrow {\frak Z}(\mathbf{g}\circ \mathbf{f})$ which by proposition~\ref{P:PtyCenter} lifts
-into an $E_1$-algebra map. It remains to check that the structure is on the nose an augmented associative algebra structure.
-The augmentation and unitality are provided by Lemma~\ref{L:compisaugmented} (since in our case $f=g=\id-A$). 
-It remains to prove associativity. It follows from Lemma~\ref{L:compisassociative}. 
-The commutativity of the lower square and triangle of the diagram follows from Lemma~\ref{L:ComTriangCent}.
-\end{proof}
-
-\greg{To add: remark taht it implies the corollary~\ref{thm: center} and so.}
-
-\section{Leftover stuff}
-
-\owen{I took the following out of Greg's version of the "main theorem" section}
-
-To any $\fg$-module $M$ (wether $\fg$ is a dg Lie algebra or an $L_\infty$-algebra), 
-we can associate its Chevalley-Eilenberg cochain complex defined 
-by 
-\begin{equation}
- \clies(\fg, M) = \Hom (Sym(\fg[-1]), M)
-\end{equation}
-with its classical differential. 
-\greg{recall....quickly. AT least for dg-part. Say something for $L_\infty$ too}
-We have the evaluation map 
-\begin{equation}
- \label{eq:defev} ev: \clies(\fg, M) \otimes Sym(\fg[-1])\to M
-\end{equation}
-given by applying a function on a given tensor in $Sym(\fg[-1])$.
-
-\begin{dfn}\label{D:convolutionalgebraCE}Let $\fg$ be a dg Lie (or $L_\infty$)-algebra and $B$ be an $E_n$-algebra in $\fg$-modules,
-that is an object of the $\infty$-category 
-$E_n-Alg(Mod_{\fg})$. Its associated convolution $E_n$-algebra structure on  $\clies(\fg, B) = \Hom (Sym(\fg[-1]), B)$ is obtained by 
- taking the \emph{convolution} between the cocommutative symmetric coalgebra $Sym(\fg[-1])$ (forgetted to an $E_n$-coalgebra) and the $E_n$-algebra $B$.
-\end{dfn}
-\greg{Probably need somewhere to say what means $E_n-Alg(Mod_{\fg})$ and find a less ugly notation for it}
-Precisely, given an explicit $E_n$-operad $D_n$ in chain complexes and $(B, \mu^B)$ a $D_n$-algebra, 
-the convolution structure is given by the following composition
-\begin{multline}
- \Big(D_n(r)\otimes \clies(\fg, B)^{\otimes r} \Big)\otimes Sym(\fg[-1])\\ \stackrel{id\otimes id \otimes\Delta^{(r-1)}}\longrightarrow 
- D_n(r)\otimes \clies(\fg, B)^{\otimes r} \otimes Sym(\fg[-1])^{\otimes r} 
- \stackrel{id \otimes (ev^{\otimes r})}\longrightarrow D_n(r)\otimes B^{\otimes r} 
- \stackrel{\mu_\sigma^B}\longrightarrow B.
-\end{multline}
-where $\Delta$ is the cocommutative comultiplication.
-In plain formula,
-for any $\sigma \in D_n(r)$ and $\phi_1,\dots, \phi_r \in 
-\clies(\fg, B)$, their multiplication (parametrized by $\sigma$) is  given by 
-\begin{equation}
- \mu_\sigma (\phi_1,\dots, \phi_r): Sym(\fg[-1]) \ni x \mapsto \pm \mu^B_{\sigma} \big(\phi_1(x^{(1)}), \dots, \phi_r(x^{(r)})\big)
-\end{equation}
-where $x\mapsto x^{(1)}\otimes \cdots x^{(r)}$ is the usual $r$-fold cocommutative comultiplication.
-Note that here, we are using the usual Koszul sign  convention.
-
-\begin{lmm}
- $\clies(\fg, M) = \Hom (Sym(\fg[-1]), B)$ is a $E_n$-algebra, naturally in $\fg$ and $B$.
-\end{lmm}
+\owen{Commented out here is a discussion of centers. We may want to resurrect it but it doesn't seem essential to the main results.}
+
+%\section{Factorization algebra description of the center}
+%\label{S:centerinFacAlg}
+%
+%The universal property of centralizer (definition~\ref{D:centralizer}) implies that, for any $E_n$-algebras maps $A\stackrel{f}\to B$ and
+%$B\stackrel{g}\to C$, there are natural morphisms
+%\begin{equation}\label{eqdef:canonicaltocentralizers} {\frak Z}_{E_n}(g) \otimes {\frak Z}_{E_n}(f) \longrightarrow {\frak Z}_{E_n}(g\circ f)
+%\end{equation}
+% 
+%in the $\infty$-catgeory of $E_n$-algebras which are given by the  
+%following commutative diagrams of $E_n$-algebras:
+%\[\begin{tikzcd}
+%&   {\frak Z}_{E_n}(g) \otimes  {\frak Z}_{E_n}(f) \otimes A \arrow[rr, "\id\otimes \ev_f"] &&  {\frak Z}_{E_n}(g) \otimes  B \arrow[dr, "\ev_g"]\\
+%A \arrow[ur, "1\otimes \id_A"] \arrow[rr, "f"] && B \arrow[rr, "g"] \arrow[ur, "1\otimes \id_B"] && C. 
+%\end{tikzcd}\]
+% When $f=g=\id_A:A\to A$, we obtain a canonical morphism \begin{equation} \label{eq:dgAssofcenter}
+% {\frak Z}_{E_n}(A){\otimes} {\frak Z}_{E_n}(A) \longrightarrow {\frak Z}_{E_n}(A).\end{equation}
+% Lurie has proved that this multiplication makes the center into an (homotopy) dg-associative algebras in $E_n$-algebras 
+% and therefore an $E_{n+1}$-algebra. Precisely: 
+%\begin{prp}[\cite{LurieHA} Section 5] \label{P:PtyCenter}
+%\begin{itemize}
+% \item The canonical map~\eqref{eq:dgAssofcenter} makes the center ${\frak Z}_{E_n}(A)$ into an $E_1$-algebra in the symmetric monoidal category of 
+% $E_n$-algebras.
+% \item There is a canonical equivalence of the $\infty$-category $E_1\mathrm{-Alg}(E_n\mathrm{-Alg})$ with $E_{n+1}\mathrm{-Alg}$.
+%\end{itemize}
+%\end{prp}
+%When $A(-)$ is a factorization algebra model for $A$, in virtue of theorem~\ref{T:En=Fac} 
+%(and \greg{add reference for fac algebra in fac algebra maybe too}), in order to have a factorization algebra 
+%model of the center of $A$, it is sufficient to describe the induced map 
+%\[{\frak Z}(A(-)){\otimes} {\frak Z}(A(-)) \longrightarrow {\frak Z}(A(-))\]
+%as a factorization algebra homomorphism which makes it an associative object in the category of locally constant factorization algebras.
+%
+%\smallskip
+%
+%We now turn to the specific case   of enveloping algebras $\UU_n(\fg)$.
+%
+%Let $f: \fg \to \fh$, $g: \fh \to \fl$ be  $L_\infty$-algebras morphisms; for instance a dg-Lie algebras morphisms. We write 
+%\[ \mathbf{f}:\cliels\big(\fg \otimes \Omega^*_c(-)\big) \to  \cliels\big(\fh \otimes \Omega^*_c(-)\big), \quad 
+%\mathbf{h}:\cliels\big(\fh \otimes \Omega^*_c(-)\big) \to  \cliels\big(\fl \otimes \Omega^*_c(-)\big)\]
+%for the induced morphisms on their enveloping factorization algebras over $\RR^n$.
+%
+%The inclusion  of compactly supported forms on all forms induces, for any open $U$,  the  map
+%\begin{equation}
+% \label{eq:incofcpctforms} 
+%\iota_U: \cliels\big(\fh \otimes \Omega^*_c(U)\big) \, \cong \, 
+%Sym\big( \fh\otimes  \Omega^*_c (U) [1]\big) \hookrightarrow  
+%Sym\big( \fh\otimes  \Omega^* (U) [1]\big).
+%\end{equation}
+%Recall from section~\ref{SS:constuctionthetaf} that the Chevalley Eilenberg cochain factorization algebras (with values in an augmented factorization 
+%algebras) 
+%are canonically pointed  by $\mathbf{1}\in \clies(\fg\otimes \Omega^*(-), B(-)) )$ which is induced by 
+%the unit $k(-)\to \clies(\fg\otimes \Omega^*(-), B(-)) )$
+% of the factorization structures.  In particular, we have the canonical splitting~\eqref{eq:splittingbyaugm} 
+%of the  Chevalley-Eilenberg cochain factorization algebras, and an associated grading~\eqref{eq:defgraduationoncentralizernonconnected2} on each open
+%set. We denote $\varphi= \lambda_\varphi +\overline{\varphi}$ the induced decomposition given by the splitting~\eqref{eq:splittingbyaugm} . 
+%We use these gradings as in section~\ref{SS:constuctionthetaf} to construct a composition as follows. 
+%\begin{dfn}\label{def:comp}
+%For any \emph{connected} open set $W$, we define  the composition 
+%$$\clies\big(\fh \otimes \Omega(W), \cliels(\fl \otimes \Omega_c(W)  \big) \otimes 
+%\clie\big(\fg \otimes \Omega(W), \cliels(\fh \otimes \Omega_c(W)  \big)
+%\stackrel{(-\star-)}\longrightarrow 
+%\clies\big(\fg \otimes \Omega(W), \cliels(\fl \otimes \Omega_c(W)  \big)
+%$$ to be given, for any $$\psi=\lambda_\psi \mathbf{1} +\overline{\psi} \in \clies\big(\fg \otimes \Omega(W), \cliels(\fh \otimes \Omega_c(W)  \big)=
+%\Hom(Sym\big( \fh\otimes  \Omega (W) [1]\big), Sym\big( \fl\otimes  \Omega_c (W) [1]\big))$$
+%$$\mbox{and }\varphi =\lambda_\varphi \mathbf{1} +\overline{\varphi}\in \clies\big(\fg \otimes \Omega(W), \cliels(\fh \otimes \Omega_c(W)  \big)= 
+%\Hom(Sym\big( \fg\otimes  \Omega (W) [1]\big), Sym\big( \fh\otimes  \Omega_c (W) [1]\big)) $$ by 
+%$$ \psi \star \varphi \, := \, \lambda_{\psi} \lambda_{\varphi} \mathbf{1}+
+%\lambda_\psi g\circ \overline{\varphi} + \lambda_{\varphi} \overline{\psi} \circ \iota_W \circ f +\overline{\psi} \circ \iota_U \circ \overline{\varphi} . $$
+%For any open 
+%$U=\coprod\limits_{i\in I}U_i$, where the $U_i$ are the connected components of $U$,  we define  the composition 
+%$$\clies\big(\fh \otimes \Omega(U), \cliels(\fl \otimes \Omega_c(U)  \big) \otimes 
+%\clie\big(\fg \otimes \Omega(U), \cliels(\fh \otimes \Omega_c(U)  \big)
+%\stackrel{(-\star-)}\longrightarrow 
+%\clies\big(\fg \otimes \Omega(U), \cliels(\fl \otimes \Omega_c(U)  \big)
+%$$ as follows. For any $$\psi \in \clies\big(\fg \otimes \Omega(U), \cliels(\fh \otimes \Omega_c(U)  \big)=
+%\Hom(Sym\big( \fh\otimes  \Omega (U) [1]\big), Sym\big( \fl\otimes  \Omega_c (U) [1]\big))$$
+%$$\mbox{and }\varphi \in \clies\big(\fg \otimes \Omega(U), \cliels(\fh \otimes \Omega_c(U)  \big)= 
+%\Hom(Sym\big( \fg\otimes  \Omega (U) [1]\big), Sym\big( \fh\otimes  \Omega_c (U) [1]\big)), $$ we write 
+%$\varphi = \mathop{\bigotimes}\limits_{i\in I} \varphi_i$, $\psi= \mathop{\bigotimes}\limits_{i\in I} \psi_i$ 
+%(where $\varphi_i \in \clies\big(\fg \otimes \Omega(U_i), \cliels(\fh \otimes \Omega_c(U_i)  \big)$,
+%$\psi_i\in \clies\big(\fh \otimes \Omega(U_i), \cliels(\fl \otimes \Omega_c(U_i)  \big)$) 
+% using the decomposition~\eqref{eq:defgraduationoncentralizernonconnected}. Then we define
+%\begin{equation} \label{eqdef:staronnonconnected}
+%\psi \star \varphi \, := \mu_{\fl} \circ \Big( \bigotimes\limits_{i\in I} (\psi_i \star \varphi_i)\Big) \end{equation}
+%where $\mu_{\fl}: \mathop{\bigotimes}\limits_{i\in I} \cliels(\fl\otimes \Omega^c(U_I)) \cong \cliels(\fl\otimes \Omega^c(U))$ 
+%is given by the factorization algebra 
+%structure. 
+%\end{dfn}
+%Since $\iota_U$ is an embeding for every $U$, in the rest of the paper, we will usually 
+%omit it in the formulas. 
+%
+%\begin{lmm}\label{L:compisfacmap} The composition $$\clies\big(\fh \otimes \Omega(-), \cliels(\fl \otimes \Omega_c(-)  \big) \otimes 
+%\clies\big(\fg \otimes \Omega(-), \cliels(\fh \otimes \Omega_c(-)  \big)
+%\stackrel{(-\star-)}\longrightarrow 
+%\clies\big(\fg \otimes \Omega(-), \cliels(\fl \otimes \Omega_c(-)  \big)
+%$$
+% is a morphism of factorization algebras.
+%\end{lmm}
+%\begin{proof}
+% 
+%\end{proof}
+%The composition is compatible with the augmentation splitting. Precisely, we have
+%\begin{lmm}\label{L:compisaugmented} For any $\varphi \in \clies\big(\fg \otimes \Omega(-), \cliels(\fh \otimes \Omega_c(-)  \big)$,
+%$\psi \in \clies\big(\fh \otimes \Omega(-), \cliels(\fl \otimes \Omega_c(-)  \big)$
+% One has the following equalities  :
+% \begin{align}
+%  \overline{\psi\star \varphi} \;= \;\mathbf{1}\star \overline{\varphi} +\overline{\psi}\star \mathbf{1} +\overline{\psi}\star \overline{\varphi} 
+%  & \quad\mbox{ (in  $\clies\big(\fg \otimes \Omega(-), \cliels(\fl \otimes \Omega_c(-)  \big) $)}\\
+% \mathbf{1}\star \varphi \;=\;  (\lambda_\varphi \mathbf{1}, g\circ \overline{\varphi})\qquad
+%  &\quad\mbox{ (in  $k(-)  \oplus \overline{\clies\big(\fg \otimes \Omega(-), \cliels(\fl \otimes \Omega_c(-)  \big)}$)}\\
+%  \psi \star \mathbf{1}\;=\; (\lambda_\psi \mathbf{1}, \overline{\psi} \circ f) \qquad
+%  &\quad\mbox{ (in  $k(-)  \oplus \overline{\clies\big(\fg \otimes \Omega(-), \cliels(\fl \otimes \Omega_c(-)  \big)}$).}
+% \end{align}
+% In particular, $\mathbf{1} \star \mathbf{1} =\mathbf{1}$.
+%\end{lmm}
+%\greg{maybe I shoudl use the notation $\mathbf{1}_{\mathbf{f}}$, $\mathbf{1}_{\mathbf{g}}$, $\mathbf{1}_{\mathbf{g\circ f}}$ to differentiate 
+%the various spaces in which leaves the units and avoid possible confusion...?}
+%\begin{proof}
+% 
+%\end{proof}
+%The composition is asscoiative in the following sense.
+%\begin{lmm}\label{L:compisassociative} Let $\fg \stackrel{f}\to \fh$, $\fh \stackrel{g}\to \fl$ and $\fl \stackrel{h}\to \fk$ be maps of $L_\infty$-algebras.
+% Then, we have, for any $\varphi \in \clies\big(\fg\otimes \Omega(-), \cliels(\fh \otimes \Omega_c(-)) \big)$, 
+%  $\psi \in \clies\big(\fh\otimes \Omega(-), \cliels(\fl \otimes \Omega_c(-)) \big)$ and  
+%  $\gamma \in \clies\big(\fl\otimes \Omega(-), \cliels(\fk \otimes \Omega_c(-)) \big)$, the equality 
+%  \[ (\gamma\star \psi)\star \varphi \;=\; \gamma\star (\psi \star \varphi) \quad \mbox{ in 
+%  $\clies\big(\fg\otimes \Omega(-), \cliels(\fk \otimes \Omega_c(-)) \big)$.}  \]
+%\end{lmm}
+%\begin{proof}
+% 
+%\end{proof}
+%
+% 
+% 
+%\begin{lmm}\label{L:NatPptyofComp}
+% The following diagram of factorization algebras 
+% \[\tiny \begin{tikzcd}
+% \clies\big(\fh \otimes \Omega(-), \cliels(\fl \otimes \Omega_c(-)  \big) 
+% \otimes  \clies\big(\fg \otimes \Omega(-), \cliels(\fh \otimes \Omega_c(-)  \big) 
+% \otimes \cliels(\fg \otimes \Omega_c(-)  \big) \arrow[rd, "(-\star-)\otimes \id"]
+% \arrow[dd, "\id\otimes \ev_ {\mathbf{f}}"]& \\ 
+% & \clies\big(\fg \otimes \Omega(-), \cliels(\fl \otimes \Omega_c(-)  \big) 
+% \otimes \cliels(\fg \otimes \Omega_c(-)  \big)
+% \arrow[dd, "\ev_{\mathbf{g}\circ \mathbf{f}}"]\\
+%\clies\big(\fh \otimes \Omega(-), \cliels(\fl \otimes \Omega_c(-)  \big) 
+% \otimes \cliels(\fh \otimes \Omega_c(-)  \big)  \arrow[rd, "\ev_{\mathbf{g}}"] & \\  & \cliels(\fl \otimes \Omega_c(-)  \big). 
+%\end{tikzcd}\]
+% is commutative.
+%\end{lmm}
+%\begin{proof}
+% 
+%\end{proof}
+%
+%\begin{thm}\label{T:compcentralizer}
+% Let $f: \fg \to \fh$, $g: \fh \to \fl$ be  $L_\infty$-algebras morphisms.
+%\begin{enumerate} \item 
+% The composition $(-\star-)$ of factorization algebras (definition~\ref{def:comp}) 
+% is the canonical map 
+%\[{\frak Z}_{E_n}(g) \otimes {\frak Z}_{E_n}(f) \longrightarrow {\frak Z}_{E_n}(g\circ f).\] 
+%\item If $f= \fg \stackrel{\id}\to \fg$,  the composition $(-\star-)$ makes 
+%$\clies\big(\fg \otimes \Omega(-), \cliels(\fg \otimes \Omega_c(-)) \big)$ into an 
+%(augmented) associative algebra object in factorization algebra, with unit given by $\mathbf{1}$, 
+%which is equivalent to the structure of the center ${\frak Z} (\cliels(\fg \otimes \Omega_c(-)))$. 
+%\end{enumerate}
+%\end{thm}
+%\begin{proof}
+%By universal property of centralizers, the canonical map~\eqref{eqdef:canonicaltocentralizers}  
+%is the unique\footnote{it is unique in the $\infty$-categorical 
+%sense, that is there is a contractible space of choices for it} map 
+%\[ \Upsilon: {\frak Z}_{E_n}(\UU_n g) \otimes {\frak Z}_{E_n}(\UU_n f) \longrightarrow {\frak Z}_{E_n}\big(\UU_n (g\circ f)\big)\] 
+%of $E_n$-algebras which makes the following diagram
+%\begin{equation}\label{eq:comdiagforcentralizercomput}\small
+% \xymatrix{
+%&   &&  
+%{\frak Z}_{E_n}\big(\UU_n (g\circ f) \big) \otimes  \UU_n \fg  \ar@/^{2pc}/[dddr]^{\ev_{\UU_n (g\circ f)}}\\
+%&{\frak Z}_{E_n}(\UU_n g) \otimes  {\frak Z}_{E_n}(\UU_n f) \otimes \UU_n \fg \ar@/^{1pc}/[rru]_{ \Upsilon \otimes \id_{\UU_n \fg}} \ar[rrd]_{\id\otimes \ev_{\UU_n f}}
+%&& (1)
+%& & \\
+%\UU_n \fg \ar[ur]_{1^{\otimes 2}\otimes \id_{\UU_n \fg}} \ar@/_{1pc}/[rrd]^{\UU_n f} \ar@/^{6pc}/[rrruu]_{1\otimes \id_{\UU_n \fg}} &&&
+%{\frak Z}_{E_n}(\UU_n g) \otimes \UU_n \fh \ar[rd]^{\ev_{\UU_n h}}  &\\
+%&& \UU_n \fh \ar[rr]^{\UU_n g} \ar[ur]^{1\otimes \id_{\UU_n \fh}} && \UU_n \fl .}
+%\end{equation}
+%commutative (since $\UU_n (g\circ f) = \UU_n g\, \circ \, \UU_n f $;  the commutativity of the lower part of the diagram being by definition of centralizers).
+%
+%By Theorem~\ref{thm:centralizerfactorization}, we know that the factorization algebras models for the centralizers are given by the respective Chevalley-Eilenberg cochain factorizations algebras 
+%(Definition~\ref{dfn:CEofFact}) $\clies\big(\fg \otimes \Omega(-), \cliels(\fh \otimes \Omega_c(-)  \big) $, 
+%$\clies\big(\fh \otimes \Omega(-), \cliels(\fl \otimes \Omega_c(-)  \big) $ and $\clies\big(\fg \otimes \Omega(-), \cliels(\fl \otimes \Omega_c(-)  \big) $ 
+%equipped with the evaluations maps are given by $\ev_{\mathbf{f}}$, $\ev_{\mathbf{g}}$ and $\ev_{\mathbf{g}\circ \mathbf{f}}$. We are thus left 
+%to prove that the same  diagram as~\eqref{eq:comdiagforcentralizercomput}, where we replace the objects and maps by their factorization analogue and $\Upsilon$
+%by $(-\star-)$, is commutative in factorization algebras.
+%
+%Thus the map $(-\star-)$ represents the canonical map of factorization algebras 
+%$ {\frak Z}(\mathbf{g}) \otimes {\frak Z}(\mathbf{f}) \longrightarrow {\frak Z}(\mathbf{g}\circ \mathbf{f})$ which by proposition~\ref{P:PtyCenter} lifts
+%into an $E_1$-algebra map. It remains to check that the structure is on the nose an augmented associative algebra structure.
+%The augmentation and unitality are provided by Lemma~\ref{L:compisaugmented} (since in our case $f=g=\id-A$). 
+%It remains to prove associativity. It follows from Lemma~\ref{L:compisassociative}. 
+%The commutativity of the lower square and triangle of the diagram follows from Lemma~\ref{L:ComTriangCent}.
+%\end{proof}
+%
+%\greg{To add: remark that it implies the corollary~\ref{thm: center} and so.}
+
+\section{Factorization algebras that model centralizers}
 

### 2020-09-01 draft.tex
cut substantially

--- 2020-08-31 draft.tex
@@
 
+Even to state our central result, we need to review a few results and terminology.
+First, our basic context is $E_n$ algebras.
+By $E_n$ we mean any operad or colored operad or $\infty$-operad equivalent to the topological operad of little $n$-disks in $\RR^n$, where the notion of equivalence is in some appropriate $\infty$-categorical setting of operads.
+In particular, we will require that its $\infty$-category of algebras in $\Ch_k^{\otimes_k}$ agree with those of the little $n$-disks operad. 
+For us the preferred presentation is by locally constant factorization algebras on $\RR^n$,
+which, as we explain below, can be understood via a colored operad whose colors are open sets in~$\RR^n$.
+
+Our approach here relies on a concrete and convenient model for these enveloping $E_n$ algebras by factorization algebras.
+In particular, thanks to Knudsen \cite{Knudsen}, 
+we know that the $E_n$ enveloping algebra $\UU_n \fg$ admits a model whose underlying functor on the poset of open sets in $\RR^n$ assigns $\cliels(\Omega_c^*(V) \otimes \fg)$ to each open set~$V$.
+There is another factorization algebra whose underlying assigns $\clies(\Omega^*(V) \otimes \fg)$ to each open~$V$.
+Our paper shows that such factorization algebras model other important $E_n$ algebras, notably centralizers.
+
 \begin{thm}
 \label{thm: centralizer}
-Let $\UU_n \fg$ be the enveloping $E_n$ algebra of a dg Lie algebra $\fg$ and let 
-\[
-f: \UU_n \fg \to B
-\]
-be a map of augmented $E_n$ algebras.
-Then
+Let $\fg$ and $\fh$ be $L_\infty$ algebras over the real or complex numbers, 
+and let $f: \fg \rightsquigarrow \fh$ be a homotopy-coherent morphism of $L_\infty$ algebras
+(i.e., a map of conilpotent cocommutative coalgebras $f: \cliels(\fg) \to \cliels(\fh)$).
+This map determines functorially a map of $E_n$ algebras
+\[
+f: \UU_n \fg \to \UU_n \fh
+\]
+between their enveloping $E_n$ algebras.
+The centralizer ${\frak Z}_{E_n}(f)$ is an $E_n$-algebra modeled by the factorization algebra 
+\[
+\clies(\Omega^* \otimes \fg, \cliels(\Omega^*_c \otimes \fh))
+\]
+equipped with a convolution-type product.
+\end{thm}
+
+\owen{I think we could (and maybe should) also discuss the $E_n$-Koszul dual situation involving cochains.}
+
+\def\Disk{{\rm Disk}}
+
+Our proof involves explicit manipulations with cochain complexes and the poset of opens in~$\RR^n$.
+To connect that setting with the abstract $\infty$-categorical setting above,
+we leverage deep, prior work:
 \begin{itemize}
-\item $f$ lets us lift $B$ to an $E_n$ algebra $B_f$ in $\fg$-modules and
-\item the centralizer ${\frak Z}_{E_n}(f)$ is an $E_n$-algebra modeled by the Chevalley-Eilenberg 
-cochains $\clies(\fg, B_f)$ equipped with the convolution $E_n$-product.
-\end{itemize}
-\end{thm}
-
-\def\Disk{{\rm Disk}}
-
-Existing work provides insight into and context for the situation:
-\begin{itemize}
-\item Lurie and Francis give a characterization of the centralizer ${\frak Z}_{E_n}(f)$ of any $E_n$ algebra map $f: A \to B$ as the ``internal hom'' in left $\int_{S^{n-1}}A$-modules from $A$ to $B_f$, where $B_f$ denotes $B$ viewed as a left module via the map~$f$.
 \item Lurie \cite{LurieHA} explains why the $\infty$-category of $E_n$ algebras is equivalent to the homotopy-coherent version of locally constant prefactorization algebras on $\RR^n$.  
@@
 Let $\Disk_n^\sqcup$ denote the colored operad whose colors are balls in $\RR^n$ and whose spaces of operations are either empty or a point, depending on whether the input balls are pairwise disjoint and subsets of the output ball.
-One can work with locally constant, homotopy-coherent algebras over $\Disk_n^\sqcup$.
-\item In particular, Knudsen verifies that we can model the enveloping $E_n$ algebra by a strict $\Disk_n$-algebra $\cliels(\fg[-n])$ that is strictly locally constant.
+One can work with locally constant, homotopy-coherent $\Disk_n^\sqcup$-algebras.
+\item In particular, in addition to the factorization algebra model, Knudsen verifies that we can model the enveloping $E_n$ algebra by a strict $\Disk_n$-algebra $\cliels(\fg[-n])$ that is strictly locally constant.
+\item Lurie and Francis give a characterization of the centralizer ${\frak Z}_{E_n}(f)$ of any $E_n$ algebra map $f: A \to B$ as the ``internal hom'' in left $\int_{S^{n-1}}A$-modules from $A$ to $B_f$, where $B_f$ denotes $B$ viewed as a left module via the map~$f$.
 \item In combination, the centralizer is characterized up to quasi-isomorphism, 
@@
 \end{itemize}
-Our approach leverages these results as follows to prove the theorem.
+In \S2 we review these results in more detail with an emphasis on what we need for our central theorem.
+
+Here is an outline of our proof:
 \begin{enumerate}
-\item By modest extensions of the works cited above, we show that  $f$ equips $B$ with the structure of an $E_n$ algebra in $\fg$-representations, which we also denote $B_f$.
-\owen{Let's hope we can justify this!}
-\item Next, we transfer the question to the setting of {\em strict} $\Disk_n$-algebras that are weakly locally constant. 
-Strictification theorems from the model category literature on operads say we can replace homotopy-coherent $\Disk_n$-algebras with strict ones. 
-\item  In particular, given our $E_n$ algebra $B_f$ in $\fg$-modules, model it by a strict $\Disk_n$-algebra ${\tt B}_f$ with values in a nice model category $\Mod_\fg(\Ch_k)$ of dg $\fg$-representations.
-The forgetful functor $\Mod_\fg(\Ch_k) \to \Ch_k$ lets us produce a strict prefactorization algebra ${\tt B}$ that models~$B$.
-\item By construction, the action of $\fg$ on ${\tt B}_f$ determines a map ${\tt f}:  {\tt U}_n \fg \to {\tt B}$ of strict $\Disk_n$-algebras that models the original map~$f$.
-\item We then construct an explicit strict $\Disk_n$-algebra $\clies(\Omega \otimes \fg, {\tt B}_f)$ as a kind of ``convolution algebra.'' 
-\item We show this object fits canonically into a centralizer diagram: there is a map
-\[
-\clies(\Omega \otimes \fg, {\tt B}_f) \otimes {\tt U}_n \fg \to {\tt B}_f
-\]
-such that precomposing with the map $1 \otimes \id_{{\tt U}_n \fg}$ is the map~${\tt f}$.
-Fitting into such a diagram guarantees a canonical map $\clies(\Omega \otimes \fg, {\tt B}_f) \to {\tt Z}_f$ as strict $\Disk_n$-algebras. 
+\item From the map $f: \cliels(\Omega_c^* \otimes \fg) \to \cliels(\Omega_c^* \otimes \fh)$, 
+we produce an explicit factorization algebra $\clies(\Omega \otimes \fg, \cliels(\Omega_c^* \otimes \fh)_f)$ as a kind of ``convolution factorization algebra.'' 
+\item We show this object fits canonically into a centralizer diagram: there is a map of factorization algebras
+\[
+\clies(\Omega \otimes \fg, \cliels(\Omega_c^* \otimes \fh)_f) \otimes \UU_n \fg \to \cliels(\Omega_c^* \otimes \fh)
+\]
+such that precomposing with the map $1 \otimes \id_{\UU_n \fg}$ is the map~$f$.
+Fitting into such a diagram guarantees a canonical map 
+\[
+\clies(\Omega \otimes \fg, \cliels(\Omega_c^* \otimes \fh)_f) \to Z_f
+\]
+as factorization algebras. 
 \item We then verify that this map is a quasi-isomorphism on disks, by the Lurie-Francis result mentioned above. 
 \end{enumerate}
-Hence it induces a weak equivalence of the associated $E_n$ algebras.
+Hence it induces a weak equivalence of the associated factorization algebras and hence as $E_n$ algebras.
 
 \subsection{Consequences of the central result}
+
+If $\rho: \fg \to \fg$ is the identity map, we get the following immediate corollary.
+
+\begin{cor}
+\label{thm: center}
+The center of the enveloping $E_n$ algebra $\UU_n\fg$ is the $E_n$ algebra $\clies(\fg, \UU_n\fg)$. 
+When $k$ is $\RR$ or $\CC$, the 
+center is modeled by the locally constant factorization algebra that assigns
+\[
+\clies(\fg \otimes \Omega^*(U), \cliels( \fg \otimes \Omega^*_c(U)))
+\]
+to each open set $U \subset \RR^n$.
+\end{cor}
+
+This result generalizes the fact that $\Hoch^*(U\fg,U\fg) \simeq \clies(\fg, U\fg)$, 
+since the associative algebra $U\fg$ is modeled by the locally constant one-dimensional factorization algebra that assigns
+$\cliels (\fg \otimes \Omega^*_c(U))$ to each open $U \subset \RR$.
+
+\owen{Add remark that by Dunn's additivity theorem, the center has a natural $E_{n+1}$ algebra structure.}
+\greg{I will add stuff and rewrite that later, hopefully to explain ``how'' to see the $E_{n+1}$-structure}
+
+\greg{We could relate this to $P_n$-center of $\fg$. That shall also (but I have to think about the proof more), 
+at least up to formality gives the $P_{n+1}$-structure on it. }
+
+If $\epsilon: \fg \to 0$ is the trivial map, then we obtain the canonical augmentation $\epsilon: \UU_n \fg \to k$ of $E_n$ algebras.
+In this case, we obtain a version of Koszul duality as the corollary.
+
+\begin{cor}
+\label{thm: koszul duality}
+The centralizer of the augmentation $\epsilon: \UU_n \fg \to k$ is equivalent to $\clies(\fg)$ viewed as an $E_n$ algebra. It is modeled by the locally constant factorization algebra that assigns
+\[
+\clies(\fg \otimes \Omega^*(V))
+\]
+to each open set $V \subset \RR^n$.
+\end{cor}
 
@@
 
-By Knudsen's results \cite{Knudsen}, we have the following explicit applications of our main theorem~\ref{thm: center}.
-
-\owen{I think we should just work in $Ch(\RR)$ or $Ch(\CC)$ throughout.}
-
-\begin{cor}\label{cor:centerfactorization}
-Let $k$ is $\RR$ or $\CC$, and assume $\UU_n \rho:  \UU_n \fg \to \UU_n \fh$ is induced by a map of Lie algebras $\rho: \fg \to \fh$. 
-Then the centralizer ${\frak Z}_{E_n}(\UU_n \rho)$ is modeled by the locally constant factorization algebra that assigns
-\[
-\clies(\fg \otimes \Omega^*(U), \cliels( \fh \otimes \Omega^*_c(U)))
-\]
-to each open set $U \subset \RR^n$. Here, $\Omega^*_c(U)$ denotes the commutative differential graded algebra (cdga) of compactly supported forms on $U$.
-\end{cor}
-
-If $\rho: \fg \to \fg$ is the identity map, we get the following immediate corollary.
-
-\begin{cor}
-\label{thm: center}
-The center of the enveloping $E_n$ algebra $\UU_n\fg$ is the $E_n$ algebra $\clies(\fg, \UU_n\fg)$. 
-When $k$ is $\RR$ or $\CC$, the 
-center is modeled by the locally constant factorization algebra that assigns
-\[
-\clies(\fg \otimes \Omega^*(U), \cliels( \fg \otimes \Omega^*_c(U)))
-\]
-to each open set $U \subset \RR^n$.
-\end{cor}
-
-\owen{Add remark that by Dunn's additivity theorem, the center has a natural $E_{n+1}$ algebra structure.}
-\greg{I will add stuff and rewrite that later, hopefully to explain ``how'' to see the $E_{n+1}$-structure}
-
-\greg{We could relate this to $P_n$-center of $\fg$. That shall also (but I have to think about the proof more), 
-at least up to formality gives the $P_{n+1}$-structure on it. }
-
-This result generalizes the fact that $\Hoch^*(U\fg,U\fg) \simeq \clies(\fg, U\fg)$, 
-since the associative algebra $U\fg$ is modeled by the locally constant one-dimensional factorization algebra that assigns
-$\cliels (\fg \otimes \Omega^*_c(U))$ to each open $U \subset \RR$.
-
 Having an explicit presentation for the centralizer of a map of $E_n$ algebras leads to a calculation of factorization homology.
@@
 \]
-
 For $n=1$, this recovers a theorem of Tamarkin and Tsygan \cite{TT} on the Hochschild cohomology of differential operators on a Lie group $G$;
@@
 \greg{Somewhere we should recall that $\UU_n$ and its center are unoriented $E_n$-algebras and define factorization algebras over any manifold that came from the formula}
-
-\owen{Commented out below is an orphaned set of results. Perhaps we prove it, or perhaps we just reserve it for future projects.}
-%
-%Our novel contribution in this paper is the following large $N$ result. Let $A$ be a unital algebra over a field $k$ of characteristic zero, 
-%and $u_A: \sl_\infty(k) \hookrightarrow \gl_\infty(A)$ be the map of Lie algebras determined by the unit in $A$. 
-%The induced map $\UU_nu_A: \UU_n\sl_\infty(k) \to \UU_n\gl_\infty(A)$ makes $\UU_n\gl_\infty(A)$ is an $E_n$ algebra in $\sl_\infty(k)$-modules.
-%
-%\begin{thm}
-%\label{thm: large N}
-%The centralizer ${\frak Z}_{E_n}(\UU_nu_A)$ of the map $\UU_nu_A$ is the $E_n$ algebra obtained by forgetting the dg commutative algebra
-%\[
-%\clies(\sl_\infty(k)) \otimes \Sym(\Cyc_*(A)[1-n])
-%\]
-%down to an $E_n$ algebra.
-%
-%When $k$ is $\RR$ or $\CC$, this centralizer is modeled by the locally constant factorization algebra that assigns
-%\[
-%\clies(\sl_\infty(\Omega^*(U)))\otimes \Sym(\Cyc_*(A \otimes \Omega^*_c(U))[1])
-%\]
-%to each open set $U \subset \RR^n$.
-%\end{thm}
-%\greg{Shall we keep these examples which uses/but are the easy part/ of LQT theorem ?}
-%\owen{We should write explicitly what happens in the case $A = k$, and maybe $n=1$.}
-%
-%We can calculate the factorization homology of this factorization algebra explicitly.
-%
 
@@
 
-See Remark 7.3.5.3 of \cite{LurieHA}, Coroallary 13 in~\cite{GG-Notes} and Section 2 of \cite{FrancisHH}.
+See Remark 7.3.5.3 of \cite{LurieHA}, Corollary 13 in~\cite{GG-Notes} and Section 2 of \cite{FrancisHH}.
 Concretely, this claim arises from the fact that as a module over $A$ as an $E_n$ algebra, 
@@
 
-\owen{I commented out a discussion of the factorization algebra version of centralizer, as I don't think it's relevant.}
-
-%
-%There is an immediate analogue of the notion of centralizers for factorization algebras.
-%\begin{dfn}\label{D:centralizerFacAlgebra}
-% Let $X$ be a manifold and  $f: A(-) \to B(-)$ be a map of locally constant factorization algebras over $X$.  
-%The {\em centralizer} ${\frak Z}(\mathbf{f})(-)$ is the locally constant factorization
-%algebra over $X$ in $\cC$ that is universal among those that fit in a commuting diagram
-%\[
-%\begin{tikzcd}
-%& {\frak Z}(\mathbf{f}) \otimes A(-) \arrow[dr] & \\
-%A(-) \arrow[ur, "u"] \arrow[rr, "f"] && B(-)
-%\end{tikzcd}
-%\]
-%where $u$ is induced by the canonical map $1_\cC= {\frak Z}(\mathbf{f})(\emptyset) \to {\frak Z}(\mathbf{f})(-)$ induced by the inclusion of the emptyset.
-The {\em center} of a locally constant  factorization algebra
-%$A(-)$ is the centralizer of its identity morphism $\id: A(-) \to A(-)$.
-%\end{dfn}
-%By Theorem~\ref{T:En=Fac} and Proposition~\ref{T:centralizer=inthom} (also see~\cite{GTZ3}) we get
-%\begin{lmm}\label{L:faccentralizerexists}
-% Let $X=\RR^n$. Then a centralizer of $f: A(-)\to B(-)$ exists for any morphism of locally constant factorization algebras over $X$. Further, if the above map is induced by 
-% an $E_n$-algebra morphism $f:A\to B$, then 
-% ${\frak Z}(\mathbf{f})(-)$ is the locally constant factorization algebra over $\RR^n$ associated to 
-% the $E_n$-algebra ${\frak Z}_{E_n}(f)$.
-%\end{lmm}
-%
-
-%We now turn to proving Theorem~\ref{thm: centralizer}.
-
-\section{Lifting $B$ to an $E_n$ algebra $B_f$ in $\fg$-modules}
-
-A technical result is the key step.
-
-\def\obl{{\rm obl}}
-
-\begin{prp}
-\label{prp: def of obl}
-For $\fg$ a dg Lie algebra in $\Ch_k^{\otimes_k}$, i.e., a dg Lie algebra, 
-there is a forgetful functor $\obl: \Mod^{E_n}_{\UU_n \fg} \to \LMod_{U\fg}$ that is lax $E_n$-monoidal.
-\end{prp}
-
-\owen{I don't know if we need to include the adjective ``lax'' here, or if it's implicit in the usual discussions these days.}
-
-Concretely, we mean there is a natural morphism
-\[
-\obl(M) \otimes_k \obl \to \obl(M \otimes_{\UU_n \fg} N) 
-\]
-as left modules over $U\fg$, i.e., as $\fg$-representations.
-
-As a consequence, we obtain the following.
-
+We now turn to proving Theorem~\ref{thm: centralizer}.
+
+\section{}
+
+The lemma allows us to define the factorization algebra given on any open $U$ by  the Chevalley-Eilenberg chain complexes
+$ \cliels\big(\fg \otimes \Omega^*_c(U), B(U) \big)$ (with their standard differential)
+of $\fg \otimes \Omega^*_c(U)$ with value on $B(U)$ whose structure maps are given, for any $(U_i)_{i\in I}$ 
+a finite family of pairwise disjoint open subsets of an open $V$, by 
+\begin{multline}\label{eq:transClieFac}
+ \bigotimes_{i\in I} \cliels\big(\fg \otimes \Omega^*_c(U_i), B(U_i) \big) \cong Sym\Big(
+ \fg\otimes (\bigoplus_{i\in I}  \Omega^*_c(U_i))[-1]  \Big) \otimes \Big( \bigotimes_{i\in I} B(U_i)\Big) \\ 
+ \cong Sym\Big(\fg\otimes \Omega_c\big(\coprod U_i\big)[-1] \Big) \otimes \Big( \bigotimes_{i\in I} B(U_i)\Big)  
+ \stackrel{\omega^*\otimes \mu_B}\longrightarrow Sym(\fg\otimes \Omega_c(V)[-1] ) \otimes B(V) \\ 
+ = \cliels(\fg\otimes \Omega_c(V), B(V))
+\end{multline}
+where $\omega$ is induced by the cosheaf structure of compactly supported form and $\mu_B$ is the factorization algebra structure of $B(-)$.
+
+\smallskip
+
+The (homotopy) sheaf structure of forms also gives us structure maps
+\begin{multline}\label{eq:transClieFacCochain}
+ \bigotimes_{i\in I} \clies\big(\fg \otimes \Omega^*(U_i), B(U_i) \big) \longrightarrow
+  \Hom\Big(Sym\big(\fg\otimes (\bigoplus_{i\in I}  \Omega^*(U_i))[-1]\big),  \bigotimes\limits_{i\in I} B(U_i) \Big) \\
+ \cong \Hom\Big(Sym\big(\fg\otimes \Omega^*(\coprod U_i)[-1]\big), \bigotimes\limits_{i\in I} B(U_i) \Big) \\
+ \stackrel{\rho}\longrightarrow \Hom\Big(Sym\big(\fg\otimes \Omega^*(V)[-1]\big), \bigotimes\limits_{i\in I} B(U_i) \Big) \\
+ \stackrel{\mu_B}\longrightarrow 
+  \clies(\fg\otimes \Omega (V), B(V))
+\end{multline}
+where $\rho$ is given by the restriction of forms onto a subspace.
+
+\label{L:ClieFacDef} 
+ Similarly, the structure maps~\eqref{eq:transClieFacCochain} makes 
+ $ \clies\big(\fg \otimes \Omega^*(-), B(-) \big)$ a (resp. locally constant) factorization algebra.
+
+\begin{dfn}\label{dfn:CEofFact}
+We {call   $\cliels\big(\fg \otimes \Omega^*_c(-), B(-) \big)$ the Chevalley-Eilenberg chain factorization algebra of $\fg$ with value in $B(-)$} 
+and $\clies\big(\fg \otimes \Omega^*(-), B(-) \big)$ the Chevalley-Eilenberg cochain factorization algebra.
+\end{dfn}
+\begin{proof}
+
+\end{proof}
+
+A special but very interesting case is of course when $B$ is itself an enveloping algebra. 
 \begin{cor}
-There is a functor 
-\[
-\Alg_{E_n}(\obl): \Alg_{E_n}({\Mod^{E_n}_{\UU_n \fg}}) \to \Alg_{E_n}(\LMod_{U\fg}).
-\]
+ Let $\fg$, $\fh$ be dg-Lie algebras and $f:\fg\to \fh$ be a dg-Lie algebra morphism. 
+ Then the induced factorization algebra map $\mathbf{\UU_n f}:  \cliels( \fg \otimes \Omega^*_c(-)) \longrightarrow  \cliels( \fh \otimes \Omega^*_c(-)) $
+ is the standard map $\cliels(f)$ induced by $f$ and the action of $\fg  \otimes \Omega^*_c(-)$ is obtained from the $\fg$-action on $\fh$ by Leibniz rule.
 \end{cor}
-
-These results can be marshaled to prove the first bullet point of our main theorem.
-
-\begin{prp}
-Let $\fg$ be a Lie algebra in $\Ch_k^{\otimes_k}$, 
-and let $B$ be an $E_n$ algebra in $\Ch_k^{\otimes_k}$.
-Given a map of $E_n$ algebras $f: \UU_n \fg \to B$, 
-there exists a lift of $B$ to an $E_n$ algebra $B_f$ in $\Mod_\fg(\Ch_k^{\otimes_k})^{\otimes_k}$, the symmetric monoidal $\infty$-category of $\fg$-modules.
-\end{prp}
-
-That is, the forgetful functor $\Mod_\fg(\Ch_k^{\otimes_k})^{\otimes_k} \to \Ch_k^{\otimes_k}$ sends $B_f$ to~$B$.
-
-\begin{proof}
-By Corollary 3.4.4.6 of \cite{LurieHA}, any $E_n$ algebra $B$ defines an $E_n$-monoidal category ${\rm Mod}_B^{E_n} (\Ch_k^{\otimes k})$ of $E_n$-$B$-modules with monoidal structure $\otimes_B$. 
-Furthermore, by Corollary 3.4.1.7 \cite{LurieHA} $B$ can be viewed as an $E_n$-algebra in this $E_n$-monoidal category. 
-(See also Example 3.4.4.7 of the same reference.)
-In other words, there is an object $\Hat{B} \in  {\rm Mod}_B^{E_n} (\Ch_k^{\otimes k})$ sent to $B$ under the forgetful functor ${\rm Mod}_B^{E_n} (\Ch_k^{\otimes k}) \to \Ch_k^{\otimes_k}$.
-
-Given a map of $E_n$-algebras $f : A \to B$, 
-the forgetful functor of $E_n$-module categories 
-\[
-f^* :  {\rm Mod}_B^{E_n} (\Ch_k^{\otimes_k}) \to  {\rm Mod}_A^{E_n} (\Ch_k^{\otimes_k}) .
-\]
-admits a natural refinement to an $E_n$-monoidal functor.
-\owen{Any place to cite?}
-In particular, for $A = \UU_n \fg$, there is an $E_n$-algebra object $f^*\Hat{B} \in {\rm Mod}_{\UU_n \fg}^{E_n} (\Ch_k^{\otimes k})$, and it forgets to $B$ under the forgetful functor to $\Ch_k^{\otimes_k}$, by construction.
-
-Applying the $E_n$-monoidal functor $\obl$, we obtain an $E_n$ algebra $\obl(f^*\Hat{B})$ in $\Mod_\fg(\Ch_k^{\otimes_k})^{\otimes_k}$.
-Again, by construction, it forgets to $B$.
-We denote $\obl(f^*\Hat{B})$ by~$B_f$.
-\end{proof}
-
-\begin{rmk}
-By the strictification results, $B_f$ admits a model ${\tt B}_f$ as a strict prefactorization algebra with values in the stable symmetric monoidal \owen{other adjectives} model category $\Alg_\Lie(\Ch_k^{\rm dg})$.
-As the forgetful functor $\Alg_\Lie({\tt Ch}_k) \to \Alg_\Lie({\tt Ch}_k)$ is \owen{more adjectives},
-we obtain an underlying strict prefactorization algebra ${\tt B}$ with values in cochain complexes.
-Moreover, there is a canonical map ${\tt U}_n \fg \to {\tt B}$ of strict prefactorization algebras that models $f$, as desired.
+\begin{rmk}\greg{Extends to $L_\infty$ case in a sentence or too}
 \end{rmk}
 
-It remains to prove the technical result.\owen{We are stuck on this point.}
-
-\begin{proof}[Proof of proposition~\ref{prp: def of obl}]
-We construct the underlying functor of $\infty$-categories $\Mod^{E_n}_{\UU_n \fg} \to \LMod_{U\fg}$ 
-before lifting to a lax $E_n$-monoidal functor.
-
-For any $E_n$-algebra the factorization homology along the $(n-1)$-sphere $\int_{S^{n-1}} A$ is an $E_1$-algebra.
-By Proposition 3.33 of \cite{FrancisHH} (see also Example 5.5.4.16 of \cite{LurieHA}), 
-there is an equivalence of $\infty$-categories ${\rm Mod}^{E_n}_A (\Ch_k^{\otimes_k}) \simeq {\rm LMod}_{\int_{S^{n-1}} A} (\Ch_k^{\otimes_k})$.
-For $A = \UU_n \fg$, the factorization homology along the $(n-1)$-sphere is 
-\[
-\int_{S^{n-1}} A \simeq \UU_1 \left(\fg[\epsilon] \right),
-\] 
-where $\epsilon$ is a formal parameter of cohomological degree $n-1$.
-It follows that there is an equivalence of $\infty$-categories 
-\[
-{\rm Mod}_{\UU_n \fg}^{E_n} (\Ch_k^{\otimes_k}) \simeq {\rm LMod}_{\UU_1(\fg[\epsilon])} (\Ch_k^{\otimes_k}).
-% = {\rm Mod}_{\fg[\epsilon]} (\Ch_k^{\otimes_k}) .
-\]
-Consider now the map of Lie algebras $i : \fg \hookrightarrow \fg[\epsilon]$,
-which induces a forgetful functor $i^* :  {\rm Mod}_{\fg[\epsilon]} (\Ch_k^{\otimes_k})  \to  {\rm Mod}_{\fg} (\Ch_k^{\otimes_k})$. 
-The composite 
-\[
-{\rm Mod}_{\UU_n \fg}^{E_n} (\Ch_k^{\otimes_k}) \simeq {\rm LMod}_{\UU_1(\fg[\epsilon])} (\Ch_k^{\otimes_k}) \xto{i^*}  {\rm LMod}_{U\fg} (\Ch_k^{\otimes_k})
-\]
-is the desired forgetful functor.
-
-\owen{Now we need to explain why it is lax monoidal.}
-\end{proof}
-
-%\section{Strictifying the map $f: \UU_n \fg \to B$}
-%
-%
-%\owen{If our new strategy works, then we can get rid of this section.}
-%
-%As a first step, we analyze the strictification of the map $f: \UU_n \fg \to B$ and show how it lets us view $B$ as an $E_n$ algebra in~$\Ch(\Rep(\fg))$.
-%
-%By using the small model \owen{see my comment \ref{note on little model}}, we can strictify to obtain a map
-%\[
-%{\tt f}: \cliel(\fg[-n]) \to {\tt B}.
-%\]
-%
-%\owen{And now I'm really confused.}
-%
-%\owen{I'm not wild about Greg's phrasing below. Also, I'd prefer to move the explicit formulas later, when we've shifted our setting to strict prefactorization algebras.}
-%
-%
-%\begin{rmk}
-%It follows from theorem~\ref{T:UnofLie} that for any $E_n$-algebra $B$, 
-%the underlying complex of the $L_\infty$-algebra $\oblv_n(B)$ is naturally quasi-isomorphic to $\Sigma^{n-1}B = B[n-1]$. 
-%Henceforth in this paper, we will simply use the notation $B[n-1]$ for $\oblv_n(B)$, 
-%that is tacitly assume we $B[n-1]$ is endowed with the $L_\infty$structure induced by its $E_n$ algebra structure.
-%\end{rmk}
-%
-%Let  $f:\UU_n \fg \to B$ be an $E_n$-algebra map. Then the adjunction 
-%\[
-%\xymatrix{\Alg_\Lie(\Mod_k) \ar@/^/[r]^{\UU_n} & \ar[l]^{\oblv_n}  \Alg_{E_n}(\Mod_k)}
-%\]
-%gives a $L_\infty$-algebra morphism 
-%\begin{equation}
-% \tilde{f}: \fg \, \longrightarrow \, \oblv(B)\cong B[n-1]
-%\end{equation}
-%which makes $B[n-1]$ into a $\fg$-module and therefore its shift $B$ inherits a  $\fg$-module structure as well from $f$.
-%
-%\brian{let's start with a strict representative $B$. 
-%So we have an actual locally constant factorization algebra.}
-%
-%\begin{prp}\label{P:inducedEngModStruct} Let $f:\UU_n \fg \to B$ be an $E_n$-algebra morphism. 
-%The induced $\fg$ $L_\infty$-module on $B$ lifts canonically to make  $B$ into an $E_n$-algebra in the category of $\fg$-modules that we denote by $B_f$. 
-%\end{prp}
-%\begin{proof}
-% 
-%\end{proof}
-%Proposition~\ref{P:inducedEngModStruct} has an easy realization in the factorization algebra setting.
-%Indeed, applying the equivalence of $E_n$-algebras with locally constant factorization algebras (Theorem~\ref{T:En=Fac}), 
-%we obtain an induced map of factorization 
-%algebras 
-%\begin{equation}\label{eq:DefofFonFaclevel}
-% \mathbf{f}: \cliels( \fg \otimes \Omega^*_c(-)) \longrightarrow B(-)
-%\end{equation}
-% where $B(-)$ is the factorization algebra associated to $B$.
-% \brian{How about $\ul{B}$ instead?}
-% 
-%\begin{lmm}\label{L:inducedFacgModstruct} The factorization algebra map  $\mathbf{f}$ makes $B(-)$ into an homotopy cosheaf of $L_\infty$-modules over 
-% $\fg \otimes \Omega^*_c(-)$.
-%\end{lmm}
-%\begin{proof}
-% 
-%\end{proof}
-%The lemma allows us to define the factorization algebra given on any open $U$ by  the Chevalley-Eilenberg chain complexes
-%$ \cliels\big(\fg \otimes \Omega^*_c(U), B(U) \big)$ (with their standard differential)
-%of $\fg \otimes \Omega^*_c(U)$ with value on $B(U)$ whose structure maps are given, for any $(U_i)_{i\in I}$ 
-%a finite family of pairwise disjoint open subsets of an open $V$, by 
-%\begin{multline}\label{eq:transClieFac}
-% \bigotimes_{i\in I} \cliels\big(\fg \otimes \Omega^*_c(U_i), B(U_i) \big) \cong Sym\Big(
-% \fg\otimes (\bigoplus_{i\in I}  \Omega^*_c(U_i))[-1]  \Big) \otimes \Big( \bigotimes_{i\in I} B(U_i)\Big) \\ 
-% \cong Sym\Big(\fg\otimes \Omega_c\big(\coprod U_i\big)[-1] \Big) \otimes \Big( \bigotimes_{i\in I} B(U_i)\Big)  
-% \stackrel{\omega^*\otimes \mu_B}\longrightarrow Sym(\fg\otimes \Omega_c(V)[-1] ) \otimes B(V) \\ 
-% = \cliels(\fg\otimes \Omega_c(V), B(V))
-%\end{multline}
-%where $\omega$ is induced by the cosheaf structure of compactly supported form and $\mu_B$ is the factorization algebra structure of $B(-)$.
-%
-%\smallskip
-%
-%The (homotopy) sheaf structure of forms also gives us structure maps
-%\begin{multline}\label{eq:transClieFacCochain}
-% \bigotimes_{i\in I} \clies\big(\fg \otimes \Omega^*(U_i), B(U_i) \big) \longrightarrow
-%  \Hom\Big(Sym\big(\fg\otimes (\bigoplus_{i\in I}  \Omega^*(U_i))[-1]\big),  \bigotimes\limits_{i\in I} B(U_i) \Big) \\
-% \cong \Hom\Big(Sym\big(\fg\otimes \Omega^*(\coprod U_i)[-1]\big), \bigotimes\limits_{i\in I} B(U_i) \Big) \\
-% \stackrel{\rho}\longrightarrow \Hom\Big(Sym\big(\fg\otimes \Omega^*(V)[-1]\big), \bigotimes\limits_{i\in I} B(U_i) \Big) \\
-% \stackrel{\mu_B}\longrightarrow 
-%  \clies(\fg\otimes \Omega (V), B(V))
-%\end{multline}
-%where $\rho$ is given by the restriction of forms onto a subspace. 
-%
-%\begin{lmm}\label{L:ClieFacDef} For any (resp. locally constant) factorization algebra $B(-)$ and factorization algebra map $\mathbf{f}:\UU_n(\fg) \to B(-)$, 
-% the structure maps~\eqref{eq:transClieFac} makes $ \cliels\big(\fg \otimes \Omega^*_c(-), B(-) \big)$ a (resp. locally constant) factorization algebra.
-% Similarly, the structure maps~\eqref{eq:transClieFacCochain} makes 
-% $ \clies\big(\fg \otimes \Omega^*(-), B(-) \big)$ a (resp. locally constant) factorization algebra.
-%\end{lmm}
-%\begin{dfn}\label{dfn:CEofFact}
-%We {call   $\cliels\big(\fg \otimes \Omega^*_c(-), B(-) \big)$ the Chevalley-Eilenberg chain factorization algebra of $\fg$ with value in $B(-)$} 
-%and $\clies\big(\fg \otimes \Omega^*(-), B(-) \big)$ the Chevalley-Eilenberg cochain factorization algebra.
-%\end{dfn}
-%\begin{proof}
-% 
-%\end{proof}
-%
-%
-%A special but very interesting case is of course when $B$ is itself an enveloping algebra. 
-%\begin{cor}
-% Let $\fg$, $\fh$ be dg-Lie algebras and $f:\fg\to \fh$ be a dg-Lie algebra morphism. 
-% Then the induced factorization algebra map $\mathbf{\UU_n f}:  \cliels( \fg \otimes \Omega^*_c(-)) \longrightarrow  \cliels( \fh \otimes \Omega^*_c(-)) $
-% is the standard map $\cliels(f)$ induced by $f$ and the action of $\fg  \otimes \Omega^*_c(-)$ is obtained from the $\fg$-action on $\fh$ by Leibniz rule.
-%\end{cor}
-%\begin{rmk}\greg{Extends to $L_\infty$ case in a sentence or too}
-%\end{rmk}
-%
-
-%\section{Convolution algebras over colored operads}
-%
-%\def\conv{{\rm Conv}}
-%
-%\owen{For an ordinary colored operad $\cO$, describe how to produce a $\cO$-algebra $\conv(C,A)$ from any $\cO$-coalgebra $C$ and $\cO$-algebra $A$.}
-%
-%\owen{A special case to consider is how a cocycle $f \in \conv(C,A)$ encodes an $\cO$-algebra morphism $C^!
+\section{Convolution algebras over colored operads}
+
+\def\conv{{\rm Conv}}
+
+\owen{For an ordinary colored operad $\cO$, describe how to produce a $\cO$-algebra $\conv(C,A)$ from any $\cO$-coalgebra $C$ and $\cO$-algebra $A$.}
+
+\owen{A special case to consider is how a cocycle $f \in \conv(C,A)$ encodes an $\cO$-algebra morphism $C^!
 \to A$ from $C^!
@@
 Hopefully this admits an obvious deformation-theoretic interpretation.}
-%
-%\owen{If we do this correctly, we might find a model category-theoretic picture of how Koszul duality works for prefactorization algebras.}
+
+\owen{If we do this correctly, we might find a model category-theoretic picture of how Koszul duality works for prefactorization algebras.}
 
@@
 
-\owen{Commented below is Greg's summary of the proof.}
-
-%Let us start by summarizing the proof. The idea, using theorem~\ref{T:En=Fac}, 
-%is that we only have to prove the factorization algebra part of the main theorem. 
-%To do so, we first use the universal property of the centralizer to obtain 
-%a canonical factorization algebra map 
-%\[\Theta_f: \clies\big(\fg\otimes \Omega (-), B(-) \big) \longrightarrow  {\frak Z}(\mathbf{f})(-)\]
-%where ${\frak Z}(\mathbf{f})(-)$ is the centralizer of locally constant factorization algebras (\ref{D:centralizerFacAlgebra}).
-%
-%
-%Using the fundamental properties of universal $E_n$-enveloping algebra, we then prove that 
-%this map is a weak-equivalence. 
-%
-%\smallskip 
-%
-%We thus let $\mathbf{f}: \cliels\big(\fg \otimes \Omega^* (-)) \to B(-)$ be a factorization algebra map (see~\eqref{eq:DefofFonFaclevel}). We can 
-%assume that the structural (natural) quasi-isomorphism
-%$$\bigotimes_{i\in I} B(U_i) 
-%\stackrel{\simeq}\longrightarrow B(\coprod  U_i)$$ are chain complexes isomorphisms by replacing $B(-)$ by the prefactorization algebra 
-%given, on any $V=\coprod_{j\in J} V_j$, where the $V_j$ are the connected components of $V$, by   $\mathop{\bigotimes}\limits_{j\in J} B(V_j)$. 
-%The structural maps of $B$ are then a quasi-isomorphism of prefactorization algebras between it and $B(-)$. The map $\mathbf{f}$ is lifted similary using 
-%the isomorphism $\bigotimes_{i\in I} \cliels\big(\fg \otimes \Omega_c^* (U_i)\big) \cong
-%\cliels\big(\fg \otimes \Omega_c^* (U)\big)$ as well. We assume we have this property in the rest of this section.
-%\greg{Technically we may need to replace the latter by a quasi-isomorphic one satisfying the same property to ensure we do have a strict fact algebra map. 
-%Not sure if we should elaborate on it more since in the end we only need that to obtain lemma~\ref{L:inducedFacgModstruct} to make the construction valid 
-%and therefore only use the induced sym on the cosheaf of $L_\infty$-module maps}
+\owen{Below is Greg's summary of the proof.}
+
+Let us start by summarizing the proof. The idea, using theorem~\ref{T:En=Fac}, 
+is that we only have to prove the factorization algebra part of the main theorem. 
+To do so, we first use the universal property of the centralizer to obtain 
+a canonical factorization algebra map 
+\[\Theta_f: \clies\big(\fg\otimes \Omega (-), B(-) \big) \longrightarrow  {\frak Z}(\mathbf{f})(-)\]
+where ${\frak Z}(\mathbf{f})(-)$ is the centralizer of locally constant factorization algebras (\ref{D:centralizerFacAlgebra}).
+
+Using the fundamental properties of universal $E_n$-enveloping algebra, we then prove that 
+this map is a weak-equivalence.
+
+\smallskip
+
+We thus let $\mathbf{f}: \cliels\big(\fg \otimes \Omega^* (-)) \to B(-)$ be a factorization algebra map (see~\eqref{eq:DefofFonFaclevel}). We can 
+assume that the structural (natural) quasi-isomorphism
+$$\bigotimes_{i\in I} B(U_i) 
+\stackrel{\simeq}\longrightarrow B(\coprod  U_i)$$ are chain complexes isomorphisms by replacing $B(-)$ by the prefactorization algebra 
+given, on any $V=\coprod_{j\in J} V_j$, where the $V_j$ are the connected components of $V$, by   $\mathop{\bigotimes}\limits_{j\in J} B(V_j)$. 
+The structural maps of $B$ are then a quasi-isomorphism of prefactorization algebras between it and $B(-)$. The map $\mathbf{f}$ is lifted similary using 
+the isomorphism $\bigotimes_{i\in I} \cliels\big(\fg \otimes \Omega_c^* (U_i)\big) \cong
+\cliels\big(\fg \otimes \Omega_c^* (U)\big)$ as well. We assume we have this property in the rest of this section.
+\greg{Technically we may need to replace the latter by a quasi-isomorphic one satisfying the same property to ensure we do have a strict fact algebra map. 
+Not sure if we should elaborate on it more since in the end we only need that to obtain lemma~\ref{L:inducedFacgModstruct} to make the construction valid 
+and therefore only use the induced sym on the cosheaf of $L_\infty$-module maps}
 
@@
 
-\section{Factorization algebra description of the center}\label{S:centerinFacAlg}
+\owen{Commented out here is a discussion of centers. We may want to resurrect it but it doesn't seem essential to the main results.}
+
+\section{Factorization algebra description of the center}
+\label{S:centerinFacAlg}
+
 The universal property of centralizer (definition~\ref{D:centralizer}) implies that, for any $E_n$-algebras maps $A\stackrel{f}\to B$ and
@@
 
-\greg{To add: remark taht it implies the corollary~\ref{thm: center} and so.}
-
-\section{Leftover stuff}
-
-\owen{I took the following out of Greg's version of the "main theorem" section}
-
-To any $\fg$-module $M$ (wether $\fg$ is a dg Lie algebra or an $L_\infty$-algebra), 
-we can associate its Chevalley-Eilenberg cochain complex defined 
-by 
-\begin{equation}
- \clies(\fg, M) = \Hom (Sym(\fg[-1]), M)
-\end{equation}
-with its classical differential. 
-\greg{recall....quickly. AT least for dg-part. Say something for $L_\infty$ too}
-We have the evaluation map 
-\begin{equation}
- \label{eq:defev} ev: \clies(\fg, M) \otimes Sym(\fg[-1])\to M
-\end{equation}
-given by applying a function on a given tensor in $Sym(\fg[-1])$.
-
-\begin{dfn}\label{D:convolutionalgebraCE}Let $\fg$ be a dg Lie (or $L_\infty$)-algebra and $B$ be an $E_n$-algebra in $\fg$-modules,
-that is an object of the $\infty$-category 
-$E_n-Alg(Mod_{\fg})$. Its associated convolution $E_n$-algebra structure on  $\clies(\fg, B) = \Hom (Sym(\fg[-1]), B)$ is obtained by 
- taking the \emph{convolution} between the cocommutative symmetric coalgebra $Sym(\fg[-1])$ (forgetted to an $E_n$-coalgebra) and the $E_n$-algebra $B$.
-\end{dfn}
-\greg{Probably need somewhere to say what means $E_n-Alg(Mod_{\fg})$ and find a less ugly notation for it}
-Precisely, given an explicit $E_n$-operad $D_n$ in chain complexes and $(B, \mu^B)$ a $D_n$-algebra, 
-the convolution structure is given by the following composition
-\begin{multline}
- \Big(D_n(r)\otimes \clies(\fg, B)^{\otimes r} \Big)\otimes Sym(\fg[-1])\\ \stackrel{id\otimes id \otimes\Delta^{(r-1)}}\longrightarrow 
- D_n(r)\otimes \clies(\fg, B)^{\otimes r} \otimes Sym(\fg[-1])^{\otimes r} 
- \stackrel{id \otimes (ev^{\otimes r})}\longrightarrow D_n(r)\otimes B^{\otimes r} 
- \stackrel{\mu_\sigma^B}\longrightarrow B.
-\end{multline}
-where $\Delta$ is the cocommutative comultiplication.
-In plain formula,
-for any $\sigma \in D_n(r)$ and $\phi_1,\dots, \phi_r \in 
-\clies(\fg, B)$, their multiplication (parametrized by $\sigma$) is  given by 
-\begin{equation}
- \mu_\sigma (\phi_1,\dots, \phi_r): Sym(\fg[-1]) \ni x \mapsto \pm \mu^B_{\sigma} \big(\phi_1(x^{(1)}), \dots, \phi_r(x^{(r)})\big)
-\end{equation}
-where $x\mapsto x^{(1)}\otimes \cdots x^{(r)}$ is the usual $r$-fold cocommutative comultiplication.
-Note that here, we are using the usual Koszul sign  convention.
-
-\begin{lmm}
- $\clies(\fg, M) = \Hom (Sym(\fg[-1]), B)$ is a $E_n$-algebra, naturally in $\fg$ and $B$.
-\end{lmm}
+\greg{To add: remark that it implies the corollary~\ref{thm: center} and so.}
 
@@
 
-%We briefly remark on a natural modification of the prefactorization algebra $\Sym(\cC_A)$. 
-%For simplicity, suppose $A$ is an ordinary (non dg) algebra, and let $\chi \in \Cyc^m(A)$ be a cyclic {\em cocycle} of degree $m$.
-%Consider for each open $U \subset \RR^n$ the cochain complex
-%\[
-%\Tilde{\cC}_{A,\chi} (U) = \left(\Cyc_*(A \tensor \Omega^*_c(U))[1] \oplus \CC \cdot K , \d_{\rm Cyc} + K \cdot \chi \right) 
-%\]
-%where $K$ is a formal parameter of degree $-m+n+1$.
-%Also, $\d_{\rm Cyc}$ is the cyclic differential and $\chi$ is defined on $m$-chains by the pairing between cyclic chains and cochains, together with integration along $U$:
-%\[
-%\chi ((a_1 \otimes \alpha_1) \tensor \cdots \tensor (a_m \otimes \alpha_m)) = \int_U \<\chi, a_1 \tensor \cdots \tensor a_m\> \alpha_1 \wedge \cdots \wedge \alpha_m.
-%\]
-%The differential is extended to the entire cochain complex by the graded Leibniz rule. 
-%By similar arguments as above, the assignment $U \subset \Tilde{\cC}_{A, \chi}$ is a precosheaf of cochain complexes and $\Sym\left(\Tilde{\cC}_{A,\chi}\right)$ is a prefactorization algebra. 
-%As a precosheaf of graded vectors spaces one has $\Tilde{\cC}_{A, \chi} = \cC_A \oplus \ul{\CC}[m-n-1]$, where $\ul{\CC}$ is the constant precosheaf, so that we may think of $\Sym\left(\Tilde{\cC}_{A,\chi}\right)$ as a twisted version of $\Sym(\cC_A)$.
-%These types of twisted \brian{what to say? check my degrees!}
-%
-
 \bibliographystyle{alpha}  

### 2020-09-01 draft.tex
TFT

--- 2020-08-31 draft.tex
@@
 
-\section{Factorization algebras that model centralizers}
-
-\section{Examples}
-
-\greg{Add the Koszul duality example. Add examples coming from topological spaces and abelian Lie algebras}
-
-\subsection{Koszul duality}
-\label{sec: Koszul}
-
-Consider the trivial $E_n$-algebra $k$ and suppose $\varepsilon : \UU_n \fg \to k$ is the natural augmentation. 
-Then, ${\frak Z}_n (\varepsilon)$ is the $E_n$-{\em Koszul dual} of the $E_n$-algebra $\UU_n \fg$. 
-Our results provide a model for this $E_n$-algebra as a locally constant factorization algebra on $\RR^n$ which assigns to an open set $U \subset \RR^n$ the cochain complex
-\[
-\clie \left(\fg \otimes \Omega(U) \right) .
-\]
-
-\subsection{Universal bulk TFT}
+\section{Universal bulk TFT}
 \label{sec: TFT}
 
-Generally speaking, the local observables of a topological field theory on a manifold $M$ form a locally constant factorization algebra on $M$.
-
-Let $\fg$ be a dg Lie algebra and consider the $E_n$ algebra $\UU_n \fg$. 
-We have shown that a model for the $E_n$-center ${\frak Z}_n (\UU_n \fg) = {\frak Z}_n ({\rm id}_{\UU_n \fg})$ is the $n$-dimensional locally constant factorization algebra 
-\[
-\clie \left( \fg \otimes \Omega \; , \; \clieu (\fg \otimes \Omega_c) \right)  .
-\]
-
-Let us place this locally constant factorization algebra on the $n$-manifold $M$.
-This factorization algebra is equivalent to the pushforward of a factorization algebra $\cF_{\rm bulk}$ on the $(n+1)$-dimensional manifold $M \times \RR$ along the projection $\pi : M \times \RR \to M$.
-We proceed to construct this factorization algebra.
-
-For an open set $V \subset M \times I$ let $\cF^{\rm cl}_{\rm bulk} (V)$ be the cochain complex 
-\[
-\cF^{\rm cl}_{\rm bulk} (V) = \clie \bigg(\fg \otimes \Omega (V) \; , \; \Sym \left(\fg \otimes \Omega_c(V) [2] \right) \bigg) .
-\]
-The assignment $V \mapsto \cF^{\rm cl}_{\rm bulk}(V)$ defines a locally constant factorization algebra $\cF^{\rm cl}_{\rm bulk}$ on $M \times \RR$.
-
-The factorization algebra $\pi_* \cF^{\rm cl}_{\rm bulk}$ on $M$ is quasi-isomorphic to a certain limit, or ``deqauntization", of the $E_n$-center of $\UU_n \fg$. 
+Generally speaking, the local observables of a topological field theory on a manifold $M$ define a locally constant factorization algebra on $M$.
+
+\begin{thm}
+Let $M$ be a smooth $n$-manifold and $\fg$ a Lie algebra. 
+There is a constructible factorization algebra on $M \times [0,1)$ satisfying the following properties:
+\begin{itemize}
+\item[(1)] On the $n$-dimensional stratum $M \times \{0\}$ the factorization algebra is equivalent to $\clieu (\fg \otimes \Omega_c)$.
+\item[(2)] On the $(n+1)$-dimensional stratum $M \times (0,1)$, the factorization algebra is a quantization of the observables of topological BF theory based on the Lie algebra $\fg$.
+\item[(3)] Locally on $\RR^n \times [0,1)$ this factorization algebra produces \brian{deligne picture how to say}
+\end{itemize}
+\end{thm}
+
+%Let $\fg$ be a dg Lie algebra and consider the $E_n$ algebra $\UU_n \fg$. 
+%We have shown that a model for the $E_n$-center ${\frak Z}_n (\UU_n \fg) = {\frak Z}_n ({\rm id}_{\UU_n \fg})$ is the $n$-dimensional locally constant factorization algebra 
+%\[
+%\clie \left( \fg \otimes \Omega \; , \; \clieu (\fg \otimes \Omega_c) \right)  .
+%\]
+
+\subsection{The bulk TFT}
+
+Let us place the locally constant factorization algebra module the $E_n$-enveloping algebra $\clieu(\fg \otimes \Omega_c)$ on the $n$-manifold $M$.
+This factorization algebra is equivalent to the pushforward of a factorization algebra $\Obs_{\rm BF}$ on the $(n+1)$-dimensional manifold $M \times \RR$ along the projection $\pi : M \times (0,1) \to M$ which we proceed to construct.
+
+\begin{dfn}
+For an open set $V \subset M \times (0,1)$ let $\Obs^{\rm cl}_{\rm BF} (V)$ be the cochain complex 
+\[
+\Obs^{\rm cl}_{\rm BF} (V) = \clie \bigg(\fg \otimes \Omega (V) \; , \; \Sym \left(\fg \otimes \Omega_c(V) [2] \right) \bigg) .
+\]
+The assignment $V \mapsto \Obs^{\rm cl}_{\rm BF}(V)$ defines a locally constant factorization algebra on $M \times (0,1)$. 
+\end{dfn}
+
+We note that $\Obs_{\rm BF}^{\rm cl}$ is a factorization algebra with values in commutative dg algebras. 
+In fact, it is given by the ``classical observables" of a topological field theory on $M \times (0,1)$ known as ``topological BF theory".
+
+We now consider the pushforward factorization algebra $\pi_* \Obs^{\rm cl}_{\rm BF}$ on $M$.
+Locally, on disks, we will see that it is quasi-isomorphic to a certain limit, or ``dequantization", of our model for the $E_n$-center of $\UU_n \fg$.
+Recall, this model is given by the factorization algebra on $M$:
+\begin{equation}\label{eqn:centerTFT}
+\clie\left(\fg \otimes \Omega \, , \, \clieu (\fg \otimes \Omega_c) \right) .
+\end{equation}
+
+The ``dequantization" is defined using the following filtration of this model.
+For any Lie algebra $\fh$, let $\clieu_{\leq k} (\fh)$ be the subcomplex of Chevalley--Eilenberg chains which is $\Sym^{\leq k} (\fh[1])$ as an underlying graded vector space.
+
+\begin{dfn}
+Introduce the filtration on the factorization algebra on $M$ in (\ref{eqn:centerTFT}) by 
+\[
+F^k \bigg(\clie\left(\fg \otimes \Omega \, , \, \clieu (\fg \otimes \Omega_c) \right) \bigg) = \clie \bigg(\fg \otimes \Omega \; , \; \clieu_{\leq k} (\fg \otimes \Omega_c) \bigg) .
+\]
+\end{dfn}
+
+This is a filtration of factorization algebras on $M$. 
+The associated graded factorization algebra is
+\[
+{\rm Gr} \; \bigg(\clie\left(\fg \otimes \Omega \, , \, \clieu (\fg \otimes \Omega_c) \right) \bigg) \; = \; \clie \bigg(\fg \otimes \Omega \; , \; \Sym \left(\fg \otimes \Omega_c [1] \right) \bigg) .
+\]
+Notice this is similar to the model $E_n$-center except we have turned off the Chevalley--Eilenberg differential on chains.
+
+ \begin{lmm}
+There is a quasi-isomorphism of commutative factorization algebras on $M$:
+\[
+\pi_* \Obs^{\rm cl}_{\rm BF} \; \xto{\simeq} \; {\rm Gr} \; \bigg(\clie\left(\fg \otimes \Omega \, , \, \clieu (\fg \otimes \Omega_c) \right) \bigg) .
+\]
+\end{lmm}
+
+In fact, we will show that this quasi-isomorphism is a deformation retraction.
+
+\begin{proof}
 To exhibit this quasi-isomorphism, we introduce the following cochain maps.
@@
 by $r_\phi (\alpha) = \alpha \wedge \phi \, \d t$. 
-
-The ``dequantization" of the $E_n$-center is defined using the following filtration of ${\frak Z}_n(\UU_n \fg)$.
-We for any Lie algebra $\fh$, let $\clieu_{\leq k} (\fh)$ be the subcomplex of Chevalley--Eilenberg chains which is $\Sym^{\leq k} (\fh[1])$ as an underlying graded vector space. 
-The increasing filtration for the $E_n$-center is defined by
-\[
-F^k {\frak Z}_n(\UU_n \fg) = \clie \bigg(\fg \otimes \Omega \; , \; \clieu_{\leq k} (\fg \otimes \Omega_c) \bigg) .
-\]
-This is a filtration of factorization algebras on $M$. 
-The associated graded factorization algebra is
-\[
-{\rm Gr} \;  {\frak Z}_n(\UU_n \fg)  = \clie \bigg(\fg \otimes \Omega \; , \; \Sym \left(\fg \otimes \Omega_c [1] \right) \bigg) .
-\]
-Notice this is similar to the model $E_n$-center except we have turned off the Chevalley--Eilenberg differential on chains.
-
-\begin{lmm}
-Integration along $\RR$ determines a quasi-isomorphism of factorization algebras on $M$:
-\[
-\int_\RR : \pi_* \cF^{\rm cl}_{\rm bulk} \xto{\simeq} {\rm Gr} \;  {\frak Z}_n(\UU_n \fg) .
-\]
-In fact, this is a deformation retraction with retract given by $r_\phi$. 
-\end{lmm}
-
-\brian{Maybe you can finesse this last part better than me.}
+\end{proof}
 
@@
 %\end{proof}
+
+\section{Factorization algebras that model centralizers}
+
+\brian{Remark about twisting in the unoriented case.}
+
+\section{Examples}
+
+\greg{Add the Koszul duality example. Add examples coming from topological spaces and abelian Lie algebras}
+
+\subsection{Koszul duality}
+\label{sec: Koszul}
+
+Consider the trivial $E_n$-algebra $k$ and suppose $\varepsilon : \UU_n \fg \to k$ is the natural augmentation. 
+Then, ${\frak Z}_n (\varepsilon)$ is the $E_n$-{\em Koszul dual} of the $E_n$-algebra $\UU_n \fg$. 
+Our results provide a model for this $E_n$-algebra as a locally constant factorization algebra on $\RR^n$ which assigns to an open set $U \subset \RR^n$ the cochain complex
+\[
+\clie \left(\fg \otimes \Omega(U) \right) .
+\]
 

### 2020-09-01 draft.tex
slowly writing the main proof

--- 2020-09-01 draft.tex
@@
 
+\owen{Recall any relevant strictification results.}
+
 Note that in the theorem we use the following equivalence due to Lurie~\cite{LurieHA}.
@@
 When $k$ is $\RR$ or $\CC$, 
-the enveloping $E_n$ algebra $\UU_n \fg$ of a dg Lie algebra $\fg$ is modeled by the locally constant factorization algebra that assigns
-\[
-\cliels(\Omega^*_c(U) \otimes \fg)
-\]
-to each open set $U \subset \RR^n$.
+the enveloping $E_n$ algebra $\UU_n \fg$ of a dg Lie algebra $\fg$ is modeled by the locally constant factorization algebra $\bU_n \fg$ that assigns
+\[
+\bU_n \fg(V) = \cliels(\Omega^*_c(V) \otimes \fg)
+\]
+to each open set $V \subset \RR^n$.
 \end{thm}
@@
 \]
-where $u$ is induced by the identity map $1_\cC \to {\frak Z}_{E_n}(f)$.
-The {\em center} of an $E_n$ algebra $A$ is the centralizer of its identity morphism $\id_A: A \to A$. We will denote it ${\frak Z}_{E_n}(A) 
-:= {\frak Z}_{E_n}(\id_A)$.
+where $u$ is the tensor product of the unit map $1_\cC \to {\frak Z}_{E_n}(f)$ and the identity map $A \to A$.
+The {\em center} of an $E_n$ algebra $A$ is the centralizer of its identity morphism $\id_A: A \to A$. 
+We  denote it ${\frak Z}_{E_n}(A) := {\frak Z}_{E_n}(\id_A)$.
 \end{dfn}
@@
 
-\begin{prp}\label{T:centralizer=inthom} 
+\begin{prp}
+\label{T:centralizer=inthom} 
 The centralizer ${\frak Z}_{E_n}(f)$ exists and can be identified with the classifying object for maps from $A$ to $B$ in the $\infty$-category $\Mod^{E_n}_A(\cC)$.
@@
 
-\section{}
+\section{Proof of Theorem \ref{thm: centralizer}}
+
+We have implemented the first step in the proof strategy.
+This section is devoted to the remaining steps.
+First, we explain steps (2)-(4), which are rather formal.
+Next, we define the $\Disk_n$-algebra $\clies(\Omega^* \otimes \fg, {\tt B}_f)$ as a kind of convolution algebra.
+Finally, we get to the heart of the construction:
+we show that this convolution algebra naturally sits inside a centralizer diagram.
+By the universal property of the centralizer, we then obtain 
+a canonical map 
+\[
+\Theta_f: \clies\big(\fg\otimes \Omega , B \big) \longrightarrow  {\frak Z}(\mathbf{f})
+\]
+where ${\frak Z}(\mathbf{f})$ is the centralizer of locally constant $\Disk_n$-algebras~(\ref{D:centralizerFacAlgebra}).
+\owen{Calibrate notations!}
+It is then a direct computation to verify $\Theta_f$ is a quasi-isomorphism.
+
+\owen{Comment on notations:}
+As we work in the setting of factorization algebras on $\RR^n$, 
+we will use bold font to indicate such factorization models for $E_n$ algebra statements.
+For instance, we use $\bU_n \fg$ for the factorization model of the enveloping $E_n$ algebra,
+and we use $\bf{f}: \bU_n \fg \to \bU_n \fh$ for the factorization model of the map $f: \UU_n \fg \to \UU_n \fh$ of $E_n$ algebras.
+
+\owen{Below is Greg's summary of the proof.}
+
+Let us start by summarizing the proof. The idea, using theorem~\ref{T:En=Fac}, 
+is that we only have to prove the factorization algebra part of the main theorem. 
+To do so, we first use the universal property of the centralizer to obtain 
+a canonical factorization algebra map 
+\[\Theta_f: \clies\big(\fg\otimes \Omega , B \big) \longrightarrow  {\frak Z}(\mathbf{f})\]
+where ${\frak Z}(\mathbf{f})$ is the centralizer of locally constant factorization algebras (\ref{D:centralizerFacAlgebra}).
+
+Using the fundamental properties of universal $E_n$-enveloping algebra, we then prove that 
+this map is a weak-equivalence.
+
+\subsection{Standard manipulations with $L_\infty$ algebras and their modules}
+
+To any $\fg$-module $M$ (wether $\fg$ is a dg Lie algebra or an $L_\infty$-algebra), 
+we can associate its Chevalley-Eilenberg cochain complex defined 
+by 
+\begin{equation}
+ \clies(\fg, M) = \Hom (Sym(\fg[-1]), M)
+\end{equation}
+with its classical differential. 
+\greg{recall....quickly. AT least for dg-part. Say something for $L_\infty$ too}
+We have the evaluation map 
+\begin{equation}
+ \label{eq:defev} ev: \clies(\fg, M) \otimes Sym(\fg[-1])\to M
+\end{equation}
+given by applying a function on a given tensor in $Sym(\fg[-1])$.
+
+\subsection{Defining the convolution factorization algebra}
 
 The lemma allows us to define the factorization algebra given on any open $U$ by  the Chevalley-Eilenberg chain complexes
-$ \cliels\big(\fg \otimes \Omega^*_c(U), B(U) \big)$ (with their standard differential)
-of $\fg \otimes \Omega^*_c(U)$ with value on $B(U)$ whose structure maps are given, for any $(U_i)_{i\in I}$ 
+$ \cliels\big(\fg \otimes \Omega^*_c(U), \bU_n \fh(U) \big)$ (with their standard differential)
+of $\fg \otimes \Omega^*_c(U)$ with value on $\bU_n \fh(U)$ whose structure maps are given, for any $(U_i)_{i\in I}$ 
 a finite family of pairwise disjoint open subsets of an open $V$, by 
 \begin{multline}\label{eq:transClieFac}
- \bigotimes_{i\in I} \cliels\big(\fg \otimes \Omega^*_c(U_i), B(U_i) \big) \cong Sym\Big(
+ \bigotimes_{i\in I} \cliels\big(\fg \otimes \Omega^*_c(U_i), \bU_n \fh(U_i) \big) \cong Sym\Big(
  \fg\otimes (\bigoplus_{i\in I}  \Omega^*_c(U_i))[-1]  \Big) \otimes \Big( \bigotimes_{i\in I} B(U_i)\Big) \\ 
@@
 \end{multline}
-where $\omega$ is induced by the cosheaf structure of compactly supported form and $\mu_B$ is the factorization algebra structure of $B(-)$.
-
-\smallskip
+where $\omega$ is induced by the cosheaf structure of compactly supported form and $\mu_B$ is the factorization algebra structure of $B$.
 
@@
  Similarly, the structure maps~\eqref{eq:transClieFacCochain} makes 
- $ \clies\big(\fg \otimes \Omega^*(-), B(-) \big)$ a (resp. locally constant) factorization algebra.
+ $ \clies\big(\fg \otimes \Omega^*, \bU_n \fh \big)$ a (resp. locally constant) factorization algebra.
 
 \begin{dfn}\label{dfn:CEofFact}
-We {call   $\cliels\big(\fg \otimes \Omega^*_c(-), B(-) \big)$ the Chevalley-Eilenberg chain factorization algebra of $\fg$ with value in $B(-)$} 
-and $\clies\big(\fg \otimes \Omega^*(-), B(-) \big)$ the Chevalley-Eilenberg cochain factorization algebra.
+We {call   $\cliels\big(\fg \otimes \Omega^*_c, \bU_n \fh \big)$ the Chevalley-Eilenberg chain factorization algebra of $\fg$ with value in $\bU_n \fh$} 
+and $\clies\big(\fg \otimes \Omega^*, \bU_n \fh \big)$ the Chevalley-Eilenberg cochain factorization algebra.
 \end{dfn}
@@
 
-A special but very interesting case is of course when $B$ is itself an enveloping algebra. 
+A special but very interesting case is of course when $\bU_n \fh$ is itself an enveloping algebra. 
 \begin{cor}
  Let $\fg$, $\fh$ be dg-Lie algebras and $f:\fg\to \fh$ be a dg-Lie algebra morphism. 
- Then the induced factorization algebra map $\mathbf{\UU_n f}:  \cliels( \fg \otimes \Omega^*_c(-)) \longrightarrow  \cliels( \fh \otimes \Omega^*_c(-)) $
- is the standard map $\cliels(f)$ induced by $f$ and the action of $\fg  \otimes \Omega^*_c(-)$ is obtained from the $\fg$-action on $\fh$ by Leibniz rule.
+ Then the induced factorization algebra map $\mathbf{\UU_n f}:  \cliels( \fg \otimes \Omega^*_c) \longrightarrow  \cliels( \fh \otimes \Omega^*_c) $
+ is the standard map $\cliels(f)$ induced by $f$ and the action of $\fg  \otimes \Omega^*_c$ is obtained from the $\fg$-action on $\fh$ by Leibniz rule.
 \end{cor}
@@
 
-\section{Convolution algebras over colored operads}
-
-\def\conv{{\rm Conv}}
-
-\owen{For an ordinary colored operad $\cO$, describe how to produce a $\cO$-algebra $\conv(C,A)$ from any $\cO$-coalgebra $C$ and $\cO$-algebra $A$.}
-
-\owen{A special case to consider is how a cocycle $f \in \conv(C,A)$ encodes an $\cO$-algebra morphism $C^!
+\owen{Add a remark on convolution}
+%
+%\def\conv{{\rm Conv}}
+%
+%\owen{For an ordinary colored operad $\cO$, describe how to produce a $\cO$-algebra $\conv(C,A)$ from any $\cO$-coalgebra $C$ and $\cO$-algebra $A$.}
+%
+%\owen{A special case to consider is how a cocycle $f \in \conv(C,A)$ encodes an $\cO$-algebra morphism $C^!
 \to A$ from $C^!
@@
 Hopefully this admits an obvious deformation-theoretic interpretation.}
-
-\owen{If we do this correctly, we might find a model category-theoretic picture of how Koszul duality works for prefactorization algebras.}
-
-\section{Proof of Theorem \ref{thm: centralizer}}
-
-We have implemented the first step in the proof strategy.
-This section is devoted to the remaining steps.
-First, we explain steps (2)-(4), which are rather formal.
-Next, we define the $\Disk_n$-algebra $\clies(\Omega^* \otimes \fg, {\tt B}_f)$ as a kind of convolution algebra.
-Finally, we get to the heart of the construction:
-we show that this convolution algebra naturally sits inside a centralizer diagram.
-By the universal property of the centralizer, we then obtain 
-a canonical map 
-\[
-\Theta_f: \clies\big(\fg\otimes \Omega (-), B(-) \big) \longrightarrow  {\frak Z}(\mathbf{f})(-)
-\]
-where ${\frak Z}(\mathbf{f})(-)$ is the centralizer of locally constant $\Disk_n$-algebras~(\ref{D:centralizerFacAlgebra}).
-\owen{Calibrate notations!}
-It is then a direct computation to verify $\Theta_f$ is a quasi-isomorphism.
-
-\owen{Below is Greg's summary of the proof.}
-
-Let us start by summarizing the proof. The idea, using theorem~\ref{T:En=Fac}, 
-is that we only have to prove the factorization algebra part of the main theorem. 
-To do so, we first use the universal property of the centralizer to obtain 
-a canonical factorization algebra map 
-\[\Theta_f: \clies\big(\fg\otimes \Omega (-), B(-) \big) \longrightarrow  {\frak Z}(\mathbf{f})(-)\]
-where ${\frak Z}(\mathbf{f})(-)$ is the centralizer of locally constant factorization algebras (\ref{D:centralizerFacAlgebra}).
-
-Using the fundamental properties of universal $E_n$-enveloping algebra, we then prove that 
-this map is a weak-equivalence.
-
-\smallskip
-
-We thus let $\mathbf{f}: \cliels\big(\fg \otimes \Omega^* (-)) \to B(-)$ be a factorization algebra map (see~\eqref{eq:DefofFonFaclevel}). We can 
-assume that the structural (natural) quasi-isomorphism
-$$\bigotimes_{i\in I} B(U_i) 
-\stackrel{\simeq}\longrightarrow B(\coprod  U_i)$$ are chain complexes isomorphisms by replacing $B(-)$ by the prefactorization algebra 
-given, on any $V=\coprod_{j\in J} V_j$, where the $V_j$ are the connected components of $V$, by   $\mathop{\bigotimes}\limits_{j\in J} B(V_j)$. 
-The structural maps of $B$ are then a quasi-isomorphism of prefactorization algebras between it and $B(-)$. The map $\mathbf{f}$ is lifted similary using 
-the isomorphism $\bigotimes_{i\in I} \cliels\big(\fg \otimes \Omega_c^* (U_i)\big) \cong
-\cliels\big(\fg \otimes \Omega_c^* (U)\big)$ as well. We assume we have this property in the rest of this section.
-\greg{Technically we may need to replace the latter by a quasi-isomorphic one satisfying the same property to ensure we do have a strict fact algebra map. 
-Not sure if we should elaborate on it more since in the end we only need that to obtain lemma~\ref{L:inducedFacgModstruct} to make the construction valid 
-and therefore only use the induced sym on the cosheaf of $L_\infty$-module maps}
-
-\subsection{Strictification}
-
-\owen{Recall the relevant strictification results.}
-
-\owen{Sketch of where ${\tt f}$ comes from.}
-Given a cochain complex $M$, every $\fg$-representation $\rho: \fg \to \End(M)$ determines a cocommutative coderivation $\cliels(\fg) \to M$.
-Conversely, such a coderivation determines an $L_\infty$ action of $\fg$ on $M$.
-\owen{\dots}
-Applying these observations to ${\tt B}_f$ disk-by-disk, we obtain the following.
-
-\begin{lmm}
-As ${\tt B}_f$ is a $\Disk_n$-algebra in $\fg$-representations,
-there is a map of $\Disk_n$-algebras in cochain complexes ${\tt f}:  {\tt U}_n \fg \to {\tt B}$.
-\end{lmm}
-
-\owen{I'm not sure how to prove the following, or even if we need to.}
-
-\begin{prp}
-The map ${\tt f}:  {\tt U}_n \fg \to {\tt B}$ of strict $\Disk_n$-algebras models the original map~$f$.
-\end{prp}
-
-\subsection{The convolution $\Disk_n$-algebra}
-
-\owen{Discussion of convolution fact algs commented out below}
 %
-%To any $\fg$-module $M$ (wether $\fg$ is a dg Lie algebra or an $L_\infty$-algebra), 
-%we can associate its Chevalley-Eilenberg cochain complex defined 
-%by 
-%\begin{equation}
-% \clies(\fg, M) = \Hom (Sym(\fg[-1]), M)
-%\end{equation}
-%with its classical differential. 
-%\greg{recall....quickly. AT least for dg-part. Say something for $L_\infty$ too}
-%We have the evaluation map 
-%\begin{equation}
-% \label{eq:defev} ev: \clies(\fg, M) \otimes Sym(\fg[-1])\to M
-%\end{equation}
-%given by applying a function on a given tensor in $Sym(\fg[-1])$.
-%
-%\begin{dfn}\label{D:convolutionalgebraCE}Let $\fg$ be a dg Lie (or $L_\infty$)-algebra and $B$ be an $E_n$-algebra in $\fg$-modules,
-%that is an object of the $\infty$-category 
-%$E_n-Alg(Mod_{\fg})$. Its associated convolution $E_n$-algebra structure on  $\clies(\fg, B) = \Hom (Sym(\fg[-1]), B)$ is obtained by 
-% taking the \emph{convolution} between the cocommutative symmetric coalgebra $Sym(\fg[-1])$ (forgetted to an $E_n$-coalgebra) and the $E_n$-algebra $B$.
-%\end{dfn}
-%\greg{Probably need somewhere to say what means $E_n-Alg(Mod_{\fg})$ and find a less ugly notation for it}
-%Precisely, given an explicit $E_n$-operad $D_n$ in chain complexes and $(B, \mu^B)$ a $D_n$-algebra, 
-%the convolution structure is given by the following composition
-%\begin{multline}
-% \Big(D_n(r)\otimes \clies(\fg, B)^{\otimes r} \Big)\otimes Sym(\fg[-1])\\ \stackrel{id\otimes id \otimes\Delta^{(r-1)}}\longrightarrow 
-% D_n(r)\otimes \clies(\fg, B)^{\otimes r} \otimes Sym(\fg[-1])^{\otimes r} 
-% \stackrel{id \otimes (ev^{\otimes r})}\longrightarrow D_n(r)\otimes B^{\otimes r} 
-% \stackrel{\mu_\sigma^B}\longrightarrow B.
-%\end{multline}
-%where $\Delta$ is the cocommutative comultiplication.
-%In plain formula,
-%for any $\sigma \in D_n(r)$ and $\phi_1,\dots, \phi_r \in 
-%\clies(\fg, B)$, their multiplication (parametrized by $\sigma$) is  given by 
-%\begin{equation}
-% \mu_\sigma (\phi_1,\dots, \phi_r): Sym(\fg[-1]) \ni x \mapsto \pm \mu^B_{\sigma} \big(\phi_1(x^{(1)}), \dots, \phi_r(x^{(r)})\big)
-%\end{equation}
-%where $x\mapsto x^{(1)}\otimes \cdots x^{(r)}$ is the usual $r$-fold cocommutative comultiplication.
-%Note that here, we are using the usual Koszul sign  convention. 
-%
-%\begin{lmm}
-% $\clies(\fg, M) = \Hom (Sym(\fg[-1]), B)$ is a $E_n$-algebra, naturally in $\fg$ and $B$.
-%\end{lmm}
-
-\owen{Describe it.}
-
-\subsection{Construction of the universal pairing in factorization algebras}\label{SS:constuctionthetaf}
+%\owen{If we do this correctly, we might find a model category-theoretic picture of how Koszul duality works for prefactorization algebras.}
+
+\subsection{Construction of the universal pairing in factorization algebras}
+\label{SS:constuctionthetaf}
 
@@
 
-\smallskip
-
 First note that compactly supported form embeds in all forms, therefore we can apply 
-any element of $\cliels\big(\fg \otimes \Omega^* (-), B(-)\big)$ 
-to any element of $\cliels\big(\fg \otimes \Omega_c^* (-)\big)$. Therefore, for any  $p\in \bN$, we have an evaluation 
+any element of $\cliels\big(\fg \otimes \Omega^* , B\big)$ 
+to any element of $\cliels\big(\fg \otimes \Omega_c^* \big)$. Therefore, for any  $p\in \bN$, we have an evaluation 
 \begin{equation} \label{eqdef:ev} \begin{array}{c}\ev: Sym^p \big( \fg \otimes \Omega^* (U)[-1] ,B(U)\big)
@@
 
-\smallskip
-
-Second, the augmentation of $B$ makes $B(-)$ augmented as well (in the obvious sense of~\cite{Gi-NotesFactorization}) and this induces an augmentation on
-$\clies\big(\fg\otimes \Omega (-), B(-) \big)$ as well as follows. 
+Second, the augmentation of $B$ makes $B$ augmented as well (in the obvious sense of~\cite{Gi-NotesFactorization}) and this induces an augmentation on
+$\clies\big(\fg\otimes \Omega , B \big)$ as well as follows. 
 We have the canonical factorization algebra map  $\mathbf{1}$  defined, for any open $U$, by 
@@
 B(\emptyset) \ar[r] & B(U)  } 
- \] where the last map is given by the factorization algebra structure of $B(-)$. This gives the canonical element element 
- $\mathbf{1}\in \clies(\fg\otimes \Omega^*(-), B(-)) )$ which is the unit $k(-)\to \clies(\fg\otimes \Omega^*(-), B(-)) )$
+ \] where the last map is given by the factorization algebra structure of $B$. This gives the canonical element element 
+ $\mathbf{1}\in \clies(\fg\otimes \Omega^*, B) )$ which is the unit $k\to \clies(\fg\otimes \Omega^*, B) )$
  of the factorization structure of 
@@
  \iota$ where $\iota: k(U) \cong k \hookrightarrow Sym(\fg \otimes \Omega (U) [1]) $ is the inclusion and $\varepsilon B(U)\to k(U)$ is the augmentation of 
- $B(-)$. We therefore obtain a canonical splitting of factorization algebras 
+ $B$. We therefore obtain a canonical splitting of factorization algebras 
  \begin{equation}\label{eq:splittingbyaugm}
-   \clies\big(\fg\otimes \Omega^*(-), B(-)\big)  \, \cong \, k(-) \oplus \overline{ \clies(\fg\otimes \Omega^*(-), B(-)) )}
+   \clies\big(\fg\otimes \Omega^*, B\big)  \, \cong \, k \oplus \overline{ \clies(\fg\otimes \Omega^*, B) )}
  \end{equation}
@@
 a natural grading on it.
-
-\smallskip
 
@@
 \[ \ev_f^W(\varphi\otimes x)= \lambda \mathbf{f}(W)(x) + \overline{\varphi}(x). \]
-
-\smallskip
 
@@
 \end{multline}
-where $\mu_B$ is the canonical structure map of the factorization algebra $B(-)$ and the other maps are given by~\eqref{eq:defgraduationoncentralizernonconnected} 
+where $\mu_B$ is the canonical structure map of the factorization algebra $B$ and the other maps are given by~\eqref{eq:defgraduationoncentralizernonconnected} 
 and~\eqref{eq:defevforconnected}.
@@
 things to do (like completion) for non-finitely dimensional Lie algebras}
-\greg{The decomposition used to extend $\ev$ on non-connected open can be done with any augmented $B(-)$, simply by defining it onto the prefact alg obtained by tensoring 
-out on non-connected components and using the quasi-isomorphism canonical map to $\clies(\fg, B(-))$ in that case. Not sure which way is easier to define/mention}
+\greg{The decomposition used to extend $\ev$ on non-connected open can be done with any augmented $B$, simply by defining it onto the prefact alg obtained by tensoring 
+out on non-connected components and using the quasi-isomorphism canonical map to $\clies(\fg, B)$ in that case. Not sure which way is easier to define/mention}
 
@@
 is compatible (by the same argument as Lemma~\ref{L:pairingCE}) with the factorization algebra structure maps of
-$\clies(\fg\otimes \Omega(-), B(-))$} graded by the subsets of its connected components:
+$\clies(\fg\otimes \Omega, B)$} graded by the subsets of its connected components:
  \begin{equation}\label{eq:defgraduationoncentralizernonconnected2}
@@
 \emph{with support $\coprod\limits_{j\in J} U_j$}.   
-Note that the component $k(-)$ in the decomposition~\eqref{eq:splittingbyaugm} is precisely the component 
+Note that the component $k$ in the decomposition~\eqref{eq:splittingbyaugm} is precisely the component 
 ${\clies}^{(\emptyset)}\big(\fg\otimes \Omega^*(U), B(U)\big)$ corresponding to the empty family.
@@
 where $\mu_{B,J}: B\Big(\coprod\limits_{i\in I\setminus J}U_i\Big)\otimes B\Big(\coprod\limits_{j\in J}U_j\Big) \to B(U)$
-is the  structure map of $B(-)$.
+is the  structure map of $B$.
 
@@
  The pairing morphism $\ev_f$ defined by formula~\eqref{eq:defineevf} extends to a factorization algebra morphism
- \[\ev_f:  \cliels\big(\fg \otimes \Omega^* (-), B(-)\big) \otimes \cliels\big(\fg \otimes \Omega_c^* (-)\big) 
- \longrightarrow B(-).\]
+ \[\ev_f:  \cliels\big(\fg \otimes \Omega^* , B\big) \otimes \cliels\big(\fg \otimes \Omega_c^* \big) 
+ \longrightarrow B.\]
 \end{lmm}
@@
 B(\emptyset) \ar[r] & B(U)  } 
- \] where the last map is given by the factorization algebra structure of $B(-)$.
-This gives the canonical element element $\mathbf{1}\in \clies(\fg\otimes \Omega^*(-), B(-)) )$ which is the unit of the factorization structure of
+ \] where the last map is given by the factorization algebra structure of $B$.
+This gives the canonical element element $\mathbf{1}\in \clies(\fg\otimes \Omega^*, B) )$ which is the unit of the factorization structure of
  the Chevalley-Eilenberg cochain factorization algebras.
@@
  $$ \xymatrix{
-& \clies ( \fg\otimes \Omega^* (-), B(-)) \otimes \cliels(\fg\otimes \Omega^*_c  (-) )
+& \clies ( \fg\otimes \Omega^* , B) \otimes \cliels(\fg\otimes \Omega^*_c   )
 \ar[dr]^{\ev_f} & \\
-\cliels(\fg\otimes \Omega^*_c (-)) \ar[ur]^{\mathbf{1} \otimes \id} \ar[rr]^{\mathbf{f}}  & &  B(-).}
+\cliels(\fg\otimes \Omega^*_c ) \ar[ur]^{\mathbf{1} \otimes \id} \ar[rr]^{\mathbf{f}}  & &  B.}
  $$
@@
 
-By universal property of the centralizer (definition~\ref{D:centralizerFacAlgebra}), lemma~\ref{L:ComTriangCent} implies that the pairing $\ev_f \,:\,\cliels\big(\fg \otimes \Omega^* (-), B(-)\big) \otimes \cliels\big(\fg \otimes \Omega_c^* (-)\big)
- \longrightarrow B(-)$ induces 
+By universal property of the centralizer (definition~\ref{D:centralizerFacAlgebra}), lemma~\ref{L:ComTriangCent} implies that the pairing $\ev_f \,:\,\cliels\big(\fg \otimes \Omega^* , B\big) \otimes \cliels\big(\fg \otimes \Omega_c^* \big)
+ \longrightarrow B$ induces 
 a canonical morphism of factorization algebras
 \begin{equation}\label{eq:canonicaltocenter}
-\theta_f: \clies\big(\fg\otimes \Omega (-), B(-) \big) \longrightarrow  {\frak Z}(\mathbf{f})(-). 
+\theta_f: \clies\big(\fg\otimes \Omega , B \big) \longrightarrow  {\frak Z}(\mathbf{f}). 
 \end{equation}
@@
  {\frak Z}(\mathbf{f})(\RR^n)\cong {\frak Z}_{E_n}(\mathbf{f})$ is a quasi-isomorphism.
-
- \smallskip
 
@@
 
-\smallskip
-
 Using the canonical inclusion $i: U\fg \to U(\fg \otimes k[\epsilon_{n-1}])$,
@@
 Recall now that $\UU_n \fg \simeq \Sym(\fg[1-n])$ as $\fg$-modules 
-since, as factorization algebras (see Theorem~\ref{T:UnofLie}),  $$\UU_n \fg \cong \cliels(\Omega^*_c(-) \otimes \fg) \cong \Sym((\fg[-n])[-1])$$ where the right hand side formula follows from the fact that the product of degree $n$ compactly supported forms is trivial and therefore $\fg[-n]$ is a trivial Lie algebra.
+since, as factorization algebras (see Theorem~\ref{T:UnofLie}),  $$\UU_n \fg \cong \cliels(\Omega^*_c \otimes \fg) \cong \Sym((\fg[-n])[-1])$$ where the right hand side formula follows from the fact that the product of degree $n$ compactly supported forms is trivial and therefore $\fg[-n]$ is a trivial Lie algebra.
 Thus, base change  gives rise to an equivalence 
@@
 \begin{prp}\label{L:canonicaltocenterisquis} The morphism~\eqref{eq:canonicaltocenter}
-\[\clies\big(\fg\otimes \Omega (-), B(-) \big) \longrightarrow  {\frak Z}(\mathbf{f})(-)\] is a weak-equivalence of factorization algebras. 
+\[\clies\big(\fg\otimes \Omega , B \big) \longrightarrow  {\frak Z}(\mathbf{f})\] is a weak-equivalence of factorization algebras. 
 \end{prp}
@@
 \begin{thm}\label{thm:centralizerfactorization}
-Let $k$ be $\RR$ or $\CC$, and assume $\mathbf{f}:  \UU_n \fg \to B(-)$ is a map of augmented factorization algebras. 
+Let $k$ be $\RR$ or $\CC$, and assume $\mathbf{f}:  \UU_n \fg \to B$ is a map of augmented factorization algebras. 
 Then, the centralizer ${\frak Z}(\mathbf{f})$ is modeled by the locally constant factorization algebra that assigns
@@
  In section~\ref{SS:constuctionthetaf}, we have constructed a factorization algebra map 
- $\theta_f: \clies\big(\fg\otimes \Omega (-), B(-) \big) \longrightarrow  {\frak Z}(\mathbf{f})(-)$. Proposition~\ref{L:canonicaltocenterisquis} 
+ $\theta_f: \clies\big(\fg\otimes \Omega , B \big) \longrightarrow  {\frak Z}(\mathbf{f})$. Proposition~\ref{L:canonicaltocenterisquis} 
  states that this map is an equivalence he Chevalley-Eilenberg factorization algebra cochains and the factorization algebra center of $f$ as claimed.
@@
 that is from Theorem~\ref{thm:centerfactorization}. This proves the theorem over $k=\RR$ (or $\CC$).
-
-\smallskip
 
@@
 \end{prp}
-When $A(-)$ is a factorization algebra model for $A$, in virtue of theorem~\ref{T:En=Fac} 
+When $A$ is a factorization algebra model for $A$, in virtue of theorem~\ref{T:En=Fac} 
 (and \greg{add reference for fac algebra in fac algebra maybe too}), in order to have a factorization algebra 
 model of the center of $A$, it is sufficient to describe the induced map 
-\[{\frak Z}(A(-)){\otimes} {\frak Z}(A(-)) \longrightarrow {\frak Z}(A(-))\]
+\[{\frak Z}(A){\otimes} {\frak Z}(A) \longrightarrow {\frak Z}(A)\]
 as a factorization algebra homomorphism which makes it an associative object in the category of locally constant factorization algebras.
 
-\smallskip
-
 We now turn to the specific case   of enveloping algebras $\UU_n(\fg)$.
@@
 Let $f: \fg \to \fh$, $g: \fh \to \fl$ be  $L_\infty$-algebras morphisms; for instance a dg-Lie algebras morphisms. We write 
-\[ \mathbf{f}:\cliels\big(\fg \otimes \Omega^*_c(-)\big) \to  \cliels\big(\fh \otimes \Omega^*_c(-)\big), \quad 
-\mathbf{h}:\cliels\big(\fh \otimes \Omega^*_c(-)\big) \to  \cliels\big(\fl \otimes \Omega^*_c(-)\big)\]
+\[ \mathbf{f}:\cliels\big(\fg \otimes \Omega^*_c\big) \to  \cliels\big(\fh \otimes \Omega^*_c\big), \quad 
+\mathbf{h}:\cliels\big(\fh \otimes \Omega^*_c\big) \to  \cliels\big(\fl \otimes \Omega^*_c\big)\]
 for the induced morphisms on their enveloping factorization algebras over $\RR^n$.
@@
 algebras) 
-are canonically pointed  by $\mathbf{1}\in \clies(\fg\otimes \Omega^*(-), B(-)) )$ which is induced by 
-the unit $k(-)\to \clies(\fg\otimes \Omega^*(-), B(-)) )$
+are canonically pointed  by $\mathbf{1}\in \clies(\fg\otimes \Omega^*, B) )$ which is induced by 
+the unit $k\to \clies(\fg\otimes \Omega^*, B) )$
  of the factorization structures.  In particular, we have the canonical splitting~\eqref{eq:splittingbyaugm} 
@@
 
-\begin{lmm}\label{L:compisfacmap} The composition $$\clies\big(\fh \otimes \Omega(-), \cliels(\fl \otimes \Omega_c(-)  \big) \otimes 
-\clies\big(\fg \otimes \Omega(-), \cliels(\fh \otimes \Omega_c(-)  \big)
+\begin{lmm}\label{L:compisfacmap} The composition $$\clies\big(\fh \otimes \Omega, \cliels(\fl \otimes \Omega_c  \big) \otimes 
+\clies\big(\fg \otimes \Omega, \cliels(\fh \otimes \Omega_c  \big)
 \stackrel{(-\star-)}\longrightarrow 
-\clies\big(\fg \otimes \Omega(-), \cliels(\fl \otimes \Omega_c(-)  \big)
+\clies\big(\fg \otimes \Omega, \cliels(\fl \otimes \Omega_c  \big)
 $$
@@
 The composition is compatible with the augmentation splitting. Precisely, we have
-\begin{lmm}\label{L:compisaugmented} For any $\varphi \in \clies\big(\fg \otimes \Omega(-), \cliels(\fh \otimes \Omega_c(-)  \big)$,
-$\psi \in \clies\big(\fh \otimes \Omega(-), \cliels(\fl \otimes \Omega_c(-)  \big)$
+\begin{lmm}\label{L:compisaugmented} For any $\varphi \in \clies\big(\fg \otimes \Omega, \cliels(\fh \otimes \Omega_c  \big)$,
+$\psi \in \clies\big(\fh \otimes \Omega, \cliels(\fl \otimes \Omega_c  \big)$
  One has the following equalities  :
@@
   \overline{\psi\star \varphi} \;= \;\mathbf{1}\star \overline{\varphi} +\overline{\psi}\star \mathbf{1} +\overline{\psi}\star \overline{\varphi} 
-  & \quad\mbox{ (in  $\clies\big(\fg \otimes \Omega(-), \cliels(\fl \otimes \Omega_c(-)  \big) $)}\\
+  & \quad\mbox{ (in  $\clies\big(\fg \otimes \Omega, \cliels(\fl \otimes \Omega_c  \big) $)}\\
  \mathbf{1}\star \varphi \;=\;  (\lambda_\varphi \mathbf{1}, g\circ \overline{\varphi})\qquad
-  &\quad\mbox{ (in  $k(-)  \oplus \overline{\clies\big(\fg \otimes \Omega(-), \cliels(\fl \otimes \Omega_c(-)  \big)}$)}\\
+  &\quad\mbox{ (in  $k  \oplus \overline{\clies\big(\fg \otimes \Omega, \cliels(\fl \otimes \Omega_c  \big)}$)}\\
   \psi \star \mathbf{1}\;=\; (\lambda_\psi \mathbf{1}, \overline{\psi} \circ f) \qquad
-  &\quad\mbox{ (in  $k(-)  \oplus \overline{\clies\big(\fg \otimes \Omega(-), \cliels(\fl \otimes \Omega_c(-)  \big)}$).}
+  &\quad\mbox{ (in  $k  \oplus \overline{\clies\big(\fg \otimes \Omega, \cliels(\fl \otimes \Omega_c  \big)}$).}
  \end{align}
@@
 \begin{lmm}\label{L:compisassociative} Let $\fg \stackrel{f}\to \fh$, $\fh \stackrel{g}\to \fl$ and $\fl \stackrel{h}\to \fk$ be maps of $L_\infty$-algebras.
- Then, we have, for any $\varphi \in \clies\big(\fg\otimes \Omega(-), \cliels(\fh \otimes \Omega_c(-)) \big)$, 
-  $\psi \in \clies\big(\fh\otimes \Omega(-), \cliels(\fl \otimes \Omega_c(-)) \big)$ and  
-  $\gamma \in \clies\big(\fl\otimes \Omega(-), \cliels(\fk \otimes \Omega_c(-)) \big)$, the equality 
+ Then, we have, for any $\varphi \in \clies\big(\fg\otimes \Omega, \cliels(\fh \otimes \Omega_c) \big)$, 
+  $\psi \in \clies\big(\fh\otimes \Omega, \cliels(\fl \otimes \Omega_c) \big)$ and  
+  $\gamma \in \clies\big(\fl\otimes \Omega, \cliels(\fk \otimes \Omega_c) \big)$, the equality 
   \[ (\gamma\star \psi)\star \varphi \;=\; \gamma\star (\psi \star \varphi) \quad \mbox{ in 
-  $\clies\big(\fg\otimes \Omega(-), \cliels(\fk \otimes \Omega_c(-)) \big)$.}  \]
+  $\clies\big(\fg\otimes \Omega, \cliels(\fk \otimes \Omega_c) \big)$.}  \]
 \end{lmm}
@@
  \[\tiny \begin{tikzcd}
- \clies\big(\fh \otimes \Omega(-), \cliels(\fl \otimes \Omega_c(-)  \big) 
- \otimes  \clies\big(\fg \otimes \Omega(-), \cliels(\fh \otimes \Omega_c(-)  \big) 
- \otimes \cliels(\fg \otimes \Omega_c(-)  \big) \arrow[rd, "(-\star-)\otimes \id"]
+ \clies\big(\fh \otimes \Omega, \cliels(\fl \otimes \Omega_c  \big) 
+ \otimes  \clies\big(\fg \otimes \Omega, \cliels(\fh \otimes \Omega_c  \big) 
+ \otimes \cliels(\fg \otimes \Omega_c  \big) \arrow[rd, "(-\star-)\otimes \id"]
  \arrow[dd, "\id\otimes \ev_ {\mathbf{f}}"]& \\ 
- & \clies\big(\fg \otimes \Omega(-), \cliels(\fl \otimes \Omega_c(-)  \big) 
- \otimes \cliels(\fg \otimes \Omega_c(-)  \big)
+ & \clies\big(\fg \otimes \Omega, \cliels(\fl \otimes \Omega_c  \big) 
+ \otimes \cliels(\fg \otimes \Omega_c  \big)
  \arrow[dd, "\ev_{\mathbf{g}\circ \mathbf{f}}"]\\
-\clies\big(\fh \otimes \Omega(-), \cliels(\fl \otimes \Omega_c(-)  \big) 
- \otimes \cliels(\fh \otimes \Omega_c(-)  \big)  \arrow[rd, "\ev_{\mathbf{g}}"] & \\  & \cliels(\fl \otimes \Omega_c(-)  \big). 
+\clies\big(\fh \otimes \Omega, \cliels(\fl \otimes \Omega_c  \big) 
+ \otimes \cliels(\fh \otimes \Omega_c  \big)  \arrow[rd, "\ev_{\mathbf{g}}"] & \\  & \cliels(\fl \otimes \Omega_c  \big). 
 \end{tikzcd}\]
@@
 \item If $f= \fg \stackrel{\id}\to \fg$,  the composition $(-\star-)$ makes 
-$\clies\big(\fg \otimes \Omega(-), \cliels(\fg \otimes \Omega_c(-)) \big)$ into an 
+$\clies\big(\fg \otimes \Omega, \cliels(\fg \otimes \Omega_c) \big)$ into an 
 (augmented) associative algebra object in factorization algebra, with unit given by $\mathbf{1}$, 
-which is equivalent to the structure of the center ${\frak Z} (\cliels(\fg \otimes \Omega_c(-)))$. 
+which is equivalent to the structure of the center ${\frak Z} (\cliels(\fg \otimes \Omega_c))$. 
 \end{enumerate}
@@
 By Theorem~\ref{thm:centralizerfactorization}, we know that the factorization algebras models for the centralizers are given by the respective Chevalley-Eilenberg cochain factorizations algebras 
-(Definition~\ref{dfn:CEofFact}) $\clies\big(\fg \otimes \Omega(-), \cliels(\fh \otimes \Omega_c(-)  \big) $, 
-$\clies\big(\fh \otimes \Omega(-), \cliels(\fl \otimes \Omega_c(-)  \big) $ and $\clies\big(\fg \otimes \Omega(-), \cliels(\fl \otimes \Omega_c(-)  \big) $ 
+(Definition~\ref{dfn:CEofFact}) $\clies\big(\fg \otimes \Omega, \cliels(\fh \otimes \Omega_c  \big) $, 
+$\clies\big(\fh \otimes \Omega, \cliels(\fl \otimes \Omega_c  \big) $ and $\clies\big(\fg \otimes \Omega, \cliels(\fl \otimes \Omega_c  \big) $ 
 equipped with the evaluations maps are given by $\ev_{\mathbf{f}}$, $\ev_{\mathbf{g}}$ and $\ev_{\mathbf{g}\circ \mathbf{f}}$. We are thus left 
@@
 let $f\otimes X  $ be an 
-element in $\cliels\big(\fg \otimes \Omega^* (-), B(-)\big) \otimes \cliels\big(\fg \otimes \Omega_c^* (-)\big)$.  
+element in $\cliels\big(\fg \otimes \Omega^* , B\big) \otimes \cliels\big(\fg \otimes \Omega_c^* \big)$.  
 Let
@@
 
-Recall that we have a factorization algebra map~\eqref{eq:DefofFonFaclevel}  $\mathbf{f}: \cliels(\fg \otimes \Omega_c^*(-) \to B(-)$.
+Recall that we have a factorization algebra map~\eqref{eq:DefofFonFaclevel}  $\mathbf{f}: \cliels(\fg \otimes \Omega_c^* \to B$.
 The unital factorization algebra is given, for any open $U$, by $k(U)=k$.
@@
 \end{multline}
-
-\smallskip
 
@@
  Using the diagramm~\eqref{eq:Cechassociatedtoconfofdisks}, it is equivalent to prove that the following diagram 
- \xymatrix{ \check{C}(\cB, (-)_\cU)\ar[r] \ar[d] & \check{C}(\cB', (-)_\cU) \ar[d] \\ \check{C}(\cC, (-)_\cU\ar[r] & \check{C}(\cC', (-)_\cU}
- is commutative. But the map $\check{C}(\cB, (-)_\cU) \to \check{C}(\cB', (-)_\cU)$ 
+ \xymatrix{ \check{C}(\cB, _\cU)\ar[r] \ar[d] & \check{C}(\cB', _\cU) \ar[d] \\ \check{C}(\cC, _\cU\ar[r] & \check{C}(\cC', _\cU}
+ is commutative. But the map $\check{C}(\cB, _\cU) \to \check{C}(\cB', _\cU)$ 
  is induced by the direct sums of tensors products of chain maps $ g(W_i): \cB(U_i)= \cB_{U_i}(W_i) \to \cB'_{U_i} (W_i)$ on each $i=1\dots r$ and 
@@
 
-We now apply this to the special case of $\UU_n(\fg)$, that is for $\cA(-)= \cliels(\Omega^*_c(-) \otimes \fg)$ as we have seen. 
+We now apply this to the special case of $\UU_n(\fg)$, that is for $\cA= \cliels(\Omega^*_c \otimes \fg)$ as we have seen. 
 \begin{lmm}
@@
 \begin{proof}
- The commtativity of the right square follows from~\eqref{eq:Cechassociatedtoconfofdisks}.
-For the left square, note that the factorization algebra structure maps on $\cliels(\Omega^*_c(-) \otimes \fg)$
+ The commtativity of the right square follows from~\eqref{eq:Cechassociatedtoconfofdisks}. For the left square, note that the factorization algebra structure maps on $\cliels(\Omega^*_c \otimes \fg)$ 
  are induced by applying the Chevalley-Eilenberg chain functor to the canonical maps of cosheaves of Lie algebras $\bigoplus_{i=1}^{r} (\Omega^*_c(U_i)\otimes \fg) \cong \Omega^*_c(\coprod U_i) \otimes \fg \longrightarrow  \Omega^*_c(V)\otimes \fg $.

### 2020-09-01 draft.tex
small stuff

@@
 
+\owen{I want to recall briefly how an $L_\infty$ action on a cochain complex leads to all the variants of CE (co)chains.}
+
 To any $\fg$-module $M$ (wether $\fg$ is a dg Lie algebra or an $L_\infty$-algebra), 
@@
 
+\begin{lmm}
+\label{lmm: CE from map}
+\owen{an $L_\infty$ map $\fg \rightsquigarrow \fh$ induces a cochain complex $\clies(\fg,\cliels(\fh))$.}
+\end{lmm}
+
 \subsection{Defining the convolution factorization algebra}
+
+Our goal here is to construct the factorization algebra that models the centralizer.
+First, we need to show that there is a well-defined functor (in the 1-categorical sense) ${\rm Opens}_{\RR^n} \to \Ch_k$ assigning $\clies(\Omega^*(V) \otimes \fg, \bU_n \fh(V))$ to each open set $V$.
+Once that is in place, it is straightforward to describe the structure maps of the prefactorization algebra.
+
+The role of
 

### 2020-09-01 draft.tex
finished def of centralizer qua fact alg

@@
 \[
-\clies(\Omega^* \otimes \fg, \cliels(\Omega^*_c \otimes \fh))
-\]
-equipped with a convolution-type product.
+\clies(\Omega^* \otimes \fg, \cliels(\Omega^*_c \otimes \fh)_f)
+\]
+equipped with a convolution-type product,
+where the subscript $f$ indicates how $\cliels(\Omega^*_c \otimes \fh)$ is a module over $\Omega^* \otimes \fg$.
 \end{thm}
@@
 
-\begin{lmm}
-\label{lmm: CE from map}
+\begin{dfn}
+\label{dfn: CE from map}
 \owen{an $L_\infty$ map $\fg \rightsquigarrow \fh$ induces a cochain complex $\clies(\fg,\cliels(\fh))$.}
-\end{lmm}
+\end{dfn}
 
@@
 First, we need to show that there is a well-defined functor (in the 1-categorical sense) ${\rm Opens}_{\RR^n} \to \Ch_k$ assigning $\clies(\Omega^*(V) \otimes \fg, \bU_n \fh(V))$ to each open set $V$.
-Once that is in place, it is straightforward to describe the structure maps of the prefactorization algebra.
-
-The role of
-
-The lemma allows us to define the factorization algebra given on any open $U$ by  the Chevalley-Eilenberg chain complexes
-$ \cliels\big(\fg \otimes \Omega^*_c(U), \bU_n \fh(U) \big)$ (with their standard differential)
-of $\fg \otimes \Omega^*_c(U)$ with value on $\bU_n \fh(U)$ whose structure maps are given, for any $(U_i)_{i\in I}$ 
-a finite family of pairwise disjoint open subsets of an open $V$, by 
-\begin{multline}\label{eq:transClieFac}
- \bigotimes_{i\in I} \cliels\big(\fg \otimes \Omega^*_c(U_i), \bU_n \fh(U_i) \big) \cong Sym\Big(
- \fg\otimes (\bigoplus_{i\in I}  \Omega^*_c(U_i))[-1]  \Big) \otimes \Big( \bigotimes_{i\in I} B(U_i)\Big) \\ 
- \cong Sym\Big(\fg\otimes \Omega_c\big(\coprod U_i\big)[-1] \Big) \otimes \Big( \bigotimes_{i\in I} B(U_i)\Big)  
- \stackrel{\omega^*\otimes \mu_B}\longrightarrow Sym(\fg\otimes \Omega_c(V)[-1] ) \otimes B(V) \\ 
- = \cliels(\fg\otimes \Omega_c(V), B(V))
-\end{multline}
-where $\omega$ is induced by the cosheaf structure of compactly supported form and $\mu_B$ is the factorization algebra structure of $B$.
-
-The (homotopy) sheaf structure of forms also gives us structure maps
-\begin{multline}\label{eq:transClieFacCochain}
- \bigotimes_{i\in I} \clies\big(\fg \otimes \Omega^*(U_i), B(U_i) \big) \longrightarrow
-  \Hom\Big(Sym\big(\fg\otimes (\bigoplus_{i\in I}  \Omega^*(U_i))[-1]\big),  \bigotimes\limits_{i\in I} B(U_i) \Big) \\
- \cong \Hom\Big(Sym\big(\fg\otimes \Omega^*(\coprod U_i)[-1]\big), \bigotimes\limits_{i\in I} B(U_i) \Big) \\
- \stackrel{\rho}\longrightarrow \Hom\Big(Sym\big(\fg\otimes \Omega^*(V)[-1]\big), \bigotimes\limits_{i\in I} B(U_i) \Big) \\
- \stackrel{\mu_B}\longrightarrow 
-  \clies(\fg\otimes \Omega (V), B(V))
-\end{multline}
-where $\rho$ is given by the restriction of forms onto a subspace.
-
-\label{L:ClieFacDef} 
- Similarly, the structure maps~\eqref{eq:transClieFacCochain} makes 
- $ \clies\big(\fg \otimes \Omega^*, \bU_n \fh \big)$ a (resp. locally constant) factorization algebra.
-
-\begin{dfn}\label{dfn:CEofFact}
-We {call   $\cliels\big(\fg \otimes \Omega^*_c, \bU_n \fh \big)$ the Chevalley-Eilenberg chain factorization algebra of $\fg$ with value in $\bU_n \fh$} 
-and $\clies\big(\fg \otimes \Omega^*, \bU_n \fh \big)$ the Chevalley-Eilenberg cochain factorization algebra.
-\end{dfn}
-\begin{proof}
-
-\end{proof}
-
-A special but very interesting case is of course when $\bU_n \fh$ is itself an enveloping algebra. 
-\begin{cor}
- Let $\fg$, $\fh$ be dg-Lie algebras and $f:\fg\to \fh$ be a dg-Lie algebra morphism. 
- Then the induced factorization algebra map $\mathbf{\UU_n f}:  \cliels( \fg \otimes \Omega^*_c) \longrightarrow  \cliels( \fh \otimes \Omega^*_c) $
- is the standard map $\cliels(f)$ induced by $f$ and the action of $\fg  \otimes \Omega^*_c$ is obtained from the $\fg$-action on $\fh$ by Leibniz rule.
-\end{cor}
-\begin{rmk}\greg{Extends to $L_\infty$ case in a sentence or too}
+Once that is in place, it is straightforward to describe the structure maps of the prefactorization algebra and to verify it forms a factorization algebra.
+
+\begin{rmk}
+These arguments are now standard in the literature of factorization algebras, so we will be brief in our discussion.
+See, e.g., \cite{CG1} \owen{stuff by Greg and others} for more.
 \end{rmk}
 
-\owen{Add a remark on convolution}
+Consider now a fixed open set $V \subset \RR^n$.
+Then the $L_\infty$ map $f: \fg \rightsquigarrow \fh$ induces canonically an $L_\infty$ map 
+\[
+\tilde{f}: \Omega^*_c(V) \otimes \fg \to \Omega^*_c(V) \otimes \fh
+\]
+by base change along the map $k \to \Omega^*_c(V)$ of dg commutative algebras,
+as the compactly supported de Rham forms form a dg commutative algebra under wedge product.
+In consequence, we see that $\Omega^*_c(V) \otimes \fg$ acts on $\Omega^*_c(V) \otimes \fh$ and hence equips it with the structure of an $L_\infty$ module over $\Omega^*_c(V) \otimes \fg$.
+We denote this module as
+\[
+(\Omega^*_c(V) \otimes \fh)_f
+\]
+to emphasize the dependence on the original map~$f$.
+In this action, the wedge product of forms intertwines with the $L_\infty$ structure on $\fg$ in a very simple way: 
+they simply happen side by side, but do not affect each other.
+
+Observe that $\Omega^*_c(V)$ is a module over the dg commutative algebra $\Omega^*(V)$ of {\em non}\/compactly supported forms.
+This action extends immediately to the module $(\Omega^*_c(V) \otimes \fh)_f$, so we now view it as an $L_\infty$ module over $\Omega^*(V)$ as well.
+In consequence, we have a cochain complex
+\[
+\clies(\Omega^*(V) \otimes \fg, (\Omega^*_c(V) \otimes \fh)_f)
+\]
+on each open set~$V$.
+
+The next step is to verify functoriality of this construction over the poset of opens.
+This property follows quickly from the fact that wedge product of forms preserves support.
+Given an inclusion $i: V' \subset V$ of opens, if we take a form $\alpha \in \Omega^*(V)$ and a compactly supported form $\beta \in \Omega^*_c(V')$, then the wedge product $\alpha \wedge i_* \beta \in \Omega^*_c(V)$ after applying the extension-by-zero map $i_*: \Omega^*_c(V') \to \Omega^*_c(V)$ equals the wedge product $i_*(i^*\alpha \wedge \beta)$ arising from the restriction $i^* \alpha$ of $\alpha$ to~$V'$.
+In consequence, the action of $\Omega^*(V) \otimes \fg$ on $(\Omega^*_c(V') \otimes \fh)_f$ arising from the restriction map $\Omega^*(V) \otimes \fg \to \Omega^*(V') \otimes \fg$ of $L_\infty$ algebras agrees with action induced by the inclusion of $(\Omega^*_c(V') \otimes \fh)_f$ as a (strict) submodule of~$(\Omega^*_c(V) \otimes \fh)_f$.
+This argument is manifestly associative under composition of inclusions, so we have shown our first claim.
+
+\begin{lmm}
+The assignment
+\[
+V \mapsto \clies(\Omega^*(V) \otimes \fg, (\Omega^*_c(V) \otimes \fh)_f)
+\]
+determines a functor from ${\rm Opens}_{\RR^n}$ to~$\Ch_k$.
+\end{lmm}
+
+We now turn to extending this functor to an algebra over the colored operad ${\rm Opens}_{\RR^n}^\sqcup$ whose colors are opens in $\RR^n$ where there is a precisely a single operation from a tuple of opens $[V_1,\ldots,V_k]$ to an open $W$ if and only if both $W$ contains every $V_j$ and the $V_j$ are all pairwise disjoint.
+
+The key fact is that the functors $\cliels$ and $\clies$ are suitably symmetric monoidal:
+they send a product of $L_\infty$ algebras to a tensor product of cochain complexes.
+Hence it suffices to examine the underlying functors to $L_\infty$ algebras.
+As the functors $\Omega^*$ and $\Omega^*_c$ send finite disjoint unions of opens to the direct product of cochain complexes, 
+the functors like $\Omega^* \otimes \fg$ and $\Omega^*_c \otimes \fh$ send finite disjoint unions of opens to products of $L_\infty$ algebras.
+In consequence, we obtain the desired second claim.
+
+\begin{lmm}
+The assignment
+\[
+V \mapsto \clies(\Omega^*(V) \otimes \fg, (\Omega^*_c(V) \otimes \fh)_f)
+\]
+determines a prefactorization algebra, i.e., a strict algebra over ${\rm Opens}_{\RR^n}^\sqcup$ with values in~$\Ch_k^\otimes$.
+\end{lmm}
+
+Due to the Poincar\'e lemma, the inclusion of a disk into a bigger disk $D \hookrightarrow D'$ makes the structure map 
+\[
+\clies(\Omega^*(D) \otimes \fg, (\Omega^*_c(D) \otimes \fh)_f) \xto{\simeq} \clies(\Omega^*(D) \otimes \fg, (\Omega^*_c(D) \otimes \fh)_f)
+\]
+a quasi-isomorphism.
+Hence this prefactorization algebra is locally constant in a homotopical sense.
+
+In fact, it defines a {\em factorization} algebra, by arguments that can be found in \owen{chapter 6 of \cite{CG1} and elsewhere}.
+
+\owen{Add a remark on convolution?}
 %

### 2020-09-01 draft.tex
finished def of pairing

@@
 Observe that $\Omega^*_c(V)$ is a module over the dg commutative algebra $\Omega^*(V)$ of {\em non}\/compactly supported forms.
-This action extends immediately to the module $(\Omega^*_c(V) \otimes \fh)_f$, so we now view it as an $L_\infty$ module over $\Omega^*(V)$ as well.
+This action extends immediately to the module $(\Omega^*_c(V) \otimes \fh)_f$, 
+so we now view it as an $L_\infty$ module over $\Omega^*(V) \otimes \fg$ as well.
+We now need to explain how to make $\cliels(\Omega^*_c(V) \otimes \fh)$ into an $L_\infty$-module over $\Omega^*(V) \otimes \fg$.
+Here we rely on the fact that modules over an $L_\infty$ algebra are symmetric monoidal over $\otimes_k$, 
+so that we can construct new modules from a given module by taking symmetric powers.
+Since
+\[
+\cliels(\Omega^*_c(V) \otimes \fh) = \bigoplus_{n \geq 0} \Sym^n(\Omega^*_c(V) \otimes \fh[1])
+\]
+as cochain complexes,
+we see that $\cliels(\Omega^*_c(V) \otimes \fh)$ acquires a canonical action of $\Omega^*(V) \otimes \fg$.
 In consequence, we have a cochain complex
 \[
-\clies(\Omega^*(V) \otimes \fg, (\Omega^*_c(V) \otimes \fh)_f)
+\clies(\Omega^*(V) \otimes \fg, \cliels(\Omega^*_c(V) \otimes \fh)_f)
 \]
@@
 Given an inclusion $i: V' \subset V$ of opens, if we take a form $\alpha \in \Omega^*(V)$ and a compactly supported form $\beta \in \Omega^*_c(V')$, then the wedge product $\alpha \wedge i_* \beta \in \Omega^*_c(V)$ after applying the extension-by-zero map $i_*: \Omega^*_c(V') \to \Omega^*_c(V)$ equals the wedge product $i_*(i^*\alpha \wedge \beta)$ arising from the restriction $i^* \alpha$ of $\alpha$ to~$V'$.
-In consequence, the action of $\Omega^*(V) \otimes \fg$ on $(\Omega^*_c(V') \otimes \fh)_f$ arising from the restriction map $\Omega^*(V) \otimes \fg \to \Omega^*(V') \otimes \fg$ of $L_\infty$ algebras agrees with action induced by the inclusion of $(\Omega^*_c(V') \otimes \fh)_f$ as a (strict) submodule of~$(\Omega^*_c(V) \otimes \fh)_f$.
+In consequence, the action of $\Omega^*(V) \otimes \fg$ on $\cliels(\Omega^*_c(V') \otimes \fh)_f$ arising from the restriction map $\Omega^*(V) \otimes \fg \to \Omega^*(V') \otimes \fg$ of $L_\infty$ algebras agrees with action induced by the inclusion of $\cliels(\Omega^*_c(V') \otimes \fh)_f$ as a (strict) submodule of~$\cliels(\Omega^*_c(V) \otimes \fh)_f$.
 This argument is manifestly associative under composition of inclusions, so we have shown our first claim.
@@
 \[
-V \mapsto \clies(\Omega^*(V) \otimes \fg, (\Omega^*_c(V) \otimes \fh)_f)
+V \mapsto \clies(\Omega^*(V) \otimes \fg, \cliels(\Omega^*_c(V) \otimes \fh)_f)
 \]
@@
 \[
-\clies(\Omega^*(D) \otimes \fg, (\Omega^*_c(D) \otimes \fh)_f) \xto{\simeq} \clies(\Omega^*(D) \otimes \fg, (\Omega^*_c(D) \otimes \fh)_f)
+\clies(\Omega^*(D) \otimes \fg, \cliels(\Omega^*_c(D) \otimes \fh)_f) \xto{\simeq} \clies(\Omega^*(D) \otimes \fg, \cliels(\Omega^*_c(D) \otimes \fh)_f)
 \]
@@
 In fact, it defines a {\em factorization} algebra, by arguments that can be found in \owen{chapter 6 of \cite{CG1} and elsewhere}.
+
+\begin{dfn}
+\label{dfn: centralizer for f}
+Let $\clies(\Omega^* \otimes \fg, (\bU_n \fh)_f)$ denote this factorization algebra on $\RR^n$ arising from the map $f: \fg \rightsquigarrow \fh$.
+\end{dfn}
 
@@
 
-We start by defining a pairing between the factorization algebras of Chevalley-Eilenberg (co)chains in order to use the universal property of centralizers.
-
-First note that compactly supported form embeds in all forms, therefore we can apply 
-any element of $\cliels\big(\fg \otimes \Omega^* , B\big)$ 
-to any element of $\cliels\big(\fg \otimes \Omega_c^* \big)$. Therefore, for any  $p\in \bN$, we have an evaluation 
-\begin{equation} \label{eqdef:ev} \begin{array}{c}\ev: Sym^p \big( \fg \otimes \Omega^* (U)[-1] ,B(U)\big)
-\otimes  Sym^p( \fg\otimes \Omega^*_c(U) [1]) \stackrel{ev}\longrightarrow B(U)  
-  \\
- (x,\Phi) \,\longmapsto\, (-1)^{p(|x|+p) } \Phi (x)\end{array}
-\end{equation} induced by this embedding  in all forms followed by evaluating on a function.
-
-Second, the augmentation of $B$ makes $B$ augmented as well (in the obvious sense of~\cite{Gi-NotesFactorization}) and this induces an augmentation on
-$\clies\big(\fg\otimes \Omega , B \big)$ as well as follows. 
-We have the canonical factorization algebra map  $\mathbf{1}$  defined, for any open $U$, by 
-\[\xymatrix{ k(U)=k  \ar[r]^{\quad \cong}& 
-B(\emptyset) \ar[r] & B(U)  } 
- \] where the last map is given by the factorization algebra structure of $B$. This gives the canonical element element 
- $\mathbf{1}\in \clies(\fg\otimes \Omega^*, B) )$ which is the unit $k\to \clies(\fg\otimes \Omega^*, B) )$
- of the factorization structure of 
- the Chevalley-Eilenberg cochain factorization algebras~\ref{dfn:CEofFact}.  
- The augmentation map is given by $\varphi\mapsto \varepsilon \circ \varphi \circ 
- \iota$ where $\iota: k(U) \cong k \hookrightarrow Sym(\fg \otimes \Omega (U) [1]) $ is the inclusion and $\varepsilon B(U)\to k(U)$ is the augmentation of 
- $B$. We therefore obtain a canonical splitting of factorization algebras 
- \begin{equation}\label{eq:splittingbyaugm}
-   \clies\big(\fg\otimes \Omega^*, B\big)  \, \cong \, k \oplus \overline{ \clies(\fg\otimes \Omega^*, B) )}
- \end{equation}
-given by the augmentation. Below~\ref{Rmk:defgraduationclie}, we refine  this splitting, using it  freely  on each-connected component, to obtain 
-a natural grading on it.
-
-We use the splitting and~\eqref{eqdef:ev} to define our pairing as follows. First for a \emph{connected} open subset $W$ of $\RR^n$, we define 
-\begin{multline}\label{eq:defevforconnected}
- \ev_f^W:   \clies (\fg\otimes \Omega (W), B(W)) \otimes \cliels\big(\fg \otimes \Omega_c^* (W)) 
- \\ \cong \, \left( k(W) \oplus \overline{\clies (\fg\otimes \Omega (W), B(W))  }\right) 
- \otimes \cliels\big(\fg \otimes \Omega_c^* (W))  \\ \cong
- \cliels\big(\fg \otimes \Omega_c^* (W))  \oplus  \left(\overline{\clies (\fg\otimes \Omega (W), B(W))  }\otimes \cliels\big(\fg \otimes \Omega_c^* (W)) 
- \right) \\
- \stackrel{ \mathbf{f}\oplus \ev}\longrightarrow  
- B(W)
-\end{multline}
-where $\mathbf{f}$ is the factorization algebra morphism  we are given.
-In other words, if $\varphi = \lambda \mathbf{1} \oplus \overline{\varphi}$ is the decomposition of $\varphi \in  \clies (\fg\otimes \Omega (W), B(W)) $,
-we have 
-\[ \ev_f^W(\varphi\otimes x)= \lambda \mathbf{f}(W)(x) + \overline{\varphi}(x). \]
-
-We extend this construction  to any 
- open subset in $\RR^n$ using the \lq\lq{}Leibniz rule\rq\rq{}, that is on using it freely on every connected components. 
- More precisely, 
-  write $U=\coprod_{i\in I} U_i$ the decomposition of an open into the  disjoint union 
-of its connected components. Using, the natural isomorphisms of complexes 
-\[Sym\big(\fg \otimes \Omega (U)[-1]\big) 
-\cong \bigotimes\limits_{i\in I} Sym\big(\fg \otimes \Omega ( U_i)[-1]\big), \mbox{  } 
-\bigotimes_{i\in I} \cliels\big(\fg \otimes \Omega_c^* (U_i)\big) \cong
-\cliels\big(\fg \otimes \Omega_c^* (U)\big)\] and
-$\bigotimes_{i\in I} B(U_i) 
-\stackrel{\simeq}\longrightarrow B(U)$, we obtain the 
- (natural) decomposition 
-\begin{multline}\label{eq:defgraduationoncentralizernonconnected}
- \clies\big(\fg\otimes \Omega^*(U), B(U)\big)  \, \cong \, 
- \Hom\left(\bigotimes\limits_{i\in I} Sym\Big(\fg\otimes \Omega (U_i)[-1]), 
- \bigotimes\limits_{i\in I} B(U_i)\right) \\ \cong \, 
- \bigotimes\limits_{i\in I}\left( k(U_i) \oplus \overline{\clies (\fg\otimes \Omega (U_i), B(U_i))  }\right).
-\end{multline}
-and we can therefore define 
-\begin{multline}\label{eq:defineevf}
- \ev_f^U: \clies (\fg\otimes \Omega (U), B(U)) \otimes \cliels\big(\fg \otimes \Omega_c^* (U)) 
- \\ \stackrel{\simeq}\longrightarrow  
-\bigotimes\limits_{i\in I}\left( k(U_i) \oplus \overline{\clies (\fg\otimes \Omega (U_i), B(U_i))  }\right) \otimes 
- \left(\bigotimes\limits_{i\in I}\cliels\big(\fg \otimes \Omega_c^* (U_i)\big)\right)  \\ 
- \stackrel{\bigotimes\limits_{i\in I}\ev^{U_i}_f}\longrightarrow  
- \bigotimes\limits_{i\in I} B(U_i) \stackrel{\mu_B}\longrightarrow B(U)
-\end{multline}
-where $\mu_B$ is the canonical structure map of the factorization algebra $B$ and the other maps are given by~\eqref{eq:defgraduationoncentralizernonconnected} 
-and~\eqref{eq:defevforconnected}.
-\greg{In~\eqref{eq:defgraduationoncentralizernonconnected} and definition of Chevalley Eilneberg complexes, one shall explain/takes care of the appropriate 
-things to do (like completion) for non-finitely dimensional Lie algebras}
-\greg{The decomposition used to extend $\ev$ on non-connected open can be done with any augmented $B$, simply by defining it onto the prefact alg obtained by tensoring 
-out on non-connected components and using the quasi-isomorphism canonical map to $\clies(\fg, B)$ in that case. Not sure which way is easier to define/mention}
-
-\begin{rmk}\label{Rmk:defgraduationclie} The decomposition~\eqref{eq:defgraduationoncentralizernonconnected} makes 
-the Chevalley-Eilenberg cochain complex with value on an open $U$ naturally\footnote{The grading
-is compatible (by the same argument as Lemma~\ref{L:pairingCE}) with the factorization algebra structure maps of
-$\clies(\fg\otimes \Omega, B)$} graded by the subsets of its connected components:
- \begin{equation}\label{eq:defgraduationoncentralizernonconnected2}
- \clies\big(\fg\otimes \Omega^*(U), B(U)\big)  \, \cong \, \bigoplus\limits_{J\subset I} {\clies}^{(J)}\big(\fg\otimes \Omega^*(U), B(U)\big) 
-\end{equation}
-where $J$ runs through all the (possibly empty) subsets of $I$.  Precisely, the $J$-piece is
-\begin{multline*}
-{\clies}^{(J)}\big(\fg\otimes \Omega^*(U), B(U)\big) = 
-\left(\bigotimes\limits_{j\in I\setminus J} k(U_j)\right) \otimes \left(\bigotimes\limits_{j\in J}
-\overline{\clies (\fg\otimes \Omega (U_j), B(U_j))  }\right) \\ \cong 
-\overline{\clies (\fg\otimes \Omega (\coprod\limits_{j\in_J}U_j), B(\coprod\limits_{j\in_J}U_j))  }.
-\end{multline*}
-We think of an element of ${\clies}^{(J)}\big(\fg\otimes \Omega^*(U), B(U)\big)$ has an element of ${\clies}\big(\fg\otimes \Omega^*(U), B(U)\big)$
-\emph{with support $\coprod\limits_{j\in J} U_j$}.   
-Note that the component $k$ in the decomposition~\eqref{eq:splittingbyaugm} is precisely the component 
-${\clies}^{(\emptyset)}\big(\fg\otimes \Omega^*(U), B(U)\big)$ corresponding to the empty family.
-\end{rmk}
-In other words, if $\varphi = \sum_{J\subset I} \varphi^{(J)}$ is the decomposition of $\varphi$ in its graded pieces, for all 
-$X= \bigotimes\limits_{i\in I} X_i \in \bigotimes\limits_{I}\cliels(\fg\otimes \Omega_c^*(U_i)) \cong \cliels(\fg\otimes \Omega^*_c(U))$, we 
-have the following formula generalizing the one for connected open  subsets:
-\begin{equation} \ev_f^U(\varphi\otimes X)= \sum_{J\subset I} \mu_B\left(\mathbf{f}\Big(\bigotimes\limits_{i\in I\setminus J} 
-X_i\Big)\otimes  \varphi^{(J)}\Big(\bigotimes\limits_{j\in J} 
-X_j\Big)\right) \end{equation}
-where $\mu_{B,J}: B\Big(\coprod\limits_{i\in I\setminus J}U_i\Big)\otimes B\Big(\coprod\limits_{j\in J}U_j\Big) \to B(U)$
-is the  structure map of $B$.
-
-\begin{lmm}\label{L:pairingCE}
- The pairing morphism $\ev_f$ defined by formula~\eqref{eq:defineevf} extends to a factorization algebra morphism
- \[\ev_f:  \cliels\big(\fg \otimes \Omega^* , B\big) \otimes \cliels\big(\fg \otimes \Omega_c^* \big) 
- \longrightarrow B.\]
+Our goal in this subsection is to construct a map of factorization algebras
+\[
+\Theta_{\bf{f}}: \clies(\Omega^* \otimes \fg, (\Omega^*_c \otimes \fh)_f) \otimes \bU_n \fg \to \bU_n \fh,
+\]
+while in the next subsection we will show it fits into a centralizer diagram.
+To produce our map, we first construct it separately on each open subset and then explain why the construction is functorial.
+
+Let $V \subset \RR^n$ be open.
+The canonical pairing between Lie algebra chains and cochains provides a canonical cochain map
+\[
+\clies(\Omega^*(V) \otimes \fg, \cliels(\Omega^*_c(V) \otimes \fh)_f) \otimes \cliels(\Omega^*(V) \otimes \fg) \to \cliels(\Omega^*_c(V) \otimes \fh)_f.
+\]
+The canonical inclusion $\Omega^*_c(V) \otimes \fg \hookrightarrow \Omega^*(V) \otimes \fg$ induces a canonical inclusion 
+\[
+\cliels(\Omega^*_c(V) \otimes \fg) \hookrightarrow \cliels(\Omega^*(V) \otimes \fg)
+\]
+and hence, precomposing this inclusion with the pairing, we obtain our desired map
+\[
+\Theta_{\bf{f}}(V): \clies(\Omega^*(V) \otimes \fg, (\Omega^*_c(V) \otimes \fh)_f) \otimes \bU_n \fg(V) \to \bU_n \fh(V)
+\]
+for each open~$V$.
+
+This construction is functorial in $V$ because wedge product of differential forms preserves support,
+so a minor variation on our argument above implies the following.
+
+\begin{lmm}
+The assignment
+\[
+V \mapsto \Theta_{\bf{f}}(V)
+\]
+determines a natural transformation between functors from ${\rm Opens}_{\RR^n}$ to~$\Ch_k$.
 \end{lmm}
-\begin{proof}
-
-\end{proof}
+
+\owen{Commented out below is an extensive argument by Greg about the existence and behavior of $\Theta_f$.
+If my explanation above is missing something crucial, I suspect it's addressed in that argument.}
+
+%We start by defining a pairing between the factorization algebras of Chevalley-Eilenberg (co)chains in order to use the universal property of centralizers.
+%
+%First note that compactly supported form embeds in all forms, therefore we can apply 
+%any element of $\cliels\big(\fg \otimes \Omega^* , B\big)$ 
+%to any element of $\cliels\big(\fg \otimes \Omega_c^* \big)$. Therefore, for any  $p\in \bN$, we have an evaluation 
+%\begin{equation} \label{eqdef:ev} \begin{array}{c}\ev: Sym^p \big( \fg \otimes \Omega^* (U)[-1] ,B(U)\big)
+%\otimes  Sym^p( \fg\otimes \Omega^*_c(U) [1]) \stackrel{ev}\longrightarrow B(U)  
+%  \\
+% (x,\Phi) \,\longmapsto\, (-1)^{p(|x|+p) } \Phi (x)\end{array}
+%\end{equation} induced by this embedding  in all forms followed by evaluating on a function.
+%
+%Second, the augmentation of $B$ makes $B$ augmented as well (in the obvious sense of~\cite{Gi-NotesFactorization}) and this induces an augmentation on
+%$\clies\big(\fg\otimes \Omega , B \big)$ as well as follows. 
+%We have the canonical factorization algebra map  $\mathbf{1}$  defined, for any open $U$, by 
+%\[\xymatrix{ k(U)=k  \ar[r]^{\quad \cong}& 
+%B(\emptyset) \ar[r] & B(U)  } 
+% \] where the last map is given by the factorization algebra structure of $B$. This gives the canonical element element 
+% $\mathbf{1}\in \clies(\fg\otimes \Omega^*, B) )$ which is the unit $k\to \clies(\fg\otimes \Omega^*, B) )$
+% of the factorization structure of 
+% the Chevalley-Eilenberg cochain factorization algebras~\ref{dfn:CEofFact}.  
+% The augmentation map is given by $\varphi\mapsto \varepsilon \circ \varphi \circ 
+% \iota$ where $\iota: k(U) \cong k \hookrightarrow Sym(\fg \otimes \Omega (U) [1]) $ is the inclusion and $\varepsilon B(U)\to k(U)$ is the augmentation of 
+% $B$. We therefore obtain a canonical splitting of factorization algebras 
+% \begin{equation}\label{eq:splittingbyaugm}
+%   \clies\big(\fg\otimes \Omega^*, B\big)  \, \cong \, k \oplus \overline{ \clies(\fg\otimes \Omega^*, B) )}
+% \end{equation}
+%given by the augmentation. Below~\ref{Rmk:defgraduationclie}, we refine  this splitting, using it  freely  on each-connected component, to obtain 
+%a natural grading on it.
+% 
+% 
+% 
+%
+%We use the splitting and~\eqref{eqdef:ev} to define our pairing as follows. First for a \emph{connected} open subset $W$ of $\RR^n$, we define 
+%\begin{multline}\label{eq:defevforconnected}
+% \ev_f^W:   \clies (\fg\otimes \Omega (W), B(W)) \otimes \cliels\big(\fg \otimes \Omega_c^* (W)) 
+% \\ \cong \, \left( k(W) \oplus \overline{\clies (\fg\otimes \Omega (W), B(W))  }\right) 
+% \otimes \cliels\big(\fg \otimes \Omega_c^* (W))  \\ \cong
+% \cliels\big(\fg \otimes \Omega_c^* (W))  \oplus  \left(\overline{\clies (\fg\otimes \Omega (W), B(W))  }\otimes \cliels\big(\fg \otimes \Omega_c^* (W)) 
+% \right) \\
+% \stackrel{ \mathbf{f}\oplus \ev}\longrightarrow  
+% B(W)
+%\end{multline}
+%where $\mathbf{f}$ is the factorization algebra morphism  we are given.
+%In other words, if $\varphi = \lambda \mathbf{1} \oplus \overline{\varphi}$ is the decomposition of $\varphi \in  \clies (\fg\otimes \Omega (W), B(W)) $,
+%we have 
+%\[ \ev_f^W(\varphi\otimes x)= \lambda \mathbf{f}(W)(x) + \overline{\varphi}(x). \]
+%
+%
+%
+%
+%
+%
+%
+%We extend this construction  to any 
+% open subset in $\RR^n$ using the \lq\lq{}Leibniz rule\rq\rq{}, that is on using it freely on every connected components. 
+% More precisely, 
+%  write $U=\coprod_{i\in I} U_i$ the decomposition of an open into the  disjoint union 
+%of its connected components. Using, the natural isomorphisms of complexes 
+%\[Sym\big(\fg \otimes \Omega (U)[-1]\big) 
+%\cong \bigotimes\limits_{i\in I} Sym\big(\fg \otimes \Omega ( U_i)[-1]\big), \mbox{  } 
+%\bigotimes_{i\in I} \cliels\big(\fg \otimes \Omega_c^* (U_i)\big) \cong
+%\cliels\big(\fg \otimes \Omega_c^* (U)\big)\] and
+%$\bigotimes_{i\in I} B(U_i) 
+%\stackrel{\simeq}\longrightarrow B(U)$, we obtain the 
+% (natural) decomposition 
+%\begin{multline}\label{eq:defgraduationoncentralizernonconnected}
+% \clies\big(\fg\otimes \Omega^*(U), B(U)\big)  \, \cong \, 
+% \Hom\left(\bigotimes\limits_{i\in I} Sym\Big(\fg\otimes \Omega (U_i)[-1]), 
+% \bigotimes\limits_{i\in I} B(U_i)\right) \\ \cong \, 
+% \bigotimes\limits_{i\in I}\left( k(U_i) \oplus \overline{\clies (\fg\otimes \Omega (U_i), B(U_i))  }\right).
+%\end{multline}
+%and we can therefore define 
+%\begin{multline}\label{eq:defineevf}
+% \ev_f^U: \clies (\fg\otimes \Omega (U), B(U)) \otimes \cliels\big(\fg \otimes \Omega_c^* (U)) 
+% \\ \stackrel{\simeq}\longrightarrow  
+%\bigotimes\limits_{i\in I}\left( k(U_i) \oplus \overline{\clies (\fg\otimes \Omega (U_i), B(U_i))  }\right) \otimes 
+% \left(\bigotimes\limits_{i\in I}\cliels\big(\fg \otimes \Omega_c^* (U_i)\big)\right)  \\ 
+% \stackrel{\bigotimes\limits_{i\in I}\ev^{U_i}_f}\longrightarrow  
+% \bigotimes\limits_{i\in I} B(U_i) \stackrel{\mu_B}\longrightarrow B(U)
+%\end{multline}
+%where $\mu_B$ is the canonical structure map of the factorization algebra $B$ and the other maps are given by~\eqref{eq:defgraduationoncentralizernonconnected} 
+%and~\eqref{eq:defevforconnected}.
+%\greg{In~\eqref{eq:defgraduationoncentralizernonconnected} and definition of Chevalley Eilneberg complexes, one shall explain/takes care of the appropriate 
+%things to do (like completion) for non-finitely dimensional Lie algebras}
+%\greg{The decomposition used to extend $\ev$ on non-connected open can be done with any augmented $B$, simply by defining it onto the prefact alg obtained by tensoring 
+%out on non-connected components and using the quasi-isomorphism canonical map to $\clies(\fg, B)$ in that case. Not sure which way is easier to define/mention}
+%
+%
+%\begin{rmk}\label{Rmk:defgraduationclie} The decomposition~\eqref{eq:defgraduationoncentralizernonconnected} makes 
+%the Chevalley-Eilenberg cochain complex with value on an open $U$ naturally\footnote{The grading
+%is compatible (by the same argument as Lemma~\ref{L:pairingCE}) with the factorization algebra structure maps of
+%$\clies(\fg\otimes \Omega, B)$} graded by the subsets of its connected components:
+% \begin{equation}\label{eq:defgraduationoncentralizernonconnected2}
+% \clies\big(\fg\otimes \Omega^*(U), B(U)\big)  \, \cong \, \bigoplus\limits_{J\subset I} {\clies}^{(J)}\big(\fg\otimes \Omega^*(U), B(U)\big) 
+%\end{equation}
+%where $J$ runs through all the (possibly empty) subsets of $I$.  Precisely, the $J$-piece is
+%\begin{multline*}
+%{\clies}^{(J)}\big(\fg\otimes \Omega^*(U), B(U)\big) = 
+%\left(\bigotimes\limits_{j\in I\setminus J} k(U_j)\right) \otimes \left(\bigotimes\limits_{j\in J}
+%\overline{\clies (\fg\otimes \Omega (U_j), B(U_j))  }\right) \\ \cong 
+%\overline{\clies (\fg\otimes \Omega (\coprod\limits_{j\in_J}U_j), B(\coprod\limits_{j\in_J}U_j))  }.
+%\end{multline*}
+%We think of an element of ${\clies}^{(J)}\big(\fg\otimes \Omega^*(U), B(U)\big)$ has an element of ${\clies}\big(\fg\otimes \Omega^*(U), B(U)\big)$
+%\emph{with support $\coprod\limits_{j\in J} U_j$}.   
+%Note that the component $k$ in the decomposition~\eqref{eq:splittingbyaugm} is precisely the component 
+%${\clies}^{(\emptyset)}\big(\fg\otimes \Omega^*(U), B(U)\big)$ corresponding to the empty family.
+%\end{rmk}
+%In other words, if $\varphi = \sum_{J\subset I} \varphi^{(J)}$ is the decomposition of $\varphi$ in its graded pieces, for all 
+%$X= \bigotimes\limits_{i\in I} X_i \in \bigotimes\limits_{I}\cliels(\fg\otimes \Omega_c^*(U_i)) \cong \cliels(\fg\otimes \Omega^*_c(U))$, we 
+%have the following formula generalizing the one for connected open  subsets:
+%\begin{equation} \ev_f^U(\varphi\otimes X)= \sum_{J\subset I} \mu_B\left(\mathbf{f}\Big(\bigotimes\limits_{i\in I\setminus J} 
+%X_i\Big)\otimes  \varphi^{(J)}\Big(\bigotimes\limits_{j\in J} 
+%X_j\Big)\right) \end{equation}
+%where $\mu_{B,J}: B\Big(\coprod\limits_{i\in I\setminus J}U_i\Big)\otimes B\Big(\coprod\limits_{j\in J}U_j\Big) \to B(U)$
+%is the  structure map of $B$.
+%
+
+We need to show that this natural transformation extends to a morphism of prefactorization algebras,
+i.e., that it intertwines with the operations over the colored operad ${\rm Opens}_{\RR^n}^\sqcup$.
+Here we use the fact that the evaluation pairing between Lie algebra chains and cochains plays nicely with products of $L_\infty$ algebras, in the following sense.
+Let $\fX, \fY$ be $L_\infty$ algebras and let $M, N$ be modules for those respective $L_\infty$ algebras.
+The direct sum $M \oplus N$ admits a natural action of the product $L_\infty$ algebra $\fX \times \fY$.
+Then the isomorphisms
+\begin{align*}
+\clies(\fX \times \fY, M \oplus N) \otimes \cliels(\fX \times \fY) 
+&\cong (\clies(\fX, M) \otimes \clies(\fY,N) ) \otimes (\cliels(\fX) \otimes \cliels(\fY) ) \\
+&\cong (\clies(\fX,M) \otimes \cliels(\fX) ) \otimes (\cliels(\fY,N) \otimes \cliels(\fY) )
+\end{align*}
+precompose with the tensored evaluation pairings
+\[
+\cong (\clies(\fX,M) \otimes \cliels(\fX) ) \otimes (\cliels(\fY,N) \otimes \cliels(\fY) ) \xto{\ev_\fX \otimes \ev_\fY} M \otimes N
+\]
+to provide a canonical map
+\[
+\clies(\fX \times \fY, M \oplus N) \otimes \cliels(\fX \times \fY) \to M \otimes N.
+\]
+In light of this observation and the fact that functors such as $\Omega^* \otimes \fg$ and $\Omega^*_c \otimes \fh$ send disjoint unions to products of $L_\infty$ algebras,
+we deduce the desired result.
+
+\begin{lmm}
+\label{L:pairingCE}
+The natural transformation $\Theta_{\bf{f}}$ determines a map of strict prefactorization algebras,
+i.e., algebras over the colored operad ${\rm Opens}_{\RR^n}^\sqcup$.
+\end{lmm}
+
+\subsection{}
+
 We write, $1$ for the factorization algebra map defined, for any open $U$, by 

### 2020-09-01 draft.tex
finetuning

@@
 & {\frak Z}_{E_n}(f) \otimes A \arrow[dr] & \\
-A \arrow[ur, "u"] \arrow[rr, "f"] && B
+A \arrow[ur, "u \otimes \id"] \arrow[rr, "f"] && B
 \end{tikzcd}
 \]
-where $u$ is the tensor product of the unit map $1_\cC \to {\frak Z}_{E_n}(f)$ and the identity map $A \to A$.
+where the arrow in the upper left is the tensor product of the unit map $u: 1_\cC \to {\frak Z}_{E_n}(f)$ and the identity map $\id: A \to A$.
 The {\em center} of an $E_n$ algebra $A$ is the centralizer of its identity morphism $\id_A: A \to A$. 
@@
 
-We have implemented the first step in the proof strategy.
-This section is devoted to the remaining steps.
-First, we explain steps (2)-(4), which are rather formal.
-Next, we define the $\Disk_n$-algebra $\clies(\Omega^* \otimes \fg, {\tt B}_f)$ as a kind of convolution algebra.
-Finally, we get to the heart of the construction:
+Recall the overall strategy.
+First, we define a factorization algebra $\clies(\Omega^* \otimes \fg, (\bU_n \fh)_f)$ as a kind of convolution factorization algebra.
+Then we get to the heart of the construction:
 we show that this convolution algebra naturally sits inside a centralizer diagram.
@@
 \[
-\Theta_f: \clies\big(\fg\otimes \Omega , B \big) \longrightarrow  {\frak Z}(\mathbf{f})
-\]
-where ${\frak Z}(\mathbf{f})$ is the centralizer of locally constant $\Disk_n$-algebras~(\ref{D:centralizerFacAlgebra}).
+\theta_{\bf{f}}: \clies\big(\fg\otimes \Omega , B \big) \longrightarrow  {\frak Z}(\mathbf{f})
+\]
+where ${\frak Z}(\mathbf{f})$ is a factorization algebra that models the centralizer ${\frak Z}(f)$ of the map $f$.
 \owen{Calibrate notations!}
-It is then a direct computation to verify $\Theta_f$ is a quasi-isomorphism.
+It is then a direct computation to verify $\theta_f$ is a quasi-isomorphism,
+using the Francis-Lurie result mentioned earlier.
 
@@
 
-\owen{Below is Greg's summary of the proof.}
-
-Let us start by summarizing the proof. The idea, using theorem~\ref{T:En=Fac}, 
-is that we only have to prove the factorization algebra part of the main theorem. 
-To do so, we first use the universal property of the centralizer to obtain 
-a canonical factorization algebra map 
-\[\Theta_f: \clies\big(\fg\otimes \Omega , B \big) \longrightarrow  {\frak Z}(\mathbf{f})\]
-where ${\frak Z}(\mathbf{f})$ is the centralizer of locally constant factorization algebras (\ref{D:centralizerFacAlgebra}).
-
-Using the fundamental properties of universal $E_n$-enveloping algebra, we then prove that 
-this map is a weak-equivalence.
-
 \subsection{Standard manipulations with $L_\infty$ algebras and their modules}
 
-\owen{I want to recall briefly how an $L_\infty$ action on a cochain complex leads to all the variants of CE (co)chains.}
-
-To any $\fg$-module $M$ (wether $\fg$ is a dg Lie algebra or an $L_\infty$-algebra), 
+\owen{I want to recall briefly how an $L_\infty$ action on a cochain complex leads to all the variants of CE (co)chains.
+It can just be a compendium of facts we use below.}
+
+To any $\fg$-module $M$ (whether $\fg$ is a dg Lie algebra or an $L_\infty$-algebra), 
 we can associate its Chevalley-Eilenberg cochain complex defined 
@@
 \begin{equation}
- \label{eq:defev} ev: \clies(\fg, M) \otimes Sym(\fg[-1])\to M
+ \label{eq:defev} \ev: \clies(\fg, M) \otimes Sym(\fg[-1])\to M
 \end{equation}
@@
 \[
-\Theta_{\bf{f}}: \clies(\Omega^* \otimes \fg, (\Omega^*_c \otimes \fh)_f) \otimes \bU_n \fg \to \bU_n \fh,
+\ev_{\bf{f}}: \clies(\Omega^* \otimes \fg, (\Omega^*_c \otimes \fh)_f) \otimes \bU_n \fg \to \bU_n \fh,
 \]
@@
 \[
-\Theta_{\bf{f}}(V): \clies(\Omega^*(V) \otimes \fg, (\Omega^*_c(V) \otimes \fh)_f) \otimes \bU_n \fg(V) \to \bU_n \fh(V)
+\ev_{\bf{f}}(V): \clies(\Omega^*(V) \otimes \fg, \cliels(\Omega^*_c(V) \otimes \fh)_f) \otimes \bU_n \fg(V) \to \bU_n \fh(V)
 \]
@@
 \[
-V \mapsto \Theta_{\bf{f}}(V)
+V \mapsto \ev_{\bf{f}}(V)
 \]
@@
 \label{L:pairingCE}
-The natural transformation $\Theta_{\bf{f}}$ determines a map of strict prefactorization algebras,
+The natural transformation $\ev_{\bf{f}}$ determines a map of strict prefactorization algebras,
 i.e., algebras over the colored operad ${\rm Opens}_{\RR^n}^\sqcup$.
@@
 
-\subsection{}
-
-We write, $1$ for the factorization algebra map defined, for any open $U$, by 
-\[\xymatrix{ k(U)=k  \ar[r]^{\quad \cong}& 
-B(\emptyset) \ar[r] & B(U)  } 
- \] where the last map is given by the factorization algebra structure of $B$.
-This gives the canonical element element $\mathbf{1}\in \clies(\fg\otimes \Omega^*, B) )$ which is the unit of the factorization structure of
- the Chevalley-Eilenberg cochain factorization algebras.
-
-\begin{lmm}\label{L:ComTriangCent} The triangle 
- $$ \xymatrix{
-& \clies ( \fg\otimes \Omega^* , B) \otimes \cliels(\fg\otimes \Omega^*_c   )
-\ar[dr]^{\ev_f} & \\
-\cliels(\fg\otimes \Omega^*_c ) \ar[ur]^{\mathbf{1} \otimes \id} \ar[rr]^{\mathbf{f}}  & &  B.}
- $$
-is a commutative triangle of factorization algebras maps.
+\subsection{The pairing fits into a centralizer diagram}
+
+For any factorization algebra $B$ on $\RR^n$, 
+there is a unit map of factorization algebras  
+\[
+1(U) = k \cong 1(\emptyset)  \xto{\cong}
+B(\emptyset) \to B(V)  
+\] 
+for each open set $V$, where the last map is structure map of~$B$.
+
+\begin{lmm}\label{L:ComTriangCent} 
+There is a commutative triangle 
+\[
+\xymatrix{
+& \clies ( \Omega \otimes \fg , (\bU_n \fh)_f) \otimes \bU_n \fg
+\ar[dr]^{\ev_{\bf{f}}} & \\
+\bU_n \fg \ar[ur]^{\mathbf{1} \otimes \id} \ar[rr]^{\mathbf{f}}  & &  \bU_n \fh}
+\]
+of maps of factorization algebras.
 \end{lmm}
+
 \begin{proof}
+This triangle commutes on the nose, as we now show.
+What we need to show is how the unit map $u$ for $\clies ( \Omega \otimes \fg , (\bU_n \fh)_f)$ encodes the map $\bf{f}$.
+\owen{I'm stuck. Greg's statement is below.}
  It follows from lemma~\ref{L:pairingCE} that this is a diagram of factorization algebras.
@@
 
-By universal property of the centralizer (definition~\ref{D:centralizerFacAlgebra}), lemma~\ref{L:ComTriangCent} implies that the pairing $\ev_f \,:\,\cliels\big(\fg \otimes \Omega^* , B\big) \otimes \cliels\big(\fg \otimes \Omega_c^* \big)
- \longrightarrow B$ induces 
-a canonical morphism of factorization algebras
-\begin{equation}\label{eq:canonicaltocenter}
-\theta_f: \clies\big(\fg\otimes \Omega , B \big) \longrightarrow  {\frak Z}(\mathbf{f}). 
+By universal property of the centralizer (definition~\ref{D:centralizerFacAlgebra}), lemma~\ref{L:ComTriangCent} implies that the pairing $\ev_{\bf{f}}$ induces a canonical morphism 
+\begin{equation}
+\label{eq:canonicaltocenter}
+\theta_{\bf{f}}: \clies\big(\fg\otimes \Omega , B \big) \longrightarrow  {\frak Z}(\mathbf{f})
 \end{equation}
-
-\subsection{The map $\theta_f$ is a weak equivalence.} 
+of factorization algebras.
+
+\subsection{The map $\theta_{\bf{f}}$ is a weak equivalence.}
+
 We have defined a functorial (in $f$) factorization algebras map 

### 2020-09-01 draft.tex
working on the unit

@@
 \[
-\tilde{f}: \Omega^*_c(V) \otimes \fg \to \Omega^*_c(V) \otimes \fh
+\tilde{f}: \Omega^*_c(V) \otimes \fg \rightsquigarrow \Omega^*_c(V) \otimes \fh
 \]
@@
 
-%We start by defining a pairing between the factorization algebras of Chevalley-Eilenberg (co)chains in order to use the universal property of centralizers.
-%
-%First note that compactly supported form embeds in all forms, therefore we can apply 
-%any element of $\cliels\big(\fg \otimes \Omega^* , B\big)$ 
-%to any element of $\cliels\big(\fg \otimes \Omega_c^* \big)$. Therefore, for any  $p\in \bN$, we have an evaluation 
-%\begin{equation} \label{eqdef:ev} \begin{array}{c}\ev: Sym^p \big( \fg \otimes \Omega^* (U)[-1] ,B(U)\big)
-%\otimes  Sym^p( \fg\otimes \Omega^*_c(U) [1]) \stackrel{ev}\longrightarrow B(U)  
-%  \\
-% (x,\Phi) \,\longmapsto\, (-1)^{p(|x|+p) } \Phi (x)\end{array}
-%\end{equation} induced by this embedding  in all forms followed by evaluating on a function.
-%
-%Second, the augmentation of $B$ makes $B$ augmented as well (in the obvious sense of~\cite{Gi-NotesFactorization}) and this induces an augmentation on
-%$\clies\big(\fg\otimes \Omega , B \big)$ as well as follows. 
-%We have the canonical factorization algebra map  $\mathbf{1}$  defined, for any open $U$, by 
-%\[\xymatrix{ k(U)=k  \ar[r]^{\quad \cong}& 
-%B(\emptyset) \ar[r] & B(U)  } 
-% \] where the last map is given by the factorization algebra structure of $B$. This gives the canonical element element 
-% $\mathbf{1}\in \clies(\fg\otimes \Omega^*, B) )$ which is the unit $k\to \clies(\fg\otimes \Omega^*, B) )$
-% of the factorization structure of 
-% the Chevalley-Eilenberg cochain factorization algebras~\ref{dfn:CEofFact}.  
-% The augmentation map is given by $\varphi\mapsto \varepsilon \circ \varphi \circ 
-% \iota$ where $\iota: k(U) \cong k \hookrightarrow Sym(\fg \otimes \Omega (U) [1]) $ is the inclusion and $\varepsilon B(U)\to k(U)$ is the augmentation of 
-% $B$. We therefore obtain a canonical splitting of factorization algebras 
-% \begin{equation}\label{eq:splittingbyaugm}
-%   \clies\big(\fg\otimes \Omega^*, B\big)  \, \cong \, k \oplus \overline{ \clies(\fg\otimes \Omega^*, B) )}
-% \end{equation}
-%given by the augmentation. Below~\ref{Rmk:defgraduationclie}, we refine  this splitting, using it  freely  on each-connected component, to obtain 
-%a natural grading on it.
-% 
-% 
-% 
-%
-%We use the splitting and~\eqref{eqdef:ev} to define our pairing as follows. First for a \emph{connected} open subset $W$ of $\RR^n$, we define 
-%\begin{multline}\label{eq:defevforconnected}
-% \ev_f^W:   \clies (\fg\otimes \Omega (W), B(W)) \otimes \cliels\big(\fg \otimes \Omega_c^* (W)) 
-% \\ \cong \, \left( k(W) \oplus \overline{\clies (\fg\otimes \Omega (W), B(W))  }\right) 
-% \otimes \cliels\big(\fg \otimes \Omega_c^* (W))  \\ \cong
-% \cliels\big(\fg \otimes \Omega_c^* (W))  \oplus  \left(\overline{\clies (\fg\otimes \Omega (W), B(W))  }\otimes \cliels\big(\fg \otimes \Omega_c^* (W)) 
-% \right) \\
-% \stackrel{ \mathbf{f}\oplus \ev}\longrightarrow  
-% B(W)
-%\end{multline}
-%where $\mathbf{f}$ is the factorization algebra morphism  we are given.
-%In other words, if $\varphi = \lambda \mathbf{1} \oplus \overline{\varphi}$ is the decomposition of $\varphi \in  \clies (\fg\otimes \Omega (W), B(W)) $,
-%we have 
-%\[ \ev_f^W(\varphi\otimes x)= \lambda \mathbf{f}(W)(x) + \overline{\varphi}(x). \]
-%
-%
-%
-%
-%
-%
-%
-%We extend this construction  to any 
-% open subset in $\RR^n$ using the \lq\lq{}Leibniz rule\rq\rq{}, that is on using it freely on every connected components. 
-% More precisely, 
-%  write $U=\coprod_{i\in I} U_i$ the decomposition of an open into the  disjoint union 
-%of its connected components. Using, the natural isomorphisms of complexes 
-%\[Sym\big(\fg \otimes \Omega (U)[-1]\big) 
-%\cong \bigotimes\limits_{i\in I} Sym\big(\fg \otimes \Omega ( U_i)[-1]\big), \mbox{  } 
-%\bigotimes_{i\in I} \cliels\big(\fg \otimes \Omega_c^* (U_i)\big) \cong
-%\cliels\big(\fg \otimes \Omega_c^* (U)\big)\] and
-%$\bigotimes_{i\in I} B(U_i) 
-%\stackrel{\simeq}\longrightarrow B(U)$, we obtain the 
-% (natural) decomposition 
-%\begin{multline}\label{eq:defgraduationoncentralizernonconnected}
-% \clies\big(\fg\otimes \Omega^*(U), B(U)\big)  \, \cong \, 
-% \Hom\left(\bigotimes\limits_{i\in I} Sym\Big(\fg\otimes \Omega (U_i)[-1]), 
-% \bigotimes\limits_{i\in I} B(U_i)\right) \\ \cong \, 
-% \bigotimes\limits_{i\in I}\left( k(U_i) \oplus \overline{\clies (\fg\otimes \Omega (U_i), B(U_i))  }\right).
-%\end{multline}
-%and we can therefore define 
-%\begin{multline}\label{eq:defineevf}
-% \ev_f^U: \clies (\fg\otimes \Omega (U), B(U)) \otimes \cliels\big(\fg \otimes \Omega_c^* (U)) 
-% \\ \stackrel{\simeq}\longrightarrow  
-%\bigotimes\limits_{i\in I}\left( k(U_i) \oplus \overline{\clies (\fg\otimes \Omega (U_i), B(U_i))  }\right) \otimes 
-% \left(\bigotimes\limits_{i\in I}\cliels\big(\fg \otimes \Omega_c^* (U_i)\big)\right)  \\ 
-% \stackrel{\bigotimes\limits_{i\in I}\ev^{U_i}_f}\longrightarrow  
-% \bigotimes\limits_{i\in I} B(U_i) \stackrel{\mu_B}\longrightarrow B(U)
-%\end{multline}
-%where $\mu_B$ is the canonical structure map of the factorization algebra $B$ and the other maps are given by~\eqref{eq:defgraduationoncentralizernonconnected} 
-%and~\eqref{eq:defevforconnected}.
-%\greg{In~\eqref{eq:defgraduationoncentralizernonconnected} and definition of Chevalley Eilneberg complexes, one shall explain/takes care of the appropriate 
-%things to do (like completion) for non-finitely dimensional Lie algebras}
-%\greg{The decomposition used to extend $\ev$ on non-connected open can be done with any augmented $B$, simply by defining it onto the prefact alg obtained by tensoring 
-%out on non-connected components and using the quasi-isomorphism canonical map to $\clies(\fg, B)$ in that case. Not sure which way is easier to define/mention}
-%
-%
-%\begin{rmk}\label{Rmk:defgraduationclie} The decomposition~\eqref{eq:defgraduationoncentralizernonconnected} makes 
-%the Chevalley-Eilenberg cochain complex with value on an open $U$ naturally\footnote{The grading
-%is compatible (by the same argument as Lemma~\ref{L:pairingCE}) with the factorization algebra structure maps of
-%$\clies(\fg\otimes \Omega, B)$} graded by the subsets of its connected components:
-% \begin{equation}\label{eq:defgraduationoncentralizernonconnected2}
-% \clies\big(\fg\otimes \Omega^*(U), B(U)\big)  \, \cong \, \bigoplus\limits_{J\subset I} {\clies}^{(J)}\big(\fg\otimes \Omega^*(U), B(U)\big) 
-%\end{equation}
-%where $J$ runs through all the (possibly empty) subsets of $I$.  Precisely, the $J$-piece is
-%\begin{multline*}
-%{\clies}^{(J)}\big(\fg\otimes \Omega^*(U), B(U)\big) = 
-%\left(\bigotimes\limits_{j\in I\setminus J} k(U_j)\right) \otimes \left(\bigotimes\limits_{j\in J}
-%\overline{\clies (\fg\otimes \Omega (U_j), B(U_j))  }\right) \\ \cong 
-%\overline{\clies (\fg\otimes \Omega (\coprod\limits_{j\in_J}U_j), B(\coprod\limits_{j\in_J}U_j))  }.
-%\end{multline*}
-%We think of an element of ${\clies}^{(J)}\big(\fg\otimes \Omega^*(U), B(U)\big)$ has an element of ${\clies}\big(\fg\otimes \Omega^*(U), B(U)\big)$
-%\emph{with support $\coprod\limits_{j\in J} U_j$}.   
-%Note that the component $k$ in the decomposition~\eqref{eq:splittingbyaugm} is precisely the component 
-%${\clies}^{(\emptyset)}\big(\fg\otimes \Omega^*(U), B(U)\big)$ corresponding to the empty family.
-%\end{rmk}
-%In other words, if $\varphi = \sum_{J\subset I} \varphi^{(J)}$ is the decomposition of $\varphi$ in its graded pieces, for all 
-%$X= \bigotimes\limits_{i\in I} X_i \in \bigotimes\limits_{I}\cliels(\fg\otimes \Omega_c^*(U_i)) \cong \cliels(\fg\otimes \Omega^*_c(U))$, we 
-%have the following formula generalizing the one for connected open  subsets:
-%\begin{equation} \ev_f^U(\varphi\otimes X)= \sum_{J\subset I} \mu_B\left(\mathbf{f}\Big(\bigotimes\limits_{i\in I\setminus J} 
-%X_i\Big)\otimes  \varphi^{(J)}\Big(\bigotimes\limits_{j\in J} 
-%X_j\Big)\right) \end{equation}
-%where $\mu_{B,J}: B\Big(\coprod\limits_{i\in I\setminus J}U_i\Big)\otimes B\Big(\coprod\limits_{j\in J}U_j\Big) \to B(U)$
-%is the  structure map of $B$.
-%
+\greg{
+We start by defining a pairing between the factorization algebras of Chevalley-Eilenberg (co)chains in order to use the universal property of centralizers.\\
+First note that compactly supported form embeds in all forms, therefore we can apply 
+any element of $\cliels\big(\fg \otimes \Omega^* , B\big)$ 
+to any element of $\cliels\big(\fg \otimes \Omega_c^* \big)$. Therefore, for any  $p\in \bN$, we have an evaluation 
+\begin{equation} \label{eqdef:ev} \begin{array}{c}\ev: Sym^p \big( \fg \otimes \Omega^* (U)[-1] ,B(U)\big)
+\otimes  Sym^p( \fg\otimes \Omega^*_c(U) [1]) \stackrel{ev}\longrightarrow B(U)  
+  \\
+ (x,\Phi) \,\longmapsto\, (-1)^{p(|x|+p) } \Phi (x)\end{array}
+\end{equation} induced by this embedding  in all forms followed by evaluating on a function.\\
+Second, the augmentation of $B$ makes $B$ augmented as well (in the obvious sense of~\cite{Gi-NotesFactorization}) and this induces an augmentation on
+$\clies\big(\fg\otimes \Omega , B \big)$ as well as follows. 
+We have the canonical factorization algebra map  $\mathbf{1}$  defined, for any open $U$, by 
+\[\xymatrix{ k(U)=k  \ar[r]^{\quad \cong}& 
+B(\emptyset) \ar[r] & B(U)  } 
+ \] where the last map is given by the factorization algebra structure of $B$. This gives the canonical element element 
+ $\mathbf{1}\in \clies(\fg\otimes \Omega^*, B) )$ which is the unit $k\to \clies(\fg\otimes \Omega^*, B) )$
+ of the factorization structure of 
+ the Chevalley-Eilenberg cochain factorization algebras~\ref{dfn:CEofFact}.  
+ The augmentation map is given by $\varphi\mapsto \varepsilon \circ \varphi \circ 
+ \iota$ where $\iota: k(U) \cong k \hookrightarrow Sym(\fg \otimes \Omega (U) [1]) $ is the inclusion and $\varepsilon B(U)\to k(U)$ is the augmentation of 
+ $B$. We therefore obtain a canonical splitting of factorization algebras 
+ \begin{equation}\label{eq:splittingbyaugm}
+   \clies\big(\fg\otimes \Omega^*, B\big)  \, \cong \, k \oplus \overline{ \clies(\fg\otimes \Omega^*, B) )}
+ \end{equation}
+given by the augmentation. Below~\ref{Rmk:defgraduationclie}, we refine  this splitting, using it  freely  on each-connected component, to obtain 
+a natural grading on it.\\
+We use the splitting and~\eqref{eqdef:ev} to define our pairing as follows. First for a \emph{connected} open subset $W$ of $\RR^n$, we define 
+\begin{multline}\label{eq:defevforconnected}
+ \ev_f^W:   \clies (\fg\otimes \Omega (W), B(W)) \otimes \cliels\big(\fg \otimes \Omega_c^* (W)) 
+ \\ \cong \, \left( k(W) \oplus \overline{\clies (\fg\otimes \Omega (W), B(W))  }\right) 
+ \otimes \cliels\big(\fg \otimes \Omega_c^* (W))  \\ \cong
+ \cliels\big(\fg \otimes \Omega_c^* (W))  \oplus  \left(\overline{\clies (\fg\otimes \Omega (W), B(W))  }\otimes \cliels\big(\fg \otimes \Omega_c^* (W)) 
+ \right) \\
+ \stackrel{ \mathbf{f}\oplus \ev}\longrightarrow  
+ B(W)
+\end{multline}
+where $\mathbf{f}$ is the factorization algebra morphism  we are given.
+In other words, if $\varphi = \lambda \mathbf{1} \oplus \overline{\varphi}$ is the decomposition of $\varphi \in  \clies (\fg\otimes \Omega (W), B(W)) $,
+we have 
+\[ \ev_f^W(\varphi\otimes x)= \lambda \mathbf{f}(W)(x) + \overline{\varphi}(x). \]
+We extend this construction  to any 
+ open subset in $\RR^n$ using the \lq\lq{}Leibniz rule\rq\rq{}, that is on using it freely on every connected components. 
+ More precisely, 
+  write $U=\coprod_{i\in I} U_i$ the decomposition of an open into the  disjoint union 
+of its connected components. Using, the natural isomorphisms of complexes 
+\[Sym\big(\fg \otimes \Omega (U)[-1]\big) 
+\cong \bigotimes\limits_{i\in I} Sym\big(\fg \otimes \Omega ( U_i)[-1]\big), \mbox{  } 
+\bigotimes_{i\in I} \cliels\big(\fg \otimes \Omega_c^* (U_i)\big) \cong
+\cliels\big(\fg \otimes \Omega_c^* (U)\big)\] and
+$\bigotimes_{i\in I} B(U_i) 
+\stackrel{\simeq}\longrightarrow B(U)$, we obtain the 
+ (natural) decomposition 
+\begin{multline}\label{eq:defgraduationoncentralizernonconnected}
+ \clies\big(\fg\otimes \Omega^*(U), B(U)\big)  \, \cong \, 
+ \Hom\left(\bigotimes\limits_{i\in I} Sym\Big(\fg\otimes \Omega (U_i)[-1]), 
+ \bigotimes\limits_{i\in I} B(U_i)\right) \\ \cong \, 
+ \bigotimes\limits_{i\in I}\left( k(U_i) \oplus \overline{\clies (\fg\otimes \Omega (U_i), B(U_i))  }\right).
+\end{multline}
+and we can therefore define 
+\begin{multline}\label{eq:defineevf}
+ \ev_f^U: \clies (\fg\otimes \Omega (U), B(U)) \otimes \cliels\big(\fg \otimes \Omega_c^* (U)) 
+ \\ \stackrel{\simeq}\longrightarrow  
+\bigotimes\limits_{i\in I}\left( k(U_i) \oplus \overline{\clies (\fg\otimes \Omega (U_i), B(U_i))  }\right) \otimes 
+ \left(\bigotimes\limits_{i\in I}\cliels\big(\fg \otimes \Omega_c^* (U_i)\big)\right)  \\ 
+ \stackrel{\bigotimes\limits_{i\in I}\ev^{U_i}_f}\longrightarrow  
+ \bigotimes\limits_{i\in I} B(U_i) \stackrel{\mu_B}\longrightarrow B(U)
+\end{multline}
+where $\mu_B$ is the canonical structure map of the factorization algebra $B$ and the other maps are given by~\eqref{eq:defgraduationoncentralizernonconnected} 
+and~\eqref{eq:defevforconnected}.
+\greg{In~\eqref{eq:defgraduationoncentralizernonconnected} and definition of Chevalley Eilneberg complexes, one shall explain/takes care of the appropriate 
+things to do (like completion) for non-finitely dimensional Lie algebras}
+\greg{The decomposition used to extend $\ev$ on non-connected open can be done with any augmented $B$, simply by defining it onto the prefact alg obtained by tensoring 
+out on non-connected components and using the quasi-isomorphism canonical map to $\clies(\fg, B)$ in that case. Not sure which way is easier to define/mention}\\
+\begin{rmk}\label{Rmk:defgraduationclie} The decomposition~\eqref{eq:defgraduationoncentralizernonconnected} makes 
+the Chevalley-Eilenberg cochain complex with value on an open $U$ naturally\footnote{The grading
+is compatible (by the same argument as Lemma~\ref{L:pairingCE}) with the factorization algebra structure maps of
+$\clies(\fg\otimes \Omega, B)$} graded by the subsets of its connected components:
+ \begin{equation}\label{eq:defgraduationoncentralizernonconnected2}
+ \clies\big(\fg\otimes \Omega^*(U), B(U)\big)  \, \cong \, \bigoplus\limits_{J\subset I} {\clies}^{(J)}\big(\fg\otimes \Omega^*(U), B(U)\big) 
+\end{equation}
+where $J$ runs through all the (possibly empty) subsets of $I$.  Precisely, the $J$-piece is
+\begin{multline*}
+{\clies}^{(J)}\big(\fg\otimes \Omega^*(U), B(U)\big) = 
+\left(\bigotimes\limits_{j\in I\setminus J} k(U_j)\right) \otimes \left(\bigotimes\limits_{j\in J}
+\overline{\clies (\fg\otimes \Omega (U_j), B(U_j))  }\right) \\ \cong 
+\overline{\clies (\fg\otimes \Omega (\coprod\limits_{j\in_J}U_j), B(\coprod\limits_{j\in_J}U_j))  }.
+\end{multline*}
+We think of an element of ${\clies}^{(J)}\big(\fg\otimes \Omega^*(U), B(U)\big)$ has an element of ${\clies}\big(\fg\otimes \Omega^*(U), B(U)\big)$
+\emph{with support $\coprod\limits_{j\in J} U_j$}.   
+Note that the component $k$ in the decomposition~\eqref{eq:splittingbyaugm} is precisely the component 
+${\clies}^{(\emptyset)}\big(\fg\otimes \Omega^*(U), B(U)\big)$ corresponding to the empty family.
+\end{rmk}
+In other words, if $\varphi = \sum_{J\subset I} \varphi^{(J)}$ is the decomposition of $\varphi$ in its graded pieces, for all 
+$X= \bigotimes\limits_{i\in I} X_i \in \bigotimes\limits_{I}\cliels(\fg\otimes \Omega_c^*(U_i)) \cong \cliels(\fg\otimes \Omega^*_c(U))$, we 
+have the following formula generalizing the one for connected open  subsets:
+\begin{equation} \ev_f^U(\varphi\otimes X)= \sum_{J\subset I} \mu_B\left(\mathbf{f}\Big(\bigotimes\limits_{i\in I\setminus J} 
+X_i\Big)\otimes  \varphi^{(J)}\Big(\bigotimes\limits_{j\in J} 
+X_j\Big)\right) \end{equation}
+where $\mu_{B,J}: B\Big(\coprod\limits_{i\in I\setminus J}U_i\Big)\otimes B\Big(\coprod\limits_{j\in J}U_j\Big) \to B(U)$
+is the  structure map of $B$.
+}
 
@@
 \end{proof}
-
-\subsection{End of the proof}
-
-Combining the result of the last two sections we obtain immediately the following factorization algebra model for our main theorem:
-\begin{thm}\label{thm:centralizerfactorization}
-Let $k$ be $\RR$ or $\CC$, and assume $\mathbf{f}:  \UU_n \fg \to B$ is a map of augmented factorization algebras. 
-Then, the centralizer ${\frak Z}(\mathbf{f})$ is modeled by the locally constant factorization algebra that assigns
-\[
-\clies(\fg \otimes \Omega^*(U), B(U))
-\]
-to each open set $U \subset \RR^n$. 
-\end{thm}
-\begin{proof}
- In section~\ref{SS:constuctionthetaf}, we have constructed a factorization algebra map 
- $\theta_f: \clies\big(\fg\otimes \Omega , B \big) \longrightarrow  {\frak Z}(\mathbf{f})$. Proposition~\ref{L:canonicaltocenterisquis} 
- states that this map is an equivalence he Chevalley-Eilenberg factorization algebra cochains and the factorization algebra center of $f$ as claimed.
-\end{proof}
-
-By Lurie's equivalence (Theorem~\ref{T:En=Fac}) between the $\infty$-categories of $E_n$-algebras and locally constant factorization algebras 
-over $\RR^n$ (and the last part of lemma~\ref{L:thetaquisondisk}),
-the main theorem~\ref{thm: centralizer} follows from its factorization algebra counterpart~\ref{thm:centralizerfactorization}, 
-that is from Theorem~\ref{thm:centerfactorization}. This proves the theorem over $k=\RR$ (or $\CC$).
-
-Corollary~\ref{cor:centerfactorization}  is a consequence of theorem~\ref{thm:centralizerfactorization} obtained from applyting the universal 
-$E_n$-enveloping algebra functor to a (homotopy) Lie algebra homomorphism.
-
-\greg{Add a base change result to get the result over Q ?
-Add the center structure.
-I.E.
-write and check (!) that we can write a structure of $E_1$algebra in factorization algebra describing the higher $E_{n+1}$-structure for $f=id$}
-
-\owen{Commented out here is a discussion of centers. We may want to resurrect it but it doesn't seem essential to the main results.}
 

### 2020-09-01 draft.tex
tidying up other areas

@@
 
-\begin{prp}\label{L:canonicaltocenterisquis} The morphism~\eqref{eq:canonicaltocenter}
-\[\clies\big(\fg\otimes \Omega , B \big) \longrightarrow  {\frak Z}(\mathbf{f})\] is a weak-equivalence of factorization algebras. 
+\begin{prp}
+\label{L:canonicaltocenterisquis} 
+The map~\eqref{eq:canonicaltocenter}
+\[
+\clies\big(\fg\otimes \Omega , B \big) \longrightarrow  {\frak Z}(\mathbf{f})
+\] 
+is a quasi-isomorphism of factorization algebras. 
 \end{prp}
+
 \begin{proof}
@@
 
-\section{Factorization algebra description of the center}
+\section{Functoriality of the centralizer construction}
 \label{S:centerinFacAlg}
+
+\owen{If I'm understanding, this section shows that our construction satisfies the ``composition'' of centralizers on the nose. One corollary is that the center has a strict associative product!}
 

### 2020-09-01 draft.tex

--- 2020-09-01 draft.tex
@@
 \[
-\clies(\Omega^* \otimes \fg, \cliels(\Omega^*_c \otimes \fh)_f)
-\]
-equipped with a convolution-type product,
-where the subscript $f$ indicates how $\cliels(\Omega^*_c \otimes \fh)$ is a module over $\Omega^* \otimes \fg$.
+\clies(\Omega^* \otimes \fg, \cliels(\Omega^*_c \otimes \fh))
+\]
+equipped with a convolution-type product.
 \end{thm}
@@
 
-\owen{Recall any relevant strictification results.}
-
 Note that in the theorem we use the following equivalence due to Lurie~\cite{LurieHA}.
@@
 When $k$ is $\RR$ or $\CC$, 
-the enveloping $E_n$ algebra $\UU_n \fg$ of a dg Lie algebra $\fg$ is modeled by the locally constant factorization algebra $\bU_n \fg$ that assigns
-\[
-\bU_n \fg(V) = \cliels(\Omega^*_c(V) \otimes \fg)
-\]
-to each open set $V \subset \RR^n$.
+the enveloping $E_n$ algebra $\UU_n \fg$ of a dg Lie algebra $\fg$ is modeled by the locally constant factorization algebra that assigns
+\[
+\cliels(\Omega^*_c(U) \otimes \fg)
+\]
+to each open set $U \subset \RR^n$.
 \end{thm}
@@
 & {\frak Z}_{E_n}(f) \otimes A \arrow[dr] & \\
-A \arrow[ur, "u \otimes \id"] \arrow[rr, "f"] && B
+A \arrow[ur, "u"] \arrow[rr, "f"] && B
 \end{tikzcd}
 \]
-where the arrow in the upper left is the tensor product of the unit map $u: 1_\cC \to {\frak Z}_{E_n}(f)$ and the identity map $\id: A \to A$.
-The {\em center} of an $E_n$ algebra $A$ is the centralizer of its identity morphism $\id_A: A \to A$. 
-We  denote it ${\frak Z}_{E_n}(A) := {\frak Z}_{E_n}(\id_A)$.
+where $u$ is induced by the identity map $1_\cC \to {\frak Z}_{E_n}(f)$.
+The {\em center} of an $E_n$ algebra $A$ is the centralizer of its identity morphism $\id_A: A \to A$. We will denote it ${\frak Z}_{E_n}(A) 
+:= {\frak Z}_{E_n}(\id_A)$.
 \end{dfn}
@@
 
-\begin{prp}
-\label{T:centralizer=inthom} 
+\begin{prp}\label{T:centralizer=inthom} 
 The centralizer ${\frak Z}_{E_n}(f)$ exists and can be identified with the classifying object for maps from $A$ to $B$ in the $\infty$-category $\Mod^{E_n}_A(\cC)$.
@@
 
-\section{Proof of Theorem \ref{thm: centralizer}}
-
-Recall the overall strategy.
-First, we define a factorization algebra $\clies(\Omega^* \otimes \fg, (\bU_n \fh)_f)$ as a kind of convolution factorization algebra.
-Then we get to the heart of the construction:
-we show that this convolution algebra naturally sits inside a centralizer diagram.
-By the universal property of the centralizer, we then obtain 
-a canonical map 
-\[
-\theta_{\bf{f}}: \clies\big(\fg\otimes \Omega , B \big) \longrightarrow  {\frak Z}(\mathbf{f})
-\]
-where ${\frak Z}(\mathbf{f})$ is a factorization algebra that models the centralizer ${\frak Z}(f)$ of the map $f$.
-\owen{Calibrate notations!}
-It is then a direct computation to verify $\theta_f$ is a quasi-isomorphism,
-using the Francis-Lurie result mentioned earlier.
-
-\owen{Comment on notations:}
-As we work in the setting of factorization algebras on $\RR^n$, 
-we will use bold font to indicate such factorization models for $E_n$ algebra statements.
-For instance, we use $\bU_n \fg$ for the factorization model of the enveloping $E_n$ algebra,
-and we use $\bf{f}: \bU_n \fg \to \bU_n \fh$ for the factorization model of the map $f: \UU_n \fg \to \UU_n \fh$ of $E_n$ algebras.
-
-\subsection{Standard manipulations with $L_\infty$ algebras and their modules}
-
-\owen{I want to recall briefly how an $L_\infty$ action on a cochain complex leads to all the variants of CE (co)chains.
-It can just be a compendium of facts we use below.}
-
-To any $\fg$-module $M$ (whether $\fg$ is a dg Lie algebra or an $L_\infty$-algebra), 
-we can associate its Chevalley-Eilenberg cochain complex defined 
-by 
-\begin{equation}
- \clies(\fg, M) = \Hom (Sym(\fg[-1]), M)
-\end{equation}
-with its classical differential. 
-\greg{recall....quickly. AT least for dg-part. Say something for $L_\infty$ too}
-We have the evaluation map 
-\begin{equation}
- \label{eq:defev} \ev: \clies(\fg, M) \otimes Sym(\fg[-1])\to M
-\end{equation}
-given by applying a function on a given tensor in $Sym(\fg[-1])$.
-
-\begin{dfn}
-\label{dfn: CE from map}
-\owen{an $L_\infty$ map $\fg \rightsquigarrow \fh$ induces a cochain complex $\clies(\fg,\cliels(\fh))$.}
+\section{}
+
+The lemma allows us to define the factorization algebra given on any open $U$ by  the Chevalley-Eilenberg chain complexes
+$ \cliels\big(\fg \otimes \Omega^*_c(U), B(U) \big)$ (with their standard differential)
+of $\fg \otimes \Omega^*_c(U)$ with value on $B(U)$ whose structure maps are given, for any $(U_i)_{i\in I}$ 
+a finite family of pairwise disjoint open subsets of an open $V$, by 
+\begin{multline}\label{eq:transClieFac}
+ \bigotimes_{i\in I} \cliels\big(\fg \otimes \Omega^*_c(U_i), B(U_i) \big) \cong Sym\Big(
+ \fg\otimes (\bigoplus_{i\in I}  \Omega^*_c(U_i))[-1]  \Big) \otimes \Big( \bigotimes_{i\in I} B(U_i)\Big) \\ 
+ \cong Sym\Big(\fg\otimes \Omega_c\big(\coprod U_i\big)[-1] \Big) \otimes \Big( \bigotimes_{i\in I} B(U_i)\Big)  
+ \stackrel{\omega^*\otimes \mu_B}\longrightarrow Sym(\fg\otimes \Omega_c(V)[-1] ) \otimes B(V) \\ 
+ = \cliels(\fg\otimes \Omega_c(V), B(V))
+\end{multline}
+where $\omega$ is induced by the cosheaf structure of compactly supported form and $\mu_B$ is the factorization algebra structure of $B(-)$.
+
+\smallskip
+
+The (homotopy) sheaf structure of forms also gives us structure maps
+\begin{multline}\label{eq:transClieFacCochain}
+ \bigotimes_{i\in I} \clies\big(\fg \otimes \Omega^*(U_i), B(U_i) \big) \longrightarrow
+  \Hom\Big(Sym\big(\fg\otimes (\bigoplus_{i\in I}  \Omega^*(U_i))[-1]\big),  \bigotimes\limits_{i\in I} B(U_i) \Big) \\
+ \cong \Hom\Big(Sym\big(\fg\otimes \Omega^*(\coprod U_i)[-1]\big), \bigotimes\limits_{i\in I} B(U_i) \Big) \\
+ \stackrel{\rho}\longrightarrow \Hom\Big(Sym\big(\fg\otimes \Omega^*(V)[-1]\big), \bigotimes\limits_{i\in I} B(U_i) \Big) \\
+ \stackrel{\mu_B}\longrightarrow 
+  \clies(\fg\otimes \Omega (V), B(V))
+\end{multline}
+where $\rho$ is given by the restriction of forms onto a subspace.
+
+\label{L:ClieFacDef} 
+ Similarly, the structure maps~\eqref{eq:transClieFacCochain} makes 
+ $ \clies\big(\fg \otimes \Omega^*(-), B(-) \big)$ a (resp. locally constant) factorization algebra.
+
+\begin{dfn}\label{dfn:CEofFact}
+We {call   $\cliels\big(\fg \otimes \Omega^*_c(-), B(-) \big)$ the Chevalley-Eilenberg chain factorization algebra of $\fg$ with value in $B(-)$} 
+and $\clies\big(\fg \otimes \Omega^*(-), B(-) \big)$ the Chevalley-Eilenberg cochain factorization algebra.
 \end{dfn}
-
-\subsection{Defining the convolution factorization algebra}
-
-Our goal here is to construct the factorization algebra that models the centralizer.
-First, we need to show that there is a well-defined functor (in the 1-categorical sense) ${\rm Opens}_{\RR^n} \to \Ch_k$ assigning $\clies(\Omega^*(V) \otimes \fg, \bU_n \fh(V))$ to each open set $V$.
-Once that is in place, it is straightforward to describe the structure maps of the prefactorization algebra and to verify it forms a factorization algebra.
-
-\begin{rmk}
-These arguments are now standard in the literature of factorization algebras, so we will be brief in our discussion.
-See, e.g., \cite{CG1} \owen{stuff by Greg and others} for more.
+\begin{proof}
+
+\end{proof}
+
+A special but very interesting case is of course when $B$ is itself an enveloping algebra. 
+\begin{cor}
+ Let $\fg$, $\fh$ be dg-Lie algebras and $f:\fg\to \fh$ be a dg-Lie algebra morphism. 
+ Then the induced factorization algebra map $\mathbf{\UU_n f}:  \cliels( \fg \otimes \Omega^*_c(-)) \longrightarrow  \cliels( \fh \otimes \Omega^*_c(-)) $
+ is the standard map $\cliels(f)$ induced by $f$ and the action of $\fg  \otimes \Omega^*_c(-)$ is obtained from the $\fg$-action on $\fh$ by Leibniz rule.
+\end{cor}
+\begin{rmk}\greg{Extends to $L_\infty$ case in a sentence or too}
 \end{rmk}
 
-Consider now a fixed open set $V \subset \RR^n$.
-Then the $L_\infty$ map $f: \fg \rightsquigarrow \fh$ induces canonically an $L_\infty$ map 
-\[
-\tilde{f}: \Omega^*_c(V) \otimes \fg \rightsquigarrow \Omega^*_c(V) \otimes \fh
-\]
-by base change along the map $k \to \Omega^*_c(V)$ of dg commutative algebras,
-as the compactly supported de Rham forms form a dg commutative algebra under wedge product.
-In consequence, we see that $\Omega^*_c(V) \otimes \fg$ acts on $\Omega^*_c(V) \otimes \fh$ and hence equips it with the structure of an $L_\infty$ module over $\Omega^*_c(V) \otimes \fg$.
-We denote this module as
-\[
-(\Omega^*_c(V) \otimes \fh)_f
-\]
-to emphasize the dependence on the original map~$f$.
-In this action, the wedge product of forms intertwines with the $L_\infty$ structure on $\fg$ in a very simple way: 
-they simply happen side by side, but do not affect each other.
-
-Observe that $\Omega^*_c(V)$ is a module over the dg commutative algebra $\Omega^*(V)$ of {\em non}\/compactly supported forms.
-This action extends immediately to the module $(\Omega^*_c(V) \otimes \fh)_f$, 
-so we now view it as an $L_\infty$ module over $\Omega^*(V) \otimes \fg$ as well.
-We now need to explain how to make $\cliels(\Omega^*_c(V) \otimes \fh)$ into an $L_\infty$-module over $\Omega^*(V) \otimes \fg$.
-Here we rely on the fact that modules over an $L_\infty$ algebra are symmetric monoidal over $\otimes_k$, 
-so that we can construct new modules from a given module by taking symmetric powers.
-Since
-\[
-\cliels(\Omega^*_c(V) \otimes \fh) = \bigoplus_{n \geq 0} \Sym^n(\Omega^*_c(V) \otimes \fh[1])
-\]
-as cochain complexes,
-we see that $\cliels(\Omega^*_c(V) \otimes \fh)$ acquires a canonical action of $\Omega^*(V) \otimes \fg$.
-In consequence, we have a cochain complex
-\[
-\clies(\Omega^*(V) \otimes \fg, \cliels(\Omega^*_c(V) \otimes \fh)_f)
-\]
-on each open set~$V$.
-
-The next step is to verify functoriality of this construction over the poset of opens.
-This property follows quickly from the fact that wedge product of forms preserves support.
-Given an inclusion $i: V' \subset V$ of opens, if we take a form $\alpha \in \Omega^*(V)$ and a compactly supported form $\beta \in \Omega^*_c(V')$, then the wedge product $\alpha \wedge i_* \beta \in \Omega^*_c(V)$ after applying the extension-by-zero map $i_*: \Omega^*_c(V') \to \Omega^*_c(V)$ equals the wedge product $i_*(i^*\alpha \wedge \beta)$ arising from the restriction $i^* \alpha$ of $\alpha$ to~$V'$.
-In consequence, the action of $\Omega^*(V) \otimes \fg$ on $\cliels(\Omega^*_c(V') \otimes \fh)_f$ arising from the restriction map $\Omega^*(V) \otimes \fg \to \Omega^*(V') \otimes \fg$ of $L_\infty$ algebras agrees with action induced by the inclusion of $\cliels(\Omega^*_c(V') \otimes \fh)_f$ as a (strict) submodule of~$\cliels(\Omega^*_c(V) \otimes \fh)_f$.
-This argument is manifestly associative under composition of inclusions, so we have shown our first claim.
-
-\begin{lmm}
-The assignment
-\[
-V \mapsto \clies(\Omega^*(V) \otimes \fg, \cliels(\Omega^*_c(V) \otimes \fh)_f)
-\]
-determines a functor from ${\rm Opens}_{\RR^n}$ to~$\Ch_k$.
-\end{lmm}
-
-We now turn to extending this functor to an algebra over the colored operad ${\rm Opens}_{\RR^n}^\sqcup$ whose colors are opens in $\RR^n$ where there is a precisely a single operation from a tuple of opens $[V_1,\ldots,V_k]$ to an open $W$ if and only if both $W$ contains every $V_j$ and the $V_j$ are all pairwise disjoint.
-
-The key fact is that the functors $\cliels$ and $\clies$ are suitably symmetric monoidal:
-they send a product of $L_\infty$ algebras to a tensor product of cochain complexes.
-Hence it suffices to examine the underlying functors to $L_\infty$ algebras.
-As the functors $\Omega^*$ and $\Omega^*_c$ send finite disjoint unions of opens to the direct product of cochain complexes, 
-the functors like $\Omega^* \otimes \fg$ and $\Omega^*_c \otimes \fh$ send finite disjoint unions of opens to products of $L_\infty$ algebras.
-In consequence, we obtain the desired second claim.
-
-\begin{lmm}
-The assignment
-\[
-V \mapsto \clies(\Omega^*(V) \otimes \fg, \cliels(\Omega^*_c(V) \otimes \fh)_f)
-\]
-determines a prefactorization algebra, i.e., a strict algebra over ${\rm Opens}_{\RR^n}^\sqcup$ with values in~$\Ch_k^\otimes$.
-\end{lmm}
-
-Due to the Poincar\'e lemma, the inclusion of a disk into a bigger disk $D \hookrightarrow D'$ makes the structure map 
-\[
-\clies(\Omega^*(D) \otimes \fg, \cliels(\Omega^*_c(D) \otimes \fh)_f) \xto{\simeq} \clies(\Omega^*(D) \otimes \fg, \cliels(\Omega^*_c(D) \otimes \fh)_f)
-\]
-a quasi-isomorphism.
-Hence this prefactorization algebra is locally constant in a homotopical sense.
-
-In fact, it defines a {\em factorization} algebra, by arguments that can be found in \owen{chapter 6 of \cite{CG1} and elsewhere}.
-
-\begin{dfn}
-\label{dfn: centralizer for f}
-Let $\clies(\Omega^* \otimes \fg, (\bU_n \fh)_f)$ denote this factorization algebra on $\RR^n$ arising from the map $f: \fg \rightsquigarrow \fh$.
-\end{dfn}
-
-\owen{Add a remark on convolution?}
-%
-%\def\conv{{\rm Conv}}
-%
-%\owen{For an ordinary colored operad $\cO$, describe how to produce a $\cO$-algebra $\conv(C,A)$ from any $\cO$-coalgebra $C$ and $\cO$-algebra $A$.}
-%
-%\owen{A special case to consider is how a cocycle $f \in \conv(C,A)$ encodes an $\cO$-algebra morphism $C^!
+\section{Convolution algebras over colored operads}
+
+\def\conv{{\rm Conv}}
+
+\owen{For an ordinary colored operad $\cO$, describe how to produce a $\cO$-algebra $\conv(C,A)$ from any $\cO$-coalgebra $C$ and $\cO$-algebra $A$.}
+
+\owen{A special case to consider is how a cocycle $f \in \conv(C,A)$ encodes an $\cO$-algebra morphism $C^!
 \to A$ from $C^!
@@
 Hopefully this admits an obvious deformation-theoretic interpretation.}
+
+\owen{If we do this correctly, we might find a model category-theoretic picture of how Koszul duality works for prefactorization algebras.}
+
+\section{Proof of Theorem \ref{thm: centralizer}}
+
+We have implemented the first step in the proof strategy.
+This section is devoted to the remaining steps.
+First, we explain steps (2)-(4), which are rather formal.
+Next, we define the $\Disk_n$-algebra $\clies(\Omega^* \otimes \fg, {\tt B}_f)$ as a kind of convolution algebra.
+Finally, we get to the heart of the construction:
+we show that this convolution algebra naturally sits inside a centralizer diagram.
+By the universal property of the centralizer, we then obtain 
+a canonical map 
+\[
+\Theta_f: \clies\big(\fg\otimes \Omega (-), B(-) \big) \longrightarrow  {\frak Z}(\mathbf{f})(-)
+\]
+where ${\frak Z}(\mathbf{f})(-)$ is the centralizer of locally constant $\Disk_n$-algebras~(\ref{D:centralizerFacAlgebra}).
+\owen{Calibrate notations!}
+It is then a direct computation to verify $\Theta_f$ is a quasi-isomorphism.
+
+\owen{Below is Greg's summary of the proof.}
+
+Let us start by summarizing the proof. The idea, using theorem~\ref{T:En=Fac}, 
+is that we only have to prove the factorization algebra part of the main theorem. 
+To do so, we first use the universal property of the centralizer to obtain 
+a canonical factorization algebra map 
+\[\Theta_f: \clies\big(\fg\otimes \Omega (-), B(-) \big) \longrightarrow  {\frak Z}(\mathbf{f})(-)\]
+where ${\frak Z}(\mathbf{f})(-)$ is the centralizer of locally constant factorization algebras (\ref{D:centralizerFacAlgebra}).
+
+Using the fundamental properties of universal $E_n$-enveloping algebra, we then prove that 
+this map is a weak-equivalence.
+
+\smallskip
+
+We thus let $\mathbf{f}: \cliels\big(\fg \otimes \Omega^* (-)) \to B(-)$ be a factorization algebra map (see~\eqref{eq:DefofFonFaclevel}). We can 
+assume that the structural (natural) quasi-isomorphism
+$$\bigotimes_{i\in I} B(U_i) 
+\stackrel{\simeq}\longrightarrow B(\coprod  U_i)$$ are chain complexes isomorphisms by replacing $B(-)$ by the prefactorization algebra 
+given, on any $V=\coprod_{j\in J} V_j$, where the $V_j$ are the connected components of $V$, by   $\mathop{\bigotimes}\limits_{j\in J} B(V_j)$. 
+The structural maps of $B$ are then a quasi-isomorphism of prefactorization algebras between it and $B(-)$. The map $\mathbf{f}$ is lifted similary using 
+the isomorphism $\bigotimes_{i\in I} \cliels\big(\fg \otimes \Omega_c^* (U_i)\big) \cong
+\cliels\big(\fg \otimes \Omega_c^* (U)\big)$ as well. We assume we have this property in the rest of this section.
+\greg{Technically we may need to replace the latter by a quasi-isomorphic one satisfying the same property to ensure we do have a strict fact algebra map. 
+Not sure if we should elaborate on it more since in the end we only need that to obtain lemma~\ref{L:inducedFacgModstruct} to make the construction valid 
+and therefore only use the induced sym on the cosheaf of $L_\infty$-module maps}
+
+\subsection{Strictification}
+
+\owen{Recall the relevant strictification results.}
+
+\owen{Sketch of where ${\tt f}$ comes from.}
+Given a cochain complex $M$, every $\fg$-representation $\rho: \fg \to \End(M)$ determines a cocommutative coderivation $\cliels(\fg) \to M$.
+Conversely, such a coderivation determines an $L_\infty$ action of $\fg$ on $M$.
+\owen{\dots}
+Applying these observations to ${\tt B}_f$ disk-by-disk, we obtain the following.
+
+\begin{lmm}
+As ${\tt B}_f$ is a $\Disk_n$-algebra in $\fg$-representations,
+there is a map of $\Disk_n$-algebras in cochain complexes ${\tt f}:  {\tt U}_n \fg \to {\tt B}$.
+\end{lmm}
+
+\owen{I'm not sure how to prove the following, or even if we need to.}
+
+\begin{prp}
+The map ${\tt f}:  {\tt U}_n \fg \to {\tt B}$ of strict $\Disk_n$-algebras models the original map~$f$.
+\end{prp}
+
+\subsection{The convolution $\Disk_n$-algebra}
+
+\owen{Discussion of convolution fact algs commented out below}
 %
-%\owen{If we do this correctly, we might find a model category-theoretic picture of how Koszul duality works for prefactorization algebras.}
-
-\subsection{Construction of the universal pairing in factorization algebras}
-\label{SS:constuctionthetaf}
-
-Our goal in this subsection is to construct a map of factorization algebras
-\[
-\ev_{\bf{f}}: \clies(\Omega^* \otimes \fg, (\Omega^*_c \otimes \fh)_f) \otimes \bU_n \fg \to \bU_n \fh,
-\]
-while in the next subsection we will show it fits into a centralizer diagram.
-To produce our map, we first construct it separately on each open subset and then explain why the construction is functorial.
-
-Let $V \subset \RR^n$ be open.
-The canonical pairing between Lie algebra chains and cochains provides a canonical cochain map
-\[
-\clies(\Omega^*(V) \otimes \fg, \cliels(\Omega^*_c(V) \otimes \fh)_f) \otimes \cliels(\Omega^*(V) \otimes \fg) \to \cliels(\Omega^*_c(V) \otimes \fh)_f.
-\]
-The canonical inclusion $\Omega^*_c(V) \otimes \fg \hookrightarrow \Omega^*(V) \otimes \fg$ induces a canonical inclusion 
-\[
-\cliels(\Omega^*_c(V) \otimes \fg) \hookrightarrow \cliels(\Omega^*(V) \otimes \fg)
-\]
-and hence, precomposing this inclusion with the pairing, we obtain our desired map
-\[
-\ev_{\bf{f}}(V): \clies(\Omega^*(V) \otimes \fg, \cliels(\Omega^*_c(V) \otimes \fh)_f) \otimes \bU_n \fg(V) \to \bU_n \fh(V)
-\]
-for each open~$V$.
-
-This construction is functorial in $V$ because wedge product of differential forms preserves support,
-so a minor variation on our argument above implies the following.
-
-\begin{lmm}
-The assignment
-\[
-V \mapsto \ev_{\bf{f}}(V)
-\]
-determines a natural transformation between functors from ${\rm Opens}_{\RR^n}$ to~$\Ch_k$.
-\end{lmm}
-
-\owen{Commented out below is an extensive argument by Greg about the existence and behavior of $\Theta_f$.
-If my explanation above is missing something crucial, I suspect it's addressed in that argument.}
-
-\greg{
-We start by defining a pairing between the factorization algebras of Chevalley-Eilenberg (co)chains in order to use the universal property of centralizers.\\
+%To any $\fg$-module $M$ (wether $\fg$ is a dg Lie algebra or an $L_\infty$-algebra), 
+%we can associate its Chevalley-Eilenberg cochain complex defined 
+%by 
+%\begin{equation}
+% \clies(\fg, M) = \Hom (Sym(\fg[-1]), M)
+%\end{equation}
+%with its classical differential. 
+%\greg{recall....quickly. AT least for dg-part. Say something for $L_\infty$ too}
+%We have the evaluation map 
+%\begin{equation}
+% \label{eq:defev} ev: \clies(\fg, M) \otimes Sym(\fg[-1])\to M
+%\end{equation}
+%given by applying a function on a given tensor in $Sym(\fg[-1])$.
+%
+%\begin{dfn}\label{D:convolutionalgebraCE}Let $\fg$ be a dg Lie (or $L_\infty$)-algebra and $B$ be an $E_n$-algebra in $\fg$-modules,
+%that is an object of the $\infty$-category 
+%$E_n-Alg(Mod_{\fg})$. Its associated convolution $E_n$-algebra structure on  $\clies(\fg, B) = \Hom (Sym(\fg[-1]), B)$ is obtained by 
+% taking the \emph{convolution} between the cocommutative symmetric coalgebra $Sym(\fg[-1])$ (forgetted to an $E_n$-coalgebra) and the $E_n$-algebra $B$.
+%\end{dfn}
+%\greg{Probably need somewhere to say what means $E_n-Alg(Mod_{\fg})$ and find a less ugly notation for it}
+%Precisely, given an explicit $E_n$-operad $D_n$ in chain complexes and $(B, \mu^B)$ a $D_n$-algebra, 
+%the convolution structure is given by the following composition
+%\begin{multline}
+% \Big(D_n(r)\otimes \clies(\fg, B)^{\otimes r} \Big)\otimes Sym(\fg[-1])\\ \stackrel{id\otimes id \otimes\Delta^{(r-1)}}\longrightarrow 
+% D_n(r)\otimes \clies(\fg, B)^{\otimes r} \otimes Sym(\fg[-1])^{\otimes r} 
+% \stackrel{id \otimes (ev^{\otimes r})}\longrightarrow D_n(r)\otimes B^{\otimes r} 
+% \stackrel{\mu_\sigma^B}\longrightarrow B.
+%\end{multline}
+%where $\Delta$ is the cocommutative comultiplication.
+%In plain formula,
+%for any $\sigma \in D_n(r)$ and $\phi_1,\dots, \phi_r \in 
+%\clies(\fg, B)$, their multiplication (parametrized by $\sigma$) is  given by 
+%\begin{equation}
+% \mu_\sigma (\phi_1,\dots, \phi_r): Sym(\fg[-1]) \ni x \mapsto \pm \mu^B_{\sigma} \big(\phi_1(x^{(1)}), \dots, \phi_r(x^{(r)})\big)
+%\end{equation}
+%where $x\mapsto x^{(1)}\otimes \cdots x^{(r)}$ is the usual $r$-fold cocommutative comultiplication.
+%Note that here, we are using the usual Koszul sign  convention. 
+%
+%\begin{lmm}
+% $\clies(\fg, M) = \Hom (Sym(\fg[-1]), B)$ is a $E_n$-algebra, naturally in $\fg$ and $B$.
+%\end{lmm}
+
+\owen{Describe it.}
+
+\subsection{Construction of the universal pairing in factorization algebras}\label{SS:constuctionthetaf}
+
+We start by defining a pairing between the factorization algebras of Chevalley-Eilenberg (co)chains in order to use the universal property of centralizers.
+
+\smallskip
+
 First note that compactly supported form embeds in all forms, therefore we can apply 
-any element of $\cliels\big(\fg \otimes \Omega^* , B\big)$ 
-to any element of $\cliels\big(\fg \otimes \Omega_c^* \big)$. Therefore, for any  $p\in \bN$, we have an evaluation 
+any element of $\cliels\big(\fg \otimes \Omega^* (-), B(-)\big)$ 
+to any element of $\cliels\big(\fg \otimes \Omega_c^* (-)\big)$. Therefore, for any  $p\in \bN$, we have an evaluation 
 \begin{equation} \label{eqdef:ev} \begin{array}{c}\ev: Sym^p \big( \fg \otimes \Omega^* (U)[-1] ,B(U)\big)
@@
  (x,\Phi) \,\longmapsto\, (-1)^{p(|x|+p) } \Phi (x)\end{array}
-\end{equation} induced by this embedding  in all forms followed by evaluating on a function.\\
-Second, the augmentation of $B$ makes $B$ augmented as well (in the obvious sense of~\cite{Gi-NotesFactorization}) and this induces an augmentation on
-$\clies\big(\fg\otimes \Omega , B \big)$ as well as follows. 
+\end{equation} induced by this embedding  in all forms followed by evaluating on a function.
+
+\smallskip
+
+Second, the augmentation of $B$ makes $B(-)$ augmented as well (in the obvious sense of~\cite{Gi-NotesFactorization}) and this induces an augmentation on
+$\clies\big(\fg\otimes \Omega (-), B(-) \big)$ as well as follows. 
 We have the canonical factorization algebra map  $\mathbf{1}$  defined, for any open $U$, by 
@@
 B(\emptyset) \ar[r] & B(U)  } 
- \] where the last map is given by the factorization algebra structure of $B$. This gives the canonical element element 
- $\mathbf{1}\in \clies(\fg\otimes \Omega^*, B) )$ which is the unit $k\to \clies(\fg\otimes \Omega^*, B) )$
+ \] where the last map is given by the factorization algebra structure of $B(-)$. This gives the canonical element element 
+ $\mathbf{1}\in \clies(\fg\otimes \Omega^*(-), B(-)) )$ which is the unit $k(-)\to \clies(\fg\otimes \Omega^*(-), B(-)) )$
  of the factorization structure of 
@@
  \iota$ where $\iota: k(U) \cong k \hookrightarrow Sym(\fg \otimes \Omega (U) [1]) $ is the inclusion and $\varepsilon B(U)\to k(U)$ is the augmentation of 
- $B$. We therefore obtain a canonical splitting of factorization algebras 
+ $B(-)$. We therefore obtain a canonical splitting of factorization algebras 
  \begin{equation}\label{eq:splittingbyaugm}
-   \clies\big(\fg\otimes \Omega^*, B\big)  \, \cong \, k \oplus \overline{ \clies(\fg\otimes \Omega^*, B) )}
+   \clies\big(\fg\otimes \Omega^*(-), B(-)\big)  \, \cong \, k(-) \oplus \overline{ \clies(\fg\otimes \Omega^*(-), B(-)) )}
  \end{equation}
 given by the augmentation. Below~\ref{Rmk:defgraduationclie}, we refine  this splitting, using it  freely  on each-connected component, to obtain 
-a natural grading on it.\\
+a natural grading on it.
+
+\smallskip
+
 We use the splitting and~\eqref{eqdef:ev} to define our pairing as follows. First for a \emph{connected} open subset $W$ of $\RR^n$, we define 
@@
 \[ \ev_f^W(\varphi\otimes x)= \lambda \mathbf{f}(W)(x) + \overline{\varphi}(x). \]
+
+\smallskip
+
 We extend this construction  to any 
@@
 \end{multline}
-where $\mu_B$ is the canonical structure map of the factorization algebra $B$ and the other maps are given by~\eqref{eq:defgraduationoncentralizernonconnected} 
+where $\mu_B$ is the canonical structure map of the factorization algebra $B(-)$ and the other maps are given by~\eqref{eq:defgraduationoncentralizernonconnected} 
 and~\eqref{eq:defevforconnected}.
@@
 things to do (like completion) for non-finitely dimensional Lie algebras}
-\greg{The decomposition used to extend $\ev$ on non-connected open can be done with any augmented $B$, simply by defining it onto the prefact alg obtained by tensoring 
-out on non-connected components and using the quasi-isomorphism canonical map to $\clies(\fg, B)$ in that case. Not sure which way is easier to define/mention}\\
+\greg{The decomposition used to extend $\ev$ on non-connected open can be done with any augmented $B(-)$, simply by defining it onto the prefact alg obtained by tensoring 
+out on non-connected components and using the quasi-isomorphism canonical map to $\clies(\fg, B(-))$ in that case. Not sure which way is easier to define/mention}
+
 \begin{rmk}\label{Rmk:defgraduationclie} The decomposition~\eqref{eq:defgraduationoncentralizernonconnected} makes 
@@
 is compatible (by the same argument as Lemma~\ref{L:pairingCE}) with the factorization algebra structure maps of
-$\clies(\fg\otimes \Omega, B)$} graded by the subsets of its connected components:
+$\clies(\fg\otimes \Omega(-), B(-))$} graded by the subsets of its connected components:
  \begin{equation}\label{eq:defgraduationoncentralizernonconnected2}
@@
 \emph{with support $\coprod\limits_{j\in J} U_j$}.   
-Note that the component $k$ in the decomposition~\eqref{eq:splittingbyaugm} is precisely the component 
+Note that the component $k(-)$ in the decomposition~\eqref{eq:splittingbyaugm} is precisely the component 
 ${\clies}^{(\emptyset)}\big(\fg\otimes \Omega^*(U), B(U)\big)$ corresponding to the empty family.
@@
 where $\mu_{B,J}: B\Big(\coprod\limits_{i\in I\setminus J}U_i\Big)\otimes B\Big(\coprod\limits_{j\in J}U_j\Big) \to B(U)$
-is the  structure map of $B$.
-}
-
-We need to show that this natural transformation extends to a morphism of prefactorization algebras,
-i.e., that it intertwines with the operations over the colored operad ${\rm Opens}_{\RR^n}^\sqcup$.
-Here we use the fact that the evaluation pairing between Lie algebra chains and cochains plays nicely with products of $L_\infty$ algebras, in the following sense.
-Let $\fX, \fY$ be $L_\infty$ algebras and let $M, N$ be modules for those respective $L_\infty$ algebras.
-The direct sum $M \oplus N$ admits a natural action of the product $L_\infty$ algebra $\fX \times \fY$.
-Then the isomorphisms
-\begin{align*}
-\clies(\fX \times \fY, M \oplus N) \otimes \cliels(\fX \times \fY) 
-&\cong (\clies(\fX, M) \otimes \clies(\fY,N) ) \otimes (\cliels(\fX) \otimes \cliels(\fY) ) \\
-&\cong (\clies(\fX,M) \otimes \cliels(\fX) ) \otimes (\cliels(\fY,N) \otimes \cliels(\fY) )
-\end{align*}
-precompose with the tensored evaluation pairings
-\[
-\cong (\clies(\fX,M) \otimes \cliels(\fX) ) \otimes (\cliels(\fY,N) \otimes \cliels(\fY) ) \xto{\ev_\fX \otimes \ev_\fY} M \otimes N
-\]
-to provide a canonical map
-\[
-\clies(\fX \times \fY, M \oplus N) \otimes \cliels(\fX \times \fY) \to M \otimes N.
-\]
-In light of this observation and the fact that functors such as $\Omega^* \otimes \fg$ and $\Omega^*_c \otimes \fh$ send disjoint unions to products of $L_\infty$ algebras,
-we deduce the desired result.
-
-\begin{lmm}
-\label{L:pairingCE}
-The natural transformation $\ev_{\bf{f}}$ determines a map of strict prefactorization algebras,
-i.e., algebras over the colored operad ${\rm Opens}_{\RR^n}^\sqcup$.
+is the  structure map of $B(-)$.
+
+\begin{lmm}\label{L:pairingCE}
+ The pairing morphism $\ev_f$ defined by formula~\eqref{eq:defineevf} extends to a factorization algebra morphism
+ \[\ev_f:  \cliels\big(\fg \otimes \Omega^* (-), B(-)\big) \otimes \cliels\big(\fg \otimes \Omega_c^* (-)\big) 
+ \longrightarrow B(-).\]
 \end{lmm}
-
-\subsection{The pairing fits into a centralizer diagram}
-
-For any factorization algebra $B$ on $\RR^n$, 
-there is a unit map of factorization algebras  
-\[
-1(U) = k \cong 1(\emptyset)  \xto{\cong}
-B(\emptyset) \to B(V)  
-\] 
-for each open set $V$, where the last map is structure map of~$B$.
-
-\begin{lmm}\label{L:ComTriangCent} 
-There is a commutative triangle 
-\[
-\xymatrix{
-& \clies ( \Omega \otimes \fg , (\bU_n \fh)_f) \otimes \bU_n \fg
-\ar[dr]^{\ev_{\bf{f}}} & \\
-\bU_n \fg \ar[ur]^{\mathbf{1} \otimes \id} \ar[rr]^{\mathbf{f}}  & &  \bU_n \fh}
-\]
-of maps of factorization algebras.
+\begin{proof}
+
+\end{proof}
+We write, $1$ for the factorization algebra map defined, for any open $U$, by 
+\[\xymatrix{ k(U)=k  \ar[r]^{\quad \cong}& 
+B(\emptyset) \ar[r] & B(U)  } 
+ \] where the last map is given by the factorization algebra structure of $B(-)$.
+This gives the canonical element element $\mathbf{1}\in \clies(\fg\otimes \Omega^*(-), B(-)) )$ which is the unit of the factorization structure of
+ the Chevalley-Eilenberg cochain factorization algebras.
+
+\begin{lmm}\label{L:ComTriangCent} The triangle 
+ $$ \xymatrix{
+& \clies ( \fg\otimes \Omega^* (-), B(-)) \otimes \cliels(\fg\otimes \Omega^*_c  (-) )
+\ar[dr]^{\ev_f} & \\
+\cliels(\fg\otimes \Omega^*_c (-)) \ar[ur]^{\mathbf{1} \otimes \id} \ar[rr]^{\mathbf{f}}  & &  B(-).}
+ $$
+is a commutative triangle of factorization algebras maps.
 \end{lmm}
-
-\begin{proof}
-This triangle commutes on the nose, as we now show.
-What we need to show is how the unit map $u$ for $\clies ( \Omega \otimes \fg , (\bU_n \fh)_f)$ encodes the map $\bf{f}$.
-\owen{I'm stuck. Greg's statement is below.}
+\begin{proof}
  It follows from lemma~\ref{L:pairingCE} that this is a diagram of factorization algebras.
@@
 
-By universal property of the centralizer (definition~\ref{D:centralizerFacAlgebra}), lemma~\ref{L:ComTriangCent} implies that the pairing $\ev_{\bf{f}}$ induces a canonical morphism 
-\begin{equation}
-\label{eq:canonicaltocenter}
-\theta_{\bf{f}}: \clies\big(\fg\otimes \Omega , B \big) \longrightarrow  {\frak Z}(\mathbf{f})
+By universal property of the centralizer (definition~\ref{D:centralizerFacAlgebra}), lemma~\ref{L:ComTriangCent} implies that the pairing $\ev_f \,:\,\cliels\big(\fg \otimes \Omega^* (-), B(-)\big) \otimes \cliels\big(\fg \otimes \Omega_c^* (-)\big)
+ \longrightarrow B(-)$ induces 
+a canonical morphism of factorization algebras
+\begin{equation}\label{eq:canonicaltocenter}
+\theta_f: \clies\big(\fg\otimes \Omega (-), B(-) \big) \longrightarrow  {\frak Z}(\mathbf{f})(-). 
 \end{equation}
-of factorization algebras.
-
-\subsection{The map $\theta_{\bf{f}}$ is a weak equivalence.}
-
+
+\subsection{The map $\theta_f$ is a weak equivalence.} 
 We have defined a functorial (in $f$) factorization algebras map 
@@
  {\frak Z}(\mathbf{f})(\RR^n)\cong {\frak Z}_{E_n}(\mathbf{f})$ is a quasi-isomorphism.
+
+ \smallskip
 
@@
 
+\smallskip
+
 Using the canonical inclusion $i: U\fg \to U(\fg \otimes k[\epsilon_{n-1}])$,
@@
 Recall now that $\UU_n \fg \simeq \Sym(\fg[1-n])$ as $\fg$-modules 
-since, as factorization algebras (see Theorem~\ref{T:UnofLie}),  $$\UU_n \fg \cong \cliels(\Omega^*_c \otimes \fg) \cong \Sym((\fg[-n])[-1])$$ where the right hand side formula follows from the fact that the product of degree $n$ compactly supported forms is trivial and therefore $\fg[-n]$ is a trivial Lie algebra.
+since, as factorization algebras (see Theorem~\ref{T:UnofLie}),  $$\UU_n \fg \cong \cliels(\Omega^*_c(-) \otimes \fg) \cong \Sym((\fg[-n])[-1])$$ where the right hand side formula follows from the fact that the product of degree $n$ compactly supported forms is trivial and therefore $\fg[-n]$ is a trivial Lie algebra.
 Thus, base change  gives rise to an equivalence 
@@
 \begin{prp}\label{L:canonicaltocenterisquis} The morphism~\eqref{eq:canonicaltocenter}
-\[\clies\big(\fg\otimes \Omega , B \big) \longrightarrow  {\frak Z}(\mathbf{f})\] is a weak-equivalence of factorization algebras. 
+\[\clies\big(\fg\otimes \Omega (-), B(-) \big) \longrightarrow  {\frak Z}(\mathbf{f})(-)\] is a weak-equivalence of factorization algebras. 
 \end{prp}
@@
 \end{proof}
+
+\subsection{End of the proof}
+
+Combining the result of the last two sections we obtain immediately the following factorization algebra model for our main theorem:
+\begin{thm}\label{thm:centralizerfactorization}
+Let $k$ be $\RR$ or $\CC$, and assume $\mathbf{f}:  \UU_n \fg \to B(-)$ is a map of augmented factorization algebras. 
+Then, the centralizer ${\frak Z}(\mathbf{f})$ is modeled by the locally constant factorization algebra that assigns
+\[
+\clies(\fg \otimes \Omega^*(U), B(U))
+\]
+to each open set $U \subset \RR^n$. 
+\end{thm}
+\begin{proof}
+ In section~\ref{SS:constuctionthetaf}, we have constructed a factorization algebra map 
+ $\theta_f: \clies\big(\fg\otimes \Omega (-), B(-) \big) \longrightarrow  {\frak Z}(\mathbf{f})(-)$. Proposition~\ref{L:canonicaltocenterisquis} 
+ states that this map is an equivalence he Chevalley-Eilenberg factorization algebra cochains and the factorization algebra center of $f$ as claimed.
+\end{proof}
+
+By Lurie's equivalence (Theorem~\ref{T:En=Fac}) between the $\infty$-categories of $E_n$-algebras and locally constant factorization algebras 
+over $\RR^n$ (and the last part of lemma~\ref{L:thetaquisondisk}),
+the main theorem~\ref{thm: centralizer} follows from its factorization algebra counterpart~\ref{thm:centralizerfactorization}, 
+that is from Theorem~\ref{thm:centerfactorization}. This proves the theorem over $k=\RR$ (or $\CC$).
+
+\smallskip
+
+Corollary~\ref{cor:centerfactorization}  is a consequence of theorem~\ref{thm:centralizerfactorization} obtained from applyting the universal 
+$E_n$-enveloping algebra functor to a (homotopy) Lie algebra homomorphism.
+
+\greg{Add a base change result to get the result over Q ?
+Add the center structure.
+I.E.
+write and check (!) that we can write a structure of $E_1$algebra in factorization algebra describing the higher $E_{n+1}$-structure for $f=id$}
+
+\owen{Commented out here is a discussion of centers. We may want to resurrect it but it doesn't seem essential to the main results.}
 
@@
 \end{prp}
-When $A$ is a factorization algebra model for $A$, in virtue of theorem~\ref{T:En=Fac} 
+When $A(-)$ is a factorization algebra model for $A$, in virtue of theorem~\ref{T:En=Fac} 
 (and \greg{add reference for fac algebra in fac algebra maybe too}), in order to have a factorization algebra 
 model of the center of $A$, it is sufficient to describe the induced map 
-\[{\frak Z}(A){\otimes} {\frak Z}(A) \longrightarrow {\frak Z}(A)\]
+\[{\frak Z}(A(-)){\otimes} {\frak Z}(A(-)) \longrightarrow {\frak Z}(A(-))\]
 as a factorization algebra homomorphism which makes it an associative object in the category of locally constant factorization algebras.
 
+\smallskip
+
 We now turn to the specific case   of enveloping algebras $\UU_n(\fg)$.
@@
 Let $f: \fg \to \fh$, $g: \fh \to \fl$ be  $L_\infty$-algebras morphisms; for instance a dg-Lie algebras morphisms. We write 
-\[ \mathbf{f}:\cliels\big(\fg \otimes \Omega^*_c\big) \to  \cliels\big(\fh \otimes \Omega^*_c\big), \quad 
-\mathbf{h}:\cliels\big(\fh \otimes \Omega^*_c\big) \to  \cliels\big(\fl \otimes \Omega^*_c\big)\]
+\[ \mathbf{f}:\cliels\big(\fg \otimes \Omega^*_c(-)\big) \to  \cliels\big(\fh \otimes \Omega^*_c(-)\big), \quad 
+\mathbf{h}:\cliels\big(\fh \otimes \Omega^*_c(-)\big) \to  \cliels\big(\fl \otimes \Omega^*_c(-)\big)\]
 for the induced morphisms on their enveloping factorization algebras over $\RR^n$.
@@
 algebras) 
-are canonically pointed  by $\mathbf{1}\in \clies(\fg\otimes \Omega^*, B) )$ which is induced by 
-the unit $k\to \clies(\fg\otimes \Omega^*, B) )$
+are canonically pointed  by $\mathbf{1}\in \clies(\fg\otimes \Omega^*(-), B(-)) )$ which is induced by 
+the unit $k(-)\to \clies(\fg\otimes \Omega^*(-), B(-)) )$
  of the factorization structures.  In particular, we have the canonical splitting~\eqref{eq:splittingbyaugm} 
@@
 
-\begin{lmm}\label{L:compisfacmap} The composition $$\clies\big(\fh \otimes \Omega, \cliels(\fl \otimes \Omega_c  \big) \otimes 
-\clies\big(\fg \otimes \Omega, \cliels(\fh \otimes \Omega_c  \big)
+\begin{lmm}\label{L:compisfacmap} The composition $$\clies\big(\fh \otimes \Omega(-), \cliels(\fl \otimes \Omega_c(-)  \big) \otimes 
+\clies\big(\fg \otimes \Omega(-), \cliels(\fh \otimes \Omega_c(-)  \big)
 \stackrel{(-\star-)}\longrightarrow 
-\clies\big(\fg \otimes \Omega, \cliels(\fl \otimes \Omega_c  \big)
+\clies\big(\fg \otimes \Omega(-), \cliels(\fl \otimes \Omega_c(-)  \big)
 $$
@@
 The composition is compatible with the augmentation splitting. Precisely, we have
-\begin{lmm}\label{L:compisaugmented} For any $\varphi \in \clies\big(\fg \otimes \Omega, \cliels(\fh \otimes \Omega_c  \big)$,
-$\psi \in \clies\big(\fh \otimes \Omega, \cliels(\fl \otimes \Omega_c  \big)$
+\begin{lmm}\label{L:compisaugmented} For any $\varphi \in \clies\big(\fg \otimes \Omega(-), \cliels(\fh \otimes \Omega_c(-)  \big)$,
+$\psi \in \clies\big(\fh \otimes \Omega(-), \cliels(\fl \otimes \Omega_c(-)  \big)$
  One has the following equalities  :
@@
   \overline{\psi\star \varphi} \;= \;\mathbf{1}\star \overline{\varphi} +\overline{\psi}\star \mathbf{1} +\overline{\psi}\star \overline{\varphi} 
-  & \quad\mbox{ (in  $\clies\big(\fg \otimes \Omega, \cliels(\fl \otimes \Omega_c  \big) $)}\\
+  & \quad\mbox{ (in  $\clies\big(\fg \otimes \Omega(-), \cliels(\fl \otimes \Omega_c(-)  \big) $)}\\
  \mathbf{1}\star \varphi \;=\;  (\lambda_\varphi \mathbf{1}, g\circ \overline{\varphi})\qquad
-  &\quad\mbox{ (in  $k  \oplus \overline{\clies\big(\fg \otimes \Omega, \cliels(\fl \otimes \Omega_c  \big)}$)}\\
+  &\quad\mbox{ (in  $k(-)  \oplus \overline{\clies\big(\fg \otimes \Omega(-), \cliels(\fl \otimes \Omega_c(-)  \big)}$)}\\
   \psi \star \mathbf{1}\;=\; (\lambda_\psi \mathbf{1}, \overline{\psi} \circ f) \qquad
-  &\quad\mbox{ (in  $k  \oplus \overline{\clies\big(\fg \otimes \Omega, \cliels(\fl \otimes \Omega_c  \big)}$).}
+  &\quad\mbox{ (in  $k(-)  \oplus \overline{\clies\big(\fg \otimes \Omega(-), \cliels(\fl \otimes \Omega_c(-)  \big)}$).}
  \end{align}
@@
 \begin{lmm}\label{L:compisassociative} Let $\fg \stackrel{f}\to \fh$, $\fh \stackrel{g}\to \fl$ and $\fl \stackrel{h}\to \fk$ be maps of $L_\infty$-algebras.
- Then, we have, for any $\varphi \in \clies\big(\fg\otimes \Omega, \cliels(\fh \otimes \Omega_c) \big)$, 
-  $\psi \in \clies\big(\fh\otimes \Omega, \cliels(\fl \otimes \Omega_c) \big)$ and  
-  $\gamma \in \clies\big(\fl\otimes \Omega, \cliels(\fk \otimes \Omega_c) \big)$, the equality 
+ Then, we have, for any $\varphi \in \clies\big(\fg\otimes \Omega(-), \cliels(\fh \otimes \Omega_c(-)) \big)$, 
+  $\psi \in \clies\big(\fh\otimes \Omega(-), \cliels(\fl \otimes \Omega_c(-)) \big)$ and  
+  $\gamma \in \clies\big(\fl\otimes \Omega(-), \cliels(\fk \otimes \Omega_c(-)) \big)$, the equality 
   \[ (\gamma\star \psi)\star \varphi \;=\; \gamma\star (\psi \star \varphi) \quad \mbox{ in 
-  $\clies\big(\fg\otimes \Omega, \cliels(\fk \otimes \Omega_c) \big)$.}  \]
+  $\clies\big(\fg\otimes \Omega(-), \cliels(\fk \otimes \Omega_c(-)) \big)$.}  \]
 \end{lmm}
@@
  \[\tiny \begin{tikzcd}
- \clies\big(\fh \otimes \Omega, \cliels(\fl \otimes \Omega_c  \big) 
- \otimes  \clies\big(\fg \otimes \Omega, \cliels(\fh \otimes \Omega_c  \big) 
- \otimes \cliels(\fg \otimes \Omega_c  \big) \arrow[rd, "(-\star-)\otimes \id"]
+ \clies\big(\fh \otimes \Omega(-), \cliels(\fl \otimes \Omega_c(-)  \big) 
+ \otimes  \clies\big(\fg \otimes \Omega(-), \cliels(\fh \otimes \Omega_c(-)  \big) 
+ \otimes \cliels(\fg \otimes \Omega_c(-)  \big) \arrow[rd, "(-\star-)\otimes \id"]
  \arrow[dd, "\id\otimes \ev_ {\mathbf{f}}"]& \\ 
- & \clies\big(\fg \otimes \Omega, \cliels(\fl \otimes \Omega_c  \big) 
- \otimes \cliels(\fg \otimes \Omega_c  \big)
+ & \clies\big(\fg \otimes \Omega(-), \cliels(\fl \otimes \Omega_c(-)  \big) 
+ \otimes \cliels(\fg \otimes \Omega_c(-)  \big)
  \arrow[dd, "\ev_{\mathbf{g}\circ \mathbf{f}}"]\\
-\clies\big(\fh \otimes \Omega, \cliels(\fl \otimes \Omega_c  \big) 
- \otimes \cliels(\fh \otimes \Omega_c  \big)  \arrow[rd, "\ev_{\mathbf{g}}"] & \\  & \cliels(\fl \otimes \Omega_c  \big). 
+\clies\big(\fh \otimes \Omega(-), \cliels(\fl \otimes \Omega_c(-)  \big) 
+ \otimes \cliels(\fh \otimes \Omega_c(-)  \big)  \arrow[rd, "\ev_{\mathbf{g}}"] & \\  & \cliels(\fl \otimes \Omega_c(-)  \big). 
 \end{tikzcd}\]
@@
 \item If $f= \fg \stackrel{\id}\to \fg$,  the composition $(-\star-)$ makes 
-$\clies\big(\fg \otimes \Omega, \cliels(\fg \otimes \Omega_c) \big)$ into an 
+$\clies\big(\fg \otimes \Omega(-), \cliels(\fg \otimes \Omega_c(-)) \big)$ into an 
 (augmented) associative algebra object in factorization algebra, with unit given by $\mathbf{1}$, 
-which is equivalent to the structure of the center ${\frak Z} (\cliels(\fg \otimes \Omega_c))$. 
+which is equivalent to the structure of the center ${\frak Z} (\cliels(\fg \otimes \Omega_c(-)))$. 
 \end{enumerate}
@@
 By Theorem~\ref{thm:centralizerfactorization}, we know that the factorization algebras models for the centralizers are given by the respective Chevalley-Eilenberg cochain factorizations algebras 
-(Definition~\ref{dfn:CEofFact}) $\clies\big(\fg \otimes \Omega, \cliels(\fh \otimes \Omega_c  \big) $, 
-$\clies\big(\fh \otimes \Omega, \cliels(\fl \otimes \Omega_c  \big) $ and $\clies\big(\fg \otimes \Omega, \cliels(\fl \otimes \Omega_c  \big) $ 
+(Definition~\ref{dfn:CEofFact}) $\clies\big(\fg \otimes \Omega(-), \cliels(\fh \otimes \Omega_c(-)  \big) $, 
+$\clies\big(\fh \otimes \Omega(-), \cliels(\fl \otimes \Omega_c(-)  \big) $ and $\clies\big(\fg \otimes \Omega(-), \cliels(\fl \otimes \Omega_c(-)  \big) $ 
 equipped with the evaluations maps are given by $\ev_{\mathbf{f}}$, $\ev_{\mathbf{g}}$ and $\ev_{\mathbf{g}\circ \mathbf{f}}$. We are thus left 
@@
 
-\section{Examples}
-
-\greg{Add the Koszul duality example. Add examples coming from topological spaces and abelian Lie algebras}
-
-\subsection{Koszul duality}
-\label{sec: Koszul}
-
-Consider the trivial $E_n$-algebra $k$ and suppose $\varepsilon : \UU_n \fg \to k$ is the natural augmentation. 
-Then, ${\frak Z}_n (\varepsilon)$ is the $E_n$-{\em Koszul dual} of the $E_n$-algebra $\UU_n \fg$. 
-Our results provide a model for this $E_n$-algebra as a locally constant factorization algebra on $\RR^n$ which assigns to an open set $U \subset \RR^n$ the cochain complex
-\[
-\clie \left(\fg \otimes \Omega(U) \right) .
-\]
-
-\subsection{Universal bulk TFT}
+\section{Universal bulk TFT}
 \label{sec: TFT}
 
-Generally speaking, the local observables of a topological field theory on a manifold $M$ form a locally constant factorization algebra on $M$.
-
-Let $\fg$ be a dg Lie algebra and consider the $E_n$ algebra $\UU_n \fg$. 
-We have shown that a model for the $E_n$-center ${\frak Z}_n (\UU_n \fg) = {\frak Z}_n ({\rm id}_{\UU_n \fg})$ is the $n$-dimensional locally constant factorization algebra 
-\[
-\clie \left( \fg \otimes \Omega \; , \; \clieu (\fg \otimes \Omega_c) \right)  .
-\]
-
-Let us place this locally constant factorization algebra on the $n$-manifold $M$.
-This factorization algebra is equivalent to the pushforward of a factorization algebra $\cF_{\rm bulk}$ on the $(n+1)$-dimensional manifold $M \times \RR$ along the projection $\pi : M \times \RR \to M$.
-We proceed to construct this factorization algebra.
-
-For an open set $V \subset M \times I$ let $\cF^{\rm cl}_{\rm bulk} (V)$ be the cochain complex 
-\[
-\cF^{\rm cl}_{\rm bulk} (V) = \clie \bigg(\fg \otimes \Omega (V) \; , \; \Sym \left(\fg \otimes \Omega_c(V) [2] \right) \bigg) .
-\]
-The assignment $V \mapsto \cF^{\rm cl}_{\rm bulk}(V)$ defines a locally constant factorization algebra $\cF^{\rm cl}_{\rm bulk}$ on $M \times \RR$.
-
-The factorization algebra $\pi_* \cF^{\rm cl}_{\rm bulk}$ on $M$ is quasi-isomorphic to a certain limit, or ``deqauntization", of the $E_n$-center of $\UU_n \fg$. 
+Generally speaking, the local observables of a topological field theory on a manifold $M$ define a locally constant factorization algebra on $M$.
+
+\begin{thm}
+Let $M$ be a smooth $n$-manifold and $\fg$ a Lie algebra. 
+There is a constructible factorization algebra on $M \times [0,1)$ satisfying the following properties:
+\begin{itemize}
+\item[(1)] On the $n$-dimensional stratum $M \times \{0\}$ the factorization algebra is equivalent to $\clieu (\fg \otimes \Omega_c)$.
+\item[(2)] On the $(n+1)$-dimensional stratum $M \times (0,1)$, the factorization algebra is a quantization of the observables of topological BF theory based on the Lie algebra $\fg$.
+\item[(3)] Locally on $\RR^n \times [0,1)$ this factorization algebra produces \brian{deligne picture how to say}
+\end{itemize}
+\end{thm}
+
+%Let $\fg$ be a dg Lie algebra and consider the $E_n$ algebra $\UU_n \fg$. 
+%We have shown that a model for the $E_n$-center ${\frak Z}_n (\UU_n \fg) = {\frak Z}_n ({\rm id}_{\UU_n \fg})$ is the $n$-dimensional locally constant factorization algebra 
+%\[
+%\clie \left( \fg \otimes \Omega \; , \; \clieu (\fg \otimes \Omega_c) \right)  .
+%\]
+
+\subsection{The bulk TFT}
+
+Let us place the locally constant factorization algebra module the $E_n$-enveloping algebra $\clieu(\fg \otimes \Omega_c)$ on the $n$-manifold $M$.
+This factorization algebra is equivalent to the pushforward of a factorization algebra $\Obs_{\rm BF}$ on the $(n+1)$-dimensional manifold $M \times \RR$ along the projection $\pi : M \times (0,1) \to M$ which we proceed to construct.
+
+\begin{dfn}
+For an open set $V \subset M \times (0,1)$ let $\Obs^{\rm cl}_{\rm BF} (V)$ be the cochain complex 
+\[
+\Obs^{\rm cl}_{\rm BF} (V) = \clie \bigg(\fg \otimes \Omega (V) \; , \; \Sym \left(\fg \otimes \Omega_c(V) [2] \right) \bigg) .
+\]
+The assignment $V \mapsto \Obs^{\rm cl}_{\rm BF}(V)$ defines a locally constant factorization algebra on $M \times (0,1)$. 
+\end{dfn}
+
+We note that $\Obs_{\rm BF}^{\rm cl}$ is a factorization algebra with values in commutative dg algebras. 
+In fact, it is given by the ``classical observables" of a topological field theory on $M \times (0,1)$ known as ``topological BF theory".
+
+We now consider the pushforward factorization algebra $\pi_* \Obs^{\rm cl}_{\rm BF}$ on $M$.
+Locally, on disks, we will see that it is quasi-isomorphic to a certain limit, or ``dequantization", of our model for the $E_n$-center of $\UU_n \fg$.
+Recall, this model is given by the factorization algebra on $M$:
+\begin{equation}\label{eqn:centerTFT}
+\clie\left(\fg \otimes \Omega \, , \, \clieu (\fg \otimes \Omega_c) \right) .
+\end{equation}
+
+The ``dequantization" is defined using the following filtration of this model.
+For any Lie algebra $\fh$, let $\clieu_{\leq k} (\fh)$ be the subcomplex of Chevalley--Eilenberg chains which is $\Sym^{\leq k} (\fh[1])$ as an underlying graded vector space.
+
+\begin{dfn}
+Introduce the filtration on the factorization algebra on $M$ in (\ref{eqn:centerTFT}) by 
+\[
+F^k \bigg(\clie\left(\fg \otimes \Omega \, , \, \clieu (\fg \otimes \Omega_c) \right) \bigg) = \clie \bigg(\fg \otimes \Omega \; , \; \clieu_{\leq k} (\fg \otimes \Omega_c) \bigg) .
+\]
+\end{dfn}
+
+This is a filtration of factorization algebras on $M$. 
+The associated graded factorization algebra is
+\[
+{\rm Gr} \; \bigg(\clie\left(\fg \otimes \Omega \, , \, \clieu (\fg \otimes \Omega_c) \right) \bigg) \; = \; \clie \bigg(\fg \otimes \Omega \; , \; \Sym \left(\fg \otimes \Omega_c [1] \right) \bigg) .
+\]
+Notice this is similar to the model $E_n$-center except we have turned off the Chevalley--Eilenberg differential on chains.
+
+ \begin{lmm}
+There is a quasi-isomorphism of commutative factorization algebras on $M$:
+\[
+\pi_* \Obs^{\rm cl}_{\rm BF} \; \xto{\simeq} \; {\rm Gr} \; \bigg(\clie\left(\fg \otimes \Omega \, , \, \clieu (\fg \otimes \Omega_c) \right) \bigg) .
+\]
+\end{lmm}
+
+In fact, we will show that this quasi-isomorphism is a deformation retraction.
+
+\begin{proof}
 To exhibit this quasi-isomorphism, we introduce the following cochain maps.
@@
 
+\section{Factorization algebras that model centralizers}
+
+\brian{Remark about twisting in the unoriented case.}
+
+\section{Examples}
+
+\greg{Add the Koszul duality example. Add examples coming from topological spaces and abelian Lie algebras}
+
+\subsection{Koszul duality}
+\label{sec: Koszul}
+
+Consider the trivial $E_n$-algebra $k$ and suppose $\varepsilon : \UU_n \fg \to k$ is the natural augmentation. 
+Then, ${\frak Z}_n (\varepsilon)$ is the $E_n$-{\em Koszul dual} of the $E_n$-algebra $\UU_n \fg$. 
+Our results provide a model for this $E_n$-algebra as a locally constant factorization algebra on $\RR^n$ which assigns to an open set $U \subset \RR^n$ the cochain complex
+\[
+\clie \left(\fg \otimes \Omega(U) \right) .
+\]
+
 \subsection{$E_n$-calculus}
@@
 let $f\otimes X  $ be an 
-element in $\cliels\big(\fg \otimes \Omega^* , B\big) \otimes \cliels\big(\fg \otimes \Omega_c^* \big)$.  
+element in $\cliels\big(\fg \otimes \Omega^* (-), B(-)\big) \otimes \cliels\big(\fg \otimes \Omega_c^* (-)\big)$.  
 Let
@@
 
-Recall that we have a factorization algebra map~\eqref{eq:DefofFonFaclevel}  $\mathbf{f}: \cliels(\fg \otimes \Omega_c^* \to B$.
+Recall that we have a factorization algebra map~\eqref{eq:DefofFonFaclevel}  $\mathbf{f}: \cliels(\fg \otimes \Omega_c^*(-) \to B(-)$.
 The unital factorization algebra is given, for any open $U$, by $k(U)=k$.
@@
 \end{multline}
+
+\smallskip
 
@@
  Using the diagramm~\eqref{eq:Cechassociatedtoconfofdisks}, it is equivalent to prove that the following diagram 
- \xymatrix{ \check{C}(\cB, _\cU)\ar[r] \ar[d] & \check{C}(\cB', _\cU) \ar[d] \\ \check{C}(\cC, _\cU\ar[r] & \check{C}(\cC', _\cU}
- is commutative. But the map $\check{C}(\cB, _\cU) \to \check{C}(\cB', _\cU)$ 
+ \xymatrix{ \check{C}(\cB, (-)_\cU)\ar[r] \ar[d] & \check{C}(\cB', (-)_\cU) \ar[d] \\ \check{C}(\cC, (-)_\cU\ar[r] & \check{C}(\cC', (-)_\cU}
+ is commutative. But the map $\check{C}(\cB, (-)_\cU) \to \check{C}(\cB', (-)_\cU)$ 
  is induced by the direct sums of tensors products of chain maps $ g(W_i): \cB(U_i)= \cB_{U_i}(W_i) \to \cB'_{U_i} (W_i)$ on each $i=1\dots r$ and 
@@
 
-We now apply this to the special case of $\UU_n(\fg)$, that is for $\cA= \cliels(\Omega^*_c \otimes \fg)$ as we have seen. 
+We now apply this to the special case of $\UU_n(\fg)$, that is for $\cA(-)= \cliels(\Omega^*_c(-) \otimes \fg)$ as we have seen. 
 \begin{lmm}
@@
 \begin{proof}
- The commtativity of the right square follows from~\eqref{eq:Cechassociatedtoconfofdisks}. For the left square, note that the factorization algebra structure maps on $\cliels(\Omega^*_c \otimes \fg)$ 
+ The commtativity of the right square follows from~\eqref{eq:Cechassociatedtoconfofdisks}.
+For the left square, note that the factorization algebra structure maps on $\cliels(\Omega^*_c(-) \otimes \fg)$
  are induced by applying the Chevalley-Eilenberg chain functor to the canonical maps of cosheaves of Lie algebras $\bigoplus_{i=1}^{r} (\Omega^*_c(U_i)\otimes \fg) \cong \Omega^*_c(\coprod U_i) \otimes \fg \longrightarrow  \Omega^*_c(V)\otimes \fg $.

### 2020-09-02 draft.tex
small discussion stuff
finished with first draft of section 3 (main proof)

@@
 In particular, thanks to Knudsen \cite{Knudsen}, 
-we know that the $E_n$ enveloping algebra $\UU_n \fg$ admits a model whose underlying functor on the poset of open sets in $\RR^n$ assigns $\cliels(\Omega_c^*(V) \otimes \fg)$ to each open set~$V$.
+we know that the $E_n$ enveloping algebra $\UU_n \fg$ admits a model $\bU_n \fg$ whose underlying functor on the poset of open sets in $\RR^n$ assigns $\cliels(\Omega_c^*(V) \otimes \fg)$ to each open set~$V$.
 There is another factorization algebra whose underlying assigns $\clies(\Omega^*(V) \otimes \fg)$ to each open~$V$.
@@
 \[
-f: \UU_n \fg \to \UU_n \fh
+\UU_n f: \UU_n \fg \to \UU_n \fh
 \]
 between their enveloping $E_n$ algebras.
-The centralizer ${\frak Z}_{E_n}(f)$ is an $E_n$-algebra modeled by the factorization algebra 
+The centralizer of this map ${\frak Z}_{E_n}(\UU_n f)$ is an $E_n$-algebra modeled by the factorization algebra 
 \[
@@
 One can work with locally constant, homotopy-coherent $\Disk_n^\sqcup$-algebras.
-\item In particular, in addition to the factorization algebra model, Knudsen verifies that we can model the enveloping $E_n$ algebra by a strict $\Disk_n$-algebra $\cliels(\fg[-n])$ that is strictly locally constant.
-\item Lurie and Francis give a characterization of the centralizer ${\frak Z}_{E_n}(f)$ of any $E_n$ algebra map $f: A \to B$ as the ``internal hom'' in left $\int_{S^{n-1}}A$-modules from $A$ to $B_f$, where $B_f$ denotes $B$ viewed as a left module via the map~$f$.
+\item Knudsen verifies that we can model the enveloping $E_n$ algebra by the factorization algebra $\bU_n \fg$ described earlier.
+\item Lurie and Francis give a characterization of the centralizer ${\frak Z}_{E_n}(f)$ of any $E_n$ algebra map $\phi: A \to B$ as the ``internal hom'' in left $\int_{S^{n-1}}A$-modules from $A$ to $B_\phi$, where $B_\phi$ denotes $B$ viewed as a left module via the map~$\phi$.
 \item In combination, the centralizer is characterized up to quasi-isomorphism, 
@@
 \begin{enumerate}
-\item From the map $f: \cliels(\Omega_c^* \otimes \fg) \to \cliels(\Omega_c^* \otimes \fh)$, 
-we produce an explicit factorization algebra $\clies(\Omega \otimes \fg, \cliels(\Omega_c^* \otimes \fh)_f)$ as a kind of ``convolution factorization algebra.'' 
+\item Let ${\bf f}: \cliels(\Omega_c^* \otimes \fg) \to \cliels(\Omega_c^* \otimes \fh)$ denote a map of factorization algebras that models with map $\UU_n f$ between enveloping algebras. 
+We use it to produce an explicit factorization algebra $\clies(\Omega \otimes \fg, \cliels(\Omega_c^* \otimes \fh)_f)$ as a kind of ``convolution factorization algebra.'' 
 \item We show this object fits canonically into a centralizer diagram: there is a map of factorization algebras
 \[
-\clies(\Omega \otimes \fg, \cliels(\Omega_c^* \otimes \fh)_f) \otimes \UU_n \fg \to \cliels(\Omega_c^* \otimes \fh)
-\]
-such that precomposing with the map $1 \otimes \id_{\UU_n \fg}$ is the map~$f$.
+\clies(\Omega \otimes \fg, \cliels(\Omega_c^* \otimes \fh)_f) \otimes \bU_n \fg \to \cliels(\Omega_c^* \otimes \fh)
+\]
+such that precomposing with the map $1 \otimes \id_{\UU_n \fg}$ is the map~${\bf f}$.
 Fitting into such a diagram guarantees a canonical map 
 \[
-\clies(\Omega \otimes \fg, \cliels(\Omega_c^* \otimes \fh)_f) \to Z_f
+\clies(\Omega \otimes \fg, \cliels(\Omega_c^* \otimes \fh)_f) \to \bZ({\bf f})
 \]
@@
 
+\owen{Add discussion of how this makes sense even on unoriented manifolds.}
+
 In fact, Knudsen shows a stronger version of the second part.
 if one restricts to working with open balls in $\RR^n$ (rather than arbitrary open sets)
-then there is a $\Disk_n$-algebra ${\tt U}_n \fg$ assigning $\cliels(\fg[-n])$ to each ball and it is manifestly locally constant.
+then there is a $\Disk_n$-algebra ${\tt U}_n \fg$ assigning $\cliels(\fg[-n]) = \Sym(\fg[1-n])$ to each ball and it is manifestly locally constant.
 This algebra ${\tt U}_n \fg$ is a model for~$\UU_n \fg$.
@@
 \[
-\theta_{\bf{f}}: \clies\big(\fg\otimes \Omega , B \big) \longrightarrow  {\frak Z}(\mathbf{f})
-\]
-where ${\frak Z}(\mathbf{f})$ is a factorization algebra that models the centralizer ${\frak Z}(f)$ of the map $f$.
-\owen{Calibrate notations!}
+\theta_{{\bf f}}: \clies\big(\fg\otimes \Omega , B \big) \longrightarrow  \bZ(\mathbf{f})
+\]
+where $\bZ(\mathbf{f})$ is some locally constant factorization algebra that models the centralizer ${\frak Z}(f)$ of the map $f$.
 It is then a direct computation to verify $\theta_f$ is a quasi-isomorphism,
@@
 For instance, we use $\bU_n \fg$ for the factorization model of the enveloping $E_n$ algebra,
-and we use $\bf{f}: \bU_n \fg \to \bU_n \fh$ for the factorization model of the map $f: \UU_n \fg \to \UU_n \fh$ of $E_n$ algebras.
+and we use ${\bf f}: \bU_n \fg \to \bU_n \fh$ for the factorization model of the map $f: \UU_n \fg \to \UU_n \fh$ of $E_n$ algebras.
 
@@
 
-\owen{I want to recall briefly how an $L_\infty$ action on a cochain complex leads to all the variants of CE (co)chains.
-It can just be a compendium of facts we use below.}
-
-To any $\fg$-module $M$ (whether $\fg$ is a dg Lie algebra or an $L_\infty$-algebra), 
-we can associate its Chevalley-Eilenberg cochain complex defined 
-by 
-\begin{equation}
- \clies(\fg, M) = \Hom (Sym(\fg[-1]), M)
-\end{equation}
-with its classical differential. 
-\greg{recall....quickly. AT least for dg-part. Say something for $L_\infty$ too}
-We have the evaluation map 
-\begin{equation}
- \label{eq:defev} \ev: \clies(\fg, M) \otimes Sym(\fg[-1])\to M
-\end{equation}
-given by applying a function on a given tensor in $Sym(\fg[-1])$.
-
-\begin{dfn}
-\label{dfn: CE from map}
-\owen{an $L_\infty$ map $\fg \rightsquigarrow \fh$ induces a cochain complex $\clies(\fg,\cliels(\fh))$.}
-\end{dfn}
+\owen{Please read and comment if it is too fast or cryptic (or wrong due, e.g., to sloppy shifts).}
+
+We assume the reader is familiar with Lie algebras and $L_\infty$ algebras and with standard constructions,
+such as the Chevalley-Eilenberg chains or cochains, which we may also call the Lie algebra (co)chains.
+A nice reference is \owen{Loday-Vallette???}
+Nonetheless, we review a few aspects that play a crucial role below.
+
+First, recall that an $L_\infty$ algebra $\fg$, with its collection of brackets $\{\ell_n\}_{n \geq 1}$ is fully encoded by its dg conilpotent cocommutative coalgebra
+\[
+\cliels(\fg) = (\Sym(\fg[1]), \d = \sum_n \ell_n)
+\]
+where the sum of the brackets provides a square-zero coderivation.
+The square-zero condition efficiently encodes the higher Jacobi relations.
+This coalgebra is canonically coaugmented by the inclusion of the base field $k \xto{\simeq} \Sym^0(\fg[1])$.
+Let $\overline{\cliels(\fg)} \subset \cliels(\fg)$ denote the subcoalgebra given by the direct sum over positive symmetric powers of $\fg[1]$,
+which can be identified with both the kernel of the counit map as well as cokernel of the coaugmentation map.
+
+By definition, an $L_\infty$ map $f: \fg \rightsquigarrow \fh$ is a (strict) map of such dg cocommutative coalgebras
+\[
+f: \cliels(\fg) \to \cliels(\fh).
+\]
+The requirement that $f$ preserves all that structure encodes efficiently that the brackets intertwine in the correct fashion.
+It is then immediate that the hom-complex
+\[
+\Hom^\bullet (\cliels(\fg), \cliels(\fh))
+\]
+admits a deformed differential
+\[
+\d_\Hom + [f,-]
+\]
+known as a twisting cocycle.
+We use 
+\[
+\clies(\fg,\cliels(\fh)_f)
+\]
+to denote this cochain complex whose differential depends on the choice of $L_\infty$ map~$f$,
+and we call it the {\em Lie algebra cochains of $\fg$ with values in $\fh$ arising from the map~$f$}.
+
+This complex $\clies(\fg,\cliels(\fh)_f)$ encodes the deformation theory for $L_\infty$ maps around the map $f$.
+That is, in a sufficiently sophisticated geometric setting, it is the tangent complex to the mapping space of $L_\infty$ maps from $\fg$ to~$\fh$.
+One should view $f$ as the basepoint for this tangent complex.
+Due to the splitting
+\[
+\cliels(\fg) = k \oplus \overline{\cliels(\fg)},
+\]
+we have a decomposition
+\[
+\clies(\fg,\cliels(\fh)_f) \cong \cliels(\fh) \oplus \Hom^\bullet(\overline{\cliels(\fg)}, \cliels(\fh)_f),
+\]
+which plays a crucial role in our argument.
+
+Indeed, consider the canonical evaluation pairing
+\[
+\ev_{f}: \clies(\fg,\cliels(\fh)_f) \otimes \cliels(\fg) \to \cliels(\fh)
+\]
+sending $(1 + g, x)$ to $f(x) + g(x)$, where $g \in \Hom^\bullet(\overline{\cliels(\fg)}, \cliels(\fh)_f)$.
+In this sense, we see how the Lie algebra cochains arising from $f$ encodes deformations.
 
@@
 
-\owen{Add a remark on convolution?}
+\begin{rmk}
+For those coming from an operadic background, it may be helpful to recognize that our approach is a variant of a familiar convolution construction.
+The functor $\bU_n \fh = \cliels(\Omega^*_c \otimes \fh)$ determines an algebra over the colored operad ${\rm Opens}_{\RR^n}^\sqcup$,
+while the functor $\cliels(\Omega^* \otimes \fg)$ determines a {\em co}\/algebra over the colored operad ${\rm Opens}_{\RR^n}^\sqcup$.
+The algebra $\clies(\Omega^* \otimes \fg, (\bU_n \fh)_f)$ assigns the graded vector space
+\[
+\Hom^\bullet(\cliels(\Omega^*(V) \otimes \fg), \cliels(\Omega^*_c(V) \otimes \fh))
+\] 
+to each open set $V$,
+twining together this coalgebra and algebra.
+\owen{This has a name, but I'm blanking at the moment.}
+The differential can be seen as a twisting cocycle arising from a choice of map $f$;
+there is a natural basepoint to the space of differentials on this graded vector space by taking the usual differential of a hom-complex.
+\end{rmk}
+
 %
@@
 \[
-\ev_{\bf{f}}: \clies(\Omega^* \otimes \fg, (\Omega^*_c \otimes \fh)_f) \otimes \bU_n \fg \to \bU_n \fh,
+\ev_{{\bf f}}: \clies(\Omega^* \otimes \fg, (\Omega^*_c \otimes \fh)_f) \otimes \bU_n \fg \to \bU_n \fh,
 \]
@@
 \[
-\ev_{\bf{f}}(V): \clies(\Omega^*(V) \otimes \fg, \cliels(\Omega^*_c(V) \otimes \fh)_f) \otimes \bU_n \fg(V) \to \bU_n \fh(V)
+\ev_{{\bf f}}(V): \clies(\Omega^*(V) \otimes \fg, \cliels(\Omega^*_c(V) \otimes \fh)_f) \otimes \bU_n \fg(V) \to \bU_n \fh(V)
 \]
@@
 \[
-V \mapsto \ev_{\bf{f}}(V)
+V \mapsto \ev_{{\bf f}}(V)
 \]
@@
 
-\greg{
-We start by defining a pairing between the factorization algebras of Chevalley-Eilenberg (co)chains in order to use the universal property of centralizers.\\
-First note that compactly supported form embeds in all forms, therefore we can apply 
-any element of $\cliels\big(\fg \otimes \Omega^* , B\big)$ 
-to any element of $\cliels\big(\fg \otimes \Omega_c^* \big)$. Therefore, for any  $p\in \bN$, we have an evaluation 
-\begin{equation} \label{eqdef:ev} \begin{array}{c}\ev: Sym^p \big( \fg \otimes \Omega^* (U)[-1] ,B(U)\big)
-\otimes  Sym^p( \fg\otimes \Omega^*_c(U) [1]) \stackrel{ev}\longrightarrow B(U)  
-  \\
- (x,\Phi) \,\longmapsto\, (-1)^{p(|x|+p) } \Phi (x)\end{array}
-\end{equation} induced by this embedding  in all forms followed by evaluating on a function.\\
-Second, the augmentation of $B$ makes $B$ augmented as well (in the obvious sense of~\cite{Gi-NotesFactorization}) and this induces an augmentation on
-$\clies\big(\fg\otimes \Omega , B \big)$ as well as follows. 
-We have the canonical factorization algebra map  $\mathbf{1}$  defined, for any open $U$, by 
-\[\xymatrix{ k(U)=k  \ar[r]^{\quad \cong}& 
-B(\emptyset) \ar[r] & B(U)  } 
- \] where the last map is given by the factorization algebra structure of $B$. This gives the canonical element element 
- $\mathbf{1}\in \clies(\fg\otimes \Omega^*, B) )$ which is the unit $k\to \clies(\fg\otimes \Omega^*, B) )$
- of the factorization structure of 
- the Chevalley-Eilenberg cochain factorization algebras~\ref{dfn:CEofFact}.  
- The augmentation map is given by $\varphi\mapsto \varepsilon \circ \varphi \circ 
- \iota$ where $\iota: k(U) \cong k \hookrightarrow Sym(\fg \otimes \Omega (U) [1]) $ is the inclusion and $\varepsilon B(U)\to k(U)$ is the augmentation of 
- $B$. We therefore obtain a canonical splitting of factorization algebras 
- \begin{equation}\label{eq:splittingbyaugm}
-   \clies\big(\fg\otimes \Omega^*, B\big)  \, \cong \, k \oplus \overline{ \clies(\fg\otimes \Omega^*, B) )}
- \end{equation}
-given by the augmentation. Below~\ref{Rmk:defgraduationclie}, we refine  this splitting, using it  freely  on each-connected component, to obtain 
-a natural grading on it.\\
-We use the splitting and~\eqref{eqdef:ev} to define our pairing as follows. First for a \emph{connected} open subset $W$ of $\RR^n$, we define 
-\begin{multline}\label{eq:defevforconnected}
- \ev_f^W:   \clies (\fg\otimes \Omega (W), B(W)) \otimes \cliels\big(\fg \otimes \Omega_c^* (W)) 
- \\ \cong \, \left( k(W) \oplus \overline{\clies (\fg\otimes \Omega (W), B(W))  }\right) 
- \otimes \cliels\big(\fg \otimes \Omega_c^* (W))  \\ \cong
- \cliels\big(\fg \otimes \Omega_c^* (W))  \oplus  \left(\overline{\clies (\fg\otimes \Omega (W), B(W))  }\otimes \cliels\big(\fg \otimes \Omega_c^* (W)) 
- \right) \\
- \stackrel{ \mathbf{f}\oplus \ev}\longrightarrow  
- B(W)
-\end{multline}
-where $\mathbf{f}$ is the factorization algebra morphism  we are given.
-In other words, if $\varphi = \lambda \mathbf{1} \oplus \overline{\varphi}$ is the decomposition of $\varphi \in  \clies (\fg\otimes \Omega (W), B(W)) $,
-we have 
-\[ \ev_f^W(\varphi\otimes x)= \lambda \mathbf{f}(W)(x) + \overline{\varphi}(x). \]
-We extend this construction  to any 
- open subset in $\RR^n$ using the \lq\lq{}Leibniz rule\rq\rq{}, that is on using it freely on every connected components. 
- More precisely, 
-  write $U=\coprod_{i\in I} U_i$ the decomposition of an open into the  disjoint union 
-of its connected components. Using, the natural isomorphisms of complexes 
-\[Sym\big(\fg \otimes \Omega (U)[-1]\big) 
-\cong \bigotimes\limits_{i\in I} Sym\big(\fg \otimes \Omega ( U_i)[-1]\big), \mbox{  } 
-\bigotimes_{i\in I} \cliels\big(\fg \otimes \Omega_c^* (U_i)\big) \cong
-\cliels\big(\fg \otimes \Omega_c^* (U)\big)\] and
-$\bigotimes_{i\in I} B(U_i) 
-\stackrel{\simeq}\longrightarrow B(U)$, we obtain the 
- (natural) decomposition 
-\begin{multline}\label{eq:defgraduationoncentralizernonconnected}
- \clies\big(\fg\otimes \Omega^*(U), B(U)\big)  \, \cong \, 
- \Hom\left(\bigotimes\limits_{i\in I} Sym\Big(\fg\otimes \Omega (U_i)[-1]), 
- \bigotimes\limits_{i\in I} B(U_i)\right) \\ \cong \, 
- \bigotimes\limits_{i\in I}\left( k(U_i) \oplus \overline{\clies (\fg\otimes \Omega (U_i), B(U_i))  }\right).
-\end{multline}
-and we can therefore define 
-\begin{multline}\label{eq:defineevf}
- \ev_f^U: \clies (\fg\otimes \Omega (U), B(U)) \otimes \cliels\big(\fg \otimes \Omega_c^* (U)) 
- \\ \stackrel{\simeq}\longrightarrow  
-\bigotimes\limits_{i\in I}\left( k(U_i) \oplus \overline{\clies (\fg\otimes \Omega (U_i), B(U_i))  }\right) \otimes 
- \left(\bigotimes\limits_{i\in I}\cliels\big(\fg \otimes \Omega_c^* (U_i)\big)\right)  \\ 
- \stackrel{\bigotimes\limits_{i\in I}\ev^{U_i}_f}\longrightarrow  
- \bigotimes\limits_{i\in I} B(U_i) \stackrel{\mu_B}\longrightarrow B(U)
-\end{multline}
-where $\mu_B$ is the canonical structure map of the factorization algebra $B$ and the other maps are given by~\eqref{eq:defgraduationoncentralizernonconnected} 
-and~\eqref{eq:defevforconnected}.
-\greg{In~\eqref{eq:defgraduationoncentralizernonconnected} and definition of Chevalley Eilneberg complexes, one shall explain/takes care of the appropriate 
-things to do (like completion) for non-finitely dimensional Lie algebras}
-\greg{The decomposition used to extend $\ev$ on non-connected open can be done with any augmented $B$, simply by defining it onto the prefact alg obtained by tensoring 
-out on non-connected components and using the quasi-isomorphism canonical map to $\clies(\fg, B)$ in that case. Not sure which way is easier to define/mention}\\
-\begin{rmk}\label{Rmk:defgraduationclie} The decomposition~\eqref{eq:defgraduationoncentralizernonconnected} makes 
-the Chevalley-Eilenberg cochain complex with value on an open $U$ naturally\footnote{The grading
-is compatible (by the same argument as Lemma~\ref{L:pairingCE}) with the factorization algebra structure maps of
-$\clies(\fg\otimes \Omega, B)$} graded by the subsets of its connected components:
- \begin{equation}\label{eq:defgraduationoncentralizernonconnected2}
- \clies\big(\fg\otimes \Omega^*(U), B(U)\big)  \, \cong \, \bigoplus\limits_{J\subset I} {\clies}^{(J)}\big(\fg\otimes \Omega^*(U), B(U)\big) 
-\end{equation}
-where $J$ runs through all the (possibly empty) subsets of $I$.  Precisely, the $J$-piece is
-\begin{multline*}
-{\clies}^{(J)}\big(\fg\otimes \Omega^*(U), B(U)\big) = 
-\left(\bigotimes\limits_{j\in I\setminus J} k(U_j)\right) \otimes \left(\bigotimes\limits_{j\in J}
-\overline{\clies (\fg\otimes \Omega (U_j), B(U_j))  }\right) \\ \cong 
-\overline{\clies (\fg\otimes \Omega (\coprod\limits_{j\in_J}U_j), B(\coprod\limits_{j\in_J}U_j))  }.
-\end{multline*}
-We think of an element of ${\clies}^{(J)}\big(\fg\otimes \Omega^*(U), B(U)\big)$ has an element of ${\clies}\big(\fg\otimes \Omega^*(U), B(U)\big)$
-\emph{with support $\coprod\limits_{j\in J} U_j$}.   
-Note that the component $k$ in the decomposition~\eqref{eq:splittingbyaugm} is precisely the component 
-${\clies}^{(\emptyset)}\big(\fg\otimes \Omega^*(U), B(U)\big)$ corresponding to the empty family.
-\end{rmk}
-In other words, if $\varphi = \sum_{J\subset I} \varphi^{(J)}$ is the decomposition of $\varphi$ in its graded pieces, for all 
-$X= \bigotimes\limits_{i\in I} X_i \in \bigotimes\limits_{I}\cliels(\fg\otimes \Omega_c^*(U_i)) \cong \cliels(\fg\otimes \Omega^*_c(U))$, we 
-have the following formula generalizing the one for connected open  subsets:
-\begin{equation} \ev_f^U(\varphi\otimes X)= \sum_{J\subset I} \mu_B\left(\mathbf{f}\Big(\bigotimes\limits_{i\in I\setminus J} 
-X_i\Big)\otimes  \varphi^{(J)}\Big(\bigotimes\limits_{j\in J} 
-X_j\Big)\right) \end{equation}
-where $\mu_{B,J}: B\Big(\coprod\limits_{i\in I\setminus J}U_i\Big)\otimes B\Big(\coprod\limits_{j\in J}U_j\Big) \to B(U)$
-is the  structure map of $B$.
-}
+%\greg{
+%We start by defining a pairing between the factorization algebras of Chevalley-Eilenberg (co)chains in order to use the universal property of centralizers.\\
+%First note that compactly supported form embeds in all forms, therefore we can apply 
+%any element of $\cliels\big(\fg \otimes \Omega^* , B\big)$ 
+%to any element of $\cliels\big(\fg \otimes \Omega_c^* \big)$. Therefore, for any  $p\in \bN$, we have an evaluation 
+%\begin{equation} \label{eqdef:ev} \begin{array}{c}\ev: Sym^p \big( \fg \otimes \Omega^* (U)[-1] ,B(U)\big)
+%\otimes  Sym^p( \fg\otimes \Omega^*_c(U) [1]) \stackrel{ev}\longrightarrow B(U)  
+%  \\
+% (x,\Phi) \,\longmapsto\, (-1)^{p(|x|+p) } \Phi (x)\end{array}
+%\end{equation} induced by this embedding  in all forms followed by evaluating on a function.\\
+%Second, the augmentation of $B$ makes $B$ augmented as well (in the obvious sense of~\cite{Gi-NotesFactorization}) and this induces an augmentation on
+%$\clies\big(\fg\otimes \Omega , B \big)$ as well as follows. 
+%We have the canonical factorization algebra map  $\mathbf{1}$  defined, for any open $U$, by 
+%\[\xymatrix{ k(U)=k  \ar[r]^{\quad \cong}& 
+%B(\emptyset) \ar[r] & B(U)  } 
+% \] where the last map is given by the factorization algebra structure of $B$. This gives the canonical element element 
+% $\mathbf{1}\in \clies(\fg\otimes \Omega^*, B) )$ which is the unit $k\to \clies(\fg\otimes \Omega^*, B) )$
+% of the factorization structure of 
+% the Chevalley-Eilenberg cochain factorization algebras~\ref{dfn:CEofFact}.  
+% The augmentation map is given by $\varphi\mapsto \varepsilon \circ \varphi \circ 
+% \iota$ where $\iota: k(U) \cong k \hookrightarrow Sym(\fg \otimes \Omega (U) [1]) $ is the inclusion and $\varepsilon B(U)\to k(U)$ is the augmentation of 
+% $B$. We therefore obtain a canonical splitting of factorization algebras 
+% \begin{equation}\label{eq:splittingbyaugm}
+%   \clies\big(\fg\otimes \Omega^*, B\big)  \, \cong \, k \oplus \overline{ \clies(\fg\otimes \Omega^*, B) )}
+% \end{equation}
+%given by the augmentation. Below~\ref{Rmk:defgraduationclie}, we refine  this splitting, using it  freely  on each-connected component, to obtain 
+%a natural grading on it.\\
+%We use the splitting and~\eqref{eqdef:ev} to define our pairing as follows. First for a \emph{connected} open subset $W$ of $\RR^n$, we define 
+%\begin{multline}\label{eq:defevforconnected}
+% \ev_f^W:   \clies (\fg\otimes \Omega (W), B(W)) \otimes \cliels\big(\fg \otimes \Omega_c^* (W)) 
+% \\ \cong \, \left( k(W) \oplus \overline{\clies (\fg\otimes \Omega (W), B(W))  }\right) 
+% \otimes \cliels\big(\fg \otimes \Omega_c^* (W))  \\ \cong
+% \cliels\big(\fg \otimes \Omega_c^* (W))  \oplus  \left(\overline{\clies (\fg\otimes \Omega (W), B(W))  }\otimes \cliels\big(\fg \otimes \Omega_c^* (W)) 
+% \right) \\
+% \stackrel{ \mathbf{f}\oplus \ev}\longrightarrow  
+% B(W)
+%\end{multline}
+%where $\mathbf{f}$ is the factorization algebra morphism  we are given.
+%In other words, if $\varphi = \lambda \mathbf{1} \oplus \overline{\varphi}$ is the decomposition of $\varphi \in  \clies (\fg\otimes \Omega (W), B(W)) $,
+%we have 
+%\[ \ev_f^W(\varphi\otimes x)= \lambda \mathbf{f}(W)(x) + \overline{\varphi}(x). \]
+%We extend this construction  to any 
+% open subset in $\RR^n$ using the \lq\lq{}Leibniz rule\rq\rq{}, that is on using it freely on every connected components. 
+% More precisely, 
+%  write $U=\coprod_{i\in I} U_i$ the decomposition of an open into the  disjoint union 
+%of its connected components. Using, the natural isomorphisms of complexes 
+%\[Sym\big(\fg \otimes \Omega (U)[-1]\big) 
+%\cong \bigotimes\limits_{i\in I} Sym\big(\fg \otimes \Omega ( U_i)[-1]\big), \mbox{  } 
+%\bigotimes_{i\in I} \cliels\big(\fg \otimes \Omega_c^* (U_i)\big) \cong
+%\cliels\big(\fg \otimes \Omega_c^* (U)\big)\] and
+%$\bigotimes_{i\in I} B(U_i) 
+%\stackrel{\simeq}\longrightarrow B(U)$, we obtain the 
+% (natural) decomposition 
+%\begin{multline}\label{eq:defgraduationoncentralizernonconnected}
+% \clies\big(\fg\otimes \Omega^*(U), B(U)\big)  \, \cong \, 
+% \Hom\left(\bigotimes\limits_{i\in I} Sym\Big(\fg\otimes \Omega (U_i)[-1]), 
+% \bigotimes\limits_{i\in I} B(U_i)\right) \\ \cong \, 
+% \bigotimes\limits_{i\in I}\left( k(U_i) \oplus \overline{\clies (\fg\otimes \Omega (U_i), B(U_i))  }\right).
+%\end{multline}
+%and we can therefore define 
+%\begin{multline}\label{eq:defineevf}
+% \ev_f^U: \clies (\fg\otimes \Omega (U), B(U)) \otimes \cliels\big(\fg \otimes \Omega_c^* (U)) 
+% \\ \stackrel{\simeq}\longrightarrow  
+%\bigotimes\limits_{i\in I}\left( k(U_i) \oplus \overline{\clies (\fg\otimes \Omega (U_i), B(U_i))  }\right) \otimes 
+% \left(\bigotimes\limits_{i\in I}\cliels\big(\fg \otimes \Omega_c^* (U_i)\big)\right)  \\ 
+% \stackrel{\bigotimes\limits_{i\in I}\ev^{U_i}_f}\longrightarrow  
+% \bigotimes\limits_{i\in I} B(U_i) \stackrel{\mu_B}\longrightarrow B(U)
+%\end{multline}
+%where $\mu_B$ is the canonical structure map of the factorization algebra $B$ and the other maps are given by~\eqref{eq:defgraduationoncentralizernonconnected} 
+%and~\eqref{eq:defevforconnected}.
+%\greg{In~\eqref{eq:defgraduationoncentralizernonconnected} and definition of Chevalley Eilneberg complexes, one shall explain/takes care of the appropriate 
+%things to do (like completion) for non-finitely dimensional Lie algebras}
+%\greg{The decomposition used to extend $\ev$ on non-connected open can be done with any augmented $B$, simply by defining it onto the prefact alg obtained by tensoring 
+%out on non-connected components and using the quasi-isomorphism canonical map to $\clies(\fg, B)$ in that case. Not sure which way is easier to define/mention}\\
+%\begin{rmk}\label{Rmk:defgraduationclie} The decomposition~\eqref{eq:defgraduationoncentralizernonconnected} makes 
+%the Chevalley-Eilenberg cochain complex with value on an open $U$ naturally\footnote{The grading
+%is compatible (by the same argument as Lemma~\ref{L:pairingCE}) with the factorization algebra structure maps of
+%$\clies(\fg\otimes \Omega, B)$} graded by the subsets of its connected components:
+% \begin{equation}\label{eq:defgraduationoncentralizernonconnected2}
+% \clies\big(\fg\otimes \Omega^*(U), B(U)\big)  \, \cong \, \bigoplus\limits_{J\subset I} {\clies}^{(J)}\big(\fg\otimes \Omega^*(U), B(U)\big) 
+%\end{equation}
+%where $J$ runs through all the (possibly empty) subsets of $I$.  Precisely, the $J$-piece is
+%\begin{multline*}
+%{\clies}^{(J)}\big(\fg\otimes \Omega^*(U), B(U)\big) = 
+%\left(\bigotimes\limits_{j\in I\setminus J} k(U_j)\right) \otimes \left(\bigotimes\limits_{j\in J}
+%\overline{\clies (\fg\otimes \Omega (U_j), B(U_j))  }\right) \\ \cong 
+%\overline{\clies (\fg\otimes \Omega (\coprod\limits_{j\in_J}U_j), B(\coprod\limits_{j\in_J}U_j))  }.
+%\end{multline*}
+%We think of an element of ${\clies}^{(J)}\big(\fg\otimes \Omega^*(U), B(U)\big)$ has an element of ${\clies}\big(\fg\otimes \Omega^*(U), B(U)\big)$
+%\emph{with support $\coprod\limits_{j\in J} U_j$}.   
+%Note that the component $k$ in the decomposition~\eqref{eq:splittingbyaugm} is precisely the component 
+%${\clies}^{(\emptyset)}\big(\fg\otimes \Omega^*(U), B(U)\big)$ corresponding to the empty family.
+%\end{rmk}
+%In other words, if $\varphi = \sum_{J\subset I} \varphi^{(J)}$ is the decomposition of $\varphi$ in its graded pieces, for all 
+%$X= \bigotimes\limits_{i\in I} X_i \in \bigotimes\limits_{I}\cliels(\fg\otimes \Omega_c^*(U_i)) \cong \cliels(\fg\otimes \Omega^*_c(U))$, we 
+%have the following formula generalizing the one for connected open  subsets:
+%\begin{equation} \ev_f^U(\varphi\otimes X)= \sum_{J\subset I} \mu_B\left(\mathbf{f}\Big(\bigotimes\limits_{i\in I\setminus J} 
+%X_i\Big)\otimes  \varphi^{(J)}\Big(\bigotimes\limits_{j\in J} 
+%X_j\Big)\right) \end{equation}
+%where $\mu_{B,J}: B\Big(\coprod\limits_{i\in I\setminus J}U_i\Big)\otimes B\Big(\coprod\limits_{j\in J}U_j\Big) \to B(U)$
+%is the  structure map of $B$.
+%}
 
@@
 \label{L:pairingCE}
-The natural transformation $\ev_{\bf{f}}$ determines a map of strict prefactorization algebras,
+The natural transformation $\ev_{{\bf f}}$ determines a map of strict prefactorization algebras,
 i.e., algebras over the colored operad ${\rm Opens}_{\RR^n}^\sqcup$.
@@
 & \clies ( \Omega \otimes \fg , (\bU_n \fh)_f) \otimes \bU_n \fg
-\ar[dr]^{\ev_{\bf{f}}} & \\
+\ar[dr]^{\ev_{{\bf f}}} & \\
 \bU_n \fg \ar[ur]^{\mathbf{1} \otimes \id} \ar[rr]^{\mathbf{f}}  & &  \bU_n \fh}
@@
 This triangle commutes on the nose, as we now show.
-What we need to show is how the unit map $u$ for $\clies ( \Omega \otimes \fg , (\bU_n \fh)_f)$ encodes the map $\bf{f}$.
-\owen{I'm stuck. Greg's statement is below.}
- It follows from lemma~\ref{L:pairingCE} that this is a diagram of factorization algebras.
-Since the unit $\mathbf{1}:Sym(\fg \otimes \Omega(U)[1]) \to B(U)$ is induced, for all $U$, by the factorization structure from the empty set $\emptyset$, we obtain that its support $I_{\mathbf{1}}=\emptyset$.
- Therefore, formula~\eqref{eq:defineevJ} yields that 
- \[\ev_{f} (\mathbf{1}\otimes X) = \ev_{\emptyset}(\tilde{\mathbf{1}}\otimes X) 
- = \mathbf{f}(X)\] which proves the commutativity.
+As a convenience, we will talk about elements, but these are only available if one evaluates a factorization algebra on an open set.
+The argument below can be expanded by verifying it holds on an arbitrary open and then by checking that it is functorial in structure maps (which is quickly confirmed).
+
+The map $\mathbf{1} \otimes \id$ sends an element $x$ of $\bU_n \fg$ to $1 \otimes x$,
+where $1 \in \clies ( \Omega \otimes \fg , (\bU_n \fh)_f)$ denotes the tensor product of the distinguished element spanning $\Sym^0$ in each tensor factor.
+(Remember that both $\clies(\Omega \otimes \fg)$ and $\cliels(\Omega_c \otimes \fh)$ have canonical retracts to the base field $k$.)
+Hence we need to show that
+\[
+\ev_{{\bf f}}(1 \otimes x) = {\bf f}(x).
+\]
+Here we recall that the evaluation pairing between Lie algebra chains and cochains that arises from an $L_\infty$ map sends the distinguished element $1$ to the map.
 \end{proof}
 
-By universal property of the centralizer (definition~\ref{D:centralizerFacAlgebra}), lemma~\ref{L:ComTriangCent} implies that the pairing $\ev_{\bf{f}}$ induces a canonical morphism 
+By universal property of the centralizer, 
+Lemma~\ref{L:ComTriangCent} implies that the pairing $\ev_{{\bf f}}$ induces a canonical morphism 
 \begin{equation}
 \label{eq:canonicaltocenter}
-\theta_{\bf{f}}: \clies\big(\fg\otimes \Omega , B \big) \longrightarrow  {\frak Z}(\mathbf{f})
+\theta_{{\bf f}}: \clies(\fg\otimes \Omega , (\bU_n \fh)_f ) \longrightarrow  {\bZ}(\mathbf{f})
 \end{equation}
@@
 
-\subsection{The map $\theta_{\bf{f}}$ is a weak equivalence.}
-
-We have defined a functorial (in $f$) factorization algebras map 
-$\theta_f$.
-
-\begin{lmm}\label{L:thetaquisondisk}Let $U$ be an open subset homeomorphic to $\RR^n$. 
- Then, the canonical map~\eqref{eq:canonicaltocenter}:
- \[\theta_f(U): \clies\big(\fg\otimes \Omega (U), B(U) \big) \longrightarrow 
- {\frak Z}(\mathbf{f})(U)\] is a quasi-isomorphism and is further quasi-isomorphic 
- to the Chevalley-Eilenberg cochain complex $\clies \big(\fg, B\big)$ 
- with value in the $E_n$-algebra $B\cong B(\RR^n)$.
+\subsection{The map $\theta_{{\bf f}}$ is a weak equivalence.}
+
+We have seen that $\clies(\fg\otimes \Omega , (\bU_n \fh )_f)$ is a locally constant factorization algebra,
+and we know the centralizer $\bZ({\bf f})$ is too.
+Thus, to show that the map $\theta_{{\bf f}}$ is a weak equivalence (or quasi-isomorphism) of factorization algebras,
+it suffices to show it is a quasi-isomorphism when evaluated on open balls.
+By local constancy, it is enough just to check on the open set~$\RR^n$ itself.
+This we now prove, and hence finish the proof of the central theorem.
+
+\begin{lmm}
+\label{L:thetaquisondisk}
+The canonical map~\eqref{eq:canonicaltocenter}
+\[
+\theta_f(D): \clies(\fg\otimes \Omega (D),  (\bU_n \fh)_f) \longrightarrow \bZ(\mathbf{f})(D)
+\] 
+ is a quasi-isomorphism for any open ball~$D$.
 \end{lmm}
+
 \begin{proof}
-Recall that $f: \UU_n \fg \to B$ denote a map of $E_n$ algebras between the enveloping $E_n$ algebra of a dg Lie algebra $\fg$ and an $E_n$ algebra $B$.
-And that $\mathbf{f}$ is the associated map of factorization algebras.
-
-Let $U\hookrightarrow \RR^n$ be the canonical inclusion. It induces a commutative diagram 
- \[ \xymatrix{ \clies\big(\fg\otimes \Omega (U), B(U) \big) \ar[d] \ar[r]^{\theta_f(U)} &
-\ar[d] {\frak Z}(\mathbf{f})(U)\\
- \clies\big(\fg\otimes \Omega (\RR^n), B(\RR^n) \big)
- \ar[r]^{\theta_f(\RR^n)}& {\frak Z}(\mathbf{f})(\RR^n)}  \]
-whose vertical maps (given by the factorization structure) are quasi-isomorphisms since the factorization algebras 
-are locally constant. 
-Therefore it is enough to prove the result for $U=\RR^n$. 
-In that case $\Omega(\RR^n) \cong k$ since $\RR^n$ is contractible and therefore  $\clies\big(\fg\otimes \Omega (\RR^n), B(\RR^n) \big) \cong \clies \big(\fg, B\big)$ as a chain complex.
-
-It therefore remains to prove that 
-$\clies\big(\fg\otimes \Omega (\RR^n), B(\RR^n) \big) \longrightarrow 
- {\frak Z}(\mathbf{f})(\RR^n)\cong {\frak Z}_{E_n}(\mathbf{f})$ is a quasi-isomorphism.
-
-The results of the preceding section imply
+Recall from Section~\ref{sec: centralizer} that 
 \begin{align*}
-{\frak Z}_{E_n}(f) &\simeq {{\rm Mor}}_{\Mod^{E_n}_{\UU_n\fg}}(\UU_n \fg, B_f) \\
-&\simeq {\rm Mor}_{\LMod_{\int_{S^{n-1}} \UU_n\fg}}(\UU_n \fg, B_f)
+{\frak Z}_{E_n}(f) &\simeq {{\rm Mor}}_{\Mod^{E_n}_{\UU_n\fg}}(\UU_n \fg, (\UU_n \fh)_f) \\
+&\simeq {\rm Mor}_{\LMod_{\int_{S^{n-1}} \UU_n\fg}}(\UU_n \fg, (\UU_n \fh)_f)
 \end{align*}
@@
 \begin{itemize}
-\item[-] $B_f$ denotes the object in $\Mod^{E_n}_{\UU_n\fg}$, as well as in $\LMod_{\int_{S^{n-1}}\UU_n}$, determined by~$f$, 
-\item[-] ${\rm Mor}_{\Mod^{E_n}_{\UU_n\fg}}(\UU_n \fg, B_f)$ denotes the classifying object for maps from $\UU_n\fg$ to $B_f$ in the $\infty$-category $\Mod^{E_n}_{\UU_n\fg}$ (i.e.
-an internal mapping object), and
-\item[-] ${\rm Mor}_{\LMod_{\int_{S^{n-1}} \UU_n\fg}} (\UU_n \fg, B_f)$ denotes the classifying object for maps from ${\UU_n\fg}$ to $B$ in the $\infty$-category $\LMod_{\int_{S^{n-1}}\UU_n\fg}$. 
+\item[-] $(\UU_n \fh)_f$ denotes the object in $\Mod^{E_n}_{\UU_n\fg}$ --- equivalently, in $\LMod_{\int_{S^{n-1}}\UU_n}$ --- determined by~$f$, 
+\item[-] ${\rm Mor}_{\Mod^{E_n}_{\UU_n\fg}}(\UU_n \fg, (\UU_n \fh)_f)$ denotes the classifying object for maps (i.e.
+an internal mapping object) from $\UU_n\fg$ to $(\UU_n \fh)_f$ in the $\infty$-category $\Mod^{E_n}_{\UU_n\fg}$, and
+\item[-] ${\rm Mor}_{\LMod_{\int_{S^{n-1}} \UU_n\fg}} (\UU_n \fg, (\UU_n \fh)_f)$ denotes the classifying object for maps from ${\UU_n\fg}$ to $\UU_n \fh$ in the $\infty$-category $\LMod_{\int_{S^{n-1}}\UU_n\fg}$.
 \end{itemize}
 Note that $\int_{S^{n-1}}\UU_n\fg$ is an $E_1$ algebra equivalent to the dg algebra $U(\fg \otimes k[\epsilon_{n-1}])$.
-This is because the rational $(n-1)$-sphere is formal, and hence its cochains are quasi-isomorphic to its cohomology $k[\epsilon_{n-1}]$.
+This identification holds because the rational $(n-1)$-sphere is formal, and hence its cochains are quasi-isomorphic to its cohomology $k[\epsilon_{n-1}]$.
 
@@
 \]
-Recall now that $\UU_n \fg \simeq \Sym(\fg[1-n])$ as $\fg$-modules 
-since, as factorization algebras (see Theorem~\ref{T:UnofLie}),  $$\UU_n \fg \cong \cliels(\Omega^*_c \otimes \fg) \cong \Sym((\fg[-n])[-1])$$ where the right hand side formula follows from the fact that the product of degree $n$ compactly supported forms is trivial and therefore $\fg[-n]$ is a trivial Lie algebra.
-Thus, base change  gives rise to an equivalence 
-\[
-{\rm Mor}_{\LMod_{\int_{S^{n-1}} \UU_n}} (\UU_n \fg, B_f)  \simeq {\rm Mor}_{U\fg} (k, B_f)
-\]
-of underlying chain complexes, i.e. an equivalence after applying forgetful functor. The right hand side is precisely Lie algebra cochains of $\fg$ with coefficients in~$B_f$, as desired.
-\end{proof}
-\greg{That proof shall still be polished but it's the idea.}
-
-\begin{prp}
-\label{L:canonicaltocenterisquis} 
-The map~\eqref{eq:canonicaltocenter}
-\[
-\clies\big(\fg\otimes \Omega , B \big) \longrightarrow  {\frak Z}(\mathbf{f})
-\] 
-is a quasi-isomorphism of factorization algebras. 
-\end{prp}
-
-\begin{proof}
-By definition (and Lemma~\ref{L:ComTriangCent}) the map 
-$\theta_f$ is a factorization algebra map between \emph{locally constant} factorization algebras. 
-Therefore, in order to prove it is a weak-equivalence of factorization algebras, it is enough to prove that 
-$\clies\big(\fg\otimes \Omega (U), B(U) \big) \longrightarrow  {\frak Z}(\mathbf{f})(U)$ is a quasi-isomorphism for every $U$ which is a disk, that is 
-homeomorphic to $\RR^n$. This is given by lemma~\ref{L:thetaquisondisk}.
+Recall from Section~\ref{sec: enveloping} that $\UU_n \fg$ admits two convenient models:
+as a factorization algebra by $\bU_n \fg$ and as a strict algebra over a colored operad $\Disk_n$ assigning $\Sym(\fg[1-n])$ to each disk.
+Base change thus gives rise to an equivalence 
+\[
+{\rm Mor}_{\LMod_{\int_{S^{n-1}} \UU_n}} (\UU_n \fg, (\UU_n \fh)_f)  \simeq {\rm Mor}_{U\fg} (k, (\UU_n \fh)_f)
+\]
+of underlying cochain complexes, i.e. an equivalence after applying the forgetful functor. 
+The right hand side is modeled by Lie algebra cochains of $\fg$ with coefficients in~$(\UU_n \fh)_f$, as desired.
+Hence the map $\theta_{\bf f}$ is a quasi-isomorphism on any disk, as needed.
 \end{proof}
@@
 
-\section{Factorization algebras that model centralizers}
-
-\brian{Remark about twisting in the unoriented case.}
-
 \section{Examples}

### 2020-09-02 draft.tex
first steps toward revising section 4

@@
 
-The universal property of centralizer (definition~\ref{D:centralizer}) implies that, for any $E_n$-algebras maps $A\stackrel{f}\to B$ and
-$B\stackrel{g}\to C$, there are natural morphisms
-\begin{equation}\label{eqdef:canonicaltocentralizers} {\frak Z}_{E_n}(g) \otimes {\frak Z}_{E_n}(f) \longrightarrow {\frak Z}_{E_n}(g\circ f)
+The universal property of centralizer (recall definition~\ref{D:centralizer}) implies that 
+for any maps $A\stackrel{f}\to B$ and $B\stackrel{g}\to C$ of $E_n$-algebras, 
+there is a natural morphism
+\begin{equation}
+\label{eqdef:canonicaltocentralizers} 
+{\frak Z}_{E_n}(g) \otimes {\frak Z}_{E_n}(f) \longrightarrow {\frak Z}_{E_n}(g\circ f)
 \end{equation}
-
-in the $\infty$-catgeory of $E_n$-algebras which are given by the  
-following commutative diagrams of $E_n$-algebras:
-\[\begin{tikzcd}
+in the $\infty$-category of $E_n$-algebras that arises from  
+following commutative diagram of $E_n$-algebras:
+\[
+\begin{tikzcd}
 &   {\frak Z}_{E_n}(g) \otimes  {\frak Z}_{E_n}(f) \otimes A \arrow[rr, "\id\otimes \ev_f"] &&  {\frak Z}_{E_n}(g) \otimes  B \arrow[dr, "\ev_g"]\\
 A \arrow[ur, "1\otimes \id_A"] \arrow[rr, "f"] && B \arrow[rr, "g"] \arrow[ur, "1\otimes \id_B"] && C. 
-\end{tikzcd}\]
- When $f=g=\id_A:A\to A$, we obtain a canonical morphism \begin{equation} \label{eq:dgAssofcenter}
- {\frak Z}_{E_n}(A){\otimes} {\frak Z}_{E_n}(A) \longrightarrow {\frak Z}_{E_n}(A).\end{equation}
- Lurie has proved that this multiplication makes the center into an (homotopy) dg-associative algebras in $E_n$-algebras 
- and therefore an $E_{n+1}$-algebra. Precisely: 
-\begin{prp}[\cite{LurieHA} Section 5] \label{P:PtyCenter}
-\begin{itemize}
- \item The canonical map~\eqref{eq:dgAssofcenter} makes the center ${\frak Z}_{E_n}(A)$ into an $E_1$-algebra in the symmetric monoidal category of 
- $E_n$-algebras.
- \item There is a canonical equivalence of the $\infty$-category $E_1\mathrm{-Alg}(E_n\mathrm{-Alg})$ with $E_{n+1}\mathrm{-Alg}$.
-\end{itemize}
-\end{prp}
+\end{tikzcd}
+\]
+When $f=g=\id_A:A\to A$, we thus obtain a canonical morphism 
+\begin{equation} 
+\label{eq:dgAssofcenter}
+{\frak Z}_{E_n}(A){\otimes} {\frak Z}_{E_n}(A) \longrightarrow {\frak Z}_{E_n}(A).
+\end{equation}
+Lurie \cite{HA} has proved that this multiplication makes the center into an $E_1$ algebra in $E_n$-algebras 
+and therefore an $E_{n+1}$-algebra, by Dunn additivity. 
+%To be precise, there is the following result.
+%
+%\begin{prp}[\cite{LurieHA} Section 5] 
+%\label{P:PtyCenter}
+%\begin{itemize}
+% \item The canonical map~\eqref{eq:dgAssofcenter} makes the center ${\frak Z}_{E_n}(A)$ into an $E_1$-algebra in the symmetric monoidal category of 
+% $E_n$-algebras.
+% \item There is a canonical equivalence of the $\infty$-category $E_1\mathrm{-Alg}(E_n\mathrm{-Alg})$ with $E_{n+1}\mathrm{-Alg}$.
+%\end{itemize}
+%\end{prp}
+
+A compelling aspect of our construction is that it lets one see these properties in a barehanded fashion,
+using familiar formulas with $L_\infty$ algebras.
+(More accurately, via composition of convolution algebras.)
+The goal of this section is to prove directly the following result.
+
+\owen{I'm pooping out, but it should be straightforward to revise this in light of our revisions above.}
+
+\begin{thm}
+\label{T:compcentralizer}
+ Let $f: \fg \to \fh$ and $g: \fh \to \fl$ be maps of  $L_\infty$-algebras.
+\begin{enumerate} 
+\item The composition $(-\star-)$ of factorization algebras (definition~\ref{def:comp}) is the canonical map 
+\[{\frak Z}_{E_n}(g) \otimes {\frak Z}_{E_n}(f) \longrightarrow {\frak Z}_{E_n}(g\circ f).\] 
+\item If $f= \fg \stackrel{\id}\to \fg$,  the composition $(-\star-)$ makes 
+$\clies\big(\fg \otimes \Omega, \cliels(\fg \otimes \Omega_c) \big)$ into an 
+(augmented) associative algebra object in factorization algebra, with unit given by $\mathbf{1}$, 
+which is equivalent to the structure of the center ${\frak Z} (\cliels(\fg \otimes \Omega_c))$. 
+\end{enumerate}
+\end{thm}
+
 When $A$ is a factorization algebra model for $A$, in virtue of theorem~\ref{T:En=Fac} 
@@
 \end{lmm}
+
 \begin{proof}
-
 \end{proof}
 
-\begin{thm}\label{T:compcentralizer}
- Let $f: \fg \to \fh$, $g: \fh \to \fl$ be  $L_\infty$-algebras morphisms.
-\begin{enumerate} \item 
- The composition $(-\star-)$ of factorization algebras (definition~\ref{def:comp}) 
- is the canonical map 
-\[{\frak Z}_{E_n}(g) \otimes {\frak Z}_{E_n}(f) \longrightarrow {\frak Z}_{E_n}(g\circ f).\] 
-\item If $f= \fg \stackrel{\id}\to \fg$,  the composition $(-\star-)$ makes 
-$\clies\big(\fg \otimes \Omega, \cliels(\fg \otimes \Omega_c) \big)$ into an 
-(augmented) associative algebra object in factorization algebra, with unit given by $\mathbf{1}$, 
-which is equivalent to the structure of the center ${\frak Z} (\cliels(\fg \otimes \Omega_c))$. 
-\end{enumerate}
-\end{thm}
-\begin{proof}
+\begin{proof}[Proof of Theorem~\ref{T:compcentralizer}]
 By universal property of centralizers, the canonical map~\eqref{eqdef:canonicaltocentralizers}  

### 2020-09-02 draft.tex
merge

--- 2020-09-01 draft.tex
@@
 
+The operad of little $n$-disks
+
+\brian{main thrust is to interpret this in terms of the BV / BD formalism}
+
 Generally speaking, the local observables of a topological field theory on a manifold $M$ define a locally constant factorization algebra on $M$.
+
+\brian{or there exists a filtration on the constructible factorization algebra whose associated graded is a commutative P0 constructible factorization algebra or $1$-shifted Poisson.}
+\brian{as a corollary butson-yoo}
 
@@
 \begin{itemize}
-\item[(1)] On the $n$-dimensional stratum $M \times \{0\}$ the factorization algebra is equivalent to $\clieu (\fg \otimes \Omega_c)$.
+\item[(1)] On the $n$-dimensional stratum $M \times \{0\}$ the factorization algebra is equivalent to $\bU_n(\fg)$.
 \item[(2)] On the $(n+1)$-dimensional stratum $M \times (0,1)$, the factorization algebra is a quantization of the observables of topological BF theory based on the Lie algebra $\fg$.
@@
 
+\subsection{A swiss cheese model}
+
+\brian{Review interpretation of the center as a swiss cheese algebra context of Deligne conjecture}
+
+\begin{prp}
+For any smooth manifold $M$ and Lie algebra $\fg$ the pair $(\bZ_n(\fg), \bU_n (\fg))$ define a constructible factorization algebra on the $(n+1)$-manifold with boundary $M \times [0,1)$.
+\end{prp}
+
 \subsection{The bulk TFT}
 
-Let us place the locally constant factorization algebra module the $E_n$-enveloping algebra $\clieu(\fg \otimes \Omega_c)$ on the $n$-manifold $M$.
+Let us place the locally constant factorization algebra model of the $E_n$-enveloping algebra $\bU_n (\fg) = \clieu(\fg \otimes \Omega_c)$ on the $n$-manifold $M$.
 This factorization algebra is equivalent to the pushforward of a factorization algebra $\Obs_{\rm BF}$ on the $(n+1)$-dimensional manifold $M \times \RR$ along the projection $\pi : M \times (0,1) \to M$ which we proceed to construct.
@@
 \begin{equation}\label{eqn:centerTFT}
-\clie\left(\fg \otimes \Omega \, , \, \clieu (\fg \otimes \Omega_c) \right) .
+\bZ_n(\fg) = \clie\left(\fg \otimes \Omega \, , \, \clieu (\fg \otimes \Omega_c) \right) .
 \end{equation}
@@
 \[
-F^k \bigg(\clie\left(\fg \otimes \Omega \, , \, \clieu (\fg \otimes \Omega_c) \right) \bigg) = \clie \bigg(\fg \otimes \Omega \; , \; \clieu_{\leq k} (\fg \otimes \Omega_c) \bigg) .
+F^k \bZ_n(\fg) = \clie \bigg(\fg \otimes \Omega \; , \; \clieu_{\leq k} (\fg \otimes \Omega_c) \bigg) .
 \]
@@
 \[
-{\rm Gr} \; \bigg(\clie\left(\fg \otimes \Omega \, , \, \clieu (\fg \otimes \Omega_c) \right) \bigg) \; = \; \clie \bigg(\fg \otimes \Omega \; , \; \Sym \left(\fg \otimes \Omega_c [1] \right) \bigg) .
+{\rm Gr} \; \bZ_n(\fg) \; = \; \clie \bigg(\fg \otimes \Omega \; , \; \Sym \left(\fg \otimes \Omega_c [1] \right) \bigg) .
 \]
@@
 \[
-\pi_* \Obs^{\rm cl}_{\rm BF} \; \xto{\simeq} \; {\rm Gr} \; \bigg(\clie\left(\fg \otimes \Omega \, , \, \clieu (\fg \otimes \Omega_c) \right) \bigg) .
+\pi_* \Obs^{\rm cl}_{\rm BF} \; \xto{\simeq} \; {\rm Gr} \; \bZ_n(\fg) .
 \]

### 2020-09-02 draft.tex
small stuff
tft changes

@@
 
-The operad of little $n$-disks
-
-\brian{main thrust is to interpret this in terms of the BV / BD formalism}
-
-Generally speaking, the local observables of a topological field theory on a manifold $M$ define a locally constant factorization algebra on $M$.
+Given an $E_{n+1}$-algebra one can speak of its $\infty$-category of left (or right) modules.
+This is obtained by ``forgetting" the $E_{n+1}$-algebra to an $E_1$-algebra then considering the left-modules for this $E_1$-algebra.
+
+The $E_n$-center, or $E_n$-Hochschild cohomology, of an $E_n$-algebra $A$ is the {\em universal} $E_{n+1}$-algebra which acts on $A$. 
+In Section \ref{sec:swiss} below, we will recall an elegant operadic interpretation of this universal picture and interpret it in terms of {\em constructible factorization algebras}. 
+In the case of $E_n$-enveloping algebras, we will provide a strict factorization model of this universal situation in terms of a constructible factorization algebra on an $(n+1)$-dimensional 
+manifold with boundary.
+
+We will furthermore provide an interpretation of this constructible factorization algebra in terms of the quantization of a certain topological field theory. 
+The key insight is that there is a {\em classical limit} of the $E_n$-center $\fZ_n(\fg)$ which is equivalent to the observables of an $(n+1)$-dimensional topological field theory known as {\em BF theory}.
+Likewise, there is a classical limit of $\UU_n(\fg)$ which can be viewed as a boundary condition for BF theory.
+
+In this sense, topological BF theory is the universal $(n+1)$-dimensional field theory which has the $E_n$-enveloping algebra as a boundary condition. 
+This partially confirms the terminology used in \cite{ButsonYoo}  of topological BF theory as the ``universal bulk theory" of $\UU_n(\fg)$.
+
+%Generally speaking, the local observables of a topological field theory on a manifold $M$ define a locally constant factorization algebra on $M$.
 
@@
 \brian{as a corollary butson-yoo}
+\brian{main thrust is to interpret this in terms of the BV / BD formalism}
 
@@
 
-\brian{Review interpretation of the center as a swiss cheese algebra context of Deligne conjecture}
+The operad of little $n$-disks is built from configurations of disjoint unions of $n$-disks inside $n$-dimensional Euclidean space.
+There is a similar operadic picture which encodes $E_{n+1}$-algebras together with their left-modules. 
+The idea is too look at configurations of disks and half-disks inside of the upper-half space $\HH^{n+1} = \{(x_1,\ldots, x_{n+1}) \; | \; x_{n+1} \geq 0\}$. 
+What results is a two-colored operad known as the $(n+1)$-dimensional Swiss cheese operad where the two colors correspond to disks and half-disks.
+
+An algebra over this colored operad can be identified with a pair of objects $(B,M)$ where $B$ is an $E_{n+1}$-algebra and $M$ is a left $B$-module. 
+Indeed, if one restricts to the ``disk" colors we recover the data of $B$. 
+The operadic structure maps which include disks and half-disks embedded inside bigger half-disks encodes the left-module structure of $A$ on $B$.
+
+Given an $E_n$-algebra $A$ we know that $E_n$-center $\fZ_n(A)$ has the structure of an $E_{n+1}$ algebra.
+Moreover, the pair $(\fZ_{n} (A), A)$ can be given the structure of an algebra over the $(n+1)$-dimensional Swiss cheese operad. 
+In fact, $(\fZ_{n} (A), A)$ is the {\em universal} such pair.
+This universality is a conjecture of \cite{Kontsevich} which was later made precise and proved in \cite{Thomas, Tamarkin, Dolgushev, jnkf others?}. 
+One consequence of this \brian{universal property}
+
+Abstractly, an algebra over the $(n+1)$-dimensional Swiss cheese operad can be modeled as a {\em constructible} factorization algebra on the upper half space $\HH^{n+1}$. 
+Concretely, this is the data of (1) a locally constant factorization algebra on the ``bulk" manifold $\RR^n \times \RR_{>0}$, (2) a locally constant factorization algebra on the boundary $\RR^n \times \{0\}$, (3) together with natural \brian{finish}
+
+We have developed locally constant factorization models separately for enveloping $E_n$-algebras and their centers.
+Combining these descriptions we obtain the following.
 
 \begin{prp}
-For any smooth manifold $M$ and Lie algebra $\fg$ the pair $(\bZ_n(\fg), \bU_n (\fg))$ define a constructible factorization algebra on the $(n+1)$-manifold with boundary $M \times [0,1)$.
+For any smooth manifold $M$ and Lie algebra $\fg$ the pair $(\bZ_n(\fg), \bU_n (\fg))$ define a constructible factorization algebra on the $(n+1)$-manifold with boundary $M \times \RR_{\geq 0}$.
+When $M = \RR^n$, this is a model for the algebra $(\fZ_n(\fg), \UU_n(\fg))$ over the $(n+1)$-dimensional Swiss cheese operad.
 \end{prp}
+
+\begin{proof}[Proof sketch]
+In the bulk manifold $M \times \RR_{>0}$ we place the 
+\end{proof}
 

### 2020-09-03 draft.tex
swiss

@@
 
+\subsection{Comments on a generalization}
+
+\owen{I think we can conjecture here the general statement that we almost proved and sketch an approach.}
+
 \section{Background}
@@
 \[
-\cliels(\fg) = (\Sym(\fg[1]), \d = \sum_n \ell_n)
+\cliels(\fg) = \bigg(\Sym(\fg[1]) \; , \; \d = \sum_{n \geq 1} \ell_n\bigg)
 \]
@@
 
-An algebra over this colored operad can be identified with a pair of objects $(B,M)$ where $B$ is an $E_{n+1}$-algebra and $M$ is a left $B$-module. 
+An algebra over this colored operad can be identified with a pair of objects $(B,M)$ where $B$ is an $E_{n+1}$-algebra and $M$ is an $E_n$-algebra in the category of left $B$-modules.
 Indeed, if one restricts to the ``disk" colors we recover the data of $B$. 
@@
 Abstractly, an algebra over the $(n+1)$-dimensional Swiss cheese operad can be modeled as a {\em constructible} factorization algebra on the upper half space $\HH^{n+1}$. 
-Concretely, this is the data of (1) a locally constant factorization algebra on the ``bulk" manifold $\RR^n \times \RR_{>0}$, (2) a locally constant factorization algebra on the boundary $\RR^n \times \{0\}$, (3) together with natural \brian{finish}
-
-We have developed locally constant factorization models separately for enveloping $E_n$-algebras and their centers.
-Combining these descriptions we obtain the following.
-
-\begin{prp}
-For any smooth manifold $M$ and Lie algebra $\fg$ the pair $(\bZ_n(\fg), \bU_n (\fg))$ define a constructible factorization algebra on the $(n+1)$-manifold with boundary $M \times \RR_{\geq 0}$.
-When $M = \RR^n$, this is a model for the algebra $(\fZ_n(\fg), \UU_n(\fg))$ over the $(n+1)$-dimensional Swiss cheese operad.
+Concretely, this is the data of a pair $(\bB, \bM)$ where $\bB$ is a locally constant factorization algebra on the ``bulk" manifold $\RR^n \times \RR_{>0}$ and $\bM$ is a locally constant factorization algebra on the boundary $\RR^n \times \{0\}$.
+
+\begin{prp}[\cite{Lurie, AF}]
+For any smooth manifold $M$ and Lie algebra $\fg$ there exists a constructible factorization algebra on $M \times \RR_{\geq 0}$ which is a model for the algebra $(\fZ_n(\fg), \UU_n(\fg))$ over the $(n+1)$-dimensional Swiss cheese operad.
 \end{prp}
 
-\begin{proof}[Proof sketch]
-In the bulk manifold $M \times \RR_{>0}$ we place the 
-\end{proof}
+%We have developed locally constant factorization models separately for enveloping $E_n$-algebras and their centers.
+%Combining these descriptions we obtain the following.
+%
+%\begin{prp}
+%For any smooth manifold $M$ and Lie algebra $\fg$ the pair $(\bZ_n(\fg), \bU_n (\fg))$ define a constructible factorization algebra on the $(n+1)$-manifold with boundary $M \times \RR_{\geq 0}$.
+%When $M = \RR^n$, this is a model for the algebra $(\fZ_n(\fg), \UU_n(\fg))$ over the $(n+1)$-dimensional Swiss cheese operad.
+%\end{prp}
+%
+%\begin{proof}[Proof sketch]
+%In the bulk manifold $M \times \RR_{>0}$ we place the 
+%\end{proof}
 

### 2020-09-03 draft.tex
small reshuffling

@@
 
-\section{Universal bulk TFT}
-\label{sec: TFT}
+\section{Higher calculus {\it \`a la} Kontsevich and Tamarkin-Tsygan}
+\label{sec: TT}
+
+The $E_n$-center, or $E_n$-Hochschild cohomology, of an $E_n$-algebra $A$ is the {\em universal} $E_{n+1}$-algebra that acts on $A$ {\em qua} $E_n$ algebra.
+
+In Section \ref{sec:swiss} below, we will recall an elegant operadic articulation of this idea and rephrase it in terms of {\em constructible factorization algebras} on a half-space~$\HH^{n+1}$.
+
+\brian{HKR}
+
+Consider the case $n=1$ and $B = U \fg$ where $f$ is simply the identity map. 
+A classic result of \cite{HochSerre} is that the Hochschild cohomology of $U \fg$ can be expressed in terms of Lie algebra cohomology as $\Hoch^*(U\fg,U\fg) \simeq \clies(\fg, U\fg^{ad})$. 
+On the right-hand side, we take the Chevalley--Eilenberg cochain complex with values in the module $U \fg$ equipped with the adjoint action.
+The algebra structure is given by a special case of the convolution product as in Section \ref{??}.
+
+On the other hand, our model for the derived center ${\frak Z}(U(\fg))$ of $U \fg$ is the one-dimensional factorization algebra assigning the cochain complex
+\[
+\clies(\fg \otimes \Omega^*(U), \cliels( \fg \otimes \Omega^*_c(U)))
+\]
+to each open set $U \subset \RR$.
+In the case that $U$ is an interval, this cochain complex is quasi-isomorphic to $\clies (\fg , U\fg^{ad})$.
+Furthermore, one can verify that the resulting $E_1$-algebra structure agrees with the one coming from convolution.
+
+Our model also gives us a simple description of the factorization homology of the derived center along the circle $S^1$.
+\[
+\int_{S^1} {\frak Z}(U(\fg)) \simeq \clies(\fg[\epsilon], \cliels( \fg[\epsilon])),
+\]
+where $\epsilon$ is a formal variable of degree~$1$. 
+\brian{We should compare with Tamarkin-Tsygan's noncommutative calculus (cf. section 2.6).
+We could exhibit Theorem 2.7.1 explicitly in this case for the $E_n$ case with enveloping algebras.}
+
+\subsection{Swiss cheese pairs well with centers}
 
 Given an $E_{n+1}$-algebra one can speak of its $\infty$-category of left (or right) modules.
-This is obtained by ``forgetting" the $E_{n+1}$-algebra to an $E_1$-algebra then considering the left-modules for this $E_1$-algebra.
-
-The $E_n$-center, or $E_n$-Hochschild cohomology, of an $E_n$-algebra $A$ is the {\em universal} $E_{n+1}$-algebra which acts on $A$. 
-In Section \ref{sec:swiss} below, we will recall an elegant operadic interpretation of this universal picture and interpret it in terms of {\em constructible factorization algebras}. 
-In the case of $E_n$-enveloping algebras, we will provide a strict factorization model of this universal situation in terms of a constructible factorization algebra on an $(n+1)$-dimensional 
-manifold with boundary.
-
-We will furthermore provide an interpretation of this constructible factorization algebra in terms of the quantization of a certain topological field theory. 
-The key insight is that there is a {\em classical limit} of the $E_n$-center $\fZ_n(\fg)$ which is equivalent to the observables of an $(n+1)$-dimensional topological field theory known as {\em BF theory}.
-Likewise, there is a classical limit of $\UU_n(\fg)$ which can be viewed as a boundary condition for BF theory.
-
-In this sense, topological BF theory is the universal $(n+1)$-dimensional field theory which has the $E_n$-enveloping algebra as a boundary condition. 
-This partially confirms the terminology used in \cite{ButsonYoo}  of topological BF theory as the ``universal bulk theory" of $\UU_n(\fg)$.
-
-%Generally speaking, the local observables of a topological field theory on a manifold $M$ define a locally constant factorization algebra on $M$.
-
-\brian{or there exists a filtration on the constructible factorization algebra whose associated graded is a commutative P0 constructible factorization algebra or $1$-shifted Poisson.}
-\brian{as a corollary butson-yoo}
-\brian{main thrust is to interpret this in terms of the BV / BD formalism}
-
-\begin{thm}
-Let $M$ be a smooth $n$-manifold and $\fg$ a Lie algebra. 
-There is a constructible factorization algebra on $M \times [0,1)$ satisfying the following properties:
-\begin{itemize}
-\item[(1)] On the $n$-dimensional stratum $M \times \{0\}$ the factorization algebra is equivalent to $\bU_n(\fg)$.
-\item[(2)] On the $(n+1)$-dimensional stratum $M \times (0,1)$, the factorization algebra is a quantization of the observables of topological BF theory based on the Lie algebra $\fg$.
-\item[(3)] Locally on $\RR^n \times [0,1)$ this factorization algebra produces \brian{deligne picture how to say}
-\end{itemize}
-\end{thm}
-
-%Let $\fg$ be a dg Lie algebra and consider the $E_n$ algebra $\UU_n \fg$. 
-%We have shown that a model for the $E_n$-center ${\frak Z}_n (\UU_n \fg) = {\frak Z}_n ({\rm id}_{\UU_n \fg})$ is the $n$-dimensional locally constant factorization algebra 
-%\[
-%\clie \left( \fg \otimes \Omega \; , \; \clieu (\fg \otimes \Omega_c) \right)  .
-%\]
-
-\subsection{A swiss cheese model}
+This $\infty$-category is obtained by ``forgetting" the $E_{n+1}$-algebra to an $E_1$-algebra and then taking the left-modules for this $E_1$-algebra.
 
@@
 %\end{proof}
+
+\section{Universal bulk TFT}
+\label{sec: TFT}
+
+Given an $E_{n+1}$-algebra one can speak of its $\infty$-category of left (or right) modules.
+This is obtained by ``forgetting" the $E_{n+1}$-algebra to an $E_1$-algebra then considering the left-modules for this $E_1$-algebra.
+
+The $E_n$-center, or $E_n$-Hochschild cohomology, of an $E_n$-algebra $A$ is the {\em universal} $E_{n+1}$-algebra which acts on $A$. 
+In Section \ref{sec:swiss} below, we will recall an elegant operadic interpretation of this universal picture and interpret it in terms of {\em constructible factorization algebras}. 
+In the case of $E_n$-enveloping algebras, we will provide a strict factorization model of this universal situation in terms of a constructible factorization algebra on an $(n+1)$-dimensional 
+manifold with boundary.
+
+We will furthermore provide an interpretation of this constructible factorization algebra in terms of the quantization of a certain topological field theory. 
+The key insight is that there is a {\em classical limit} of the $E_n$-center $\fZ_n(\fg)$ which is equivalent to the observables of an $(n+1)$-dimensional topological field theory known as {\em BF theory}.
+Likewise, there is a classical limit of $\UU_n(\fg)$ which can be viewed as a boundary condition for BF theory.
+
+In this sense, topological BF theory is the universal $(n+1)$-dimensional field theory which has the $E_n$-enveloping algebra as a boundary condition. 
+This partially confirms the terminology used in \cite{ButsonYoo}  of topological BF theory as the ``universal bulk theory" of $\UU_n(\fg)$.
+
+%Generally speaking, the local observables of a topological field theory on a manifold $M$ define a locally constant factorization algebra on $M$.
+
+\brian{or there exists a filtration on the constructible factorization algebra whose associated graded is a commutative P0 constructible factorization algebra or $1$-shifted Poisson.}
+\brian{as a corollary butson-yoo}
+\brian{main thrust is to interpret this in terms of the BV / BD formalism}
+
+\begin{thm}
+Let $M$ be a smooth $n$-manifold and $\fg$ a Lie algebra. 
+There is a constructible factorization algebra on $M \times [0,1)$ satisfying the following properties:
+\begin{itemize}
+\item[(1)] On the $n$-dimensional stratum $M \times \{0\}$ the factorization algebra is equivalent to $\bU_n(\fg)$.
+\item[(2)] On the $(n+1)$-dimensional stratum $M \times (0,1)$, the factorization algebra is a quantization of the observables of topological BF theory based on the Lie algebra $\fg$.
+\item[(3)] Locally on $\RR^n \times [0,1)$ this factorization algebra produces \brian{deligne picture how to say}
+\end{itemize}
+\end{thm}
+
+%Let $\fg$ be a dg Lie algebra and consider the $E_n$ algebra $\UU_n \fg$. 
+%We have shown that a model for the $E_n$-center ${\frak Z}_n (\UU_n \fg) = {\frak Z}_n ({\rm id}_{\UU_n \fg})$ is the $n$-dimensional locally constant factorization algebra 
+%\[
+%\clie \left( \fg \otimes \Omega \; , \; \clieu (\fg \otimes \Omega_c) \right)  .
+%\]
 
@@
 
-\subsection{Koszul duality}
-\label{sec: Koszul}
-
-Consider the trivial $E_n$-algebra $k$ and suppose $\varepsilon : \UU_n \fg \to k$ is the natural augmentation. 
-Then, ${\frak Z}_n (\varepsilon)$ is the $E_n$-{\em Koszul dual} of the $E_n$-algebra $\UU_n \fg$. 
-Our results provide a model for this $E_n$-algebra as a locally constant factorization algebra on $\RR^n$ which assigns to an open set $U \subset \RR^n$ the cochain complex
-\[
-\clie \left(\fg \otimes \Omega(U) \right) .
-\]
-
 \subsection{$E_n$-calculus}
-\label{sec: TT}
-
-\brian{HKR}
-
-Consider the case $n=1$ and $B = U \fg$ where $f$ is simply the identity map. 
-A classic result of \cite{HochSerre} is that the Hochschild cohomology of $U \fg$ can be expressed in terms of Lie algebra cohomology as $\Hoch^*(U\fg,U\fg) \simeq \clies(\fg, U\fg^{ad})$. 
-On the right-hand side, we take the Chevalley--Eilenberg cochain complex with values in the module $U \fg$ equipped with the adjoint action.
-The algebra structure is given by a special case of the convolution product as in Section \ref{??}.
-
-On the other hand, our model for the derived center ${\frak Z}(U(\fg))$ of $U \fg$ is the one-dimensional factorization algebra assigning the cochain complex
-\[
-\clies(\fg \otimes \Omega^*(U), \cliels( \fg \otimes \Omega^*_c(U)))
-\]
-to each open set $U \subset \RR$.
-In the case that $U$ is an interval, this cochain complex is quasi-isomorphic to $\clies (\fg , U\fg^{ad})$.
-Furthermore, one can verify that the resulting $E_1$-algebra structure agrees with the one coming from convolution.
-
-Our model also gives us a simple description of the factorization homology of the derived center along the circle $S^1$.
-\[
-\int_{S^1} {\frak Z}(U(\fg)) \simeq \clies(\fg[\epsilon], \cliels( \fg[\epsilon])),
-\]
-where $\epsilon$ is a formal variable of degree~$1$. 
-\brian{We should compare with Tamarkin-Tsygan's noncommutative calculus (cf. section 2.6).
-We could exhibit Theorem 2.7.1 explicitly in this case for the $E_n$ case with enveloping algebras.}
-
 \bibliographystyle{alpha}  

### 2020-09-03 draft.tex
comments twd future

@@
 
-\brian{HKR}
-
-Consider the case $n=1$ and $B = U \fg$ where $f$ is simply the identity map. 
-A classic result of \cite{HochSerre} is that the Hochschild cohomology of $U \fg$ can be expressed in terms of Lie algebra cohomology as $\Hoch^*(U\fg,U\fg) \simeq \clies(\fg, U\fg^{ad})$. 
-On the right-hand side, we take the Chevalley--Eilenberg cochain complex with values in the module $U \fg$ equipped with the adjoint action.
-The algebra structure is given by a special case of the convolution product as in Section \ref{??}.
-
-On the other hand, our model for the derived center ${\frak Z}(U(\fg))$ of $U \fg$ is the one-dimensional factorization algebra assigning the cochain complex
-\[
-\clies(\fg \otimes \Omega^*(U), \cliels( \fg \otimes \Omega^*_c(U)))
-\]
-to each open set $U \subset \RR$.
-In the case that $U$ is an interval, this cochain complex is quasi-isomorphic to $\clies (\fg , U\fg^{ad})$.
-Furthermore, one can verify that the resulting $E_1$-algebra structure agrees with the one coming from convolution.
-
-Our model also gives us a simple description of the factorization homology of the derived center along the circle $S^1$.
-\[
-\int_{S^1} {\frak Z}(U(\fg)) \simeq \clies(\fg[\epsilon], \cliels( \fg[\epsilon])),
-\]
-where $\epsilon$ is a formal variable of degree~$1$. 
-\brian{We should compare with Tamarkin-Tsygan's noncommutative calculus (cf. section 2.6).
-We could exhibit Theorem 2.7.1 explicitly in this case for the $E_n$ case with enveloping algebras.}
+%
+%\brian{HKR}
+%
+%Consider the case $n=1$ and $B = U \fg$ where $f$ is simply the identity map. 
+%A classic result of \cite{HochSerre} is that the Hochschild cohomology of $U \fg$ can be expressed in terms of Lie algebra cohomology as $\Hoch^*(U\fg,U\fg) \simeq \clies(\fg, U\fg^{ad})$. 
+%On the right-hand side, we take the Chevalley--Eilenberg cochain complex with values in the module $U \fg$ equipped with the adjoint action.
+%The algebra structure is given by a special case of the convolution product as in Section \ref{??}. 
+%
+%On the other hand, our model for the derived center ${\frak Z}(U(\fg))$ of $U \fg$ is the one-dimensional factorization algebra assigning the cochain complex
+%\[
+%\clies(\fg \otimes \Omega^*(U), \cliels( \fg \otimes \Omega^*_c(U)))
+%\]
+%to each open set $U \subset \RR$.
+%In the case that $U$ is an interval, this cochain complex is quasi-isomorphic to $\clies (\fg , U\fg^{ad})$.
+%Furthermore, one can verify that the resulting $E_1$-algebra structure agrees with the one coming from convolution. 
+%
+%Our model also gives us a simple description of the factorization homology of the derived center along the circle $S^1$.
+%\[
+%\int_{S^1} {\frak Z}(U(\fg)) \simeq \clies(\fg[\epsilon], \cliels( \fg[\epsilon])),
+%\]
+%where $\epsilon$ is a formal variable of degree~$1$. 
+%\brian{We should compare with Tamarkin-Tsygan's noncommutative calculus (cf. section 2.6).
+%We could exhibit Theorem 2.7.1 explicitly in this case for the $E_n$ case with enveloping algebras.}
 
@@
 
+\subsection{How factorization homology intertwines with taking the center}
+
+\owen{Explain why there is a canonical map from the fact hlgy of a center to the center of the fact hlgy}
+
+\begin{prp}
+For any $L_\infty$ algebra $\fg$ and any closed $(n-k)$-dimensional manifold $S$,
+the canonical map of $E_k$-algebras
+\[
+\int_{S} \fZ_n(\fg) \to \fZ_k \left( \int_S \UU_n \fg \right)
+\]
+is a weak equivalence.
+\end{prp}
+
+As a slogan, we say ``factorization homology commutes with taking centers,'' 
+at least for enveloping $E_n$ algebras.
+It is natural to ask whether this result holds in general.
+
+\begin{qtn}
+Is the canonical map always a weak equivalence?
+\end{qtn}
+
+\owen{We should see if that's what Tamarkin-Tsygan prove for  $E_1$ algebras, as it would be further evidence.}
+
+\owen{Then ask what is the factorization homology on a compact manifold with boundary, which leads into next section.}
+
 \section{Universal bulk TFT}
@@
 This partially confirms the terminology used in \cite{ButsonYoo}  of topological BF theory as the ``universal bulk theory" of $\UU_n(\fg)$.
+
+\owen{Somewhere please mention that the slogan ``quantization commutes with pushforward'' holds for this class of theories.}
 
@@
 
-\section{Examples}
+\section{Examples?}
 

### 2020-09-04 draft.tex
sketch of argument about calculus

@@
 
-\owen{Explain why there is a canonical map from the fact hlgy of a center to the center of the fact hlgy}
+A natural question in our setting is what happens to our pair $(\bZ_n(\fg), \bU_n \fg)$ when we take factorization homology.
+As we will see below, the behavior is optimal.
+
+Let us start with a discussion of the general situation.
+Let $(A,B)$ be a Swiss cheese pair: $A$ is an $E_1$ algebra in $E_n$ algebras and $B$ is an $E_n$ algebra in left $A$-modules. 
+We will freely view these as locally constant factorization algebras on framed $n$-manifolds.
+Observe that since factorization homology is a symmetric monoidal functor, 
+it is immediate that $\int_S B$ is a left module over $\int_S A$.
+Indeed, for any $(n-k)$-dimensional framed manifold $S$, 
+taking factorization homology $\int_S B$ yields a locally constant factorization algebra on $\RR^k$ 
+and this factorization structure is compatible with the left action of $\int_S A$ as a locally constant factorization algebra on $\RR^k$.
+The universal property of the center implies there is then a canonical map
+\[
+\int_{S} A \to \fZ_k \left( \int_S B \right).
+\]
+In particular, when $A = \fZ(B)$, we have
+\begin{equation}
+\label{eqn: can cen int}
+\int_{S} \fZ(B) \to \fZ_k \left( \int_S B \right),
+\end{equation}
+so that taking centers intertwines with taking factorization homology.
+In our favorite case, this relationship is as nice as possible.
 
 \begin{prp}
+\label{prp: z commutes with int}
 For any $L_\infty$ algebra $\fg$ and any closed $(n-k)$-dimensional manifold $S$,
@@
 \begin{qtn}
-Is the canonical map always a weak equivalence?
+Is the canonical map \eqref{eqn: can cen int} always a weak equivalence?
 \end{qtn}
@@
 \owen{We should see if that's what Tamarkin-Tsygan prove for  $E_1$ algebras, as it would be further evidence.}
+
+\begin{proof}[Proof of Proposition~\ref{prp: z commutes with int}]
+The key fact is a simple consequence of the K\"unneth theorem in the setting of de Rham forms.
+Let $S$ be the closed $n-k$-dimensional manifold of the proposition,
+and let $V$ be an arbitrary manifold without boundary.
+Then there is a canonical map
+\[
+\Omega^*(V) \otimes \Omega^*(S) \to \Omega^*(V \times S),
+\]
+by wedge product after pulling back along the two projection maps.
+It is a quasi-isomorphism, by K\"unneth.
+Similarly, the canonical map
+\[
+\Omega_c^*(V) \otimes \Omega^*(S) \to \Omega_c^*(V \times S),
+\]
+is a quasi-isomorphism, as $S$ is compact.
+
+Let $\fg_S$ denote the $L_\infty$ algebra $\Omega^*(S) \otimes \fg$. 
+Then these quasi-isomorphisms above imply there are quasi-isomorphisms of $L_\infty$ algebras
+\begin{align*}
+\Omega^*(V) \otimes \fg_S &\xto{\simeq} \Omega^*(V \times S) \otimes \fg \\
+\Omega_c^*(V) \otimes \fg_S &\xto{\simeq} \Omega_c^*(V \times S) \otimes \fg 
+\end{align*}
+and hence a quasi-isomorphism
+\[
+\bU_k \fg_S \xto{\simeq} \int_S \bU_n \fg
+\]
+of factorization algebras.
+
+Likewise, on each open set $V \subset \RR^k$, 
+we obtain a quasi-isomorphism
+\[
+\bZ_k(\fg_S)(V) \cong \clies( \Omega^*(V) \otimes \fg_S, \bU_k \fg_S) \xto{\simeq} \clies(\Omega^*(V \times S) \otimes \fg, \bU_n(V \times S))
+\]
+and this map is functorial in opens.
+The righthand side is, however, the pushforward $\int_S \bZ_n \fg$.
+\owen{Hmmm, that map goes the wrong way, but I'm pretty sure it provides the inverse-up-to-qiso we need.}
+\end{proof}
 

### 2020-09-04 draft.tex
AKSZ

@@
 \begin{qtn}
-Is the canonical map \eqref{eqn: can cen int} always a weak equivalence?
+Is the canonical map \eqref{eqn: can cen int} a weak equivalence when $\UU_n \fg$ is replaced by an arbitrary $E_n$-algebra?
 \end{qtn}
@@
 \label{sec: TFT}
-
-Given an $E_{n+1}$-algebra one can speak of its $\infty$-category of left (or right) modules.
-This is obtained by ``forgetting" the $E_{n+1}$-algebra to an $E_1$-algebra then considering the left-modules for this $E_1$-algebra.
-
-The $E_n$-center, or $E_n$-Hochschild cohomology, of an $E_n$-algebra $A$ is the {\em universal} $E_{n+1}$-algebra which acts on $A$. 
-In Section \ref{sec:swiss} below, we will recall an elegant operadic interpretation of this universal picture and interpret it in terms of {\em constructible factorization algebras}. 
-In the case of $E_n$-enveloping algebras, we will provide a strict factorization model of this universal situation in terms of a constructible factorization algebra on an $(n+1)$-dimensional 
-manifold with boundary.
-
-We will furthermore provide an interpretation of this constructible factorization algebra in terms of the quantization of a certain topological field theory. 
-The key insight is that there is a {\em classical limit} of the $E_n$-center $\fZ_n(\fg)$ which is equivalent to the observables of an $(n+1)$-dimensional topological field theory known as {\em BF theory}.
-Likewise, there is a classical limit of $\UU_n(\fg)$ which can be viewed as a boundary condition for BF theory.
-
-In this sense, topological BF theory is the universal $(n+1)$-dimensional field theory which has the $E_n$-enveloping algebra as a boundary condition. 
-This partially confirms the terminology used in \cite{ButsonYoo}  of topological BF theory as the ``universal bulk theory" of $\UU_n(\fg)$.
+%
+%Given an $E_{n+1}$-algebra one can speak of its $\infty$-category of left (or right) modules.
+%This is obtained by ``forgetting" the $E_{n+1}$-algebra to an $E_1$-algebra then considering the left-modules for this $E_1$-algebra.
+%
+%The $E_n$-center, or $E_n$-Hochschild cohomology, of an $E_n$-algebra $A$ is the {\em universal} $E_{n+1}$-algebra which acts on $A$. 
+%In Section \ref{sec:swiss} below, we will recall an elegant operadic interpretation of this universal picture and interpret it in terms of {\em constructible factorization algebras}. 
+%In the case of $E_n$-enveloping algebras, we will provide a strict factorization model of this universal situation in terms of a constructible factorization algebra on an $(n+1)$-dimensional 
+%manifold with boundary. 
+%
+%We will furthermore provide an interpretation of this constructible factorization algebra in terms of the quantization of a certain topological field theory. 
+%The key insight is that there is a {\em classical limit} of the $E_n$-center $\fZ_n(\fg)$ which is equivalent to the observables of an $(n+1)$-dimensional topological field theory known as {\em BF theory}.
+%Likewise, there is a classical limit of $\UU_n(\fg)$ which can be viewed as a boundary condition for BF theory.
+%
+%In this sense, topological BF theory is the universal $(n+1)$-dimensional field theory which has the $E_n$-enveloping algebra as a boundary condition. 
+%This partially confirms the terminology used in \cite{ButsonYoo}  of topological BF theory as the ``universal bulk theory" of $\UU_n(\fg)$.
+
+In this section, we turn to an interpretation of the $E_n$-center of an $E_n$-enveloping algebra in terms of a certain topological field theory (TFT).
 
@@
 
+Abstractly, we know that any algebra over the Swiss cheese operad can be modeled as a constructible factorization algebra on a manifold with boundary. 
+One drawback of the previous section is that we did not provide a model for the $E_n$-center of an enveloping algebra as a constructible factorization algebra on an $(n+1)$-dimensional manifold with boundary.
+There is, however, a certain ``dequantization" of the $E_n$-center that we do have an explicit description of.
+
+The key insight is that there exists a filtration on our model for the $E_n$-center $\bZ_n(\fg)$ and the $E_n$-enveloping algebra $\bU_n (\fg)$ whose associated graded factorization algebras ${\rm Gr} \; \bZ_n(\fg)$ and ${\rm Gr} \; \bU_n(\fg)$ are {\em commutative} factorization algebras.
+
+Our first main result is the following.
+
 %Generally speaking, the local observables of a topological field theory on a manifold $M$ define a locally constant factorization algebra on $M$.
 
-\brian{or there exists a filtration on the constructible factorization algebra whose associated graded is a commutative P0 constructible factorization algebra or $1$-shifted Poisson.}
+\begin{prp}
+Let $M$ be a smooth $n$-dimensional manifold and $\fg$ a Lie algebra. 
+There is a constructible $\PP_0$-factorization algebra 
+\begin{equation}\label{eqn:graded}
+\left(\Tilde{\bZ}_n (\fg) \; , \; {\rm Gr} \; \bU_n(\fg) \right)
+\end{equation}
+on $M \times \RR_{\geq 0}$ such that $\pi_* \Tilde{\bZ}_n (\fg)$ is equivalent to ${\rm Gr} \; \bZ_n(\fg)$ as commutative factorization algebras on $M$ where $\pi : M \times \RR_{\geq 0} \to M$ is the projection.
+\end{prp}
+
+A $\PP_0$, or $1$-shifted Poisson, algebra is a commutative dg algebra equipped with a bracket of cohomological degree $+1$ that satisfies a graded version of the Jacobi identity and is a biderivation with respect to the commutative product \brian{reference}.
+Likewise, a $\PP_0$-factorization algebra is a factorization algebra whose value on each open set is $\PP_0$-algebra.
+
+The Batalin--Vilkovisky (BV) formalism for studying quantum field theory \brian{finish}
+
+Following the proof of this proposition, our main thrust is to interpret this result in the BV formalism by exhibiting a topological field theory on the $(n+1)$-dimensional manifold with boundary $M \times \RR_{\geq 0}$ whose factorization algebra of classical observables is precisely the constructible factorization algebra in (\ref{eqn:graded}).
+
 \brian{as a corollary butson-yoo}
-\brian{main thrust is to interpret this in terms of the BV / BD formalism}
-
-\begin{thm}
-Let $M$ be a smooth $n$-manifold and $\fg$ a Lie algebra. 
-There is a constructible factorization algebra on $M \times [0,1)$ satisfying the following properties:
-\begin{itemize}
-\item[(1)] On the $n$-dimensional stratum $M \times \{0\}$ the factorization algebra is equivalent to $\bU_n(\fg)$.
-\item[(2)] On the $(n+1)$-dimensional stratum $M \times (0,1)$, the factorization algebra is a quantization of the observables of topological BF theory based on the Lie algebra $\fg$.
-\item[(3)] Locally on $\RR^n \times [0,1)$ this factorization algebra produces \brian{deligne picture how to say}
-\end{itemize}
-\end{thm}
+
+%\begin{thm}
+%Let $M$ be a smooth $n$-manifold and $\fg$ a Lie algebra. 
+%There is a constructible factorization algebra on $M \times [0,1)$ satisfying the following properties:
+%\begin{itemize}
+%\item[(1)] On the $n$-dimensional stratum $M \times \{0\}$ the factorization algebra is equivalent to $\bU_n(\fg)$.
+%\item[(2)] On the $(n+1)$-dimensional stratum $M \times (0,1)$, the factorization algebra is a quantization of the observables of topological BF theory based on the Lie algebra $\fg$.
+%\item[(3)] Locally on $\RR^n \times [0,1)$ this factorization algebra produces \brian{deligne picture how to say}
+%\end{itemize}
+%\end{thm}
 
@@
 
-\subsection{The bulk TFT}
-
-Let us place the locally constant factorization algebra model of the $E_n$-enveloping algebra $\bU_n (\fg) = \clieu(\fg \otimes \Omega_c)$ on the $n$-manifold $M$.
-This factorization algebra is equivalent to the pushforward of a factorization algebra $\Obs_{\rm BF}$ on the $(n+1)$-dimensional manifold $M \times \RR$ along the projection $\pi : M \times (0,1) \to M$ which we proceed to construct.
+\subsection{The bulk factorization algebra}
+
+Let $M$ be an $n$-dimensional manifold and $\fg$ a Lie algebra.
 
 \begin{dfn}
-For an open set $V \subset M \times (0,1)$ let $\Obs^{\rm cl}_{\rm BF} (V)$ be the cochain complex 
-\[
-\Obs^{\rm cl}_{\rm BF} (V) = \clie \bigg(\fg \otimes \Omega (V) \; , \; \Sym \left(\fg \otimes \Omega_c(V) [2] \right) \bigg) .
-\]
-The assignment $V \mapsto \Obs^{\rm cl}_{\rm BF}(V)$ defines a locally constant factorization algebra on $M \times (0,1)$. 
+For an open set $U \subset M \times \RR_{>0}$ let $\Tilde{\bZ}_n(\fg) (U)$ be the cochain complex 
+\[
+\Tilde{\bZ}_n(\fg) (U) = \clie \bigg(\fg \otimes \Omega (U) \; , \; \Sym \left(\fg \otimes \Omega_c(U) [2] \right) \bigg) .
+\]
+The assignment $\Tilde{\bZ}_n(\fg) (U)$ defines a locally constant factorization algebra on $M \times \RR_{>0}$. 
 \end{dfn}
 
-We note that $\Obs_{\rm BF}^{\rm cl}$ is a factorization algebra with values in commutative dg algebras. 
-In fact, it is given by the ``classical observables" of a topological field theory on $M \times (0,1)$ known as ``topological BF theory".
-
-We now consider the pushforward factorization algebra $\pi_* \Obs^{\rm cl}_{\rm BF}$ on $M$.
-Locally, on disks, we will see that it is quasi-isomorphic to a certain limit, or ``dequantization", of our model for the $E_n$-center of $\UU_n \fg$.
-Recall, this model is given by the factorization algebra on $M$:
-\begin{equation}\label{eqn:centerTFT}
-\bZ_n(\fg) = \clie\left(\fg \otimes \Omega \, , \, \clieu (\fg \otimes \Omega_c) \right) .
-\end{equation}
-
-The ``dequantization" is defined using the following filtration of this model.
-For any Lie algebra $\fh$, let $\clieu_{\leq k} (\fh)$ be the subcomplex of Chevalley--Eilenberg chains which is $\Sym^{\leq k} (\fh[1])$ as an underlying graded vector space.
-
-\begin{dfn}
-Introduce the filtration on the factorization algebra on $M$ in (\ref{eqn:centerTFT}) by 
+On each open set $U$, the cochain complex $\Tilde{\bZ}_n(\fg) (U)$ is actually a commutative dg algebra. 
+In fact, it has the structure of a $\PP_0$-algebra where the $1$-shifted bracket $\{\cdot, \cdot\}$ is defined as follows.
+
+\begin{prp}
+$\Tilde{\bZ}_n(\fg)$ has the structure of a $\PP_0$-factorization algebra on $M \times \RR_{>0}$. 
+\end{prp}
+\begin{proof}
+Note that as an underlying graded vector space $\Tilde{\bZ}_n(\fg) (U)$ is of the form
+\[
+{\rm Sym} \left(\fg^* \otimes \Bar{\Omega}_c (U) [n-1] \right) \; \Hat{\otimes} \; {\rm Sym}  \left(\fg \otimes \Omega_c(U) [2] \right)  .
+\]
+Let $x^* \otimes \alpha$ denote an element of $\fg \otimes \Bar{\Omega}_c (U)$ and $y \otimes \beta$ denote an element of $\fg \otimes \Omega_c(U) [2]$. 
+Then, the bracket involving the linear elements $(x^* \otimes \alpha) \otimes 1$ and $1 \otimes (y \otimes \beta)$ is defined by
+\begin{align*}
+\{(x^* \otimes \alpha) \otimes 1 , 1 \otimes (y \otimes \beta)\} & = \<x^*, y\>_\fg \int_U \alpha \beta \\
+\{(x^* \otimes \alpha) \otimes 1 , (x'^* \otimes \alpha') \otimes 1\} & = 0 \\
+\{1 \otimes (y \otimes \beta) , 1 \otimes (y' \otimes \beta')\} & = 0 . 
+\end{align*}
+Here, $\<x^*, y\>_\fg$ denotes the linear pairing between $\fg$ and $\fg^*$ and $\int_U\alpha \beta$ denotes the linear pairing between compactly supported distributional differential forms and differential forms.
+The bracket is extended to the entire symmetric algebra by using the graded Leibniz rule.
+\end{proof}
+
+\subsection{The ``classical limit"}
+
+For any dg Lie (in fact, $L_\infty$) algebra, the Chevalley--Eilenberg cochain complex computing Lie algebra homology admits a natural filtration whose associated graded has the structure of a commutative dg algebra.
+If $\fh$ is a dg Lie algebra, let $\clieu_{\leq k} (\fh)$ be the subcomplex of Chevalley--Eilenberg chains which is $\Sym^{\leq k} (\fh[1])$ as an underlying graded vector space. 
+The associated graded is the free symmetric algebra on $\fh[1]$ thought of as simply a cochain complex:
+\[
+{\rm Gr} \; \clieu (\fh) = {\rm Sym} (\fh [1])  .
+\]
+Here, the differential on the right-hand side is simply the underlying linear differential of $\fh$ (in terms of $L_\infty$ algebras, this is the $1$-ary operation $\ell_1$).
+
+The Lie bracket on $\fh$ endows ${\rm Sym} (\fh [1])$ with the additional structure of a $\PP_0$-algebra. 
+On linear elements this is simply the Lie bracket on $\fh$, and one extends to the full symmetric algebra by the graded Leibniz rule.
+
+Consider our factorization model for the $E_n$-enveloping algebra $\bU_n(\fg) = \clieu (\fg \otimes \Omega_c)$. 
+The filtration on Chevalley--Eilenberg chains equips $\bU_n(\fg)$ with a filtration as a factorization algebra. 
+Furthermore, the resulting associated graded ${\rm Gr} \; \bU_n (\fg)$ has the natural structure of a $\PP_0$-factorization algebra.
+
+There is a similar filtration on our model for the $E_n$-center $\bZ_n(\fg)$. 
+Define
 \[
@@
 \]
-\end{dfn}
-
-This is a filtration of factorization algebras on $M$. 
-The associated graded factorization algebra is
-\[
-{\rm Gr} \; \bZ_n(\fg) \; = \; \clie \bigg(\fg \otimes \Omega \; , \; \Sym \left(\fg \otimes \Omega_c [1] \right) \bigg) .
-\]
-Notice this is similar to the model $E_n$-center except we have turned off the Chevalley--Eilenberg differential on chains.
+It is immediate to check that this is a filtration of factorization algebras and that its associated graded has the structure of a $\PP_0$-factorization algebra.
+In fact, we have the following result, which explains the relationship to the ``bulk" $(n+1)$-dimensional factorization algebra $\Tilde{\bZ}_n(\fg)$ we introduced in the last section.
 
  \begin{lmm}
-There is a quasi-isomorphism of commutative factorization algebras on $M$:
-\[
-\pi_* \Obs^{\rm cl}_{\rm BF} \; \xto{\simeq} \; {\rm Gr} \; \bZ_n(\fg) .
-\]
+Let $M$ be an $n$-dimensional manifold.
+There is a quasi-isomorphism of  $\PP_0$-factorization algebras on $M$:
+\[
+\pi_* \Tilde{\bZ}_n(\fg) \; \xto{\simeq} \; {\rm Gr} \; \bZ_n(\fg) .
+\]
+where $\pi : M \times \RR_{>0} \to M$ is the projection. 
 \end{lmm}
@@
 \end{proof}
+
+Since the universal action of $\bZ_n(\fg)$ on $\bU_n (\fg)$ is compatible with the above filtrations, we obtain the following constructible factorization algebra on $M \times \RR_{\geq 0}$.
+
+\begin{dfn}\label{dfn:constructible1}
+Let $(\Tilde{\bZ}_n (\fg), {\rm Gr} \bU_n(\fg))$ be the following constructible $\PP_0$-factorization algebra on $M \times \RR_{\geq 0}$:
+\begin{itemize}
+\item to an open set $U \subset M \times \RR_{> 0}$, we assign the cochain complex $\Tilde{\bZ}_n (\fg)(U)$.
+\item to an open set $U \subset M \times \RR_{\geq 0}$ with $U \cap (M \times \{0\}) \ne 0$ we assign the cochain complex ${\rm Gr} \;\bU_n(\fg)(U)$. 
+\end{itemize}
+\brian{not sure how much to say about structure maps}
+\end{dfn}
+
+\subsection{Bulk-boundary topological field theory}
+
+It is the central theme of \cite{CG1, CG2} that the observables of a perturbative quantum field theory define the structure of a factorization algebra. 
+In this setup, one first uses the Batalin--Vilkovisky (BV) formalism to define a perturbative classical field theory. 
+The key ingredient in this formalism is a $(-1)$-shifted symplectic structure on the classical space of fields. 
+The observables, or functions on the classical space of fields is then equipped with the structure of a $\PP_0$-factorization algebra.
+
+More recently in \cite{ButsonYoo} and \cite{Eugene}, it is shown how to run the classical BV formalism on manifolds with boundary. 
+Let $N$ be such a manifold with boundary and let $\cE$ denote the space of fields, typically given as the space of sections of a finite rank vector bundle on $N$. 
+The definition of a classical BV theory on $N$ amounts to prescribing the following data:
+\begin{itemize}
+\item[(1)]
+an ordinary classical BV theory on the interior $N \setminus \partial N$ whose space of fields is $\cE|_{N \setminus \partial N}$;
+\item[(2)] 
+a compatible $0$-shifted symplectic structure on $\cE|_{\partial N}$ equipped with a Lagrangian subspace $\cL \subset \cE|_{\partial N}$.
+This is called a {\em boundary condition}.
+\end{itemize}
+From this data at the level of fields, one obtains a constructible $\PP_0$-factorization algebra on the manifold with boundary $N$ at the level of the observables.
+
+For any Lie algebra $\fg$, there is a topological field theory defined in any dimension known as ``topological BF theory". 
+Suppose $N$ is an $(n+1)$-dimensional manifold, which for now we assume has no boundary $\partial N = \emptyset$. 
+In the BV formalism, the perturbative space of fields of BF theory on $N$ consists of
+\[
+(A, B) \in \Omega^{\bu} (N) \otimes \fg [1] \oplus \Omega^{\bu} (N) \otimes \fg^* [n-1] .
+\]
+When $N$ is compact, the classical moduli space underlying this field theory has an elegant description in terms of the AKSZ formalism. 
+It can be interpreted as the following mapping stack 
+\begin{equation} \label{stack1}
+{\rm Map}(N_{\rm dR} ,  {\rm T}^*[n] {\rm B} G)
+\end{equation}
+where $N_{\rm dR}$ denotes the de Rham stack of $N$ and where $G$ is a Lie group whose Lie algebra is $\fg$. 
+Perturbative BF theory is obtained by taking the tangent space of the above mapping stack near at the trivial $G$-bundle.
+Concretely, the classical moduli space consists of pairs $(A, B)$ where $A \in \Omega^1 (N) \otimes \fg$ and $B \in \Omega^{n-1} (N) \otimes \fg^*$ satisfying the equations
+\begin{align*}
+\d A + \frac12 [A,A] & = 0 \\
+\d_A B + [A,B] & = 0 .
+\end{align*}
+
+Now, suppose $N$ has a boundary $\partial N \ne 0$.
+Then, (\ref{stack1}) no longer admits a $(-1)$-shifted symplectic structure. 
+However, the AKSZ construction equips 
+\[
+{\rm Map}(\partial N , {\rm T}^* [n] {\rm B} G)
+\]
+with a $0$-shifted symplectic structure. 
+Perturbatively, this mapping stack represents the restriction of the fields to the boundary.
+
+For BF theory, there is a natural choice of a Lagrangian for this boundary condition. 
+In terms of mapping stacks, it is given by considering maps from $N_{\rm dR}$ into the $n$-shifted conormal bundle of ${\rm B} G$:
+\[
+{\rm Map}(N_{\rm dR} , {\rm N}^*_e [n] {\rm B}G) .
+\]
+Then, by abstract maneuvers \brian{reference} the following fiber product
+\[
+\begin{tikzcd}
+X \ar[r] \ar[d] & {\rm Map} (N , {\rm T}^* [n] {\rm B} G) \ar[d] \\
+{\rm Map}(\partial N_{\rm dR} , {\rm N}^*_e  [n] {\rm B}G) \ar[r] & {\rm Map}(\partial N_{\rm dR} , {\rm T}^*[n]  {\rm B}G)
+\end{tikzcd}
+\]
+is equipped with a $(-1)$-shifted symplectic structure. 
+Heuristically, the classical observables are given by functions on the $(-1)$-shifted symplectic space $X$.
+
+Perturbatively, we follow \cite{ButsonYoo} and \cite{Eugene} to make the following definition within the BV formalism.
+
+\begin{dfn}
+Let $M$ be an $n$-dimensional manifold.
+{\em Topological BF theory with its universal Neumann boundary condition} is the classical bulk-boundary theory on $M \times \RR_{\geq 0}$ described as follows:
+\begin{itemize}
+\item[(1)] 
+The bulk theory is that of topological BF theory on $M \times \RR_{>0}$, where the space of fields is 
+\[
+\cE|_{M \times \RR_{>0}} = \Omega^{\bu} (M \times \RR_{>0}) \otimes \fg [1] \oplus \Omega^{\bu} (M \times \RR_{>0}) \otimes \fg^* [n-2] .
+\]
+\item[(2)] 
+The boundary condition is determined by the subspace of the fields on the boundary
+\[
+\Omega^{\bu} (M) \otimes \fg^* [n-2] \subset \cE|_{M \times \{0\}} .
+\]
+\end{itemize}
+\end{dfn}
+
+We obtain the following by a direct unpacking of the setup in \cite{Eugene}.
+
+\begin{prp}
+The constructible $\PP_0$-factorization algebra of topological BF theory with its universal Neumann boundary condition is equivalent to the constructible factorization algebra $(\Tilde{\bZ}_n (\fg), {\rm Gr} \bU_n (\fg))$ of Definition \ref{dfn:constructible1}.
+\end{prp}
+%\subsection{The bulk TFT}
+%
+%Let us place the locally constant factorization algebra model of the $E_n$-enveloping algebra $\bU_n (\fg) = \clieu(\fg \otimes \Omega_c)$ on the $n$-manifold $M$.
+%This factorization algebra is equivalent to the pushforward of a factorization algebra $\Obs_{\rm BF}$ on the $(n+1)$-dimensional manifold $M \times \RR$ along the projection $\pi : M \times (0,1) \to M$ which we proceed to construct.
+%
+%\begin{dfn}
+%For an open set $V \subset M \times (0,1)$ let $\Obs^{\rm cl}_{\rm BF} (V)$ be the cochain complex 
+%\[
+%\Obs^{\rm cl}_{\rm BF} (V) = \clie \bigg(\fg \otimes \Omega (V) \; , \; \Sym \left(\fg \otimes \Omega_c(V) [2] \right) \bigg) .
+%\]
+%The assignment $V \mapsto \Obs^{\rm cl}_{\rm BF}(V)$ defines a locally constant factorization algebra on $M \times (0,1)$. 
+%\end{dfn}
+%
+%We note that $\Obs_{\rm BF}^{\rm cl}$ is a factorization algebra with values in commutative dg algebras. 
+%In fact, it is given by the ``classical observables" of a topological field theory on $M \times (0,1)$ known as ``topological BF theory". 
+%
+%We now consider the pushforward factorization algebra $\pi_* \Obs^{\rm cl}_{\rm BF}$ on $M$.
+%Locally, on disks, we will see that it is quasi-isomorphic to a certain limit, or ``dequantization", of our model for the $E_n$-center of $\UU_n \fg$.
+%Recall, this model is given by the factorization algebra on $M$:
+%\begin{equation}\label{eqn:centerTFT}
+%\bZ_n(\fg) = \clie\left(\fg \otimes \Omega \, , \, \clieu (\fg \otimes \Omega_c) \right) .
+%\end{equation}
+%
+%The ``dequantization" is defined using the following filtration of this model.
+%For any Lie algebra $\fh$, let $\clieu_{\leq k} (\fh)$ be the subcomplex of Chevalley--Eilenberg chains which is $\Sym^{\leq k} (\fh[1])$ as an underlying graded vector space. 
+%
+%\begin{dfn}
+%Introduce the filtration on the factorization algebra on $M$ in (\ref{eqn:centerTFT}) by 
+%\[
+%F^k \bZ_n(\fg) = \clie \bigg(\fg \otimes \Omega \; , \; \clieu_{\leq k} (\fg \otimes \Omega_c) \bigg) .
+%\]
+%\end{dfn}
+%
+%This is a filtration of factorization algebras on $M$. 
+%The associated graded factorization algebra is
+%\[
+%{\rm Gr} \; \bZ_n(\fg) \; = \; \clie \bigg(\fg \otimes \Omega \; , \; \Sym \left(\fg \otimes \Omega_c [1] \right) \bigg) .
+%\]
+%Notice this is similar to the model $E_n$-center except we have turned off the Chevalley--Eilenberg differential on chains. 
+%
+% \begin{lmm}
+%There is a quasi-isomorphism of commutative factorization algebras on $M$:
+%\[
+%\pi_* \Obs^{\rm cl}_{\rm BF} \; \xto{\simeq} \; {\rm Gr} \; \bZ_n(\fg) .
+%\]
+%\end{lmm}
+%
+%In fact, we will show that this quasi-isomorphism is a deformation retraction. 
+%
+%\begin{proof}
+%To exhibit this quasi-isomorphism, we introduce the following cochain maps.
+%For an open set $U \subset M$ let
+%\[
+%\int_\RR : \Omega_c(U \times \RR) \to \Omega_c (U) [1] 
+%\] 
+%be the map which integrates a compactly supported form on $U \times \RR$ along $\RR$. 
+%This map is a quasi-isomorphism for any $U $ and admits the following explicit retract. 
+%Let $\phi$ be a fixed compactly supported function on $\RR$ of mass $1$ and define
+%\[
+%r_\phi : \Omega_c(U) [1] \to \Omega_c (U \times \RR)
+%\]
+%by $r_\phi (\alpha) = \alpha \wedge \phi \, \d t$. 
+%\end{proof}
 

### 2020-09-06 draft.tex
partway through section 4

@@
 
-Our approach here relies on a concrete and convenient model for these enveloping $E_n$ algebras by factorization algebras.
-In particular, thanks to Knudsen \cite{Knudsen}, 
+Many notions from ordinary algebra admit natural generalizations to $E_n$ algebras.
+For instance, to each Lie algebra $\fg$ (and more generally $L_\infty$ algebra),
+there is an {\em enveloping $E_n$ algebra} $\UU_n \fg$, thanks to \cite{Knudsen}.
+Similarly, every $E_n$ algebra $A$ has a {\em center} ${\frak Z}_n(A)$, which is an $E_{n+1}$ algebra and hence more commutative than~$A$.
+More generally, for any map of $E_n$ algebras $f: A \to B$, there is a {\em centralizer} ${\frak Z}_n(f)$, 
+which is a generalization of the commutant.
+We review these notions more fully in Section~\ref{sec: background}.
+
+Our work here relies on a concrete and convenient model for these enveloping $E_n$ algebras by factorization algebras.
+In particular, thanks again to \cite{Knudsen}, 
 we know that the $E_n$ enveloping algebra $\UU_n \fg$ admits a model $\bU_n \fg$ whose underlying functor on the poset of open sets in $\RR^n$ assigns $\cliels(\Omega_c^*(V) \otimes \fg)$ to each open set~$V$.
@@
 between their enveloping $E_n$ algebras.
-The centralizer of this map ${\frak Z}_{E_n}(\UU_n f)$ is an $E_n$-algebra modeled by the factorization algebra 
+The centralizer of this map ${\frak Z}_n(\UU_n f)$ is an $E_n$-algebra modeled by the factorization algebra 
 \[
@@
 \item Knudsen verifies that we can model the enveloping $E_n$ algebra by the factorization algebra $\bU_n \fg$ described earlier.
-\item Lurie and Francis give a characterization of the centralizer ${\frak Z}_{E_n}(f)$ of any $E_n$ algebra map $\phi: A \to B$ as the ``internal hom'' in left $\int_{S^{n-1}}A$-modules from $A$ to $B_\phi$, where $B_\phi$ denotes $B$ viewed as a left module via the map~$\phi$.
+\item Francis and Lurie give a characterization of the centralizer ${\frak Z}_n(f)$ of any $E_n$ algebra map $\phi: A \to B$ as the ``internal hom'' in left $\int_{S^{n-1}}A$-modules from $A$ to $B_\phi$, where $B_\phi$ denotes $B$ viewed as a left module via the map~$\phi$.
 \item In combination, the centralizer is characterized up to quasi-isomorphism, 
@@
 \[
-\clies(\Omega \otimes \fg, \cliels(\Omega_c^* \otimes \fh)_f) \to \bZ({\bf f})
-\]
-as factorization algebras. 
-\item We then verify that this map is a quasi-isomorphism on disks, by the Lurie-Francis result mentioned above. 
+\clies(\Omega \otimes \fg, \cliels(\Omega_c^* \otimes \fh)_f) \to \bZ_n({\bf f})
+\]
+as factorization algebras, where $\bZ({\bf f})$ is some factorization algebra modeling the centralizer~${\frak Z}_n(f)$. 
+\item We then verify that this map is a quasi-isomorphism on disks, by the Francis-Lurie result mentioned above. 
 \end{enumerate}
@@
 \label{thm: center}
-The center of the enveloping $E_n$ algebra $\UU_n\fg$ is the $E_n$ algebra $\clies(\fg, \UU_n\fg)$. 
+The center ${\frak Z}_n(\fg)$ of the enveloping $E_n$ algebra $\UU_n\fg$ is the $E_n$ algebra $\clies(\fg, \UU_n\fg)$. 
 When $k$ is $\RR$ or $\CC$, the 
@@
 \[
-\int_M {\frak Z}_{E_n}(\UU_n \rho) \simeq \clies(\fg \otimes \Omega^*(M), \cliels( \fh \otimes \Omega^*(M))).
+\int_M {\frak Z}_n(\UU_n \rho) \simeq \clies(\fg \otimes \Omega^*(M), \cliels( \fh \otimes \Omega^*(M))).
 \]
@@
 \[
-\int_{S^n} {\frak Z}_{E_n}(\UU_n \rho) \simeq \clies(\fg[\epsilon_n], \cliels( \fh[\epsilon_n]))
+\int_{S^n} {\frak Z}_n(\UU_n \rho) \simeq \clies(\fg[\epsilon_n], \cliels( \fh[\epsilon_n]))
 \]
@@
 \section{Background}
+\label{sec: background}
 
@@
 For a map $f: A \to B$ of $E_n$ algebras in $\cC$, 
-the {\em centralizer} ${\frak Z}_{E_n}(f)$ is the $E_n$ algebra in $\cC$ that is universal among those that fit in a commuting diagram
+the {\em centralizer} ${\frak Z}_n(f)$ is the $E_n$ algebra in $\cC$ that is universal among those that fit in a commuting diagram
 \[
 \begin{tikzcd}
-& {\frak Z}_{E_n}(f) \otimes A \arrow[dr] & \\
+& {\frak Z}_n(f) \otimes A \arrow[dr] & \\
 A \arrow[ur, "u \otimes \id"] \arrow[rr, "f"] && B
@@
 \]
-where the arrow in the upper left is the tensor product of the unit map $u: 1_\cC \to {\frak Z}_{E_n}(f)$ and the identity map $\id: A \to A$.
+where the arrow in the upper left is the tensor product of the unit map $u: 1_\cC \to {\frak Z}_n(f)$ and the identity map $\id: A \to A$.
 The {\em center} of an $E_n$ algebra $A$ is the centralizer of its identity morphism $\id_A: A \to A$. 
-We  denote it ${\frak Z}_{E_n}(A) := {\frak Z}_{E_n}(\id_A)$.
+We  denote it ${\frak Z}_n(A) := {\frak Z}_n(\id_A)$.
 \end{dfn}
@@
 \label{T:centralizer=inthom} 
-The centralizer ${\frak Z}_{E_n}(f)$ exists and can be identified with the classifying object for maps from $A$ to $B$ in the $\infty$-category $\Mod^{E_n}_A(\cC)$.
+The centralizer ${\frak Z}_n(f)$ exists and can be identified with the classifying object for maps from $A$ to $B$ in the $\infty$-category $\Mod^{E_n}_A(\cC)$.
 \mahmoud{we should probably spell out the meaning of the classifying object in this case to make it obvious that the centralizer is the classifying object}
@@
 For $A$ be an $E_n$ algebra in $\cC$,
-the $\infty$-category $\Mod^{E_n}_A(\cC)$ is equivalent to the $\infty$-category $\LMod_{\int_{S^{n-1} A}}(\cC)$.
+the $\infty$-category $\Mod^{E_n}_A(\cC)$ is equivalent to the $\infty$-category $\LMod_{{\int_{S^{n-1}} A}}(\cC)$.
 \end{prp}
@@
 \]
-where $\bZ(\mathbf{f})$ is some locally constant factorization algebra that models the centralizer ${\frak Z}(f)$ of the map $f$.
+where $\bZ_n(\mathbf{f})$ is some locally constant factorization algebra that models the centralizer ${\frak Z}_n(f)$ of the map~$f$.
 It is then a direct computation to verify $\theta_f$ is a quasi-isomorphism,
@@
 \subsection{Standard manipulations with $L_\infty$ algebras and their modules}
+\label{sec: review of linfty}
 
@@
 This coalgebra is canonically coaugmented by the inclusion of the base field $k \xto{\simeq} \Sym^0(\fg[1])$.
-Let $\overline{\cliels(\fg)} \subset \cliels(\fg)$ denote the subcoalgebra given by the direct sum over positive symmetric powers of $\fg[1]$,
+There is thus a subcoalgebra $\overline{\cliels(\fg)} \subset \cliels(\fg)$ given by the direct sum over positive symmetric powers of $\fg[1]$,
 which can be identified with both the kernel of the counit map as well as cokernel of the coaugmentation map.
+In short,
+\[
+\cliels(\fg) = k \oplus \overline{\cliels(\fg)}
+\]
+as complexes.
 
@@
 One should view $f$ as the basepoint for this tangent complex.
-Due to the splitting
-\[
-\cliels(\fg) = k \oplus \overline{\cliels(\fg)},
-\]
+Due to the splitting $\cliels(\fg) = k \oplus \overline{\cliels(\fg)}$,
 we have a decomposition
-\[
-\clies(\fg,\cliels(\fh)_f) \cong \cliels(\fh) \oplus \Hom^\bullet(\overline{\cliels(\fg)}, \cliels(\fh)_f),
-\]
+\begin{align*}
+\clies(\fg,\cliels(\fh)_f) 
+&\cong \cliels(\fh) \oplus \Hom^\bullet(\overline{\cliels(\fg)}, \cliels(\fh)_f)\\
+&\cong k \oplus \overline{\cliels(\fh)} \oplus \Hom^\bullet(\overline{\cliels(\fg)}, \cliels(\fh)_f)
+\end{align*}
 which plays a crucial role in our argument.
@@
 sending $(1 + g, x)$ to $f(x) + g(x)$, where $g \in \Hom^\bullet(\overline{\cliels(\fg)}, \cliels(\fh)_f)$.
-In this sense, we see how the Lie algebra cochains arising from $f$ encodes deformations.
+In this sense, we see how $\clies(\fg,\cliels(\fh)_f)$ encodes deformations of~$f$.
 
 \subsection{Defining the convolution factorization algebra}
+\label{sec: dfn of centralizer fact alg}
 
@@
 \begin{align*}
-{\frak Z}_{E_n}(f) &\simeq {{\rm Mor}}_{\Mod^{E_n}_{\UU_n\fg}}(\UU_n \fg, (\UU_n \fh)_f) \\
+{\frak Z}_n(f) &\simeq {{\rm Mor}}_{\Mod^{E_n}_{\UU_n\fg}}(\UU_n \fg, (\UU_n \fh)_f) \\
 &\simeq {\rm Mor}_{\LMod_{\int_{S^{n-1}} \UU_n\fg}}(\UU_n \fg, (\UU_n \fh)_f)
@@
 \begin{itemize}
-\item[-] $(\UU_n \fh)_f$ denotes the object in $\Mod^{E_n}_{\UU_n\fg}$ --- equivalently, in $\LMod_{\int_{S^{n-1}}\UU_n}$ --- determined by~$f$, 
-\item[-] ${\rm Mor}_{\Mod^{E_n}_{\UU_n\fg}}(\UU_n \fg, (\UU_n \fh)_f)$ denotes the classifying object for maps (i.e.
+\item $(\UU_n \fh)_f$ denotes the object in $\Mod^{E_n}_{\UU_n\fg}$ --- equivalently, in $\LMod_{\int_{S^{n-1}}\UU_n}$ --- determined by~$f$, 
+\item ${\rm Mor}_{\Mod^{E_n}_{\UU_n\fg}}(\UU_n \fg, (\UU_n \fh)_f)$ denotes the classifying object for maps (i.e.
 an internal mapping object) from $\UU_n\fg$ to $(\UU_n \fh)_f$ in the $\infty$-category $\Mod^{E_n}_{\UU_n\fg}$, and
-\item[-] ${\rm Mor}_{\LMod_{\int_{S^{n-1}} \UU_n\fg}} (\UU_n \fg, (\UU_n \fh)_f)$ denotes the classifying object for maps from ${\UU_n\fg}$ to $\UU_n \fh$ in the $\infty$-category $\LMod_{\int_{S^{n-1}}\UU_n\fg}$.
+\item ${\rm Mor}_{\LMod_{\int_{S^{n-1}} \UU_n\fg}} (\UU_n \fg, (\UU_n \fh)_f)$ denotes the classifying object for maps from ${\UU_n\fg}$ to $\UU_n \fh$ in the $\infty$-category $\LMod_{\int_{S^{n-1}}\UU_n\fg}$.
 \end{itemize}
-Note that $\int_{S^{n-1}}\UU_n\fg$ is an $E_1$ algebra equivalent to the dg algebra $U(\fg \otimes k[\epsilon_{n-1}])$.
-This identification holds because the rational $(n-1)$-sphere is formal, and hence its cochains are quasi-isomorphic to its cohomology $k[\epsilon_{n-1}]$.
-
-Using the canonical inclusion $i: U\fg \to U(\fg \otimes k[\epsilon_{n-1}])$,
-we find
-\[
-k \otimes_{U\fg} U(\fg \otimes k[\epsilon_{n-1}]) \simeq \Sym(\fg[1-n]).
-\]
+In the case at hand, this object is eminently computable.
+
+The notation $\int_{S^{n-1}}\UU_n\fg$ produces a factorization algebra on $\RR$.
+Indeed,
+\begin{align*}
+\int_{S^{n-1}}\UU_n\fg 
+&\simeq \cliels(\Omega^*_c(\RR_{> 0} \times S^{n-1}) \otimes \fg)\\
+&\simeq \cliels(\Omega^*_c(\RR_{> 0}) \otimes H^*(S^{n-1}) \otimes \fg)
+\end{align*}
+because $(n-1)$-sphere is formal over the rationals (or reals). 
+We thus see that 
+\[
+\int_{S^{n-1}}\UU_n\fg \simeq \UU_1 (H^*(S^{n-1}) \otimes \fg)
+\]
+The cohomology of the $(n-1)$-sphere is 
+\[
+R_n = k[\epsilon_{n-1}]/(\epsilon_{n-1}^2),
+\] 
+where $|\epsilon_{n-1}| = n-1$.
+Since $\UU_1 (H^*(S^{n-1}) \otimes \fg)$ is manifestly equivalent to the dg algebra~$U(\fg \otimes R_n)$,
+we find that 
+\[
+\int_{S^{n-1}}\UU_n\fg \simeq U(\fg \otimes R_n)
+\]
+as $E_1$ algebras.
+
 Recall from Section~\ref{sec: enveloping} that $\UU_n \fg$ admits two convenient models:
 as a factorization algebra by $\bU_n \fg$ and as a strict algebra over a colored operad $\Disk_n$ assigning $\Sym(\fg[1-n])$ to each disk.
-Base change thus gives rise to an equivalence 
-\[
-{\rm Mor}_{\LMod_{\int_{S^{n-1}} \UU_n}} (\UU_n \fg, (\UU_n \fh)_f)  \simeq {\rm Mor}_{U\fg} (k, (\UU_n \fh)_f)
+For $n > 1$ that is a commutative algebra.
+\owen{Should I say that??? And should we remark that the $n=1$ case is known???}
+
+We have thus reduced the situation to familiar dg algebra via the equivalence
+\[
+{\rm Mor}_{\LMod_{\int_{S^{n-1}} \UU_n\fg}}(\UU_n \fg, (\UU_n \fh)_f) 
+\simeq 
+{\rm Mor}_{\LMod_{U(\fg \otimes R_n)}} (\Sym(\fg[1-n]), (\Sym(\fh[1-n]))_f).
+\]
+By the inclusion of the unit $k \hookrightarrow R_n = k \oplus k[1-n]$,
+we obtain a canonical inclusion $i: U\fg \to U(\fg \otimes R_n)$ of dg associative algebras,
+and so
+\[
+k \otimes_{U\fg} U(\fg \otimes R_n) \simeq \Sym(\fg[1-n]).
+\]
+Base change along $i$ thus gives rise to an equivalence 
+\[
+{\rm Mor}_{\LMod_{U\fg}} (k, (\Sym(\fh[1-n]))_f) \simeq {\rm Mor}_{\LMod_{U(\fg \otimes R_n)}} (\Sym(\fg[1-n]), (\Sym(\fh[1-n]))_f)
 \]
 of underlying cochain complexes, i.e. an equivalence after applying the forgetful functor. 
-The right hand side is modeled by Lie algebra cochains of $\fg$ with coefficients in~$(\UU_n \fh)_f$, as desired.
+The left hand side is modeled by $\clies(\fg,(\Sym(\fh[1-n]))_f)$, 
+the Lie algebra cochains of $\fg$ with coefficients in~$(\UU_n \fh)_f$, as desired.
 Hence the map $\theta_{\bf f}$ is a quasi-isomorphism on any disk, as needed.
@@
 for any maps $A\stackrel{f}\to B$ and $B\stackrel{g}\to C$ of $E_n$-algebras, 
-there is a natural morphism
+there is a natural map of $E_n$-algebras
 \begin{equation}
 \label{eqdef:canonicaltocentralizers} 
-{\frak Z}_{E_n}(g) \otimes {\frak Z}_{E_n}(f) \longrightarrow {\frak Z}_{E_n}(g\circ f)
+{\frak Z}_n(g) \otimes {\frak Z}_n(f) \longrightarrow {\frak Z}_n(g\circ f)
 \end{equation}
-in the $\infty$-category of $E_n$-algebras that arises from  
-following commutative diagram of $E_n$-algebras:
+that arises from following commutative diagram of $E_n$-algebras:
 \[
 \begin{tikzcd}
-&   {\frak Z}_{E_n}(g) \otimes  {\frak Z}_{E_n}(f) \otimes A \arrow[rr, "\id\otimes \ev_f"] &&  {\frak Z}_{E_n}(g) \otimes  B \arrow[dr, "\ev_g"]\\
-A \arrow[ur, "1\otimes \id_A"] \arrow[rr, "f"] && B \arrow[rr, "g"] \arrow[ur, "1\otimes \id_B"] && C. 
-\end{tikzcd}
+&   {\frak Z}_n(g) \otimes  {\frak Z}_n(f) \otimes A \arrow[rr, "\id\otimes \ev_f"] &&  {\frak Z}_n(g) \otimes  B \arrow[dr, "\ev_g"]\\
+A \arrow[ur, "1\otimes \id_A"] \arrow[rr, "f"] && B \arrow[rr, "g"] \arrow[ur, "1\otimes \id_B"] && C 
+\end{tikzcd}.
 \]
@@
 \label{eq:dgAssofcenter}
-{\frak Z}_{E_n}(A){\otimes} {\frak Z}_{E_n}(A) \longrightarrow {\frak Z}_{E_n}(A).
+{\frak Z}_n(A){\otimes} {\frak Z}_n(A) \longrightarrow {\frak Z}_n(A).
 \end{equation}
@@
 %\begin{itemize}
-% \item The canonical map~\eqref{eq:dgAssofcenter} makes the center ${\frak Z}_{E_n}(A)$ into an $E_1$-algebra in the symmetric monoidal category of 
+% \item The canonical map~\eqref{eq:dgAssofcenter} makes the center ${\frak Z}_n(A)$ into an $E_1$-algebra in the symmetric monoidal category of 
 % $E_n$-algebras.
@@
 
-A compelling aspect of our construction is that it lets one see these properties in a barehanded fashion,
+A compelling aspect of our construction is that one can see these properties in a barehanded fashion,
 using familiar formulas with $L_\infty$ algebras.
@@
 
-\owen{I'm pooping out, but it should be straightforward to revise this in light of our revisions above.}
-
 \begin{thm}
 \label{T:compcentralizer}
- Let $f: \fg \to \fh$ and $g: \fh \to \fl$ be maps of  $L_\infty$-algebras.
+Let $f: \fg \rightsquigarrow \fh$ and $g: \fh \rightsquigarrow \fl$ be maps of  $L_\infty$-algebras,
+and let $\bold{f}: \bU_n \fg \to \bU_n \fh$ and $\bold{g}: \bU_n \fh \to \bU_n \fl$ denote the induced maps of factorization algebras.
 \begin{enumerate} 
-\item The composition $(-\star-)$ of factorization algebras (definition~\ref{def:comp}) is the canonical map 
-\[{\frak Z}_{E_n}(g) \otimes {\frak Z}_{E_n}(f) \longrightarrow {\frak Z}_{E_n}(g\circ f).\] 
-\item If $f= \fg \stackrel{\id}\to \fg$,  the composition $(-\star-)$ makes 
-$\clies\big(\fg \otimes \Omega, \cliels(\fg \otimes \Omega_c) \big)$ into an 
-(augmented) associative algebra object in factorization algebra, with unit given by $\mathbf{1}$, 
-which is equivalent to the structure of the center ${\frak Z} (\cliels(\fg \otimes \Omega_c))$. 
+\item There is a natural map of factorization algebras
+\[
+(-\star-) : \bZ_n(g) \otimes \bZ_n(f) \to \bZ_n(g \circ f),
+\]
+given by definition~\ref{def:comp}, 
+that models the canonical map 
+\[
+{\frak Z}_n(g) \otimes {\frak Z}_n(f) \longrightarrow {\frak Z}_n(g\circ f).
+\] 
+\item If $f= \fg \stackrel{\id}\to \fg$, 
+then the composition $(-\star-)$ makes $\bZ_n(\fg)$ into an 
+augmented associative algebra {\em on the nose} in the 1-category of factorization algebras on~$\RR^n$,
+and it models the center ${\frak Z}_n(\fg)$ as an $E_1$ algebra in $E_n$ algebras.
 \end{enumerate}
@@
 
-When $A$ is a factorization algebra model for $A$, in virtue of theorem~\ref{T:En=Fac} 
-(and \greg{add reference for fac algebra in fac algebra maybe too}), in order to have a factorization algebra 
-model of the center of $A$, it is sufficient to describe the induced map 
-\[{\frak Z}(A){\otimes} {\frak Z}(A) \longrightarrow {\frak Z}(A)\]
-as a factorization algebra homomorphism which makes it an associative object in the category of locally constant factorization algebras.
-
-We now turn to the specific case   of enveloping algebras $\UU_n(\fg)$.
-
-Let $f: \fg \to \fh$, $g: \fh \to \fl$ be  $L_\infty$-algebras morphisms; for instance a dg-Lie algebras morphisms. We write 
-\[ \mathbf{f}:\cliels\big(\fg \otimes \Omega^*_c\big) \to  \cliels\big(\fh \otimes \Omega^*_c\big), \quad 
-\mathbf{h}:\cliels\big(\fh \otimes \Omega^*_c\big) \to  \cliels\big(\fl \otimes \Omega^*_c\big)\]
-for the induced morphisms on their enveloping factorization algebras over $\RR^n$.
-
-The inclusion  of compactly supported forms on all forms induces, for any open $U$,  the  map
-\begin{equation}
- \label{eq:incofcpctforms} 
-\iota_U: \cliels\big(\fh \otimes \Omega^*_c(U)\big) \, \cong \, 
-Sym\big( \fh\otimes  \Omega^*_c (U) [1]\big) \hookrightarrow  
-Sym\big( \fh\otimes  \Omega^* (U) [1]\big).
-\end{equation}
-Recall from section~\ref{SS:constuctionthetaf} that the Chevalley Eilenberg cochain factorization algebras (with values in an augmented factorization 
-algebras) 
-are canonically pointed  by $\mathbf{1}\in \clies(\fg\otimes \Omega^*, B) )$ which is induced by 
-the unit $k\to \clies(\fg\otimes \Omega^*, B) )$
- of the factorization structures.  In particular, we have the canonical splitting~\eqref{eq:splittingbyaugm} 
-of the  Chevalley-Eilenberg cochain factorization algebras, and an associated grading~\eqref{eq:defgraduationoncentralizernonconnected2} on each open
-set. We denote $\varphi= \lambda_\varphi +\overline{\varphi}$ the induced decomposition given by the splitting~\eqref{eq:splittingbyaugm} . 
-We use these gradings as in section~\ref{SS:constuctionthetaf} to construct a composition as follows. 
+The proof follows by a steady accumulation of natural observations.
+
+First, as discussed in Section~\ref{sec: dfn of centralizer fact alg},
+given $L_\infty$ maps $f: \fg \to \fh$, $g: \fh \to \fl$ be  $L_\infty$-algebras morphisms,
+we obtain canonical $L_\infty$ maps
+\[
+\tilde{f}: \Omega^*_c(V) \otimes \fg \rightsquigarrow \Omega^*_c(V) \otimes \fh
+\]
+and
+\[
+\tilde{g}: \Omega^*_c(V) \otimes \fh \rightsquigarrow \Omega^*_c(V) \otimes \fl
+\]
+for each open set~$V$,
+which are functorial in opens.
+These $L_\infty$ maps correspond to maps of their Lie algebra chains and hence we obtain
+\[ 
+\mathbf{f}: \bU_n \fg \to  \bU_n \fh \quad \text{and} \quad \mathbf{g}: \bU_n \fh \to  \bU_n \fl,
+\]
+maps between their enveloping factorization algebras.
+
+Recall from Section~\ref{sec: review of linfty} the natural decomposition 
+\[
+\clies(\fg,(\cliels(\fh)_f)) \cong k \oplus \Hom^\bullet(\overline{\cliels(\fg)}, \cliels(\fh)_f)
+\]
+and that the summand $k$ encodes the defining map~$f: \fg \rightsquigarrow \fh$.
+(Abusively, here $f$, $\fg$, and $\fh$ denote generic elements and not those appearing in the theorem we are proving.)
+Hence, any element $\varphi$ in $\bZ_n(f)$, for instance, has the form
+\[
+\varphi =\lambda_\varphi \mathbf{1} +\overline{\varphi}
+\]
+where $\lambda_\varphi \in k$, encoding the component in the first summand, and $\overline{\varphi}$ denotes the component in the second summand.
+
 \begin{dfn}\label{def:comp}
 For any \emph{connected} open set $W$, we define the composition 
-$$\clies\big(\fh \otimes \Omega(W), \cliels(\fl \otimes \Omega_c(W)  \big) \otimes 
-\clie\big(\fg \otimes \Omega(W), \cliels(\fh \otimes \Omega_c(W)  \big)
-\stackrel{(-\star-)}\longrightarrow 
-\clies\big(\fg \otimes \Omega(W), \cliels(\fl \otimes \Omega_c(W)  \big)
-$$ to be given, for any $$\psi=\lambda_\psi \mathbf{1} +\overline{\psi} \in \clies\big(\fg \otimes \Omega(W), \cliels(\fh \otimes \Omega_c(W)  \big)=
-\Hom(Sym\big( \fh\otimes  \Omega (W) [1]\big), Sym\big( \fl\otimes  \Omega_c (W) [1]\big))$$
-$$\mbox{and }\varphi =\lambda_\varphi \mathbf{1} +\overline{\varphi}\in \clies\big(\fg \otimes \Omega(W), \cliels(\fh \otimes \Omega_c(W)  \big)= 
-\Hom(Sym\big( \fg\otimes  \Omega (W) [1]\big), Sym\big( \fh\otimes  \Omega_c (W) [1]\big)) $$ by 
-$$ \psi \star \varphi \, := \, \lambda_{\psi} \lambda_{\varphi} \mathbf{1}+
-\lambda_\psi g\circ \overline{\varphi} + \lambda_{\varphi} \overline{\psi} \circ \iota_W \circ f +\overline{\psi} \circ \iota_U \circ \overline{\varphi} . $$
-For any open 
-$U=\coprod\limits_{i\in I}U_i$, where the $U_i$ are the connected components of $U$,  we define  the composition 
-$$\clies\big(\fh \otimes \Omega(U), \cliels(\fl \otimes \Omega_c(U)  \big) \otimes 
-\clie\big(\fg \otimes \Omega(U), \cliels(\fh \otimes \Omega_c(U)  \big)
-\stackrel{(-\star-)}\longrightarrow 
-\clies\big(\fg \otimes \Omega(U), \cliels(\fl \otimes \Omega_c(U)  \big)
-$$ as follows. For any $$\psi \in \clies\big(\fg \otimes \Omega(U), \cliels(\fh \otimes \Omega_c(U)  \big)=
-\Hom(Sym\big( \fh\otimes  \Omega (U) [1]\big), Sym\big( \fl\otimes  \Omega_c (U) [1]\big))$$
-$$\mbox{and }\varphi \in \clies\big(\fg \otimes \Omega(U), \cliels(\fh \otimes \Omega_c(U)  \big)= 
-\Hom(Sym\big( \fg\otimes  \Omega (U) [1]\big), Sym\big( \fh\otimes  \Omega_c (U) [1]\big)), $$ we write 
-$\varphi = \mathop{\bigotimes}\limits_{i\in I} \varphi_i$, $\psi= \mathop{\bigotimes}\limits_{i\in I} \psi_i$ 
-(where $\varphi_i \in \clies\big(\fg \otimes \Omega(U_i), \cliels(\fh \otimes \Omega_c(U_i)  \big)$,
-$\psi_i\in \clies\big(\fh \otimes \Omega(U_i), \cliels(\fl \otimes \Omega_c(U_i)  \big)$) 
- using the decomposition~\eqref{eq:defgraduationoncentralizernonconnected}. Then we define
-\begin{equation} \label{eqdef:staronnonconnected}
-\psi \star \varphi \, := \mu_{\fl} \circ \Big( \bigotimes\limits_{i\in I} (\psi_i \star \varphi_i)\Big) \end{equation}
-where $\mu_{\fl}: \mathop{\bigotimes}\limits_{i\in I} \cliels(\fl\otimes \Omega^c(U_I)) \cong \cliels(\fl\otimes \Omega^c(U))$ 
-is given by the factorization algebra 
-structure. 
+\[
+\bZ_n(g)(W) \otimes \bZ_n(f)(W) \xto{(-\star-)} \bZ_n(g \circ f)(W)
+\]
+as follows.
+For any element
+\[
+\psi=\lambda_\psi \mathbf{1} +\overline{\psi} \in \bZ_n(g)(W) = \clies(\fh \otimes \Omega(W), \bU_n \fl (W)  )
+\]
+and any element
+\[
+\varphi =\lambda_\varphi \mathbf{1} +\overline{\varphi}\in \bZ_n(f)(W) = \clies(\fg \otimes \Omega(W), \bU_n \fh (W)  ),
+\] 
+set
+\[
+\psi \star \varphi =  \lambda_{\psi} \lambda_{\varphi} \mathbf{1}+
+\lambda_\psi g\circ \overline{\varphi} + \lambda_{\varphi} \overline{\psi} \circ \iota_W \circ f +\overline{\psi} \circ \iota_W \circ \overline{\varphi} 
+\]
+where $\iota_W$ denotes the inclusion $\Omega^*_c(W) \hookrightarrow \Omega^*(W)$ extended in the obvious way to this setting.
 \end{dfn}
-Since $\iota_U$ is an embeding for every $U$, in the rest of the paper, we will usually 
-omit it in the formulas.
-
-\begin{lmm}\label{L:compisfacmap} The composition $$\clies\big(\fh \otimes \Omega, \cliels(\fl \otimes \Omega_c  \big) \otimes 
+
+Since $\iota_V$ is an embedding for every open $V$, 
+we will usually omit it in the formulas for the rest of the paper.
+
+For a disconnected open $U=\coprod\limits_{i\in I}U_i$, 
+where the $U_i$ are the connected components of $U$,  
+we define the composition $(-\star-)$ by applying it to each component and then applying the structure map of the factorization algebras,
+as follows.
+For any $\psi \in \bZ_n(f)(U)$ and $\varphi \in \bZ_n(g)(U)$,
+we write 
+\[
+\varphi = \mathop{\bigotimes}\limits_{i\in I} \varphi_i
+\]
+where $\varphi_i \in \bZ_n(g)(U_i)$ and likewise $\psi= \mathop{\bigotimes}\limits_{i\in I} \psi_i$.
+Then we define
+\begin{equation} 
+\label{eqdef:staronnonconnected}
+\psi \star \varphi \, := \mu_{\fl} \circ \Big( \bigotimes\limits_{i\in I} (\psi_i \star \varphi_i)\Big) 
+\end{equation}
+where $\mu_{\fl}: \mathop{\bigotimes}\limits_{i\in I} \bU_n \fl (U_i) \cong \bU_n \fl (U)$ 
+is the structure map.
+
+\owen{I pooped out here.}
+
+\begin{lmm}
+\label{L:compisfacmap} 
+The composition $$\clies\big(\fh \otimes \Omega, \cliels(\fl \otimes \Omega_c  \big) \otimes 
 \clies\big(\fg \otimes \Omega, \cliels(\fh \otimes \Omega_c  \big)
@@
 \end{lmm}
+
 \begin{proof}
@@
 sense, that is there is a contractible space of choices for it} map 
-\[ \Upsilon: {\frak Z}_{E_n}(\UU_n g) \otimes {\frak Z}_{E_n}(\UU_n f) \longrightarrow {\frak Z}_{E_n}\big(\UU_n (g\circ f)\big)\] 
+\[ \Upsilon: {\frak Z}_n(\UU_n g) \otimes {\frak Z}_n(\UU_n f) \longrightarrow {\frak Z}_n\big(\UU_n (g\circ f)\big)\] 
 of $E_n$-algebras which makes the following diagram
@@
 &   &&  
-{\frak Z}_{E_n}\big(\UU_n (g\circ f) \big) \otimes  \UU_n \fg  \ar@/^{2pc}/[dddr]^{\ev_{\UU_n (g\circ f)}}\\
-&{\frak Z}_{E_n}(\UU_n g) \otimes  {\frak Z}_{E_n}(\UU_n f) \otimes \UU_n \fg \ar@/^{1pc}/[rru]_{ \Upsilon \otimes \id_{\UU_n \fg}} \ar[rrd]_{\id\otimes \ev_{\UU_n f}}
+{\frak Z}_n\big(\UU_n (g\circ f) \big) \otimes  \UU_n \fg  \ar@/^{2pc}/[dddr]^{\ev_{\UU_n (g\circ f)}}\\
+&{\frak Z}_n(\UU_n g) \otimes  {\frak Z}_n(\UU_n f) \otimes \UU_n \fg \ar@/^{1pc}/[rru]_{ \Upsilon \otimes \id_{\UU_n \fg}} \ar[rrd]_{\id\otimes \ev_{\UU_n f}}
 && (1)
@@
 \UU_n \fg \ar[ur]_{1^{\otimes 2}\otimes \id_{\UU_n \fg}} \ar@/_{1pc}/[rrd]^{\UU_n f} \ar@/^{6pc}/[rrruu]_{1\otimes \id_{\UU_n \fg}} &&&
-{\frak Z}_{E_n}(\UU_n g) \otimes \UU_n \fh \ar[rd]^{\ev_{\UU_n h}}  &\\
+{\frak Z}_n(\UU_n g) \otimes \UU_n \fh \ar[rd]^{\ev_{\UU_n h}}  &\\
 && \UU_n \fh \ar[rr]^{\UU_n g} \ar[ur]^{1\otimes \id_{\UU_n \fh}} && \UU_n \fl .}

### 2020-09-06 draft.tex
merge

--- 2020-09-04 draft.tex
@@
 Let $M$ be a smooth $n$-dimensional manifold and $\fg$ a Lie algebra. 
-There is a constructible $\PP_0$-factorization algebra 
+There is a constructible commutative factorization algebra 
 \begin{equation}\label{eqn:graded}
-\left(\Tilde{\bZ}_n (\fg) \; , \; {\rm Gr} \; \bU_n(\fg) \right)
+\left({\bf Bulk}_n (\fg) \; , \; {\rm Gr} \; \bU_n(\fg) \right)
 \end{equation}
-on $M \times \RR_{\geq 0}$ such that $\pi_* \Tilde{\bZ}_n (\fg)$ is equivalent to ${\rm Gr} \; \bZ_n(\fg)$ as commutative factorization algebras on $M$ where $\pi : M \times \RR_{\geq 0} \to M$ is the projection.
+on $M \times \RR_{\geq 0}$ such that $\pi_* {\bf Bulk}_n (\fg)$ is equivalent to ${\rm Gr} \; \bZ_n(\fg)$ as commutative factorization algebras on $M$ where $\pi : M \times \RR_{\geq 0} \to M$ is the projection.
+
+\brian{lifts to $\PP_0$}.
 \end{prp}
@@
 %\]
+
+\begin{prp}
+Filtered swiss cheese.
+Gr is a P_0 swiss cheese algebra.
+\end{prp}
 
@@
 \d A + \frac12 [A,A] & = 0 \\
-\d_A B + [A,B] & = 0 .
+\d B + [A,B] & = 0 .
 \end{align*}
@@
 \end{prp}
+
+\brian{spectral sequence}
+
 %\subsection{The bulk TFT}

### 2020-09-07 draft.tex
revised structure and added stubs for some easy applications

@@
 
-%Recently, a generalization of the concept of the enveloping algebra of a Lie algebra has emerged: each dg Lie algebra $\fg$ has an enveloping $E_n$ algebra $\UU_n\fg$, for every $n$, so that $\UU_1\fg$ is the usual enveloping algebra $U\fg$.
-Building on prior work \cite{BD, AF} [Owen's thesis?], Knudsen \cite{Knudsen} developed these ideas extensively and offered a useful factorization algebra model for the enveloping $E_n$ algebra.
-Our central goal here is to generalize the following results about the enveloping algebra $U\fg$ to $\UU_n\fg$, for all $n$.
-%
-%\begin{enumerate}
-%\item[(1)] the (underived) center of $U\sl_{N+1}$ is isomorphic to $(\Sym(\CC^{N}))^{S_N}$, where $\CC^{N}$ denotes the Cartan subalgebra of $\sl_{N+1}$ and $S_N$ is the Weyl group of $SL_{N+1}$, and
-%\item[(2)] the derived center of the enveloping algebra $U\fg$ is given by derived invariants of the adjoint action of $\fg$ on $U\fg$. That is to say $\Hoch^*(U\fg,U\fg) \simeq \clies(\fg, U\fg)$.
-%\end{enumerate}
+\section{Introduction}
+
+Recently, a generalization of the concept of the enveloping algebra of a Lie algebra has emerged: 
+each dg Lie algebra $\fg$ has an enveloping $E_n$ algebra $\UU_n\fg$, for every $n$, 
+so that $\UU_1\fg$ is the usual enveloping algebra $U\fg$. 
+Building on prior work \cite{BD, AF} [Owen's thesis?], 
+Knudsen \cite{Knudsen} developed these ideas extensively and offered a useful factorization algebra model for the enveloping $E_n$ algebra. 
+Our central goal here is to generalize the some well-known results about the enveloping algebra $U\fg$ to $\UU_n\fg$, for all $n$, such as
+\begin{enumerate}
+\item[(1)] the (underived) center of $U\sl_{N+1}$ is isomorphic to $(\Sym(\CC^{N}))^{S_N}$, where $\CC^{N}$ denotes the Cartan subalgebra of $\sl_{N+1}$ and $S_N$ is the Weyl group of $SL_{N+1}$, and
+\item[(2)] the derived center of the enveloping algebra $U\fg$ is given by derived invariants of the adjoint action of $\fg$ on $U\fg$. That is to say $\Hoch^*(U\fg,U\fg) \simeq \clies(\fg, U\fg)$.
+\end{enumerate}
+\owen{And keep going}
 %
@@
 We hope these ideas have exciting applications in quantum field theory and random matrix theory, as well as to other large $N$ limit phenomena.
+
+\subsection{Overview of the paper}
+
+\subsection{Acknowledgments}
+
+\subsection{Notations}
 
@@
 
+\section{A few examples of the central result}
+
+\subsection{Abelian Lie algebras and an $E_n$ HKR theorem}
+
+Given a free dg commutative algebra $A = \Sym(V^\bullet)$ generated by a cochain complex $V^\bullet$,
+one can view it as an $E_n$ algebra via the forgetful functor determined by the operad map $E_n \to E_\infty$.
+We will blithely view any commutative algebra as an $E_n$ algebra for any $n$ via this forgetting.
+
+We also know that for an abelian dg Lie algebra~${\frak a}$, 
+\[
+\cliels({\frak a}) = \Sym({\frak a}[1])
+\]
+and hence provides a free dg commutative algebra.
+This feature can be leveraged to prove the following result about $E_n$-centers of free commutative algebras.
+
+\begin{prp}
+Given a free dg commutative algebra $A = \Sym(V^\bullet)$ generated by a cochain complex $V^\bullet$,
+its center ${\frak Z}_n(A)$ is equivalent to the $E_{n+1}$ algebra of its shifted polyvector fields 
+\[
+{\rm Poly}_n(A) = \Sym(V^\bullet \oplus (V\bullet)^\vee[-n]).
+\]
+\end{prp}
+
+\begin{proof}
+A cochain complex $V^\bullet$ is an abelian dg Lie algebra;
+indeed, so is any shift $V^\bullet[k]$. 
+Let $\fg_V$ denote $V^\bullet[-n+1]$ viewed as an abelian dg Lie algebra.
+The Poincar\'e lemma for compactly supported de Rham forms on $\RR^n$ provides a canonical quasi-isomorphism
+\[
+\Omega^*_c(\RR^n) \xto{\simeq} \RR[-n]
+\]
+by the natural quotient map and hence determines a canonical quasi-isomorphism
+\[
+\cliels(\Omega^*_c(\RR^n) \otimes \fg_V) \xto{\simeq} \Sym(V^\bullet).
+\]
+This map makes sense on any ball in $\RR^n$ and thus implies that $\bU_n \fg_V$ is quasi-isomorphic as a $\Disk_n$ algebra to~$\Sym(V^\bullet)$.
+Applying our central theorem, we see
+\begin{align*}
+\bZ_n(\fg_V) &= \clies(\Omega^* \otimes \fg_V, \bU_n \fg_V) \\
+&= \Sym((\Omega^* \otimes \fg_V)^\vee[-1]) \otimes \Sym(\Omega^*_c \otimes \fg_V[1])\\
+& \simeq \Sym(V^\bullet \oplus (V\bullet)^\vee[-n])
+\end{align*}
+because
+\[
+\Omega^*(\RR^n) \otimes \fg_V \simeq V[-n+1]
+\]
+so
+\[
+\Sym( (\Omega^*(\RR^n) \otimes \fg_V)^\vee[-1]) \simeq \Sym( V^\vee[-n]).
+\]
+This identification concludes the argument.
+\end{proof}
+
+This result is the simplest case of a generalized Hochschild-Kostant-Rosenberg theorem for commutative algebras viewed as $E_n$ algebras.
+(The classic theorem proves the $n=1$ situation.)
+Such a result is proved by very different methods in~\cite{CalWil}.
+Now we swiftly describe how to use methods like those in this paper to prove a version of this powerful result.
+
+Our approach applies only to a certain class of dg commutative algebras,
+due to a technical hypothesis necessary to apply our methods.
+We need as input an augmented dg commutative algebra $\epsilon: A \to k$ that admits a semifree resolution of the form $(\Sym(V^\vee), \partial)$, where $V$ is some graded vector space.
+In other words, we want to know that the generators can be realized as the graded linear dual of some other graded vector space.
+We say such an $A$ is of {\em type~($\star$)}.
+
+\begin{prp}
+Let $A$ be an augmented dg commutative algebra of type~($\star$).
+Then 
+\[
+{\frak Z}_n(A) \simeq {\rm Poly}_n(A) \simeq \Sym_A(\TT_A[-n]).
+\]
+\end{prp}
+
+\owen{This proposition should be phrased correctly. The RHS isn't quite correct unless $A$ is good enough.}
+
+\begin{proof}
+\owen{The method described in the email.}
+\end{proof}
+
+\owen{Also prove that the $E_n$ center of $\clies(\fg)$ is also $\clies(\fg, \UU_n \fg)$}
+
+\begin{cor}
+\label{cor: koszul dual to main theorem}
+For any $L_\infty$ algebra $\fg$,
+there is a quasi-isomorphism
+\[
+{\frak Z}_n(\clies(\fg)) \simeq \clies(\fg, \UU_n \fg).
+\]
+\end{cor}
+
+\subsection{Reductive Lie algebras and a generalized Harish-Chandra homomorphism}
+
+\begin{prp}
+For $\fg$ a reductive \owen{semisimple?} Lie algebra with Cartan subalgebra~$\fh$ and Weyl group~$W$, 
+there is a quasi-isomorphism of $E_{n+1}$ algebra
+\[
+{\frak Z}_n(\UU_n \fg) \simeq H^*_{\rm Lie}(\fg) \otimes \Sym(\fh[1-n])^W.
+\]
+\end{prp}
+
+\begin{proof}
+\owen{In brief
+\[
+{\frak Z}_n(\UU_n \fg) \simeq \clies(\fg, \Sym(\fg[1-n])
+\]
+and then apply theorems about Lie algebra cohomology plus Chevalley restriction theorem.}
+\end{proof}
+
+\subsection{The large $N$ limit of the center ${\frak Z}_n(\UU_n {\frak gl}_N)$ and cyclic cohomology}
+
+\owen{Point out how to use LQT map and deduce existence of $E_n$ algebra structure on a shifted copy of cyclic cohomology of~$\Omega^*_c$}
+
+\subsection{Free Lie algebras and free $E_n$ algebras}
+
+\owen{Describe what we can of the center of a free $E_n$ algebra thanks to Ben's theorem}
+
 \section{Functoriality of the centralizer construction}
@@
 The righthand side is, however, the pushforward $\int_S \bZ_n \fg$.
-\owen{Hmmm, that map goes the wrong way, but I'm pretty sure it provides the inverse-up-to-qiso we need.}
+\owen{That map is not the canonical map as it goes the ``wrong way,'' but I'm pretty sure it provides the inverse-up-to-qiso we need.}
 \end{proof}
@@
 
-\section{Universal bulk TFT}
+\subsection{Koszul duality for enveloping $E_n$ algebras}
+
+\owen{Use corollary~\ref{cor: koszul dual to main theorem} to exhibit a "dual" Swiss cheese pair and then compute the relative tensor product over the center, which will be the unit $E_n$ algebra.
+Draw a picture of the strip.}
+
+\section{Centers and topological field theories}
 \label{sec: TFT}
@@
 Filtered swiss cheese.
-Gr is a P_0 swiss cheese algebra.
+$Gr$ is a $P_0$ swiss cheese algebra.
 \end{prp}
@@
 
-\section{Examples?}
-
-\greg{Add the Koszul duality example. Add examples coming from topological spaces and abelian Lie algebras}
-
-\subsection{$E_n$-calculus}
 \bibliographystyle{alpha}  

### 2020-09-07 draft.tex
almost there

--- 2020-09-06 draft.tex
@@
 
-Abstractly, we know that any algebra over the Swiss cheese operad can be modeled as a constructible factorization algebra on a manifold with boundary. 
+Given an $E_n$-algebra $A$ the pair $(\fZ_n (A) , A)$ is an algebra over the $(n+1)$-dimensional Swiss cheese operad. 
+The first objective is to define a certain ``classical limit" of this pair in the case that $A$ is an $E_n$-enveloping algebra.
+
+\begin{prp} \label{prp:swiss1}
+Let $\fg$ be a Lie algebra. 
+The pair $(\fZ_n(\fg) , \UU_n(\fg))$ is a filtered object in the $\infty$-category of algebras over the $(n+1)$-dimensional Swiss cheese operad. 
+The resulting associated graded pair $({\rm Gr} \; \fZ_n(\fg) , {\rm Gr} \; \UU_n(\fg))$ is a commutative algebra object.
+\end{prp}
+
+The key insight is that there exists a filtration on our model for the $E_n$-center $\bZ_n(\fg)$ and the $E_n$-enveloping algebra $\bU_n (\fg)$ whose associated graded factorization algebras ${\rm Gr} \; \bZ_n(\fg)$ and ${\rm Gr} \; \bU_n(\fg)$ are {\em commutative} factorization algebras.
+
+\brian{additivity}
+
+\begin{rmk}
+By a similar proof as in the main part of the paper, we expect that one can see that the factorization algebra
+\[
+\clie \bigg(\Omega^\bu \otimes \fg \; ; \; {\rm Sym} \left(\Omega^\bu_c \otimes \fg [1] \right) \bigg)
+\]
+is a model for the {\em $\PP_n$-center} of the $\PP_n$-enveloping algebra $\UU_{\PP_n} (\fg)$. 
+\end{rmk}
+
+The associated graded pair in Proposition \ref{prp:swiss1} carries the additional Poisson-type structure.
+
+\begin{prp} \label{prp:poisson}
+The associated graded pair $({\rm Gr} \; \fZ_n(\fg) , {\rm Gr} \; \UU_n(\fg))$ determines an algebra over the operad $\PP_{[n+1,n]}$. 
+\end{prp}
+
+There is another geometric picture for algebras over the $(n+1)$-dimensional Swiss cheese operad in terms of constructible factorization algebras on $(n+1)$-manifolds with boundary.
 One drawback of the previous section is that we did not provide a model for the $E_n$-center of an enveloping algebra as a constructible factorization algebra on an $(n+1)$-dimensional manifold with boundary.
-There is, however, a certain ``dequantization" of the $E_n$-center that we do have an explicit description of.
-
-The key insight is that there exists a filtration on our model for the $E_n$-center $\bZ_n(\fg)$ and the $E_n$-enveloping algebra $\bU_n (\fg)$ whose associated graded factorization algebras ${\rm Gr} \; \bZ_n(\fg)$ and ${\rm Gr} \; \bU_n(\fg)$ are {\em commutative} factorization algebras.
-
-Our first main result is the following.
+
+A constructible factorization algebra $\bA$ on $M \times \RR_{\geq 0}$ determines a pair of factorization algebras $(\pi_* \bA , \bA_{\partial})$ on $M$ which locally define the $E_1$-model for $(n+1)$-Swiss cheese algebras.
+
+The next goal of this section is to provide a model of the classical limit of the $E_n$-center as a constructible factorization algebra.
 
@@
 Let $M$ be a smooth $n$-dimensional manifold and $\fg$ a Lie algebra. 
-There is a constructible commutative factorization algebra 
-\begin{equation}\label{eqn:graded}
-\left({\bf Bulk}_n (\fg) \; , \; {\rm Gr} \; \bU_n(\fg) \right)
-\end{equation}
-on $M \times \RR_{\geq 0}$ such that $\pi_* {\bf Bulk}_n (\fg)$ is equivalent to ${\rm Gr} \; \bZ_n(\fg)$ as commutative factorization algebras on $M$ where $\pi : M \times \RR_{\geq 0} \to M$ is the projection.
-
-\brian{lifts to $\PP_0$}.
+There is a constructible commutative factorization algebra ${\bf C}_n (\fg)$
+%\begin{equation}\label{eqn:graded}
+%\left({\bf Bulk}_n (\fg) \; , \; {\rm Gr} \; \bU_n(\fg) \right)
+%\end{equation}
+on $M \times \RR_{\geq 0}$ such that the pair 
+\[
+(\pi_* {\bf C}_n (\fg), {\bf C}_n (\fg)_\partial)
+\]
+is equivalent to the pair $({\rm Gr} \; \bZ_n(\fg), {\rm Gr} \; \bU_n(\fg))$ as commutative factorization algebras \brian{adjectives}
 \end{prp}
 
-A $\PP_0$, or $1$-shifted Poisson, algebra is a commutative dg algebra equipped with a bracket of cohomological degree $+1$ that satisfies a graded version of the Jacobi identity and is a biderivation with respect to the commutative product \brian{reference}.
-Likewise, a $\PP_0$-factorization algebra is a factorization algebra whose value on each open set is $\PP_0$-algebra.
+%A $\PP_0$, or $1$-shifted Poisson, algebra is a commutative dg algebra equipped with a bracket of cohomological degree $+1$ that satisfies a graded version of the Jacobi identity and is a biderivation with respect to the commutative product \brian{reference}.
+%Likewise, a $\PP_0$-factorization algebra is a factorization algebra whose value on each open set is $\PP_0$-algebra.
+
+Following the proof of this proposition, our main thrust is to interpret this result by exhibiting a topological field theory on the $(n+1)$-dimensional manifold with boundary $M \times \RR_{\geq 0}$ whose factorization algebra of classical observables is precisely the constructible factorization algebra in (\ref{eqn:graded}).
 
 The Batalin--Vilkovisky (BV) formalism for studying quantum field theory \brian{finish}
-
-Following the proof of this proposition, our main thrust is to interpret this result in the BV formalism by exhibiting a topological field theory on the $(n+1)$-dimensional manifold with boundary $M \times \RR_{\geq 0}$ whose factorization algebra of classical observables is precisely the constructible factorization algebra in (\ref{eqn:graded}).
 
@@
 
+\subsection{The ``classical limit"}
+
+We accomplish Proposition \ref{prp:swiss1} by exhibiting a filtration at the level of strict factorization algebras in our model of the $E_n$-center.
+
+For any dg Lie (in fact, $L_\infty$) algebra, the Chevalley--Eilenberg cochain complex computing Lie algebra homology admits a natural filtration whose associated graded has the structure of a commutative dg algebra.
+If $\fh$ is a dg Lie algebra, let $\clieu_{\leq k} (\fh)$ be the subcomplex of Chevalley--Eilenberg chains which is $\Sym^{\leq k} (\fh[1])$ as an underlying graded vector space. 
+The associated graded cochain complex is the free symmetric algebra on $\fh[1]$ thought of as simply a cochain complex:
+\[
+{\rm Gr} \; \clieu (\fh) = {\rm Sym} (\fh [1])  .
+\]
+Here, the differential on the right-hand side is simply the underlying linear differential of $\fh$ (in terms of $L_\infty$ algebras, this is the $1$-ary operation $\ell_1$).
+
+The Lie bracket on $\fh$ endows ${\rm Sym} (\fh [1])$ with the additional structure of a $\PP_0$-algebra. 
+On linear elements this is simply the Lie bracket on $\fh$, and one extends to the full symmetric algebra by the graded Leibniz rule.
+
+Consider our factorization model for the $E_n$-enveloping algebra $\bU_n(\fg) = \clieu (\fg \otimes \Omega_c)$. 
+The filtration on Chevalley--Eilenberg chains equips $\bU_n(\fg)$ with a filtration as a factorization algebra.
+
+There is a similar filtration on our model for the $E_n$-center $\bZ_n(\fg)$. 
+Define
+\[
+F^k \bZ_n(\fg) = \clie \bigg(\fg \otimes \Omega \; , \; \clieu_{\leq k} (\fg \otimes \Omega_c) \bigg) .
+\]
+
+\brian{$\PP_0$ stuff}
+
+The associated graded commutative factorization algebras ${\rm Gr} \; \bU_n (\fg)$ and ${\rm Gr} \; \bZ_n(\fg)$ lift to $\PP_0$-factorization algebras.
+
 \begin{prp}
-Filtered swiss cheese.
-Gr is a P_0 swiss cheese algebra.
+The pair $(\bZ_n (\fg), \bU_n(\fg)$ is a filtered, \brian{not sure what we're calling this}. 
+Further, the associated graded $({\rm Gr} \; \bZ_n (\fg), {\rm Gr} \; \bU_n(\fg)$ is a $\PP_0$ \brian{not sure what we're calling this}. 
 \end{prp}
 
+It is immediate to check that this is a filtration of factorization algebras and that its associated graded has the structure of a $\PP_0$-factorization algebra.
+In fact, we have the following result, which explains the relationship to the ``bulk" $(n+1)$-dimensional factorization algebra $\Tilde{\bZ}_n(\fg)$ we introduced in the last section.
+
+ \begin{lmm}
+Let $M$ be an $n$-dimensional manifold.
+There is a quasi-isomorphism of  $\PP_0$-factorization algebras on $M$:
+\[
+\pi_* \Tilde{\bZ}_n(\fg) \; \xto{\simeq} \; {\rm Gr} \; \bZ_n(\fg) .
+\]
+where $\pi : M \times \RR_{>0} \to M$ is the projection. 
+\end{lmm}
+
+In fact, we will show that this quasi-isomorphism is a deformation retraction.
+
+\begin{proof}
+To exhibit this quasi-isomorphism, we introduce the following cochain maps.
+For an open set $U \subset M$ let
+\[
+\int_\RR : \Omega_c(U \times \RR) \to \Omega_c (U) [1] 
+\] 
+be the map which integrates a compactly supported form on $U \times \RR$ along $\RR$. 
+This map is a quasi-isomorphism for any $U $ and admits the following explicit retract. 
+Let $\phi$ be a fixed compactly supported function on $\RR$ of mass $1$ and define
+\[
+r_\phi : \Omega_c(U) [1] \to \Omega_c (U \times \RR)
+\]
+by $r_\phi (\alpha) = \alpha \wedge \phi \, \d t$. 
+\end{proof}
+
+Since the universal action of $\bZ_n(\fg)$ on $\bU_n (\fg)$ is compatible with the above filtrations, we obtain the following constructible factorization algebra on $M \times \RR_{\geq 0}$.
+
+\begin{dfn}\label{dfn:constructible1}
+Let $(\Tilde{\bZ}_n (\fg), {\rm Gr} \bU_n(\fg))$ be the following constructible $\PP_0$-factorization algebra on $M \times \RR_{\geq 0}$:
+\begin{itemize}
+\item to an open set $U \subset M \times \RR_{> 0}$, we assign the cochain complex $\Tilde{\bZ}_n (\fg)(U)$.
+\item to an open set $U \subset M \times \RR_{\geq 0}$ with $U \cap (M \times \{0\}) \ne 0$ we assign the cochain complex ${\rm Gr} \;\bU_n(\fg)(U)$. 
+\end{itemize}
+\brian{not sure how much to say about structure maps}
+\end{dfn}
+
 \subsection{The bulk factorization algebra}
+
+It is immediate to check that this is a filtration of factorization algebras and that its associated graded has the structure of a $\PP_0$-factorization algebra.
+In fact, we have the following result, which explains the relationship to the ``bulk" $(n+1)$-dimensional factorization algebra $\Tilde{\bZ}_n(\fg)$ we introduced in the last section.
+
+ \begin{lmm}
+Let $M$ be an $n$-dimensional manifold.
+There is a quasi-isomorphism of  $\PP_0$-factorization algebras on $M$:
+\[
+\pi_* \Tilde{\bZ}_n(\fg) \; \xto{\simeq} \; {\rm Gr} \; \bZ_n(\fg) .
+\]
+where $\pi : M \times \RR_{>0} \to M$ is the projection. 
+\end{lmm}
+
+In fact, we will show that this quasi-isomorphism is a deformation retraction.
+
+\begin{proof}
+To exhibit this quasi-isomorphism, we introduce the following cochain maps.
+For an open set $U \subset M$ let
+\[
+\int_\RR : \Omega_c(U \times \RR) \to \Omega_c (U) [1] 
+\] 
+be the map which integrates a compactly supported form on $U \times \RR$ along $\RR$. 
+This map is a quasi-isomorphism for any $U $ and admits the following explicit retract. 
+Let $\phi$ be a fixed compactly supported function on $\RR$ of mass $1$ and define
+\[
+r_\phi : \Omega_c(U) [1] \to \Omega_c (U \times \RR)
+\]
+by $r_\phi (\alpha) = \alpha \wedge \phi \, \d t$. 
+\end{proof}
+
+Since the universal action of $\bZ_n(\fg)$ on $\bU_n (\fg)$ is compatible with the above filtrations, we obtain the following constructible factorization algebra on $M \times \RR_{\geq 0}$.
+
+\begin{dfn}\label{dfn:constructible1}
+Let $(\Tilde{\bZ}_n (\fg), {\rm Gr} \bU_n(\fg))$ be the following constructible $\PP_0$-factorization algebra on $M \times \RR_{\geq 0}$:
+\begin{itemize}
+\item to an open set $U \subset M \times \RR_{> 0}$, we assign the cochain complex $\Tilde{\bZ}_n (\fg)(U)$.
+\item to an open set $U \subset M \times \RR_{\geq 0}$ with $U \cap (M \times \{0\}) \ne 0$ we assign the cochain complex ${\rm Gr} \;\bU_n(\fg)(U)$. 
+\end{itemize}
+\brian{not sure how much to say about structure maps}
+\end{dfn}
 
@@
 \end{proof}
-
-\subsection{The ``classical limit"}
-
-For any dg Lie (in fact, $L_\infty$) algebra, the Chevalley--Eilenberg cochain complex computing Lie algebra homology admits a natural filtration whose associated graded has the structure of a commutative dg algebra.
-If $\fh$ is a dg Lie algebra, let $\clieu_{\leq k} (\fh)$ be the subcomplex of Chevalley--Eilenberg chains which is $\Sym^{\leq k} (\fh[1])$ as an underlying graded vector space. 
-The associated graded is the free symmetric algebra on $\fh[1]$ thought of as simply a cochain complex:
-\[
-{\rm Gr} \; \clieu (\fh) = {\rm Sym} (\fh [1])  .
-\]
-Here, the differential on the right-hand side is simply the underlying linear differential of $\fh$ (in terms of $L_\infty$ algebras, this is the $1$-ary operation $\ell_1$).
-
-The Lie bracket on $\fh$ endows ${\rm Sym} (\fh [1])$ with the additional structure of a $\PP_0$-algebra. 
-On linear elements this is simply the Lie bracket on $\fh$, and one extends to the full symmetric algebra by the graded Leibniz rule.
-
-Consider our factorization model for the $E_n$-enveloping algebra $\bU_n(\fg) = \clieu (\fg \otimes \Omega_c)$. 
-The filtration on Chevalley--Eilenberg chains equips $\bU_n(\fg)$ with a filtration as a factorization algebra. 
-Furthermore, the resulting associated graded ${\rm Gr} \; \bU_n (\fg)$ has the natural structure of a $\PP_0$-factorization algebra.
-
-There is a similar filtration on our model for the $E_n$-center $\bZ_n(\fg)$. 
-Define
-\[
-F^k \bZ_n(\fg) = \clie \bigg(\fg \otimes \Omega \; , \; \clieu_{\leq k} (\fg \otimes \Omega_c) \bigg) .
-\]
-It is immediate to check that this is a filtration of factorization algebras and that its associated graded has the structure of a $\PP_0$-factorization algebra.
-In fact, we have the following result, which explains the relationship to the ``bulk" $(n+1)$-dimensional factorization algebra $\Tilde{\bZ}_n(\fg)$ we introduced in the last section.
-
- \begin{lmm}
-Let $M$ be an $n$-dimensional manifold.
-There is a quasi-isomorphism of  $\PP_0$-factorization algebras on $M$:
-\[
-\pi_* \Tilde{\bZ}_n(\fg) \; \xto{\simeq} \; {\rm Gr} \; \bZ_n(\fg) .
-\]
-where $\pi : M \times \RR_{>0} \to M$ is the projection. 
-\end{lmm}
-
-In fact, we will show that this quasi-isomorphism is a deformation retraction.
-
-\begin{proof}
-To exhibit this quasi-isomorphism, we introduce the following cochain maps.
-For an open set $U \subset M$ let
-\[
-\int_\RR : \Omega_c(U \times \RR) \to \Omega_c (U) [1] 
-\] 
-be the map which integrates a compactly supported form on $U \times \RR$ along $\RR$. 
-This map is a quasi-isomorphism for any $U $ and admits the following explicit retract. 
-Let $\phi$ be a fixed compactly supported function on $\RR$ of mass $1$ and define
-\[
-r_\phi : \Omega_c(U) [1] \to \Omega_c (U \times \RR)
-\]
-by $r_\phi (\alpha) = \alpha \wedge \phi \, \d t$. 
-\end{proof}
-
-Since the universal action of $\bZ_n(\fg)$ on $\bU_n (\fg)$ is compatible with the above filtrations, we obtain the following constructible factorization algebra on $M \times \RR_{\geq 0}$.
-
-\begin{dfn}\label{dfn:constructible1}
-Let $(\Tilde{\bZ}_n (\fg), {\rm Gr} \bU_n(\fg))$ be the following constructible $\PP_0$-factorization algebra on $M \times \RR_{\geq 0}$:
-\begin{itemize}
-\item to an open set $U \subset M \times \RR_{> 0}$, we assign the cochain complex $\Tilde{\bZ}_n (\fg)(U)$.
-\item to an open set $U \subset M \times \RR_{\geq 0}$ with $U \cap (M \times \{0\}) \ne 0$ we assign the cochain complex ${\rm Gr} \;\bU_n(\fg)(U)$. 
-\end{itemize}
-\brian{not sure how much to say about structure maps}
-\end{dfn}
 

### 2020-09-07 draft.tex

--- 2020-09-07 draft.tex
@@
 
+\subsection{The ``classical limit"}
+
+We accomplish Proposition \ref{prp:swiss1} by exhibiting a filtration at the level of strict factorization algebras in our model of the $E_n$-center.
+
+For any dg Lie (in fact, $L_\infty$) algebra, the Chevalley--Eilenberg cochain complex computing Lie algebra homology admits a natural filtration whose associated graded has the structure of a commutative dg algebra.
+If $\fh$ is a dg Lie algebra, let $\clieu_{\leq k} (\fh)$ be the subcomplex of Chevalley--Eilenberg chains which is $\Sym^{\leq k} (\fh[1])$ as an underlying graded vector space. 
+The associated graded cochain complex is the free symmetric algebra on $\fh[1]$ thought of as simply a cochain complex:
+\[
+{\rm Gr} \; \clieu (\fh) = {\rm Sym} (\fh [1])  .
+\]
+Here, the differential on the right-hand side is simply the underlying linear differential of $\fh$ (in terms of $L_\infty$ algebras, this is the $1$-ary operation $\ell_1$).
+
+The Lie bracket on $\fh$ endows ${\rm Sym} (\fh [1])$ with the additional structure of a $\PP_0$-algebra. 
+On linear elements this is simply the Lie bracket on $\fh$, and one extends to the full symmetric algebra by the graded Leibniz rule.
+
+Consider our factorization model for the $E_n$-enveloping algebra $\bU_n(\fg) = \clieu (\fg \otimes \Omega_c)$. 
+The filtration on Chevalley--Eilenberg chains equips $\bU_n(\fg)$ with a filtration as a factorization algebra.
+
+There is a similar filtration on our model for the $E_n$-center $\bZ_n(\fg)$. 
+Define
+\[
+F^k \bZ_n(\fg) = \clie \bigg(\fg \otimes \Omega \; , \; \clieu_{\leq k} (\fg \otimes \Omega_c) \bigg) .
+\]
+
+\brian{$\PP_0$ stuff}
+
+The associated graded commutative factorization algebras ${\rm Gr} \; \bU_n (\fg)$ and ${\rm Gr} \; \bZ_n(\fg)$ lift to $\PP_0$-factorization algebras.
+
 \begin{prp}
-Filtered swiss cheese.
-$Gr$ is a $P_0$ swiss cheese algebra.
+The pair $(\bZ_n (\fg), \bU_n(\fg)$ is a filtered, \brian{not sure what we're calling this}. 
+Further, the associated graded $({\rm Gr} \; \bZ_n (\fg), {\rm Gr} \; \bU_n(\fg)$ is a $\PP_0$ \brian{not sure what we're calling this}. 
 \end{prp}
 
+It is immediate to check that this is a filtration of factorization algebras and that its associated graded has the structure of a $\PP_0$-factorization algebra.
+In fact, we have the following result, which explains the relationship to the ``bulk" $(n+1)$-dimensional factorization algebra $\Tilde{\bZ}_n(\fg)$ we introduced in the last section.
+
+ \begin{lmm}
+Let $M$ be an $n$-dimensional manifold.
+There is a quasi-isomorphism of  $\PP_0$-factorization algebras on $M$:
+\[
+\pi_* \Tilde{\bZ}_n(\fg) \; \xto{\simeq} \; {\rm Gr} \; \bZ_n(\fg) .
+\]
+where $\pi : M \times \RR_{>0} \to M$ is the projection. 
+\end{lmm}
+
+In fact, we will show that this quasi-isomorphism is a deformation retraction.
+
+\begin{proof}
+To exhibit this quasi-isomorphism, we introduce the following cochain maps.
+For an open set $U \subset M$ let
+\[
+\int_\RR : \Omega_c(U \times \RR) \to \Omega_c (U) [1] 
+\] 
+be the map which integrates a compactly supported form on $U \times \RR$ along $\RR$. 
+This map is a quasi-isomorphism for any $U $ and admits the following explicit retract. 
+Let $\phi$ be a fixed compactly supported function on $\RR$ of mass $1$ and define
+\[
+r_\phi : \Omega_c(U) [1] \to \Omega_c (U \times \RR)
+\]
+by $r_\phi (\alpha) = \alpha \wedge \phi \, \d t$. 
+\end{proof}
+
+Since the universal action of $\bZ_n(\fg)$ on $\bU_n (\fg)$ is compatible with the above filtrations, we obtain the following constructible factorization algebra on $M \times \RR_{\geq 0}$.
+
+\begin{dfn}\label{dfn:constructible1}
+Let $(\Tilde{\bZ}_n (\fg), {\rm Gr} \bU_n(\fg))$ be the following constructible $\PP_0$-factorization algebra on $M \times \RR_{\geq 0}$:
+\begin{itemize}
+\item to an open set $U \subset M \times \RR_{> 0}$, we assign the cochain complex $\Tilde{\bZ}_n (\fg)(U)$.
+\item to an open set $U \subset M \times \RR_{\geq 0}$ with $U \cap (M \times \{0\}) \ne 0$ we assign the cochain complex ${\rm Gr} \;\bU_n(\fg)(U)$. 
+\end{itemize}
+\brian{not sure how much to say about structure maps}
+\end{dfn}
+
 \subsection{The bulk factorization algebra}
+
+It is immediate to check that this is a filtration of factorization algebras and that its associated graded has the structure of a $\PP_0$-factorization algebra.
+In fact, we have the following result, which explains the relationship to the ``bulk" $(n+1)$-dimensional factorization algebra $\Tilde{\bZ}_n(\fg)$ we introduced in the last section.
+
+ \begin{lmm}
+Let $M$ be an $n$-dimensional manifold.
+There is a quasi-isomorphism of  $\PP_0$-factorization algebras on $M$:
+\[
+\pi_* \Tilde{\bZ}_n(\fg) \; \xto{\simeq} \; {\rm Gr} \; \bZ_n(\fg) .
+\]
+where $\pi : M \times \RR_{>0} \to M$ is the projection. 
+\end{lmm}
+
+In fact, we will show that this quasi-isomorphism is a deformation retraction.
+
+\begin{proof}
+To exhibit this quasi-isomorphism, we introduce the following cochain maps.
+For an open set $U \subset M$ let
+\[
+\int_\RR : \Omega_c(U \times \RR) \to \Omega_c (U) [1] 
+\] 
+be the map which integrates a compactly supported form on $U \times \RR$ along $\RR$. 
+This map is a quasi-isomorphism for any $U $ and admits the following explicit retract. 
+Let $\phi$ be a fixed compactly supported function on $\RR$ of mass $1$ and define
+\[
+r_\phi : \Omega_c(U) [1] \to \Omega_c (U \times \RR)
+\]
+by $r_\phi (\alpha) = \alpha \wedge \phi \, \d t$. 
+\end{proof}
+
+Since the universal action of $\bZ_n(\fg)$ on $\bU_n (\fg)$ is compatible with the above filtrations, we obtain the following constructible factorization algebra on $M \times \RR_{\geq 0}$.
+
+\begin{dfn}\label{dfn:constructible1}
+Let $(\Tilde{\bZ}_n (\fg), {\rm Gr} \bU_n(\fg))$ be the following constructible $\PP_0$-factorization algebra on $M \times \RR_{\geq 0}$:
+\begin{itemize}
+\item to an open set $U \subset M \times \RR_{> 0}$, we assign the cochain complex $\Tilde{\bZ}_n (\fg)(U)$.
+\item to an open set $U \subset M \times \RR_{\geq 0}$ with $U \cap (M \times \{0\}) \ne 0$ we assign the cochain complex ${\rm Gr} \;\bU_n(\fg)(U)$. 
+\end{itemize}
+\brian{not sure how much to say about structure maps}
+\end{dfn}
 

### 2020-09-07 draft.tex
small additions

@@
 \begin{document}
-\title{Centralizers of higher enveloping algebras of Lie algebras}
+\title{Centers and centralizers of higher enveloping algebras of Lie algebras}
 
@@
 The square-zero condition efficiently encodes the higher Jacobi relations.
+We call $\cliels(\fg)$ the {\em Lie algebra chains} (or Chevalley-Eilenberg chains) of~$\fg$.
+
 This coalgebra is canonically coaugmented by the inclusion of the base field $k \xto{\simeq} \Sym^0(\fg[1])$.
@@
 as complexes.
+
+This construction is symmetric monoidal.
+The {\em product} of two $L_\infty$ algebras $\fg \times \fh$ is the direct sum of the underlying graded vector spaces $\fg \oplus \fh$ equipped with the brackets encoded by the tensor product of their chains
+\[
+\cliels(\fg \times \fh) = \cliels(\fg) \otimes \cliels(\fh),
+\]
+which piggybacks on the fact that $\Sym$ is a symmetric monoidal functor.
 
@@
 
+\owen{The weird and interesting bit is to compute the factorization homology over a nontrivial (closed) manifold.}
+
 \subsection{Free Lie algebras and free $E_n$ algebras}
@@
 \]
-and that the summand $k$ encodes the defining map~$f: \fg \rightsquigarrow \fh$.
-(Abusively, here $f$, $\fg$, and $\fh$ denote generic elements and not those appearing in the theorem we are proving.)
+and that the summand $k$ corresponds to (scalar multiples of) the defining map~$f: \fg \rightsquigarrow \fh$.
+(Abusively, here $f$, $\fg$, and $\fh$ are generic and are not those appearing in the theorem we are proving here.)
 Hence, any element $\varphi$ in $\bZ_n(f)$, for instance, has the form
@@
 \]
-where $\iota_W$ denotes the inclusion $\Omega^*_c(W) \hookrightarrow \Omega^*(W)$ extended in the obvious way to this setting.
+where the inclusion $\iota_W: \Omega^*_c(W) \hookrightarrow \Omega^*(W)$ is extended in the obvious, functorial way to this setting.
 \end{dfn}

### 2020-09-07 draft.tex
more swiss cheese

@@
 \begin{thm}
-\label{T:En=Fac} 
+\label{thm:lurie1} 
 There is an equivalence of $\infty$-categories between $E_n$-algebras and locally constant prefactorization algebras on~$\RR^n$. 
@@
 
-Given an $E_{n+1}$-algebra one can speak of its $\infty$-category of left (or right) modules.
-This $\infty$-category is obtained by ``forgetting" the $E_{n+1}$-algebra to an $E_1$-algebra and then taking the left-modules for this $E_1$-algebra.
+Given an $\EE_{n+1}$-algebra one can speak of its $\infty$-category of left (or right) modules.
+This $\infty$-category is obtained by ``forgetting" the $\EE_{n+1}$-algebra to an $\EE_1$-algebra and then taking the left-modules for this $\EE_1$-algebra.
 
 The operad of little $n$-disks is built from configurations of disjoint unions of $n$-disks inside $n$-dimensional Euclidean space.
-There is a similar operadic picture which encodes $E_{n+1}$-algebras together with their left-modules. 
-The idea is too look at configurations of disks and half-disks inside of the upper-half space $\HH^{n+1} = \{(x_1,\ldots, x_{n+1}) \; | \; x_{n+1} \geq 0\}$. 
-What results is a two-colored operad known as the $(n+1)$-dimensional Swiss cheese operad where the two colors correspond to disks and half-disks.
-
-An algebra over this colored operad can be identified with a pair of objects $(B,M)$ where $B$ is an $E_{n+1}$-algebra and $M$ is an $E_n$-algebra in the category of left $B$-modules.
-Indeed, if one restricts to the ``disk" colors we recover the data of $B$. 
-The operadic structure maps which include disks and half-disks embedded inside bigger half-disks encodes the left-module structure of $A$ on $B$.
-
-Given an $E_n$-algebra $A$ we know that $E_n$-center $\fZ_n(A)$ has the structure of an $E_{n+1}$ algebra.
-Moreover, the pair $(\fZ_{n} (A), A)$ can be given the structure of an algebra over the $(n+1)$-dimensional Swiss cheese operad. 
-In fact, $(\fZ_{n} (A), A)$ is the {\em universal} such pair.
+The $(n+1)$-dimensional Swiss cheese operad is a two-colored operad whose algebras include pairs $(B, M)$ where $B$ is an $\EE_{n+1}$-algebra, $M$ is an $\EE_n$-algebra, and where $M$ is a left-module for $B$.
+
+Geometrically, it is most constructive to view this operad as built from open sets in the upper half space $\HH^{n+1} = \{(x_1,\ldots, x_{n+1}) \; | \; x_{n+1} \geq 0\}$.
+The colors include disks and half-disks. 
+If one restricts to the ``disk" colors we recover the data of the $\EE_{n+1}$-algebra $B$. 
+The operadic structure maps which include disks and half-disks embedded inside bigger half-disks encodes the left-module structure of $B$ on $M$.
+
+The pair $(\fZ_{n} (A), A)$ can be given the structure of an algebra over the $(n+1)$-dimensional Swiss cheese operad. 
+In fact, $(\fZ_{n} (A), A)$ is the {\em universal} such pair in the sense that if $(B, A)$ is another such pair then there exists a unique (up to equivalence) map of $\EE_{n+1}$-algebras $B \to \fZ_n(A)$.
 This universality is a conjecture of \cite{Kontsevich} which was later made precise and proved in \cite{Thomas, Tamarkin, Dolgushev, jnkf others?}.
-One consequence of this \brian{universal property}
-
-Abstractly, an algebra over the $(n+1)$-dimensional Swiss cheese operad can be modeled as a {\em constructible} factorization algebra on the upper half space $\HH^{n+1}$. 
-Concretely, this is the data of a pair $(\bB, \bM)$ where $\bB$ is a locally constant factorization algebra on the ``bulk" manifold $\RR^n \times \RR_{>0}$ and $\bM$ is a locally constant factorization algebra on the boundary $\RR^n \times \{0\}$.
-
-\begin{prp}[\cite{Lurie, AF}]
-For any smooth manifold $M$ and Lie algebra $\fg$ there exists a constructible factorization algebra on $M \times \RR_{\geq 0}$ which is a model for the algebra $(\fZ_n(\fg), \UU_n(\fg))$ over the $(n+1)$-dimensional Swiss cheese operad.
-\end{prp}
+
+In this paper, we will use two models for algebras over the $(n+1)$-dimensional Swiss cheese operad. 
+The first is obtained by considering pairs of locally constant factorization algebras on an $n$-dimensional manifold.
+
+\begin{dfn}\label{dfn:pair}
+A {\em factorization pair} on a manifold $M$ is a pair $(\bB, \bM)$ where
+\begin{itemize}
+\item $\bB$ is an $\EE_1$-algebra in locally constant factorization algebras;
+\item $\bM$ is a locally constant factorization algebra together with map of $\EE_1$ factorization algebras $\bB \to \bZ_n(\bM)$.
+\end{itemize}
+\end{dfn}
+
+An immediate consequence of Theorem \ref{thm:lurie1} and Theorem \ref{thm: centralizer} is that a factorization pair on $\RR^n$ determines an algebra over the $(n+1)$-dimensional Swiss cheese operad.
+
+In the next section we will recall a different model for algebras over the $(n+1)$-dimensional Swiss cheese operad in terms of constructible factorization algebras on $(n+1)$-dimensional manifolds with boundary.
 
@@
 
-Given an $E_n$-algebra $A$ the pair $(\fZ_n (A) , A)$ is an algebra over the $(n+1)$-dimensional Swiss cheese operad. 
-The first objective is to define a certain ``classical limit" of this pair in the case that $A$ is an $E_n$-enveloping algebra.
+Given an $\EE_n$-algebra $A$, the pair $(\fZ_n (A) , A)$ is an algebra over the $(n+1)$-dimensional Swiss cheese operad. 
+The first objective is to define a certain ``classical limit" of this pair in the case that $A$ is an $\EE_n$-enveloping algebra.
 
@@
 
-The key insight is that there exists a filtration on our model for the $E_n$-center $\bZ_n(\fg)$ and the $E_n$-enveloping algebra $\bU_n (\fg)$ whose associated graded factorization algebras ${\rm Gr} \; \bZ_n(\fg)$ and ${\rm Gr} \; \bU_n(\fg)$ are {\em commutative} factorization algebras.
-
-\brian{additivity}
-
-\begin{rmk}
-By a similar proof as in the main part of the paper, we expect that one can see that the factorization algebra
-\[
-\clie \bigg(\Omega^\bu \otimes \fg \; ; \; {\rm Sym} \left(\Omega^\bu_c \otimes \fg [1] \right) \bigg)
-\]
-is a model for the {\em $\PP_n$-center} of the $\PP_n$-enveloping algebra $\UU_{\PP_n} (\fg)$. 
-\end{rmk}
-
-The associated graded pair in Proposition \ref{prp:swiss1} carries the additional Poisson-type structure.
+The key insight is that there exists a filtration on our model for the $E_n$-center $\bZ_n(\fg)$ and the $E_n$-enveloping algebra $\bU_n (\fg)$ whose associated graded factorization algebras ${\rm Gr} \; \bZ_n(\fg)$ and ${\rm Gr} \; \bU_n(\fg)$ are commutative factorization algebras.
+
+Given a filtered associative algebra whose associated graded is commutative, there exists a Poisson bracket on the associated graded algebra. 
+If the associated graded of a filtered $\EE_n$-algebra is commutative, then it carries the structure of a $\PP_n$-algebra, which is similar to a Poisson algebra except the bracket is of cohomological degree $1-n$.
+There is a similar description of the ``classical limit"  of algebras over the $(n+1)$-dimensional Swiss cheese operad in terms of algebras over a certain two-colored operad $\PP_{[n+1,n]}$, see \cite{Pavel1, Pavel2}.
+We recall the definition of this operad below.
 
@@
 
+\begin{rmk}
+By a similar proof as in the main part of the paper, we expect that one can see that the factorization algebra
+\[
+\clie \bigg(\Omega^\bu \otimes \fg \; ; \; {\rm Sym} \left(\Omega^\bu_c \otimes \fg [1] \right) \bigg)
+\]
+is a model for the {\em $\PP_n$-center} of the $\PP_n$-enveloping algebra $\UU_{\PP_n} (\fg)$. 
+\end{rmk}
+
+There is another geometric model \brian{finish}
+The idea is too look at configurations of disks and half-disks inside of the upper-half space $\HH^{n+1} = \{(x_1,\ldots, x_{n+1}) \; | \; x_{n+1} \geq 0\}$. 
+What results is a two-colored operad known as the $(n+1)$-dimensional Swiss cheese operad where the two colors correspond to disks and half-disks.
+
 There is another geometric picture for algebras over the $(n+1)$-dimensional Swiss cheese operad in terms of constructible factorization algebras on $(n+1)$-manifolds with boundary.
@@
 
-A constructible factorization algebra $\bA$ on $M \times \RR_{\geq 0}$ determines a pair of factorization algebras $(\pi_* \bA , \bA_{\partial})$ on $M$ which locally define the $E_1$-model for $(n+1)$-Swiss cheese algebras.
-
-The next goal of this section is to provide a model of the classical limit of the $E_n$-center as a constructible factorization algebra.
+A constructible factorization algebra $\bA$ on $M \times \RR_{\geq 0}$ determines a pair of factorization algebras $(\pi_* \bA , \bA_{\partial})$ on $M$ which define a factorization pair as in Definition \ref{dfn:pair}.
+
+The next goal of this section is to provide a model of the classical limit of the $\EE_n$-center as a constructible factorization algebra.
 
@@
 
-We accomplish Proposition \ref{prp:swiss1} by exhibiting a filtration at the level of strict factorization algebras in our model of the $E_n$-center.
+We prove Proposition \ref{prp:swiss1} by exhibiting a filtration at the level of strict factorization algebras in our model of the $\EE_n$-center.
 
@@
 
-Consider our factorization model for the $E_n$-enveloping algebra $\bU_n(\fg) = \clieu (\fg \otimes \Omega_c)$. 
+Consider our factorization model for the $\EE_n$-enveloping algebra $\bU_n(\fg) = \clieu (\fg \otimes \Omega_c)$. 
 The filtration on Chevalley--Eilenberg chains equips $\bU_n(\fg)$ with a filtration as a factorization algebra.
 
-There is a similar filtration on our model for the $E_n$-center $\bZ_n(\fg)$. 
-Define
+There is a similar filtration on our model for the $\EE_n$-center $\bZ_n(\fg)$ defined by
 \[
@@
 
-\brian{$\PP_0$ stuff}
+Proposition \ref{prp:swiss1} is a direct consequence of the following lemma.
+
+\begin{lmm}
+These filtrations equip the pair $(\bZ_n (\fg), \bU_n(\fg))$ with the structure of a filtered \brian{name}.
+Moreover, the associated graded pair $({\rm Gr} \; \bZ_n (\fg), {\rm Gr} \; \bU_n(\fg))$ is a commutative \brian{name}. 
+\end{lmm}
+\begin{proof}
+One has
+\[
+{\rm Gr} \; \UU_n (\fg) = {\rm Sym} \left(\fg \otimes \Omega^\bu_c [1] \right)
+\]
+and
+\[
+{\rm Gr} \; \bZ_n (\fg) = \clie^\bu\bigg(\fg \otimes \Omega^\bu \; , \; {\rm Sym} \left(\fg \otimes \Omega^\bu_c [1]\right) \bigg) 
+\]
+as factorization algebras. 
+These are both commutative by direct inspection. 
+\end{proof}
 
@@
 
-\begin{prp}
-The pair $(\bZ_n (\fg), \bU_n(\fg)$ is a filtered, \brian{not sure what we're calling this}. 
-Further, the associated graded $({\rm Gr} \; \bZ_n (\fg), {\rm Gr} \; \bU_n(\fg)$ is a $\PP_0$ \brian{not sure what we're calling this}. 
-\end{prp}
-
-It is immediate to check that this is a filtration of factorization algebras and that its associated graded has the structure of a $\PP_0$-factorization algebra.
-In fact, we have the following result, which explains the relationship to the ``bulk" $(n+1)$-dimensional factorization algebra $\Tilde{\bZ}_n(\fg)$ we introduced in the last section.
+\subsection{The bulk factorization algebra}
+
+We turn towards a model for the $\EE_n$-center as a constructible factorization algebra.
+
+\begin{dfn}
+For an open set $U \subset M \times \RR_{>0}$ let $\overset{\circ}{\bf Z}_n(\fg) (U)$ be the cochain complex 
+\[
+\overset{\circ}{\bf Z}_n(\fg) (U) = \clie \bigg(\fg \otimes \Omega (U) \; , \; \Sym \left(\fg \otimes \Omega_c(U) [2] \right) \bigg) .
+\]
+The assignment $U \mapsto \overset{\circ}{\bf Z}_n(\fg) (U)$ defines a locally constant factorization algebra on $M \times \RR_{>0}$. 
+\end{dfn}
 
@@
 \[
-\pi_* \Tilde{\bZ}_n(\fg) \; \xto{\simeq} \; {\rm Gr} \; \bZ_n(\fg) .
+\pi_* \overset{\circ}{\bf Z}_n(\fg) \; \xto{\simeq} \; {\rm Gr} \; \bZ_n(\fg) .
 \]
@@
 \begin{dfn}\label{dfn:constructible1}
-Let $(\Tilde{\bZ}_n (\fg), {\rm Gr} \bU_n(\fg))$ be the following constructible $\PP_0$-factorization algebra on $M \times \RR_{\geq 0}$:
+Let $\bC_n(\fg)$ be the following constructible $\PP_0$-factorization algebra on $M \times \RR_{\geq 0}$:
 \begin{itemize}
-\item to an open set $U \subset M \times \RR_{> 0}$, we assign the cochain complex $\Tilde{\bZ}_n (\fg)(U)$.
-\item to an open set $U \subset M \times \RR_{\geq 0}$ with $U \cap (M \times \{0\}) \ne 0$ we assign the cochain complex ${\rm Gr} \;\bU_n(\fg)(U)$. 
+\item to an open set $U \subset M \times \RR_{> 0}$, we assign the cochain complex $\overset{\circ}{\bf Z}_n (\fg)(U)$.
+\item to an open set $V \times [0,\epsilon)$ we assign the cochain complex ${\rm Gr} \;\bU_n(\fg)(V)$. 
 \end{itemize}
@@
 
-\subsection{The bulk factorization algebra}
-
-It is immediate to check that this is a filtration of factorization algebras and that its associated graded has the structure of a $\PP_0$-factorization algebra.
-In fact, we have the following result, which explains the relationship to the ``bulk" $(n+1)$-dimensional factorization algebra $\Tilde{\bZ}_n(\fg)$ we introduced in the last section.
-
- \begin{lmm}
-Let $M$ be an $n$-dimensional manifold.
-There is a quasi-isomorphism of  $\PP_0$-factorization algebras on $M$:
-\[
-\pi_* \Tilde{\bZ}_n(\fg) \; \xto{\simeq} \; {\rm Gr} \; \bZ_n(\fg) .
-\]
-where $\pi : M \times \RR_{>0} \to M$ is the projection. 
-\end{lmm}
-
-In fact, we will show that this quasi-isomorphism is a deformation retraction.
-
-\begin{proof}
-To exhibit this quasi-isomorphism, we introduce the following cochain maps.
-For an open set $U \subset M$ let
-\[
-\int_\RR : \Omega_c(U \times \RR) \to \Omega_c (U) [1] 
-\] 
-be the map which integrates a compactly supported form on $U \times \RR$ along $\RR$. 
-This map is a quasi-isomorphism for any $U $ and admits the following explicit retract. 
-Let $\phi$ be a fixed compactly supported function on $\RR$ of mass $1$ and define
-\[
-r_\phi : \Omega_c(U) [1] \to \Omega_c (U \times \RR)
-\]
-by $r_\phi (\alpha) = \alpha \wedge \phi \, \d t$. 
-\end{proof}
-
-Since the universal action of $\bZ_n(\fg)$ on $\bU_n (\fg)$ is compatible with the above filtrations, we obtain the following constructible factorization algebra on $M \times \RR_{\geq 0}$.
-
-\begin{dfn}\label{dfn:constructible1}
-Let $(\Tilde{\bZ}_n (\fg), {\rm Gr} \bU_n(\fg))$ be the following constructible $\PP_0$-factorization algebra on $M \times \RR_{\geq 0}$:
-\begin{itemize}
-\item to an open set $U \subset M \times \RR_{> 0}$, we assign the cochain complex $\Tilde{\bZ}_n (\fg)(U)$.
-\item to an open set $U \subset M \times \RR_{\geq 0}$ with $U \cap (M \times \{0\}) \ne 0$ we assign the cochain complex ${\rm Gr} \;\bU_n(\fg)(U)$. 
-\end{itemize}
-\brian{not sure how much to say about structure maps}
-\end{dfn}
-
-Let $M$ be an $n$-dimensional manifold and $\fg$ a Lie algebra.
-
-\begin{dfn}
-For an open set $U \subset M \times \RR_{>0}$ let $\Tilde{\bZ}_n(\fg) (U)$ be the cochain complex 
-\[
-\Tilde{\bZ}_n(\fg) (U) = \clie \bigg(\fg \otimes \Omega (U) \; , \; \Sym \left(\fg \otimes \Omega_c(U) [2] \right) \bigg) .
-\]
-The assignment $\Tilde{\bZ}_n(\fg) (U)$ defines a locally constant factorization algebra on $M \times \RR_{>0}$. 
-\end{dfn}
-
 On each open set $U$, the cochain complex $\Tilde{\bZ}_n(\fg) (U)$ is actually a commutative dg algebra. 
@@
 
-\begin{prp}
-$\Tilde{\bZ}_n(\fg)$ has the structure of a $\PP_0$-factorization algebra on $M \times \RR_{>0}$. 
-\end{prp}
+\begin{lmm}
+$\bC_n(\fg)$ has the structure of a constructible $\PP_0$-factorization algebra on $M \times \RR_{\geq 0}$. 
+\end{lmm}
 \begin{proof}
@@
 Let $\cA \stackrel{f}\to \cB$ be a morphism of locally constant factorization algebras on $\RR^n$ corresponding to an $E_n$-algebra map similarly denoted.
-Then by Theorems~\ref{T:En=Fac}, \ref{T:centralizer=inthom} the centralizer of $f$ is represented by the locally constant factorization algebra
+Then by Theorems~\ref{thm:lurie1}, \ref{T:centralizer=inthom} the centralizer of $f$ is represented by the locally constant factorization algebra
 ${\rm Mor}_{\Fac_{\cA}}(\cA, \cB_f)$ which is the internal mapping object  of maps from $\cA$ to $\cB_f$ in the $\infty$-category of locally constant factorization algebras on $\RR^n$ which are a $\cA$-module.

### 2020-09-07 draft.tex
changes

@@
 
-The key insight is that there exists a filtration on our model for the $E_n$-center $\bZ_n(\fg)$ and the $E_n$-enveloping algebra $\bU_n (\fg)$ whose associated graded factorization algebras ${\rm Gr} \; \bZ_n(\fg)$ and ${\rm Gr} \; \bU_n(\fg)$ are commutative factorization algebras.
+The key insight is that there exists a filtration on our model for the $\EE_n$-center $\bZ_n(\fg)$ and the $\EE_n$-enveloping algebra $\bU_n (\fg)$ whose associated graded factorization algebras ${\rm Gr} \; \bZ_n(\fg)$ and ${\rm Gr} \; \bU_n(\fg)$ are commutative factorization algebras.
 
@@
 
-There is another geometric model \brian{finish}
-The idea is too look at configurations of disks and half-disks inside of the upper-half space $\HH^{n+1} = \{(x_1,\ldots, x_{n+1}) \; | \; x_{n+1} \geq 0\}$. 
-What results is a two-colored operad known as the $(n+1)$-dimensional Swiss cheese operad where the two colors correspond to disks and half-disks.
-
-There is another geometric picture for algebras over the $(n+1)$-dimensional Swiss cheese operad in terms of constructible factorization algebras on $(n+1)$-manifolds with boundary.
-One drawback of the previous section is that we did not provide a model for the $E_n$-center of an enveloping algebra as a constructible factorization algebra on an $(n+1)$-dimensional manifold with boundary.
-
-A constructible factorization algebra $\bA$ on $M \times \RR_{\geq 0}$ determines a pair of factorization algebras $(\pi_* \bA , \bA_{\partial})$ on $M$ which define a factorization pair as in Definition \ref{dfn:pair}.
-
+%The idea is too look at configurations of disks and half-disks inside of the upper-half space $\HH^{n+1} = \{(x_1,\ldots, x_{n+1}) \; | \; x_{n+1} \geq 0\}$. 
+%What results is a two-colored operad known as the $(n+1)$-dimensional Swiss cheese operad where the two colors correspond to disks and half-disks.
+
+In the previous section, we mentioned another geometric model for algebras over the $(n+1)$-dimensional Swiss cheese operad in terms of constructible factorization algebras on $(n+1)$-manifolds with boundary.
+One drawback of the previous section is that we did not provide a model of this type for the $\EE_n$-center of an enveloping algebra. 
 The next goal of this section is to provide a model of the classical limit of the $\EE_n$-center as a constructible factorization algebra.
 
+Any constructible factorization algebra $\bA$ on $M \times \RR_{\geq 0}$ determines a factorization pair $(\pi_* \overset{\circ}{\bA} , \bA_{\partial})$ in the sense of Definition \ref{dfn:pair}.
+We recall this construction in Section \ref{sec:bulk}. 
+In particular, on the upper half space $\HH^n$, a constructible factorization algebra determines an algebra over the $(n+1)$-dimensional Swiss cheese operad.
+
 %Generally speaking, the local observables of a topological field theory on a manifold $M$ define a locally constant factorization algebra on $M$.
 
-\begin{prp}
+\begin{prp}\label{prp:pair}
 Let $M$ be a smooth $n$-dimensional manifold and $\fg$ a Lie algebra. 
@@
 \[
-(\pi_* {\bf C}_n (\fg), {\bf C}_n (\fg)_\partial)
+(\pi_* \overset{\circ}{\bf C}_n (\fg), {\bf C}_n (\fg)_\partial)
 \]
@@
 \begin{lmm}
-These filtrations equip the pair $(\bZ_n (\fg), \bU_n(\fg))$ with the structure of a filtered \brian{name}.
-Moreover, the associated graded pair $({\rm Gr} \; \bZ_n (\fg), {\rm Gr} \; \bU_n(\fg))$ is a commutative \brian{name}. 
+These filtrations equip $(\bZ_n (\fg), \bU_n(\fg))$ with the structure of a filtered factorization pair.
+Moreover, the associated graded pair $({\rm Gr} \; \bZ_n (\fg), {\rm Gr} \; \bU_n(\fg))$ is a commutative factorization pair. 
 \end{lmm}
@@
 
-\subsection{The bulk factorization algebra}
+\subsection{The bulk factorization algebra} \label{sec:bulk}
 
@@
 \begin{dfn}
-For an open set $U \subset M \times \RR_{>0}$ let $\overset{\circ}{\bf Z}_n(\fg) (U)$ be the cochain complex 
-\[
-\overset{\circ}{\bf Z}_n(\fg) (U) = \clie \bigg(\fg \otimes \Omega (U) \; , \; \Sym \left(\fg \otimes \Omega_c(U) [2] \right) \bigg) .
-\]
-The assignment $U \mapsto \overset{\circ}{\bf Z}_n(\fg) (U)$ defines a locally constant factorization algebra on $M \times \RR_{>0}$. 
+For an open set $U \subset M \times \RR_{>0}$ let $\overset{\circ}{\bC}_n(\fg) (U)$ be the cochain complex 
+\[
+\overset{\circ}{\bC}_n (\fg) (U) = \clie \bigg(\fg \otimes \Omega (U) \; , \; \Sym \left(\fg \otimes \Omega_c(U) [2] \right) \bigg) .
+\]
 \end{dfn}
 
- \begin{lmm}
-Let $M$ be an $n$-dimensional manifold.
-There is a quasi-isomorphism of  $\PP_0$-factorization algebras on $M$:
-\[
-\pi_* \overset{\circ}{\bf Z}_n(\fg) \; \xto{\simeq} \; {\rm Gr} \; \bZ_n(\fg) .
-\]
-where $\pi : M \times \RR_{>0} \to M$ is the projection. 
-\end{lmm}
-
-In fact, we will show that this quasi-isomorphism is a deformation retraction.
-
-\begin{proof}
-To exhibit this quasi-isomorphism, we introduce the following cochain maps.
-For an open set $U \subset M$ let
-\[
-\int_\RR : \Omega_c(U \times \RR) \to \Omega_c (U) [1] 
-\] 
-be the map which integrates a compactly supported form on $U \times \RR$ along $\RR$. 
-This map is a quasi-isomorphism for any $U $ and admits the following explicit retract. 
-Let $\phi$ be a fixed compactly supported function on $\RR$ of mass $1$ and define
-\[
-r_\phi : \Omega_c(U) [1] \to \Omega_c (U \times \RR)
-\]
-by $r_\phi (\alpha) = \alpha \wedge \phi \, \d t$. 
-\end{proof}
-
-Since the universal action of $\bZ_n(\fg)$ on $\bU_n (\fg)$ is compatible with the above filtrations, we obtain the following constructible factorization algebra on $M \times \RR_{\geq 0}$.
+The assignment $U \mapsto \overset{\circ}{\bC}_n(\fg)(U)$ defines a locally constant factorization algebra on $M \times \RR_{>0}$. 
+In fact, it extends to a constructible factorization algebra on $M \times \RR_{\geq 0}$ in the following way.
+
+To state the definition, we will make use of the following map of cochain complexes.
 
@@
 \begin{itemize}
-\item to an open set $U \subset M \times \RR_{> 0}$, we assign the cochain complex $\overset{\circ}{\bf Z}_n (\fg)(U)$.
+\item to an open set $U \subset M \times \RR_{> 0}$, we assign the cochain complex $\overset{\circ}{\bC}_n (\fg)(U)$.
 \item to an open set $V \times [0,\epsilon)$ we assign the cochain complex ${\rm Gr} \;\bU_n(\fg)(V)$. 
 \end{itemize}
-\brian{not sure how much to say about structure maps}
+The structure map associated to the embedding 
+\[
+U \sqcup V \times [0, \epsilon) \hookrightarrow V' \times [0,\epsilon')
+\]
+is
+\[
+\clie \bigg(\fg \otimes \Omega^\bu (U) \; , \; \Sym \left(\fg \otimes \Omega^\bu_c(U) [2] \right) \bigg) \; \otimes \;  {\rm Sym} \left(\fg \otimes \Omega^\bu_c (V) [1] \right) 
+\]
 \end{dfn}
 
-On each open set $U$, the cochain complex $\Tilde{\bZ}_n(\fg) (U)$ is actually a commutative dg algebra. 
+On each open set $U \subset M \times \RR_{\geq 0}$, the cochain complex $\bC_n(\fg) (U)$ is a commutative dg algebra. 
 In fact, it has the structure of a $\PP_0$-algebra where the $1$-shifted bracket $\{\cdot, \cdot\}$ is defined as follows.
@@
 \end{proof}
+
+Suppose $\bA$ is any constructible factorization algebra on a manifold with boundary $M \times \RR_{\geq 0}$. 
+Then, restricting to the boundary $M$, we obtain a locally constant factorization algebra that we will denote by $\bA_{\partial}$. 
+Likewise, we can restrict to the bulk $M \times \RR_{> 0}$ and pushforward along $\pi : M \times \RR_{> 0} \to M$ to obtain another locally constant factorization algebra on $M$ that we will denote by $\pi_* \overset{\circ}{\bA}$.
+It is immediate to check that $(\pi_* \overset{\circ}{\bA} , \bA_{\partial})$ form a factorization pair in the sense of Definition \ref{dfn:pair}.
+
+ \begin{lmm}
+Let $M$ be an $n$-dimensional manifold.
+There is a quasi-isomorphism of  $\PP_0$-factorization algebras on $M$:
+\[
+\pi_* \overset{\circ}{\bf Z}_n(\fg) \; \xto{\simeq} \; {\rm Gr} \; \bZ_n(\fg) .
+\]
+where $\pi : M \times \RR_{>0} \to M$ is the projection. 
+\end{lmm}
+
+In fact, we will show that this quasi-isomorphism is a deformation retraction.
+
+\begin{proof}
+To exhibit this quasi-isomorphism, we introduce the following cochain maps.
+For an open set $U \subset M$ let
+\[
+\int_\RR : \Omega_c(U \times \RR) \to \Omega_c (U) [1] 
+\] 
+be the map which integrates a compactly supported form on $U \times \RR$ along $\RR$. 
+This map is a quasi-isomorphism for any $U $ and admits the following explicit retract. 
+Let $\phi$ be a fixed compactly supported function on $\RR$ of mass $1$ and define
+\[
+r_\phi : \Omega_c(U) [1] \to \Omega_c (U \times \RR)
+\]
+by $r_\phi (\alpha) = \alpha \wedge \phi \, \d t$. 
+\end{proof}
+
+Since the universal action of $\bZ_n(\fg)$ on $\bU_n (\fg)$ is compatible with the above filtrations, we obtain the following constructible factorization algebra on $M \times \RR_{\geq 0}$.
 

### 2020-09-08 draft.tex
fixes with owen

@@
 
+\brian{notation $\EE$ and $\bE$}
+
 \subsection{Enveloping $E_n$ algebras of Lie algebras}
@@
 \[
-\bU_n \fg(V) = \cliels(\Omega^*_c(V) \otimes \fg)
+\bU_n \fg(V) = \cliels(\Omega^\bu_c(V) \otimes \fg)
 \]
@@
 \begin{itemize}
-\item $\bB$ is an $\EE_1$-algebra in locally constant factorization algebras;
-\item $\bM$ is a locally constant factorization algebra together with map of $\EE_1$ factorization algebras $\bB \to \bZ_n(\bM)$.
+\item $\bB$ is an associative algebra in locally constant factorization algebras;
+\item $\bM$ is a locally constant factorization algebra together with map $\bB \to \bZ_n(\bM)$ of associative algebras in factorization algebras.
 \end{itemize}
+\brian{add remark about 1 categorical notion}
 \end{dfn}
@@
 
-\owen{Somewhere please mention that the slogan ``quantization commutes with pushforward'' holds for this class of theories.}
-
 Given an $\EE_n$-algebra $A$, the pair $(\fZ_n (A) , A)$ is an algebra over the $(n+1)$-dimensional Swiss cheese operad. 
@@
 \begin{prp} \label{prp:swiss1}
-Let $\fg$ be a Lie algebra. 
+Let $\fg$ be an $L_\infty$ algebra. 
 The pair $(\fZ_n(\fg) , \UU_n(\fg))$ is a filtered object in the $\infty$-category of algebras over the $(n+1)$-dimensional Swiss cheese operad. 
@@
 
-The key insight is that there exists a filtration on our model for the $\EE_n$-center $\bZ_n(\fg)$ and the $\EE_n$-enveloping algebra $\bU_n (\fg)$ whose associated graded factorization algebras ${\rm Gr} \; \bZ_n(\fg)$ and ${\rm Gr} \; \bU_n(\fg)$ are commutative factorization algebras.
+The key insight is that there exists a filtration on our model $\bZ_n(\fg)$ for the $\EE_n$-center and our model $\bU_n (\fg)$ for the $\EE_n$-enveloping algebra  whose associated graded factorization algebras ${\rm Gr} \; \bZ_n(\fg)$ and ${\rm Gr} \; \bU_n(\fg)$ are commutative factorization algebras.
 
@@
 If the associated graded of a filtered $\EE_n$-algebra is commutative, then it carries the structure of a $\PP_n$-algebra, which is similar to a Poisson algebra except the bracket is of cohomological degree $1-n$.
-There is a similar description of the ``classical limit"  of algebras over the $(n+1)$-dimensional Swiss cheese operad in terms of algebras over a certain two-colored operad $\PP_{[n+1,n]}$, see \cite{Pavel1, Pavel2}.
-We recall the definition of this operad below.
+There is a similar description of the ``classical limit"  of algebras over the $(n+1)$-dimensional Swiss cheese operad in terms of algebras over a certain two-colored operad $\PP_{[n+1,n]}$, introduced by Safronov \cite{Pavel1, Pavel2}, whose definition we recall below.
 
@@
 \[
-\clie \bigg(\Omega^\bu \otimes \fg \; ; \; {\rm Sym} \left(\Omega^\bu_c \otimes \fg [1] \right) \bigg)
+\clies \bigg(\Omega^\bu \otimes \fg \; ; \; {\rm Sym} \left(\Omega^\bu_c \otimes \fg [1] \right) \bigg)
 \]
@@
 
-Any constructible factorization algebra $\bA$ on $M \times \RR_{\geq 0}$ determines a factorization pair $(\pi_* \overset{\circ}{\bA} , \bA_{\partial})$ in the sense of Definition \ref{dfn:pair}.
+Any constructible factorization algebra $\bA$ on $M \times \RR_{\geq 0}$ determines a factorization pair $(\bA^\circ , \bA^{\partial})$ in the sense of Definition \ref{dfn:pair}.
 We recall this construction in Section \ref{sec:bulk}. 
@@
 \[
-(\pi_* \overset{\circ}{\bf C}_n (\fg), {\bf C}_n (\fg)_\partial)
-\]
-is equivalent to the pair $({\rm Gr} \; \bZ_n(\fg), {\rm Gr} \; \bU_n(\fg))$ as commutative factorization algebras \brian{adjectives}
+\left( {\bf C}_n (\fg)^\circ \; , \; {\bf C}_n (\fg)^\partial \right)
+\]
+is equivalent to the pair $({\rm Gr} \; \bZ_n(\fg), {\rm Gr} \; \bU_n(\fg))$ as a commutative factorization pair.
 \end{prp}
@@
 
-Following the proof of this proposition, our main thrust is to interpret this result by exhibiting a topological field theory on the $(n+1)$-dimensional manifold with boundary $M \times \RR_{\geq 0}$ whose factorization algebra of classical observables is precisely the constructible factorization algebra in (\ref{eqn:graded}).
-
-The Batalin--Vilkovisky (BV) formalism for studying quantum field theory \brian{finish}
-
-\brian{as a corollary butson-yoo}
+Following the proof of this proposition, our main thrust is to interpret this result by exhibiting a topological field theory on the $(n+1)$-dimensional manifold with boundary $M \times \RR_{\geq 0}$ whose factorization algebra of classical observables is equivalent to the constructible factorization algebra $\bC_n(\fg)$.
+\brian{improve this pointer}
+\owen{Somewhere please mention that the slogan ``quantization commutes with pushforward'' holds for this class of theories.}
+
+%The Batalin--Vilkovisky (BV) formalism for studying quantum field theory \brian{finish}
+%
+%\brian{as a corollary butson-yoo}
 
@@
 
-For any dg Lie (in fact, $L_\infty$) algebra, the Chevalley--Eilenberg cochain complex computing Lie algebra homology admits a natural filtration whose associated graded has the structure of a commutative dg algebra.
-If $\fh$ is a dg Lie algebra, let $\clieu_{\leq k} (\fh)$ be the subcomplex of Chevalley--Eilenberg chains which is $\Sym^{\leq k} (\fh[1])$ as an underlying graded vector space. 
+For any $L_\infty$ algebra, the Chevalley--Eilenberg cochain complex computing Lie algebra homology admits a natural filtration whose associated graded has the structure of a commutative dg algebra.
+If $\fh$ is an $L_\infty$ algebra, let $\clieu_{\leq k} (\fh)$ be the subcomplex of Chevalley--Eilenberg chains which is $\Sym^{\leq k} (\fh[1])$ as an underlying graded vector space. 
 The associated graded cochain complex is the free symmetric algebra on $\fh[1]$ thought of as simply a cochain complex:
 \[
-{\rm Gr} \; \clieu (\fh) = {\rm Sym} (\fh [1])  .
+{\rm Gr} \; \cliels (\fh) = {\rm Sym} (\fh [1])  .
 \]
@@
 \[
-F^k \bZ_n(\fg) = \clie \bigg(\fg \otimes \Omega \; , \; \clieu_{\leq k} (\fg \otimes \Omega_c) \bigg) .
+F^k \bZ_n(\fg) = \clies \bigg(\fg \otimes \Omega \; , \; \clieu_{\leq k} (\fg \otimes \Omega_c) \bigg) .
 \]
@@
 
+\brian{define $\PP_0$ factorization algebra}
+
 The associated graded commutative factorization algebras ${\rm Gr} \; \bU_n (\fg)$ and ${\rm Gr} \; \bZ_n(\fg)$ lift to $\PP_0$-factorization algebras.
@@
 \begin{dfn}
-For an open set $U \subset M \times \RR_{>0}$ let $\overset{\circ}{\bC}_n(\fg) (U)$ be the cochain complex 
-\[
-\overset{\circ}{\bC}_n (\fg) (U) = \clie \bigg(\fg \otimes \Omega (U) \; , \; \Sym \left(\fg \otimes \Omega_c(U) [2] \right) \bigg) .
-\]
-\end{dfn}
-
-The assignment $U \mapsto \overset{\circ}{\bC}_n(\fg)(U)$ defines a locally constant factorization algebra on $M \times \RR_{>0}$. 
-In fact, it extends to a constructible factorization algebra on $M \times \RR_{\geq 0}$ in the following way.
-
-To state the definition, we will make use of the following map of cochain complexes.
-
-\begin{dfn}\label{dfn:constructible1}
-Let $\bC_n(\fg)$ be the following constructible $\PP_0$-factorization algebra on $M \times \RR_{\geq 0}$:
+\label{dfn:constructible1}
+Let $\bC_n(\fg)$ be the following constructible factorization algebra on $M \times \RR_{\geq 0}$:
 \begin{itemize}
-\item to an open set $U \subset M \times \RR_{> 0}$, we assign the cochain complex $\overset{\circ}{\bC}_n (\fg)(U)$.
-\item to an open set $V \times [0,\epsilon)$ we assign the cochain complex ${\rm Gr} \;\bU_n(\fg)(V)$. 
+\item to an open set $U \subset M \times \RR_{> 0}$, we assign the cochain complex 
+\[
+\bC_n (\fg) (U) = \clies \bigg(\fg \otimes \Omega (U) \; , \; \Sym \left(\fg \otimes \Omega_c(U) [2] \right) \bigg) .
+\]
+\item to an open set $V \times [0,\epsilon)$ we assign the cochain complex 
+\[
+\bC_n (\fg) (V \times [0,\epsilon)) = {\rm Sym} \left(\fg \otimes \Omega^\bu_c (V \times [0,\epsilon) [2] \right).
+\]
 \end{itemize}
@@
 \[
-\clie \bigg(\fg \otimes \Omega^\bu (U) \; , \; \Sym \left(\fg \otimes \Omega^\bu_c(U) [2] \right) \bigg) \; \otimes \;  {\rm Sym} \left(\fg \otimes \Omega^\bu_c (V) [1] \right) 
-\]
+\clies \bigg(\fg \otimes \Omega^\bu (U) \; , \; \Sym \left(\fg \otimes \Omega^\bu_c(U) [2] \right) \bigg) \; \otimes \;  {\rm Sym} \left(\fg \otimes \Omega^\bu_c (V\times [0,\epsilon)) [2] \right) 
+\]
+\brian{finish}
 \end{dfn}
@@
 \[
-{\rm Sym} \left(\fg^* \otimes \Bar{\Omega}_c (U) [n-1] \right) \; \Hat{\otimes} \; {\rm Sym}  \left(\fg \otimes \Omega_c(U) [2] \right)  .
-\]
+{\rm Hom}^\bu\left(\Sym(\fg \otimes \Omega^\bu (U)[1]) \; , \; {\rm Sym}  \left(\fg \otimes \Omega^\bu_c(U) [2] \right) \right)  .
+\]
+\brian{explain notation with homs} 
 Let $x^* \otimes \alpha$ denote an element of $\fg \otimes \Bar{\Omega}_c (U)$ and $y \otimes \beta$ denote an element of $\fg \otimes \Omega_c(U) [2]$. 
-Then, the bracket involving the linear elements $(x^* \otimes \alpha) \otimes 1$ and $1 \otimes (y \otimes \beta)$ is defined by
+Then, the bracket involving the linear elements $(x^* \otimes \alpha) \otimes 1$ 
+and $1 \otimes (y \otimes \beta)$ is defined by
 \begin{align*}
@@
 
+Next, we provide a construction of a factorization pair on the manifold $M$ from that data of a constructible factorization algebra on $M \times \RR_{\geq 0}$. 
 Suppose $\bA$ is any constructible factorization algebra on a manifold with boundary $M \times \RR_{\geq 0}$. 
-Then, restricting to the boundary $M$, we obtain a locally constant factorization algebra that we will denote by $\bA_{\partial}$. 
-Likewise, we can restrict to the bulk $M \times \RR_{> 0}$ and pushforward along $\pi : M \times \RR_{> 0} \to M$ to obtain another locally constant factorization algebra on $M$ that we will denote by $\pi_* \overset{\circ}{\bA}$.
-It is immediate to check that $(\pi_* \overset{\circ}{\bA} , \bA_{\partial})$ form a factorization pair in the sense of Definition \ref{dfn:pair}.
+Let $\pi : M \times \RR_{\geq 0} \to M$ be the projection and denote by $\pi|_{M \times \RR_{>0}}$ its restriction to the interior. 
+Define the following two factorization algebras on $M$:
+\begin{align*}
+\bA^\circ & = \left(\left.\pi\right|_{M \times \RR_{>0}} \right)_* \bA \\
+\bA^\partial & = \pi_* \bA
+\end{align*}
+It is immediate to check that $(\bA^\circ, \bA^\partial)$ form a factorization pair in the sense of Definition \ref{dfn:pair}. 
+In fact, this construction determines a functor from the category of constructible factorization algebras on $M \times \RR_{\geq 0}$ to factorization pairs on $M$.
 
  \begin{lmm}
+ \brian{fix notation}
 Let $M$ be an $n$-dimensional manifold.
@@
 \subsection{Bulk-boundary topological field theory}
+
+\brian{intro paragraph}
 
@@
 The observables, or functions on the classical space of fields is then equipped with the structure of a $\PP_0$-factorization algebra.
+
+\brian{maybe say AKSZ here}
 
@@
 
-For any Lie algebra $\fg$, there is a topological field theory defined in any dimension known as ``topological BF theory". 
+For any Lie algebra $\fg$, there is a topological field theory defined in any dimension known as {\em topological BF theory}.
 Suppose $N$ is an $(n+1)$-dimensional manifold, which for now we assume has no boundary $\partial N = \emptyset$. 
-In the BV formalism, the perturbative space of fields of BF theory on $N$ consists of
+In the BV formalism, the perturbative space of fields of topological $BF$ theory on $N$ consists of
 \[
@@
 \]
+Concretely, the classical moduli space consists of pairs $(A, B)$ where $A \in \Omega^1 (N) \otimes \fg$ and $B \in \Omega^{n-1} (N) \otimes \fg^*$ satisfying the equations
+\begin{align*}
+\d A + \frac12 [A,A] & = 0 \\
+\d B + [A,B] & = 0 .
+\end{align*}
 When $N$ is compact, the classical moduli space underlying this field theory has an elegant description in terms of the AKSZ formalism. 
@@
 Perturbative BF theory is obtained by taking the tangent space of the above mapping stack near at the trivial $G$-bundle.
-Concretely, the classical moduli space consists of pairs $(A, B)$ where $A \in \Omega^1 (N) \otimes \fg$ and $B \in \Omega^{n-1} (N) \otimes \fg^*$ satisfying the equations
-\begin{align*}
-\d A + \frac12 [A,A] & = 0 \\
-\d B + [A,B] & = 0 .
-\end{align*}
 
@@
 \[
-{\rm Map}(\partial N , {\rm T}^* [n] {\rm B} G)
+{\rm Map}(\partial N_{\rm dR} , {\rm T}^* [n] {\rm B} G)
 \]
@@
 \item[(1)] 
-The bulk theory is that of topological BF theory on $M \times \RR_{>0}$, where the space of fields is 
+The bulk theory is topological BF theory on $M \times \RR_{>0}$, where the space of fields is 
 \[
@@
 \item[(2)] 
-The boundary condition is determined by the subspace of the fields on the boundary
+The boundary condition is the Lagrangian subspace
 \[
@@
 \begin{prp}
-The constructible $\PP_0$-factorization algebra of topological BF theory with its universal Neumann boundary condition is equivalent to the constructible factorization algebra $(\Tilde{\bZ}_n (\fg), {\rm Gr} \bU_n (\fg))$ of Definition \ref{dfn:constructible1}.
+The constructible $\PP_0$-factorization algebra of topological BF theory with its universal Neumann boundary condition is equivalent to the constructible factorization algebra $\bC_n(\fg)$. 
 \end{prp}
+
+\begin{rmk} Examples
+
+Poisson $\sigma$-model. 
+$B$-model. 
+cite paper with Eugene.
+Kapustin-Witten. 
+\end{rmk}
+
+\subsection{Factorization homology on manifolds with boundary}
 

### 2020-09-08 draft.tex
not sure what i did

--- 2020-09-07 draft.tex
@@
 Recently, a generalization of the concept of the enveloping algebra of a Lie algebra has emerged: 
-each dg Lie algebra $\fg$ has an enveloping $E_n$ algebra $\UU_n\fg$, for every $n$, 
+each dg Lie algebra $\fg$ has an enveloping $\EE_n$ algebra $\UU_n\fg$, for every $n$, 
 so that $\UU_1\fg$ is the usual enveloping algebra $U\fg$. 
 Building on prior work \cite{BD, AF} [Owen's thesis?], 
-Knudsen \cite{Knudsen} developed these ideas extensively and offered a useful factorization algebra model for the enveloping $E_n$ algebra. 
+Knudsen \cite{Knudsen} developed these ideas extensively and offered a useful factorization algebra model for the enveloping $\EE_n$ algebra. 
 Our central goal here is to generalize the some well-known results about the enveloping algebra $U\fg$ to $\UU_n\fg$, for all $n$, such as
@@
 %Our primary tool here is the Loday-Quillen-Tsygan (LQT) theorem which describes the large $N$ limit of the Lie algebra homology of $\gl_N(A)$, for a dg associative algebra $A$.
-Since the enveloping $E_n$ algebra of a Lie algebra can be constructed as a locally constant factorization algebra made out of the shifted Chevalley-Eilenberg chains \cite{}, the relevance of the LQT theorem in this context  should be apparent.
-From this point of view, one can think of our main result as an $E_n$ generalization of the LQT theorem.
+Since the enveloping $\EE_n$ algebra of a Lie algebra can be constructed as a locally constant factorization algebra made out of the shifted Chevalley-Eilenberg chains \cite{}, the relevance of the LQT theorem in this context  should be apparent.
+From this point of view, one can think of our main result as an $\EE_n$ generalization of the LQT theorem.
 We hope these ideas have exciting applications in quantum field theory and random matrix theory, as well as to other large $N$ limit phenomena.
@@
 
-See section~\ref{sec: en background} for a brief discussion of $E_n$ algebras and their relationship with locally constant factorization algebras on $\RR^n$, section~\ref{sec: enveloping} for a brief discussion of the enveloping $E_n$ algebra construction, and see section~\ref{sec: centralizer}
-for a brief discussion about centralizers to maps of $E_n$ algebras.
+See section~\ref{sec: en background} for a brief discussion of $\EE_n$ algebras and their relationship with locally constant factorization algebras on $\RR^n$, section~\ref{sec: enveloping} for a brief discussion of the enveloping $\EE_n$ algebra construction, and see section~\ref{sec: centralizer}
+for a brief discussion about centralizers to maps of $\EE_n$ algebras.
 
@@
 Even to state our central result, we need to review a few results and terminology.
-First, our basic context is $E_n$ algebras.
-By $E_n$ we mean any operad or colored operad or $\infty$-operad equivalent to the topological operad of little $n$-disks in $\RR^n$, where the notion of equivalence is in some appropriate $\infty$-categorical setting of operads.
+First, our basic context is $\EE_n$ algebras.
+By $\EE_n$ we mean any operad or colored operad or $\infty$-operad equivalent to the topological operad of little $n$-disks in $\RR^n$, where the notion of equivalence is in some appropriate $\infty$-categorical setting of operads.
 In particular, we will require that its $\infty$-category of algebras in $\Ch_k^{\otimes_k}$ agree with those of the little $n$-disks operad. 
@@
 
-Many notions from ordinary algebra admit natural generalizations to $E_n$ algebras.
+Many notions from ordinary algebra admit natural generalizations to $\EE_n$ algebras.
 For instance, to each Lie algebra $\fg$ (and more generally $L_\infty$ algebra),
-there is an {\em enveloping $E_n$ algebra} $\UU_n \fg$, thanks to \cite{Knudsen}.
-Similarly, every $E_n$ algebra $A$ has a {\em center} ${\frak Z}_n(A)$, which is an $E_{n+1}$ algebra and hence more commutative than~$A$.
-More generally, for any map of $E_n$ algebras $f: A \to B$, there is a {\em centralizer} ${\frak Z}_n(f)$, 
+there is an {\em enveloping $\EE_n$ algebra} $\UU_n \fg$, thanks to \cite{Knudsen}.
+Similarly, every $\EE_n$ algebra $A$ has a {\em center} ${\frak Z}_n(A)$, which is an $E_{n+1}$ algebra and hence more commutative than~$A$.
+More generally, for any map of $\EE_n$ algebras $f: A \to B$, there is a {\em centralizer} ${\frak Z}_n(f)$, 
 which is a generalization of the commutant.
@@
 
-Our work here relies on a concrete and convenient model for these enveloping $E_n$ algebras by factorization algebras.
+Our work here relies on a concrete and convenient model for these enveloping $\EE_n$ algebras by factorization algebras.
 In particular, thanks again to \cite{Knudsen}, 
-we know that the $E_n$ enveloping algebra $\UU_n \fg$ admits a model $\bU_n \fg$ whose underlying functor on the poset of open sets in $\RR^n$ assigns $\cliels(\Omega_c^*(V) \otimes \fg)$ to each open set~$V$.
+we know that the $\EE_n$ enveloping algebra $\UU_n \fg$ admits a model $\bU_n \fg$ whose underlying functor on the poset of open sets in $\RR^n$ assigns $\cliels(\Omega_c^*(V) \otimes \fg)$ to each open set~$V$.
 There is another factorization algebra whose underlying assigns $\clies(\Omega^*(V) \otimes \fg)$ to each open~$V$.
-Our paper shows that such factorization algebras model other important $E_n$ algebras, notably centralizers.
+Our paper shows that such factorization algebras model other important $\EE_n$ algebras, notably centralizers.
 
@@
 (i.e., a map of conilpotent cocommutative coalgebras $f: \cliels(\fg) \to \cliels(\fh)$).
-This map determines functorially a map of $E_n$ algebras
+This map determines functorially a map of $\EE_n$ algebras
 \[
@@
 \]
-between their enveloping $E_n$ algebras.
-The centralizer of this map ${\frak Z}_n(\UU_n f)$ is an $E_n$-algebra modeled by the factorization algebra 
+between their enveloping $\EE_n$ algebras.
+The centralizer of this map ${\frak Z}_n(\UU_n f)$ is an $\EE_n$-algebra modeled by the factorization algebra 
 \[
@@
 
-\owen{I think we could (and maybe should) also discuss the $E_n$-Koszul dual situation involving cochains.}
+\owen{I think we could (and maybe should) also discuss the $\EE_n$-Koszul dual situation involving cochains.}
 
@@
 \begin{itemize}
-\item Lurie \cite{LurieHA} explains why the $\infty$-category of $E_n$ algebras is equivalent to the homotopy-coherent version of locally constant prefactorization algebras on $\RR^n$.  
+\item Lurie \cite{LurieHA} explains why the $\infty$-category of $\EE_n$ algebras is equivalent to the homotopy-coherent version of locally constant prefactorization algebras on $\RR^n$.  
 In fact, he simplifies the situation a bit more. 
@@
 One can work with locally constant, homotopy-coherent $\Disk_n^\sqcup$-algebras.
-\item Knudsen verifies that we can model the enveloping $E_n$ algebra by the factorization algebra $\bU_n \fg$ described earlier.
-\item Francis and Lurie give a characterization of the centralizer ${\frak Z}_n(f)$ of any $E_n$ algebra map $\phi: A \to B$ as the ``internal hom'' in left $\int_{S^{n-1}}A$-modules from $A$ to $B_\phi$, where $B_\phi$ denotes $B$ viewed as a left module via the map~$\phi$.
+\item Knudsen verifies that we can model the enveloping $\EE_n$ algebra by the factorization algebra $\bU_n \fg$ described earlier.
+\item Francis and Lurie give a characterization of the centralizer ${\frak Z}_n(f)$ of any $\EE_n$ algebra map $\phi: A \to B$ as the ``internal hom'' in left $\int_{S^{n-1}}A$-modules from $A$ to $B_\phi$, where $B_\phi$ denotes $B$ viewed as a left module via the map~$\phi$.
 \item In combination, the centralizer is characterized up to quasi-isomorphism, 
@@
 \end{enumerate}
-Hence it induces a weak equivalence of the associated factorization algebras and hence as $E_n$ algebras.
+Hence it induces a weak equivalence of the associated factorization algebras and hence as $\EE_n$ algebras.
 
@@
 \label{thm: center}
-The center ${\frak Z}_n(\fg)$ of the enveloping $E_n$ algebra $\UU_n\fg$ is the $E_n$ algebra $\clies(\fg, \UU_n\fg)$. 
+The center ${\frak Z}_n(\fg)$ of the enveloping $\EE_n$ algebra $\UU_n\fg$ is the $\EE_n$ algebra $\clies(\fg, \UU_n\fg)$. 
 When $k$ is $\RR$ or $\CC$, the 
@@
 
-If $\epsilon: \fg \to 0$ is the trivial map, then we obtain the canonical augmentation $\epsilon: \UU_n \fg \to k$ of $E_n$ algebras.
+If $\epsilon: \fg \to 0$ is the trivial map, then we obtain the canonical augmentation $\epsilon: \UU_n \fg \to k$ of $\EE_n$ algebras.
 In this case, we obtain a version of Koszul duality as the corollary.
@@
 \label{thm: koszul duality}
-The centralizer of the augmentation $\epsilon: \UU_n \fg \to k$ is equivalent to $\clies(\fg)$ viewed as an $E_n$ algebra. It is modeled by the locally constant factorization algebra that assigns
+The centralizer of the augmentation $\epsilon: \UU_n \fg \to k$ is equivalent to $\clies(\fg)$ viewed as an $\EE_n$ algebra. It is modeled by the locally constant factorization algebra that assigns
 \[
@@
 \item When $n=1$, unpack in detail how the convolution picture matches the classic view of Koszul duality for associative (co)algebras.
-\item Consider $\fg$ {\em abelian} for arbitrary $n$ and compare to the $E_n$ HKR theorem.
-\item Compare with $E_n$ HKR theorem for $\clies(\fg)$ via $E_n$ Koszul duality.
+\item Consider $\fg$ {\em abelian} for arbitrary $n$ and compare to the $\EE_n$ HKR theorem.
+\item Compare with $\EE_n$ HKR theorem for $\clies(\fg)$ via $\EE_n$ Koszul duality.
 \item Use these facts to compute factorization homology of centralizers on manifolds with boundary --- kind of like Chern-Simons states!
@@
 
-Having an explicit presentation for the centralizer of a map of $E_n$ algebras leads to a calculation of factorization homology.
-The enveloping $E_n$ algebra is the homotopy $O(n)$-fixed points, or a $\mathrm{Disk}_n$-algebra in the sense of~\cite{AF},
+Having an explicit presentation for the centralizer of a map of $\EE_n$ algebras leads to a calculation of factorization homology.
+The enveloping $\EE_n$ algebra is the homotopy $O(n)$-fixed points, or a $\mathrm{Disk}_n$-algebra in the sense of~\cite{AF},
 and hence determines a factorization algebra on any un-oriented $n$-dimensional manifold \cite{Knudsen}.
@@
 
-\greg{Somewhere we should recall that $\UU_n$ and its center are unoriented $E_n$-algebras and define factorization algebras over any manifold that came from the formula}
+\greg{Somewhere we should recall that $\UU_n$ and its center are unoriented $\EE_n$-algebras and define factorization algebras over any manifold that came from the formula}
 
@@
 
-\subsection{Recollections on $E_n$ algebras and prefactorization algebras}
+\subsection{Recollections on $\EE_n$ algebras and prefactorization algebras}
 \label{sec: en background}
@@
 \label{thm:lurie1} 
-There is an equivalence of $\infty$-categories between $E_n$-algebras and locally constant prefactorization algebras on~$\RR^n$. 
+There is an equivalence of $\infty$-categories between $\EE_n$-algebras and locally constant prefactorization algebras on~$\RR^n$. 
 \end{thm}
@@
 
-\subsection{Enveloping $E_n$ algebras of Lie algebras}
+\subsection{Enveloping $\EE_n$ algebras of Lie algebras}
 \label{sec: enveloping}
 
-Although \cite{Knudsen} develops an adjunction between Lie and $E_n$ algebras \mahmoud{non-unital?}\greg{Both I think}\owen{augmented is probably best for us}
+Although \cite{Knudsen} develops an adjunction between Lie and $\EE_n$ algebras \mahmoud{non-unital?}\greg{Both I think}\owen{augmented is probably best for us}
 in any presentable symmetric monoidal stable $\infty$-category $\cC$,
@@
 \begin{tikzcd}
-\Alg_\Lie(\Mod_k) \arrow[r, bend left=20, shift left=.5ex,"\UU_n"] \arrow[dd] & \Alg_{E_n}(\Mod_k) \arrow[l, shift left=.5ex, "\oblv_n"] \arrow[dd]\\
+\Alg_\Lie(\Mod_k) \arrow[r, bend left=20, shift left=.5ex,"\UU_n"] \arrow[dd] & \Alg_{\EE_n}(\Mod_k) \arrow[l, shift left=.5ex, "\oblv_n"] \arrow[dd]\\
 &\\
-\Mod_k \arrow[r, bend left=20, shift left=.5ex, "\Sigma^{1-n}"] \arrow[uu, bend left=20, shift left=.5ex, "\Free_\Lie"] & \Mod_k \arrow[l, shift left=.5ex,"\Sigma^{n-1}"] \arrow[uu, bend right=20, shift right=.5ex, "\Free_{E_n}"']
+\Mod_k \arrow[r, bend left=20, shift left=.5ex, "\Sigma^{1-n}"] \arrow[uu, bend left=20, shift left=.5ex, "\Free_\Lie"] & \Mod_k \arrow[l, shift left=.5ex,"\Sigma^{n-1}"] \arrow[uu, bend right=20, shift right=.5ex, "\Free_{\EE_n}"']
 \end{tikzcd}
@@
 When $k$ is $\RR$ or $\CC$, 
-the enveloping $E_n$ algebra $\UU_n \fg$ of a dg Lie algebra $\fg$ is modeled by the locally constant factorization algebra $\bU_n \fg$ that assigns
+the enveloping $\EE_n$ algebra $\UU_n \fg$ of a dg Lie algebra $\fg$ is modeled by the locally constant factorization algebra $\bU_n \fg$ that assigns
 \[
@@
 \begin{rmk}
-It follows from theorem~\ref{T:UnofLie} that for any $E_n$-algebra $B$, 
+It follows from theorem~\ref{T:UnofLie} that for any $\EE_n$-algebra $B$, 
 its underlying complex is equipped with a homotopy-coherent Lie algebra structure.
@@
 
-\subsection{Centralizers of maps of $E_n$ algebras and the derived center}
+\subsection{Centralizers of maps of $\EE_n$ algebras and the derived center}
 \label{sec: centralizer}
@@
 \begin{dfn}\label{D:centralizer}
-For a map $f: A \to B$ of $E_n$ algebras in $\cC$, 
-the {\em centralizer} ${\frak Z}_n(f)$ is the $E_n$ algebra in $\cC$ that is universal among those that fit in a commuting diagram
+For a map $f: A \to B$ of $\EE_n$ algebras in $\cC$, 
+the {\em centralizer} ${\frak Z}_n(f)$ is the $\EE_n$ algebra in $\cC$ that is universal among those that fit in a commuting diagram
 \[
@@
 where the arrow in the upper left is the tensor product of the unit map $u: 1_\cC \to {\frak Z}_n(f)$ and the identity map $\id: A \to A$.
-The {\em center} of an $E_n$ algebra $A$ is the centralizer of its identity morphism $\id_A: A \to A$. 
+The {\em center} of an $\EE_n$ algebra $A$ is the centralizer of its identity morphism $\id_A: A \to A$. 
 We  denote it ${\frak Z}_n(A) := {\frak Z}_n(\id_A)$.
@@
 \label{T:centralizer=inthom} 
-The centralizer ${\frak Z}_n(f)$ exists and can be identified with the classifying object for maps from $A$ to $B$ in the $\infty$-category $\Mod^{E_n}_A(\cC)$.
+The centralizer ${\frak Z}_n(f)$ exists and can be identified with the classifying object for maps from $A$ to $B$ in the $\infty$-category $\Mod^{\EE_n}_A(\cC)$.
 \mahmoud{we should probably spell out the meaning of the classifying object in this case to make it obvious that the centralizer is the classifying object}
@@
 Let $\cC^\otimes$ be a presentable symmetric monoidal stable $\infty$-category whose tensor product preserves colimits in each variable separately.
-For $A$ be an $E_n$ algebra in $\cC$,
-the $\infty$-category $\Mod^{E_n}_A(\cC)$ is equivalent to the $\infty$-category $\LMod_{{\int_{S^{n-1}} A}}(\cC)$.
+For $A$ be an $\EE_n$ algebra in $\cC$,
+the $\infty$-category $\Mod^{\EE_n}_A(\cC)$ is equivalent to the $\infty$-category $\LMod_{{\int_{S^{n-1}} A}}(\cC)$.
 \end{prp}
@@
 See Remark 7.3.5.3 of \cite{LurieHA}, Corollary 13 in~\cite{GG-Notes} and Section 2 of \cite{FrancisHH}.
-Concretely, this claim arises from the fact that as a module over $A$ as an $E_n$ algebra, 
-$M \in \Mod^{E_n}_A(\cC)$ is equipped with a commuting family of actions by $A$ parametrized by $\RR^n \setminus \{0\}\cong S^{n-1} \times \RR_{>0}$.
+Concretely, this claim arises from the fact that as a module over $A$ as an $\EE_n$ algebra, 
+$M \in \Mod^{\EE_n}_A(\cC)$ is equipped with a commuting family of actions by $A$ parametrized by $\RR^n \setminus \{0\}\cong S^{n-1} \times \RR_{>0}$.
 This action factors through the left action of the $E_1$ algebra $\int_{S^{n-1} \times \RR_{>0}} A$ arising from factorization homology over the complement of the origin,
@@
 this algebra $\int_{S^{n-1} \times \RR} A$ is equivalent to ${\rm Free}(1_\cC)$, 
-the image of the unit object $1_\cC \in \cC$ under the left adjoint ${\rm Free}$ to the forgetful functor $\Mod^{E_n}_A(\cC) \to \cC$.
+the image of the unit object $1_\cC \in \cC$ under the left adjoint ${\rm Free}$ to the forgetful functor $\Mod^{\EE_n}_A(\cC) \to \cC$.
 
@@
 As we work in the setting of factorization algebras on $\RR^n$, 
-we will use bold font to indicate such factorization models for $E_n$ algebra statements.
-For instance, we use $\bU_n \fg$ for the factorization model of the enveloping $E_n$ algebra,
-and we use ${\bf f}: \bU_n \fg \to \bU_n \fh$ for the factorization model of the map $f: \UU_n \fg \to \UU_n \fh$ of $E_n$ algebras.
+we will use bold font to indicate such factorization models for $\EE_n$ algebra statements.
+For instance, we use $\bU_n \fg$ for the factorization model of the enveloping $\EE_n$ algebra,
+and we use ${\bf f}: \bU_n \fg \to \bU_n \fh$ for the factorization model of the map $f: \UU_n \fg \to \UU_n \fh$ of $\EE_n$ algebras.
 
@@
 \[
-\cliels(\fg \times \fh) = \cliels(\fg) \otimes \cliels(\fh),
+\cliels(\fg_1 \times \fg_2) = \cliels(\fg_1) \otimes \cliels(\fg_2),
 \]
@@
 In this sense, we see how $\clies(\fg,\cliels(\fh)_f)$ encodes deformations of~$f$.
+
+\owen{Probably need to mention somewhere that it's better to work with $\clies(\fg)$ as a completed object.}
 
@@
 \begin{align*}
-{\frak Z}_n(f) &\simeq {{\rm Mor}}_{\Mod^{E_n}_{\UU_n\fg}}(\UU_n \fg, (\UU_n \fh)_f) \\
+{\frak Z}_n(f) &\simeq {{\rm Mor}}_{\Mod^{\EE_n}_{\UU_n\fg}}(\UU_n \fg, (\UU_n \fh)_f) \\
 &\simeq {\rm Mor}_{\LMod_{\int_{S^{n-1}} \UU_n\fg}}(\UU_n \fg, (\UU_n \fh)_f)
@@
 \begin{itemize}
-\item $(\UU_n \fh)_f$ denotes the object in $\Mod^{E_n}_{\UU_n\fg}$ --- equivalently, in $\LMod_{\int_{S^{n-1}}\UU_n}$ --- determined by~$f$, 
-\item ${\rm Mor}_{\Mod^{E_n}_{\UU_n\fg}}(\UU_n \fg, (\UU_n \fh)_f)$ denotes the classifying object for maps (i.e.
-an internal mapping object) from $\UU_n\fg$ to $(\UU_n \fh)_f$ in the $\infty$-category $\Mod^{E_n}_{\UU_n\fg}$, and
+\item $(\UU_n \fh)_f$ denotes the object in $\Mod^{\EE_n}_{\UU_n\fg}$ --- equivalently, in $\LMod_{\int_{S^{n-1}}\UU_n}$ --- determined by~$f$, 
+\item ${\rm Mor}_{\Mod^{\EE_n}_{\UU_n\fg}}(\UU_n \fg, (\UU_n \fh)_f)$ denotes the classifying object for maps (i.e.
+an internal mapping object) from $\UU_n\fg$ to $(\UU_n \fh)_f$ in the $\infty$-category $\Mod^{\EE_n}_{\UU_n\fg}$, and
 \item ${\rm Mor}_{\LMod_{\int_{S^{n-1}} \UU_n\fg}} (\UU_n \fg, (\UU_n \fh)_f)$ denotes the classifying object for maps from ${\UU_n\fg}$ to $\UU_n \fh$ in the $\infty$-category $\LMod_{\int_{S^{n-1}}\UU_n\fg}$.
@@
 
-\subsection{Abelian Lie algebras and an $E_n$ HKR theorem}
+\subsection{Abelian Lie algebras and an $\EE_n$ HKR theorem}
 
 Given a free dg commutative algebra $A = \Sym(V^\bullet)$ generated by a cochain complex $V^\bullet$,
-one can view it as an $E_n$ algebra via the forgetful functor determined by the operad map $E_n \to E_\infty$.
-We will blithely view any commutative algebra as an $E_n$ algebra for any $n$ via this forgetting.
+one can view it as an $\EE_n$ algebra via the forgetful functor determined by the operad map $\EE_n \to E_\infty$.
+We will blithely view any commutative algebra as an $\EE_n$ algebra for any $n$ via this forgetting.
 
@@
 and hence provides a free dg commutative algebra.
-This feature can be leveraged to prove the following result about $E_n$-centers of free commutative algebras.
+This feature can be leveraged to prove the following result about $\EE_n$-centers of free commutative algebras.
 
@@
 
-This result is the simplest case of a generalized Hochschild-Kostant-Rosenberg theorem for commutative algebras viewed as $E_n$ algebras.
+This result is the simplest case of a generalized Hochschild-Kostant-Rosenberg theorem for commutative algebras viewed as $\EE_n$ algebras.
 (The classic theorem proves the $n=1$ situation.)
@@
 
-\owen{Also prove that the $E_n$ center of $\clies(\fg)$ is also $\clies(\fg, \UU_n \fg)$}
+\owen{Also prove that the $\EE_n$ center of $\clies(\fg)$ is also $\clies(\fg, \UU_n \fg)$}
 
@@
 
-\owen{Point out how to use LQT map and deduce existence of $E_n$ algebra structure on a shifted copy of cyclic cohomology of~$\Omega^*_c$}
+\owen{Point out how to use LQT map and deduce existence of $\EE_n$ algebra structure on a shifted copy of cyclic cohomology of~$\Omega^*_c$}
 
@@
 
-\subsection{Free Lie algebras and free $E_n$ algebras}
-
-\owen{Describe what we can of the center of a free $E_n$ algebra thanks to Ben's theorem}
+\subsection{Free Lie algebras and free $\EE_n$ algebras}
+
+\owen{Describe what we can of the center of a free $\EE_n$ algebra thanks to Ben's theorem}
 
@@
 The universal property of centralizer (recall definition~\ref{D:centralizer}) implies that 
-for any maps $A\stackrel{f}\to B$ and $B\stackrel{g}\to C$ of $E_n$-algebras, 
-there is a natural map of $E_n$-algebras
+for any maps $A\stackrel{f}\to B$ and $B\stackrel{g}\to C$ of $\EE_n$-algebras, 
+there is a natural map of $\EE_n$-algebras
 \begin{equation}
@@
 \end{equation}
-that arises from following commutative diagram of $E_n$-algebras:
+that arises from following commutative diagram of $\EE_n$-algebras:
 \[
@@
 \end{equation}
-Lurie \cite{HA} has proved that this multiplication makes the center into an $E_1$ algebra in $E_n$-algebras 
+Lurie \cite{HA} has proved that this multiplication makes the center into an $E_1$ algebra in $\EE_n$-algebras 
 and therefore an $E_{n+1}$-algebra, by Dunn additivity. 
@@
 % \item The canonical map~\eqref{eq:dgAssofcenter} makes the center ${\frak Z}_n(A)$ into an $E_1$-algebra in the symmetric monoidal category of 
-% $E_n$-algebras.
-% \item There is a canonical equivalence of the $\infty$-category $E_1\mathrm{-Alg}(E_n\mathrm{-Alg})$ with $E_{n+1}\mathrm{-Alg}$.
+% $\EE_n$-algebras.
+% \item There is a canonical equivalence of the $\infty$-category $E_1\mathrm{-Alg}(\EE_n\mathrm{-Alg})$ with $E_{n+1}\mathrm{-Alg}$.
 %\end{itemize}
@@
 augmented associative algebra {\em on the nose} in the 1-category of factorization algebras on~$\RR^n$,
-and it models the center ${\frak Z}_n(\fg)$ as an $E_1$ algebra in $E_n$ algebras.
+and it models the center ${\frak Z}_n(\fg)$ as an $E_1$ algebra in $\EE_n$ algebras.
 \end{enumerate}
@@
 \[ \Upsilon: {\frak Z}_n(\UU_n g) \otimes {\frak Z}_n(\UU_n f) \longrightarrow {\frak Z}_n\big(\UU_n (g\circ f)\big)\] 
-of $E_n$-algebras which makes the following diagram
+of $\EE_n$-algebras which makes the following diagram
 \begin{equation}\label{eq:comdiagforcentralizercomput}\small
@@
 
-The $E_n$-center, or $E_n$-Hochschild cohomology, of an $E_n$-algebra $A$ is the {\em universal} $E_{n+1}$-algebra that acts on $A$ {\em qua} $E_n$ algebra.
+The $\EE_n$-center, or $\EE_n$-Hochschild cohomology, of an $\EE_n$-algebra $A$ is the {\em universal} $E_{n+1}$-algebra that acts on $A$ {\em qua} $\EE_n$ algebra.
 
@@
 %\brian{We should compare with Tamarkin-Tsygan's noncommutative calculus (cf. section 2.6).
-%We could exhibit Theorem 2.7.1 explicitly in this case for the $E_n$ case with enveloping algebras.}
+%We could exhibit Theorem 2.7.1 explicitly in this case for the $\EE_n$ case with enveloping algebras.}
 
@@
 
-%We have developed locally constant factorization models separately for enveloping $E_n$-algebras and their centers.
+%We have developed locally constant factorization models separately for enveloping $\EE_n$-algebras and their centers.
 %Combining these descriptions we obtain the following.
@@
 Let us start with a discussion of the general situation.
-Let $(A,B)$ be a Swiss cheese pair: $A$ is an $E_1$ algebra in $E_n$ algebras and $B$ is an $E_n$ algebra in left $A$-modules. 
+Let $(A,B)$ be a Swiss cheese pair: $A$ is an $E_1$ algebra in $\EE_n$ algebras and $B$ is an $\EE_n$ algebra in left $A$-modules. 
 We will freely view these as locally constant factorization algebras on framed $n$-manifolds.
@@
 As a slogan, we say ``factorization homology commutes with taking centers,'' 
-at least for enveloping $E_n$ algebras.
+at least for enveloping $\EE_n$ algebras.
 It is natural to ask whether this result holds in general.
@@
 \begin{qtn}
-Is the canonical map \eqref{eqn: can cen int} a weak equivalence when $\UU_n \fg$ is replaced by an arbitrary $E_n$-algebra?
+Is the canonical map \eqref{eqn: can cen int} a weak equivalence when $\UU_n \fg$ is replaced by an arbitrary $\EE_n$-algebra?
 \end{qtn}
@@
 
-\subsection{Koszul duality for enveloping $E_n$ algebras}
-
-\owen{Use corollary~\ref{cor: koszul dual to main theorem} to exhibit a "dual" Swiss cheese pair and then compute the relative tensor product over the center, which will be the unit $E_n$ algebra.
+\subsection{Koszul duality for enveloping $\EE_n$ algebras}
+
+\owen{Use corollary~\ref{cor: koszul dual to main theorem} to exhibit a "dual" Swiss cheese pair and then compute the relative tensor product over the center, which will be the unit $\EE_n$ algebra.
 Draw a picture of the strip.}
@@
 %
-%The $E_n$-center, or $E_n$-Hochschild cohomology, of an $E_n$-algebra $A$ is the {\em universal} $E_{n+1}$-algebra which acts on $A$. 
+%The $\EE_n$-center, or $\EE_n$-Hochschild cohomology, of an $\EE_n$-algebra $A$ is the {\em universal} $E_{n+1}$-algebra which acts on $A$. 
 %In Section \ref{sec:swiss} below, we will recall an elegant operadic interpretation of this universal picture and interpret it in terms of {\em constructible factorization algebras}. 
-%In the case of $E_n$-enveloping algebras, we will provide a strict factorization model of this universal situation in terms of a constructible factorization algebra on an $(n+1)$-dimensional 
+%In the case of $\EE_n$-enveloping algebras, we will provide a strict factorization model of this universal situation in terms of a constructible factorization algebra on an $(n+1)$-dimensional 
 %manifold with boundary. 
@@
 %We will furthermore provide an interpretation of this constructible factorization algebra in terms of the quantization of a certain topological field theory. 
-%The key insight is that there is a {\em classical limit} of the $E_n$-center $\fZ_n(\fg)$ which is equivalent to the observables of an $(n+1)$-dimensional topological field theory known as {\em BF theory}.
+%The key insight is that there is a {\em classical limit} of the $\EE_n$-center $\fZ_n(\fg)$ which is equivalent to the observables of an $(n+1)$-dimensional topological field theory known as {\em BF theory}.
 %Likewise, there is a classical limit of $\UU_n(\fg)$ which can be viewed as a boundary condition for BF theory.
 %
-%In this sense, topological BF theory is the universal $(n+1)$-dimensional field theory which has the $E_n$-enveloping algebra as a boundary condition. 
+%In this sense, topological BF theory is the universal $(n+1)$-dimensional field theory which has the $\EE_n$-enveloping algebra as a boundary condition. 
 %This partially confirms the terminology used in \cite{ButsonYoo}  of topological BF theory as the ``universal bulk theory" of $\UU_n(\fg)$.
 
-In this section, we turn to an interpretation of the $E_n$-center of an $E_n$-enveloping algebra in terms of a certain topological field theory (TFT).
+In this section, we turn to an interpretation of the $\EE_n$-center of an $\EE_n$-enveloping algebra in terms of a certain topological field theory (TFT).
 
@@
 
-%Let $\fg$ be a dg Lie algebra and consider the $E_n$ algebra $\UU_n \fg$. 
-%We have shown that a model for the $E_n$-center ${\frak Z}_n (\UU_n \fg) = {\frak Z}_n ({\rm id}_{\UU_n \fg})$ is the $n$-dimensional locally constant factorization algebra 
+%Let $\fg$ be a dg Lie algebra and consider the $\EE_n$ algebra $\UU_n \fg$. 
+%We have shown that a model for the $\EE_n$-center ${\frak Z}_n (\UU_n \fg) = {\frak Z}_n ({\rm id}_{\UU_n \fg})$ is the $n$-dimensional locally constant factorization algebra 
 %\[
@@
 %
-%Let us place the locally constant factorization algebra model of the $E_n$-enveloping algebra $\bU_n (\fg) = \clieu(\fg \otimes \Omega_c)$ on the $n$-manifold $M$.
+%Let us place the locally constant factorization algebra model of the $\EE_n$-enveloping algebra $\bU_n (\fg) = \clieu(\fg \otimes \Omega_c)$ on the $n$-manifold $M$.
 %This factorization algebra is equivalent to the pushforward of a factorization algebra $\Obs_{\rm BF}$ on the $(n+1)$-dimensional manifold $M \times \RR$ along the projection $\pi : M \times (0,1) \to M$ which we proceed to construct.
@@
 %We now consider the pushforward factorization algebra $\pi_* \Obs^{\rm cl}_{\rm BF}$ on $M$.
-%Locally, on disks, we will see that it is quasi-isomorphic to a certain limit, or ``dequantization", of our model for the $E_n$-center of $\UU_n \fg$.
+%Locally, on disks, we will see that it is quasi-isomorphic to a certain limit, or ``dequantization", of our model for the $\EE_n$-center of $\UU_n \fg$.
 %Recall, this model is given by the factorization algebra on $M$:
@@
 %\]
-%Notice this is similar to the model $E_n$-center except we have turned off the Chevalley--Eilenberg differential on chains. 
+%Notice this is similar to the model $\EE_n$-center except we have turned off the Chevalley--Eilenberg differential on chains. 
 %
@@
 \def \Fac {\mathrm{Fac}}
-We now need to express the $E_n$-structure on ${\rm Mor}_{\LMod_{\int_{S^{n-1}} \UU_n\fg}}(\UU_n \fg, B_f)$ induced by the equivalence of Proposition~\ref{P:ModentoModSn}, and then on the subsequent isomorphic hom spaces of modules morphisms.
+We now need to express the $\EE_n$-structure on ${\rm Mor}_{\LMod_{\int_{S^{n-1}} \UU_n\fg}}(\UU_n \fg, B_f)$ induced by the equivalence of Proposition~\ref{P:ModentoModSn}, and then on the subsequent isomorphic hom spaces of modules morphisms.
 Since we are going to take advantage of the factorization algebra presentation of $\UU_n( \fg)$, see~Theorem~\ref{T:UnofLie}, we recall the following factorization algebra description of the centralizer.
-Let $\cA \stackrel{f}\to \cB$ be a morphism of locally constant factorization algebras on $\RR^n$ corresponding to an $E_n$-algebra map similarly denoted.
+Let $\cA \stackrel{f}\to \cB$ be a morphism of locally constant factorization algebras on $\RR^n$ corresponding to an $\EE_n$-algebra map similarly denoted.
 Then by Theorems~\ref{thm:lurie1}, \ref{T:centralizer=inthom} the centralizer of $f$ is represented by the locally constant factorization algebra

### 2020-09-08 draft.tex

@@
 
+\brian{notation $\EE$ and $\bE$}
+
 \subsection{Enveloping $\EE_n$ algebras of Lie algebras}
@@
 in any presentable symmetric monoidal stable $\infty$-category $\cC$,
-we only work in the infinity category of chain complexes $(\Mod_k, \otimes_k)$, where $k$ is a field of characteristic zero.
+we only work in the $\infty$-category of chain complexes $(\Mod_k, \otimes_k)$, 
+where $k$ is a field of characteristic zero.
 We summarize Knudsen's result in this setting as follows.

### 2020-09-08 draft.tex
tiny by o

@@
 
-\subsection{The large $N$ limit of the center ${\frak Z}_n(\UU_n {\frak gl}_N)$ and cyclic cohomology}
+\subsection{The large $N$ limit of the center ${\frak Z}_n(\UU_n \frak{gl}_N)$ and cyclic cohomology}
 
@@
 
-By Theorem~\ref{thm:centralizerfactorization}, we know that the factorization algebras models for the centralizers are given by the respective Chevalley-Eilenberg cochain factorizations algebras 
+By Theorem~\ref{thm:centralizerfactorization}, we know that the factorization algebra models for the centralizers are given by the respective Chevalley-Eilenberg cochain factorizations algebras 
 (Definition~\ref{dfn:CEofFact}) $\clies\big(\fg \otimes \Omega, \cliels(\fh \otimes \Omega_c  \big) $, 
@@
 
-\section{Higher calculus {\it \`a la} Kontsevich and Tamarkin-Tsygan}
+\section{Higher calculus {\it \`a la} Kontsevich-Soibelman}
 \label{sec: TT}
@@
 In Section \ref{sec:swiss} below, we will recall an elegant operadic articulation of this idea and rephrase it in terms of {\em constructible factorization algebras} on a half-space~$\HH^{n+1}$.
+
+\owen{Mention lots of prior work, e.g., Greg et al, Ayala-Francis, Geoffroy Horel, and so on}
 

### 2020-09-08 draft.tex
poisson

--- 2020-09-08 draft.tex
@@
 Recently, a generalization of the concept of the enveloping algebra of a Lie algebra has emerged: 
-each dg Lie algebra $\fg$ has an enveloping $\EE_n$ algebra $\UU_n\fg$, for every $n$, 
+each dg Lie algebra $\fg$ has an enveloping $E_n$ algebra $\UU_n\fg$, for every $n$, 
 so that $\UU_1\fg$ is the usual enveloping algebra $U\fg$. 
 Building on prior work \cite{BD, AF} [Owen's thesis?], 
-Knudsen \cite{Knudsen} developed these ideas extensively and offered a useful factorization algebra model for the enveloping $\EE_n$ algebra. 
+Knudsen \cite{Knudsen} developed these ideas extensively and offered a useful factorization algebra model for the enveloping $E_n$ algebra. 
 Our central goal here is to generalize the some well-known results about the enveloping algebra $U\fg$ to $\UU_n\fg$, for all $n$, such as
@@
 %Our primary tool here is the Loday-Quillen-Tsygan (LQT) theorem which describes the large $N$ limit of the Lie algebra homology of $\gl_N(A)$, for a dg associative algebra $A$.
-Since the enveloping $\EE_n$ algebra of a Lie algebra can be constructed as a locally constant factorization algebra made out of the shifted Chevalley-Eilenberg chains \cite{}, the relevance of the LQT theorem in this context  should be apparent.
-From this point of view, one can think of our main result as an $\EE_n$ generalization of the LQT theorem.
+Since the enveloping $E_n$ algebra of a Lie algebra can be constructed as a locally constant factorization algebra made out of the shifted Chevalley-Eilenberg chains \cite{}, the relevance of the LQT theorem in this context  should be apparent.
+From this point of view, one can think of our main result as an $E_n$ generalization of the LQT theorem.
 We hope these ideas have exciting applications in quantum field theory and random matrix theory, as well as to other large $N$ limit phenomena.
@@
 
-See section~\ref{sec: en background} for a brief discussion of $\EE_n$ algebras and their relationship with locally constant factorization algebras on $\RR^n$, section~\ref{sec: enveloping} for a brief discussion of the enveloping $\EE_n$ algebra construction, and see section~\ref{sec: centralizer}
-for a brief discussion about centralizers to maps of $\EE_n$ algebras.
+See section~\ref{sec: en background} for a brief discussion of $E_n$ algebras and their relationship with locally constant factorization algebras on $\RR^n$, section~\ref{sec: enveloping} for a brief discussion of the enveloping $E_n$ algebra construction, and see section~\ref{sec: centralizer}
+for a brief discussion about centralizers to maps of $E_n$ algebras.
 
@@
 Even to state our central result, we need to review a few results and terminology.
-First, our basic context is $\EE_n$ algebras.
-By $\EE_n$ we mean any operad or colored operad or $\infty$-operad equivalent to the topological operad of little $n$-disks in $\RR^n$, where the notion of equivalence is in some appropriate $\infty$-categorical setting of operads.
+First, our basic context is $E_n$ algebras.
+By $E_n$ we mean any operad or colored operad or $\infty$-operad equivalent to the topological operad of little $n$-disks in $\RR^n$, where the notion of equivalence is in some appropriate $\infty$-categorical setting of operads.
 In particular, we will require that its $\infty$-category of algebras in $\Ch_k^{\otimes_k}$ agree with those of the little $n$-disks operad. 
@@
 
-Many notions from ordinary algebra admit natural generalizations to $\EE_n$ algebras.
+Many notions from ordinary algebra admit natural generalizations to $E_n$ algebras.
 For instance, to each Lie algebra $\fg$ (and more generally $L_\infty$ algebra),
-there is an {\em enveloping $\EE_n$ algebra} $\UU_n \fg$, thanks to \cite{Knudsen}.
-Similarly, every $\EE_n$ algebra $A$ has a {\em center} ${\frak Z}_n(A)$, which is an $E_{n+1}$ algebra and hence more commutative than~$A$.
-More generally, for any map of $\EE_n$ algebras $f: A \to B$, there is a {\em centralizer} ${\frak Z}_n(f)$, 
+there is an {\em enveloping $E_n$ algebra} $\UU_n \fg$, thanks to \cite{Knudsen}.
+Similarly, every $E_n$ algebra $A$ has a {\em center} ${\frak Z}_n(A)$, which is an $E_{n+1}$ algebra and hence more commutative than~$A$.
+More generally, for any map of $E_n$ algebras $f: A \to B$, there is a {\em centralizer} ${\frak Z}_n(f)$, 
 which is a generalization of the commutant.
@@
 
-Our work here relies on a concrete and convenient model for these enveloping $\EE_n$ algebras by factorization algebras.
+Our work here relies on a concrete and convenient model for these enveloping $E_n$ algebras by factorization algebras.
 In particular, thanks again to \cite{Knudsen}, 
-we know that the $\EE_n$ enveloping algebra $\UU_n \fg$ admits a model $\bU_n \fg$ whose underlying functor on the poset of open sets in $\RR^n$ assigns $\cliels(\Omega_c^*(V) \otimes \fg)$ to each open set~$V$.
+we know that the $E_n$ enveloping algebra $\UU_n \fg$ admits a model $\bU_n \fg$ whose underlying functor on the poset of open sets in $\RR^n$ assigns $\cliels(\Omega_c^*(V) \otimes \fg)$ to each open set~$V$.
 There is another factorization algebra whose underlying assigns $\clies(\Omega^*(V) \otimes \fg)$ to each open~$V$.
-Our paper shows that such factorization algebras model other important $\EE_n$ algebras, notably centralizers.
+Our paper shows that such factorization algebras model other important $E_n$ algebras, notably centralizers.
 
@@
 (i.e., a map of conilpotent cocommutative coalgebras $f: \cliels(\fg) \to \cliels(\fh)$).
-This map determines functorially a map of $\EE_n$ algebras
+This map determines functorially a map of $E_n$ algebras
 \[
@@
 \]
-between their enveloping $\EE_n$ algebras.
-The centralizer of this map ${\frak Z}_n(\UU_n f)$ is an $\EE_n$-algebra modeled by the factorization algebra 
+between their enveloping $E_n$ algebras.
+The centralizer of this map ${\frak Z}_n(\UU_n f)$ is an $E_n$-algebra modeled by the factorization algebra 
 \[
@@
 
-\owen{I think we could (and maybe should) also discuss the $\EE_n$-Koszul dual situation involving cochains.}
+\owen{I think we could (and maybe should) also discuss the $E_n$-Koszul dual situation involving cochains.}
 
@@
 \begin{itemize}
-\item Lurie \cite{LurieHA} explains why the $\infty$-category of $\EE_n$ algebras is equivalent to the homotopy-coherent version of locally constant prefactorization algebras on $\RR^n$.  
+\item Lurie \cite{LurieHA} explains why the $\infty$-category of $E_n$ algebras is equivalent to the homotopy-coherent version of locally constant prefactorization algebras on $\RR^n$.  
 In fact, he simplifies the situation a bit more. 
@@
 One can work with locally constant, homotopy-coherent $\Disk_n^\sqcup$-algebras.
-\item Knudsen verifies that we can model the enveloping $\EE_n$ algebra by the factorization algebra $\bU_n \fg$ described earlier.
-\item Francis and Lurie give a characterization of the centralizer ${\frak Z}_n(f)$ of any $\EE_n$ algebra map $\phi: A \to B$ as the ``internal hom'' in left $\int_{S^{n-1}}A$-modules from $A$ to $B_\phi$, where $B_\phi$ denotes $B$ viewed as a left module via the map~$\phi$.
+\item Knudsen verifies that we can model the enveloping $E_n$ algebra by the factorization algebra $\bU_n \fg$ described earlier.
+\item Francis and Lurie give a characterization of the centralizer ${\frak Z}_n(f)$ of any $E_n$ algebra map $\phi: A \to B$ as the ``internal hom'' in left $\int_{S^{n-1}}A$-modules from $A$ to $B_\phi$, where $B_\phi$ denotes $B$ viewed as a left module via the map~$\phi$.
 \item In combination, the centralizer is characterized up to quasi-isomorphism, 
@@
 \end{enumerate}
-Hence it induces a weak equivalence of the associated factorization algebras and hence as $\EE_n$ algebras.
+Hence it induces a weak equivalence of the associated factorization algebras and hence as $E_n$ algebras.
 
@@
 \label{thm: center}
-The center ${\frak Z}_n(\fg)$ of the enveloping $\EE_n$ algebra $\UU_n\fg$ is the $\EE_n$ algebra $\clies(\fg, \UU_n\fg)$. 
+The center ${\frak Z}_n(\fg)$ of the enveloping $E_n$ algebra $\UU_n\fg$ is the $E_n$ algebra $\clies(\fg, \UU_n\fg)$. 
 When $k$ is $\RR$ or $\CC$, the 
@@
 
-If $\epsilon: \fg \to 0$ is the trivial map, then we obtain the canonical augmentation $\epsilon: \UU_n \fg \to k$ of $\EE_n$ algebras.
+If $\epsilon: \fg \to 0$ is the trivial map, then we obtain the canonical augmentation $\epsilon: \UU_n \fg \to k$ of $E_n$ algebras.
 In this case, we obtain a version of Koszul duality as the corollary.
@@
 \label{thm: koszul duality}
-The centralizer of the augmentation $\epsilon: \UU_n \fg \to k$ is equivalent to $\clies(\fg)$ viewed as an $\EE_n$ algebra. It is modeled by the locally constant factorization algebra that assigns
+The centralizer of the augmentation $\epsilon: \UU_n \fg \to k$ is equivalent to $\clies(\fg)$ viewed as an $E_n$ algebra. It is modeled by the locally constant factorization algebra that assigns
 \[
@@
 \item When $n=1$, unpack in detail how the convolution picture matches the classic view of Koszul duality for associative (co)algebras.
-\item Consider $\fg$ {\em abelian} for arbitrary $n$ and compare to the $\EE_n$ HKR theorem.
-\item Compare with $\EE_n$ HKR theorem for $\clies(\fg)$ via $\EE_n$ Koszul duality.
+\item Consider $\fg$ {\em abelian} for arbitrary $n$ and compare to the $E_n$ HKR theorem.
+\item Compare with $E_n$ HKR theorem for $\clies(\fg)$ via $E_n$ Koszul duality.
 \item Use these facts to compute factorization homology of centralizers on manifolds with boundary --- kind of like Chern-Simons states!
@@
 
-Having an explicit presentation for the centralizer of a map of $\EE_n$ algebras leads to a calculation of factorization homology.
-The enveloping $\EE_n$ algebra is the homotopy $O(n)$-fixed points, or a $\mathrm{Disk}_n$-algebra in the sense of~\cite{AF},
+Having an explicit presentation for the centralizer of a map of $E_n$ algebras leads to a calculation of factorization homology.
+The enveloping $E_n$ algebra is the homotopy $O(n)$-fixed points, or a $\mathrm{Disk}_n$-algebra in the sense of~\cite{AF},
 and hence determines a factorization algebra on any un-oriented $n$-dimensional manifold \cite{Knudsen}.
@@
 
-\greg{Somewhere we should recall that $\UU_n$ and its center are unoriented $\EE_n$-algebras and define factorization algebras over any manifold that came from the formula}
+\greg{Somewhere we should recall that $\UU_n$ and its center are unoriented $E_n$-algebras and define factorization algebras over any manifold that came from the formula}
 
@@
 
-\subsection{Recollections on $\EE_n$ algebras and prefactorization algebras}
+\subsection{Recollections on $E_n$ algebras and prefactorization algebras}
 \label{sec: en background}
@@
 \label{thm:lurie1} 
-There is an equivalence of $\infty$-categories between $\EE_n$-algebras and locally constant prefactorization algebras on~$\RR^n$. 
+There is an equivalence of $\infty$-categories between $E_n$-algebras and locally constant prefactorization algebras on~$\RR^n$. 
 \end{thm}
@@
 
-\subsection{Enveloping $\EE_n$ algebras of Lie algebras}
+\subsection{Enveloping $E_n$ algebras of Lie algebras}
 \label{sec: enveloping}
 
-Although \cite{Knudsen} develops an adjunction between Lie and $\EE_n$ algebras \mahmoud{non-unital?}\greg{Both I think}\owen{augmented is probably best for us}
+Although \cite{Knudsen} develops an adjunction between Lie and $E_n$ algebras \mahmoud{non-unital?}\greg{Both I think}\owen{augmented is probably best for us}
 in any presentable symmetric monoidal stable $\infty$-category $\cC$,
-we only work in the $\infty$-category of chain complexes $(\Mod_k, \otimes_k)$, 
-where $k$ is a field of characteristic zero.
+we only work in the infinity category of chain complexes $(\Mod_k, \otimes_k)$, where $k$ is a field of characteristic zero.
 We summarize Knudsen's result in this setting as follows.
@@
 \begin{tikzcd}
-\Alg_\Lie(\Mod_k) \arrow[r, bend left=20, shift left=.5ex,"\UU_n"] \arrow[dd] & \Alg_{\EE_n}(\Mod_k) \arrow[l, shift left=.5ex, "\oblv_n"] \arrow[dd]\\
+\Alg_\Lie(\Mod_k) \arrow[r, bend left=20, shift left=.5ex,"\UU_n"] \arrow[dd] & \Alg_{E_n}(\Mod_k) \arrow[l, shift left=.5ex, "\oblv_n"] \arrow[dd]\\
 &\\
-\Mod_k \arrow[r, bend left=20, shift left=.5ex, "\Sigma^{1-n}"] \arrow[uu, bend left=20, shift left=.5ex, "\Free_\Lie"] & \Mod_k \arrow[l, shift left=.5ex,"\Sigma^{n-1}"] \arrow[uu, bend right=20, shift right=.5ex, "\Free_{\EE_n}"']
+\Mod_k \arrow[r, bend left=20, shift left=.5ex, "\Sigma^{1-n}"] \arrow[uu, bend left=20, shift left=.5ex, "\Free_\Lie"] & \Mod_k \arrow[l, shift left=.5ex,"\Sigma^{n-1}"] \arrow[uu, bend right=20, shift right=.5ex, "\Free_{E_n}"']
 \end{tikzcd}
@@
 When $k$ is $\RR$ or $\CC$, 
-the enveloping $\EE_n$ algebra $\UU_n \fg$ of a dg Lie algebra $\fg$ is modeled by the locally constant factorization algebra $\bU_n \fg$ that assigns
+the enveloping $E_n$ algebra $\UU_n \fg$ of a dg Lie algebra $\fg$ is modeled by the locally constant factorization algebra $\bU_n \fg$ that assigns
 \[
@@
 \begin{rmk}
-It follows from theorem~\ref{T:UnofLie} that for any $\EE_n$-algebra $B$, 
+It follows from theorem~\ref{T:UnofLie} that for any $E_n$-algebra $B$, 
 its underlying complex is equipped with a homotopy-coherent Lie algebra structure.
@@
 
-\subsection{Centralizers of maps of $\EE_n$ algebras and the derived center}
+\subsection{Centralizers of maps of $E_n$ algebras and the derived center}
 \label{sec: centralizer}
@@
 \begin{dfn}\label{D:centralizer}
-For a map $f: A \to B$ of $\EE_n$ algebras in $\cC$, 
-the {\em centralizer} ${\frak Z}_n(f)$ is the $\EE_n$ algebra in $\cC$ that is universal among those that fit in a commuting diagram
+For a map $f: A \to B$ of $E_n$ algebras in $\cC$, 
+the {\em centralizer} ${\frak Z}_n(f)$ is the $E_n$ algebra in $\cC$ that is universal among those that fit in a commuting diagram
 \[
@@
 where the arrow in the upper left is the tensor product of the unit map $u: 1_\cC \to {\frak Z}_n(f)$ and the identity map $\id: A \to A$.
-The {\em center} of an $\EE_n$ algebra $A$ is the centralizer of its identity morphism $\id_A: A \to A$. 
+The {\em center} of an $E_n$ algebra $A$ is the centralizer of its identity morphism $\id_A: A \to A$. 
 We  denote it ${\frak Z}_n(A) := {\frak Z}_n(\id_A)$.
@@
 \label{T:centralizer=inthom} 
-The centralizer ${\frak Z}_n(f)$ exists and can be identified with the classifying object for maps from $A$ to $B$ in the $\infty$-category $\Mod^{\EE_n}_A(\cC)$.
+The centralizer ${\frak Z}_n(f)$ exists and can be identified with the classifying object for maps from $A$ to $B$ in the $\infty$-category $\Mod^{E_n}_A(\cC)$.
 \mahmoud{we should probably spell out the meaning of the classifying object in this case to make it obvious that the centralizer is the classifying object}
@@
 Let $\cC^\otimes$ be a presentable symmetric monoidal stable $\infty$-category whose tensor product preserves colimits in each variable separately.
-For $A$ be an $\EE_n$ algebra in $\cC$,
-the $\infty$-category $\Mod^{\EE_n}_A(\cC)$ is equivalent to the $\infty$-category $\LMod_{{\int_{S^{n-1}} A}}(\cC)$.
+For $A$ be an $E_n$ algebra in $\cC$,
+the $\infty$-category $\Mod^{E_n}_A(\cC)$ is equivalent to the $\infty$-category $\LMod_{{\int_{S^{n-1}} A}}(\cC)$.
 \end{prp}
@@
 See Remark 7.3.5.3 of \cite{LurieHA}, Corollary 13 in~\cite{GG-Notes} and Section 2 of \cite{FrancisHH}.
-Concretely, this claim arises from the fact that as a module over $A$ as an $\EE_n$ algebra, 
-$M \in \Mod^{\EE_n}_A(\cC)$ is equipped with a commuting family of actions by $A$ parametrized by $\RR^n \setminus \{0\}\cong S^{n-1} \times \RR_{>0}$.
+Concretely, this claim arises from the fact that as a module over $A$ as an $E_n$ algebra, 
+$M \in \Mod^{E_n}_A(\cC)$ is equipped with a commuting family of actions by $A$ parametrized by $\RR^n \setminus \{0\}\cong S^{n-1} \times \RR_{>0}$.
 This action factors through the left action of the $E_1$ algebra $\int_{S^{n-1} \times \RR_{>0}} A$ arising from factorization homology over the complement of the origin,
@@
 this algebra $\int_{S^{n-1} \times \RR} A$ is equivalent to ${\rm Free}(1_\cC)$, 
-the image of the unit object $1_\cC \in \cC$ under the left adjoint ${\rm Free}$ to the forgetful functor $\Mod^{\EE_n}_A(\cC) \to \cC$.
+the image of the unit object $1_\cC \in \cC$ under the left adjoint ${\rm Free}$ to the forgetful functor $\Mod^{E_n}_A(\cC) \to \cC$.
 
@@
 As we work in the setting of factorization algebras on $\RR^n$, 
-we will use bold font to indicate such factorization models for $\EE_n$ algebra statements.
-For instance, we use $\bU_n \fg$ for the factorization model of the enveloping $\EE_n$ algebra,
-and we use ${\bf f}: \bU_n \fg \to \bU_n \fh$ for the factorization model of the map $f: \UU_n \fg \to \UU_n \fh$ of $\EE_n$ algebras.
+we will use bold font to indicate such factorization models for $E_n$ algebra statements.
+For instance, we use $\bU_n \fg$ for the factorization model of the enveloping $E_n$ algebra,
+and we use ${\bf f}: \bU_n \fg \to \bU_n \fh$ for the factorization model of the map $f: \UU_n \fg \to \UU_n \fh$ of $E_n$ algebras.
 
@@
 \[
-\cliels(\fg_1 \times \fg_2) = \cliels(\fg_1) \otimes \cliels(\fg_2),
+\cliels(\fg \times \fh) = \cliels(\fg) \otimes \cliels(\fh),
 \]
@@
 In this sense, we see how $\clies(\fg,\cliels(\fh)_f)$ encodes deformations of~$f$.
-
-\owen{Probably need to mention somewhere that it's better to work with $\clies(\fg)$ as a completed object.}
 
@@
 \begin{align*}
-{\frak Z}_n(f) &\simeq {{\rm Mor}}_{\Mod^{\EE_n}_{\UU_n\fg}}(\UU_n \fg, (\UU_n \fh)_f) \\
+{\frak Z}_n(f) &\simeq {{\rm Mor}}_{\Mod^{E_n}_{\UU_n\fg}}(\UU_n \fg, (\UU_n \fh)_f) \\
 &\simeq {\rm Mor}_{\LMod_{\int_{S^{n-1}} \UU_n\fg}}(\UU_n \fg, (\UU_n \fh)_f)
@@
 \begin{itemize}
-\item $(\UU_n \fh)_f$ denotes the object in $\Mod^{\EE_n}_{\UU_n\fg}$ --- equivalently, in $\LMod_{\int_{S^{n-1}}\UU_n}$ --- determined by~$f$, 
-\item ${\rm Mor}_{\Mod^{\EE_n}_{\UU_n\fg}}(\UU_n \fg, (\UU_n \fh)_f)$ denotes the classifying object for maps (i.e.
-an internal mapping object) from $\UU_n\fg$ to $(\UU_n \fh)_f$ in the $\infty$-category $\Mod^{\EE_n}_{\UU_n\fg}$, and
+\item $(\UU_n \fh)_f$ denotes the object in $\Mod^{E_n}_{\UU_n\fg}$ --- equivalently, in $\LMod_{\int_{S^{n-1}}\UU_n}$ --- determined by~$f$, 
+\item ${\rm Mor}_{\Mod^{E_n}_{\UU_n\fg}}(\UU_n \fg, (\UU_n \fh)_f)$ denotes the classifying object for maps (i.e.
+an internal mapping object) from $\UU_n\fg$ to $(\UU_n \fh)_f$ in the $\infty$-category $\Mod^{E_n}_{\UU_n\fg}$, and
 \item ${\rm Mor}_{\LMod_{\int_{S^{n-1}} \UU_n\fg}} (\UU_n \fg, (\UU_n \fh)_f)$ denotes the classifying object for maps from ${\UU_n\fg}$ to $\UU_n \fh$ in the $\infty$-category $\LMod_{\int_{S^{n-1}}\UU_n\fg}$.
@@
 
-\subsection{Abelian Lie algebras and an $\EE_n$ HKR theorem}
+\subsection{Abelian Lie algebras and an $E_n$ HKR theorem}
 
 Given a free dg commutative algebra $A = \Sym(V^\bullet)$ generated by a cochain complex $V^\bullet$,
-one can view it as an $\EE_n$ algebra via the forgetful functor determined by the operad map $\EE_n \to E_\infty$.
-We will blithely view any commutative algebra as an $\EE_n$ algebra for any $n$ via this forgetting.
+one can view it as an $E_n$ algebra via the forgetful functor determined by the operad map $E_n \to E_\infty$.
+We will blithely view any commutative algebra as an $E_n$ algebra for any $n$ via this forgetting.
 
@@
 and hence provides a free dg commutative algebra.
-This feature can be leveraged to prove the following result about $\EE_n$-centers of free commutative algebras.
+This feature can be leveraged to prove the following result about $E_n$-centers of free commutative algebras.
 
@@
 
-This result is the simplest case of a generalized Hochschild-Kostant-Rosenberg theorem for commutative algebras viewed as $\EE_n$ algebras.
+This result is the simplest case of a generalized Hochschild-Kostant-Rosenberg theorem for commutative algebras viewed as $E_n$ algebras.
 (The classic theorem proves the $n=1$ situation.)
@@
 
-\owen{Also prove that the $\EE_n$ center of $\clies(\fg)$ is also $\clies(\fg, \UU_n \fg)$}
+\owen{Also prove that the $E_n$ center of $\clies(\fg)$ is also $\clies(\fg, \UU_n \fg)$}
 
@@
 
-\owen{Point out how to use LQT map and deduce existence of $\EE_n$ algebra structure on a shifted copy of cyclic cohomology of~$\Omega^*_c$}
+\owen{Point out how to use LQT map and deduce existence of $E_n$ algebra structure on a shifted copy of cyclic cohomology of~$\Omega^*_c$}
 
@@
 
-\subsection{Free Lie algebras and free $\EE_n$ algebras}
-
-\owen{Describe what we can of the center of a free $\EE_n$ algebra thanks to Ben's theorem}
+\subsection{Free Lie algebras and free $E_n$ algebras}
+
+\owen{Describe what we can of the center of a free $E_n$ algebra thanks to Ben's theorem}
 
@@
 The universal property of centralizer (recall definition~\ref{D:centralizer}) implies that 
-for any maps $A\stackrel{f}\to B$ and $B\stackrel{g}\to C$ of $\EE_n$-algebras, 
-there is a natural map of $\EE_n$-algebras
+for any maps $A\stackrel{f}\to B$ and $B\stackrel{g}\to C$ of $E_n$-algebras, 
+there is a natural map of $E_n$-algebras
 \begin{equation}
@@
 \end{equation}
-that arises from following commutative diagram of $\EE_n$-algebras:
+that arises from following commutative diagram of $E_n$-algebras:
 \[
@@
 \end{equation}
-Lurie \cite{HA} has proved that this multiplication makes the center into an $E_1$ algebra in $\EE_n$-algebras 
+Lurie \cite{HA} has proved that this multiplication makes the center into an $E_1$ algebra in $E_n$-algebras 
 and therefore an $E_{n+1}$-algebra, by Dunn additivity. 
@@
 % \item The canonical map~\eqref{eq:dgAssofcenter} makes the center ${\frak Z}_n(A)$ into an $E_1$-algebra in the symmetric monoidal category of 
-% $\EE_n$-algebras.
-% \item There is a canonical equivalence of the $\infty$-category $E_1\mathrm{-Alg}(\EE_n\mathrm{-Alg})$ with $E_{n+1}\mathrm{-Alg}$.
+% $E_n$-algebras.
+% \item There is a canonical equivalence of the $\infty$-category $E_1\mathrm{-Alg}(E_n\mathrm{-Alg})$ with $E_{n+1}\mathrm{-Alg}$.
 %\end{itemize}
@@
 augmented associative algebra {\em on the nose} in the 1-category of factorization algebras on~$\RR^n$,
-and it models the center ${\frak Z}_n(\fg)$ as an $E_1$ algebra in $\EE_n$ algebras.
+and it models the center ${\frak Z}_n(\fg)$ as an $E_1$ algebra in $E_n$ algebras.
 \end{enumerate}
@@
 \[ \Upsilon: {\frak Z}_n(\UU_n g) \otimes {\frak Z}_n(\UU_n f) \longrightarrow {\frak Z}_n\big(\UU_n (g\circ f)\big)\] 
-of $\EE_n$-algebras which makes the following diagram
+of $E_n$-algebras which makes the following diagram
 \begin{equation}\label{eq:comdiagforcentralizercomput}\small
@@
 
-The $\EE_n$-center, or $\EE_n$-Hochschild cohomology, of an $\EE_n$-algebra $A$ is the {\em universal} $E_{n+1}$-algebra that acts on $A$ {\em qua} $\EE_n$ algebra.
+The $E_n$-center, or $E_n$-Hochschild cohomology, of an $E_n$-algebra $A$ is the {\em universal} $E_{n+1}$-algebra that acts on $A$ {\em qua} $E_n$ algebra.
 
@@
 %\brian{We should compare with Tamarkin-Tsygan's noncommutative calculus (cf. section 2.6).
-%We could exhibit Theorem 2.7.1 explicitly in this case for the $\EE_n$ case with enveloping algebras.}
+%We could exhibit Theorem 2.7.1 explicitly in this case for the $E_n$ case with enveloping algebras.}
 
@@
 
-%We have developed locally constant factorization models separately for enveloping $\EE_n$-algebras and their centers.
+%We have developed locally constant factorization models separately for enveloping $E_n$-algebras and their centers.
 %Combining these descriptions we obtain the following.
@@
 Let us start with a discussion of the general situation.
-Let $(A,B)$ be a Swiss cheese pair: $A$ is an $E_1$ algebra in $\EE_n$ algebras and $B$ is an $\EE_n$ algebra in left $A$-modules. 
+Let $(A,B)$ be a Swiss cheese pair: $A$ is an $E_1$ algebra in $E_n$ algebras and $B$ is an $E_n$ algebra in left $A$-modules. 
 We will freely view these as locally constant factorization algebras on framed $n$-manifolds.
@@
 As a slogan, we say ``factorization homology commutes with taking centers,'' 
-at least for enveloping $\EE_n$ algebras.
+at least for enveloping $E_n$ algebras.
 It is natural to ask whether this result holds in general.
@@
 \begin{qtn}
-Is the canonical map \eqref{eqn: can cen int} a weak equivalence when $\UU_n \fg$ is replaced by an arbitrary $\EE_n$-algebra?
+Is the canonical map \eqref{eqn: can cen int} a weak equivalence when $\UU_n \fg$ is replaced by an arbitrary $E_n$-algebra?
 \end{qtn}
@@
 
-\subsection{Koszul duality for enveloping $\EE_n$ algebras}
-
-\owen{Use corollary~\ref{cor: koszul dual to main theorem} to exhibit a "dual" Swiss cheese pair and then compute the relative tensor product over the center, which will be the unit $\EE_n$ algebra.
+\subsection{Koszul duality for enveloping $E_n$ algebras}
+
+\owen{Use corollary~\ref{cor: koszul dual to main theorem} to exhibit a "dual" Swiss cheese pair and then compute the relative tensor product over the center, which will be the unit $E_n$ algebra.
 Draw a picture of the strip.}
@@
 %
-%The $\EE_n$-center, or $\EE_n$-Hochschild cohomology, of an $\EE_n$-algebra $A$ is the {\em universal} $E_{n+1}$-algebra which acts on $A$. 
+%The $E_n$-center, or $E_n$-Hochschild cohomology, of an $E_n$-algebra $A$ is the {\em universal} $E_{n+1}$-algebra which acts on $A$. 
 %In Section \ref{sec:swiss} below, we will recall an elegant operadic interpretation of this universal picture and interpret it in terms of {\em constructible factorization algebras}. 
-%In the case of $\EE_n$-enveloping algebras, we will provide a strict factorization model of this universal situation in terms of a constructible factorization algebra on an $(n+1)$-dimensional 
+%In the case of $E_n$-enveloping algebras, we will provide a strict factorization model of this universal situation in terms of a constructible factorization algebra on an $(n+1)$-dimensional 
 %manifold with boundary. 
@@
 %We will furthermore provide an interpretation of this constructible factorization algebra in terms of the quantization of a certain topological field theory. 
-%The key insight is that there is a {\em classical limit} of the $\EE_n$-center $\fZ_n(\fg)$ which is equivalent to the observables of an $(n+1)$-dimensional topological field theory known as {\em BF theory}.
+%The key insight is that there is a {\em classical limit} of the $E_n$-center $\fZ_n(\fg)$ which is equivalent to the observables of an $(n+1)$-dimensional topological field theory known as {\em BF theory}.
 %Likewise, there is a classical limit of $\UU_n(\fg)$ which can be viewed as a boundary condition for BF theory.
 %
-%In this sense, topological BF theory is the universal $(n+1)$-dimensional field theory which has the $\EE_n$-enveloping algebra as a boundary condition. 
+%In this sense, topological BF theory is the universal $(n+1)$-dimensional field theory which has the $E_n$-enveloping algebra as a boundary condition. 
 %This partially confirms the terminology used in \cite{ButsonYoo}  of topological BF theory as the ``universal bulk theory" of $\UU_n(\fg)$.
 
-In this section, we turn to an interpretation of the $\EE_n$-center of an $\EE_n$-enveloping algebra in terms of a certain topological field theory (TFT).
+In this section, we turn to an interpretation of the $E_n$-center of an $E_n$-enveloping algebra in terms of a certain topological field theory (TFT).
 
@@
 
-\begin{prp} \label{prp:poisson}
+\begin{prp} 
+\label{prp:poisson}
 The associated graded pair $({\rm Gr} \; \fZ_n(\fg) , {\rm Gr} \; \UU_n(\fg))$ determines an algebra over the operad $\PP_{[n+1,n]}$. 
 \end{prp}
-
-\begin{rmk}
-By a similar proof as in the main part of the paper, we expect that one can see that the factorization algebra
-\[
-\clies \bigg(\Omega^\bu \otimes \fg \; ; \; {\rm Sym} \left(\Omega^\bu_c \otimes \fg [1] \right) \bigg)
-\]
-is a model for the {\em $\PP_n$-center} of the $\PP_n$-enveloping algebra $\UU_{\PP_n} (\fg)$. 
-\end{rmk}
 
@@
 
-\begin{prp}\label{prp:pair}
+\begin{prp}
+\label{prp:pair}
 Let $M$ be a smooth $n$-dimensional manifold and $\fg$ a Lie algebra. 
@@
 
-%Let $\fg$ be a dg Lie algebra and consider the $\EE_n$ algebra $\UU_n \fg$. 
-%We have shown that a model for the $\EE_n$-center ${\frak Z}_n (\UU_n \fg) = {\frak Z}_n ({\rm id}_{\UU_n \fg})$ is the $n$-dimensional locally constant factorization algebra 
+%Let $\fg$ be a dg Lie algebra and consider the $E_n$ algebra $\UU_n \fg$. 
+%We have shown that a model for the $E_n$-center ${\frak Z}_n (\UU_n \fg) = {\frak Z}_n ({\rm id}_{\UU_n \fg})$ is the $n$-dimensional locally constant factorization algebra 
 %\[
@@
 
-\brian{define $\PP_0$ factorization algebra}
-
-The associated graded commutative factorization algebras ${\rm Gr} \; \bU_n (\fg)$ and ${\rm Gr} \; \bZ_n(\fg)$ lift to $\PP_0$-factorization algebras.
+The associated graded factorization algebras ${\rm Gr} \; \bU_n (\fg)$ and ${\rm Gr} \; \bZ_n(\fg)$ are equipped with Poisson brackets that are compatible with the factorization structure.
+
+For $k \geq -1$, a {\em $\PP_k$-factorization algebra} is a factorization algebra $\bA$ such that for every open set $U$ the cochain complex $\bA(U)$ is equipped with the structure of a $\PP_k$-algebra.
+Furthermore, we require that the factorization structure maps be compatible with the $\PP_k$-algebra structure.
+
+Theorem \ref{thm:lurie1} combines with the additivity result of \cite{SafronovAdd} to show that there is an equivalence of categories between the category of locally constant $\PP_k$-factorization algebras on $\RR^n$ and $\PP_{n+k}$-algebras.
+
+In light of this, the following lemma implies that ${\rm Gr} \; \bU_n (\fg)$ and ${\rm Gr} \; \bZ_n(\fg)$ determine $\PP_n$ and $\PP_{n+1}$ algebras respectively.
+
+\begin{lmm}
+\label{lmm:pois1}
+Consider the factorization algebras ${\rm Gr} \; \bU_n (\fg)$ and ${\rm Gr} \; \bZ_n(\fg)$ on a manifold $M$.
+Then
+\begin{itemize}
+\item ${\rm Gr} \; \bU_n (\fg)$ is equipped with the structure of a $\PP_0$-factorization algebra.
+\item ${\rm Gr} \; \bZ_n(\fg)$ is equipped with the structure of a $\PP_1$-factorization algebra.
+\end{itemize}
+\end{lmm}
+
+The pair $(\fZ_n(\fg), \UU_n(\fg))$ is an algebra over the $(n+1)$-dimensional Swiss cheese operad. 
+At the level of the associated graded algebras, we obtain an algebra over a certain classical limit of this operad which takes into account the aforementioned Poisson structures.
+
+The definition of this two-colored operad $\PP_{[n+1,n]}$ can be found in \cite{SafronovCoiso}. 
+A $\PP_{[n+1,n]}$-algebra consists of a pair $(A,B)$ where $A$ is a $\PP_{n+1}$-algebra and $B$ is a $\PP_n$ algebra which receives an action by $A$.
+
+The action of $\bZ_n(\fg)$ on $\bU_n(\fg)$ descends to an action at the level of the associated graded factorization algebras
+Together with Lemma \ref{lmm:pois1}, we obtain Proposition \ref{prp:poisson}.
+
+\begin{rmk}
+One way to formulate the definition of a $\PP_{[n+1,n]}$ algebra $(A,B)$ is to require a map of commutative dg algebras $A \to B$ together with a lift to a map of $\PP_{n+1}$-algebras $A \to \fZ_{\PP_n} (B)$, where $\fZ_{\PP_n}(B)$ is the {\em $\PP_n$-center} of the $\PP_n$-algebra $B$.
+By a similar proof as in the main part of the paper, we expect that one can see that the factorization algebra
+\[
+\clies \bigg(\Omega^\bu \otimes \fg \; ; \; {\rm Sym} \left(\Omega^\bu_c \otimes \fg [1] \right) \bigg)
+\]
+is a model for the $\PP_n$-center of the $\PP_n$-{\em enveloping algebra} $\UU_{\PP_n} (\fg) = {\rm Sym} (\fg [1-n])$. 
+\end{rmk}
 
@@
 %
-%Let us place the locally constant factorization algebra model of the $\EE_n$-enveloping algebra $\bU_n (\fg) = \clieu(\fg \otimes \Omega_c)$ on the $n$-manifold $M$.
+%Let us place the locally constant factorization algebra model of the $E_n$-enveloping algebra $\bU_n (\fg) = \clieu(\fg \otimes \Omega_c)$ on the $n$-manifold $M$.
 %This factorization algebra is equivalent to the pushforward of a factorization algebra $\Obs_{\rm BF}$ on the $(n+1)$-dimensional manifold $M \times \RR$ along the projection $\pi : M \times (0,1) \to M$ which we proceed to construct.
@@
 %We now consider the pushforward factorization algebra $\pi_* \Obs^{\rm cl}_{\rm BF}$ on $M$.
-%Locally, on disks, we will see that it is quasi-isomorphic to a certain limit, or ``dequantization", of our model for the $\EE_n$-center of $\UU_n \fg$.
+%Locally, on disks, we will see that it is quasi-isomorphic to a certain limit, or ``dequantization", of our model for the $E_n$-center of $\UU_n \fg$.
 %Recall, this model is given by the factorization algebra on $M$:
@@
 %\]
-%Notice this is similar to the model $\EE_n$-center except we have turned off the Chevalley--Eilenberg differential on chains. 
+%Notice this is similar to the model $E_n$-center except we have turned off the Chevalley--Eilenberg differential on chains. 
 %
@@
 \def \Fac {\mathrm{Fac}}
-We now need to express the $\EE_n$-structure on ${\rm Mor}_{\LMod_{\int_{S^{n-1}} \UU_n\fg}}(\UU_n \fg, B_f)$ induced by the equivalence of Proposition~\ref{P:ModentoModSn}, and then on the subsequent isomorphic hom spaces of modules morphisms.
+We now need to express the $E_n$-structure on ${\rm Mor}_{\LMod_{\int_{S^{n-1}} \UU_n\fg}}(\UU_n \fg, B_f)$ induced by the equivalence of Proposition~\ref{P:ModentoModSn}, and then on the subsequent isomorphic hom spaces of modules morphisms.
 Since we are going to take advantage of the factorization algebra presentation of $\UU_n( \fg)$, see~Theorem~\ref{T:UnofLie}, we recall the following factorization algebra description of the centralizer.
-Let $\cA \stackrel{f}\to \cB$ be a morphism of locally constant factorization algebras on $\RR^n$ corresponding to an $\EE_n$-algebra map similarly denoted.
+Let $\cA \stackrel{f}\to \cB$ be a morphism of locally constant factorization algebras on $\RR^n$ corresponding to an $E_n$-algebra map similarly denoted.
 Then by Theorems~\ref{thm:lurie1}, \ref{T:centralizer=inthom} the centralizer of $f$ is represented by the locally constant factorization algebra

### 2020-09-08 draft.tex
small changes

@@
 
-The Lie bracket on $\fh$ endows ${\rm Sym} (\fh [1])$ with the additional structure of a $\PP_0$-algebra. 
-On linear elements this is simply the Lie bracket on $\fh$, and one extends to the full symmetric algebra by the graded Leibniz rule.
-
-Consider our factorization model for the $\EE_n$-enveloping algebra $\bU_n(\fg) = \clieu (\fg \otimes \Omega_c)$. 
+Consider our factorization model for the $\EE_n$-enveloping algebra $\bU_n(\fg) = \cliels (\fg \otimes \Omega^\bu_c)$. 
 The filtration on Chevalley--Eilenberg chains equips $\bU_n(\fg)$ with a filtration as a factorization algebra.
@@
 
+\begin{proof}
+For any $L_\infty$ algebra $\fh$, the associated graded of the Chevalley--Eilenberg complex ${\rm Gr} \; \cliels {\rm Sym} (\fh [1])$ is equipped with the structure of a $\PP_0$-algebra.
+It is given by the sum of the $L_\infty$-operations $\ell_2 + \ell_3 + \cdots$. 
+This implies that ${\rm Gr} \; \bU_n (\fg)$ is a $\PP_0$-factorization algebra.
+
+Next, recall that to an open set $U \subset M$ the factorization algebra ${\rm Gr} \; \bZ_n (\fg)$ assigns the cochain complex whose underlying 
+\[
+\clie^\bu\bigg(\fg \otimes \Omega^\bu (U) \; , \; {\rm Sym} \left(\fg \otimes \Omega^\bu_c(U) [1]\right) \bigg) = {\rm Hom}^\bu \bigg(\cliels(\fg \otimes \Omega^\bu(U)) , \cliels (\fg \otimes \Omega^\bu_c(U)) \bigg).
+\]
+\brian{how to handle homs}.
+\end{proof}
+
 The pair $(\fZ_n(\fg), \UU_n(\fg))$ is an algebra over the $(n+1)$-dimensional Swiss cheese operad. 
@@
 The structure map associated to the embedding 
-\[
+\begin{equation}\label{eqn:embed}
 U \sqcup V \times [0, \epsilon) \hookrightarrow V' \times [0,\epsilon')
-\]
+\end{equation}
 is
 \[
-\clies \bigg(\fg \otimes \Omega^\bu (U) \; , \; \Sym \left(\fg \otimes \Omega^\bu_c(U) [2] \right) \bigg) \; \otimes \;  {\rm Sym} \left(\fg \otimes \Omega^\bu_c (V\times [0,\epsilon)) [2] \right) 
-\]
-\brian{finish}
+\begin{tikzcd}
+\clies \bigg(\fg \otimes \Omega^\bu (U) \; , \; \Sym \left(\fg \otimes \Omega^\bu_c(U) [2] \right) \bigg) \; \otimes \;  {\rm Sym} \left(\fg \otimes \Omega^\bu_c (V\times [0,\epsilon)) [2] \right) \ar[d] \\
+\Sym \left(\fg \otimes \Omega^\bu_c(U) [2] \right) \; \otimes \; \Sym \left(\fg \otimes \Omega^\bu_c (V \times [0,\epsilon)) [2] \right) \ar[d] \\
+\Sym\left(\fg \otimes \left(\Omega^\bu_c(U) \oplus \Omega^\bu_c(V \times [0,\epsilon)) \right) [2] \right) \ar[d]\\
+\Sym \left( \fg \otimes \Omega^\bu_c(V' \times [0,\epsilon')) [2] \right)
+\end{tikzcd}
+\]
+The first map projects onto the $\Sym^0$ component of $\clie^\bu$ and the second map uses the fact that the symmetric algebra functor is monoidal. 
+Finally, the third map is induced by the extension of compactly supported de Rham forms along the embedding (\ref{eqn:embed}). 
 \end{dfn}
@@
 
-Next, we provide a construction of a factorization pair on the manifold $M$ from that data of a constructible factorization algebra on $M \times \RR_{\geq 0}$. 
+Next, we provide a construction of a factorization pair on the manifold $M$ from the data of a constructible factorization algebra on $M \times \RR_{\geq 0}$. 
 Suppose $\bA$ is any constructible factorization algebra on a manifold with boundary $M \times \RR_{\geq 0}$. 
@@
 
- \begin{lmm}
- \brian{fix notation}
-Let $M$ be an $n$-dimensional manifold.
-There is a quasi-isomorphism of  $\PP_0$-factorization algebras on $M$:
-\[
-\pi_* \overset{\circ}{\bf Z}_n(\fg) \; \xto{\simeq} \; {\rm Gr} \; \bZ_n(\fg) .
-\]
-where $\pi : M \times \RR_{>0} \to M$ is the projection. 
-\end{lmm}
-
-In fact, we will show that this quasi-isomorphism is a deformation retraction.
-
-\begin{proof}
+We are now ready to prove Proposition \ref{prp:pair}.
+
+\begin{proof}[Proof of Proposition \ref{prp:pair}]
 To exhibit this quasi-isomorphism, we introduce the following cochain maps.
@@
 \end{proof}
-
-Since the universal action of $\bZ_n(\fg)$ on $\bU_n (\fg)$ is compatible with the above filtrations, we obtain the following constructible factorization algebra on $M \times \RR_{\geq 0}$.
 

### 2020-09-08 draft.tex
tft reorganize

@@
 %\end{equation}
-on $M \times \RR_{\geq 0}$ such that the pair 
-\[
-\left( {\bf C}_n (\fg)^\circ \; , \; {\bf C}_n (\fg)^\partial \right)
-\]
-is equivalent to the pair $({\rm Gr} \; \bZ_n(\fg), {\rm Gr} \; \bU_n(\fg))$ as a commutative factorization pair.
+on $M \times \RR_{\geq 0}$ and a quasi-isomorphism of factorization pairs
+\[
+\bigg( {\bf C}_n (\fg)^\circ \; , \; {\bf C}_n (\fg)^\partial \bigg) \xto{\simeq} \bigg({\rm Gr} \; \bZ_n(\fg), {\rm Gr} \; \bU_n(\fg) \bigg).
+\]
+
+In fact, $\bC_n(\fg)$ is a constructible $\PP_0$-factorization algebra and this quasi-isomorphism is compatible with Poisson structures.
 \end{prp}
@@
 To exhibit this quasi-isomorphism, we introduce the following cochain maps.
-For an open set $U \subset M$ let
-\[
-\int_\RR : \Omega_c(U \times \RR) \to \Omega_c (U) [1] 
-\] 
-be the map which integrates a compactly supported form on $U \times \RR$ along $\RR$. 
-This map is a quasi-isomorphism for any $U $ and admits the following explicit retract. 
+For an open set $V \subset M$ let
+\[
+\int_{\RR_{>0}} : \Omega_c(V \times \RR_{>0}) \to \Omega_c (U) [1] 
+\] 
+be the map which integrates a compactly supported form on $U \times \RR_{> 0}$ along $\RR_{> 0}$. 
+This map is a quasi-isomorphism for any $U$ and, in fact, admits the following explicit retract. 
 Let $\phi$ be a fixed compactly supported function on $\RR$ of mass $1$ and define
 \[
-r_\phi : \Omega_c(U) [1] \to \Omega_c (U \times \RR)
+r_\phi : \Omega_c(U) [1] \to \Omega_c (U \times \RR_{\geq 0})
 \]
 by $r_\phi (\alpha) = \alpha \wedge \phi \, \d t$.
+
+Notice that for an open set $V \subset M$ we have 
+\[
+\bC_n(\fg)^{\circ} (V) = \clies \bigg(\fg \otimes \Omega (V \otimes \RR_{>0} ) \; , \; \Sym \left(\fg \otimes \Omega_c(V \times \RR_{>0}) [2] \right) \bigg)  .
+\]
+The map $\int_{\RR_{>0}}$ induces a map of factorization algebras on $M$
+\[
+\int_{\RR_{>0}} : \bC_n(\fg)^\circ \to {\rm Gr} \; \bZ_n (\fg)
+\]
+which on linear elements in ${\rm Sym}(\fg \otimes \Omega^\bu_c (V \times \RR_{>0})$ sends $x \otimes \alpha \in \Omega^\bu_c(V \times \RR_{>0})[2]$ to $x \otimes \int_{\RR_{>0}} \alpha \in \Omega^\bu_c (V)[1]$.
+Using the retract $r_\phi$, we see that this is a quasi-isomorphism of factorization algebras on $M$.
+
+Similarly, integration of compactly supported forms along $\RR_{\geq 0}$ determines a quasi-isomorphism of factorization algebras $\int_{\RR_{\geq 0}} : \bC_n(\fg)^\partial \to {\rm Gr} \; \bU_n(\fg)$.
+
+The pair $(\int_{\RR_{>0}} , \int_{\RR_{\geq 0}})$ is a quasi-isomorphisms of factorization pairs. 
+The compatibility of this quasi-isomorphism with Poisson brackets is a direct calculation. 
 \end{proof}
@@
 
-\brian{intro paragraph}
-
-It is the central theme of \cite{CG1, CG2} that the observables of a perturbative quantum field theory define the structure of a factorization algebra. 
-In this setup, one first uses the Batalin--Vilkovisky (BV) formalism to define a perturbative classical field theory. 
-The key ingredient in this formalism is a $(-1)$-shifted symplectic structure on the classical space of fields. 
-The observables, or functions on the classical space of fields is then equipped with the structure of a $\PP_0$-factorization algebra.
-
-\brian{maybe say AKSZ here}
-
-More recently in \cite{ButsonYoo} and \cite{Eugene}, it is shown how to run the classical BV formalism on manifolds with boundary. 
-Let $N$ be such a manifold with boundary and let $\cE$ denote the space of fields, typically given as the space of sections of a finite rank vector bundle on $N$. 
-The definition of a classical BV theory on $N$ amounts to prescribing the following data:
-\begin{itemize}
-\item[(1)]
-an ordinary classical BV theory on the interior $N \setminus \partial N$ whose space of fields is $\cE|_{N \setminus \partial N}$;
-\item[(2)] 
-a compatible $0$-shifted symplectic structure on $\cE|_{\partial N}$ equipped with a Lagrangian subspace $\cL \subset \cE|_{\partial N}$.
-This is called a {\em boundary condition}.
-\end{itemize}
-From this data at the level of fields, one obtains a constructible $\PP_0$-factorization algebra on the manifold with boundary $N$ at the level of the observables.
+In this section, we describe a relationship of our model of the $\EE_n$-center with a certain topological field theory. 
+This theory admits a natural description via the AKSZ formalism \cite{AKSZ}, which we briefly recount now.
 
@@
 Suppose $N$ is an $(n+1)$-dimensional manifold, which for now we assume has no boundary $\partial N = \emptyset$. 
-In the BV formalism, the perturbative space of fields of topological $BF$ theory on $N$ consists of
-\[
-(A, B) \in \Omega^{\bu} (N) \otimes \fg [1] \oplus \Omega^{\bu} (N) \otimes \fg^* [n-1] .
-\]
-Concretely, the classical moduli space consists of pairs $(A, B)$ where $A \in \Omega^1 (N) \otimes \fg$ and $B \in \Omega^{n-1} (N) \otimes \fg^*$ satisfying the equations
+When $N$ is compact, the classical moduli space underlying this topological field theory can be described as the following mapping space 
+\begin{equation} \label{stack1}
+{\rm Map}(N_{\rm dR} ,  {\rm T}^*[n] {\rm B} G)
+\end{equation}
+where $N_{\rm dR}$ denotes the de Rham stack of $N$ and where $G$ is a Lie group whose Lie algebra is $\fg$. 
+Via the obvious $n$-shifted symplectic structure on ${\rm T}^* [n] {\rm B} G$, the AKSZ formalism equips the mapping space with a $(-1)$-shifted symplectic structure. 
+Classically, on manifolds without boundary, this is the complete description of topological BF theory in the Batalin--Vilkovisky formalism \cite{BV}.
+
+Now, suppose $N$ has non-empty boundary $\partial N \ne 0$.
+Then, (\ref{stack1}) no longer admits a $(-1)$-shifted symplectic structure. 
+However, the AKSZ construction equips 
+\[
+{\rm Map}(\partial N_{\rm dR} , {\rm T}^* [n] {\rm B} G)
+\]
+with a $0$-shifted symplectic structure. 
+Moreover, the restriction map 
+\[
+{\rm Map}(N_{\rm dR} , {\rm T}^* [n] {\rm B} G) \to {\rm Map}(\partial N_{\rm dR} , {\rm T}^* [n] {\rm B} G)
+\]
+is a Lagrangian morphism. 
+%Perturbatively, this mapping stack represents the restriction of the fields to the boundary.
+
+For BF theory, this $0$-shifted symplectic manifold admits another natural Lagrangian. 
+In terms of mapping stacks, it is given by considering maps from $\partial N_{\rm dR}$ into the $n$-shifted conormal bundle of ${\rm B} G$:
+\[
+{\rm Map}(\partial N_{\rm dR} , {\rm N}^*_e [n] {\rm B}G) .
+\]
+Then, by abstract maneuvers \brian{reference} the following fiber product
+\[
+\begin{tikzcd}
+X \ar[r] \ar[d] & {\rm Map} (N , {\rm T}^* [n] {\rm B} G) \ar[d] \\
+{\rm Map}(\partial N_{\rm dR} , {\rm N}^*_e  [n] {\rm B}G) \ar[r] & {\rm Map}(\partial N_{\rm dR} , {\rm T}^*[n]  {\rm B}G)
+\end{tikzcd}
+\]
+is equipped with a $(-1)$-shifted symplectic structure. 
+Heuristically, the classical observables are given by functions on the $(-1)$-shifted symplectic space $X$.
+
+It is the central theme of \cite{CG1, CG2} that the observables of a {\em perturbative} field theory define the structure of a factorization algebra. 
+Moreover, the observables, is equipped with the structure of a $\PP_0$-factorization algebra.
+
+Perturbative BF theory is the formal moduli space is defined by the formal neighborhood of a point in the derived mapping space (\ref{stack1}). 
+For simplicity, we will work near the trivial $G$-bundle. 
+Here, the formal moduli space is described in terms of the following dg Lie algebra 
+\begin{equation}\label{eqn:fields}
+\cL = \Omega^{\bu} (N) \otimes \fg \ltimes \Omega^{\bu} (N) \otimes \fg^* [n-3] .
+\end{equation}
+We denote elements of this dg Lie algebra by pairs $(A,B)$.
+
+The classical {\em fields} of the theory are given by shifting the dg Lie algebra down by one $\cL[1]$. 
+One can read off the $(-1)$-symplectic structure on the fields simply by $\int A \wedge B$.
+
+Perturbatively, the classical moduli space is the space of Maurer--Cartan elements of this dg Lie algebra.
+These are pairs $(A,B)$ where $A \in \Omega^1 (N) \otimes \fg$ and $B \in \Omega^{n-1} (N) \otimes \fg^*$ satisfying the equations
 \begin{align*}
@@
 \end{align*}
-When $N$ is compact, the classical moduli space underlying this field theory has an elegant description in terms of the AKSZ formalism. 
-It can be interpreted as the following mapping stack 
-\begin{equation} \label{stack1}
-{\rm Map}(N_{\rm dR} ,  {\rm T}^*[n] {\rm B} G)
-\end{equation}
-where $N_{\rm dR}$ denotes the de Rham stack of $N$ and where $G$ is a Lie group whose Lie algebra is $\fg$. 
-Perturbative BF theory is obtained by taking the tangent space of the above mapping stack near at the trivial $G$-bundle.
-
-Now, suppose $N$ has a boundary $\partial N \ne 0$.
-Then, (\ref{stack1}) no longer admits a $(-1)$-shifted symplectic structure. 
-However, the AKSZ construction equips 
-\[
-{\rm Map}(\partial N_{\rm dR} , {\rm T}^* [n] {\rm B} G)
-\]
-with a $0$-shifted symplectic structure. 
-Perturbatively, this mapping stack represents the restriction of the fields to the boundary.
-
-For BF theory, there is a natural choice of a Lagrangian for this boundary condition. 
-In terms of mapping stacks, it is given by considering maps from $N_{\rm dR}$ into the $n$-shifted conormal bundle of ${\rm B} G$:
-\[
-{\rm Map}(N_{\rm dR} , {\rm N}^*_e [n] {\rm B}G) .
-\]
-Then, by abstract maneuvers \brian{reference} the following fiber product
-\[
-\begin{tikzcd}
-X \ar[r] \ar[d] & {\rm Map} (N , {\rm T}^* [n] {\rm B} G) \ar[d] \\
-{\rm Map}(\partial N_{\rm dR} , {\rm N}^*_e  [n] {\rm B}G) \ar[r] & {\rm Map}(\partial N_{\rm dR} , {\rm T}^*[n]  {\rm B}G)
-\end{tikzcd}
-\]
-is equipped with a $(-1)$-shifted symplectic structure. 
-Heuristically, the classical observables are given by functions on the $(-1)$-shifted symplectic space $X$.
-
-Perturbatively, we follow \cite{ButsonYoo} and \cite{Eugene} to make the following definition within the BV formalism.
+
+We remark that we are free to replace $\fg$ by an arbitrary $L_\infty$ algebra, which we will do so for the remainder of this section. 
+It is clear that the $L_\infty$-algebra $\cL$ in (\ref{eqn:fields}) can be enhanced to a sheaf of $L_\infty$-algebras. 
+In the setup of \cite{CG2}, the factorization algebra of classical observables is the Chevalley--Eilenberg cochains $\clies (\cL)$.   
+The $\PP_0$-structure is induced from the explicit $(-1)$-symplectic pairing $\int A \wedge B$ at the level of the fields.
+
+So far, we have provided a description of perturbative BF theory on manifolds without boundary. 
+More recently, in \cite{ButsonYoo} and \cite{Eugene}, it is shown how to run the perturbative BV formalism on manifolds with boundary which we follow in the definition below.
+
+%Let $N$ be such a manifold with boundary $\partial N \ne \emptyset$ and let $\cE$ denote the space of fields, typically given as the space of sections of a finite rank vector bundle on $N$. 
+%The definition of a classical BV theory on $N$ amounts to prescribing the following data:
+%\begin{itemize}
+%\item[(1)]
+%an ordinary classical BV theory on the interior $N \setminus \partial N$ whose space of fields is $\cE|_{N \setminus \partial N}$;
+%\item[(2)] 
+%a compatible $0$-shifted symplectic structure on $\cE|_{\partial N}$ equipped with a Lagrangian subspace $\cL \subset \cE|_{\partial N}$.
+%This is called a {\em boundary condition}.
+%\end{itemize}
+%From this data at the level of fields, one obtains a constructible $\PP_0$-factorization algebra on the manifold with boundary $N$ at the level of the observables.
 
 \begin{dfn}
-Let $M$ be an $n$-dimensional manifold.
-{\em Topological BF theory with its universal Neumann boundary condition} is the classical bulk-boundary theory on $M \times \RR_{\geq 0}$ described as follows:
+Let $M$ be an $n$-dimensional manifold and let $\fg$ be an $L_\infty$-algebra. 
+{\em Topological BF theory with its universal Neumann boundary condition} is the classical BV theory on $M \times \RR_{\geq 0}$ described by the following constructible sheaf $\cL$ of $L_\infty$-algebras:
 \begin{itemize}
 \item[(1)] 
-The bulk theory is topological BF theory on $M \times \RR_{>0}$, where the space of fields is 
-\[
-\cE|_{M \times \RR_{>0}} = \Omega^{\bu} (M \times \RR_{>0}) \otimes \fg [1] \oplus \Omega^{\bu} (M \times \RR_{>0}) \otimes \fg^* [n-2] .
+The bulk theory is perturbative topological BF theory on $M \times \RR_{>0}$. 
+That is, to an open set $U \subset M \times \RR_{>0}$ the theory is described by the $L_\infty$-algebra 
+\[
+\cL (U) = \Omega^{\bu} (U) \otimes \fg [1] \ltimes \Omega^{\bu} (U) \otimes \fg^* [n-3] .
 \]
 \item[(2)] 
-The boundary condition is the Lagrangian subspace
-\[
-\Omega^{\bu} (M) \otimes \fg^* [n-2] \subset \cE|_{M \times \{0\}} .
+To an open set $V \times [0,\epsilon)$, we assign the (abelian) $L_\infty$-algebra
+\[
+\cL (V \times [0,\epsilon)) = \Omega^{\bu} (V \times [0,\epsilon)) \otimes \fg^* [n-3] .
 \]
@@
 
-We obtain the following by a direct unpacking of the setup in \cite{Eugene}.
+By definition, the classical observables of perturbative BF theory suppported on an open set $U \subset M \times \RR_{\geq 0}$ is the cochain complex $\clies (\cL (U))$. 
+In \cite{Eugene}, it is shown that the assignment $U \mapsto \clies (\cL(U))$ has the structure of a constructible $\PP_0$-factorization algebra on $M \times \RR_{\geq 0}$.
+
+The main result of this section is that the classical observables are equivalent to our constructible model for the classical limit of the $\EE_n$-center.
 
 \begin{prp}
-The constructible $\PP_0$-factorization algebra of topological BF theory with its universal Neumann boundary condition is equivalent to the constructible factorization algebra $\bC_n(\fg)$. 
+There is a quasi-isomorphism of constructible $\PP_0$-factorization algebras on $M \times \RR_{\geq 0}$:
+\[
+\bC_n (\fg) \xto{\simeq} \clies(\cL) .
+\]
 \end{prp}
+
+\begin{proof}
+Suppose $U \subset M \times \RR_{>0}$ is an open set 
+\end{proof}
 

### 2020-09-08 draft.tex
sec 3.1

@@
 
-\owen{Recall Jacob's results and what it means in conjunction with strictification.}
-
-\owen{I want to work with a colored operad $\Disk_n$ of round disks (or rectilinear boxes) in $\RR^n$.}
-
-\owen{Recall any relevant strictification results.}
-
-Note that in the theorem we use the following equivalence due to Lurie~\cite{LurieHA}.
-
-\begin{thm}
-\label{thm:lurie1} 
-There is an equivalence of $\infty$-categories between $\EE_n$-algebras and locally constant prefactorization algebras on~$\RR^n$. 
+We reemphasize that $\EE_n$ refers to any operad or colored operad or $\infty$-operad equivalent to the topological operad of little $n$-disks.
+
+Let $M$ be a manifold. 
+The collection of disjoint disks in $M$ form a colored operad that we will denote by ${\rm Disk}^\sqcup_M$. 
+When $M = \RR^n$ we will denote this colored operad by ${\rm Disk}^{\sqcup}_n$.
+
+A ${\rm Disk}^\sqcup_M$-algebra $A$ is {\em locally constant} if for any embedding of disks $D \hookrightarrow D'$ in $M$ that the induced map $A(D) \to A(D')$ is an equivalence. 
+When $M = \RR^n$, it is a result of Lurie that the theory of locally constant ${\rm Disk}^\sqcup_n$-algebras is equivalent to the theory of $\EE_n$-algebras.
+
+\begin{thm}[\cite{LurieHA} Proposition 5.4.5.15]
+\label{thm:lurie0} 
+There is a fully faithful embedding of $\infty$-categories
+\[
+{\rm Alg}_{\EE_n} \to {\rm Alg}_{{\rm Disk}^\sqcup_n}
+\]
+whose essential image is the full subcategory of locally constant ${\rm Disk}^\sqcup_n$-algebras. 
 \end{thm}
 
-\owen{Plus a version for $\Disk_n$ algebras}
-
-\brian{notation $\EE$ and $\bE$}
+In the above proposition, we refer to ${\rm Disk}^\sqcup_n$-algebras in the homotopically coherent sense. 
+In particular, the requisite associativity axioms hold up to a prescribed homotopy.
+For algebras over a colored operad satisfying some modest axioms, one can find a ``strictification" which is equivalent to the original homotopically coherent algebra.
+See Theorem 1.1 of \cite{PavlovRectify} for a general result of this type that is sufficient for our purposes. 
+There is a $1$-category of ${\rm Disk}^\sqcup_n$-algebras where we require associativity to hold in the strict sense. 
+By this general strictification result, given any homotopically coherent ${\rm Disk}^{\sqcup}_n$-algebra we can find an equivalent algebra which is an object in this $1$-category.
+
+There is another colored operad ${\rm Opens}^\sqcup_M$ whose colors consist of all connected open subsets of $M$. 
+We note that ${\rm Disk}^\sqcup_M$ is a full subcategory of ${\rm Opens}^\sqcup_M$.
+%The set of operations ${\rm Disj}_M \left(\{U_\alpha\} , V \right)$ consists of a single point if the collection $\{U_\alpha\}$ is pairwise disjoint and are all contained in $V$.
+%Otherwise the set is empty. 
+A {\em prefactorization algebra} on $M$ is an algebra over the colored operad ${\rm Opens}^{\sqcup}_M$. 
+We say a prefactorization algebra on $M$ is locally constant if its associated ${\rm Disk}_n$-algebra is.
+
+Again, the $\infty$-category of prefactorization algebras consists of objects where associativity only holds up to homotopy. 
+We can equally apply strictification for prefactorization algebras: given a homotopy coherent prefactorization algebra, we can find an equivalent object in the $1$-category of strict prefactorization algebras.
+
+A prefactorization algebra is a {\em factorization} algebra if it satisfies a certain codescent condition, see Section 5.5.4 of \cite{LurieHA} or Chapter 6 \cite{CG1}. 
+Locally constant factorization algebras provide another model for $\EE_n$-algebras: there is an equivalence of $\infty$-categories between locally constant factorization algebras on $\RR^n$ and $\EE_n$-algebras.
+
+Throughout the text, we will refer to particular strict factorization (or strict ${\rm Disk}^\sqcup_M$) algebras using bold fonts, e.g. $\bU, \bZ$, etc.. 
+The homotopy coherent $\EE_n$-algebras will be denoted by blackboard font, e.g. $\UU$, except for the centralizer of a map where we will use the symbol $\fZ(f)$.
 
@@
 It is the central theme of \cite{CG1, CG2} that the observables of a {\em perturbative} field theory define the structure of a factorization algebra. 
-Moreover, the observables, is equipped with the structure of a $\PP_0$-factorization algebra.
+Moreover, the observables are equipped with the structure of a $\PP_0$-factorization algebra.
 
@@
 By definition, the classical observables of perturbative BF theory suppported on an open set $U \subset M \times \RR_{\geq 0}$ is the cochain complex $\clies (\cL (U))$. 
-In \cite{Eugene}, it is shown that the assignment $U \mapsto \clies (\cL(U))$ has the structure of a constructible $\PP_0$-factorization algebra on $M \times \RR_{\geq 0}$.
+In \cite{Eugene}, it is shown that the assignment $U \mapsto \clies (\cL(U))$ has the structure of a constructible factorization algebra on $M \times \RR_{\geq 0}$.
 
@@
 \begin{prp}
-There is a quasi-isomorphism of constructible $\PP_0$-factorization algebras on $M \times \RR_{\geq 0}$:
+There is a quasi-isomorphism of constructible factorization algebras on $M \times \RR_{\geq 0}$:
 \[
@@
 \begin{proof}
-Suppose $U \subset M \times \RR_{>0}$ is an open set 
+Suppose $V \times [0,\epsilon) \subset M \times \RR_{\geq 0}$ is an open set. 
+Then, as cochain complexes 
+\[
+\clie^\bu(\cL(V \times [0,\epsilon)) = {\rm Sym} \left(\Bar{\Omega}^\bu_c(V \times [0,\epsilon) [2] \right)  .
+\]
+Here $\Bar{\Omega}^\bu_c$ denotes the compactly supported distributional de Rham forms. 
+By ellipticity, the inclusion $\Omega^\bu \hookrightarrow \Bar{\Omega}^\bu_c$ is a quasi-isomorphism which induces a quasi-isomorphism
+\[
+\bC_n(\fg) (V \times [0,\epsilon)) \hookrightarrow \clie^\bu(\cL(V \times [0,\epsilon)) 
+\]
+as desired. 
+The quasi-isomorphism for the value of the factorization algebras on open sets $U \subset M \times \RR_{>0}$ is defined similarly. 
 \end{proof}

### 2020-09-08 draft.tex
typos

@@
 \end{equation}
-is
+is given by the composition
 \[
@@
 \]
-The first map projects onto the $\Sym^0$ component of $\clie^\bu$ and the second map uses the fact that the symmetric algebra functor is monoidal. 
+The first map evaluates the unit in $\Sym\left(\fg \otimes \Omega^\bu(U)\right)$ and the second map uses the fact that the symmetric algebra functor is monoidal. 
 Finally, the third map is induced by the extension of compactly supported de Rham forms along the embedding (\ref{eqn:embed}). 

### 2020-09-08 draft.tex
version of functoriality finished

--- 2020-09-08 draft.tex
@@
 \end{thm}
+
+{\em Nota bene:}\/ For concision --- and since it is essentially the only kind of map we deal with in this paper --- we simply write $f: \UU_n \fg \to \UU_n \fh$ for the map $\UU_n(f)$ arising from the $L_\infty$ map $f: \fg \rightsquigarrow \fh$.
+Likewise, we write ${\frak Z}_n(f)$ instead of~${\frak Z}_n(\UU_n f)$.
 
@@
 
-This complex $\clies(\fg,\cliels(\fh)_f)$ encodes the deformation theory for $L_\infty$ maps around the map $f$.
-That is, in a sufficiently sophisticated geometric setting, it is the tangent complex to the mapping space of $L_\infty$ maps from $\fg$ to~$\fh$.
-One should view $f$ as the basepoint for this tangent complex.
+This complex $\clies(\fg,\cliels(\fh)_f)$ encodes the deformation theory for $L_\infty$ maps around the map~$f$.
+In concrete terms, the Hom-complex $\Hom^\bullet (\cliels(\fg), \cliels(\fh))$ describes the ``linear space'' of linear maps between those complexes.
+Hence, if we pick a particular map, such as $f$, the underlying graded space of its ``tangent space''
+\[
+T_f \Hom^\bullet (\cliels(\fg), \cliels(\fh))
+\]
+is naturally isomorphic to the ambient linear space,
+but the basepoint $f$ of this tangent space is remembered in the twisted differential $\d_\Hom + [f,-]$.
+In a sufficiently sophisticated geometric setting, there is a moduli space of $L_\infty$ maps from $\fg$ to~$\fh$,
+and $\clies(\fg,\cliels(\fh)_f)$ is this tangent complex with basepoint~$f$.
+
 Due to the splitting $\cliels(\fg) = k \oplus \overline{\cliels(\fg)}$,
@@
 
+We apply our central result to important classes of Lie algebras: 
+abelian, semisimple, and free.
+We also indicate the large $N$ behavior of enveloping algebras for the infinite families $\frak{gl}_N$, $\frak{sp}_N$, and $\frak{so}_N$,
+by exploiting the Loday-Quillen-Tsygan theorem and its cousins.
+
 \subsection{Abelian Lie algebras and an $\EE_n$ HKR theorem}
@@
 
-\owen{Point out how to use LQT map and deduce existence of $\EE_n$ algebra structure on a shifted copy of cyclic cohomology of~$\Omega^*_c$}
+\owen{Point out how to use LQT map and deduce existence of $\EE_n$ algebra structure on a shifted copy of cyclic cohomology of~$\Omega^*_c$.
+Also do the Loday versions that use the other infinite series.}
 
@@
 First, as discussed in Section~\ref{sec: dfn of centralizer fact alg},
-given $L_\infty$ maps $f: \fg \to \fh$, $g: \fh \to \fl$ be  $L_\infty$-algebras morphisms,
+given $L_\infty$ maps $f: \fg \to \fh$ and $g: \fh \to \fl$,
 we obtain canonical $L_\infty$ maps
@@
 maps between their enveloping factorization algebras.
+The composite $L_\infty$ maps $g \circ f: \fg \rightsquigarrow \fl$ determines canonically a map
+\[
+\mathbf{g \circ f}: \bU_n \fg \to \bU_n \fl
+\]
+of factorization algebras.
+
+Now recall that
+\[
+\clies(\Omega^* \otimes \fg, (\bU_n \fh)_f) = \Hom^\bullet(\cliels(\Omega^* \otimes \fg), \cliels(\Omega^*_c \otimes \fh)_f)
+\]
+and similarly for the centralizer~$\bZ_n(g)$.
+As linear maps compose and hence produce pairings between Hom-complexes,
+we expect it should be obvious to produce the desired map
+\begin{align*}
+\Hom^\bullet(\cliels(\Omega^* \otimes \fh), \cliels(\Omega^*_c \otimes \fl)) 
+\otimes \Hom^\bullet(&\cliels(\Omega^* \otimes \fg), \cliels(\Omega^*_c \otimes \fh))\\
+ &\xto{{\rm comp}} \Hom^\bullet(\cliels(\Omega^* \otimes \fg), \cliels(\Omega^*_c \otimes \fl)).
+\end{align*}
+This map is easily concocted thanks to the canonical inclusion $\iota_V: \Omega^*_c(V) \hookrightarrow \Omega^*(V)$ for any open set~$V$.
+Indeed, for any $\varphi \in \Hom^\bullet(\cliels(\Omega^* \otimes \fg), \cliels(\Omega^*_c \otimes \fh))$,
+the composite $\iota_V \circ \varphi|_V$ lives in $\Hom^\bullet(\cliels(\Omega^*(V) \otimes \fg), \cliels(\Omega^*(V) \otimes \fh))$,
+and so we define
+\[
+{\rm comp}(\psi, \varphi)|_V = \psi|_V \circ \iota_V \circ \varphi|_V \in \Hom^\bullet(\cliels(\Omega^*(V) \otimes \fg), \cliels(\Omega^*_c(V) \otimes \fl))
+\]
+on each open~$V$.
+This construction is functorial in the open $V$ and hence determines the desired map ${\rm comp}$.
+
+This construction is {\em almost} what we need, 
+but it does not take into account $f$ or $g$.
+To do that, we need to recall that we view these Hom-complexes as describing the tangent spaces where the maps label the basepoints.
+Once we do, a modest revision of formula above works.
 
@@
 \[
-\varphi =\lambda_\varphi \mathbf{1} +\overline{\varphi}
-\]
-where $\lambda_\varphi \in k$, encoding the component in the first summand, and $\overline{\varphi}$ denotes the component in the second summand.
-
-\begin{dfn}\label{def:comp}
-For any \emph{connected} open set $W$, we define the composition 
-\[
-\bZ_n(g)(W) \otimes \bZ_n(f)(W) \xto{(-\star-)} \bZ_n(g \circ f)(W)
+\varphi =\lambda_\varphi {\bf 1_f} +\overline{\varphi}
+\]
+where $\lambda_\varphi \in k$ encodes the component in the first summand and $\overline{\varphi}$ denotes the component in the second summand.
+
+\begin{dfn}
+\label{def:comp}
+For any open set $V$, we define the composition 
+\[
+\bZ_n(g)(V) \otimes \bZ_n(f)(V) \xto{(-\star-)} \bZ_n(g \circ f)(V)
 \]
@@
 \[
-\psi=\lambda_\psi \mathbf{1} +\overline{\psi} \in \bZ_n(g)(W) = \clies(\fh \otimes \Omega(W), \bU_n \fl (W)  )
+\psi=\lambda_\psi {\bf 1_g} +\overline{\psi} \in \bZ_n(g)(V) = \clies(\fh \otimes \Omega^*(V), (\bU_n \fl (V))_g  )
 \]
@@
 \[
-\varphi =\lambda_\varphi \mathbf{1} +\overline{\varphi}\in \bZ_n(f)(W) = \clies(\fg \otimes \Omega(W), \bU_n \fh (W)  ),
+\varphi =\lambda_\varphi {\bf 1_f} +\overline{\varphi}\in \bZ_n(f)(V) = \clies(\fg \otimes \Omega^*(V), (\bU_n \fh (V))_f  ),
 \] 
@@
 \[
-\psi \star \varphi =  \lambda_{\psi} \lambda_{\varphi} \mathbf{1}+
-\lambda_\psi g\circ \overline{\varphi} + \lambda_{\varphi} \overline{\psi} \circ \iota_W \circ f +\overline{\psi} \circ \iota_W \circ \overline{\varphi} 
-\]
-where the inclusion $\iota_W: \Omega^*_c(W) \hookrightarrow \Omega^*(W)$ is extended in the obvious, functorial way to this setting.
+\psi \star \varphi =  
+\lambda_{\psi} \lambda_{\varphi} \mathbf{1_{g\circ f}}
++ \lambda_\psi \,g \circ \overline{\varphi} 
++ \lambda_{\varphi}\, \overline{\psi} \circ \iota_V \circ f 
++\overline{\psi} \circ \iota_V \circ \overline{\varphi} 
+\]
+where the inclusion $\iota_V: \Omega^*_c(V) \hookrightarrow \Omega^*(V)$ is extended in the obvious, functorial way to this setting.
 \end{dfn}
@@
 
-For a disconnected open $U=\coprod\limits_{i\in I}U_i$, 
-where the $U_i$ are the connected components of $U$,  
-we define the composition $(-\star-)$ by applying it to each component and then applying the structure map of the factorization algebras,
-as follows.
-For any $\psi \in \bZ_n(f)(U)$ and $\varphi \in \bZ_n(g)(U)$,
-we write 
-\[
-\varphi = \mathop{\bigotimes}\limits_{i\in I} \varphi_i
-\]
-where $\varphi_i \in \bZ_n(g)(U_i)$ and likewise $\psi= \mathop{\bigotimes}\limits_{i\in I} \psi_i$.
-Then we define
-\begin{equation} 
-\label{eqdef:staronnonconnected}
-\psi \star \varphi \, := \mu_{\fl} \circ \Big( \bigotimes\limits_{i\in I} (\psi_i \star \varphi_i)\Big) 
-\end{equation}
-where $\mu_{\fl}: \mathop{\bigotimes}\limits_{i\in I} \bU_n \fl (U_i) \cong \bU_n \fl (U)$ 
-is the structure map.
-
-\owen{I pooped out here.}
+\owen{Greg gave the above definition for {\em connected} open sets and then extended it to disconnected open sets b an explicit formula. 
+I don't see why that's necessary (but maybe I'm being silly), so I've cut it as I am aiming for concision.
+We can revive Greg's argument if needed.}
+
+By direct inspection this construction is functorial in opens and respects structure maps.
 
@@
 \label{L:compisfacmap} 
-The composition $$\clies\big(\fh \otimes \Omega, \cliels(\fl \otimes \Omega_c  \big) \otimes 
-\clies\big(\fg \otimes \Omega, \cliels(\fh \otimes \Omega_c  \big)
-\stackrel{(-\star-)}\longrightarrow 
-\clies\big(\fg \otimes \Omega, \cliels(\fl \otimes \Omega_c  \big)
-$$
- is a morphism of factorization algebras.
+The composition 
+\[
+ \bZ_n(g) \otimes  \bZ_n(f) \xto{(-\star-)}  \bZ_n(g \circ f)
+\]
+ is a map of factorization algebras.
 \end{lmm}
 
-\begin{proof}
-
-\end{proof}
-The composition is compatible with the augmentation splitting. Precisely, we have
-\begin{lmm}\label{L:compisaugmented} For any $\varphi \in \clies\big(\fg \otimes \Omega, \cliels(\fh \otimes \Omega_c  \big)$,
-$\psi \in \clies\big(\fh \otimes \Omega, \cliels(\fl \otimes \Omega_c  \big)$
- One has the following equalities  :
+It is also straightforward to check the following properties,
+which we record as a trio of lemmas.
+The first is about associativity.
+
+\begin{lmm}
+\label{L:compisassociative} 
+Let $f: \fg \rightsquigarrow \fh$, $g: \fh \rightsquigarrow \fl$ and $h: \fl \rightsquigarrow \fk$ be maps of $L_\infty$-algebras.
+For any $\varphi \in \bZ_n(f)$, $\psi \in \bZ_n(g)$, and $\gamma \in \bZ_n(h)$,  
+the equality 
+\[ 
+(\gamma\star \psi)\star \varphi \;=\; \gamma\star (\psi \star \varphi)  
+\]
+holds in $\clies\big(\fg\otimes \Omega^*, (\bU_n \fk)_{h \circ g \circ f} \big)$.
+\end{lmm}
+
+The second verifies that augmentations are preserved.
+
+\begin{lmm}
+\label{L:compisaugmented} 
+For any $\varphi \in \bZ_n(g)$ and
+$\psi \in \bZ_n(f)$,
+the following equalities 
 \begin{align}
-  \overline{\psi\star \varphi} \;= \;\mathbf{1}\star \overline{\varphi} +\overline{\psi}\star \mathbf{1} +\overline{\psi}\star \overline{\varphi} 
-  & \quad\mbox{ (in  $\clies\big(\fg \otimes \Omega, \cliels(\fl \otimes \Omega_c  \big) $)}\\
- \mathbf{1}\star \varphi \;=\;  (\lambda_\varphi \mathbf{1}, g\circ \overline{\varphi})\qquad
-  &\quad\mbox{ (in  $k  \oplus \overline{\clies\big(\fg \otimes \Omega, \cliels(\fl \otimes \Omega_c  \big)}$)}\\
-  \psi \star \mathbf{1}\;=\; (\lambda_\psi \mathbf{1}, \overline{\psi} \circ f) \qquad
-  &\quad\mbox{ (in  $k  \oplus \overline{\clies\big(\fg \otimes \Omega, \cliels(\fl \otimes \Omega_c  \big)}$).}
+\overline{\psi\star \varphi} &\;= \;\mathbf{1_g}\star \overline{\varphi} +\overline{\psi}\star \mathbf{1_f} +\overline{\psi}\star \overline{\varphi} \\
+\mathbf{1_g}\star \varphi &\;=\;  (\lambda_\varphi \mathbf{1_{g \circ f}}, g\circ \overline{\varphi})\\
+\psi \star \mathbf{1_f} &\;=\; (\lambda_\psi \mathbf{1_{g \circ f}}, \overline{\psi} \circ f) 
 \end{align}
- In particular, $\mathbf{1} \star \mathbf{1} =\mathbf{1}$.
+hold in $\bZ_n(g \circ f) = k  \oplus \overline{\clies\big(\fg \otimes \Omega^*, (\bU_n \fl)_{g \circ f}  \big)}$.
+In particular, $\mathbf{1_g} \star \mathbf{1_f} =\mathbf{1_{g \circ f}}$.
 \end{lmm}
-\greg{maybe I shoudl use the notation $\mathbf{1}_{\mathbf{f}}$, $\mathbf{1}_{\mathbf{g}}$, $\mathbf{1}_{\mathbf{g\circ f}}$ to differentiate 
-the various spaces in which leaves the units and avoid possible confusion...?}
-\begin{proof}
-
-\end{proof}
-The composition is asscoiative in the following sense.
-\begin{lmm}\label{L:compisassociative} Let $\fg \stackrel{f}\to \fh$, $\fh \stackrel{g}\to \fl$ and $\fl \stackrel{h}\to \fk$ be maps of $L_\infty$-algebras.
- Then, we have, for any $\varphi \in \clies\big(\fg\otimes \Omega, \cliels(\fh \otimes \Omega_c) \big)$, 
-  $\psi \in \clies\big(\fh\otimes \Omega, \cliels(\fl \otimes \Omega_c) \big)$ and  
-  $\gamma \in \clies\big(\fl\otimes \Omega, \cliels(\fk \otimes \Omega_c) \big)$, the equality 
-  \[ (\gamma\star \psi)\star \varphi \;=\; \gamma\star (\psi \star \varphi) \quad \mbox{ in 
-  $\clies\big(\fg\otimes \Omega, \cliels(\fk \otimes \Omega_c) \big)$.}  \]
-\end{lmm}
-\begin{proof}
-
-\end{proof}
-
-\begin{lmm}\label{L:NatPptyofComp}
- The following diagram of factorization algebras 
- \[\tiny \begin{tikzcd}
- \clies\big(\fh \otimes \Omega, \cliels(\fl \otimes \Omega_c  \big) 
- \otimes  \clies\big(\fg \otimes \Omega, \cliels(\fh \otimes \Omega_c  \big) 
- \otimes \cliels(\fg \otimes \Omega_c  \big) \arrow[rd, "(-\star-)\otimes \id"]
+
+The third is about compatibility with the pairings that characterize the centralizers.
+
+\begin{lmm}
+\label{L:NatPptyofComp}
+ The diagram of factorization algebras 
+ \[
+ \small
+ \begin{tikzcd}
+ \bZ_n(g)
+ \otimes  \bZ_n(f) \otimes \bU_n \fg \arrow[rd, "(-\star-)\otimes \id"]
  \arrow[dd, "\id\otimes \ev_ {\mathbf{f}}"]& \\ 
- & \clies\big(\fg \otimes \Omega, \cliels(\fl \otimes \Omega_c  \big) 
- \otimes \cliels(\fg \otimes \Omega_c  \big)
+ & \bZ_n(g \circ f)
+ \otimes \bU_n \fg
  \arrow[dd, "\ev_{\mathbf{g}\circ \mathbf{f}}"]\\
-\clies\big(\fh \otimes \Omega, \cliels(\fl \otimes \Omega_c  \big) 
- \otimes \cliels(\fh \otimes \Omega_c  \big)  \arrow[rd, "\ev_{\mathbf{g}}"] & \\  & \cliels(\fl \otimes \Omega_c  \big). 
-\end{tikzcd}\]
+\bZ_n(g) \otimes \bU_n \fh  \arrow[rd, "\ev_{\mathbf{g}}"] & \\  
+ & \bU_n \fl. 
+\end{tikzcd}
+\]
  is commutative.
@@
 
-\begin{proof}
-\end{proof}
+\owen{I did not include a proof because I think it's immediate once you write down the formulas,
+but maybe I'm overly optimistic.}
 
 \begin{proof}[Proof of Theorem~\ref{T:compcentralizer}]
-By universal property of centralizers, the canonical map~\eqref{eqdef:canonicaltocentralizers}  
-is the unique\footnote{it is unique in the $\infty$-categorical 
-sense, that is there is a contractible space of choices for it} map 
-\[ \Upsilon: {\frak Z}_n(\UU_n g) \otimes {\frak Z}_n(\UU_n f) \longrightarrow {\frak Z}_n\big(\UU_n (g\circ f)\big)\] 
-of $\EE_n$-algebras which makes the following diagram
-\begin{equation}\label{eq:comdiagforcentralizercomput}\small
+By the universal property of centralizers, 
+the canonical map~\eqref{eqdef:canonicaltocentralizers} is the unique map 
+\[ 
+\Upsilon: {\frak Z}_n(g) \otimes {\frak Z}_n(f) \longrightarrow {\frak Z}_n(g\circ f)
+\] 
+of $\EE_n$ algebras (up to a contractible space of choices) that makes the following diagram
+\begin{equation}
+\label{eq:comdiagforcentralizercomput}
 \xymatrix{
 &   &&  
-{\frak Z}_n\big(\UU_n (g\circ f) \big) \otimes  \UU_n \fg  \ar@/^{2pc}/[dddr]^{\ev_{\UU_n (g\circ f)}}\\
-&{\frak Z}_n(\UU_n g) \otimes  {\frak Z}_n(\UU_n f) \otimes \UU_n \fg \ar@/^{1pc}/[rru]_{ \Upsilon \otimes \id_{\UU_n \fg}} \ar[rrd]_{\id\otimes \ev_{\UU_n f}}
-&& (1)
+{\frak Z}_n(g\circ f) \otimes  \UU_n \fg  \ar@/^{2pc}/[dddr]^{\ev_{g\circ f}}\\
+&{\frak Z}_n(g) \otimes  {\frak Z}_n(f) \otimes \UU_n \fg \ar@/^{1pc}/[rru]_{ \Upsilon \otimes \id_{\UU_n \fg}} \ar[rrd]_{\id\otimes \ev_{f}}
+&& (\dagger)
 & & \\
-\UU_n \fg \ar[ur]_{1^{\otimes 2}\otimes \id_{\UU_n \fg}} \ar@/_{1pc}/[rrd]^{\UU_n f} \ar@/^{6pc}/[rrruu]_{1\otimes \id_{\UU_n \fg}} &&&
-{\frak Z}_n(\UU_n g) \otimes \UU_n \fh \ar[rd]^{\ev_{\UU_n h}}  &\\
-&& \UU_n \fh \ar[rr]^{\UU_n g} \ar[ur]^{1\otimes \id_{\UU_n \fh}} && \UU_n \fl .}
+\UU_n \fg \ar[ur]_{1^{\otimes 2}\otimes \id_{\UU_n \fg}} \ar@/_{1pc}/[rrd]^{f} \ar@/^{6pc}/[rrruu]_{1\otimes \id_{\UU_n \fg}} &&&
+{\frak Z}_n(g) \otimes \UU_n \fh \ar[rd]^{\ev_{h}}  &\\
+&& \UU_n \fh \ar[rr]^{g} \ar[ur]^{1\otimes \id_{\UU_n \fh}} && \UU_n \fl .
+}
 \end{equation}
-commutative (since $\UU_n (g\circ f) = \UU_n g\, \circ \, \UU_n f $;  the commutativity of the lower part of the diagram being by definition of centralizers).
-
-By Theorem~\ref{thm:centralizerfactorization}, we know that the factorization algebra models for the centralizers are given by the respective Chevalley-Eilenberg cochain factorizations algebras 
-(Definition~\ref{dfn:CEofFact}) $\clies\big(\fg \otimes \Omega, \cliels(\fh \otimes \Omega_c  \big) $, 
-$\clies\big(\fh \otimes \Omega, \cliels(\fl \otimes \Omega_c  \big) $ and $\clies\big(\fg \otimes \Omega, \cliels(\fl \otimes \Omega_c  \big) $ 
-equipped with the evaluations maps are given by $\ev_{\mathbf{f}}$, $\ev_{\mathbf{g}}$ and $\ev_{\mathbf{g}\circ \mathbf{f}}$. We are thus left 
-to prove that the same  diagram as~\eqref{eq:comdiagforcentralizercomput}, where we replace the objects and maps by their factorization analogue and $\Upsilon$
-by $(-\star-)$, is commutative in factorization algebras.
-
-Thus the map $(-\star-)$ represents the canonical map of factorization algebras 
-$ {\frak Z}(\mathbf{g}) \otimes {\frak Z}(\mathbf{f}) \longrightarrow {\frak Z}(\mathbf{g}\circ \mathbf{f})$ which by proposition~\ref{P:PtyCenter} lifts
-into an $E_1$-algebra map. It remains to check that the structure is on the nose an augmented associative algebra structure.
-The augmentation and unitality are provided by Lemma~\ref{L:compisaugmented} (since in our case $f=g=\id-A$). 
-It remains to prove associativity. It follows from Lemma~\ref{L:compisassociative}. 
-The commutativity of the lower square and triangle of the diagram follows from Lemma~\ref{L:ComTriangCent}.
+commutative.
+%Note that the lower part of the diagram commutes by definition of centralizers.
+
+The diagram above is model-independent,
+but we will check that the analogous diagram~\eqref{eq:comdiagforcentralizercomput} commutes when we use our models $\bU_n \fg$, $\bZ_n(f)$, and so on for the objects and when we use our factorization maps $\ev_{{\bf f}}$ (for $\ev_f$), ${\bf 1}$ (for the unit elements $1$),  and so on.
+In particular, we use $(-\star-)$ for~$\Upsilon$.
+
+The commutativity of the bottom square and bottom triangle follows from Lemma~\ref{L:ComTriangCent}.
+The square with ($\dagger$) in the middle follows from Lemma~\ref{L:NatPptyofComp}.
+The top triangle commutes by Lemma~\ref{L:compisassociative}. 
+Thus we have shown statement~(1) of the theorem.
+
+To prove statement~(2), we note that we have the associative multiplication.
+Since here $f=g=\id_A$, we have the unitality,
+while the augmentation is provided by Lemma~\ref{L:compisaugmented}.
 \end{proof}
-
-\greg{To add: remark that it implies the corollary~\ref{thm: center} and so.}
 
@@
 
-In this section, we describe a relationship of our model of the $\EE_n$-center with a certain topological field theory. 
+In this section, we describe a relationship between our model of the $\EE_n$-center and a certain topological field theory. 
 This theory admits a natural description via the AKSZ formalism \cite{AKSZ}, which we briefly recount now.
@@
 where $N_{\rm dR}$ denotes the de Rham stack of $N$ and where $G$ is a Lie group whose Lie algebra is $\fg$. 
-Via the obvious $n$-shifted symplectic structure on ${\rm T}^* [n] {\rm B} G$, the AKSZ formalism equips the mapping space with a $(-1)$-shifted symplectic structure. 
-Classically, on manifolds without boundary, this is the complete description of topological BF theory in the Batalin--Vilkovisky formalism \cite{BV}.
+Via the canonical $n$-shifted symplectic structure on ${\rm T}^* [n] {\rm B} G$, the AKSZ construction equips the mapping space with a $(-1)$-shifted symplectic structure. 
+Classically, on manifolds without boundary, this produce describes topological BF theory in the Batalin--Vilkovisky formalism~\cite{BV}.
 
@@
 is a Lagrangian morphism. 
+\owen{Somewhere say that $N$ and $\partial N$ are still compact here.}
 %Perturbatively, this mapping stack represents the restriction of the fields to the boundary.
@@
 \]
-Then, by abstract maneuvers \brian{reference} the following fiber product
+Then, by higher abstract nonsense \brian{reference} the fiber product
 \[
@@
 Heuristically, the classical observables are given by functions on the $(-1)$-shifted symplectic space $X$.
+\owen{I'm not sure it's a heuristic. I think we could say that we interpret functions on $X$ as the classical observables for the classical field theory with this boundary condition.}
 

### 2020-09-09 draft.tex
harish chandra

@@
 \[
-\Omega^*_c(\RR^n) \xto{\simeq} \RR[-n]
+\Omega^\bu_c(\RR^n) \xto{\simeq} \RR[-n]
 \]
@@
 \[
-\cliels(\Omega^*_c(\RR^n) \otimes \fg_V) \xto{\simeq} \Sym(V^\bullet).
+\cliels(\Omega^\bu_c(\RR^n) \otimes \fg_V) \xto{\simeq} \Sym(V^\bullet).
 \]
@@
 \bZ_n(\fg_V) &= \clies(\Omega^* \otimes \fg_V, \bU_n \fg_V) \\
-&= \Sym((\Omega^* \otimes \fg_V)^\vee[-1]) \otimes \Sym(\Omega^*_c \otimes \fg_V[1])\\
+&= \Sym((\Omega^\bu \otimes \fg_V)^\vee[-1]) \otimes \Sym(\Omega^\bu_c \otimes \fg_V[1])\\
 & \simeq \Sym(V^\bullet \oplus (V\bullet)^\vee[-n])
@@
 \[
-\Omega^*(\RR^n) \otimes \fg_V \simeq V[-n+1]
+\Omega^\bu (\RR^n) \otimes \fg_V \simeq V[-n+1]
 \]
@@
 \[
-\Sym( (\Omega^*(\RR^n) \otimes \fg_V)^\vee[-1]) \simeq \Sym( V^\vee[-n]).
+\Sym( (\Omega^\bu(\RR^n) \otimes \fg_V)^\vee[-1]) \simeq \Sym( V^\vee[-n]).
 \]
@@
 
+For a reductive Lie algebra $\fg$, the Harish-Chandra isomorphism is an isomorphism of commutative algebras
+\[
+Z(U(\fg)) \xto{\cong} {\rm Sym} (\fh)^W
+\]
+where $\fh$ is a Cartan subalgebra and $W$ is the Weyl group of $\fg$. 
+Here $Z(U(\fg))$ denotes the ordinary center of the associative algebra $U(\fg)$.
+
+The following result generalizes (and implies) the Harish--Chandra isomorphism for the $\EE_n$-center of the $\EE_n$-enveloping algebra.
+
 \begin{prp}
 For $\fg$ a reductive \owen{semisimple?} Lie algebra with Cartan subalgebra~$\fh$ and Weyl group~$W$, 
-there is a quasi-isomorphism of $E_{n+1}$ algebra
-\[
-{\frak Z}_n(\UU_n \fg) \simeq H^*_{\rm Lie}(\fg) \otimes \Sym(\fh[1-n])^W.
+there is a quasi-isomorphism of $\EE_{n+1}$-algebras
+\[
+{\frak Z}_n(\UU_n \fg) \simeq H^\bu_{\rm Lie}(\fg) \otimes \Sym(\fh[1-n])^W.
 \]
@@
 
+\brian{Is there an explicit description of the $\EE_{n+1}$-structure for the RHS?}
+
 \begin{proof}
-\owen{In brief
-\[
-{\frak Z}_n(\UU_n \fg) \simeq \clies(\fg, \Sym(\fg[1-n])
-\]
-and then apply theorems about Lie algebra cohomology plus Chevalley restriction theorem.}
+By the Poincar\'{e} lemma for de Rham forms and compactly supported de Rham forms, one has a canonical quasi-isomorphism
+\[
+\bZ_n(\UU_n \fg) \xto{\simeq} \clies\left(\fg, \Sym(\fg[1-n]) \right) .
+\]
+Since $\fg$ is reductive, there is a quasi-isomorphism \brian{do we actually need semisimple here?}
+\[
+\clies(\fg, \Sym(\fg[1-n]) \simeq H^\bu_{\rm Lie} (\fg) \otimes \Sym(\fg[1-n])^G 
+\]
+where $G$ is a compact connected Lie group whose Lie algebra is $\fg$. 
+Further, by the Chevalley restriction theorem one has 
+\[
+\Sym(\fg[1-n])^G \cong \Sym \left(\fh[1-n]\right)^W .
+\]
 \end{proof}

### 2020-09-09 draft.tex
minor changes

@@
 The diagram above is model-independent,
-but we will check that the analogous diagram~\eqref{eq:comdiagforcentralizercomput} commutes when we use our models $\bU_n \fg$, $\bZ_n(f)$, and so on for the objects and when we use our factorization maps $\ev_{{\bf f}}$ (for $\ev_f$), ${\bf 1}$ (for the unit elements $1$),  and so on.
+but we will check that the analogous diagram~\eqref{eq:comdiagforcentralizercomput} commutes when we use our models $\bU_n (\fg)$, $\bZ_n(f)$, and so on for the objects and when we use our factorization maps $\ev_{{\bf f}}$ (for $\ev_f$), ${\bf 1}$ (for the unit elements $1$),  and so on.
 In particular, we use $(-\star-)$ for~$\Upsilon$.
@@
 
-Next, recall that to an open set $U \subset M$ the factorization algebra ${\rm Gr} \; \bZ_n (\fg)$ assigns the cochain complex whose underlying 
+Next, recall that to an open set $U \subset M$ the factorization algebra ${\rm Gr} \; \bZ_n (\fg)$ assigns the cochain complex
 \[
@@
 \begin{equation}\label{eqn:embed}
-U \sqcup V \times [0, \epsilon) \hookrightarrow V' \times [0,\epsilon')
+i : U \sqcup V \times [0, \epsilon) \hookrightarrow V' \times [0,\epsilon')
 \end{equation}
@@
 \begin{tikzcd}
-\clies \bigg(\fg \otimes \Omega^\bu (U) \; , \; \Sym \left(\fg \otimes \Omega^\bu_c(U) [2] \right) \bigg) \; \otimes \;  {\rm Sym} \left(\fg \otimes \Omega^\bu_c (V\times [0,\epsilon)) [2] \right) \ar[d] \\
-\Sym \left(\fg \otimes \Omega^\bu_c(U) [2] \right) \; \otimes \; \Sym \left(\fg \otimes \Omega^\bu_c (V \times [0,\epsilon)) [2] \right) \ar[d] \\
-\Sym\left(\fg \otimes \left(\Omega^\bu_c(U) \oplus \Omega^\bu_c(V \times [0,\epsilon)) \right) [2] \right) \ar[d]\\
+\clies \bigg(\fg \otimes \Omega^\bu (U) \; , \; \Sym \left(\fg \otimes \Omega^\bu_c(U) [2] \right) \bigg) \; \otimes \;  {\rm Sym} \left(\fg \otimes \Omega^\bu_c (V\times [0,\epsilon)) [2] \right) \ar[d, "{\rm ev}_1"] \\
+\Sym \left(\fg \otimes \Omega^\bu_c(U) [2] \right) \; \otimes \; \Sym \left(\fg \otimes \Omega^\bu_c (V \times [0,\epsilon)) [2] \right) \ar[d, "\simeq"] \\
+\Sym\left(\fg \otimes \left(\Omega^\bu_c(U) \oplus \Omega^\bu_c(V \times [0,\epsilon)) \right) [2] \right) \ar[d, "i_*"]\\
 \Sym \left( \fg \otimes \Omega^\bu_c(V' \times [0,\epsilon')) [2] \right)
@@
 \]
-The first map evaluates the unit in $\Sym\left(\fg \otimes \Omega^\bu(U)\right)$ and the second map uses the fact that the symmetric algebra functor is monoidal. 
+The first map ${\rm ev}_1$ evaluates the unit $1$ in $\Sym\left(\fg \otimes \Omega^\bu(U)\right)$ and the second map uses the fact that the symmetric algebra functor is monoidal. 
 Finally, the third map is induced by the extension of compactly supported de Rham forms along the embedding (\ref{eqn:embed}). 
@@
 \begin{proof}
-Note that as an underlying graded vector space $\Tilde{\bZ}_n(\fg) (U)$ is of the form
+For $U \subset M \times \RR_{>0}$ the underlying graded vector space of $\bC_n(\fg)(U)$ is of the form
 \[
@@
 \]
-\brian{explain notation with homs} 
-Let $x^* \otimes \alpha$ denote an element of $\fg \otimes \Bar{\Omega}_c (U)$ and $y \otimes \beta$ denote an element of $\fg \otimes \Omega_c(U) [2]$. 
-Then, the bracket involving the linear elements $(x^* \otimes \alpha) \otimes 1$ 
-and $1 \otimes (y \otimes \beta)$ is defined by
+Let $x^* \otimes \alpha$ denote an homorphism of the form $\fg \otimes \Omega (U) \to \Sym^0 = k$ and $y \otimes \beta$ denote a homomorphism $k = \Sym^0 \to \fg \otimes \Omega_c(U) [2]$. 
+Then, the bracket involving the linear elements $x^* \otimes \alpha$ 
+and $y \otimes \beta$ is defined by
 \begin{align*}
-\{(x^* \otimes \alpha) \otimes 1 , 1 \otimes (y \otimes \beta)\} & = \<x^*, y\>_\fg \int_U \alpha \beta \\
-\{(x^* \otimes \alpha) \otimes 1 , (x'^* \otimes \alpha') \otimes 1\} & = 0 \\
-\{1 \otimes (y \otimes \beta) , 1 \otimes (y' \otimes \beta')\} & = 0 . 
+\{x^* \otimes \alpha  , y \otimes \beta \} & = \<x^*, y\>_\fg \int_U \alpha \beta \\
+\{x^* \otimes \alpha , x'^* \otimes \alpha' \} & = 0 \\
+\{y \otimes \beta , y' \otimes \beta'\} & = 0 . 
 \end{align*}
 Here, $\<x^*, y\>_\fg$ denotes the linear pairing between $\fg$ and $\fg^*$ and $\int_U\alpha \beta$ denotes the linear pairing between compactly supported distributional differential forms and differential forms.
+\brian{how to say this now}
 The bracket is extended to the entire symmetric algebra by using the graded Leibniz rule.

### 2020-09-09 draft.tex
edits in section on calculus

--- 2020-09-08 draft.tex
@@
 between their enveloping $\EE_n$ algebras.
-The centralizer of this map ${\frak Z}_n(\UU_n f)$ is an $\EE_n$-algebra modeled by the factorization algebra 
+The centralizer of this map ${\frak Z}_n(\UU_n f)$ is an $\EE_n$ algebra modeled by the factorization algebra 
 \[
@@
 
-\owen{I think we could (and maybe should) also discuss the $\EE_n$-Koszul dual situation involving cochains.}
+\owen{I think we could (and maybe should) also discuss the $\EE_n$ Koszul dual situation involving cochains.}
 
@@
 
-\greg{Somewhere we should recall that $\UU_n$ and its center are unoriented $\EE_n$-algebras and define factorization algebras over any manifold that came from the formula}
+\greg{Somewhere we should recall that $\UU_n$ and its center are unoriented $\EE_n$ algebras and define factorization algebras over any manifold that came from the formula}
 
@@
 A ${\rm Disk}^\sqcup_M$-algebra $A$ is {\em locally constant} if for any embedding of disks $D \hookrightarrow D'$ in $M$ that the induced map $A(D) \to A(D')$ is an equivalence. 
-When $M = \RR^n$, it is a result of Lurie that the theory of locally constant ${\rm Disk}^\sqcup_n$-algebras is equivalent to the theory of $\EE_n$-algebras.
+When $M = \RR^n$, it is a result of Lurie that the theory of locally constant ${\rm Disk}^\sqcup_n$-algebras is equivalent to the theory of $\EE_n$ algebras.
 
@@
 A prefactorization algebra is a {\em factorization} algebra if it satisfies a certain codescent condition, see Section 5.5.4 of \cite{LurieHA} or Chapter 6 \cite{CG1}. 
-Locally constant factorization algebras provide another model for $\EE_n$-algebras: there is an equivalence of $\infty$-categories between locally constant factorization algebras on $\RR^n$ and $\EE_n$-algebras.
+Locally constant factorization algebras provide another model for $\EE_n$ algebras: there is an equivalence of $\infty$-categories between locally constant factorization algebras on $\RR^n$ and $\EE_n$ algebras.
 
 Throughout the text, we will refer to particular strict factorization (or strict ${\rm Disk}^\sqcup_M$) algebras using bold fonts, e.g. $\bU, \bZ$, etc.. 
-The homotopy coherent $\EE_n$-algebras will be denoted by blackboard font, e.g. $\UU$, except for the centralizer of a map where we will use the symbol $\fZ(f)$.
+The homotopy coherent $\EE_n$ algebras will be denoted by blackboard font, e.g. $\UU$, except for the centralizer of a map where we will use the symbol $\fZ(f)$.
 
@@
 \begin{rmk}
-It follows from theorem~\ref{T:UnofLie} that for any $\EE_n$-algebra $B$, 
+It follows from theorem~\ref{T:UnofLie} that for any $\EE_n$ algebra $B$, 
 its underlying complex is equipped with a homotopy-coherent Lie algebra structure.
@@
 as $E_1$ algebras.
-
-Recall from Section~\ref{sec: enveloping} that $\UU_n \fg$ admits two convenient models:
-as a factorization algebra by $\bU_n \fg$ and as a strict algebra over a colored operad $\Disk_n$ assigning $\Sym(\fg[1-n])$ to each disk.
-For $n > 1$ that is a commutative algebra.
-\owen{Should I say that??? And should we remark that the $n=1$ case is known???}
+Recall as well that $\UU_n \fg$ is quasi-isomorphic to $\Sym(\fg[1-n])$ as cochain complexes.
 
@@
 and hence provides a free dg commutative algebra.
-This feature can be leveraged to prove the following result about $\EE_n$-centers of free commutative algebras.
+This feature can be leveraged to prove the following result about $\EE_n$ centers of free commutative algebras.
 
@@
 
-\owen{If I'm understanding, this section shows that our construction satisfies the ``composition'' of centralizers on the nose. One corollary is that the center has a strict associative product!}
-
 The universal property of centralizer (recall definition~\ref{D:centralizer}) implies that 
-for any maps $A\stackrel{f}\to B$ and $B\stackrel{g}\to C$ of $\EE_n$-algebras, 
-there is a natural map of $\EE_n$-algebras
+for any maps $A\stackrel{f}\to B$ and $B\stackrel{g}\to C$ of $\EE_n$ algebras, 
+there is a natural map of $\EE_n$ algebras
 \begin{equation}
@@
 \end{equation}
-that arises from following commutative diagram of $\EE_n$-algebras:
+that arises from following commutative diagram of $\EE_n$ algebras:
 \[
@@
 \end{equation}
-Lurie \cite{HA} has proved that this multiplication makes the center into an $E_1$ algebra in $\EE_n$-algebras 
+Lurie \cite{HA} has proved that this multiplication makes the center into an $E_1$ algebra in $\EE_n$ algebras 
 and therefore an $E_{n+1}$-algebra, by Dunn additivity. 
@@
 
-The $\EE_n$-center, or $\EE_n$-Hochschild cohomology, of an $\EE_n$-algebra $A$ is the {\em universal} $E_{n+1}$-algebra that acts on $A$ {\em qua} $\EE_n$ algebra.
-
-In Section \ref{sec:swiss} below, we will recall an elegant operadic articulation of this idea and rephrase it in terms of {\em constructible factorization algebras} on a half-space~$\HH^{n+1}$.
-
-\owen{Mention lots of prior work, e.g., Greg et al, Ayala-Francis, Geoffroy Horel, and so on}
-
-%
-%\brian{HKR}
-%
-%Consider the case $n=1$ and $B = U \fg$ where $f$ is simply the identity map. 
-%A classic result of \cite{HochSerre} is that the Hochschild cohomology of $U \fg$ can be expressed in terms of Lie algebra cohomology as $\Hoch^*(U\fg,U\fg) \simeq \clies(\fg, U\fg^{ad})$. 
-%On the right-hand side, we take the Chevalley--Eilenberg cochain complex with values in the module $U \fg$ equipped with the adjoint action.
-%The algebra structure is given by a special case of the convolution product as in Section \ref{??}. 
-%
-%On the other hand, our model for the derived center ${\frak Z}(U(\fg))$ of $U \fg$ is the one-dimensional factorization algebra assigning the cochain complex
-%\[
-%\clies(\fg \otimes \Omega^*(U), \cliels( \fg \otimes \Omega^*_c(U)))
-%\]
-%to each open set $U \subset \RR$.
-%In the case that $U$ is an interval, this cochain complex is quasi-isomorphic to $\clies (\fg , U\fg^{ad})$.
-%Furthermore, one can verify that the resulting $E_1$-algebra structure agrees with the one coming from convolution. 
-%
-%Our model also gives us a simple description of the factorization homology of the derived center along the circle $S^1$.
-%\[
-%\int_{S^1} {\frak Z}(U(\fg)) \simeq \clies(\fg[\epsilon], \cliels( \fg[\epsilon])),
-%\]
-%where $\epsilon$ is a formal variable of degree~$1$. 
-%\brian{We should compare with Tamarkin-Tsygan's noncommutative calculus (cf. section 2.6).
-%We could exhibit Theorem 2.7.1 explicitly in this case for the $\EE_n$ case with enveloping algebras.}
+The $\EE_n$ center ${\frak Z}_n(A)$ of an $\EE_n$ algebra $A$ is a rich object 
+and controls how other algebras can act on $A$ as an $\EE_n$ algebra.
+In a precise sense that we will discuss below, 
+it is the {\em universal} $\EE_{n+1}$-algebra that acts on $A$ {\em qua} $\EE_n$ algebra.
+
+As a familiar example, consider the degenerate situation of an $\EE_0$ algebra $V$, 
+which is simply a cochain complex with a cochain map $k \to V$.
+The $\EE_0$ center ${\frak Z}_0(V)$ is then $\End^\bullet(V)$,
+the dg associative algebra that controls all actions of algebras on~$V$:
+an action of an algebra $A$ on $V$ is equivalent to giving an algebra map $A \to \End^\bullet(V)$.
+As another example, the $\EE_1$ center of a dg associative algebra $A$ is modeled by the Hochschild cochains $\Hoch^\bullet(A,A)$,
+which is an $\EE_2$ algebra by Deligne's conjecture and which controls actions of $\EE_2$ algebras on~$A$.
+
+Our model for $\EE_n$ centers of enveloping $\EE_n$ algebras provides useful insight into the behavior of centers and into how they interact with factorization homology.
+
+Before we explore consequence of our results,
+we review some key results about $\EE_n$ centers and how they act.
+In Section \ref{sec:swiss} below, we will recall an elegant operadic articulation of how an $\EE_{n+1}$ algebra can act on an $\EE_n$ algebra 
+and then we rephrase it in terms of {\em constructible factorization algebras} on a half-space~$\HH^{n+1}$. 
+\owen{Mention lots of prior work, e.g., Greg et al, Ayala-Francis, Geoffroy Horel, and so on}.
 
@@
 The operad of little $n$-disks is built from configurations of disjoint unions of $n$-disks inside $n$-dimensional Euclidean space.
-The $(n+1)$-dimensional Swiss cheese operad is a two-colored operad whose algebras include pairs $(B, M)$ where $B$ is an $\EE_{n+1}$-algebra, $M$ is an $\EE_n$-algebra, and where $M$ is a left-module for $B$.
+The $(n+1)$-dimensional Swiss cheese operad is a two-colored operad whose algebras include pairs $(B, M)$ where $B$ is an $\EE_{n+1}$-algebra, $M$ is an $\EE_n$ algebra, and where $M$ is a left-module for $B$.
 
@@
 \begin{qtn}
-Is the canonical map \eqref{eqn: can cen int} a weak equivalence when $\UU_n \fg$ is replaced by an arbitrary $\EE_n$-algebra?
+Is the canonical map \eqref{eqn: can cen int} a weak equivalence when $\UU_n \fg$ is replaced by an arbitrary $\EE_n$ algebra?
 \end{qtn}
 
-\owen{We should see if that's what Tamarkin-Tsygan prove for  $E_1$ algebras, as it would be further evidence.}
+Even in the classical setting of associative algebras, it seems \dots
+
+\owen{For all the associative algebras I tried, it seemed like this way true, but I only tried a very short list ...}
 
@@
 
-\owen{Then ask what is the factorization homology on a compact manifold with boundary, which leads into next section.}
+In the case $k = 0$, we have the immediate corollary that
+\[
+\int_{S} \fZ_n(\fg) \simeq \fZ_0 \left( \int_S \UU_n \fg \right) ,
+\]
+which unwinds to 
+\[
+\clies(\fg \otimes \Omega^*(S), \cliels(\fg \otimes \Omega^*(S)) \simeq \End^\bullet(\cliels(\fg \otimes \Omega^*(S))),
+\]
+which looks rather tautological.
+Nonetheless, by using other models for factorization homology,
+one obtains less obvious identifications.
+
+Consider first the case $n=1$ and $B = U \fg$. 
+A classic result of \cite{HochSerre} is that the Hochschild cohomology of $U \fg$ can be expressed in terms of Lie algebra cohomology as 
+\[
+\Hoch^*(U\fg,U\fg) \simeq \clies(\fg, U\fg^{ad}).
+\] 
+On the right-hand side, we take the Chevalley--Eilenberg cochain complex with values in the module $U \fg$ equipped with the adjoint action.
+The algebra structure is given by a special case of the convolution product as in Section~\ref{??}.
+
+On the other hand, our model for the derived center ${\frak Z}(U(\fg))$ of $U \fg$ is the one-dimensional factorization algebra assigning the cochain complex
+\[
+\clies(\fg \otimes \Omega^*(U), \cliels( \fg \otimes \Omega^*_c(U)))
+\]
+to each open set $U \subset \RR$.
+In the case that $U$ is an interval, this cochain complex is quasi-isomorphic to $\clies (\fg , U\fg^{ad})$.
+Furthermore, one can verify that the resulting $E_1$-algebra structure agrees with the one coming from convolution.
+
+Our model also gives us a simple description of the factorization homology of the derived center along the circle~$S^1$:
+\begin{align*}
+\Hoch_*(\Hoch^*(U \fg, U\fg)) 
+&\simeq \int_{S^1} {\frak Z}(U(\fg)) \\
+&\simeq \clies(\fg[\epsilon], \cliels( \fg[\epsilon])),
+\end{align*}
+where $\epsilon$ is a formal variable of degree~$1$. 
+In the last step we use the fact that the circle is formal as a rational space.
+\brian{We should compare with Tamarkin-Tsygan's noncommutative calculus (cf. section 2.6).
+We could exhibit Theorem 2.7.1 explicitly in this case for the $\EE_n$ case with enveloping algebras.}
+
+\owen{Other manifolds? Products of circles? Spheres?}
 
@@
 %
-%The $\EE_n$-center, or $\EE_n$-Hochschild cohomology, of an $\EE_n$-algebra $A$ is the {\em universal} $E_{n+1}$-algebra which acts on $A$. 
+%The $\EE_n$ center, or $\EE_n$ Hochschild cohomology, of an $\EE_n$-algebra $A$ is the {\em universal} $E_{n+1}$-algebra which acts on $A$. 
 %In Section \ref{sec:swiss} below, we will recall an elegant operadic interpretation of this universal picture and interpret it in terms of {\em constructible factorization algebras}. 
@@
 
-In this section, we turn to an interpretation of the $\EE_n$-center of an $\EE_n$-enveloping algebra in terms of a certain topological field theory (TFT).
-
-Given an $\EE_n$-algebra $A$, the pair $(\fZ_n (A) , A)$ is an algebra over the $(n+1)$-dimensional Swiss cheese operad. 
-The first objective is to define a certain ``classical limit" of this pair in the case that $A$ is an $\EE_n$-enveloping algebra.
+In this section, we turn to an interpretation of the $\EE_n$ center of an $\EE_n$ enveloping algebra in terms of a certain topological field theory (TFT).
+
+Given an $\EE_n$ algebra $A$, the pair $(\fZ_n (A) , A)$ is an algebra over the $(n+1)$-dimensional Swiss cheese operad. 
+The first objective is to define a certain ``classical limit" of this pair in the case that $A$ is an $\EE_n$ enveloping algebra.
 
@@
 
-The key insight is that there exists a filtration on our model $\bZ_n(\fg)$ for the $\EE_n$-center and our model $\bU_n (\fg)$ for the $\EE_n$-enveloping algebra  whose associated graded factorization algebras ${\rm Gr} \; \bZ_n(\fg)$ and ${\rm Gr} \; \bU_n(\fg)$ are commutative factorization algebras.
+The key insight is that there exists a filtration on our model $\bZ_n(\fg)$ for the $\EE_n$ center and our model $\bU_n (\fg)$ for the $\EE_n$ enveloping algebra  whose associated graded factorization algebras ${\rm Gr} \; \bZ_n(\fg)$ and ${\rm Gr} \; \bU_n(\fg)$ are commutative factorization algebras.
 
 Given a filtered associative algebra whose associated graded is commutative, there exists a Poisson bracket on the associated graded algebra. 
-If the associated graded of a filtered $\EE_n$-algebra is commutative, then it carries the structure of a $\PP_n$-algebra, which is similar to a Poisson algebra except the bracket is of cohomological degree $1-n$.
+If the associated graded of a filtered $\EE_n$ algebra is commutative, then it carries the structure of a $\PP_n$-algebra, which is similar to a Poisson algebra except the bracket is of cohomological degree $1-n$.
 There is a similar description of the ``classical limit"  of algebras over the $(n+1)$-dimensional Swiss cheese operad in terms of algebras over a certain two-colored operad $\PP_{[n+1,n]}$, introduced by Safronov \cite{Pavel1, Pavel2}, whose definition we recall below.
@@
 In the previous section, we mentioned another geometric model for algebras over the $(n+1)$-dimensional Swiss cheese operad in terms of constructible factorization algebras on $(n+1)$-manifolds with boundary.
-One drawback of the previous section is that we did not provide a model of this type for the $\EE_n$-center of an enveloping algebra. 
-The next goal of this section is to provide a model of the classical limit of the $\EE_n$-center as a constructible factorization algebra.
+One drawback of the previous section is that we did not provide a model of this type for the $\EE_n$ center of an enveloping algebra. 
+The next goal of this section is to provide a model of the classical limit of the $\EE_n$ center as a constructible factorization algebra.
 
@@
 %Let $\fg$ be a dg Lie algebra and consider the $\EE_n$ algebra $\UU_n \fg$. 
-%We have shown that a model for the $\EE_n$-center ${\frak Z}_n (\UU_n \fg) = {\frak Z}_n ({\rm id}_{\UU_n \fg})$ is the $n$-dimensional locally constant factorization algebra 
+%We have shown that a model for the $\EE_n$ center ${\frak Z}_n (\UU_n \fg) = {\frak Z}_n ({\rm id}_{\UU_n \fg})$ is the $n$-dimensional locally constant factorization algebra 
 %\[
@@
 
-We prove Proposition \ref{prp:swiss1} by exhibiting a filtration at the level of strict factorization algebras in our model of the $\EE_n$-center.
+We prove Proposition \ref{prp:swiss1} by exhibiting a filtration at the level of strict factorization algebras in our model of the $\EE_n$ center.
 
@@
 
-Consider our factorization model for the $\EE_n$-enveloping algebra $\bU_n(\fg) = \cliels (\fg \otimes \Omega^\bu_c)$. 
+Consider our factorization model for the $\EE_n$ enveloping algebra $\bU_n(\fg) = \cliels (\fg \otimes \Omega^\bu_c)$. 
 The filtration on Chevalley--Eilenberg chains equips $\bU_n(\fg)$ with a filtration as a factorization algebra.
 
-There is a similar filtration on our model for the $\EE_n$-center $\bZ_n(\fg)$ defined by
+There is a similar filtration on our model for the $\EE_n$ center $\bZ_n(\fg)$ defined by
 \[
@@
 
-We turn towards a model for the $\EE_n$-center as a constructible factorization algebra.
+We turn towards a model for the $\EE_n$ center as a constructible factorization algebra.
 
@@
 
-In this section, we describe a relationship between our model of the $\EE_n$-center and a certain topological field theory. 
+In this section, we describe a relationship between our model of the $\EE_n$ center and a certain topological field theory. 
 This theory admits a natural description via the AKSZ formalism \cite{AKSZ}, which we briefly recount now.
@@
 
-The main result of this section is that the classical observables are equivalent to our constructible model for the classical limit of the $\EE_n$-center.
+The main result of this section is that the classical observables are equivalent to our constructible model for the classical limit of the $\EE_n$ center.
 
@@
 \def \Fac {\mathrm{Fac}}
-We now need to express the $\EE_n$-structure on ${\rm Mor}_{\LMod_{\int_{S^{n-1}} \UU_n\fg}}(\UU_n \fg, B_f)$ induced by the equivalence of Proposition~\ref{P:ModentoModSn}, and then on the subsequent isomorphic hom spaces of modules morphisms.
+We now need to express the $\EE_n$ structure on ${\rm Mor}_{\LMod_{\int_{S^{n-1}} \UU_n\fg}}(\UU_n \fg, B_f)$ induced by the equivalence of Proposition~\ref{P:ModentoModSn}, and then on the subsequent isomorphic hom spaces of modules morphisms.
 Since we are going to take advantage of the factorization algebra presentation of $\UU_n( \fg)$, see~Theorem~\ref{T:UnofLie}, we recall the following factorization algebra description of the centralizer.
-Let $\cA \stackrel{f}\to \cB$ be a morphism of locally constant factorization algebras on $\RR^n$ corresponding to an $\EE_n$-algebra map similarly denoted.
+Let $\cA \stackrel{f}\to \cB$ be a morphism of locally constant factorization algebras on $\RR^n$ corresponding to an $\EE_n$ algebra map similarly denoted.
 Then by Theorems~\ref{thm:lurie1}, \ref{T:centralizer=inthom} the centralizer of $f$ is represented by the locally constant factorization algebra

### 2020-09-09 draft.tex
simplified knudsens theorem

@@
 
-\owen{Add remark that by Dunn's additivity theorem, the center has a natural $E_{n+1}$ algebra structure.}
-\greg{I will add stuff and rewrite that later, hopefully to explain ``how'' to see the $E_{n+1}$-structure}
-
 \greg{We could relate this to $P_n$-center of $\fg$. That shall also (but I have to think about the proof more), 
-at least up to formality gives the $P_{n+1}$-structure on it. }
-
-If $\epsilon: \fg \to 0$ is the trivial map, then we obtain the canonical augmentation $\epsilon: \UU_n \fg \to k$ of $\EE_n$ algebras.
+at least up to formality gives the $P_{n+1}$-structure on it. }\owen{Brian now does this in the TFT section.}
+
+If $\epsilon: \fg \to 0$ is the trivial map, then by taking the enveloping $\EE_n$ algebras, we obtain the canonical augmentation $\epsilon: \UU_n \fg \to k$ of $\EE_n$ algebras.
 In this case, we obtain a version of Koszul duality as the corollary.
@@
 
-\greg{Somewhere we should recall that $\UU_n$ and its center are unoriented $\EE_n$ algebras and define factorization algebras over any manifold that came from the formula}
-
 \subsection{Comments on a generalization}
@@
 
-\owen{Add overview}
+In this section we review key definitions and facts from the literature on $\EE_n$ and factorization algebras.
 
@@
 
-Although \cite{Knudsen} develops an adjunction between Lie and $\EE_n$ algebras \mahmoud{non-unital?}\greg{Both I think}\owen{augmented is probably best for us}
+Although \cite{Knudsen} develops an adjunction between Lie and augmented $\EE_n$ algebras
 in any presentable symmetric monoidal stable $\infty$-category $\cC$,
-we only work in the $\infty$-category of chain complexes $(\Mod_k, \otimes_k)$, 
+we only work in the $\infty$-category of cochain complexes $(\Ch_k, \otimes_k)$, 
 where $k$ is a field of characteristic zero.
@@
 \begin{thm}\label{T:UnofLie}
-There is a commuting square of adjunctions
+There is an adjunction of $\infty$-categories
 \[
 \begin{tikzcd}
-\Alg_\Lie(\Mod_k) \arrow[r, bend left=20, shift left=.5ex,"\UU_n"] \arrow[dd] & \Alg_{\EE_n}(\Mod_k) \arrow[l, shift left=.5ex, "\oblv_n"] \arrow[dd]\\
-&\\
-\Mod_k \arrow[r, bend left=20, shift left=.5ex, "\Sigma^{1-n}"] \arrow[uu, bend left=20, shift left=.5ex, "\Free_\Lie"] & \Mod_k \arrow[l, shift left=.5ex,"\Sigma^{n-1}"] \arrow[uu, bend right=20, shift right=.5ex, "\Free_{\EE_n}"']
+\Alg_\Lie(\Ch_k) \arrow[r, bend left=20, shift left=.5ex,"\UU_n"]  & \Alg_{\EE_n}(\Ch_k) \arrow[l, shift left=.5ex, "\oblv_n"]
 \end{tikzcd}
 \]
-\greg{Also explains what commutatrive means here ? Meaning the curved arrow diagram and the straight arrow diagram only; not combos of such}
-\mahmoud{explain what oblv stands for}
-where $\Sigma$ denotes suspension \owen{because tikzcd does weird things with ``[1-n]'' instead}, \mahmoud{earlier we denoted the shift by [n]. should we use $\Sigma^n$ everywhere?}.
-(Curving arrows denote left adjoints.)
+where $\oblv_n$ denotes a ``forgetful'' functor from $\EE_n$ algebras to Lie algebras.
+
+Both $\infty$-categories admit canonical forgetful functors to $\Ch_k$ and we denote both functors by $\oblv$;
+these functors have left adjoints $\Free_\Lie$ and $\Free_{\EE_n}$, respectively.
+There is a natural equivalence
+\[
+\UU_n (\Free_\Lie V) \simeq \Free_{\EE_n}(V[1-n])
+\]
+for every cochain complex~$V$.
 
@@
 
-The second part of this result leads to the explicit models in our theorems.
-
-\owen{Add discussion of how this makes sense even on unoriented manifolds.}
+The final part of this result leads to the explicit models in our theorems.
+
+\begin{rmk}
+An appealing aspect of this result is that it makes manifest why such enveloping $\EE_n$ algebras determine factorization algebras on all $n$-dimensional manifolds, whether framed or oriented or unoriented.
+The key point is that the model uses the compactly supported de Rham complex (or some other model of chains)
+and hence makes sense on general manifolds.
+\end{rmk}
 
@@
 then there is a $\Disk_n$-algebra ${\tt U}_n \fg$ assigning $\cliels(\fg[-n]) = \Sym(\fg[1-n])$ to each ball and it is manifestly locally constant.
-This algebra ${\tt U}_n \fg$ is a model for~$\UU_n \fg$.
+This $\Disk_n$-algebra ${\tt U}_n \fg$ is another model for~$\UU_n \fg$.
 

### 2020-09-09 draft.tex
more calculus revisions

@@
 Let $\Disk_n^\sqcup$ denote the colored operad whose colors are balls in $\RR^n$ and whose spaces of operations are either empty or a point, depending on whether the input balls are pairwise disjoint and subsets of the output ball.
-One can work with locally constant, homotopy-coherent $\Disk_n^\sqcup$-algebras.
+One can work with locally constant, homotopy-coherent $\Disk_n^\sqcup$ algebras.
 \item Knudsen verifies that we can model the enveloping $\EE_n$ algebra by the factorization algebra $\bU_n \fg$ described earlier.
@@
 Having an explicit presentation for the centralizer of a map of $\EE_n$ algebras leads to a calculation of factorization homology.
-The enveloping $\EE_n$ algebra is the homotopy $O(n)$-fixed points, or a $\mathrm{Disk}_n$-algebra in the sense of~\cite{AF},
+The enveloping $\EE_n$ algebra is the homotopy $O(n)$-fixed points, or a $\mathrm{Disk}_n$ algebra in the sense of~\cite{AF},
 and hence determines a factorization algebra on any un-oriented $n$-dimensional manifold \cite{Knudsen}.
@@
 
-A ${\rm Disk}^\sqcup_M$-algebra $A$ is {\em locally constant} if for any embedding of disks $D \hookrightarrow D'$ in $M$ that the induced map $A(D) \to A(D')$ is an equivalence. 
-When $M = \RR^n$, it is a result of Lurie that the theory of locally constant ${\rm Disk}^\sqcup_n$-algebras is equivalent to the theory of $\EE_n$ algebras.
+A ${\rm Disk}^\sqcup_M$ algebra $A$ is {\em locally constant} if for any embedding of disks $D \hookrightarrow D'$ in $M$ that the induced map $A(D) \to A(D')$ is an equivalence. 
+When $M = \RR^n$, it is a result of Lurie that the theory of locally constant ${\rm Disk}^\sqcup_n$ algebras is equivalent to the theory of $\EE_n$ algebras.
 
@@
 \]
-whose essential image is the full subcategory of locally constant ${\rm Disk}^\sqcup_n$-algebras. 
+whose essential image is the full subcategory of locally constant ${\rm Disk}^\sqcup_n$ algebras. 
 \end{thm}
 
-In the above proposition, we refer to ${\rm Disk}^\sqcup_n$-algebras in the homotopically coherent sense. 
+In the above proposition, we refer to ${\rm Disk}^\sqcup_n$ algebras in the homotopically coherent sense. 
 In particular, the requisite associativity axioms hold up to a prescribed homotopy.
@@
 See Theorem 1.1 of \cite{PavlovRectify} for a general result of this type that is sufficient for our purposes. 
-There is a $1$-category of ${\rm Disk}^\sqcup_n$-algebras where we require associativity to hold in the strict sense. 
-By this general strictification result, given any homotopically coherent ${\rm Disk}^{\sqcup}_n$-algebra we can find an equivalent algebra which is an object in this $1$-category.
+There is a $1$-category of ${\rm Disk}^\sqcup_n$ algebras where we require associativity to hold in the strict sense. 
+By this general strictification result, given any homotopically coherent ${\rm Disk}^{\sqcup}_n$ algebra we can find an equivalent algebra which is an object in this $1$-category.
 
@@
 A {\em prefactorization algebra} on $M$ is an algebra over the colored operad ${\rm Opens}^{\sqcup}_M$. 
-We say a prefactorization algebra on $M$ is locally constant if its associated ${\rm Disk}_n$-algebra is.
+We say a prefactorization algebra on $M$ is locally constant if its associated ${\rm Disk}_n$ algebra is.
 
@@
 if one restricts to working with open balls in $\RR^n$ (rather than arbitrary open sets)
-then there is a $\Disk_n$-algebra ${\tt U}_n \fg$ assigning $\cliels(\fg[-n]) = \Sym(\fg[1-n])$ to each ball and it is manifestly locally constant.
-This $\Disk_n$-algebra ${\tt U}_n \fg$ is another model for~$\UU_n \fg$.
+then there is a $\Disk_n$ algebra ${\tt U}_n \fg$ assigning $\cliels(\fg[-n]) = \Sym(\fg[1-n])$ to each ball and it is manifestly locally constant.
+This $\Disk_n$ algebra ${\tt U}_n \fg$ is another model for~$\UU_n \fg$.
 
@@
 its underlying complex is equipped with a homotopy-coherent Lie algebra structure.
-Depending on one's preferences, one can work with an an $L_\infty$-algebra structure or strictify to a dg Lie algebra structure (at the cost of replacing the complex with something quasi-isomorphic but typically much larger).
+Depending on one's preferences, one can work with an an $L_\infty$ algebra structure or strictify to a dg Lie algebra structure (at the cost of replacing the complex with something quasi-isomorphic but typically much larger).
 \end{rmk}
@@
 For $\fg$ a reductive \owen{semisimple?} Lie algebra with Cartan subalgebra~$\fh$ and Weyl group~$W$, 
-there is a quasi-isomorphism of $\EE_{n+1}$-algebras
+there is a quasi-isomorphism of $\EE_{n+1}$ algebras
 \[
@@
 Lurie \cite{HA} has proved that this multiplication makes the center into an $E_1$ algebra in $\EE_n$ algebras 
-and therefore an $E_{n+1}$-algebra, by Dunn additivity. 
+and therefore an $E_{n+1}$ algebra, by Dunn additivity. 
 %To be precise, there is the following result.
@@
 \label{T:compcentralizer}
-Let $f: \fg \rightsquigarrow \fh$ and $g: \fh \rightsquigarrow \fl$ be maps of  $L_\infty$-algebras,
+Let $f: \fg \rightsquigarrow \fh$ and $g: \fh \rightsquigarrow \fl$ be maps of  $L_\infty$ algebras,
 and let $\bold{f}: \bU_n \fg \to \bU_n \fh$ and $\bold{g}: \bU_n \fh \to \bU_n \fl$ denote the induced maps of factorization algebras.
@@
 \label{L:compisassociative} 
-Let $f: \fg \rightsquigarrow \fh$, $g: \fh \rightsquigarrow \fl$ and $h: \fl \rightsquigarrow \fk$ be maps of $L_\infty$-algebras.
+Let $f: \fg \rightsquigarrow \fh$, $g: \fh \rightsquigarrow \fl$ and $h: \fl \rightsquigarrow \fk$ be maps of $L_\infty$ algebras.
 For any $\varphi \in \bZ_n(f)$, $\psi \in \bZ_n(g)$, and $\gamma \in \bZ_n(h)$,  
@@
 In a precise sense that we will discuss below, 
-it is the {\em universal} $\EE_{n+1}$-algebra that acts on $A$ {\em qua} $\EE_n$ algebra.
+it is the {\em universal} $\EE_{n+1}$ algebra that acts on $A$ {\em qua} $\EE_n$ algebra.
 
@@
 
-Given an $\EE_{n+1}$-algebra one can speak of its $\infty$-category of left (or right) modules.
-This $\infty$-category is obtained by ``forgetting" the $\EE_{n+1}$-algebra to an $\EE_1$-algebra and then taking the left-modules for this $\EE_1$-algebra.
-
-The operad of little $n$-disks is built from configurations of disjoint unions of $n$-disks inside $n$-dimensional Euclidean space.
-The $(n+1)$-dimensional Swiss cheese operad is a two-colored operad whose algebras include pairs $(B, M)$ where $B$ is an $\EE_{n+1}$-algebra, $M$ is an $\EE_n$ algebra, and where $M$ is a left-module for $B$.
-
-Geometrically, it is most constructive to view this operad as built from open sets in the upper half space $\HH^{n+1} = \{(x_1,\ldots, x_{n+1}) \; | \; x_{n+1} \geq 0\}$.
-The colors include disks and half-disks. 
-If one restricts to the ``disk" colors we recover the data of the $\EE_{n+1}$-algebra $B$. 
-The operadic structure maps which include disks and half-disks embedded inside bigger half-disks encodes the left-module structure of $B$ on $M$.
-
-The pair $(\fZ_{n} (A), A)$ can be given the structure of an algebra over the $(n+1)$-dimensional Swiss cheese operad. 
-In fact, $(\fZ_{n} (A), A)$ is the {\em universal} such pair in the sense that if $(B, A)$ is another such pair then there exists a unique (up to equivalence) map of $\EE_{n+1}$-algebras $B \to \fZ_n(A)$.
-This universality is a conjecture of \cite{Kontsevich} which was later made precise and proved in \cite{Thomas, Tamarkin, Dolgushev, jnkf others?}.
+We review now the notion of Swiss cheese algebras.
+As with the $\EE_n$ operad, we will first fix a specific presentation but will then use Swiss cheese to mean any equivalent operadic structure.
+
+First, observe that given an $\EE_{n+1}$ algebra $B$, 
+one can speak of its $\infty$-category of left (or right) modules.
+This $\infty$-category is obtained by ``forgetting" the $\EE_{n+1}$ algebra to an $\EE_1$ algebra and then taking the left-modules for this underlying $\EE_1$ algebra.
+This $\infty$-category has a natural $\EE_n$-monoidal structure by tensoring over~$B$
+\owen{citation to Lurie?}, a rather nontrivial result.
+
+Recall now the topological operad of little $n$-disks whose operations are parametrized by configurations of disjoint unions of $n$-disks inside a big $n$-disk.
+There is a natural extension to a two-colored topological operad where the first color is an $n$-disk and the second color is an $n$-dimensional semi-disk, 
+and whose operations are parametrized by configurations of disjoint unions of disks and semi-disks, where the disks live in the interior of a big semi-disk and where the little semi-disks have their straight boundary lying on the boundary of the big semi-disk.\owen{Citations?}
+
+If one works through the definition, one finds that a Swiss cheese algebra consists of  a pair $(B, M)$, 
+where $B$ is an $\EE_{n+1}$ algebra and $M$ is an $\EE_n$ algebra in the $\infty$-category of left-modules for~$B$.
+The crucial example is that the pair $(\fZ_{n} (A), A)$ naturally determines a Swiss cheese algebra, 
+in fact, the {\em universal} such pair in a sense conjectured by Kontsevich \cite{}.
+
+\begin{thm}[\cite{Thomas, Tamarkin, Dolgushev, jnkf others?}] 
+For any $\EE_n$ algebra $A$ and any $\EE_{n+1}$ algebra~$B$,
+the space of Swiss cheese algebras whose underlying algebras are $B$ and $A$, respectively,
+is weakly equivalent to the space of maps of $\EE_{n+1}$ algebras $B \to \fZ_n(A)$. 
+\end{thm}
 
@@
 
-\begin{dfn}\label{dfn:pair}
-A {\em factorization pair} on a manifold $M$ is a pair $(\bB, \bM)$ where
+\begin{dfn}
+\label{dfn:pair}
+A {\em factorization sc-pair} on a manifold $M$ is a pair $(\bB, \bM)$ where
 \begin{itemize}
-\item $\bB$ is an associative algebra in locally constant factorization algebras;
-\item $\bM$ is a locally constant factorization algebra together with map $\bB \to \bZ_n(\bM)$ of associative algebras in factorization algebras.
+\item $\bB$ is an associative algebra in locally constant prefactorization algebras;
+\item $\bM$ is a locally constant prefactorization algebra together with map $\bB \to \bZ_n(\bM)$ of associative algebras in prefactorization algebras.
 \end{itemize}
-\brian{add remark about 1 categorical notion}
 \end{dfn}
 
-An immediate consequence of Theorem \ref{thm:lurie1} and Theorem \ref{thm: centralizer} is that a factorization pair on $\RR^n$ determines an algebra over the $(n+1)$-dimensional Swiss cheese operad.
+\begin{rmk}
+Since our focus is on concrete models, we mean here a strictly associative algebra $\bB$ in the 1-category of prefactorization algebras on $M$,
+and the map $\bB \to \bZ_n(\bM)$ should be strictly associative.
+It is straightforward to take such a pair and produce a Swiss cheese algebra in an $\infty$-categorical sense.
+In this paper we will always go in this concrete-to-abstract direction,
+never needing to start with a Swiss cheese algebra and produce a factorization sc-pair.
+\end{rmk}
+
+An immediate consequence of Theorem~\ref{thm:lurie1} and Theorem~\ref{thm: centralizer} is that a factorization sc-pair on $\RR^n$ determines an algebra over the $(n+1)$-dimensional Swiss cheese operad.
 
 In the next section we will recall a different model for algebras over the $(n+1)$-dimensional Swiss cheese operad in terms of constructible factorization algebras on $(n+1)$-dimensional manifolds with boundary.
-
-%We have developed locally constant factorization models separately for enveloping $\EE_n$-algebras and their centers.
-%Combining these descriptions we obtain the following.
-%
-%\begin{prp}
-%For any smooth manifold $M$ and Lie algebra $\fg$ the pair $(\bZ_n(\fg), \bU_n (\fg))$ define a constructible factorization algebra on the $(n+1)$-manifold with boundary $M \times \RR_{\geq 0}$.
-%When $M = \RR^n$, this is a model for the algebra $(\fZ_n(\fg), \UU_n(\fg))$ over the $(n+1)$-dimensional Swiss cheese operad.
-%\end{prp}
-%
-%\begin{proof}[Proof sketch]
-%In the bulk manifold $M \times \RR_{>0}$ we place the 
-%\end{proof}
 
@@
 For any $L_\infty$ algebra $\fg$ and any closed $(n-k)$-dimensional manifold $S$,
-the canonical map of $E_k$-algebras
+the canonical map of $E_k$ algebras
 \[
@@
 In the case that $U$ is an interval, this cochain complex is quasi-isomorphic to $\clies (\fg , U\fg^{ad})$.
-Furthermore, one can verify that the resulting $E_1$-algebra structure agrees with the one coming from convolution.
+Furthermore, one can verify that the resulting $E_1$ algebra structure agrees with the one coming from convolution.
 
@@
 Given a filtered associative algebra whose associated graded is commutative, there exists a Poisson bracket on the associated graded algebra. 
-If the associated graded of a filtered $\EE_n$ algebra is commutative, then it carries the structure of a $\PP_n$-algebra, which is similar to a Poisson algebra except the bracket is of cohomological degree $1-n$.
+If the associated graded of a filtered $\EE_n$ algebra is commutative, then it carries the structure of a $\PP_n$ algebra, which is similar to a Poisson algebra except the bracket is of cohomological degree $1-n$.
 There is a similar description of the ``classical limit"  of algebras over the $(n+1)$-dimensional Swiss cheese operad in terms of algebras over a certain two-colored operad $\PP_{[n+1,n]}$, introduced by Safronov \cite{Pavel1, Pavel2}, whose definition we recall below.
@@
 
-Any constructible factorization algebra $\bA$ on $M \times \RR_{\geq 0}$ determines a factorization pair $(\bA^\circ , \bA^{\partial})$ in the sense of Definition \ref{dfn:pair}.
+Any constructible factorization algebra $\bA$ on $M \times \RR_{\geq 0}$ determines a factorization sc-pair $(\bA^\circ , \bA^{\partial})$ in the sense of Definition \ref{dfn:pair}.
 We recall this construction in Section \ref{sec:bulk}. 
@@
 %\end{equation}
-on $M \times \RR_{\geq 0}$ and a quasi-isomorphism of factorization pairs
+on $M \times \RR_{\geq 0}$ and a quasi-isomorphism of factorization sc-pairs
 \[
@@
 \begin{lmm}
-These filtrations equip $(\bZ_n (\fg), \bU_n(\fg))$ with the structure of a filtered factorization pair.
-Moreover, the associated graded pair $({\rm Gr} \; \bZ_n (\fg), {\rm Gr} \; \bU_n(\fg))$ is a commutative factorization pair. 
+These filtrations equip $(\bZ_n (\fg), \bU_n(\fg))$ with the structure of a filtered factorization sc-pair.
+Moreover, the associated graded pair $({\rm Gr} \; \bZ_n (\fg), {\rm Gr} \; \bU_n(\fg))$ is a commutative factorization sc-pair. 
 \end{lmm}
@@
 
-For $k \geq -1$, a {\em $\PP_k$-factorization algebra} is a factorization algebra $\bA$ such that for every open set $U$ the cochain complex $\bA(U)$ is equipped with the structure of a $\PP_k$-algebra.
-Furthermore, we require that the factorization structure maps be compatible with the $\PP_k$-algebra structure.
-
-Theorem \ref{thm:lurie1} combines with the additivity result of \cite{SafronovAdd} to show that there is an equivalence of categories between the category of locally constant $\PP_k$-factorization algebras on $\RR^n$ and $\PP_{n+k}$-algebras.
+For $k \geq -1$, a {\em $\PP_k$-factorization algebra} is a factorization algebra $\bA$ such that for every open set $U$ the cochain complex $\bA(U)$ is equipped with the structure of a $\PP_k$ algebra.
+Furthermore, we require that the factorization structure maps be compatible with the $\PP_k$ algebra structure.
+
+Theorem \ref{thm:lurie1} combines with the additivity result of \cite{SafronovAdd} to show that there is an equivalence of categories between the category of locally constant $\PP_k$-factorization algebras on $\RR^n$ and $\PP_{n+k}$ algebras.
 
@@
 \begin{proof}
-For any $L_\infty$ algebra $\fh$, the associated graded of the Chevalley--Eilenberg complex ${\rm Gr} \; \cliels {\rm Sym} (\fh [1])$ is equipped with the structure of a $\PP_0$-algebra.
+For any $L_\infty$ algebra $\fh$, the associated graded of the Chevalley--Eilenberg complex ${\rm Gr} \; \cliels {\rm Sym} (\fh [1])$ is equipped with the structure of a $\PP_0$ algebra.
 It is given by the sum of the $L_\infty$-operations $\ell_2 + \ell_3 + \cdots$. 
@@
 The definition of this two-colored operad $\PP_{[n+1,n]}$ can be found in \cite{SafronovCoiso}. 
-A $\PP_{[n+1,n]}$-algebra consists of a pair $(A,B)$ where $A$ is a $\PP_{n+1}$-algebra and $B$ is a $\PP_n$ algebra which receives an action by $A$.
+A $\PP_{[n+1,n]}$ algebra consists of a pair $(A,B)$ where $A$ is a $\PP_{n+1}$ algebra and $B$ is a $\PP_n$ algebra which receives an action by $A$.
 
@@
 \begin{rmk}
-One way to formulate the definition of a $\PP_{[n+1,n]}$ algebra $(A,B)$ is to require a map of commutative dg algebras $A \to B$ together with a lift to a map of $\PP_{n+1}$-algebras $A \to \fZ_{\PP_n} (B)$, where $\fZ_{\PP_n}(B)$ is the {\em $\PP_n$-center} of the $\PP_n$-algebra $B$.
+One way to formulate the definition of a $\PP_{[n+1,n]}$ algebra $(A,B)$ is to require a map of commutative dg algebras $A \to B$ together with a lift to a map of $\PP_{n+1}$ algebras $A \to \fZ_{\PP_n} (B)$, where $\fZ_{\PP_n}(B)$ is the {\em $\PP_n$-center} of the $\PP_n$ algebra $B$.
 By a similar proof as in the main part of the paper, we expect that one can see that the factorization algebra
@@
 On each open set $U \subset M \times \RR_{\geq 0}$, the cochain complex $\bC_n(\fg) (U)$ is a commutative dg algebra. 
-In fact, it has the structure of a $\PP_0$-algebra where the $1$-shifted bracket $\{\cdot, \cdot\}$ is defined as follows.
+In fact, it has the structure of a $\PP_0$ algebra where the $1$-shifted bracket $\{\cdot, \cdot\}$ is defined as follows.
 
@@
 
-Next, we provide a construction of a factorization pair on the manifold $M$ from the data of a constructible factorization algebra on $M \times \RR_{\geq 0}$. 
+Next, we provide a construction of a factorization sc-pair on the manifold $M$ from the data of a constructible factorization algebra on $M \times \RR_{\geq 0}$. 
 Suppose $\bA$ is any constructible factorization algebra on a manifold with boundary $M \times \RR_{\geq 0}$. 
@@
 \end{align*}
-It is immediate to check that $(\bA^\circ, \bA^\partial)$ form a factorization pair in the sense of Definition \ref{dfn:pair}. 
-In fact, this construction determines a functor from the category of constructible factorization algebras on $M \times \RR_{\geq 0}$ to factorization pairs on $M$.
+It is immediate to check that $(\bA^\circ, \bA^\partial)$ form a factorization sc-pair in the sense of Definition \ref{dfn:pair}. 
+In fact, this construction determines a functor from the category of constructible factorization algebras on $M \times \RR_{\geq 0}$ to factorization sc-pairs on $M$.
 
@@
 
-The pair $(\int_{\RR_{>0}} , \int_{\RR_{\geq 0}})$ is a quasi-isomorphisms of factorization pairs. 
+The pair $(\int_{\RR_{>0}} , \int_{\RR_{\geq 0}})$ is a quasi-isomorphisms of factorization sc-pairs. 
 The compatibility of this quasi-isomorphism with Poisson brackets is a direct calculation. 
@@
 We remark that we are free to replace $\fg$ by an arbitrary $L_\infty$ algebra, which we will do so for the remainder of this section. 
-It is clear that the $L_\infty$-algebra $\cL$ in (\ref{eqn:fields}) can be enhanced to a sheaf of $L_\infty$-algebras. 
+It is clear that the $L_\infty$ algebra $\cL$ in (\ref{eqn:fields}) can be enhanced to a sheaf of $L_\infty$ algebras. 
 In the setup of \cite{CG2}, the factorization algebra of classical observables is the Chevalley--Eilenberg cochains $\clies (\cL)$.   
@@
 \begin{dfn}
-Let $M$ be an $n$-dimensional manifold and let $\fg$ be an $L_\infty$-algebra. 
-{\em Topological BF theory with its universal Neumann boundary condition} is the classical BV theory on $M \times \RR_{\geq 0}$ described by the following constructible sheaf $\cL$ of $L_\infty$-algebras:
+Let $M$ be an $n$-dimensional manifold and let $\fg$ be an $L_\infty$ algebra. 
+{\em Topological BF theory with its universal Neumann boundary condition} is the classical BV theory on $M \times \RR_{\geq 0}$ described by the following constructible sheaf $\cL$ of $L_\infty$ algebras:
 \begin{itemize}
@@
 The bulk theory is perturbative topological BF theory on $M \times \RR_{>0}$. 
-That is, to an open set $U \subset M \times \RR_{>0}$ the theory is described by the $L_\infty$-algebra 
+That is, to an open set $U \subset M \times \RR_{>0}$ the theory is described by the $L_\infty$ algebra 
 \[
@@
 \item[(2)] 
-To an open set $V \times [0,\epsilon)$, we assign the (abelian) $L_\infty$-algebra
+To an open set $V \times [0,\epsilon)$, we assign the (abelian) $L_\infty$ algebra
 \[

### 2020-09-09 draft.tex
koszul pairing filled in

@@
 
+\subsection{A Koszul pairing with enveloping $\EE_n$ algebras}
+
+We now briefly remark on how Corollary~\ref{cor: koszul dual to main theorem} lets us see aspects of $\EE_n$-Koszul duality in concrete terms.
+Note that $\clies(\fg)$ and $\UU_n(\fg)$ have equivalent $\EE_n$ centers.
+If we choose to view $\clies(\fg)$ as an $\EE_n$ algebra in {\em right} modules for ${\frak Z}_n(\fg)$,
+then we can consider the relative tensor product
+\[
+\clies(\fg) \otimes_{{\frak Z}_n(\fg)} \UU_n \fg
+\]
+and obtain an $\EE_n$ algebra in cochain complexes.
+Our models let us show that this relative pairing is trivial, in the following sense.
+
+\begin{lmm}
+There is an equivalence  
+\[
+k \simeq \clies(\fg) \otimes_{{\frak Z}_n(\fg)} \UU_n \fg
+\]
+of $\EE_n$ algebras.
+\end{lmm}
+
+\begin{proof}
+Our model $\bZ_n(\fg)$ is an strict associative algebra, and our models $\clies(\Omega^* \otimes \fg)$ and $\bU_n\fg$ are strict right, respectively left, modules over $\bZ_n(\fg)$.
+On each open set~$V$, we compute
+\begin{align*}
+\clies(\Omega^*(V) \otimes \fg) &\otimes^\LL_{\bZ_n(\fg)(V)} \bU_n(V) \\
+&\simeq \clies(\Omega^*(V) \otimes \fg) \otimes^\LL_{\Hom^\bullet(\cliels(\Omega^*(V) \otimes \fg, \cliels(\Omega^*_c(V)\otimes \fg))} \cliels(\Omega^*_c(V)\otimes \fg)
+\end{align*}
+and it is a standard argument to show that this relative tensor product is the unit.
+\end{proof}
+
+\owen{Lurie has a beautiful discussion of such pairings somewhere,
+so maybe we can borrow his riffs and extend the above in a nice way.}
+
 \subsection{How factorization homology intertwines with taking the center}
@@
 \owen{Other manifolds? Products of circles? Spheres?}
-
-\subsection{Koszul duality for enveloping $\EE_n$ algebras}
-
-\owen{Use corollary~\ref{cor: koszul dual to main theorem} to exhibit a "dual" Swiss cheese pair and then compute the relative tensor product over the center, which will be the unit $\EE_n$ algebra.
-Draw a picture of the strip.}
 
@@
 \end{proof}
+
+\owen{Consider referring back to the Koszul pairing (in the calculus section) to talk about Neumann vs Dirichlet boundary conditions.}
 

### 2020-09-09 draft.tex
revised AKSZ stuff

@@
 \]
-
 In fact, $\bC_n(\fg)$ is a constructible $\PP_0$-factorization algebra and this quasi-isomorphism is compatible with Poisson structures.
@@
 \begin{lmm}
-$\bC_n(\fg)$ has the structure of a constructible $\PP_0$-factorization algebra on $M \times \RR_{\geq 0}$. 
+$\bC_n(\fg)$ admits the structure of a constructible $\PP_0$-factorization algebra on~$M \times \RR_{\geq 0}$. 
 \end{lmm}
@@
 
-For any Lie algebra $\fg$, there is a topological field theory defined in any dimension known as {\em topological BF theory}.
-Suppose $N$ is an $(n+1)$-dimensional manifold, which for now we assume has no boundary $\partial N = \emptyset$. 
-When $N$ is compact, the classical moduli space underlying this topological field theory can be described as the following mapping space 
-\begin{equation} \label{stack1}
-{\rm Map}(N_{\rm dR} ,  {\rm T}^*[n] {\rm B} G)
+For any Lie group $G$, there is a gauge theory defined in any dimension known as {\em topological BF theory}.
+Let the ``spacetime'' be an $(n+1)$-dimensional manifold $N$, 
+which for now we assume has no boundary $\partial N = \emptyset$. 
+As a field theory, there is a system of PDE known as the ``solutions to the equations of motion.''
+When $N$ is compact, the moduli space of solutions to these equations of motion for topological BF theory can be described as the mapping space 
+\begin{equation} 
+\label{stack1}
+{\rm Map}(N_{\rm dR} ,  {\rm T}^*[n] {\rm B} G),
 \end{equation}
-where $N_{\rm dR}$ denotes the de Rham stack of $N$ and where $G$ is a Lie group whose Lie algebra is $\fg$. 
-Via the canonical $n$-shifted symplectic structure on ${\rm T}^* [n] {\rm B} G$, the AKSZ construction equips the mapping space with a $(-1)$-shifted symplectic structure. 
-Classically, on manifolds without boundary, this produce describes topological BF theory in the Batalin--Vilkovisky formalism~\cite{BV}.
-
-Now, suppose $N$ has non-empty boundary $\partial N \ne 0$.
-Then, (\ref{stack1}) no longer admits a $(-1)$-shifted symplectic structure. 
-However, the AKSZ construction equips 
+where $N_{\rm dR}$ denotes the de Rham stack of $N$ and where ${\rm B}G$ is the classifying stack of $G$.
+Via the canonical $n$-shifted symplectic structure on ${\rm T}^* [n] {\rm B} G$, 
+the AKSZ construction equips this mapping space with a $(-1)$-shifted symplectic structure. 
+On manifolds without boundary, this procedure describes topological BF theory in the Batalin--Vilkovisky formalism~\cite{BV}.
+
+Now, suppose that our compact manifold $N$ has non-empty boundary $\partial N \ne 0$.
+Then (\ref{stack1}) no longer admits a $(-1)$-shifted symplectic structure. 
+In this case, the AKSZ construction equips 
 \[
@@
 with a $0$-shifted symplectic structure. 
-Moreover, the restriction map 
+Moreover, the map that restricts a map from all of $N$ to its boundary
 \[
@@
 is a Lagrangian morphism.
-\owen{Somewhere say that $N$ and $\partial N$ are still compact here.}
-%Perturbatively, this mapping stack represents the restriction of the fields to the boundary.
-
-For BF theory, this $0$-shifted symplectic manifold admits another natural Lagrangian. 
-In terms of mapping stacks, it is given by considering maps from $\partial N_{\rm dR}$ into the $n$-shifted conormal bundle of ${\rm B} G$:
+
+For topological BF theory, this $0$-shifted symplectic manifold admits another natural Lagrangian ``subspace.'' 
+In terms of mapping stacks, it is given by maps from $\partial N_{\rm dR}$ into the $n$-shifted conormal bundle of ${\rm B} G$:
 \[
@@
 \]
-Then, by higher abstract nonsense \brian{reference} the fiber product
+The fiber product
 \[
@@
 \]
-is equipped with a $(-1)$-shifted symplectic structure. 
-Heuristically, the classical observables are given by functions on the $(-1)$-shifted symplectic space $X$.
-\owen{I'm not sure it's a heuristic. I think we could say that we interpret functions on $X$ as the classical observables for the classical field theory with this boundary condition.}
+is then equipped with a $(-1)$-shifted symplectic structure. 
+From the point of view of classical physics, 
+we view the algebra of functions $\cO_X$ on $X$ as the {\em classical observables} of topological BF theory with these boundary conditions.
+
+\owen{Brian: please edit this paragraph.}
+Although we have started here with a Lie group $G$, 
+one can replace $T^*[n] {\rm B}G$ with {\em any} $n$-shifted symplectic derived stack.
+Such AKSZ theories encompass examples of interest in physics (e.g., the A- and B-models or Rozansky-Witten theories).
+Of particular interest to us here are the shifted cotangent spaces~$T^*[n] X$.
+
+We now turn to relating these ideas to the constructions of this paper.
 
@@
 
-Perturbative BF theory is the formal moduli space is defined by the formal neighborhood of a point in the derived mapping space (\ref{stack1}). 
-For simplicity, we will work near the trivial $G$-bundle. 
+Perturbative BF theory for the group $G$ is the formal moduli space is defined by the formal neighborhood of a point in a derived mapping space such as (\ref{stack1}). 
+For simplicity, consider working around the trivial $G$-bundle. 
 Here, the formal moduli space is described in terms of the following dg Lie algebra 
@@
 \end{equation}
-We denote elements of this dg Lie algebra by pairs $(A,B)$.
-
-The classical {\em fields} of the theory are given by shifting the dg Lie algebra down by one $\cL[1]$. 
-One can read off the $(-1)$-symplectic structure on the fields simply by $\int A \wedge B$.
+We denote elements of this dg Lie algebra by pairs~$(A,B)$.
+
+\begin{rmk}
+In the physics literature, one does not work with the $L_\infty$ algebra $\fg$ arising from a formal moduli space,
+but the shifted $L_\infty$ algebra $\fg[1]$. 
+In physical terminology, the classical {\em fields} here are $A$ and $B$, 
+and the $(-1)$-shifted symplectic structure on the fields is~$\int A \wedge B$. 
+\end{rmk}
 
@@
 \d A + \frac12 [A,A] & = 0 \\
-\d B + [A,B] & = 0 .
+\d B + [A,B] & = 0 ,
 \end{align*}
-
-We remark that we are free to replace $\fg$ by an arbitrary $L_\infty$ algebra, which we will do so for the remainder of this section. 
-It is clear that the $L_\infty$ algebra $\cL$ in (\ref{eqn:fields}) can be enhanced to a sheaf of $L_\infty$ algebras. 
-In the setup of \cite{CG2}, the factorization algebra of classical observables is the Chevalley--Eilenberg cochains $\clies (\cL)$.   
+which ask for a flat $G$-connection $\d + A$ and a flat section $B$ in the coadjoint bundle.
+
+As noted earlier, we could replace ${\rm B}G$ by any (reasonable) derived stack $X$.
+In that setting, the ordinary Lie algebra $\fg$ is replaced by the $L_\infty$ algebra describing the formal neighborhood of some point on $X$.
+(Or, more generally, the $L_\infty$ algebra describing the formal neighborhood around some point on the whole mapping space.)
+Indeed, we might as well view $\fg$ as an arbitrary $L_\infty$ algebra,
+which we will do for the remainder of this section.
+
+\begin{rmk}
+The $L_\infty$ algebra $\cL$ in (\ref{eqn:fields}) can be enhanced to a sheaf of $L_\infty$ algebras,
+and it can be understood as a generalized topological BF theory. 
+In the setup of \cite{CG2}, the factorization algebra of classical observables of generalized topological BF theory is given by the Chevalley--Eilenberg cochains $\clies (\cL)$.   
 The $\PP_0$-structure is induced from the explicit $(-1)$-symplectic pairing $\int A \wedge B$ at the level of the fields. 
+\end{rmk}
 
 So far, we have provided a description of perturbative BF theory on manifolds without boundary. 
-More recently, in \cite{ButsonYoo} and \cite{Eugene}, it is shown how to run the perturbative BV formalism on manifolds with boundary which we follow in the definition below.
-
-%Let $N$ be such a manifold with boundary $\partial N \ne \emptyset$ and let $\cE$ denote the space of fields, typically given as the space of sections of a finite rank vector bundle on $N$. 
-%The definition of a classical BV theory on $N$ amounts to prescribing the following data:
-%\begin{itemize}
-%\item[(1)]
-%an ordinary classical BV theory on the interior $N \setminus \partial N$ whose space of fields is $\cE|_{N \setminus \partial N}$;
-%\item[(2)] 
-%a compatible $0$-shifted symplectic structure on $\cE|_{\partial N}$ equipped with a Lagrangian subspace $\cL \subset \cE|_{\partial N}$.
-%This is called a {\em boundary condition}.
-%\end{itemize}
-%From this data at the level of fields, one obtains a constructible $\PP_0$-factorization algebra on the manifold with boundary $N$ at the level of the observables.
+More recently, in \cite{ButsonYoo} and \cite{Eugene}, 
+it is shown how to extend the perturbative BV formalism to manifolds with boundary, 
+which we follow in the definition below.
 
@@
 \end{prp}
+
+\owen{$\PP_0$ algebras?}
 

### 2020-09-09 draft.tex
added large N section

@@
 
-\owen{Point out how to use LQT map and deduce existence of $\EE_n$ algebra structure on a shifted copy of cyclic cohomology of~$\Omega^*_c$.
-Also do the Loday versions that use the other infinite series.}
-
-\owen{The weird and interesting bit is to compute the factorization homology over a nontrivial (closed) manifold.}
+\owen{Please check this carefully, Greg. The lemma is meaningful even if the proposition is bogus.}
+
+In the case of the infinite series of Lie algebras, 
+there are theorems that tell us about the limiting behavior of Lie algebra chains and cochains as $N$ goes to infinity.
+These can be applied to our models of the center to obtain novel $\EE_n$ algebras.
+
+Let $\Cyc_*(A)$ denote the {\em cyclic chains} of a dg associative algebra~$A$.
+
+\def\gl{\frak{gl}}
+
+\begin{prp}
+There is a quasi-isomorphism of $\EE_n$ algebras
+\[
+{\frak Z}_n(\frak{gl}_\infty) \xto{\simeq} \clies(\frak{\gl}_\infty) \otimes \Sym(\Cyc_*(k[-n])[1])  ,
+\]
+and so, in particular, the $N \to \infty$ limit of ${\frak Z}_n(\frak{gl}_N)$ is commutative.
+\end{prp}
+
+\begin{proof}
+The Loday-Quillen-Tsygan (LQT) theorem --- for nonunital algebras --- provides a quasi-isomorphism
+\[
+\cliels(\gl_\infty(A))^{\gl_\infty(k)} \xto{\simeq} \Sym(\Cyc_*(A)[1])
+\] 
+and it is functorial in the algebra~$A$.
+\owen{I used {\em invariants} here rather than {\em coinvariants}. Is that allowed?}
+Now
+\[
+\clies(\gl_\infty, \cliels(\gl_\infty(A)) \simeq \cliels(\gl_\infty) \otimes \cliels(\gl_\infty(A))^{\gl_\infty(k)},
+\]
+as shown in the proof of the LQT theorem.
+
+We take $A = \Omega^*_c(V)$ and use the functoriality to see that we get a quasi-isomorphism of prefactorization algebras, as claimed.
+\end{proof}
+
+There are immediate analogs of this theorem where we replace $\gl_N$ by $\frak{so}_N$ or $\frak{sp}_N$ and where we replace cyclic chains by dihedral chains.
+
+A striking consequence of the LQT map appears at the level of factorization homology.
+
+\begin{lmm}
+For a closed $n$-dimensional manifold~$M$, 
+\begin{align*}
+\int_M {\frak Z}_n(\frak{gl}_\infty) 
+&\simeq \clies(\Omega^*(M) \otimes \gl_\infty, \Sym(\Cyc_*(\Omega^*(M))[1])) \\
+&\simeq \clies(\Omega^*(M) \otimes \gl_\infty, \Sym(\Omega^*(LM/^h S^1))[1]))
+\end{align*}
+where $\Omega^*(LM/^h S^1)$ denotes some cochain model for the cochains of the homotopy quotient of the free loop space under the canonical rotation action on loops.
+\end{lmm}
+
+\owen{That phrasing could be improved.}
+
+Implicit in the statement is that one must describe the needed (and non-obvious) action of $\gl_\infty(\Omega^*(M))$ on a symmetric algebra generated by cyclic chains, respectively the rotation-equivariant cochains on the free loop space~$LM$.
+
+What makes this result striking is that it shows how the {\em cyclic loop space} $LM/^h S^1$ appears out of taking a large $N$ limit of factorization homology.
+This kind of result is especially interesting from the perspective of physics, 
+as a kind of topological gauge/string duality.
+In Section~\ref{sec: TFT} we explain how the center $\frak{Z}_n(\gl_\infty)$ can be understood as the {\em quantum observables} of topological BF theory for the Lie algebra $\gl_\infty$.
+In this sense, the left hand side of the lemma $\int_M {\frak Z}_n(\frak{gl}_\infty)$ describes the global quantum observables over the manifold $M$.
+On the right hand side, we see the cyclic loop space of $M$,
+which arises naturally as the configuration space of a closed string theory with target~$M$.
+
+\begin{proof}
+As $\Omega^*_c(M) = \Omega^*(M)$ because $M$ is closed, 
+one applies the LQT theorem for {\em unital} algebras
+\[
+\cliels(\gl_\infty(\Omega^*(M))) \xto{\simeq} \Sym(\Cyc_*(\Omega^*(M))[1])
+\]
+to obtain the first weak equivalence.
+(In fact, one must transfer the $\gl_\infty(\Omega^*(M))$ along the LQT map.)
+Then Jones' theorem \cite{} provides the second weak equivalence.
+\end{proof}
 

### 2020-09-09 draft.tex
slight rearrangement

@@
 \end{enumerate}
-\owen{And keep going}
+\owen{And keep going just a little.}
 %
@@
 
-\owen{Some easy but important situations to examine:}
-\begin{itemize}
-\item When $n=0$, we see naive endomorphisms arise.
-\item When $n=1$, we recover standard Koszul duality and Hochschild cohomology examples.
-\item When $n=1$, unpack in detail how the convolution picture matches the classic view of Koszul duality for associative (co)algebras.
-\item Consider $\fg$ {\em abelian} for arbitrary $n$ and compare to the $\EE_n$ HKR theorem.
-\item Compare with $\EE_n$ HKR theorem for $\clies(\fg)$ via $\EE_n$ Koszul duality.
-\item Use these facts to compute factorization homology of centralizers on manifolds with boundary --- kind of like Chern-Simons states!
-\end{itemize}
-
-Having an explicit presentation for the centralizer of a map of $\EE_n$ algebras leads to a calculation of factorization homology.
-The enveloping $\EE_n$ algebra is the homotopy $O(n)$-fixed points, or a $\mathrm{Disk}_n$ algebra in the sense of~\cite{AF},
-and hence determines a factorization algebra on any un-oriented $n$-dimensional manifold \cite{Knudsen}.
-Therefore, for a closed $n$-dimensional manifold $M$, one has
-\[
-\int_M {\frak Z}_n(\UU_n \rho) \simeq \clies(\fg \otimes \Omega^*(M), \cliels( \fh \otimes \Omega^*(M))).
-\]
-Since $\Omega^*(S^n) \simeq \CC[\epsilon_n]$, where $\epsilon_n$ is a formal variable with $|\epsilon_n| = n$ and $\epsilon_n^2 = 0$, we have
-\[
-\int_{S^n} {\frak Z}_n(\UU_n \rho) \simeq \clies(\fg[\epsilon_n], \cliels( \fh[\epsilon_n]))
-\]
-For $n=1$, this recovers a theorem of Tamarkin and Tsygan \cite{TT} on the Hochschild cohomology of differential operators on a Lie group $G$;
-see Example~\ref{eg: TT}.
+\owen{We could describe more that we do.}
 
@@
 
-\owen{I think we can conjecture here the general statement that we almost proved and sketch an approach.}
+\owen{If we want, we could conjecture here the general statement that we almost proved (for $f: \UU_n \fg \to B$, $\frak{Z}_n(f) \simeq \clies(\fg, B_f)$) and maybe even sketch an approach.}
 
@@
 In the last step we use the fact that the circle is formal as a rational space.
-\brian{We should compare with Tamarkin-Tsygan's noncommutative calculus (cf. section 2.6).
-We could exhibit Theorem 2.7.1 explicitly in this case for the $\EE_n$ case with enveloping algebras.}
+\brian{For $n=1$, this recovers a theorem of Tamarkin and Tsygan \cite{TT} on the Hochschild cohomology of differential operators on a Lie group $G$;
+see Example~\ref{eg: TT}(cf. section 2.6).
+We could describe an $\EE_n$ generalization?}
 

### 2020-09-09 draft.tex
damnit

--- 2020-09-09 draft.tex
@@
 we know that the $\EE_n$ enveloping algebra $\UU_n \fg$ admits a model $\bU_n \fg$ whose underlying functor on the poset of open sets in $\RR^n$ assigns $\cliels(\Omega_c^*(V) \otimes \fg)$ to each open set~$V$.
-There is another factorization algebra whose underlying assigns $\clies(\Omega^*(V) \otimes \fg)$ to each open~$V$.
+There is another factorization algebra whose underlying assigns $\clies(\Omega^\bu(V) \otimes \fg)$ to each open~$V$.
 Our paper shows that such factorization algebras model other important $\EE_n$ algebras, notably centralizers.
@@
 \[
-\clies(\Omega^* \otimes \fg, \cliels(\Omega^*_c \otimes \fh)_f)
+\clies(\Omega^\bu \otimes \fg, \cliels(\Omega^\bu_c \otimes \fh)_f)
 \]
 equipped with a convolution-type product,
-where the subscript $f$ indicates how $\cliels(\Omega^*_c \otimes \fh)$ is a module over $\Omega^* \otimes \fg$.
+where the subscript $f$ indicates how $\cliels(\Omega^\bu_c \otimes \fh)$ is a module over $\Omega^\bu \otimes \fg$.
 \end{thm}
@@
 \[
-\clies(\fg \otimes \Omega^*(U), \cliels( \fg \otimes \Omega^*_c(U)))
+\clies(\fg \otimes \Omega^\bu(U), \cliels( \fg \otimes \Omega^\bu_c(U)))
 \]
@@
 since the associative algebra $U\fg$ is modeled by the locally constant one-dimensional factorization algebra that assigns
-$\cliels (\fg \otimes \Omega^*_c(U))$ to each open $U \subset \RR$.
+$\cliels (\fg \otimes \Omega^\bu_c(U))$ to each open $U \subset \RR$.
 
@@
 \[
-\clies(\fg \otimes \Omega^*(V))
+\clies(\fg \otimes \Omega^\bu(V))
 \]
@@
 \[
-\int_M {\frak Z}_n(\UU_n \rho) \simeq \clies(\fg \otimes \Omega^*(M), \cliels( \fh \otimes \Omega^*(M))).
-\]
-Since $\Omega^*(S^n) \simeq \CC[\epsilon_n]$, where $\epsilon_n$ is a formal variable with $|\epsilon_n| = n$ and $\epsilon_n^2 = 0$, we have
+\int_M {\frak Z}_n(\UU_n \rho) \simeq \clies(\fg \otimes \Omega^\bu(M), \cliels( \fh \otimes \Omega^\bu(M))).
+\]
+Since $\Omega^\bu(S^n) \simeq \CC[\epsilon_n]$, where $\epsilon_n$ is a formal variable with $|\epsilon_n| = n$ and $\epsilon_n^2 = 0$, we have
 \[
@@
 \begin{thm}[\cite{LurieHA} Proposition 5.4.5.15]
-\label{thm:lurie0} 
+\label{thm:lurie1} 
 There is a fully faithful embedding of $\infty$-categories
@@
 Recall the overall strategy.
-First, we define a factorization algebra $\clies(\Omega^* \otimes \fg, (\bU_n \fh)_f)$ as a kind of convolution factorization algebra.
+First, we define a factorization algebra $\clies(\Omega^\bu \otimes \fg, (\bU_n \fh)_f)$ as a kind of convolution factorization algebra.
 Then we get to the heart of the construction:
@@
 
-\owen{Please read and comment if it is too fast or cryptic (or wrong due, e.g., to sloppy shifts).}
-
 We assume the reader is familiar with Lie algebras and $L_\infty$ algebras and with standard constructions,
 such as the Chevalley-Eilenberg chains or cochains, which we may also call the Lie algebra (co)chains.
-A nice reference is \owen{Loday-Vallette???}
+A nice reference is \cite{LodayVallette}.
 Nonetheless, we review a few aspects that play a crucial role below.
@@
 \]
-as complexes.
+as cochain complexes.
 
@@
 \owen{Probably need to mention somewhere that it's better to work with $\clies(\fg)$ as a completed object.}
+\brian{I think you've got around this issue by talking about Homs}
 
@@
 Our goal here is to construct the factorization algebra that models the centralizer.
-First, we need to show that there is a well-defined functor (in the 1-categorical sense) ${\rm Opens}_{\RR^n} \to \Ch_k$ assigning $\clies(\Omega^*(V) \otimes \fg, \bU_n \fh(V))$ to each open set $V$.
+First, we need to show that there is a well-defined functor (in the 1-categorical sense) ${\rm Opens}_{\RR^n} \to \Ch_k$ assigning $\clies(\Omega^\bu(V) \otimes \fg, \bU_n \fh(V))$ to each open set $V$.
 Once that is in place, it is straightforward to describe the structure maps of the prefactorization algebra and to verify it forms a factorization algebra.
@@
 \[
-\tilde{f}: \Omega^*_c(V) \otimes \fg \rightsquigarrow \Omega^*_c(V) \otimes \fh
-\]
-by base change along the map $k \to \Omega^*_c(V)$ of dg commutative algebras,
+\tilde{f}: \Omega^\bu_c(V) \otimes \fg \rightsquigarrow \Omega^\bu_c(V) \otimes \fh
+\]
+by base change along the map $k \to \Omega^\bu_c(V)$ of dg commutative algebras,
 as the compactly supported de Rham forms form a dg commutative algebra under wedge product.
-In consequence, we see that $\Omega^*_c(V) \otimes \fg$ acts on $\Omega^*_c(V) \otimes \fh$ and hence equips it with the structure of an $L_\infty$ module over $\Omega^*_c(V) \otimes \fg$.
+In consequence, we see that $\Omega^\bu_c(V) \otimes \fg$ acts on $\Omega^\bu_c(V) \otimes \fh$ and hence equips it with the structure of an $L_\infty$ module over $\Omega^\bu_c(V) \otimes \fg$.
 We denote this module as
 \[
-(\Omega^*_c(V) \otimes \fh)_f
+(\Omega^\bu_c(V) \otimes \fh)_f
 \]
@@
 
-Observe that $\Omega^*_c(V)$ is a module over the dg commutative algebra $\Omega^*(V)$ of {\em non}\/compactly supported forms.
-This action extends immediately to the module $(\Omega^*_c(V) \otimes \fh)_f$, 
-so we now view it as an $L_\infty$ module over $\Omega^*(V) \otimes \fg$ as well.
-We now need to explain how to make $\cliels(\Omega^*_c(V) \otimes \fh)$ into an $L_\infty$-module over $\Omega^*(V) \otimes \fg$.
+Observe that $\Omega^\bu_c(V)$ is a module over the dg commutative algebra $\Omega^\bu(V)$ of {\em non}\/compactly supported forms.
+This action extends immediately to the module $(\Omega^\bu_c(V) \otimes \fh)_f$, 
+so we now view it as an $L_\infty$ module over $\Omega^\bu(V) \otimes \fg$ as well.
+We now need to explain how to make $\cliels(\Omega^\bu_c(V) \otimes \fh)$ into an $L_\infty$-module over $\Omega^\bu(V) \otimes \fg$.
 Here we rely on the fact that modules over an $L_\infty$ algebra are symmetric monoidal over $\otimes_k$, 
@@
 \[
-\cliels(\Omega^*_c(V) \otimes \fh) = \bigoplus_{n \geq 0} \Sym^n(\Omega^*_c(V) \otimes \fh[1])
+\cliels(\Omega^\bu_c(V) \otimes \fh) = \bigoplus_{n \geq 0} \Sym^n(\Omega^\bu_c(V) \otimes \fh[1])
 \]
 as cochain complexes,
-we see that $\cliels(\Omega^*_c(V) \otimes \fh)$ acquires a canonical action of $\Omega^*(V) \otimes \fg$.
+we see that $\cliels(\Omega^\bu_c(V) \otimes \fh)$ acquires a canonical action of $\Omega^\bu(V) \otimes \fg$.
 In consequence, we have a cochain complex
 \[
-\clies(\Omega^*(V) \otimes \fg, \cliels(\Omega^*_c(V) \otimes \fh)_f)
+\clies(\Omega^\bu(V) \otimes \fg, \cliels(\Omega^\bu_c(V) \otimes \fh)_f)
 \]
@@
 This property follows quickly from the fact that wedge product of forms preserves support.
-Given an inclusion $i: V' \subset V$ of opens, if we take a form $\alpha \in \Omega^*(V)$ and a compactly supported form $\beta \in \Omega^*_c(V')$, then the wedge product $\alpha \wedge i_* \beta \in \Omega^*_c(V)$ after applying the extension-by-zero map $i_*: \Omega^*_c(V') \to \Omega^*_c(V)$ equals the wedge product $i_*(i^*\alpha \wedge \beta)$ arising from the restriction $i^* \alpha$ of $\alpha$ to~$V'$.
-In consequence, the action of $\Omega^*(V) \otimes \fg$ on $\cliels(\Omega^*_c(V') \otimes \fh)_f$ arising from the restriction map $\Omega^*(V) \otimes \fg \to \Omega^*(V') \otimes \fg$ of $L_\infty$ algebras agrees with action induced by the inclusion of $\cliels(\Omega^*_c(V') \otimes \fh)_f$ as a (strict) submodule of~$\cliels(\Omega^*_c(V) \otimes \fh)_f$.
+Given an inclusion $i: V' \subset V$ of opens, if we take a form $\alpha \in \Omega^\bu(V)$ and a compactly supported form $\beta \in \Omega^\bu_c(V')$, then the wedge product $\alpha \wedge i_* \beta \in \Omega^\bu_c(V)$ after applying the extension-by-zero map $i_*: \Omega^\bu_c(V') \to \Omega^\bu_c(V)$ equals the wedge product $i_*(i^*\alpha \wedge \beta)$ arising from the restriction $i^* \alpha$ of $\alpha$ to~$V'$.
+In consequence, the action of $\Omega^\bu(V) \otimes \fg$ on $\cliels(\Omega^\bu_c(V') \otimes \fh)_f$ arising from the restriction map $\Omega^\bu(V) \otimes \fg \to \Omega^\bu(V') \otimes \fg$ of $L_\infty$ algebras agrees with action induced by the inclusion of $\cliels(\Omega^\bu_c(V') \otimes \fh)_f$ as a (strict) submodule of~$\cliels(\Omega^\bu_c(V) \otimes \fh)_f$.
 This argument is manifestly associative under composition of inclusions, so we have shown our first claim.
@@
 \[
-V \mapsto \clies(\Omega^*(V) \otimes \fg, \cliels(\Omega^*_c(V) \otimes \fh)_f)
+V \mapsto \clies(\Omega^\bu(V) \otimes \fg, \cliels(\Omega^\bu_c(V) \otimes \fh)_f)
 \]
@@
 Hence it suffices to examine the underlying functors to $L_\infty$ algebras.
-As the functors $\Omega^*$ and $\Omega^*_c$ send finite disjoint unions of opens to the direct product of cochain complexes, 
-the functors like $\Omega^* \otimes \fg$ and $\Omega^*_c \otimes \fh$ send finite disjoint unions of opens to products of $L_\infty$ algebras.
+As the functors $\Omega^\bu$ and $\Omega^\bu_c$ send finite disjoint unions of opens to the direct product of cochain complexes, 
+the functors like $\Omega^\bu \otimes \fg$ and $\Omega^\bu_c \otimes \fh$ send finite disjoint unions of opens to products of $L_\infty$ algebras.
 In consequence, we obtain the desired second claim.
@@
 \[
-\clies(\Omega^*(D) \otimes \fg, \cliels(\Omega^*_c(D) \otimes \fh)_f) \xto{\simeq} \clies(\Omega^*(D) \otimes \fg, \cliels(\Omega^*_c(D) \otimes \fh)_f)
+\clies(\Omega^\bu(D) \otimes \fg, \cliels(\Omega^\bu_c(D) \otimes \fh)_f) \xto{\simeq} \clies(\Omega^\bu(D) \otimes \fg, \cliels(\Omega^\bu_c(D) \otimes \fh)_f)
 \]
@@
 \label{dfn: centralizer for f}
-Let $\clies(\Omega^* \otimes \fg, (\bU_n \fh)_f)$ denote this factorization algebra on $\RR^n$ arising from the map $f: \fg \rightsquigarrow \fh$.
+Let $\clies(\Omega^\bu \otimes \fg, (\bU_n \fh)_f)$ denote this factorization algebra on $\RR^n$ arising from the map $f: \fg \rightsquigarrow \fh$.
 \end{dfn}
@@
 For those coming from an operadic background, it may be helpful to recognize that our approach is a variant of a familiar convolution construction.
-The functor $\bU_n \fh = \cliels(\Omega^*_c \otimes \fh)$ determines an algebra over the colored operad ${\rm Opens}_{\RR^n}^\sqcup$,
-while the functor $\cliels(\Omega^* \otimes \fg)$ determines a {\em co}\/algebra over the colored operad ${\rm Opens}_{\RR^n}^\sqcup$.
-The algebra $\clies(\Omega^* \otimes \fg, (\bU_n \fh)_f)$ assigns the graded vector space
-\[
-\Hom^\bullet(\cliels(\Omega^*(V) \otimes \fg), \cliels(\Omega^*_c(V) \otimes \fh))
+The functor $\bU_n \fh = \cliels(\Omega^\bu_c \otimes \fh)$ determines an algebra over the colored operad ${\rm Opens}_{\RR^n}^\sqcup$,
+while the functor $\cliels(\Omega^\bu \otimes \fg)$ determines a {\em co}\/algebra over the colored operad ${\rm Opens}_{\RR^n}^\sqcup$.
+The algebra $\clies(\Omega^\bu \otimes \fg, (\bU_n \fh)_f)$ assigns the graded vector space
+\[
+\Hom^\bullet(\cliels(\Omega^\bu(V) \otimes \fg), \cliels(\Omega^\bu_c(V) \otimes \fh))
 \] 
@@
 \owen{This has a name, but I'm blanking at the moment.}
+\brian{convolution?}
 The differential can be seen as a twisting cocycle arising from a choice of map $f$;
@@
 \[
-\ev_{{\bf f}}: \clies(\Omega^* \otimes \fg, (\Omega^*_c \otimes \fh)_f) \otimes \bU_n \fg \to \bU_n \fh,
+\ev_{{\bf f}}: \clies(\Omega^\bu \otimes \fg, (\Omega^\bu_c \otimes \fh)_f) \otimes \bU_n \fg \to \bU_n \fh,
 \]
@@
 \[
-\clies(\Omega^*(V) \otimes \fg, \cliels(\Omega^*_c(V) \otimes \fh)_f) \otimes \cliels(\Omega^*(V) \otimes \fg) \to \cliels(\Omega^*_c(V) \otimes \fh)_f.
-\]
-The canonical inclusion $\Omega^*_c(V) \otimes \fg \hookrightarrow \Omega^*(V) \otimes \fg$ induces a canonical inclusion 
-\[
-\cliels(\Omega^*_c(V) \otimes \fg) \hookrightarrow \cliels(\Omega^*(V) \otimes \fg)
+\clies(\Omega^\bu(V) \otimes \fg, \cliels(\Omega^\bu_c(V) \otimes \fh)_f) \otimes \cliels(\Omega^\bu(V) \otimes \fg) \to \cliels(\Omega^\bu_c(V) \otimes \fh)_f.
+\]
+The canonical inclusion $\Omega^\bu_c(V) \otimes \fg \hookrightarrow \Omega^\bu(V) \otimes \fg$ induces a canonical inclusion 
+\[
+\cliels(\Omega^\bu_c(V) \otimes \fg) \hookrightarrow \cliels(\Omega^\bu(V) \otimes \fg)
 \]
@@
 \[
-\ev_{{\bf f}}(V): \clies(\Omega^*(V) \otimes \fg, \cliels(\Omega^*_c(V) \otimes \fh)_f) \otimes \bU_n \fg(V) \to \bU_n \fh(V)
+\ev_{{\bf f}}(V): \clies(\Omega^\bu(V) \otimes \fg, \cliels(\Omega^\bu_c(V) \otimes \fh)_f) \otimes \bU_n \fg(V) \to \bU_n \fh(V)
 \]
@@
 %First note that compactly supported form embeds in all forms, therefore we can apply 
-%any element of $\cliels\big(\fg \otimes \Omega^* , B\big)$ 
+%any element of $\cliels\big(\fg \otimes \Omega^\bu , B\big)$ 
 %to any element of $\cliels\big(\fg \otimes \Omega_c^* \big)$. Therefore, for any  $p\in \bN$, we have an evaluation 
-%\begin{equation} \label{eqdef:ev} \begin{array}{c}\ev: Sym^p \big( \fg \otimes \Omega^* (U)[-1] ,B(U)\big)
-%\otimes  Sym^p( \fg\otimes \Omega^*_c(U) [1]) \stackrel{ev}\longrightarrow B(U)  
+%\begin{equation} \label{eqdef:ev} \begin{array}{c}\ev: Sym^p \big( \fg \otimes \Omega^\bu (U)[-1] ,B(U)\big)
+%\otimes  Sym^p( \fg\otimes \Omega^\bu_c(U) [1]) \stackrel{ev}\longrightarrow B(U)  
 %  \\
@@
 % \] where the last map is given by the factorization algebra structure of $B$. This gives the canonical element element 
-% $\mathbf{1}\in \clies(\fg\otimes \Omega^*, B) )$ which is the unit $k\to \clies(\fg\otimes \Omega^*, B) )$
+% $\mathbf{1}\in \clies(\fg\otimes \Omega^\bu, B) )$ which is the unit $k\to \clies(\fg\otimes \Omega^\bu, B) )$
 % of the factorization structure of 
@@
 % \begin{equation}\label{eq:splittingbyaugm}
-%   \clies\big(\fg\otimes \Omega^*, B\big)  \, \cong \, k \oplus \overline{ \clies(\fg\otimes \Omega^*, B) )}
+%   \clies\big(\fg\otimes \Omega^\bu, B\big)  \, \cong \, k \oplus \overline{ \clies(\fg\otimes \Omega^\bu, B) )}
 % \end{equation}
@@
 %\begin{multline}\label{eq:defgraduationoncentralizernonconnected}
-% \clies\big(\fg\otimes \Omega^*(U), B(U)\big)  \, \cong \, 
+% \clies\big(\fg\otimes \Omega^\bu(U), B(U)\big)  \, \cong \, 
 % \Hom\left(\bigotimes\limits_{i\in I} Sym\Big(\fg\otimes \Omega (U_i)[-1]), 
@@
 % \begin{equation}\label{eq:defgraduationoncentralizernonconnected2}
-% \clies\big(\fg\otimes \Omega^*(U), B(U)\big)  \, \cong \, \bigoplus\limits_{J\subset I} {\clies}^{(J)}\big(\fg\otimes \Omega^*(U), B(U)\big) 
+% \clies\big(\fg\otimes \Omega^\bu(U), B(U)\big)  \, \cong \, \bigoplus\limits_{J\subset I} {\clies}^{(J)}\big(\fg\otimes \Omega^\bu(U), B(U)\big) 
 %\end{equation}
@@
 %\begin{multline*}
-%{\clies}^{(J)}\big(\fg\otimes \Omega^*(U), B(U)\big) = 
+%{\clies}^{(J)}\big(\fg\otimes \Omega^\bu(U), B(U)\big) = 
 %\left(\bigotimes\limits_{j\in I\setminus J} k(U_j)\right) \otimes \left(\bigotimes\limits_{j\in J}
@@
 %\end{multline*}
-%We think of an element of ${\clies}^{(J)}\big(\fg\otimes \Omega^*(U), B(U)\big)$ has an element of ${\clies}\big(\fg\otimes \Omega^*(U), B(U)\big)$
+%We think of an element of ${\clies}^{(J)}\big(\fg\otimes \Omega^\bu(U), B(U)\big)$ has an element of ${\clies}\big(\fg\otimes \Omega^\bu(U), B(U)\big)$
 %\emph{with support $\coprod\limits_{j\in J} U_j$}.   
 %Note that the component $k$ in the decomposition~\eqref{eq:splittingbyaugm} is precisely the component 
-%${\clies}^{(\emptyset)}\big(\fg\otimes \Omega^*(U), B(U)\big)$ corresponding to the empty family.
+%${\clies}^{(\emptyset)}\big(\fg\otimes \Omega^\bu(U), B(U)\big)$ corresponding to the empty family.
 %\end{rmk}
 %In other words, if $\varphi = \sum_{J\subset I} \varphi^{(J)}$ is the decomposition of $\varphi$ in its graded pieces, for all 
-%$X= \bigotimes\limits_{i\in I} X_i \in \bigotimes\limits_{I}\cliels(\fg\otimes \Omega_c^*(U_i)) \cong \cliels(\fg\otimes \Omega^*_c(U))$, we 
+%$X= \bigotimes\limits_{i\in I} X_i \in \bigotimes\limits_{I}\cliels(\fg\otimes \Omega_c^*(U_i)) \cong \cliels(\fg\otimes \Omega^\bu_c(U))$, we 
 %have the following formula generalizing the one for connected open  subsets:
@@
 \]
-In light of this observation and the fact that functors such as $\Omega^* \otimes \fg$ and $\Omega^*_c \otimes \fh$ send disjoint unions to products of $L_\infty$ algebras,
+In light of this observation and the fact that functors such as $\Omega^\bu \otimes \fg$ and $\Omega^\bu_c \otimes \fh$ send disjoint unions to products of $L_\infty$ algebras,
 we deduce the desired result.
@@
 \int_{S^{n-1}}\UU_n\fg 
-&\simeq \cliels(\Omega^*_c(\RR_{> 0} \times S^{n-1}) \otimes \fg)\\
-&\simeq \cliels(\Omega^*_c(\RR_{> 0}) \otimes H^*(S^{n-1}) \otimes \fg)
+&\simeq \cliels(\Omega^\bu_c(\RR_{> 0} \times S^{n-1}) \otimes \fg)\\
+&\simeq \cliels(\Omega^\bu_c(\RR_{> 0}) \otimes H^*(S^{n-1}) \otimes \fg)
 \end{align*}
@@
 
-\subsection{Abelian Lie algebras and an $\EE_n$ HKR theorem}
+\subsection{Abelian Lie algebras and an $\EE_n$ Hochschild-Kostant-Rosenberg theorem}
 
@@
 \begin{align*}
-\bZ_n(\fg_V) &= \clies(\Omega^* \otimes \fg_V, \bU_n \fg_V) \\
+\bZ_n(\fg_V) &= \clies(\Omega^\bu \otimes \fg_V, \bU_n \fg_V) \\
 &= \Sym((\Omega^\bu \otimes \fg_V)^\vee[-1]) \otimes \Sym(\Omega^\bu_c \otimes \fg_V[1])\\
@@
 \[
-{\frak Z}_n(\UU_n \fg) \simeq H^\bu_{\rm Lie}(\fg) \otimes \Sym(\fh[1-n])^W.
+{\frak Z}_n(\UU_n \fg) \simeq \clies (\fg) \otimes \Sym(\fh[1-n])^W.
 \]
@@
 \brian{Is there an explicit description of the $\EE_{n+1}$-structure for the RHS?}
+\brian{Is the RHS formal, can we replace by Lie algebra cohomology.}
 
@@
 \[
-\clies(\fg, \Sym(\fg[1-n]) \simeq H^\bu_{\rm Lie} (\fg) \otimes \Sym(\fg[1-n])^G 
+\clies(\fg, \Sym(\fg[1-n]) \simeq \clies (\fg) \otimes \Sym(\fg[1-n])^G 
 \]
@@
 
-\owen{Point out how to use LQT map and deduce existence of $\EE_n$ algebra structure on a shifted copy of cyclic cohomology of~$\Omega^*_c$.
+\owen{Point out how to use LQT map and deduce existence of $\EE_n$ algebra structure on a shifted copy of cyclic cohomology of~$\Omega^\bu_c$.
 Also do the Loday versions that use the other infinite series.}
@@
 \[
-\tilde{f}: \Omega^*_c(V) \otimes \fg \rightsquigarrow \Omega^*_c(V) \otimes \fh
+\tilde{f}: \Omega^\bu_c(V) \otimes \fg \rightsquigarrow \Omega^\bu_c(V) \otimes \fh
 \]
@@
 \[
-\tilde{g}: \Omega^*_c(V) \otimes \fh \rightsquigarrow \Omega^*_c(V) \otimes \fl
+\tilde{g}: \Omega^\bu_c(V) \otimes \fh \rightsquigarrow \Omega^\bu_c(V) \otimes \fl
 \]
@@
 \[
-\clies(\Omega^* \otimes \fg, (\bU_n \fh)_f) = \Hom^\bullet(\cliels(\Omega^* \otimes \fg), \cliels(\Omega^*_c \otimes \fh)_f)
+\clies(\Omega^\bu \otimes \fg, (\bU_n \fh)_f) = \Hom^\bullet(\cliels(\Omega^\bu \otimes \fg), \cliels(\Omega^\bu_c \otimes \fh)_f)
 \]
@@
 \begin{align*}
-\Hom^\bullet(\cliels(\Omega^* \otimes \fh), \cliels(\Omega^*_c \otimes \fl)) 
-\otimes \Hom^\bullet(&\cliels(\Omega^* \otimes \fg), \cliels(\Omega^*_c \otimes \fh))\\
- &\xto{{\rm comp}} \Hom^\bullet(\cliels(\Omega^* \otimes \fg), \cliels(\Omega^*_c \otimes \fl)).
+\Hom^\bullet(\cliels(\Omega^\bu \otimes \fh), \cliels(\Omega^\bu_c \otimes \fl)) 
+\otimes \Hom^\bullet(&\cliels(\Omega^\bu \otimes \fg), \cliels(\Omega^\bu_c \otimes \fh))\\
+ &\xto{{\rm comp}} \Hom^\bullet(\cliels(\Omega^\bu \otimes \fg), \cliels(\Omega^\bu_c \otimes \fl)).
 \end{align*}
-This map is easily concocted thanks to the canonical inclusion $\iota_V: \Omega^*_c(V) \hookrightarrow \Omega^*(V)$ for any open set~$V$.
-Indeed, for any $\varphi \in \Hom^\bullet(\cliels(\Omega^* \otimes \fg), \cliels(\Omega^*_c \otimes \fh))$,
-the composite $\iota_V \circ \varphi|_V$ lives in $\Hom^\bullet(\cliels(\Omega^*(V) \otimes \fg), \cliels(\Omega^*(V) \otimes \fh))$,
+This map is easily concocted thanks to the canonical inclusion $\iota_V: \Omega^\bu_c(V) \hookrightarrow \Omega^\bu(V)$ for any open set~$V$.
+Indeed, for any $\varphi \in \Hom^\bullet(\cliels(\Omega^\bu \otimes \fg), \cliels(\Omega^\bu_c \otimes \fh))$,
+the composite $\iota_V \circ \varphi|_V$ lives in $\Hom^\bullet(\cliels(\Omega^\bu(V) \otimes \fg), \cliels(\Omega^\bu(V) \otimes \fh))$,
 and so we define
 \[
-{\rm comp}(\psi, \varphi)|_V = \psi|_V \circ \iota_V \circ \varphi|_V \in \Hom^\bullet(\cliels(\Omega^*(V) \otimes \fg), \cliels(\Omega^*_c(V) \otimes \fl))
+{\rm comp}(\psi, \varphi)|_V = \psi|_V \circ \iota_V \circ \varphi|_V \in \Hom^\bullet(\cliels(\Omega^\bu(V) \otimes \fg), \cliels(\Omega^\bu_c(V) \otimes \fl))
 \]
@@
 \[
-\psi=\lambda_\psi {\bf 1_g} +\overline{\psi} \in \bZ_n(g)(V) = \clies(\fh \otimes \Omega^*(V), (\bU_n \fl (V))_g  )
+\psi=\lambda_\psi {\bf 1_g} +\overline{\psi} \in \bZ_n(g)(V) = \clies(\fh \otimes \Omega^\bu(V), (\bU_n \fl (V))_g  )
 \]
@@
 \[
-\varphi =\lambda_\varphi {\bf 1_f} +\overline{\varphi}\in \bZ_n(f)(V) = \clies(\fg \otimes \Omega^*(V), (\bU_n \fh (V))_f  ),
+\varphi =\lambda_\varphi {\bf 1_f} +\overline{\varphi}\in \bZ_n(f)(V) = \clies(\fg \otimes \Omega^\bu(V), (\bU_n \fh (V))_f  ),
 \] 
@@
 \]
-where the inclusion $\iota_V: \Omega^*_c(V) \hookrightarrow \Omega^*(V)$ is extended in the obvious, functorial way to this setting.
+where the inclusion $\iota_V: \Omega^\bu_c(V) \hookrightarrow \Omega^\bu(V)$ is extended in the obvious, functorial way to this setting.
 \end{dfn}
@@
 \]
-holds in $\clies\big(\fg\otimes \Omega^*, (\bU_n \fk)_{h \circ g \circ f} \big)$.
+holds in $\clies\big(\fg\otimes \Omega^\bu, (\bU_n \fk)_{h \circ g \circ f} \big)$.
 \end{lmm}
@@
 \end{align}
-hold in $\bZ_n(g \circ f) = k  \oplus \overline{\clies\big(\fg \otimes \Omega^*, (\bU_n \fl)_{g \circ f}  \big)}$.
+hold in $\bZ_n(g \circ f) = k  \oplus \overline{\clies\big(\fg \otimes \Omega^\bu, (\bU_n \fl)_{g \circ f}  \big)}$.
 In particular, $\mathbf{1_g} \star \mathbf{1_f} =\mathbf{1_{g \circ f}}$.
@@
 
-\subsection{Swiss cheese pairs well with centers}
+\subsection{Swiss cheese pairs well with centers} \label{sec:swiss}
 
@@
 \begin{proof}
-Our model $\bZ_n(\fg)$ is an strict associative algebra, and our models $\clies(\Omega^* \otimes \fg)$ and $\bU_n\fg$ are strict right, respectively left, modules over $\bZ_n(\fg)$.
+Our model $\bZ_n(\fg)$ is an strict associative algebra, and our models $\clies(\Omega^\bu \otimes \fg)$ and $\bU_n\fg$ are strict right, respectively left, modules over $\bZ_n(\fg)$.
 On each open set~$V$, we compute
 \begin{align*}
-\clies(\Omega^*(V) \otimes \fg) &\otimes^\LL_{\bZ_n(\fg)(V)} \bU_n(V) \\
-&\simeq \clies(\Omega^*(V) \otimes \fg) \otimes^\LL_{\Hom^\bullet(\cliels(\Omega^*(V) \otimes \fg, \cliels(\Omega^*_c(V)\otimes \fg))} \cliels(\Omega^*_c(V)\otimes \fg)
+\clies(\Omega^\bu(V) \otimes \fg) &\otimes^\LL_{\bZ_n(\fg)(V)} \bU_n(V) \\
+&\simeq \clies(\Omega^\bu(V) \otimes \fg) \otimes^\LL_{\Hom^\bullet(\cliels(\Omega^\bu(V) \otimes \fg, \cliels(\Omega^\bu_c(V)\otimes \fg))} \cliels(\Omega^\bu_c(V)\otimes \fg)
 \end{align*}
@@
 \[
-\Omega^*(V) \otimes \Omega^*(S) \to \Omega^*(V \times S),
+\Omega^\bu(V) \otimes \Omega^\bu(S) \to \Omega^\bu(V \times S),
 \]
@@
 \[
-\Omega_c^*(V) \otimes \Omega^*(S) \to \Omega_c^*(V \times S),
+\Omega_c^*(V) \otimes \Omega^\bu(S) \to \Omega_c^*(V \times S),
 \]
@@
 
-Let $\fg_S$ denote the $L_\infty$ algebra $\Omega^*(S) \otimes \fg$. 
+Let $\fg_S$ denote the $L_\infty$ algebra $\Omega^\bu(S) \otimes \fg$. 
 Then these quasi-isomorphisms above imply there are quasi-isomorphisms of $L_\infty$ algebras
 \begin{align*}
-\Omega^*(V) \otimes \fg_S &\xto{\simeq} \Omega^*(V \times S) \otimes \fg \\
+\Omega^\bu(V) \otimes \fg_S &\xto{\simeq} \Omega^\bu(V \times S) \otimes \fg \\
 \Omega_c^*(V) \otimes \fg_S &\xto{\simeq} \Omega_c^*(V \times S) \otimes \fg 
@@
 \[
-\bZ_k(\fg_S)(V) \cong \clies( \Omega^*(V) \otimes \fg_S, \bU_k \fg_S) \xto{\simeq} \clies(\Omega^*(V \times S) \otimes \fg, \bU_n(V \times S))
+\bZ_k(\fg_S)(V) \cong \clies( \Omega^\bu(V) \otimes \fg_S, \bU_k \fg_S) \xto{\simeq} \clies(\Omega^\bu(V \times S) \otimes \fg, \bU_n(V \times S))
 \]
@@
 \[
-\clies(\fg \otimes \Omega^*(S), \cliels(\fg \otimes \Omega^*(S)) \simeq \End^\bullet(\cliels(\fg \otimes \Omega^*(S))),
+\clies(\fg \otimes \Omega^\bu(S), \cliels(\fg \otimes \Omega^\bu(S)) \simeq \End^\bullet(\cliels(\fg \otimes \Omega^\bu(S))),
 \]
@@
 \begin{align*}
-\Hoch_*(\Hoch^*(U \fg, U\fg)) 
+\Hoch_\bu(\Hoch^\bu(U \fg, U\fg)) 
 &\simeq \int_{S^1} {\frak Z}(U(\fg)) \\
@@
 \]
+
 In fact, $\bC_n(\fg)$ is a constructible $\PP_0$-factorization algebra and this quasi-isomorphism is compatible with Poisson structures.
@@
 \]
-\brian{how to handle homs}.
+For $U \subset M \times \RR_{>0}$ the underlying graded vector space of $\bC_n(\fg)(U)$ is of the form
+\[
+{\rm Hom}^\bu\left(\Sym(\fg \otimes \Omega^\bu (U)[1]) \; , \; {\rm Sym}  \left(\fg \otimes \Omega^\bu_c(U) [2] \right) \right)  .
+\]
+Let $x^* \otimes \alpha$ denote an homorphism of the form $\fg \otimes \Omega (U)[1] \to \Sym^0 = k$ and $y \otimes \beta$ denote a homomorphism $k = \Sym^0 \to \fg \otimes \Omega_c(U) [1]$. 
+Then, the bracket involving the linear elements $x^* \otimes \alpha$ 
+and $y \otimes \beta$ is defined by
+\begin{align*}
+\{x^* \otimes \alpha  , y \otimes \beta \} & = \<x^*, y\>_\fg \int_U \alpha \beta \\
+\{x^* \otimes \alpha , x'^* \otimes \alpha' \} & = 0 \\
+\{y \otimes \beta , y' \otimes \beta'\} & = 0 . 
+\end{align*}
+Here, $\<x^*, y\>_\fg$ denotes the linear pairing between $\fg$ and $\fg^*$ and $\int_U\alpha \beta$ denotes the linear pairing between compactly supported distributional differential forms and differential forms.
+\brian{how to say this now}
 \end{proof}
@@
 We turn towards a model for the $\EE_n$ center as a constructible factorization algebra.
+
+\brian{I think this definition is fucked}
 
@@
 \begin{lmm}
-$\bC_n(\fg)$ admits the structure of a constructible $\PP_0$-factorization algebra on~$M \times \RR_{\geq 0}$. 
+$\bC_n(\fg)$ has the structure of a constructible $\PP_0$-factorization algebra on $M \times \RR_{\geq 0}$. 
 \end{lmm}
@@
 
-For any Lie group $G$, there is a gauge theory defined in any dimension known as {\em topological BF theory}.
-Let the ``spacetime'' be an $(n+1)$-dimensional manifold $N$, 
-which for now we assume has no boundary $\partial N = \emptyset$. 
-As a field theory, there is a system of PDE known as the ``solutions to the equations of motion.''
-When $N$ is compact, the moduli space of solutions to these equations of motion for topological BF theory can be described as the mapping space 
-\begin{equation} 
-\label{stack1}
-{\rm Map}(N_{\rm dR} ,  {\rm T}^*[n] {\rm B} G),
+For any Lie algebra $\fg$, there is a topological field theory defined in any dimension known as {\em topological BF theory}.
+Suppose $N$ is an $(n+1)$-dimensional manifold, which for now we assume has no boundary $\partial N = \emptyset$. 
+When $N$ is compact, the classical moduli space underlying this topological field theory can be described as the following mapping space 
+\begin{equation} \label{stack1}
+{\rm Map}(N_{\rm dR} ,  {\rm T}^*[n] {\rm B} G)
 \end{equation}
-where $N_{\rm dR}$ denotes the de Rham stack of $N$ and where ${\rm B}G$ is the classifying stack of $G$.
-Via the canonical $n$-shifted symplectic structure on ${\rm T}^* [n] {\rm B} G$, 
-the AKSZ construction equips this mapping space with a $(-1)$-shifted symplectic structure. 
-On manifolds without boundary, this procedure describes topological BF theory in the Batalin--Vilkovisky formalism~\cite{BV}.
-
-Now, suppose that our compact manifold $N$ has non-empty boundary $\partial N \ne 0$.
-Then (\ref{stack1}) no longer admits a $(-1)$-shifted symplectic structure. 
-In this case, the AKSZ construction equips 
+where $N_{\rm dR}$ denotes the de Rham stack of $N$ and where $G$ is a Lie group whose Lie algebra is $\fg$. 
+Via the canonical $n$-shifted symplectic structure on ${\rm T}^* [n] {\rm B} G$, the AKSZ construction equips the mapping space with a $(-1)$-shifted symplectic structure. 
+Classically, on manifolds without boundary, this produce describes topological BF theory in the Batalin--Vilkovisky formalism~\cite{BV}.
+
+Now, suppose $N$ has non-empty boundary $\partial N \ne 0$.
+Then, (\ref{stack1}) no longer admits a $(-1)$-shifted symplectic structure. 
+However, the AKSZ construction equips 
 \[
@@
 with a $0$-shifted symplectic structure. 
-Moreover, the map that restricts a map from all of $N$ to its boundary
+Moreover, the restriction map 
 \[
@@
 is a Lagrangian morphism. 
-
-For topological BF theory, this $0$-shifted symplectic manifold admits another natural Lagrangian ``subspace.'' 
-In terms of mapping stacks, it is given by maps from $\partial N_{\rm dR}$ into the $n$-shifted conormal bundle of ${\rm B} G$:
+\owen{Somewhere say that $N$ and $\partial N$ are still compact here.}
+%Perturbatively, this mapping stack represents the restriction of the fields to the boundary.
+
+For BF theory, this $0$-shifted symplectic manifold admits another natural Lagrangian. 
+In terms of mapping stacks, it is given by considering maps from $\partial N_{\rm dR}$ into the $n$-shifted conormal bundle of ${\rm B} G$:
 \[
@@
 \]
-The fiber product
+Then, by higher abstract nonsense \brian{reference} the fiber product
 \[
@@
 \]
-is then equipped with a $(-1)$-shifted symplectic structure. 
-From the point of view of classical physics, 
-we view the algebra of functions $\cO_X$ on $X$ as the {\em classical observables} of topological BF theory with these boundary conditions.
-
-\owen{Brian: please edit this paragraph.}
-Although we have started here with a Lie group $G$, 
-one can replace $T^*[n] {\rm B}G$ with {\em any} $n$-shifted symplectic derived stack.
-Such AKSZ theories encompass examples of interest in physics (e.g., the A- and B-models or Rozansky-Witten theories).
-Of particular interest to us here are the shifted cotangent spaces~$T^*[n] X$.
-
-We now turn to relating these ideas to the constructions of this paper.
+is equipped with a $(-1)$-shifted symplectic structure. 
+Heuristically, the classical observables are given by functions on the $(-1)$-shifted symplectic space $X$.
+\owen{I'm not sure it's a heuristic. I think we could say that we interpret functions on $X$ as the classical observables for the classical field theory with this boundary condition.}
 
@@
 
-Perturbative BF theory for the group $G$ is the formal moduli space is defined by the formal neighborhood of a point in a derived mapping space such as (\ref{stack1}). 
-For simplicity, consider working around the trivial $G$-bundle. 
+Perturbative BF theory is the formal moduli space is defined by the formal neighborhood of a point in the derived mapping space (\ref{stack1}). 
+For simplicity, we will work near the trivial $G$-bundle. 
 Here, the formal moduli space is described in terms of the following dg Lie algebra 
@@
 \end{equation}
-We denote elements of this dg Lie algebra by pairs~$(A,B)$.
-
-\begin{rmk}
-In the physics literature, one does not work with the $L_\infty$ algebra $\fg$ arising from a formal moduli space,
-but the shifted $L_\infty$ algebra $\fg[1]$. 
-In physical terminology, the classical {\em fields} here are $A$ and $B$, 
-and the $(-1)$-shifted symplectic structure on the fields is~$\int A \wedge B$. 
-\end{rmk}
+We denote elements of this dg Lie algebra by pairs $(A,B)$.
+
+The classical {\em fields} of the theory are given by shifting the dg Lie algebra down by one $\cL[1]$. 
+One can read off the $(-1)$-symplectic structure on the fields simply by $\int A \wedge B$.
 
@@
 \d A + \frac12 [A,A] & = 0 \\
-\d B + [A,B] & = 0 ,
+\d B + [A,B] & = 0 .
 \end{align*}
-which ask for a flat $G$-connection $\d + A$ and a flat section $B$ in the coadjoint bundle.
-
-As noted earlier, we could replace ${\rm B}G$ by any (reasonable) derived stack $X$.
-In that setting, the ordinary Lie algebra $\fg$ is replaced by the $L_\infty$ algebra describing the formal neighborhood of some point on $X$.
-(Or, more generally, the $L_\infty$ algebra describing the formal neighborhood around some point on the whole mapping space.)
-Indeed, we might as well view $\fg$ as an arbitrary $L_\infty$ algebra,
-which we will do for the remainder of this section.
-
-\begin{rmk}
-The $L_\infty$ algebra $\cL$ in (\ref{eqn:fields}) can be enhanced to a sheaf of $L_\infty$ algebras,
-and it can be understood as a generalized topological BF theory. 
-In the setup of \cite{CG2}, the factorization algebra of classical observables of generalized topological BF theory is given by the Chevalley--Eilenberg cochains $\clies (\cL)$.   
+
+We remark that we are free to replace $\fg$ by an arbitrary $L_\infty$ algebra, which we will do so for the remainder of this section. 
+It is clear that the $L_\infty$ algebra $\cL$ in (\ref{eqn:fields}) can be enhanced to a sheaf of $L_\infty$ algebras. 
+In the setup of \cite{CG2}, the factorization algebra of classical observables is the Chevalley--Eilenberg cochains $\clies (\cL)$.   
 The $\PP_0$-structure is induced from the explicit $(-1)$-symplectic pairing $\int A \wedge B$ at the level of the fields.
-\end{rmk}
 
 So far, we have provided a description of perturbative BF theory on manifolds without boundary. 
-More recently, in \cite{ButsonYoo} and \cite{Eugene}, 
-it is shown how to extend the perturbative BV formalism to manifolds with boundary, 
-which we follow in the definition below.
+More recently, in \cite{ButsonYoo} and \cite{Eugene}, it is shown how to run the perturbative BV formalism on manifolds with boundary which we follow in the definition below.
+
+%Let $N$ be such a manifold with boundary $\partial N \ne \emptyset$ and let $\cE$ denote the space of fields, typically given as the space of sections of a finite rank vector bundle on $N$. 
+%The definition of a classical BV theory on $N$ amounts to prescribing the following data:
+%\begin{itemize}
+%\item[(1)]
+%an ordinary classical BV theory on the interior $N \setminus \partial N$ whose space of fields is $\cE|_{N \setminus \partial N}$;
+%\item[(2)] 
+%a compatible $0$-shifted symplectic structure on $\cE|_{\partial N}$ equipped with a Lagrangian subspace $\cL \subset \cE|_{\partial N}$.
+%This is called a {\em boundary condition}.
+%\end{itemize}
+%From this data at the level of fields, one obtains a constructible $\PP_0$-factorization algebra on the manifold with boundary $N$ at the level of the observables.
 
@@
 \end{prp}
-
-\owen{$\PP_0$ algebras?}
 
@@
 let $f\otimes X  $ be an 
-element in $\cliels\big(\fg \otimes \Omega^* , B\big) \otimes \cliels\big(\fg \otimes \Omega_c^* \big)$.  
+element in $\cliels\big(\fg \otimes \Omega^\bu , B\big) \otimes \cliels\big(\fg \otimes \Omega_c^* \big)$.  
 Let
@@
 \begin{multline}
- Sym^n\big(\fg \otimes \Omega^*_c(U)[1]\big) \otimes Sym^p \big( \fg \otimes \Omega^* (U)[-1] ,B(U)\big) \\
+ Sym^n\big(\fg \otimes \Omega^\bu_c(U)[1]\big) \otimes Sym^p \big( \fg \otimes \Omega^\bu (U)[-1] ,B(U)\big) \\
  \stackrel{\Delta \otimes id}\longrightarrow 
- \bigoplus_{q} Sym^{n-q}\big(\fg \otimes \Omega^*_c(U)[1]\big) \otimes  Sym^q\big(\fg \otimes \Omega^*_c(U)[1]\big) 
- \otimes Sym^p \big( \fg \otimes \Omega^* (U)[-1] , B(U)\big)
+ \bigoplus_{q} Sym^{n-q}\big(\fg \otimes \Omega^\bu_c(U)[1]\big) \otimes  Sym^q\big(\fg \otimes \Omega^\bu_c(U)[1]\big) 
+ \otimes Sym^p \big( \fg \otimes \Omega^\bu (U)[-1] , B(U)\big)
  \\ 
- \stackrel{\id \otimes ev}\longrightarrow Sym^{n-p}\big(\fg \otimes \Omega^*_c(U)\big) \otimes B(U)  \hookrightarrow
+ \stackrel{\id \otimes ev}\longrightarrow Sym^{n-p}\big(\fg \otimes \Omega^\bu_c(U)\big) \otimes B(U)  \hookrightarrow
  \cliels\big(\fg \otimes \Omega_c^*(U), B(U) \big) 
@@
 
-We now apply this to the special case of $\UU_n(\fg)$, that is for $\cA= \cliels(\Omega^*_c \otimes \fg)$ as we have seen. 
+We now apply this to the special case of $\UU_n(\fg)$, that is for $\cA= \cliels(\Omega^\bu_c \otimes \fg)$ as we have seen. 
 \begin{lmm}
  There is a commutative diagram 
- \[ \xymatrix{ \Sym( \fg[1-n])^{\otimes r} \ar[r]^{\simeq}& \bigotimes_{i=1}^r\cliels(\Omega^*_c(U_i) \otimes \fg) \ar[d]^{\rho} \ar[r]^{\bigotimes \phi_i(U_i)}  & \cB_f(U_1)\otimes \cdots \otimes B_f(U_r) \ar[d]^{\rho} \\
-\Sym( \fg[1-n]) \ar[u]^{\delta^{r}} \ar[r]^{\simeq} & \cliels(\Omega^*_c(V) \otimes \fg) \ar[r]_{\rho_{\cU}^{(\phi_i)}(V)}& \cB_f(V)  } \] where $\delta^r$ is the iterated cocommuative coproduct. 
+ \[ \xymatrix{ \Sym( \fg[1-n])^{\otimes r} \ar[r]^{\simeq}& \bigotimes_{i=1}^r\cliels(\Omega^\bu_c(U_i) \otimes \fg) \ar[d]^{\rho} \ar[r]^{\bigotimes \phi_i(U_i)}  & \cB_f(U_1)\otimes \cdots \otimes B_f(U_r) \ar[d]^{\rho} \\
+\Sym( \fg[1-n]) \ar[u]^{\delta^{r}} \ar[r]^{\simeq} & \cliels(\Omega^\bu_c(V) \otimes \fg) \ar[r]_{\rho_{\cU}^{(\phi_i)}(V)}& \cB_f(V)  } \] where $\delta^r$ is the iterated cocommuative coproduct. 
 \end{lmm}
 \begin{proof}
- The commtativity of the right square follows from~\eqref{eq:Cechassociatedtoconfofdisks}. For the left square, note that the factorization algebra structure maps on $\cliels(\Omega^*_c \otimes \fg)$ 
- are induced by applying the Chevalley-Eilenberg chain functor to the canonical maps of cosheaves of Lie algebras $\bigoplus_{i=1}^{r} (\Omega^*_c(U_i)\otimes \fg) \cong \Omega^*_c(\coprod U_i) \otimes \fg \longrightarrow  \Omega^*_c(V)\otimes \fg $.
+ The commtativity of the right square follows from~\eqref{eq:Cechassociatedtoconfofdisks}.
+For the left square, note that the factorization algebra structure maps on $\cliels(\Omega^\bu_c \otimes \fg)$
+ are induced by applying the Chevalley-Eilenberg chain functor to the canonical maps of cosheaves of Lie algebras $\bigoplus_{i=1}^{r} (\Omega^\bu_c(U_i)\otimes \fg) \cong \Omega^\bu_c(\coprod U_i) \otimes \fg \longrightarrow  \Omega^\bu_c(V)\otimes \fg $.
 \end{proof}

### 2020-09-09 draft.tex

@@
 
-\owen{Point out how to use LQT map and deduce existence of $\EE_n$ algebra structure on a shifted copy of cyclic cohomology of~$\Omega^\bu_c$.
-Also do the Loday versions that use the other infinite series.}
-
-\owen{The weird and interesting bit is to compute the factorization homology over a nontrivial (closed) manifold.}
+\owen{Please check this carefully, Greg. The lemma is meaningful even if the proposition is bogus.}
+
+In the case of the infinite series of Lie algebras, 
+there are theorems that tell us about the limiting behavior of Lie algebra chains and cochains as $N$ goes to infinity.
+These can be applied to our models of the center to obtain novel $\EE_n$ algebras.
+
+Let $\Cyc_*(A)$ denote the {\em cyclic chains} of a dg associative algebra~$A$.
+
+\def\gl{\frak{gl}}
+
+\begin{prp}
+There is a quasi-isomorphism of $\EE_n$ algebras
+\[
+{\frak Z}_n(\frak{gl}_\infty) \xto{\simeq} \clies(\frak{\gl}_\infty) \otimes \Sym(\Cyc_*(k[-n])[1])  ,
+\]
+and so, in particular, the $N \to \infty$ limit of ${\frak Z}_n(\frak{gl}_N)$ is commutative.
+\end{prp}
+
+\begin{proof}
+The Loday-Quillen-Tsygan (LQT) theorem --- for nonunital algebras --- provides a quasi-isomorphism
+\[
+\cliels(\gl_\infty(A))^{\gl_\infty(k)} \xto{\simeq} \Sym(\Cyc_*(A)[1])
+\] 
+and it is functorial in the algebra~$A$.
+\owen{I used {\em invariants} here rather than {\em coinvariants}. Is that allowed?}
+Now
+\[
+\clies(\gl_\infty, \cliels(\gl_\infty(A)) \simeq \cliels(\gl_\infty) \otimes \cliels(\gl_\infty(A))^{\gl_\infty(k)},
+\]
+as shown in the proof of the LQT theorem.
+
+We take $A = \Omega^*_c(V)$ and use the functoriality to see that we get a quasi-isomorphism of prefactorization algebras, as claimed.
+\end{proof}
+
+There are immediate analogs of this theorem where we replace $\gl_N$ by $\frak{so}_N$ or $\frak{sp}_N$ and where we replace cyclic chains by dihedral chains.
+
+A striking consequence of the LQT map appears at the level of factorization homology.
+
+\begin{lmm}
+For a closed $n$-dimensional manifold~$M$, 
+\begin{align*}
+\int_M {\frak Z}_n(\frak{gl}_\infty) 
+&\simeq \clies(\Omega^*(M) \otimes \gl_\infty, \Sym(\Cyc_*(\Omega^*(M))[1])) \\
+&\simeq \clies(\Omega^*(M) \otimes \gl_\infty, \Sym(\Omega^*(LM/^h S^1))[1]))
+\end{align*}
+where $\Omega^*(LM/^h S^1)$ denotes some cochain model for the cochains of the homotopy quotient of the free loop space under the canonical rotation action on loops.
+\end{lmm}
+
+\owen{That phrasing could be improved.}
+
+Implicit in the statement is that one must describe the needed (and non-obvious) action of $\gl_\infty(\Omega^*(M))$ on a symmetric algebra generated by cyclic chains, respectively the rotation-equivariant cochains on the free loop space~$LM$.
+
+What makes this result striking is that it shows how the {\em cyclic loop space} $LM/^h S^1$ appears out of taking a large $N$ limit of factorization homology.
+This kind of result is especially interesting from the perspective of physics, 
+as a kind of topological gauge/string duality.
+In Section~\ref{sec: TFT} we explain how the center $\frak{Z}_n(\gl_\infty)$ can be understood as the {\em quantum observables} of topological BF theory for the Lie algebra $\gl_\infty$.
+In this sense, the left hand side of the lemma $\int_M {\frak Z}_n(\frak{gl}_\infty)$ describes the global quantum observables over the manifold $M$.
+On the right hand side, we see the cyclic loop space of $M$,
+which arises naturally as the configuration space of a closed string theory with target~$M$.
+
+\begin{proof}
+As $\Omega^*_c(M) = \Omega^*(M)$ because $M$ is closed, 
+one applies the LQT theorem for {\em unital} algebras
+\[
+\cliels(\gl_\infty(\Omega^*(M))) \xto{\simeq} \Sym(\Cyc_*(\Omega^*(M))[1])
+\]
+to obtain the first weak equivalence.
+(In fact, one must transfer the $\gl_\infty(\Omega^*(M))$ along the LQT map.)
+Then Jones' theorem \cite{} provides the second weak equivalence.
+\end{proof}
 

### 2020-09-09 draft.tex
moved and improved the cyclic stuff

@@
 %
-%Our results pertains to (1) by taking $N \to \infty$, and to (2) through the derived {\em centralizer} of the map $\UU_n\sl_\infty \hookrightarrow \UU_n\gl_\infty(A)$, where $A$ is a dg algebra.
+%Our results pertains to (1) by taking $N \to \infty$, and to (2) through the derived {\em centralizer} of the map $\UU_n\sl_\infty \hookrightarrow \UU_n\fgl_\infty(A)$, where $A$ is a dg algebra.
 Note that the usual derived center is the centralizer of the identity map $\UU_n\fg \to \UU_n\fg$.
@@
 %
-%Our primary tool here is the Loday-Quillen-Tsygan (LQT) theorem which describes the large $N$ limit of the Lie algebra homology of $\gl_N(A)$, for a dg associative algebra $A$.
+%Our primary tool here is the Loday-Quillen-Tsygan (LQT) theorem which describes the large $N$ limit of the Lie algebra homology of $\fgl_N(A)$, for a dg associative algebra $A$.
 Since the enveloping $\EE_n$ algebra of a Lie algebra can be constructed as a locally constant factorization algebra made out of the shifted Chevalley-Eilenberg chains \cite{}, the relevance of the LQT theorem in this context  should be apparent.
@@
 abelian, semisimple, and free.
-We also indicate the large $N$ behavior of enveloping algebras for the infinite families $\frak{gl}_N$, $\frak{sp}_N$, and $\frak{so}_N$,
-by exploiting the Loday-Quillen-Tsygan theorem and its cousins.
 
@@
 \]
-\end{proof}
-
-\subsection{The large $N$ limit of the center ${\frak Z}_n(\UU_n \frak{gl}_N)$ and cyclic cohomology}
-
-\owen{Please check this carefully, Greg. The lemma is meaningful even if the proposition is bogus.}
-
-In the case of the infinite series of Lie algebras, 
-there are theorems that tell us about the limiting behavior of Lie algebra chains and cochains as $N$ goes to infinity.
-These can be applied to our models of the center to obtain novel $\EE_n$ algebras.
-
-Let $\Cyc_*(A)$ denote the {\em cyclic chains} of a dg associative algebra~$A$.
-
-\def\gl{\frak{gl}}
-
-\begin{prp}
-There is a quasi-isomorphism of $\EE_n$ algebras
-\[
-{\frak Z}_n(\frak{gl}_\infty) \xto{\simeq} \clies(\frak{\gl}_\infty) \otimes \Sym(\Cyc_*(k[-n])[1])  ,
-\]
-and so, in particular, the $N \to \infty$ limit of ${\frak Z}_n(\frak{gl}_N)$ is commutative.
-\end{prp}
-
-\begin{proof}
-The Loday-Quillen-Tsygan (LQT) theorem --- for nonunital algebras --- provides a quasi-isomorphism
-\[
-\cliels(\gl_\infty(A))^{\gl_\infty(k)} \xto{\simeq} \Sym(\Cyc_*(A)[1])
-\] 
-and it is functorial in the algebra~$A$.
-\owen{I used {\em invariants} here rather than {\em coinvariants}. Is that allowed?}
-Now
-\[
-\clies(\gl_\infty, \cliels(\gl_\infty(A)) \simeq \cliels(\gl_\infty) \otimes \cliels(\gl_\infty(A))^{\gl_\infty(k)},
-\]
-as shown in the proof of the LQT theorem.
-
-We take $A = \Omega^*_c(V)$ and use the functoriality to see that we get a quasi-isomorphism of prefactorization algebras, as claimed.
-\end{proof}
-
-There are immediate analogs of this theorem where we replace $\gl_N$ by $\frak{so}_N$ or $\frak{sp}_N$ and where we replace cyclic chains by dihedral chains.
-
-A striking consequence of the LQT map appears at the level of factorization homology.
-
-\begin{lmm}
-For a closed $n$-dimensional manifold~$M$, 
-\begin{align*}
-\int_M {\frak Z}_n(\frak{gl}_\infty) 
-&\simeq \clies(\Omega^*(M) \otimes \gl_\infty, \Sym(\Cyc_*(\Omega^*(M))[1])) \\
-&\simeq \clies(\Omega^*(M) \otimes \gl_\infty, \Sym(\Omega^*(LM/^h S^1))[1]))
-\end{align*}
-where $\Omega^*(LM/^h S^1)$ denotes some cochain model for the cochains of the homotopy quotient of the free loop space under the canonical rotation action on loops.
-\end{lmm}
-
-\owen{That phrasing could be improved.}
-
-Implicit in the statement is that one must describe the needed (and non-obvious) action of $\gl_\infty(\Omega^*(M))$ on a symmetric algebra generated by cyclic chains, respectively the rotation-equivariant cochains on the free loop space~$LM$.
-
-What makes this result striking is that it shows how the {\em cyclic loop space} $LM/^h S^1$ appears out of taking a large $N$ limit of factorization homology.
-This kind of result is especially interesting from the perspective of physics, 
-as a kind of topological gauge/string duality.
-In Section~\ref{sec: TFT} we explain how the center $\frak{Z}_n(\gl_\infty)$ can be understood as the {\em quantum observables} of topological BF theory for the Lie algebra $\gl_\infty$.
-In this sense, the left hand side of the lemma $\int_M {\frak Z}_n(\frak{gl}_\infty)$ describes the global quantum observables over the manifold $M$.
-On the right hand side, we see the cyclic loop space of $M$,
-which arises naturally as the configuration space of a closed string theory with target~$M$.
-
-\begin{proof}
-As $\Omega^*_c(M) = \Omega^*(M)$ because $M$ is closed, 
-one applies the LQT theorem for {\em unital} algebras
-\[
-\cliels(\gl_\infty(\Omega^*(M))) \xto{\simeq} \Sym(\Cyc_*(\Omega^*(M))[1])
-\]
-to obtain the first weak equivalence.
-(In fact, one must transfer the $\gl_\infty(\Omega^*(M))$ along the LQT map.)
-Then Jones' theorem \cite{} provides the second weak equivalence.
 \end{proof}
@@
 which unwinds to 
-\[
+\begin{equation}
+\label{eqn: taut}
 \clies(\fg \otimes \Omega^\bu(S), \cliels(\fg \otimes \Omega^\bu(S)) \simeq \End^\bullet(\cliels(\fg \otimes \Omega^\bu(S))),
-\]
+\end{equation}
 which looks rather tautological.
@@
 
+\subsection{Cyclic homology and the large $N$ limits of $\UU_n \fgl_N$ and ${\frak Z}_n(\fgl_N)$}
+
+In the case of the infinite series of Lie algebras, 
+there are theorems that tell us about the limiting behavior of Lie algebra chains and cochains as $N$ goes to infinity.
+These can be applied to our models to obtain striking results about factorization homology.
+
+\def\Dih{{\rm Dih}}
+
+Let $\Cyc_*(A)$ denote the {\em cyclic chains} of a dg associative algebra~$A$.
+A key theorem --- one of the original motivations for cyclic homology --- is the Loday-Quillen-Tsygan (LQT) theorem \cite{},
+which provides an explicit quasi-isomorphism
+\begin{equation}
+\label{eqn: LQT}
+\cliels(\fgl_\infty(A)) \xto{\simeq} \Sym(\Cyc_*(A)[1])
+\end{equation}
+for any unital dg associative algebra~$A$.
+A similar result \cite{} holds when we replace $\fgl_N$ by $\frak{so}_N$ or $\frak{sp}_N$, with
+\[
+\label{eqn: LQT}
+\cliels({\frak{so}}_\infty(A)) \xto{\simeq} \Sym(\Dih_*(A)[1]),
+\]
+with $\Dih_*$ denoting the dihedral chains.
+Note that one can use either $\frak{so}_N$ or $\frak{sp}_N$ on the left hand side.
+
+\owen{Please verify my conditions, as I got a bit confused between different sources.}
+
+Another key theorem, due to Jones \cite{} for cyclic chains and extend to dihedral chains by Ungheretti \cite{},
+is that
+\[
+\Cyc_*(\Omega^*(M)) \simeq \Omega^*(LM/^h S^1)
+\]
+for a simply connected manifold $M$, 
+where $LM/^h S^1$ denotes the homotopy quotient of the free loop space $LM$ under the canonical rotation action on loops,
+and where we mean some model of cochains on the right hand side.
+In other words, the right hand side is the $S^1$-equivariant cochains of the free loop space.
+(This result holds, more generally, for a simply connected topological space of finite type, so long as one uses an appropriate model of cochains of the space, 
+but we focus here on manifolds.)
+
+From hereon we will work only with cyclic chains and $\fgl$,
+but one obtains immediate analogs by replacing those with dihedral chains and $\frak{so}$ or~$\frak{sp}$.
+
+As a first observation, let us see what this result implies about factorization homology of the enveloping $\EE_n$ algebra.
+
+\begin{lmm}
+For a closed $n$-dimensional manifold~$M$, 
+\begin{align*}
+\int_M \UU_n(\frak{gl}_\infty)
+&\simeq \cliels(\Omega^*(M) \otimes \fgl_\infty) \\
+&\simeq \Sym(\Cyc_*(\Omega^*(M))[1]) \\
+&\simeq \Sym(\Omega^*(LM/^h S^1))[1])).
+\end{align*}
+\end{lmm}
+
+Although this result is immediate from the theorems we just mentioned,
+it is rather surprising to see the {\em cyclic loop space} $LM/^h S^1$ appears out of taking a large $N$ limit of factorization homology.
+Note that this identification provides a commutative algebra structure on the factorization homology for $\fgl_\infty$, 
+which is nowhere to be seen for~$\fgl_N$.
+
+\begin{qtn}
+Is there some local version of this relationship?
+That is, can we obtain a version of the LQT theorem at the level of $\EE_n$ algebras such that factorization homology recovers the quasi-isomorphism of this lemma?
+\end{qtn}
+
+This kind of result is especially interesting from the perspective of physics, 
+as a kind of topological gauge/string duality.
+In Section~\ref{sec: TFT} we explain how $\UU_n(\fgl_\infty)$ can be understood as the {\em quantum observables} of a gauge theory for the Lie algebra $\fgl_\infty$.
+In this sense, the left hand side of the lemma $\int_M \UU_n(\frak{gl}_\infty)$ describes the global quantum observables over the manifold $M$.
+On the right hand side, we see the cyclic loop space of $M$,
+which arises naturally as the configuration space of a closed string theory with target~$M$.
+Indeed, those familiar with closed string field theory will recognize the right hand side as related to the ``Fock space'' of such a theory.
+\owen{Check me, Bri-guy.}
+
+Now let's examine what our calculus results imply;
+we simply apply quasi-isomorphism~\eqref{eqn: taut} in conjunction with the theorems.
+
+\begin{lmm}
+For a closed $n$-dimensional manifold~$M$, 
+\[
+\clies(\fgl_\infty \otimes \Omega^\bu(M), \cliels(\fgl_\infty \otimes \Omega^\bu(M)) \simeq \End^\bullet(\Sym(\Omega^*(LM/^h S^1))[1])))
+\]
+where the left hand side is the factorization homology of $\EE_n$ center ${\frak Z}_n(\fgl_\infty)$ and the right hand side is the $\EE_0$ center of the factorization homology of~$\UU_n \fgl_\infty$.
+\end{lmm}
+
+In physical terms, the right hand side encodes the algebra of operators on the Fock space of a closed string field theory.
+Hence this statement provides a novel way to construct that algebra.
+Even better, in Section~\ref{sec: TFT}, we identify the left hand side as the quantum observables of the topological BF theory for $\fgl_N$ on $M \times \RR$.
+In this sense we have deepened the topological gauge/string duality just introduced.
+
 \section{Centers and topological field theories}
@@
 
-\begin{prp} \label{prp:swiss1}
+\begin{prp}
+\label{prp:swiss1}
 Let $\fg$ be an $L_\infty$ algebra. 

### 2020-09-09 draft.tex
constructible

--- 2020-09-09 draft.tex
@@
 
-\brian{I think this definition is fucked}
+Before stating the definition of this model, we introduce the following variant of the de Rham complex of differential forms on $\RR_{\geq 0}$. 
+Let $j : \RR_{>0} \hookrightarrow \RR_{\geq 0}$ be the embedding of the open ray into the closed ray. 
+Define the complex
+\[
+\begin{tikzcd}
+& \ul{0} & \ul{1} \\
+\Tilde{\Omega}^\bu (\RR_{\geq 0}) = & \Omega^0 (\RR_{\geq 0}) \ar[r, "j^* \circ \d_{\rm dR}"] & \Omega^1(\RR_{>0})  .
+\end{tikzcd}
+\]
+The commutative dg algebra structure on $\Tilde{\Omega}^\bu (\RR_{\geq 0})$ is defined by the rule
+\[
+f \cdot (g \, \d t) = (j^* f) g\, \d t .
+\]
 
@@
 \[
-\bC_n (\fg) (U) = \clies \bigg(\fg \otimes \Omega (U) \; , \; \Sym \left(\fg \otimes \Omega_c(U) [2] \right) \bigg) .
+\bC_n (\fg) (U) = \clies \bigg(\fg \otimes \Omega^\bu (U) \; , \; \Sym \left(\fg \otimes \Omega^\bu_c(U) [2] \right) \bigg) .
 \]
@@
 \[
-\bC_n (\fg) (V \times [0,\epsilon)) = {\rm Sym} \left(\fg \otimes \Omega^\bu_c (V \times [0,\epsilon) [2] \right).
-\]
+\bC_n (\fg) (V \times [0,\epsilon)) = \clies\bigg(\fg \otimes \Omega^\bu(V) \Hat{\otimes} \Tilde{\Omega}^\bu([0,\epsilon))  \; , \; \Sym\left(\fg \otimes \Omega^\bu_c (V \times [0,\epsilon))[2] \right) \bigg).
+\]
+%\brian{this is wrong
+%\[
+%\bC_n (\fg) (V \times [0,\epsilon)) = {\rm Sym} \left(\fg \otimes \Omega^\bu_c (V \times [0,\epsilon) [2] \right).
+%\]
+%}
 \end{itemize}
@@
 \begin{tikzcd}
-\clies \bigg(\fg \otimes \Omega^\bu (U) \; , \; \Sym \left(\fg \otimes \Omega^\bu_c(U) [2] \right) \bigg) \; \otimes \;  {\rm Sym} \left(\fg \otimes \Omega^\bu_c (V\times [0,\epsilon)) [2] \right) \ar[d, "{\rm ev}_1"] \\
-\Sym \left(\fg \otimes \Omega^\bu_c(U) [2] \right) \; \otimes \; \Sym \left(\fg \otimes \Omega^\bu_c (V \times [0,\epsilon)) [2] \right) \ar[d, "\simeq"] \\
-\Sym\left(\fg \otimes \left(\Omega^\bu_c(U) \oplus \Omega^\bu_c(V \times [0,\epsilon)) \right) [2] \right) \ar[d, "i_*"]\\
-\Sym \left( \fg \otimes \Omega^\bu_c(V' \times [0,\epsilon')) [2] \right)
+\clies \bigg(\fg \otimes \Omega^\bu (U) \; , \; \Sym \left(\fg \otimes \Omega^\bu_c(U) [2] \right) \bigg) \; \otimes \;  \clies\bigg(\fg \otimes \Omega^\bu(V) \otimes \Tilde{\Omega}^\bu([0,\epsilon))  \; , \; \Sym\left(\fg \otimes \Omega^\bu_c (V \times [0,\epsilon))[2] \right) \bigg) \ar[d, "\simeq"] \\
+\clies \bigg(\fg \otimes \left(\Omega^\bu (U) \oplus \Omega^\bu(V) \Hat{\otimes} \Tilde{\Omega}^\bu([0,\epsilon)) \right) \; , \; \Sym \left(\fg \otimes \left(\Omega^\bu_c(U) [2] \oplus \Omega^\bu_c(V \times [0,\epsilon)) [2]\right)\right) \bigg) \ar[d, "i^* \otimes i_*"] \\
+\clies\bigg(\fg \otimes \Omega^\bu(V') \Hat{\otimes} \Tilde{\Omega}^\bu([0,\epsilon'))  \; , \; \Sym\left(\fg \otimes \Omega^\bu_c (V' \times [0,\epsilon'))[2] \right) \bigg).
 \end{tikzcd}
 \]
-The first map ${\rm ev}_1$ evaluates the unit $1$ in $\Sym\left(\fg \otimes \Omega^\bu(U)\right)$ and the second map uses the fact that the symmetric algebra functor is monoidal. 
-Finally, the third map is induced by the extension of compactly supported de Rham forms along the embedding (\ref{eqn:embed}). 
+
+%\Sym \left(\fg \otimes \Omega^\bu_c(U) [2] \right) \; \otimes \; \Sym \left(\fg \otimes \Omega^\bu_c (V \times [0,\epsilon)) [2] \right) \ar[d, "\simeq"] \\
+%\Sym\left(\fg \otimes \left(\Omega^\bu_c(U) \oplus \Omega^\bu_c(V \times [0,\epsilon)) \right) [2] \right) \ar[d, "i_*"]\\
+%\Sym \left( \fg \otimes \Omega^\bu_c(V' \times [0,\epsilon')) [2] \right)
+The first map uses the fact that the symmetric algebra functor is monoidal. 
+The second map is induced from restriction and extension of de Rham forms and compactly supported de Rham forms along the embedding (\ref{eqn:embed}). 
 \end{dfn}
+
+\begin{rmk}
+Here, we remark that pulling back along an embedding $\iota : U \hookrightarrow V \times [0,\epsilon)$, where $U \subset M \times \RR_{>0}$ determines a composition of cochain complexes
+\[
+\Omega^\bu (V') \otimes \Tilde{\Omega}^\bu([0,\epsilon)) \xto{j^*}  \Omega^\bu (V') \Hat{\otimes} \Omega^\bu((0,\epsilon)) \cong \Omega^\bu(V \times (0,\epsilon)) \xto{\iota^*} \Omega^\bu(U) .
+\]
+This is our model for restriction $\iota^*$ of de Rham forms that is used in the definition above.
+\end{rmk}
 
@@
 Similarly, integration of compactly supported forms along $\RR_{\geq 0}$ determines a quasi-isomorphism of factorization algebras $\int_{\RR_{\geq 0}} : \bC_n(\fg)^\partial \to {\rm Gr} \; \bU_n(\fg)$.
+\brian{I should spell this out now.}
 
@@
 \begin{proof}
+\brian{we should just cite our paper with Eugene for this, with a few comments about what changes}
 Suppose $V \times [0,\epsilon) \subset M \times \RR_{\geq 0}$ is an open set. 

### 2020-09-09 draft.tex
small tweaks

@@
 
-\greg{We could relate this to $P_n$-center of $\fg$. That shall also (but I have to think about the proof more), 
-at least up to formality gives the $P_{n+1}$-structure on it. }\owen{Brian now does this in the TFT section.}
+\greg{We could relate this to $P_n$ center of $\fg$. That shall also (but I have to think about the proof more), 
+at least up to formality gives the $P_{n+1}$ structure on it. }\owen{Brian now does this in the TFT section.}
 
@@
 
-For a reductive Lie algebra $\fg$, the Harish-Chandra isomorphism is an isomorphism of commutative algebras
-\[
-Z(U(\fg)) \xto{\cong} {\rm Sym} (\fh)^W
-\]
-where $\fh$ is a Cartan subalgebra and $W$ is the Weyl group of $\fg$. 
-Here $Z(U(\fg))$ denotes the ordinary center of the associative algebra $U(\fg)$.
-
-The following result generalizes (and implies) the Harish--Chandra isomorphism for the $\EE_n$-center of the $\EE_n$-enveloping algebra.
+For a reductive Lie group $G$, the Harish-Chandra isomorphism is an isomorphism of commutative algebras
+\[
+Z(U(\fg)) \xto{\cong} {\rm Sym} (\fh)^W,
+\]
+where $\fh$ is a Cartan subalgebra of the Lie algebra $\fg$ of $G$ and $W$ is the Weyl group of $G$. 
+Here $Z(U(\fg))$ denotes the ordinary center of the associative algebra~$U(\fg)$.
+
+The following result generalizes the Harish--Chandra isomorphism to the $\EE_n$ center of the  enveloping $\EE_n$ algebra.
 
@@
 \end{proof}
+
+\owen{I think the usual Chevalley theorem only applies when $1-n$ is an even integer. I'm not sure what the theorem is called when $1-n$ is odd.}
 
@@
 \begin{rmk}
-One way to formulate the definition of a $\PP_{[n+1,n]}$ algebra $(A,B)$ is to require a map of commutative dg algebras $A \to B$ together with a lift to a map of $\PP_{n+1}$ algebras $A \to \fZ_{\PP_n} (B)$, where $\fZ_{\PP_n}(B)$ is the {\em $\PP_n$-center} of the $\PP_n$ algebra $B$.
+One way to formulate the definition of a $\PP_{[n+1,n]}$ algebra $(A,B)$ is to require a map of commutative dg algebras $A \to B$ together with a lift to a map of $\PP_{n+1}$ algebras $A \to \fZ_{\PP_n} (B)$, where $\fZ_{\PP_n}(B)$ is the {\em $\PP_n$ center} of the $\PP_n$ algebra $B$.
 By a similar proof as in the main part of the paper, we expect that one can see that the factorization algebra
@@
 \]
-is a model for the $\PP_n$-center of the $\PP_n$-{\em enveloping algebra} $\UU_{\PP_n} (\fg) = {\rm Sym} (\fg [1-n])$. 
+is a model for the $\PP_n$ center of the {\em enveloping $\PP_n$ algebra} $\UU_{\PP_n} (\fg) = {\rm Sym} (\fg [1-n])$. 
 \end{rmk}
@@
 \]
-
 %\Sym \left(\fg \otimes \Omega^\bu_c(U) [2] \right) \; \otimes \; \Sym \left(\fg \otimes \Omega^\bu_c (V \times [0,\epsilon)) [2] \right) \ar[d, "\simeq"] \\
@@
 \begin{rmk}
-Here, we remark that pulling back along an embedding $\iota : U \hookrightarrow V \times [0,\epsilon)$, where $U \subset M \times \RR_{>0}$ determines a composition of cochain complexes
+For an open $U \subset M \times \RR_{>0}$, pulling back along an embedding $\iota : U \hookrightarrow V \times [0,\epsilon)$ determines a composition of cochain complexes
 \[
@@
 
-On each open set $U \subset M \times \RR_{\geq 0}$, the cochain complex $\bC_n(\fg) (U)$ is a commutative dg algebra. 
+On each open set $U \subset M \times \RR_{\geq 0}$, the cochain complex $\bC_n(\fg) (U)$ is a dg commutative algebra. 
 In fact, it has the structure of a $\PP_0$ algebra where the $1$-shifted bracket $\{\cdot, \cdot\}$ is defined as follows.
@@
 \begin{lmm}
-$\bC_n(\fg)$ admits the structure of a constructible $\PP_0$-factorization algebra on~$M \times \RR_{\geq 0}$. 
+$\bC_n(\fg)$ admits the structure of a constructible $\PP_0$ factorization algebra on~$M \times \RR_{\geq 0}$. 
 \end{lmm}
@@
 which for now we assume has no boundary $\partial N = \emptyset$. 
-As a field theory, there is a system of PDE known as the ``solutions to the equations of motion.''
-When $N$ is compact, the moduli space of solutions to these equations of motion for topological BF theory can be described as the mapping space 
+For a field theory, there is a system of PDE, known as the equations of motion, that govern the behavior of the system.
+When $N$ is compact, the moduli space of ``solutions to the equations of motion'' for topological BF theory is provided the mapping space 
 \begin{equation} 
@@
 It is the central theme of \cite{CG1, CG2} that the observables of a {\em perturbative} field theory define the structure of a factorization algebra. 
-Moreover, the observables are equipped with the structure of a $\PP_0$-factorization algebra.
+Moreover, the observables are equipped with the structure of a $\PP_0$ factorization algebra.
 
@@
 In the setup of \cite{CG2}, the factorization algebra of classical observables of generalized topological BF theory is given by the Chevalley--Eilenberg cochains $\clies (\cL)$.   
-The $\PP_0$-structure is induced from the explicit $(-1)$-symplectic pairing $\int A \wedge B$ at the level of the fields. 
+The $\PP_0$ structure is induced from the explicit $(-1)$-symplectic pairing $\int A \wedge B$ at the level of the fields. 
 \end{rmk}

### 2020-09-10 draft.tex
spec seq

@@
 \]
-Let $x^* \otimes \alpha$ denote an homorphism of the form $\fg \otimes \Omega (U) \to \Sym^0 = k$ and $y \otimes \beta$ denote a homomorphism $k = \Sym^0 \to \fg \otimes \Omega_c(U) [2]$. 
-Then, the bracket involving the linear elements $x^* \otimes \alpha$ 
+Let $x^* \otimes \alpha$ denote an homomorphism of the form $\fg \otimes \Omega (U) \to \Sym^0 = k$ and $y \otimes \beta$ denote a homomorphism $k = \Sym^0 \to \fg \otimes \Omega_c(U) [2]$. 
+The bracket between these linear elements $x^* \otimes \alpha$ 
 and $y \otimes \beta$ is defined by
@@
 
-The pair $(\int_{\RR_{>0}} , \int_{\RR_{\geq 0}})$ is a quasi-isomorphisms of factorization sc-pairs. 
-The compatibility of this quasi-isomorphism with Poisson brackets is a direct calculation. 
+The pair of maps $(\int_{\RR_{>0}} , \int_{\RR_{\geq 0}})$ is a quasi-isomorphism of factorization sc-pairs. 
+An explicit and direct calculation verifies that this quasi-isomorphism respects the Poisson brackets. 
 \end{proof}
@@
 
-\brian{spectral sequence}
-
-%\subsection{The bulk TFT}
-%
-%Let us place the locally constant factorization algebra model of the $\EE_n$-enveloping algebra $\bU_n (\fg) = \clieu(\fg \otimes \Omega_c)$ on the $n$-manifold $M$.
-%This factorization algebra is equivalent to the pushforward of a factorization algebra $\Obs_{\rm BF}$ on the $(n+1)$-dimensional manifold $M \times \RR$ along the projection $\pi : M \times (0,1) \to M$ which we proceed to construct.
-%
-%\begin{dfn}
-%For an open set $V \subset M \times (0,1)$ let $\Obs^{\rm cl}_{\rm BF} (V)$ be the cochain complex 
-%\[
-%\Obs^{\rm cl}_{\rm BF} (V) = \clie \bigg(\fg \otimes \Omega (V) \; , \; \Sym \left(\fg \otimes \Omega_c(V) [2] \right) \bigg) .
-%\]
-%The assignment $V \mapsto \Obs^{\rm cl}_{\rm BF}(V)$ defines a locally constant factorization algebra on $M \times (0,1)$. 
-%\end{dfn}
-%
-%We note that $\Obs_{\rm BF}^{\rm cl}$ is a factorization algebra with values in commutative dg algebras. 
-%In fact, it is given by the ``classical observables" of a topological field theory on $M \times (0,1)$ known as ``topological BF theory". 
-%
-%We now consider the pushforward factorization algebra $\pi_* \Obs^{\rm cl}_{\rm BF}$ on $M$.
-%Locally, on disks, we will see that it is quasi-isomorphic to a certain limit, or ``dequantization", of our model for the $\EE_n$-center of $\UU_n \fg$.
-%Recall, this model is given by the factorization algebra on $M$:
-%\begin{equation}\label{eqn:centerTFT}
-%\bZ_n(\fg) = \clie\left(\fg \otimes \Omega \, , \, \clieu (\fg \otimes \Omega_c) \right) .
-%\end{equation}
-%
-%The ``dequantization" is defined using the following filtration of this model.
-%For any Lie algebra $\fh$, let $\clieu_{\leq k} (\fh)$ be the subcomplex of Chevalley--Eilenberg chains which is $\Sym^{\leq k} (\fh[1])$ as an underlying graded vector space. 
-%
-%\begin{dfn}
-%Introduce the filtration on the factorization algebra on $M$ in (\ref{eqn:centerTFT}) by 
-%\[
-%F^k \bZ_n(\fg) = \clie \bigg(\fg \otimes \Omega \; , \; \clieu_{\leq k} (\fg \otimes \Omega_c) \bigg) .
-%\]
-%\end{dfn}
-%
-%This is a filtration of factorization algebras on $M$. 
-%The associated graded factorization algebra is
-%\[
-%{\rm Gr} \; \bZ_n(\fg) \; = \; \clie \bigg(\fg \otimes \Omega \; , \; \Sym \left(\fg \otimes \Omega_c [1] \right) \bigg) .
-%\]
-%Notice this is similar to the model $\EE_n$-center except we have turned off the Chevalley--Eilenberg differential on chains. 
-%
-% \begin{lmm}
-%There is a quasi-isomorphism of commutative factorization algebras on $M$:
-%\[
-%\pi_* \Obs^{\rm cl}_{\rm BF} \; \xto{\simeq} \; {\rm Gr} \; \bZ_n(\fg) .
-%\]
-%\end{lmm}
-%
-%In fact, we will show that this quasi-isomorphism is a deformation retraction. 
-%
-%\begin{proof}
-%To exhibit this quasi-isomorphism, we introduce the following cochain maps.
-%For an open set $U \subset M$ let
-%\[
-%\int_\RR : \Omega_c(U \times \RR) \to \Omega_c (U) [1] 
-%\] 
-%be the map which integrates a compactly supported form on $U \times \RR$ along $\RR$. 
-%This map is a quasi-isomorphism for any $U $ and admits the following explicit retract. 
-%Let $\phi$ be a fixed compactly supported function on $\RR$ of mass $1$ and define
-%\[
-%r_\phi : \Omega_c(U) [1] \to \Omega_c (U \times \RR)
-%\]
-%by $r_\phi (\alpha) = \alpha \wedge \phi \, \d t$. 
-%\end{proof}
-
-%\begin{lmm}
-%Consider the locally constant factorization algebra $\cF_{\rm bulk}$ on $M \times \RR$ which assigns to an open set $U \subset M \times \RR$
-%\[
-%\cF_{\rm bulk} = \clie \left(\fg \otimes \Omega (U) \; , \; \clieu (\fg \otimes \Omega_c (U)[1]) \right) .
-%\]
-%Then, 
-%\end{lmm}
-%
-%\begin{proof}
-%For $V \subset M$, the integration of compactly supported de Rham forms along $\RR$ 
-%\[
-%\fg \otimes \Omega_c (\pi^{-1} (V)) = \fg \otimes \Omega_c (V \times \RR) \xto{\int_{\RR}} \fg \otimes \Omega_c (V) [-1] .
-%\]
-%is a quasi-isomorphism. 
-%
-%\end{proof}
+We conclude by describing a useful application of this work back in algebraic topology.
+The factorization sc-pair $(\bZ_n(\fg), \bU_n \fg)$ makes it quick and convenient to compute factorization homology over an $n$-dimensional manifold,
+but that model is not amenable to computations over $n+1$-dimensional manifolds with boundary,
+because $\bZ_n(\fg)$ is not explicitly described as a factorization algebra on $n+1$-dimensional manifolds.
+Our work in this section does provide, however, an explicit description of~$\Gr {\frak Z}_n(\fg)$. 
+Thus, we have access to the beginning of a spectral sequence.
+
+\begin{prp}
+Let $M$ be an $n+1$-dimensional manifold with boundary $\partial M$. 
+As $(\frak{Z}_n(\fg), \UU_n \fg)$ form a filtered algebra over the Swiss cheese operad, 
+there is a spectral sequence
+\[
+\int_{(M,\partial M)} (\Gr \frak{Z}_n(\fg), \Gr \UU_n \fg) \Longrightarrow \int_{(M,\partial M)} (\frak{Z}_n(\fg), \UU_n \fg).
+\]
+\end{prp}
 

### 2020-09-10 draft.tex
merge

--- 2020-09-09 draft.tex
@@
 \]
-For $U \subset M \times \RR_{>0}$ the underlying graded vector space of $\bC_n(\fg)(U)$ is of the form
-\[
-{\rm Hom}^\bu\left(\Sym(\fg \otimes \Omega^\bu (U)[1]) \; , \; {\rm Sym}  \left(\fg \otimes \Omega^\bu_c(U) [2] \right) \right)  .
-\]
-Let $x^* \otimes \alpha$ denote an homorphism of the form $\fg \otimes \Omega (U)[1] \to \Sym^0 = k$ and $y \otimes \beta$ denote a homomorphism $k = \Sym^0 \to \fg \otimes \Omega_c(U) [1]$. 
-Then, the bracket involving the linear elements $x^* \otimes \alpha$ 
-and $y \otimes \beta$ is defined by
-\begin{align*}
-\{x^* \otimes \alpha  , y \otimes \beta \} & = \<x^*, y\>_\fg \int_U \alpha \beta \\
-\{x^* \otimes \alpha , x'^* \otimes \alpha' \} & = 0 \\
-\{y \otimes \beta , y' \otimes \beta'\} & = 0 . 
-\end{align*}
-Here, $\<x^*, y\>_\fg$ denotes the linear pairing between $\fg$ and $\fg^*$ and $\int_U\alpha \beta$ denotes the linear pairing between compactly supported distributional differential forms and differential forms.
-\brian{how to say this now}
+We first define the bracket $\{F,G\}$ between the following simple elements $F : \fg \otimes \Omega^\bu (U)[1] \to k$ and $G : k \to \fg \otimes \Omega^\bu_c(U)[1]$. 
+Define $\{F, G\} \in k$ by the composition
+\[
+k \xto{G} \fg \otimes \Omega^\bu_c(U)[1] \hookrightarrow \fg \otimes \Omega^\bu(U)[1] \xto{F} k
+\]
+where the middle arrow uses the obvious inclusion of compactly supported de Rham forms inside of all de Rham forms. 
+We extend this to a bracket on the full complex by the graded Leibniz rule.
+
+%Let $x^* \otimes \alpha$ denote an homorphism of the form $\fg \otimes \Omega (U)[1] \to \Sym^0 = k$ and $y \otimes \beta$ denote a homomorphism $k = \Sym^0 \to \fg \otimes \Omega_c(U) [1]$. 
+%Then, the bracket involving the linear elements $x^* \otimes \alpha$ 
+%and $y \otimes \beta$ is defined by
+%\begin{align*}
+%\{x^* \otimes \alpha  , y \otimes \beta \} & = \<x^*, y\>_\fg \int_U \alpha \beta \\
+%\{x^* \otimes \alpha , x'^* \otimes \alpha' \} & = 0 \\
+%\{y \otimes \beta , y' \otimes \beta'\} & = 0 . 
+%\end{align*}
+%Here, $\<x^*, y\>_\fg$ denotes the linear pairing between $\fg$ and $\fg^*$ and $\int_U\alpha \beta$ denotes the linear pairing between compactly supported distributional differential forms and differential forms.
+%\brian{how to say this now}
 \end{proof}
@@
 
-We turn towards a model for the $\EE_n$ center as a constructible factorization algebra.
+We turn towards a model for the $\EE_n$-center as a constructible factorization algebra on an $(n+1)$-manifold with boundary.
 
@@
 Let $j : \RR_{>0} \hookrightarrow \RR_{\geq 0}$ be the embedding of the open ray into the closed ray. 
-Define the complex
-\[
-\begin{tikzcd}
-& \ul{0} & \ul{1} \\
-\Tilde{\Omega}^\bu (\RR_{\geq 0}) = & \Omega^0 (\RR_{\geq 0}) \ar[r, "j^* \circ \d_{\rm dR}"] & \Omega^1(\RR_{>0})  .
-\end{tikzcd}
+Let $\Tilde{\Omega}^\bu (\RR_{\geq 0})$ be the two-term complex
+\[
+\Omega^0(\RR_{\geq 0}) \xto{j^* \circ \d_{\rm dR}} \Omega^1(\RR_{>0})[-1]  .
 \]
@@
 \]
-Let $x^* \otimes \alpha$ denote an homorphism of the form $\fg \otimes \Omega (U) \to \Sym^0 = k$ and $y \otimes \beta$ denote a homomorphism $k = \Sym^0 \to \fg \otimes \Omega_c(U) [2]$. 
-Then, the bracket involving the linear elements $x^* \otimes \alpha$ 
-and $y \otimes \beta$ is defined by
-\begin{align*}
-\{x^* \otimes \alpha  , y \otimes \beta \} & = \<x^*, y\>_\fg \int_U \alpha \beta \\
-\{x^* \otimes \alpha , x'^* \otimes \alpha' \} & = 0 \\
-\{y \otimes \beta , y' \otimes \beta'\} & = 0 . 
-\end{align*}
-Here, $\<x^*, y\>_\fg$ denotes the linear pairing between $\fg$ and $\fg^*$ and $\int_U\alpha \beta$ denotes the linear pairing between compactly supported distributional differential forms and differential forms.
-\brian{how to say this now}
-The bracket is extended to the entire symmetric algebra by using the graded Leibniz rule.
+The Poisson structure is described in a similar way as in the proof of Lemma \ref{lmm:pois1}. 
+We first define the bracket $\{F,G\}$ between the following simple elements $F : \fg \otimes \Omega^\bu (U)[2] \to k$ and $G : k \to \fg \otimes \Omega^\bu_c(U)[2]$. 
+Define $\{F, G\} \in k$ by the composition
+\[
+k \xto{G} \fg \otimes \Omega^\bu_c(U)[2] \hookrightarrow \fg \otimes \Omega^\bu(U)[2] \xto{F} k
+\]
+where the middle arrow uses the obvious inclusion of compactly supported de Rham forms inside of all de Rham forms. 
+Notice that this bracket has cohomological degree $+1$ as desired.
+We extend this to a bracket on the full complex by the graded Leibniz rule.
+
+Next, we define the $\PP_0$-bracket for the value of the factorization algebra on open sets of the form $V \times [0,\epsilon)$. 
+Notice that the underlying graded vector space of $\bC_n(\fg)(V \times [0,\epsilon))$ is of the form
+\[
+{\rm Hom}^\bu\left(\Sym(\fg \otimes \Omega^\bu (V) \otimes \Tilde{\Omega}^\bu ([0,\epsilon))) [1]) \; , \; \Sym \left(\fg \otimes \Omega^\bu_c(V \times [0,\epsilon)) [2] \right) \right)  .
+\]
+We first define the bracket $\{F,G\}$ between the following simple elements 
+\[
+F : \fg \otimes \Omega^\bu(V) \Hat{\otimes} \Tilde{\Omega}^\bu([0,\epsilon)) [2] \to k
+\]
+and 
+\[
+G : k \to \fg \otimes \Omega^\bu_c(V \times [0,\epsilon))[2] .
+\]
+Define $\{F, G\}$ by the composition
+\[
+\begin{tikzcd}
+k \otimes \bigg(\fg \otimes \Omega^\bu(V) \Hat{\otimes} \Tilde{\Omega}^\bu([0,\epsilon)) \bigg) \ar[rdd, dotted, "{\{F,G\}}"'] \ar[r, "G \otimes 1"] & 
+\bigg(\fg \otimes \Omega^\bu_c(V \times [0,\epsilon)) [2]\bigg) \otimes \bigg(\fg \otimes \Omega^\bu(V) \Hat{\otimes} \Tilde{\Omega}^\bu([0,\epsilon)) \bigg) \ar[d,"{[\cdot, \cdot]}"] \\
+& \fg \otimes \Omega^\bu(V) \Hat{\otimes} \Tilde{\Omega}^\bu([0,\epsilon)) [2] \ar[d, "F"] \\ & k
+\end{tikzcd}
+\]
+The middle bracket is induced from the Lie bracket on $\fg$ and the wedge product of differential forms.
+Again, this bracket is extended to the full algebra by the Leibniz rule.
 \end{proof}
@@
 \]
-The map $\int_{\RR_{>0}}$ induces a map of factorization algebras on $M$
-\[
-\int_{\RR_{>0}} : \bC_n(\fg)^\circ \to {\rm Gr} \; \bZ_n (\fg)
+Integration along $\RR_{>0}$ induces a map of factorization algebras on $M$
+\[
+I^{\circ} : \bC_n(\fg)^\circ \to {\rm Gr} \; \bZ_n (\fg)
 \]
 which on linear elements in ${\rm Sym}(\fg \otimes \Omega^\bu_c (V \times \RR_{>0})$ sends $x \otimes \alpha \in \Omega^\bu_c(V \times \RR_{>0})[2]$ to $x \otimes \int_{\RR_{>0}} \alpha \in \Omega^\bu_c (V)[1]$.
-Using the retract $r_\phi$, we see that this is a quasi-isomorphism of factorization algebras on $M$.
-
-Similarly, integration of compactly supported forms along $\RR_{\geq 0}$ determines a quasi-isomorphism of factorization algebras $\int_{\RR_{\geq 0}} : \bC_n(\fg)^\partial \to {\rm Gr} \; \bU_n(\fg)$.
-\brian{I should spell this out now.}
-
-The pair $(\int_{\RR_{>0}} , \int_{\RR_{\geq 0}})$ is a quasi-isomorphisms of factorization sc-pairs. 
+
+Next, using the map $r_\phi$, define a map of factorization algebras
+\[
+r_\phi^\circ : {\rm Gr} \; \bZ_n (\fg) \to \bC_n(\fg)^\circ
+\]
+as follows. 
+For an open set $V \subset M$, define $r_{\phi}^\circ (V)$ on linear elements $x \otimes \alpha$ in $\Sym(\fg \otimes \Omega^\bu(V)_c[1])$ by
+\[
+r_\phi^\circ (U) (x \otimes \alpha) = x \otimes (\pi^* \alpha \wedge \phi \d t)  .
+\]
+This map can be extended to all of ${\rm Gr} \; \bZ_n(\fg)$ in a similar fashion. 
+One can show that $r_\phi^\circ$ is a deformation retract of $I^\partial$.
+In particular, $I^\partial$ is a quasi-isomorphism of factorization algebras on $M$.
+
+Similarly, integration of compactly supported forms along $\RR_{\geq 0}$ determines a quasi-isomorphism of factorization algebras 
+\[
+I^\partial : \bC_n(\fg)^\partial \to {\rm Gr} \; \bU_n(\fg) .
+\]
+Recall that for $V \subset M$ we have
+\[
+\bC_n(\fg)^\partial (V) = \clies\bigg(\fg \otimes \Omega^\bu(V) \Hat{\otimes} \Tilde{\Omega}^\bu(\RR_{\geq 0})  \; , \; \Sym\left(\fg \otimes \Omega^\bu_c (V \times \RR_{\geq 0})[2] \right) \bigg) .
+\]
+On $V$, the map $I^\partial (V)$ is defined by the composition
+\[
+\begin{tikzcd}
+\clies\bigg(\fg \otimes \Omega^\bu(V) \Hat{\otimes} \Tilde{\Omega}^\bu(\RR_{\geq 0})  \; , \; \Sym\left(\fg \otimes \Omega^\bu_c (V \times \RR_{\geq 0})[2] \right) \bigg) \ar[r, "{{\rm ev}_1}"] & \Sym\left(\fg \otimes \Omega^\bu_c (V \times \RR_{\geq 0})[2] \right) \ar[d, "{\int_{\RR_{\geq 0}}}"] \\ &  \Sym\left(\fg \otimes \Omega^\bu_c (V)[1] \right) .
+\end{tikzcd}
+\]
+The first map ${\rm ev}_1$ evaluates the unit in $\Sym \left(\fg \otimes \Omega^\bu(V) \Hat{\otimes} \Tilde{\Omega}^\bu(\RR_{\geq 0})\right)$ and the second map is induced by integration along $\RR_{\geq 0}$.
+It is immediate to check that $I^{\partial}$ extends to a map of factorization algebras.
+
+For an open set $V$ the cochain map $I^{\partial}(V)$ admits the following explicit retract $r_\phi^\partial(V)$ defined on linear elements $x \otimes \alpha$ in $\Sym (\fg \otimes \Omega^\bu_c(V)[1])$ by the formula
+\[
+r_{\phi}^\partial (x \otimes \alpha) = x \otimes (\pi^* \alpha \wedge \phi \d t) \pm \d_{\rm CE} (x \otimes \pi^* \alpha \phi ) .
+\]
+The map $r_\phi^\partial (V)$ is extended to the entire symmetric algebra in the obvious way.
+
+We have shown that $(I^{\circ}, I^\partial)$ is a quasi-isomorphism of factorization sc-pairs. 
 The compatibility of this quasi-isomorphism with Poisson brackets is a direct calculation. 
@@
 
-\owen{Brian: please edit this paragraph.}
 Although we have started here with a Lie group $G$, 
-one can replace $T^*[n] {\rm B}G$ with {\em any} $n$-shifted symplectic derived stack.
+one can replace ${\rm T}^*[n] {\rm B}G$ with {\em any} $n$-shifted symplectic derived stack.
 Such AKSZ theories encompass examples of interest in physics (e.g., the A- and B-models or Rozansky-Witten theories).
-Of particular interest to us here are the shifted cotangent spaces~$T^*[n] X$.
+Of particular interest to us here are the shifted cotangent spaces~${\rm T}^*[n] X$.
 

### 2020-09-10 draft.tex

--- 2020-09-10 draft.tex
@@
 \]
-Let $x^* \otimes \alpha$ denote an homomorphism of the form $\fg \otimes \Omega (U) \to \Sym^0 = k$ and $y \otimes \beta$ denote a homomorphism $k = \Sym^0 \to \fg \otimes \Omega_c(U) [2]$. 
-The bracket between these linear elements $x^* \otimes \alpha$ 
-and $y \otimes \beta$ is defined by
-\begin{align*}
-\{x^* \otimes \alpha  , y \otimes \beta \} & = \<x^*, y\>_\fg \int_U \alpha \beta \\
-\{x^* \otimes \alpha , x'^* \otimes \alpha' \} & = 0 \\
-\{y \otimes \beta , y' \otimes \beta'\} & = 0 . 
-\end{align*}
-Here, $\<x^*, y\>_\fg$ denotes the linear pairing between $\fg$ and $\fg^*$ and $\int_U\alpha \beta$ denotes the linear pairing between compactly supported distributional differential forms and differential forms.
-\brian{how to say this now}
-The bracket is extended to the entire symmetric algebra by using the graded Leibniz rule.
+
+The Poisson structure is described in a similar way as in the proof of Lemma \ref{lmm:pois1}. 
+We first define the bracket $\{F,G\}$ between the following simple elements $F : \fg \otimes \Omega^\bu (U)[2] \to k$ and $G : k \to \fg \otimes \Omega^\bu_c(U)[2]$. 
+Define $\{F, G\} \in k$ by the composition
+\[
+k \xto{G} \fg \otimes \Omega^\bu_c(U)[2] \hookrightarrow \fg \otimes \Omega^\bu(U)[2] \xto{F} k
+\]
+where the middle arrow uses the obvious inclusion of compactly supported de Rham forms inside of all de Rham forms. 
+Notice that this bracket has cohomological degree $+1$ as desired.
+We extend this to a bracket on the full complex by the graded Leibniz rule.
+
+Next, we define the $\PP_0$-bracket for the value of the factorization algebra on open sets of the form $V \times [0,\epsilon)$. 
+Notice that the underlying graded vector space of $\bC_n(\fg)(V \times [0,\epsilon))$ is of the form
+\[
+{\rm Hom}^\bu\left(\Sym(\fg \otimes \Omega^\bu (V) \otimes \Tilde{\Omega}^\bu ([0,\epsilon))) [1]) \; , \; \Sym \left(\fg \otimes \Omega^\bu_c(V \times [0,\epsilon)) [2] \right) \right)  .
+\]
+We first define the bracket $\{F,G\}$ between the following simple elements 
+\[
+F : \fg \otimes \Omega^\bu(V) \Hat{\otimes} \Tilde{\Omega}^\bu([0,\epsilon)) [2] \to k
+\]
+and 
+\[
+G : k \to \fg \otimes \Omega^\bu_c(V \times [0,\epsilon))[2] .
+\]
+Define $\{F, G\}$ by the composition
+\[
+\begin{tikzcd}
+k \otimes \bigg(\fg \otimes \Omega^\bu(V) \Hat{\otimes} \Tilde{\Omega}^\bu([0,\epsilon)) \bigg) \ar[rdd, dotted, "{\{F,G\}}"'] \ar[r, "G \otimes 1"] & 
+\bigg(\fg \otimes \Omega^\bu_c(V \times [0,\epsilon)) [2]\bigg) \otimes \bigg(\fg \otimes \Omega^\bu(V) \Hat{\otimes} \Tilde{\Omega}^\bu([0,\epsilon)) \bigg) \ar[d,"{[\cdot, \cdot]}"] \\
+& \fg \otimes \Omega^\bu(V) \Hat{\otimes} \Tilde{\Omega}^\bu([0,\epsilon)) [2] \ar[d, "F"] \\ & k
+\end{tikzcd}
+\]
+The middle bracket is induced from the Lie bracket on $\fg$ and the wedge product of differential forms.
+Again, this bracket is extended to the full algebra by the Leibniz rule.
 \end{proof}
@@
 \]
-The map $\int_{\RR_{>0}}$ induces a map of factorization algebras on $M$
-\[
-\int_{\RR_{>0}} : \bC_n(\fg)^\circ \to {\rm Gr} \; \bZ_n (\fg)
+Integration along $\RR_{>0}$ induces a map of factorization algebras on $M$
+\[
+I^{\circ} : \bC_n(\fg)^\circ \to {\rm Gr} \; \bZ_n (\fg)
 \]
 which on linear elements in ${\rm Sym}(\fg \otimes \Omega^\bu_c (V \times \RR_{>0})$ sends $x \otimes \alpha \in \Omega^\bu_c(V \times \RR_{>0})[2]$ to $x \otimes \int_{\RR_{>0}} \alpha \in \Omega^\bu_c (V)[1]$.
-Using the retract $r_\phi$, we see that this is a quasi-isomorphism of factorization algebras on $M$.
-
-Similarly, integration of compactly supported forms along $\RR_{\geq 0}$ determines a quasi-isomorphism of factorization algebras $\int_{\RR_{\geq 0}} : \bC_n(\fg)^\partial \to {\rm Gr} \; \bU_n(\fg)$.
-\brian{I should spell this out now.}
-
-The pair of maps $(\int_{\RR_{>0}} , \int_{\RR_{\geq 0}})$ is a quasi-isomorphism of factorization sc-pairs. 
-An explicit and direct calculation verifies that this quasi-isomorphism respects the Poisson brackets. 
+
+Next, using the map $r_\phi$, define a map of factorization algebras
+\[
+r_\phi^\circ : {\rm Gr} \; \bZ_n (\fg) \to \bC_n(\fg)^\circ
+\]
+as follows. 
+For an open set $V \subset M$, define $r_{\phi}^\circ (V)$ on linear elements $x \otimes \alpha$ in $\Sym(\fg \otimes \Omega^\bu(V)_c[1])$ by
+\[
+r_\phi^\circ (U) (x \otimes \alpha) = x \otimes (\pi^* \alpha \wedge \phi \d t)  .
+\]
+This map can be extended to all of ${\rm Gr} \; \bZ_n(\fg)$ in a similar fashion. 
+One can show that $r_\phi^\circ$ is a deformation retract of $I^\partial$.
+In particular, $I^\partial$ is a quasi-isomorphism of factorization algebras on $M$.
+
+Similarly, integration of compactly supported forms along $\RR_{\geq 0}$ determines a quasi-isomorphism of factorization algebras 
+\[
+I^\partial : \bC_n(\fg)^\partial \to {\rm Gr} \; \bU_n(\fg) .
+\]
+Recall that for $V \subset M$ we have
+\[
+\bC_n(\fg)^\partial (V) = \clies\bigg(\fg \otimes \Omega^\bu(V) \Hat{\otimes} \Tilde{\Omega}^\bu(\RR_{\geq 0})  \; , \; \Sym\left(\fg \otimes \Omega^\bu_c (V \times \RR_{\geq 0})[2] \right) \bigg) .
+\]
+On $V$, the map $I^\partial (V)$ is defined by the composition
+\[
+\begin{tikzcd}
+\clies\bigg(\fg \otimes \Omega^\bu(V) \Hat{\otimes} \Tilde{\Omega}^\bu(\RR_{\geq 0})  \; , \; \Sym\left(\fg \otimes \Omega^\bu_c (V \times \RR_{\geq 0})[2] \right) \bigg) \ar[r, "{{\rm ev}_1}"] & \Sym\left(\fg \otimes \Omega^\bu_c (V \times \RR_{\geq 0})[2] \right) \ar[d, "{\int_{\RR_{\geq 0}}}"] \\ &  \Sym\left(\fg \otimes \Omega^\bu_c (V)[1] \right) .
+\end{tikzcd}
+\]
+The first map ${\rm ev}_1$ evaluates the unit in $\Sym \left(\fg \otimes \Omega^\bu(V) \Hat{\otimes} \Tilde{\Omega}^\bu(\RR_{\geq 0})\right)$ and the second map is induced by integration along $\RR_{\geq 0}$.
+It is immediate to check that $I^{\partial}$ extends to a map of factorization algebras.
+
+For an open set $V$ the cochain map $I^{\partial}(V)$ admits the following explicit retract $r_\phi^\partial(V)$ defined on linear elements $x \otimes \alpha$ in $\Sym (\fg \otimes \Omega^\bu_c(V)[1])$ by the formula
+\[
+r_{\phi}^\partial (x \otimes \alpha) = x \otimes (\pi^* \alpha \wedge \phi \d t) \pm \d_{\rm CE} (x \otimes \pi^* \alpha \phi ) .
+\]
+The map $r_\phi^\partial (V)$ is extended to the entire symmetric algebra in the obvious way.
+
+We have shown that $(I^{\circ}, I^\partial)$ is a quasi-isomorphism of factorization sc-pairs. 
+The compatibility of this quasi-isomorphism with Poisson brackets is a direct calculation. 
 \end{proof}

### 2020-09-10 draft.tex
small edits

@@
 We extend this to a bracket on the full complex by the graded Leibniz rule. 
-
 %Let $x^* \otimes \alpha$ denote an homorphism of the form $\fg \otimes \Omega (U)[1] \to \Sym^0 = k$ and $y \otimes \beta$ denote a homomorphism $k = \Sym^0 \to \fg \otimes \Omega_c(U) [1]$. 
@@
 \]
-The commutative dg algebra structure on $\Tilde{\Omega}^\bu (\RR_{\geq 0})$ is defined by the rule
+The dg commutative algebra structure on $\Tilde{\Omega}^\bu (\RR_{\geq 0})$ is defined by the formula
 \[
@@
 \label{dfn:constructible1}
-Let $\bC_n(\fg)$ be the following constructible factorization algebra on $M \times \RR_{\geq 0}$:
+Let $\bC_n(\fg)$ be the constructible factorization algebra on $M \times \RR_{\geq 0}$ where
 \begin{itemize}
@@
 \[
-\bC_n (\fg) (U) = \clies \bigg(\fg \otimes \Omega^\bu (U) \; , \; \Sym \left(\fg \otimes \Omega^\bu_c(U) [2] \right) \bigg) .
+\bC_n (\fg) (U) = \clies \bigg(\fg \otimes \Omega^\bu (U) \; , \; \Sym \left(\fg \otimes \Omega^\bu_c(U) [2] \right) \bigg), 
 \]
@@
 %\Sym \left( \fg \otimes \Omega^\bu_c(V' \times [0,\epsilon')) [2] \right)
-The first map uses the fact that the symmetric algebra functor is monoidal. 
-The second map is induced from restriction and extension of de Rham forms and compactly supported de Rham forms along the embedding (\ref{eqn:embed}). 
+The first map uses the fact that the symmetric algebra functor is symmetric monoidal. 
+The second map is induced from restriction and extension of de Rham forms and compactly supported de Rham forms along the embedding~(\ref{eqn:embed}). 
 \end{dfn}
@@
 k \otimes \bigg(\fg \otimes \Omega^\bu(V) \Hat{\otimes} \Tilde{\Omega}^\bu([0,\epsilon)) \bigg) \ar[rdd, dotted, "{\{F,G\}}"'] \ar[r, "G \otimes 1"] & 
-\bigg(\fg \otimes \Omega^\bu_c(V \times [0,\epsilon)) [2]\bigg) \otimes \bigg(\fg \otimes \Omega^\bu(V) \Hat{\otimes} \Tilde{\Omega}^\bu([0,\epsilon)) \bigg) \ar[d,"{[\cdot, \cdot]}"] \\
+\bigg(\fg \otimes \Omega^\bu_c(V \times [0,\epsilon)) [2]\bigg) \otimes \bigg(\fg \otimes \Omega^\bu(V) \Hat{\otimes} \Tilde{\Omega}^\bu([0,\epsilon)) \bigg) \ar[d,"{[\cdot, \cdot] \otimes \wedge}"] \\
 & \fg \otimes \Omega^\bu(V) \Hat{\otimes} \Tilde{\Omega}^\bu([0,\epsilon)) [2] \ar[d, "F"] \\ & k
@@
 \[
-\bC_n(\fg)^{\circ} (V) = \clies \bigg(\fg \otimes \Omega (V \otimes \RR_{>0} ) \; , \; \Sym \left(\fg \otimes \Omega_c(V \times \RR_{>0}) [2] \right) \bigg)  .
+\bC_n(\fg)^{\circ} (V) = \clies \bigg(\fg \otimes \Omega (V \times \RR_{>0} ) \; , \; \Sym \left(\fg \otimes \Omega_c(V \times \RR_{>0}) [2] \right) \bigg)  .
 \]
@@
 
-Next, using the map $r_\phi$, define a map of factorization algebras
+Next, using the map $r_\phi$, wedefine a map of factorization algebras
 \[
@@
 The first map ${\rm ev}_1$ evaluates the unit in $\Sym \left(\fg \otimes \Omega^\bu(V) \Hat{\otimes} \Tilde{\Omega}^\bu(\RR_{\geq 0})\right)$ and the second map is induced by integration along $\RR_{\geq 0}$.
-It is immediate to check that $I^{\partial}$ extends to a map of factorization algebras.
+It is quick to check that $I^{\partial}$ extends to a map of factorization algebras.
 
@@
 We have shown that $(I^{\circ}, I^\partial)$ is a quasi-isomorphism of factorization sc-pairs. 
-The compatibility of this quasi-isomorphism with Poisson brackets is a direct calculation. 
+A direct calculation verifies that this quasi-isomorphism respects Poisson brackets. 
 \end{proof}

### 2020-09-10 draft.tex
work on 8.2

@@
 In particular, thanks again to \cite{Knudsen}, 
-we know that the $\EE_n$ enveloping algebra $\UU_n \fg$ admits a model $\bU_n \fg$ whose underlying functor on the poset of open sets in $\RR^n$ assigns $\cliels(\Omega_c^*(V) \otimes \fg)$ to each open set~$V$.
+we know that the enveloping $\EE_n$ algebra $\UU_n \fg$ admits a model $\bU_n \fg$ whose underlying functor on the poset of open sets in $\RR^n$ assigns $\cliels(\Omega_c^*(V) \otimes \fg)$ to each open set~$V$.
 There is another factorization algebra whose underlying assigns $\clies(\Omega^\bu(V) \otimes \fg)$ to each open~$V$.
@@
 \begin{qtn}
-Is there some local version of this relationship?
+Is there a local version of this relationship?
 That is, can we obtain a version of the LQT theorem at the level of $\EE_n$ algebras such that factorization homology recovers the quasi-isomorphism of this lemma?
@@
 
-In this section, we turn to an interpretation of the $\EE_n$ center of an $\EE_n$ enveloping algebra in terms of a certain topological field theory (TFT).
+In this section, we turn to an interpretation of the $\EE_n$ center of an enveloping $\EE_n$ algebra in terms of a certain topological field theory (TFT).
 
 Given an $\EE_n$ algebra $A$, the pair $(\fZ_n (A) , A)$ is an algebra over the $(n+1)$-dimensional Swiss cheese operad. 
-The first objective is to define a certain ``classical limit" of this pair in the case that $A$ is an $\EE_n$ enveloping algebra.
+The first objective is to define a certain ``classical limit" of this pair in the case that $A$ is an enveloping $\EE_n$ algebra.
 
@@
 
-The key insight is that there exists a filtration on our model $\bZ_n(\fg)$ for the $\EE_n$ center and our model $\bU_n (\fg)$ for the $\EE_n$ enveloping algebra  whose associated graded factorization algebras ${\rm Gr} \; \bZ_n(\fg)$ and ${\rm Gr} \; \bU_n(\fg)$ are commutative factorization algebras.
+The key insight is that there exists a filtration on our model $\bZ_n(\fg)$ for the $\EE_n$ center and our model $\bU_n (\fg)$ for the enveloping $\EE_n$ algebra  whose associated graded factorization algebras ${\rm Gr} \; \bZ_n(\fg)$ and ${\rm Gr} \; \bU_n(\fg)$ are commutative factorization algebras.
 
@@
 
-Consider our factorization model for the $\EE_n$ enveloping algebra $\bU_n(\fg) = \cliels (\fg \otimes \Omega^\bu_c)$. 
+Consider our factorization model for the enveloping $\EE_n$ algebra $\bU_n(\fg) = \cliels (\fg \otimes \Omega^\bu_c)$. 
 The filtration on Chevalley--Eilenberg chains equips $\bU_n(\fg)$ with a filtration as a factorization algebra.
@@
 It is given by the sum of the $L_\infty$-operations $\ell_2 + \ell_3 + \cdots$. 
-This implies that ${\rm Gr} \; \bU_n (\fg)$ is a $\PP_0$-factorization algebra.
+This observation implies that ${\rm Gr} \; \bU_n (\fg)$ is a $\PP_0$-factorization algebra.
 
@@
 The pair $(\fZ_n(\fg), \UU_n(\fg))$ is an algebra over the $(n+1)$-dimensional Swiss cheese operad. 
-At the level of the associated graded algebras, we obtain an algebra over a certain classical limit of this operad which takes into account the aforementioned Poisson structures.
-
-The definition of this two-colored operad $\PP_{[n+1,n]}$ can be found in \cite{SafronovCoiso}. 
-A $\PP_{[n+1,n]}$ algebra consists of a pair $(A,B)$ where $A$ is a $\PP_{n+1}$ algebra and $B$ is a $\PP_n$ algebra which receives an action by $A$.
+At the level of the associated graded algebras, 
+we obtain an algebra over a certain classical limit of this operad that takes into account the aforementioned Poisson structures.
+The definition of this two-colored operad $\PP_{[n+1,n]}$ can be found in~\cite{SafronovCoiso}. 
+A {\em $\PP_{[n+1,n]}$ algebra} consists of a pair $(A,B)$ where $A$ is a $\PP_{n+1}$ algebra and $B$ is a $\PP_n$ algebra that receives an action by $A$.
 
 The action of $\bZ_n(\fg)$ on $\bU_n(\fg)$ descends to an action at the level of the associated graded factorization algebras
-Together with Lemma \ref{lmm:pois1}, we obtain Proposition \ref{prp:poisson}.
+Together with Lemma~\ref{lmm:pois1}, we obtain Proposition~\ref{prp:poisson}.
 
@@
 
-We turn towards a model for the $\EE_n$-center as a constructible factorization algebra on an $(n+1)$-manifold with boundary.
+We turn towards a model for the $\EE_n$ center as a constructible factorization algebra on an $(n+1)$-manifold with boundary.
 
@@
 \]
-This is our model for restriction $\iota^*$ of de Rham forms that is used in the definition above.
+This composition provides the version of restriction $\iota^*$ of de Rham forms used in the definition above.
 \end{rmk}
@@
 \begin{proof}[Proof of Proposition \ref{prp:pair}]
-To exhibit this quasi-isomorphism, we introduce the following cochain maps.
+To exhibit the desired quasi-isomorphism, 
+we first construct a map of factorization algebras and then provide a retract that shows it is a quasi-isomorphism.
+
+We will use the following cochain maps in our constructions.
 For an open set $V \subset M$ let
 \[
-\int_{\RR_{>0}} : \Omega_c(V \times \RR_{>0}) \to \Omega_c (U) [1] 
+\int_{\RR_{>0}} : \Omega^*_c(V \times \RR_{>0}) \to \Omega^*_c (U) [1] 
 \] 
@@
 \[
-r_\phi : \Omega_c(U) [1] \to \Omega_c (U \times \RR_{\geq 0})
+r_\phi : \Omega^*_c(U) [1] \to \Omega^*_c (U \times \RR_{\geq 0})
 \]
@@
 \[
-\bC_n(\fg)^{\circ} (V) = \clies \bigg(\fg \otimes \Omega (V \times \RR_{>0} ) \; , \; \Sym \left(\fg \otimes \Omega_c(V \times \RR_{>0}) [2] \right) \bigg)  .
+\bC_n(\fg)^{\circ} (V) = \clies \bigg(\fg \otimes \Omega^* (V \times \RR_{>0} ) \; , \; \Sym \left(\fg \otimes \Omega^*_c(V \times \RR_{>0}) [2] \right) \bigg)  .
 \]
@@
 \]
-which on linear elements in ${\rm Sym}(\fg \otimes \Omega^\bu_c (V \times \RR_{>0})$ sends $x \otimes \alpha \in \Omega^\bu_c(V \times \RR_{>0})[2]$ to $x \otimes \int_{\RR_{>0}} \alpha \in \Omega^\bu_c (V)[1]$.
-
-Next, using the map $r_\phi$, wedefine a map of factorization algebras
+that on linear elements in ${\rm Sym}(\fg \otimes \Omega^\bu_c (V \times \RR_{>0}))$ sends $x \otimes \alpha \in \fg \otimes \Omega^\bu_c(V \times \RR_{>0})[2]$ to $x \otimes \int_{\RR_{>0}} \alpha \in \fg \otimes \Omega^\bu_c (V)[1]$.
+
+Next, using the map $r_\phi$, we define a map of factorization algebras
 \[
@@
 This map can be extended to all of ${\rm Gr} \; \bZ_n(\fg)$ in a similar fashion. 
-One can show that $r_\phi^\circ$ is a deformation retract of $I^\partial$.
-In particular, $I^\partial$ is a quasi-isomorphism of factorization algebras on $M$.
-
-Similarly, integration of compactly supported forms along $\RR_{\geq 0}$ determines a quasi-isomorphism of factorization algebras 
+A quick computation shows that $r_\phi^\circ$ is a deformation retract of $I^\circ$.
+In consequence, $I^\circ$ is a quasi-isomorphism of factorization algebras on~$M$.
+
+Similarly, we now use integration of compactly supported forms along $\RR_{\geq 0}$ to produce  a quasi-isomorphism of factorization algebras 
 \[
@@
 \]
+We begin by constructing this map and then provide a retract that shows it is a quasi-isomorphism.
+
 Recall that for $V \subset M$ we have

### 2020-09-10 draft.tex
good

@@
 
-For an open set $V$ the cochain map $I^{\partial}(V)$ admits the following explicit retract $r_\phi^\partial(V)$ defined on linear elements $x \otimes \alpha$ in $\Sym (\fg \otimes \Omega^\bu_c(V)[1])$ by the formula
+For an open set $V$ the cochain map $I^{\partial}(V)$ admits an explicit retract $r_\phi^\partial(V)$ defined on linear elements $x \otimes \alpha$ in $\Sym (\fg \otimes \Omega^\bu_c(V)[1])$ by the formula
 \[

### 2020-09-10 draft.tex
reminder on what to add to spectral sequence section
cleaning up proof

@@
 
-We will use the following cochain maps in our constructions.
-For an open set $V \subset M$ let
-\[
-\int_{\RR_{>0}} : \Omega^*_c(V \times \RR_{>0}) \to \Omega^*_c (U) [1] 
-\] 
-be the map which integrates a compactly supported form on $U \times \RR_{> 0}$ along $\RR_{> 0}$. 
+We will use the following cochain maps defined at the level of differential forms in our constructions.
+For an open set $V \subset M$ let $\int_{\RR_{>0}}$
+(or $\int_{\RR_{\geq 0}}$)
+be the map which integrates a compactly supported form on $V \times \RR_{> 0}$ or ($V \times \RR_{\geq 0}$) along $\RR_{> 0}$ (or $\RR_{\geq 0}$).
 This map is a quasi-isomorphism for any $U$ and, in fact, admits the following explicit retract. 
-Let $\phi$ be a fixed compactly supported function on $\RR$ of mass $1$ and define
+Let $\phi$ be a fixed compactly supported function on $\RR_{\geq 0}$ of mass $1$ and define
 \[
@@
 \]
-by $r_\phi (\alpha) = \alpha \wedge \phi \, \d t$.
+by $r_\phi (\alpha) = \pi^*\alpha \wedge \phi \, \d t$.
 
@@
 \]
-that on linear elements in ${\rm Sym}(\fg \otimes \Omega^\bu_c (V \times \RR_{>0}))$ sends $x \otimes \alpha \in \fg \otimes \Omega^\bu_c(V \times \RR_{>0})[2]$ to $x \otimes \int_{\RR_{>0}} \alpha \in \fg \otimes \Omega^\bu_c (V)[1]$.
+which is defined on basic elements as follows.
+On linear elements of the form $G : k \to \fg \otimes \Omega^\bu_c (V \times \RR_{>0})[2]$ the element $I^\circ(G)$ is given by the composition
+\[
+k \xto{G} \fg \otimes \Omega^\bu_c (V \times \RR_{>0})[2] \xto{1 \otimes \int_{\RR_{> 0}}} \fg \otimes \Omega^\bu_c(V) [1] .
+\]
+On linear elements of the form $F : \fg \otimes \Omega^\bu(V \times \RR_{>0})[1] \to k$ the element $I^{\circ} (F)$ is the composition
+\[
+\fg \otimes \Omega^\bu(V) [1] \xto{\pi^*} \fg \otimes \Omega^\bu(V \times \RR_{>0}) [1] \xto{F} k  .
+\]
 
@@
 as follows. 
-For an open set $V \subset M$, define $r_{\phi}^\circ (V)$ on linear elements $x \otimes \alpha$ in $\Sym(\fg \otimes \Omega^\bu(V)_c[1])$ by
-\[
-r_\phi^\circ (U) (x \otimes \alpha) = x \otimes (\pi^* \alpha \wedge \phi \d t)  .
-\]
-This map can be extended to all of ${\rm Gr} \; \bZ_n(\fg)$ in a similar fashion. 
+For an open set $V \subset M$, it is defined on basic elements as follows.
+On linear elements $G : k \to \fg \otimes \Omega^\bu(V)_c[1]$ the element $r_\phi^\circ (G)$ is defined by
+\[
+k \xto{G} \fg \otimes \Omega^\bu(V)_c[1] \xto{1 \otimes r_\phi} \fg \otimes \Omega^\bu_c (V \times \RR_{>0}) [2]  .
+\]
+On linear elements $F : \fg \otimes \Omega^\bu(V)[1] \to k$ the element $r_\phi^\circ (F)$ is defined by
+\[
+\fg \otimes \Omega^\bu (V \times \RR_{>0}) [1] \xto{1 \otimes \int_{\RR_{>0}} (-) \wedge \phi \d t} \fg \otimes \Omega^\bu(V) [1] \xto{F} k .
+\]
+
 A quick computation shows that $r_\phi^\circ$ is a deformation retract of $I^\circ$.
@@
 \]
-On $V$, the map $I^\partial (V)$ is defined by the composition
+On $V$, the map $I^\partial$ is defined by the composition
 \[
@@
 
-For an open set $V$ the cochain map $I^{\partial}(V)$ admits an explicit retract $r_\phi^\partial(V)$ defined on linear elements $x \otimes \alpha$ in $\Sym (\fg \otimes \Omega^\bu_c(V)[1])$ by the formula
+On an open set $V$ the cochain map $I^{\partial}$ admits an explicit retract $r_\phi^\partial$ defined on linear elements $x \otimes \alpha$ in $\Sym (\fg \otimes \Omega^\bu_c(V)[1])$ by the formula
 \[
@@
 \]
-The map $r_\phi^\partial (V)$ is extended to the entire symmetric algebra in the obvious way.
-
-We have shown that $(I^{\circ}, I^\partial)$ is a quasi-isomorphism of factorization sc-pairs. 
+The map $r_\phi^\partial$ is extended to the entire symmetric algebra in the obvious way. 
+It is a more involved, yet straightforward, computation to see that $r^\partial_\phi$ is a deformation retract, as factorization algebras, of $I^\partial$.
+
+In conclusion, $(I^{\circ}, I^\partial)$ is a quasi-isomorphism of factorization sc-pairs. 
 A direct calculation verifies that this quasi-isomorphism respects Poisson brackets. 
@@
 \end{prp}
+
+\owen{We should "compute" the left hand side, borrowing from the GRW paper.}
 

### 2020-09-10 draft.tex
checking closed string paragraph
bullets

@@
 \item[(1)] the (underived) center of $U\sl_{N+1}$ is isomorphic to $(\Sym(\CC^{N}))^{S_N}$, where $\CC^{N}$ denotes the Cartan subalgebra of $\sl_{N+1}$ and $S_N$ is the Weyl group of $SL_{N+1}$, and
-\item[(2)] the derived center of the enveloping algebra $U\fg$ is given by derived invariants of the adjoint action of $\fg$ on $U\fg$. That is to say $\Hoch^*(U\fg,U\fg) \simeq \clies(\fg, U\fg)$.
+\item[(2)] the derived center of the enveloping algebra $U\fg$ is given by derived invariants of the adjoint action of $\fg$ on $U\fg$. That is to say $\Hoch^\bu(U\fg,U\fg) \simeq \clies(\fg, U\fg)$.
 \end{enumerate}
@@
 In particular, thanks again to \cite{Knudsen}, 
-we know that the enveloping $\EE_n$ algebra $\UU_n \fg$ admits a model $\bU_n \fg$ whose underlying functor on the poset of open sets in $\RR^n$ assigns $\cliels(\Omega_c^*(V) \otimes \fg)$ to each open set~$V$.
+we know that the enveloping $\EE_n$ algebra $\UU_n \fg$ admits a model $\bU_n \fg$ whose underlying functor on the poset of open sets in $\RR^n$ assigns $\cliels(\Omega_c^\bu(V) \otimes \fg)$ to each open set~$V$.
 There is another factorization algebra whose underlying assigns $\clies(\Omega^\bu(V) \otimes \fg)$ to each open~$V$.
@@
 \begin{enumerate}
-\item Let ${\bf f}: \cliels(\Omega_c^* \otimes \fg) \to \cliels(\Omega_c^* \otimes \fh)$ denote a map of factorization algebras that models with map $\UU_n f$ between enveloping algebras. 
-We use it to produce an explicit factorization algebra $\clies(\Omega \otimes \fg, \cliels(\Omega_c^* \otimes \fh)_f)$ as a kind of ``convolution factorization algebra.'' 
+\item Let ${\bf f}: \cliels(\Omega_c^\bu \otimes \fg) \to \cliels(\Omega_c^\bu \otimes \fh)$ denote a map of factorization algebras that models with map $\UU_n f$ between enveloping algebras. 
+We use it to produce an explicit factorization algebra $\clies(\Omega \otimes \fg, \cliels(\Omega_c^\bu \otimes \fh)_f)$ as a kind of ``convolution factorization algebra.'' 
 \item We show this object fits canonically into a centralizer diagram: there is a map of factorization algebras
 \[
-\clies(\Omega \otimes \fg, \cliels(\Omega_c^* \otimes \fh)_f) \otimes \bU_n \fg \to \cliels(\Omega_c^* \otimes \fh)
+\clies(\Omega \otimes \fg, \cliels(\Omega_c^\bu \otimes \fh)_f) \otimes \bU_n \fg \to \cliels(\Omega_c^\bu \otimes \fh)
 \]
@@
 \[
-\clies(\Omega \otimes \fg, \cliels(\Omega_c^* \otimes \fh)_f) \to \bZ_n({\bf f})
+\clies(\Omega \otimes \fg, \cliels(\Omega_c^\bu \otimes \fh)_f) \to \bZ_n({\bf f})
 \]
@@
 
-This result generalizes the fact that $\Hoch^*(U\fg,U\fg) \simeq \clies(\fg, U\fg)$, 
+This result generalizes the fact that $\Hoch^\bu(U\fg,U\fg) \simeq \clies(\fg, U\fg)$, 
 since the associative algebra $U\fg$ is modeled by the locally constant one-dimensional factorization algebra that assigns
@@
 
-When $n=1$ and $\cC$ is chain complexes over the field $k$, then $\Mod^{E_1}_A(\cC)$ is equivalent to $A\otimes A^{op}$-modules and hence ${\frak Z}_{E_1}(f) \simeq {\rm Hoch}^*(A,B_f)$,
+When $n=1$ and $\cC$ is chain complexes over the field $k$, then $\Mod^{E_1}_A(\cC)$ is equivalent to $A\otimes A^{op}$-modules and hence ${\frak Z}_{E_1}(f) \simeq {\rm Hoch}^\bu(A,B_f)$,
 where $B_f$ denotes $B$ viewed as an $A\otimes A^{op}$-modules via the map~$f$.
@@
 &\simeq \cliels(\Omega^\bu_c(\RR_{> 0} \times S^{n-1}) \otimes \fg)\\
-&\simeq \cliels(\Omega^\bu_c(\RR_{> 0}) \otimes H^*(S^{n-1}) \otimes \fg)
+&\simeq \cliels(\Omega^\bu_c(\RR_{> 0}) \otimes H^\bu(S^{n-1}) \otimes \fg)
 \end{align*}
@@
 \[
-\int_{S^{n-1}}\UU_n\fg \simeq \UU_1 (H^*(S^{n-1}) \otimes \fg)
+\int_{S^{n-1}}\UU_n\fg \simeq \UU_1 (H^\bu(S^{n-1}) \otimes \fg)
 \]
@@
 where $|\epsilon_{n-1}| = n-1$.
-Since $\UU_1 (H^*(S^{n-1}) \otimes \fg)$ is manifestly equivalent to the dg algebra~$U(\fg \otimes R_n)$,
+Since $\UU_1 (H^\bu(S^{n-1}) \otimes \fg)$ is manifestly equivalent to the dg algebra~$U(\fg \otimes R_n)$,
 we find that 
@@
 \[
-\Omega_c^*(V) \otimes \Omega^\bu(S) \to \Omega_c^*(V \times S),
+\Omega_c^\bu(V) \otimes \Omega^\bu(S) \to \Omega_c^\bu(V \times S),
 \]
@@
 \Omega^\bu(V) \otimes \fg_S &\xto{\simeq} \Omega^\bu(V \times S) \otimes \fg \\
-\Omega_c^*(V) \otimes \fg_S &\xto{\simeq} \Omega_c^*(V \times S) \otimes \fg 
+\Omega_c^\bu(V) \otimes \fg_S &\xto{\simeq} \Omega_c^\bu(V \times S) \otimes \fg 
 \end{align*}
@@
 \[
-\Hoch^*(U\fg,U\fg) \simeq \clies(\fg, U\fg^{ad}).
+\Hoch^\bu(U\fg,U\fg) \simeq \clies(\fg, U\fg^{ad}).
 \] 
@@
 
-Let $\Cyc_*(A)$ denote the {\em cyclic chains} of a dg associative algebra~$A$.
+Let $\Cyc_\bu(A)$ denote the {\em cyclic chains} of a dg associative algebra~$A$.
 A key theorem --- one of the original motivations for cyclic homology --- is the Loday-Quillen-Tsygan (LQT) theorem \cite{},
@@
 \label{eqn: LQT}
-\cliels(\fgl_\infty(A)) \xto{\simeq} \Sym(\Cyc_*(A)[1])
+\cliels(\fgl_\infty(A)) \xto{\simeq} \Sym(\Cyc_\bu(A)[1])
 \end{equation}
@@
 \label{eqn: LQT}
-\cliels({\frak{so}}_\infty(A)) \xto{\simeq} \Sym(\Dih_*(A)[1]),
-\]
-with $\Dih_*$ denoting the dihedral chains.
+\cliels({\frak{so}}_\infty(A)) \xto{\simeq} \Sym(\Dih_\bu(A)[1]),
+\]
+with $\Dih_\bu$ denoting the dihedral chains.
 Note that one can use either $\frak{so}_N$ or $\frak{sp}_N$ on the left hand side.
@@
 \[
-\Cyc_*(\Omega^*(M)) \simeq \Omega^*(LM/^h S^1)
+\Cyc_\bu(\Omega^\bu(M)) \simeq \Omega^\bu(LM/^h S^1)
 \]
@@
 \int_M \UU_n(\frak{gl}_\infty)
-&\simeq \cliels(\Omega^*(M) \otimes \fgl_\infty) \\
-&\simeq \Sym(\Cyc_*(\Omega^*(M))[1]) \\
-&\simeq \Sym(\Omega^*(LM/^h S^1))[1])).
+&\simeq \cliels(\Omega^\bu(M) \otimes \fgl_\infty) \\
+&\simeq \Sym(\Cyc_\bu(\Omega^\bu(M))[1]) \\
+&\simeq \Sym(\Omega^\bu(LM/^h S^1))[1])).
 \end{align*}
@@
 Indeed, those familiar with closed string field theory will recognize the right hand side as related to the ``Fock space'' of such a theory.
-\owen{Check me, Bri-guy.}
 
@@
 \[
-\clies(\fgl_\infty \otimes \Omega^\bu(M), \cliels(\fgl_\infty \otimes \Omega^\bu(M)) \simeq \End^\bullet(\Sym(\Omega^*(LM/^h S^1))[1])))
+\clies(\fgl_\infty \otimes \Omega^\bu(M), \cliels(\fgl_\infty \otimes \Omega^\bu(M)) \simeq \End^\bullet(\Sym(\Omega^\bu(LM/^h S^1))[1])))
 \]
@@
 \[
-r_\phi : \Omega^*_c(U) [1] \to \Omega^*_c (U \times \RR_{\geq 0})
+r_\phi : \Omega^\bu_c(U) [1] \to \Omega^\bu_c (U \times \RR_{\geq 0})
 \]
@@
 \[
-\bC_n(\fg)^{\circ} (V) = \clies \bigg(\fg \otimes \Omega^* (V \times \RR_{>0} ) \; , \; \Sym \left(\fg \otimes \Omega^*_c(V \times \RR_{>0}) [2] \right) \bigg)  .
+\bC_n(\fg)^{\circ} (V) = \clies \bigg(\fg \otimes \Omega^\bu (V \times \RR_{>0} ) \; , \; \Sym \left(\fg \otimes \Omega^\bu_c(V \times \RR_{>0}) [2] \right) \bigg)  .
 \]
@@
 let $f\otimes X  $ be an 
-element in $\cliels\big(\fg \otimes \Omega^\bu , B\big) \otimes \cliels\big(\fg \otimes \Omega_c^* \big)$.  
+element in $\cliels\big(\fg \otimes \Omega^\bu , B\big) \otimes \cliels\big(\fg \otimes \Omega_c^\bu \big)$.  
 Let
@@
 
-Recall that we have a factorization algebra map~\eqref{eq:DefofFonFaclevel}  $\mathbf{f}: \cliels(\fg \otimes \Omega_c^* \to B$.
+Recall that we have a factorization algebra map~\eqref{eq:DefofFonFaclevel}  $\mathbf{f}: \cliels(\fg \otimes \Omega_c^\bu \to B$.
 The unital factorization algebra is given, for any open $U$, by $k(U)=k$.
@@
  \stackrel{\id \otimes ev}\longrightarrow Sym^{n-p}\big(\fg \otimes \Omega^\bu_c(U)\big) \otimes B(U)  \hookrightarrow
- \cliels\big(\fg \otimes \Omega_c^*(U), B(U) \big) 
+ \cliels\big(\fg \otimes \Omega_c^\bu(U), B(U) \big) 
 \end{multline}

### 2020-09-10 draft.tex
fields

@@
 \item[(2)] 
-To an open set $V \times [0,\epsilon)$, we assign the (abelian) $L_\infty$ algebra
-\[
-\cL (V \times [0,\epsilon)) = \Omega^{\bu} (V \times [0,\epsilon)) \otimes \fg^* [n-3] .
+To an open set $V \times [0,\epsilon)$, we assign the $L_\infty$ algebra
+\[
+\cL (V \times [0,\epsilon)) = \Omega^\bu (V) \Hat{\otimes} \Tilde{\Omega}^\bu([0,\epsilon)) \otimes \fg \ltimes \Omega^{\bu} (V \times [0,\epsilon)) \otimes \fg^* [n-3] .
 \]
@@
 \begin{prp}
-There is a quasi-isomorphism of constructible factorization algebras on $M \times \RR_{\geq 0}$:
+There is a quasi-isomorphism of constructible $\PP_0$-factorization algebras on $M \times \RR_{\geq 0}$:
 \[

### 2020-09-14 draft.tex
tiny tweaks

@@
 \item Let ${\bf f}: \cliels(\Omega_c^\bu \otimes \fg) \to \cliels(\Omega_c^\bu \otimes \fh)$ denote a map of factorization algebras that models with map $\UU_n f$ between enveloping algebras. 
-We use it to produce an explicit factorization algebra $\clies(\Omega \otimes \fg, \cliels(\Omega_c^\bu \otimes \fh)_f)$ as a kind of ``convolution factorization algebra.'' 
+We use it to produce an explicit factorization algebra $\clies(\Omega^\bu \otimes \fg, \cliels(\Omega_c^\bu \otimes \fh)_f)$ as a kind of ``convolution factorization algebra.'' 
 \item We show this object fits canonically into a centralizer diagram: there is a map of factorization algebras
@@
 \end{cor}
-
-\owen{Some easy but important situations to examine:}
-\begin{itemize}
-\item When $n=0$, we see naive endomorphisms arise.
-\item When $n=1$, we recover standard Koszul duality and Hochschild cohomology examples.
-\item When $n=1$, unpack in detail how the convolution picture matches the classic view of Koszul duality for associative (co)algebras.
-\item Consider $\fg$ {\em abelian} for arbitrary $n$ and compare to the $\EE_n$ HKR theorem.
-\item Compare with $\EE_n$ HKR theorem for $\clies(\fg)$ via $\EE_n$ Koszul duality.
-\item Use these facts to compute factorization homology of centralizers on manifolds with boundary --- kind of like Chern-Simons states!
-\end{itemize}
+%
+%\owen{Some easy but important situations to examine:}
+%\begin{itemize}
+%\item When $n=0$, we see naive endomorphisms arise.
+%\item When $n=1$, we recover standard Koszul duality and Hochschild cohomology examples.
+%\item When $n=1$, unpack in detail how the convolution picture matches the classic view of Koszul duality for associative (co)algebras.
+%\item Consider $\fg$ {\em abelian} for arbitrary $n$ and compare to the $\EE_n$ HKR theorem.
+%\item Compare with $\EE_n$ HKR theorem for $\clies(\fg)$ via $\EE_n$ Koszul duality.
+%\item Use these facts to compute factorization homology of centralizers on manifolds with boundary --- kind of like Chern-Simons states!
+%\end{itemize}
 
@@
 
+\owen{I think the usual Chevalley theorem only applies when $1-n$ is an even integer. I'm not sure if or what the theorem is when $1-n$ is odd.}
+
 \brian{Is there an explicit description of the $\EE_{n+1}$-structure for the RHS?}
@@
 \end{proof}
-
-\owen{I think the usual Chevalley theorem only applies when $1-n$ is an even integer. I'm not sure what the theorem is called when $1-n$ is odd.}
 

### 2020-09-22 draft.tex
merge

--- 2020-09-10 draft.tex
@@
 \begin{proof}
-\brian{we should just cite our paper with Eugene for this, with a few comments about what changes}
-Suppose $V \times [0,\epsilon) \subset M \times \RR_{\geq 0}$ is an open set. 
-Then, as cochain complexes 
-\[
-\clie^\bu(\cL(V \times [0,\epsilon)) = {\rm Sym} \left(\Bar{\Omega}^\bu_c(V \times [0,\epsilon) [2] \right)  .
-\]
-Here $\Bar{\Omega}^\bu_c$ denotes the compactly supported distributional de Rham forms. 
-By ellipticity, the inclusion $\Omega^\bu \hookrightarrow \Bar{\Omega}^\bu_c$ is a quasi-isomorphism which induces a quasi-isomorphism
-\[
-\bC_n(\fg) (V \times [0,\epsilon)) \hookrightarrow \clie^\bu(\cL(V \times [0,\epsilon)) 
-\]
-as desired. 
-The quasi-isomorphism for the value of the factorization algebras on open sets $U \subset M \times \RR_{>0}$ is defined similarly. 
+\brian{all we need to say is that half-smeared is equivalent to full observables}
+
+%Suppose $V \times [0,\epsilon) \subset M \times \RR_{\geq 0}$ is an open set. 
+%Then, as cochain complexes 
+%\[
+%\clie^\bu(\cL(V \times [0,\epsilon)) = {\rm Sym} \left(\Bar{\Omega}^\bu_c(V \times [0,\epsilon) [2] \right)  .
+%\]
+%Here $\Bar{\Omega}^\bu_c$ denotes the compactly supported distributional de Rham forms. 
+%By ellipticity, the inclusion $\Omega^\bu \hookrightarrow \Bar{\Omega}^\bu_c$ is a quasi-isomorphism which induces a quasi-isomorphism
+%\[
+%\bC_n(\fg) (V \times [0,\epsilon)) \hookrightarrow \clie^\bu(\cL(V \times [0,\epsilon)) 
+%\]
+%as desired. 
+%The quasi-isomorphism for the value of the factorization algebras on open sets $U \subset M \times \RR_{>0}$ is defined similarly. 
 \end{proof}

### 2020-09-25 draft.tex
not sure what i did

--- 2020-09-14 draft.tex
@@
 augmented associative algebra {\em on the nose} in the 1-category of factorization algebras on~$\RR^n$,
-and it models the center ${\frak Z}_n(\fg)$ as an $E_1$ algebra in $\EE_n$ algebras.
+and it models the center ${\frak Z}_n(\fg)$ as an $\EE_1$ algebra in $\EE_n$ algebras.
 \end{enumerate}
@@
 \int_M \UU_n(\frak{gl}_\infty)
-&\simeq \cliels(\Omega^\bu(M) \otimes \fgl_\infty) \\
+&\simeq \cliels(\fgl_\infty(\Omega^\bu(M) )) \\
 &\simeq \Sym(\Cyc_\bu(\Omega^\bu(M))[1]) \\
@@
 \[
-\clies(\fgl_\infty \otimes \Omega^\bu(M), \cliels(\fgl_\infty \otimes \Omega^\bu(M)) \simeq \End^\bullet(\Sym(\Omega^\bu(LM/^h S^1))[1])))
+\clies(\fgl_\infty(\Omega^\bu(M)), \cliels(\fgl_\infty (\Omega^\bu(M))) \simeq \End^\bullet(\Sym(\Omega^\bu(LM/^h S^1))[1])))
 \]

### 2020-09-28 draft.tex
harish chandra

--- 2020-09-22 draft.tex
@@
 
-\subsection{Reductive Lie algebras and a generalized Harish-Chandra homomorphism}
+\subsection{A generalized Harish-Chandra isomorphism}
 
@@
 
-The following result generalizes the Harish--Chandra isomorphism to the $\EE_n$ center of the  enveloping $\EE_n$ algebra.
+Using our models, we obtain a generalization of the Harish--Chandra isomorphism to the $\EE_n$ center of the  enveloping $\EE_n$ algebra. 
+The following result follows from a simple application of the Poincar\'{e} lemma for de Rham forms and compactly supported de Rham forms.
 
 \begin{prp}
-For $\fg$ a reductive \owen{semisimple?} Lie algebra with Cartan subalgebra~$\fh$ and Weyl group~$W$, 
-there is a quasi-isomorphism of $\EE_{n+1}$ algebras
+There is a canonical quasi-isomorphism of $\EE_{n+1}$-algebras
+\[
+\bZ_n(\UU_n \fg) \xto{\simeq} \clies\left(\fg, \Sym(\fg[1-n]) \right) .
+\]
+\end{prp}
+
+In the case that $\fg$ is semi-simple, there is the following modest refinement of the result. 
+To state it, we set up some notation. 
+Since $\fg$ is reductive, the $\fg$-invariants of the exterior algebra $\Sym(\fg[1])^\fg = \left(\oplus_{k \geq 0} \wedge^k \fg[k]\right)^\fg$ is isomorphic to the Lie algebra homology $H^{\rm Lie}_\bu(\fg)$ \cite{Cartan}.
+Similarly, if $2\ell+1$ is an odd integer, then the $\fg$ invariants of $\Sym(\fg[k])^\fg = \oplus_{k \geq 0} \wedge^k \fg[2 \ell k + k]$ is isomorphic to the regraded Lie algebra homology $\Tilde{H}_\bu^{\rm Lie} (\fg, \ell)$
+which in degrees $-2\ell k - k$, $k \in \ZZ$ is $H_{k}^{\rm Lie}(\fg)$ and zero in all other degrees.
+
+\begin{prp}
+For $\fg$ a semi-simple Lie algebra with Cartan subalgebra~$\fh$ and Weyl group~$W$, we have the following:
+\begin{itemize}
+\item if $n$ is odd, then there is a quasi-isomorphism of $\EE_{n+1}$-algebras
 \[
@@
 \]
+\item if $n$ is even, then there is a quasi-isomorphism of $\EE_{n+1}$-algebras
+\[
+{\frak Z}_n(\UU_n \fg) \simeq \clies (\fg) \otimes \Tilde{H}_\bu^{\rm Lie} \left(\fg, \frac{n}{2} -1\right).
+\]
+\end{itemize}
 \end{prp}
-
-\owen{I think the usual Chevalley theorem only applies when $1-n$ is an even integer. I'm not sure if or what the theorem is when $1-n$ is odd.}
-
-\brian{Is there an explicit description of the $\EE_{n+1}$-structure for the RHS?}
-\brian{Is the RHS formal, can we replace by Lie algebra cohomology.}
-
 \begin{proof}
@@
 \]
-Since $\fg$ is reductive, there is a quasi-isomorphism \brian{do we actually need semisimple here?}
+Since $\fg$ is semi-simple, there is a quasi-isomorphism
 \[
@@
 where $G$ is a compact connected Lie group whose Lie algebra is $\fg$.
-Further, by the Chevalley restriction theorem one has 
+
+Now, when $n$ is odd, we apply the Chevalley restriction theorem to obtain an isomorphism of graded vector spaces
 \[
@@
 \]
+
+Similarly, when $n$ is even, we apply the discussion in the paragraph preceding the statement of this proposition 
 \end{proof}

### 2020-09-28 draft.tex
small changes in HKR section

@@
 (The classic theorem proves the $n=1$ situation.)
-Such a result is proved by very different methods in~\cite{CalWil}.
+Such a result is proved by very different methods in~\cite{CalWil, ToenBranes}.
 Now we swiftly describe how to use methods like those in this paper to prove a version of this powerful result.
 
-Our approach applies only to a certain class of dg commutative algebras,
-due to a technical hypothesis necessary to apply our methods.
-We need as input an augmented dg commutative algebra $\epsilon: A \to k$ that admits a semifree resolution of the form $(\Sym(V^\vee), \partial)$, where $V$ is some graded vector space.
-In other words, we want to know that the generators can be realized as the graded linear dual of some other graded vector space.
-We say such an $A$ is of {\em type~($\star$)}.
+\owen{Greg, please read this below.}
+First, we wish to define ${\rm Poly}_n(A)$ for an arbitrary dg commutative algebra $A$ in a way that gives the ``correct'' derived answer, i.e., the answer up to quasi-isomorphism of dg commutative algebras.
+Concretely, one should replace $A$ by a quasi-isomorphic but better behaved algebra $\widetilde{A}$, 
+such as semi-free resolution or cofibrant replacement with respect to some nice model category structure.
+Then one computes the tangent complex $\TT_{\widetilde{A}}$, i.e., the derived derivations.
+The {\em shifted polyvector fields} of $A$ means
+\[
+{\rm Poly}_n(A) \simeq \Sym_{\widetilde{A}} (\TT_{\widetilde{A}}[1-n]),
+\]
+which is again a dg commutative algebra up to quasi-isomorphism.
+
+Second, we introduce a technical hypothesis  needed to apply our methods.
+We need an {\em augmented} dg commutative algebra $\epsilon: A \to k$ that admits a semifree resolution of the form $(\Sym(V^\vee), \partial)$, where $V$ is some graded vector space.
+In other words, we need that the generators can be realized as the graded linear dual of some other graded vector space.
+We say such an algebra $A$ is of {\em type~($\star$)}.
 
@@
 \[
-{\frak Z}_n(A) \simeq {\rm Poly}_n(A) \simeq \Sym_A(\TT_A[-n]).
+{\frak Z}_n(A) \simeq {\rm Poly}_n(A).
 \]
@@
 
-\owen{This proposition should be phrased correctly. The RHS isn't quite correct unless $A$ is good enough.}
-
 \begin{proof}
-\owen{The method described in the email.}
+By our technical hypothesis, we are free to replace $A$ by a semifree resolution $(\Sym(V^\vee), \partial)$. 
+Ignoring the differential, we see that our situation resembles our central result for an abelian Lie algebra,
+and so we now mimic the proof of our central result.
+
+There is a natural homotopy-locally constant sheaf of cochain complexes $\Omega^* \otimes V$ with differential $\d_{dR} + \partial$,
+which is a soft replacement for the locally constant sheaf $V$.
+Define the factorization algebra 
+\[
+F_A = (\Sym((\Omega* \otimes V)* ), \d_{dR} + \partial) 
+\]
+which is manifestly commutative and is quasi-isomorphic to $A$ on every disk.
+Hence $F_A$ is a commutative, locally constant factorization algebra that models~$A$.
+
+\owen{I'm partway done.}
+
+3) Define the putative center as a factorization algebra by starting with the polyvector fields for this semifree resolution
+
+4) Show this putative center fits into the commuting triangle and hence possesses a canonical map to the "true" center
+
+5) Use the Francis-Lurie recognition principle to show this map is a quasi-iso
 \end{proof}
@@
 
-Let $\fg_S$ denote the $L_\infty$ algebra $\Omega^\bu(S) \otimes \fg$. 
+Let $\fg^S$ denote the $L_\infty$ algebra $\Omega^\bu(S) \otimes \fg$. 
 Then these quasi-isomorphisms above imply there are quasi-isomorphisms of $L_\infty$ algebras
 \begin{align*}
-\Omega^\bu(V) \otimes \fg_S &\xto{\simeq} \Omega^\bu(V \times S) \otimes \fg \\
-\Omega_c^\bu(V) \otimes \fg_S &\xto{\simeq} \Omega_c^\bu(V \times S) \otimes \fg 
+\Omega^\bu(V) \otimes \fg^S &\xto{\simeq} \Omega^\bu(V \times S) \otimes \fg \\
+\Omega_c^\bu(V) \otimes \fg^S &\xto{\simeq} \Omega_c^\bu(V \times S) \otimes \fg 
 \end{align*}
@@
 \[
-\bU_k \fg_S \xto{\simeq} \int_S \bU_n \fg
+\bU_k \left(\fg^S\right) \xto{\simeq} \int_S \bU_n \fg
 \]
@@
 
+\owen{The following does not make sense. An injective quasi-isomorphism of dg vector spaces does not induce a map of endomorphisms on the nose. But they are canonically quasi-isomorphic by a zigzag.}
 Likewise, on each open set $V \subset \RR^k$, 
@@
 \[
-\bZ_k(\fg_S)(V) \cong \clies( \Omega^\bu(V) \otimes \fg_S, \bU_k \fg_S) \xto{\simeq} \clies(\Omega^\bu(V \times S) \otimes \fg, \bU_n(V \times S))
+\bZ_k(\fg^S)(V) \cong \clies( \Omega^\bu(V) \otimes \fg^S, \bU_k \left(\fg^S\right)) \xto{\simeq} \clies(\Omega^\bu(V \times S) \otimes \fg, \bU_n(V \times S))
 \]
@@
 The righthand side is, however, the pushforward $\int_S \bZ_n \fg$.
-\owen{That map is not the canonical map as it goes the ``wrong way,'' but I'm pretty sure it provides the inverse-up-to-qiso we need.}
 \end{proof}

### 2020-10-02 draft.tex
def

@@
 
-\section{A few examples of the central result}
-
-We apply our central result to important classes of Lie algebras: 
-abelian, semisimple, and free.
-
-\subsection{Abelian Lie algebras and an $\EE_n$ Hochschild-Kostant-Rosenberg theorem}
-
-Given a free dg commutative algebra $A = \Sym(V^\bullet)$ generated by a cochain complex $V^\bullet$,
-one can view it as an $\EE_n$ algebra via the forgetful functor determined by the operad map $\EE_n \to E_\infty$.
-We will blithely view any commutative algebra as an $\EE_n$ algebra for any $n$ via this forgetting.
-
-We also know that for an abelian dg Lie algebra~${\frak a}$, 
-\[
-\cliels({\frak a}) = \Sym({\frak a}[1])
-\]
-and hence provides a free dg commutative algebra.
-This feature can be leveraged to prove the following result about $\EE_n$ centers of free commutative algebras.
-
-\begin{prp}
-Given a free dg commutative algebra $A = \Sym(V^\bullet)$ generated by a cochain complex $V^\bullet$,
-its center ${\frak Z}_n(A)$ is equivalent to the $E_{n+1}$ algebra of its shifted polyvector fields 
-\[
-{\rm Poly}_n(A) = \Sym(V^\bullet \oplus (V\bullet)^\vee[-n]).
-\]
-\end{prp}
-
-\begin{proof}
-A cochain complex $V^\bullet$ is an abelian dg Lie algebra;
-indeed, so is any shift $V^\bullet[k]$. 
-Let $\fg_V$ denote $V^\bullet[-n+1]$ viewed as an abelian dg Lie algebra.
-The Poincar\'e lemma for compactly supported de Rham forms on $\RR^n$ provides a canonical quasi-isomorphism
-\[
-\Omega^\bu_c(\RR^n) \xto{\simeq} \RR[-n]
-\]
-by the natural quotient map and hence determines a canonical quasi-isomorphism
-\[
-\cliels(\Omega^\bu_c(\RR^n) \otimes \fg_V) \xto{\simeq} \Sym(V^\bullet).
-\]
-This map makes sense on any ball in $\RR^n$ and thus implies that $\bU_n \fg_V$ is quasi-isomorphic as a $\Disk_n$ algebra to~$\Sym(V^\bullet)$.
-Applying our central theorem, we see
-\begin{align*}
-\bZ_n(\fg_V) &= \clies(\Omega^\bu \otimes \fg_V, \bU_n \fg_V) \\
-&= \Sym((\Omega^\bu \otimes \fg_V)^\vee[-1]) \otimes \Sym(\Omega^\bu_c \otimes \fg_V[1])\\
-& \simeq \Sym(V^\bullet \oplus (V\bullet)^\vee[-n])
-\end{align*}
-because
-\[
-\Omega^\bu (\RR^n) \otimes \fg_V \simeq V[-n+1]
-\]
-so
-\[
-\Sym( (\Omega^\bu(\RR^n) \otimes \fg_V)^\vee[-1]) \simeq \Sym( V^\vee[-n]).
-\]
-This identification concludes the argument.
-\end{proof}
-
-This result is the simplest case of a generalized Hochschild-Kostant-Rosenberg theorem for commutative algebras viewed as $\EE_n$ algebras.
-(The classic theorem proves the $n=1$ situation.)
-Such a result is proved by very different methods in~\cite{CalWil, ToenBranes}.
-Now we swiftly describe how to use methods like those in this paper to prove a version of this powerful result.
-
-\owen{Greg, please read this below.}
-First, we wish to define ${\rm Poly}_n(A)$ for an arbitrary dg commutative algebra $A$ in a way that gives the ``correct'' derived answer, i.e., the answer up to quasi-isomorphism of dg commutative algebras.
-Concretely, one should replace $A$ by a quasi-isomorphic but better behaved algebra $\widetilde{A}$, 
-such as semi-free resolution or cofibrant replacement with respect to some nice model category structure.
-Then one computes the tangent complex $\TT_{\widetilde{A}}$, i.e., the derived derivations.
-The {\em shifted polyvector fields} of $A$ means
-\[
-{\rm Poly}_n(A) \simeq \Sym_{\widetilde{A}} (\TT_{\widetilde{A}}[1-n]),
-\]
-which is again a dg commutative algebra up to quasi-isomorphism.
-
-Second, we introduce a technical hypothesis  needed to apply our methods.
-We need an {\em augmented} dg commutative algebra $\epsilon: A \to k$ that admits a semifree resolution of the form $(\Sym(V^\vee), \partial)$, where $V$ is some graded vector space.
-In other words, we need that the generators can be realized as the graded linear dual of some other graded vector space.
-We say such an algebra $A$ is of {\em type~($\star$)}.
-
-\begin{prp}
-Let $A$ be an augmented dg commutative algebra of type~($\star$).
-Then 
-\[
-{\frak Z}_n(A) \simeq {\rm Poly}_n(A).
-\]
-\end{prp}
-
-\begin{proof}
-By our technical hypothesis, we are free to replace $A$ by a semifree resolution $(\Sym(V^\vee), \partial)$. 
-Ignoring the differential, we see that our situation resembles our central result for an abelian Lie algebra,
-and so we now mimic the proof of our central result.
-
-There is a natural homotopy-locally constant sheaf of cochain complexes $\Omega^* \otimes V$ with differential $\d_{dR} + \partial$,
-which is a soft replacement for the locally constant sheaf $V$.
-Define the factorization algebra 
-\[
-F_A = (\Sym((\Omega* \otimes V)* ), \d_{dR} + \partial) 
-\]
-which is manifestly commutative and is quasi-isomorphic to $A$ on every disk.
-Hence $F_A$ is a commutative, locally constant factorization algebra that models~$A$.
-
-\owen{I'm partway done.}
-
-3) Define the putative center as a factorization algebra by starting with the polyvector fields for this semifree resolution
-
-4) Show this putative center fits into the commuting triangle and hence possesses a canonical map to the "true" center
-
-5) Use the Francis-Lurie recognition principle to show this map is a quasi-iso
-\end{proof}
-
-\owen{Also prove that the $\EE_n$ center of $\clies(\fg)$ is also $\clies(\fg, \UU_n \fg)$}
-
-\begin{cor}
-\label{cor: koszul dual to main theorem}
-For any $L_\infty$ algebra $\fg$,
-there is a quasi-isomorphism
-\[
-{\frak Z}_n(\clies(\fg)) \simeq \clies(\fg, \UU_n \fg).
-\]
-\end{cor}
-
-\subsection{A generalized Harish-Chandra isomorphism}
-
-For a reductive Lie group $G$, the Harish-Chandra isomorphism is an isomorphism of commutative algebras
-\[
-Z(U(\fg)) \xto{\cong} {\rm Sym} (\fh)^W,
-\]
-where $\fh$ is a Cartan subalgebra of the Lie algebra $\fg$ of $G$ and $W$ is the Weyl group of $G$. 
-Here $Z(U(\fg))$ denotes the ordinary center of the associative algebra~$U(\fg)$.
-
-Using our models, we obtain a generalization of the Harish--Chandra isomorphism to the $\EE_n$ center of the  enveloping $\EE_n$ algebra. 
-The following result follows from a simple application of the Poincar\'{e} lemma for de Rham forms and compactly supported de Rham forms.
-
-\begin{prp}
-There is a canonical quasi-isomorphism of $\EE_{n+1}$-algebras
-\[
-\bZ_n(\UU_n \fg) \xto{\simeq} \clies\left(\fg, \Sym(\fg[1-n]) \right) .
-\]
-\end{prp}
-
-In the case that $\fg$ is semi-simple, there is the following modest refinement of the result. 
-To state it, we set up some notation. 
-Since $\fg$ is reductive, the $\fg$-invariants of the exterior algebra $\Sym(\fg[1])^\fg = \left(\oplus_{k \geq 0} \wedge^k \fg[k]\right)^\fg$ is isomorphic to the Lie algebra homology $H^{\rm Lie}_\bu(\fg)$ \cite{Cartan}.
-Similarly, if $2\ell+1$ is an odd integer, then the $\fg$ invariants of $\Sym(\fg[k])^\fg = \oplus_{k \geq 0} \wedge^k \fg[2 \ell k + k]$ is isomorphic to the regraded Lie algebra homology $\Tilde{H}_\bu^{\rm Lie} (\fg, \ell)$
-which in degrees $-2\ell k - k$, $k \in \ZZ$ is $H_{k}^{\rm Lie}(\fg)$ and zero in all other degrees.
-
-\begin{prp}
-For $\fg$ a semi-simple Lie algebra with Cartan subalgebra~$\fh$ and Weyl group~$W$, we have the following:
-\begin{itemize}
-\item if $n$ is odd, then there is a quasi-isomorphism of $\EE_{n+1}$-algebras
-\[
-{\frak Z}_n(\UU_n \fg) \simeq \clies (\fg) \otimes \Sym(\fh[1-n])^W.
-\]
-\item if $n$ is even, then there is a quasi-isomorphism of $\EE_{n+1}$-algebras
-\[
-{\frak Z}_n(\UU_n \fg) \simeq \clies (\fg) \otimes \Tilde{H}_\bu^{\rm Lie} \left(\fg, \frac{n}{2} -1\right).
-\]
-\end{itemize}
-\end{prp}
-\begin{proof}
-By the Poincar\'{e} lemma for de Rham forms and compactly supported de Rham forms, one has a canonical quasi-isomorphism
-\[
-\bZ_n(\UU_n \fg) \xto{\simeq} \clies\left(\fg, \Sym(\fg[1-n]) \right) .
-\]
-Since $\fg$ is semi-simple, there is a quasi-isomorphism
-\[
-\clies(\fg, \Sym(\fg[1-n]) \simeq \clies (\fg) \otimes \Sym(\fg[1-n])^G 
-\]
-where $G$ is a compact connected Lie group whose Lie algebra is $\fg$.
-
-Now, when $n$ is odd, we apply the Chevalley restriction theorem to obtain an isomorphism of graded vector spaces
-\[
-\Sym(\fg[1-n])^G \cong \Sym \left(\fh[1-n]\right)^W .
-\]
-
-Similarly, when $n$ is even, we apply the discussion in the paragraph preceding the statement of this proposition 
-\end{proof}
-
-\subsection{Free Lie algebras and free $\EE_n$ algebras}
-
-\owen{Describe what we can of the center of a free $\EE_n$ algebra thanks to Ben's theorem}
-
 \section{Functoriality of the centralizer construction}
@@
 \end{equation}
-Lurie \cite{HA} has proved that this multiplication makes the center into an $E_1$ algebra in $\EE_n$ algebras 
-and therefore an $E_{n+1}$ algebra, by Dunn additivity. 
+Lurie \cite{HA} has proved that this multiplication makes the center into an $\EE_1$ algebra in $\EE_n$ algebras 
+and therefore an $\EE_{n+1}$ algebra, by Dunn additivity. 
 %To be precise, there is the following result.
@@
 \end{proof}
+
+\section{A few applications and examples of the central result}
+
+In this section we pursue a few immediate corollaries of the central results above.
+We apply our central result to important classes of Lie algebras: 
+abelian, semisimple, and free.
+
+\subsection{Deformations of $\EE_n$ enveloping algebras}
+It is well-known that the Hochschild cohomology of an associative, or $\EE_1$-algebra, controls its deformations. 
+Precisely, if $A$ is an $\EE_1$-algebra then the shift of its Hochschild cohomology ${\rm Hoch}^\bu (A , A)[1]$ carries a Lie algebra structure (in the homotopical sense). 
+The Maurer--Cartan elements of this dg Lie algebra classify deformations of $A$ as an $\EE_1$-algebra.
+
+Similarly, if $A$ is an $\EE_n$-algebra, the $\EE_n$-center $\fZ_n(A)$ controls deformations of $A$ as $\EE_n$-algebra. 
+Since $\fZ_n(A)$ is an $\EE_{n+1}$-algebra, the shift $\fZ_n(A)[n]$ is equipped with a Lie bracket. 
+Maurer--Cartan elements classify deformations of $A$ as an $\EE_{n}$-algebra.
+
+Using our model for the $\EE_n$-center, we obtain an explicit description 
+of deformations of $\EE_n$-enveloping algebras.
+
+\begin{prp}\label{prop:def}
+There is a canonical quasi-isomorphism 
+\begin{equation}\label{eqn:def}
+\bZ_n(\UU_n \fg) \xto{\simeq} \clies\left(\fg, \Sym(\fg[1-n]) \right) .
+\end{equation}
+%In particular, the cochain complex on the right-hand side has the structure of an $\EE_{n+1}$ algebra. 
+In particular, $\EE_n$-deformations of $\UU_n \fg$ up to equivalence are in bijective correspondence with the cohomology group
+\[
+H^{n+1} \bigg(\clie^\bu \left(\fg , \Sym(\fg[1-n]) \right) \bigg).
+\]
+\end{prp}
+\begin{proof}
+The first statement follows from the Poincar\'{e} lemma for de Rham forms and compactly supported de Rham forms
+\[
+\bZ_n(\UU_n \fg) = \clie^\bu\left(\Omega^\bu(\RR^n) \otimes \fg, \clieu_\bu(\Omega^\bu_c (\RR^n) \otimes \fg\right) \xto{\simeq} \clies\left(\fg, \Sym(\fg[1-n]) \right) .
+\]
+The second statement follows from the fact that Maurer--Cartan elements in $\bZ_n(\UU_n \fg)[n]$ classify deformations of $\UU_n \fg$. 
+\end{proof}
+
+\begin{rmk}
+When $n=1$ the quasi-isomorphism of the above proposition produces the well-known quasi-isomorphism
+\[
+{\rm Hoch}^\bu(U \fg , U \fg) \simeq \clie^\bu(\fg , \Sym(\fg)) ,
+\]
+see \cite{LodayCyclicBook}. 
+\end{rmk}
+
+%As a corollary of the above proposition, we obtain a concrete description for $\EE_n$-deformations of $\UU_n \fg$ when $\fg$ is an ordinary (strict) Lie algebra. 
+Suppose $\fg$ is an ordinary Lie algebra.
+It is known that if $\fg$ is semi-simple then the $\EE_1$-enveloping algebra $\UU_1 \fg$ is rigid in the sense that it admits no nontrivial deformations. 
+This follows from the above equivalence (\ref{eqn:def}) together with the fact that $H_{\rm Lie}^2(\fg , \Sym(\fg)) = 0$ when $\fg$ is semi-simple by Whitehead's theorem.
+
+For higher $n$, the $\EE_n$-enveloping algebra is no longer rigid, even in the case of semi-simple Lie algebras. 
+For instance, consider the case $n=2$.
+\begin{cor}
+Deformations of $\UU_2 \fg$ are in bijective correspondence with the group
+\[
+H^3_{\rm Lie}(\fg) \oplus H^2_{\rm Lie}(\fg , \fg) \oplus H^1_{\rm Lie}(\fg , \wedge^2 \fg) \oplus \wedge^3(\fg)^\fg .
+\]
+\end{cor}
+
+In particular, when $\fg$ is semisimple the middle two terms in the above corollary vanish and we are left with a two-dimensional space of deformations $H^3_{\rm Lie}(\fg) \oplus \wedge^3 (\fg)^\fg = k \oplus k$.
+\brian{check me}
+
+We have not yet described explicitly the Lie algebra structure on $\bZ_n(\UU_n \fg)[n]$ which is implicitly used in the characterization of deformations above. 
+\brian{can we describe $\PP_{n+1}$ structure explicitly?}
+
+\subsection{Abelian Lie algebras and an $\EE_n$ Hochschild-Kostant-Rosenberg theorem}
+
+Given a free dg commutative algebra $A = \Sym(V^\bullet)$ generated by a cochain complex $V^\bullet$,
+one can view it as an $\EE_n$ algebra via the forgetful functor determined by the operad map $\EE_n \to \EE_\infty$.
+We will blithely view any commutative algebra as an $\EE_n$ algebra for any $n$ via this forgetting.
+
+We also know that for an abelian dg Lie algebra~${\frak a}$, 
+\[
+\cliels({\frak a}) = \Sym({\frak a}[1])
+\]
+and hence provides a free dg commutative algebra.
+This feature can be leveraged to prove the following result about $\EE_n$ centers of free commutative algebras.
+
+\begin{prp}
+Given a free dg commutative algebra $A = \Sym(V^\bullet)$ generated by a cochain complex $V^\bullet$,
+its center ${\frak Z}_n(A)$ is equivalent to the $E_{n+1}$ algebra of its shifted polyvector fields 
+\[
+{\rm Poly}_n(A) = \Sym(V^\bullet \oplus (V\bullet)^\vee[-n]).
+\]
+\end{prp}
+
+\begin{proof}
+A cochain complex $V^\bullet$ is an abelian dg Lie algebra;
+indeed, so is any shift $V^\bullet[k]$. 
+Let $\fg_V$ denote $V^\bullet[-n+1]$ viewed as an abelian dg Lie algebra.
+The Poincar\'e lemma for compactly supported de Rham forms on $\RR^n$ provides a canonical quasi-isomorphism
+\[
+\Omega^\bu_c(\RR^n) \xto{\simeq} \RR[-n]
+\]
+by the natural quotient map and hence determines a canonical quasi-isomorphism
+\[
+\cliels(\Omega^\bu_c(\RR^n) \otimes \fg_V) \xto{\simeq} \Sym(V^\bullet).
+\]
+This map makes sense on any ball in $\RR^n$ and thus implies that $\bU_n \fg_V$ is quasi-isomorphic as a $\Disk_n$ algebra to~$\Sym(V^\bullet)$.
+Applying our central theorem, we see
+\begin{align*}
+\bZ_n(\fg_V) &= \clies(\Omega^\bu \otimes \fg_V, \bU_n \fg_V) \\
+&= \Sym((\Omega^\bu \otimes \fg_V)^\vee[-1]) \otimes \Sym(\Omega^\bu_c \otimes \fg_V[1])\\
+& \simeq \Sym(V^\bullet \oplus (V\bullet)^\vee[-n])
+\end{align*}
+because
+\[
+\Omega^\bu (\RR^n) \otimes \fg_V \simeq V[-n+1]
+\]
+so
+\[
+\Sym( (\Omega^\bu(\RR^n) \otimes \fg_V)^\vee[-1]) \simeq \Sym( V^\vee[-n]).
+\]
+This identification concludes the argument.
+\end{proof}
+
+This result is the simplest case of a generalized Hochschild-Kostant-Rosenberg theorem for commutative algebras viewed as $\EE_n$ algebras.
+(The classic theorem proves the $n=1$ situation.)
+Such a result is proved by very different methods in~\cite{CalWil, ToenBranes}.
+Now we swiftly describe how to use methods like those in this paper to prove a version of this powerful result.
+
+\owen{Greg, please read this below.}
+First, we wish to define ${\rm Poly}_n(A)$ for an arbitrary dg commutative algebra $A$ in a way that gives the ``correct'' derived answer, i.e., the answer up to quasi-isomorphism of dg commutative algebras.
+Concretely, one should replace $A$ by a quasi-isomorphic but better behaved algebra $\widetilde{A}$, 
+such as semi-free resolution or cofibrant replacement with respect to some nice model category structure.
+Then one computes the tangent complex $\TT_{\widetilde{A}}$, i.e., the derived derivations.
+The {\em shifted polyvector fields} of $A$ means
+\[
+{\rm Poly}_n(A) \simeq \Sym_{\widetilde{A}} (\TT_{\widetilde{A}}[1-n]),
+\]
+which is again a dg commutative algebra up to quasi-isomorphism.
+
+Second, we introduce a technical hypothesis  needed to apply our methods.
+We need an {\em augmented} dg commutative algebra $\epsilon: A \to k$ that admits a semifree resolution of the form $(\Sym(V^\vee), \partial)$, where $V$ is some graded vector space.
+In other words, we need that the generators can be realized as the graded linear dual of some other graded vector space.
+We say such an algebra $A$ is of {\em type~($\star$)}.
+
+\begin{prp}
+Let $A$ be an augmented dg commutative algebra of type~($\star$).
+Then 
+\[
+{\frak Z}_n(A) \simeq {\rm Poly}_n(A).
+\]
+\end{prp}
+
+\begin{proof}
+By our technical hypothesis, we are free to replace $A$ by a semifree resolution $(\Sym(V^\vee), \partial)$. 
+Ignoring the differential, we see that our situation resembles our central result for an abelian Lie algebra,
+and so we now mimic the proof of our central result.
+
+There is a natural homotopy-locally constant sheaf of cochain complexes $\Omega^* \otimes V$ with differential $\d_{dR} + \partial$,
+which is a soft replacement for the locally constant sheaf $V$.
+Define the factorization algebra 
+\[
+F_A = (\Sym((\Omega* \otimes V)* ), \d_{dR} + \partial) 
+\]
+which is manifestly commutative and is quasi-isomorphic to $A$ on every disk.
+Hence $F_A$ is a commutative, locally constant factorization algebra that models~$A$.
+
+\owen{I'm partway done.}
+
+3) Define the putative center as a factorization algebra by starting with the polyvector fields for this semifree resolution
+
+4) Show this putative center fits into the commuting triangle and hence possesses a canonical map to the "true" center
+
+5) Use the Francis-Lurie recognition principle to show this map is a quasi-iso
+\end{proof}
+
+\owen{Also prove that the $\EE_n$ center of $\clies(\fg)$ is also $\clies(\fg, \UU_n \fg)$}
+
+\begin{cor}
+\label{cor: koszul dual to main theorem}
+For any $L_\infty$ algebra $\fg$,
+there is a quasi-isomorphism
+\[
+{\frak Z}_n(\clies(\fg)) \simeq \clies(\fg, \UU_n \fg).
+\]
+\end{cor}
+
+\subsection{A generalized Harish-Chandra isomorphism}
+
+For a reductive Lie group $G$, the Harish-Chandra isomorphism is an isomorphism of commutative algebras
+\[
+Z(U(\fg)) \xto{\cong} {\rm Sym} (\fh)^W,
+\]
+where $\fh$ is a Cartan subalgebra of the Lie algebra $\fg$ of $G$ and $W$ is the Weyl group of $G$. 
+Here $Z(U(\fg))$ denotes the ordinary center of the associative algebra~$U(\fg)$.
+
+Using our models, we can obtain a generalization of the Harish--Chandra isomorphism to the $\EE_n$ center of the  enveloping $\EE_n$ algebra. 
+%The following result follows from a simple application of the Poincar\'{e} lemma for de Rham forms and compactly supported de Rham forms.
+
+In the case that $\fg$ is semi-simple, there is the following modest refinement of the result. 
+To state it, we set up some notation. 
+Since $\fg$ is reductive, the $\fg$-invariants of the exterior algebra $\Sym(\fg[1])^\fg = \left(\oplus_{k \geq 0} \wedge^k \fg[k]\right)^\fg$ is isomorphic to the Lie algebra homology $H^{\rm Lie}_\bu(\fg)$ \cite{Cartan}.
+Similarly, if $2\ell+1$ is an odd integer, then the $\fg$ invariants of $\Sym(\fg[k])^\fg = \oplus_{k \geq 0} \wedge^k \fg[2 \ell k + k]$ is isomorphic to the regraded Lie algebra homology $\Tilde{H}_\bu^{\rm Lie} (\fg, \ell)$
+which in degrees $-2\ell k - k$, $k \in \ZZ$ is $H_{k}^{\rm Lie}(\fg)$ and zero in all other degrees.
+
+\begin{prp}
+For $\fg$ a semi-simple Lie algebra with Cartan subalgebra~$\fh$ and Weyl group~$W$, we have the following:
+\begin{itemize}
+\item if $n$ is odd, then there is a quasi-isomorphism 
+\[
+{\frak Z}_n(\UU_n \fg) \simeq \clies (\fg) \otimes \Sym(\fh[1-n])^W.
+\]
+\item if $n$ is even, then there is a quasi-isomorphism 
+\[
+{\frak Z}_n(\UU_n \fg) \simeq \clies (\fg) \otimes \Tilde{H}_\bu^{\rm Lie} \left(\fg, \frac{n}{2} -1\right).
+\]
+\end{itemize}
+\end{prp}
+\begin{proof}
+We apply the quasi-isomorphism of Proposition \ref{prop:def}
+\[
+\bZ_n(\UU_n \fg) \xto{\simeq} \clies\left(\fg, \Sym(\fg[1-n]) \right) .
+\]
+Since $\fg$ is semi-simple, there is a further quasi-isomorphism
+\[
+\clies(\fg, \Sym(\fg[1-n]) \simeq \clies (\fg) \otimes \Sym(\fg[1-n])^G 
+\]
+where $G$ is a compact connected Lie group whose Lie algebra is $\fg$.
+
+Now, when $n$ is odd, we apply the Chevalley restriction theorem to obtain an isomorphism of graded vector spaces
+\[
+\Sym(\fg[1-n])^G \cong \Sym \left(\fh[1-n]\right)^W .
+\]
+
+Similarly, when $n$ is even, we apply the discussion in the paragraph preceding the statement of this proposition 
+\end{proof}
+
+\subsection{Free Lie algebras and free $\EE_n$ algebras}
+
+\owen{Describe what we can of the center of a free $\EE_n$ algebra thanks to Ben's theorem}
 

### 2020-10-16 draft.tex
unsuccessful attempt by O to finish the E_n HKR theorem

@@
 
-\begin{dfn}\label{D:centralizer}
+\begin{dfn}
+\label{D:centralizer}
 For a map $f: A \to B$ of $\EE_n$ algebras in $\cC$, 
@@
 
-\owen{Greg, please read this below.}
+\owen{I've gotten myself pretty mixed up about this \dots It's fixable but I need to think things through.}
+
 First, we wish to define ${\rm Poly}_n(A)$ for an arbitrary dg commutative algebra $A$ in a way that gives the ``correct'' derived answer, i.e., the answer up to quasi-isomorphism of dg commutative algebras.
@@
 \[
-{\rm Poly}_n(A) \simeq \Sym_{\widetilde{A}} (\TT_{\widetilde{A}}[1-n]),
+{\rm Poly}_n(A) \simeq \Sym_{\widetilde{A}} (\TT_{\widetilde{A}}[-n]),
 \]
@@
 
-Second, we introduce a technical hypothesis  needed to apply our methods.
-We need an {\em augmented} dg commutative algebra $\epsilon: A \to k$ that admits a semifree resolution of the form $(\Sym(V^\vee), \partial)$, where $V$ is some graded vector space.
-In other words, we need that the generators can be realized as the graded linear dual of some other graded vector space.
-We say such an algebra $A$ is of {\em type~($\star$)}.
+%Second, we introduce a technical hypothesis  needed to apply our methods.
+%We need an {\em augmented} dg commutative algebra $\epsilon: A \to k$ that admits a semifree resolution of the form $(\Sym(V^\vee), \partial)$, where $V$ is some graded vector space.
+%In other words, we need that the generators can be realized as the graded linear dual of some other graded vector space.
+%We say such an algebra $A$ is of {\em type~($\star$)}.
 
 \begin{prp}
-Let $A$ be an augmented dg commutative algebra of type~($\star$).
+Let $A$ be an augmented dg commutative algebra.
 Then 
@@
 \begin{proof}
-By our technical hypothesis, we are free to replace $A$ by a semifree resolution $(\Sym(V^\vee), \partial)$. 
+We are free to replace $A$ by a semifree resolution $(\Sym(V), \partial)$,
+where $\partial$ sends $V$ to the augmentation ideal $\Sym^{> 0}(V)$.
+Below we will (abusively) use $A$ to denote this semifree resolution,
+as the original $A$ is irrelevant for us.
 Ignoring the differential, we see that our situation resembles our central result for an abelian Lie algebra,
@@
 
-There is a natural homotopy-locally constant sheaf of cochain complexes $\Omega^* \otimes V$ with differential $\d_{dR} + \partial$,
+There is a natural homotopy-locally constant sheaf of cochain complexes $\Omega^\bu \otimes V$ with differential $\d_{dR} + \partial$,
 which is a soft replacement for the locally constant sheaf $V$.
-Define the factorization algebra 
-\[
-F_A = (\Sym((\Omega* \otimes V)* ), \d_{dR} + \partial) 
+In the same way, we define the factorization algebra 
+\[
+F_A = (\Sym((\Omega^\bu)^* \otimes V ), \d_{dR} + \partial) 
 \]
@@
 
-\owen{I'm partway done.}
-
-3) Define the putative center as a factorization algebra by starting with the polyvector fields for this semifree resolution
+Similar techniques allow us to construct a factorization algebra modeling the polyvector fields ${\rm Poly}_n(A)$.
+Define
+\[
+Z_A = (\Hom^\bu(\Sym((\Omega^\bu)^* \otimes V), \Sym(\Omega_c^* \otimes V), [\d_{dR} + \partial,-]).
+\]
+Note its similarity to our model $\bZ_\fg$ for the center of~$\bU_n \fg$.
+%There is a canonical shifted Poisson structure here by extending the canonical  pairing
+%\[
+%(\Omega^\bu \otimes V)^* \otimes \Omega^\bu_c \otimes V \to \RR
+%\]
+%arising from the inclusion $\Omega^\bu_c \otimes V \hookrightarrow \Omega^\bu \otimes V$.
+
+Let us verify that 
+\[
+Z_A(D) \simeq {\rm Poly}_n(A)
+\]
+for any open disk $D$.
+Due to the Poincar\'e lemma, we have canonical quasi-isomorphisms $(\Omega^\bu(D))^* \otimes V \xto{\simeq} V$ and $\Omega^\bu_c(D) \otimes V \xto{\simeq} V[-n]$,
+where we view $V$ as simply a graded vector space but the de Rham complexes have the differential $\d_{dR}$.
+(The differential $\partial$ will make its appearance shortly.)
+Thus we have quasi-isomorphisms
+\[
+i: \Sym((\Omega^\bu(D))^* \otimes V) \xto{\simeq} \Sym(V)
+\]
+and 
+\[
+i_c: \Sym(\Omega_c^*(D) \otimes V) \xto{\simeq} \Sym(V[-n]).
+\]
+As $\partial$ acts only on the $V$-factors and not the de Rham factors,
+we can modify all the complexes by adding $\partial$ to the differential.
+Finally, if we fix a quasi-isomorphism 
+\[
+s: \Sym(V) \xto{\simeq} \Sym((\Omega^\bu(D))^* \otimes V),
+\]
+we get a map
+\[
+\begin{array}{ccc}
+Z_A(D) & \to & \Hom^\bu(A,A)\\
+\Phi & \mapsto & i_c \circ \Phi \circ s
+\end{array}
+\]
+that is a quasi-isomorphism.
+(Note that $s$ depends on the disk~$D$. 
+We do not construct a map that intertwines with any structure maps of~$Z_A$.)
+
+We now turn to constructing a map from this factorization algebra $Z_A$ to the center ${\frak Z}_n(A)$.
+The key is to show that $Z_A$ fits into a commuting triangle as in Definition~\ref{D:centralizer},
+because then we know $Z_A$ has a canonical map to~${\frak Z}_n(A)$.
+This action is quite easy to see here: there is a canonical map
+\[
+\Hom^\bu(\Sym((\Omega^\bu)^* \otimes V), \Sym(\Omega_c^* \otimes V) \otimes \Sym((\Omega^\bu)^* \otimes V) \to \Sym((\Omega^\bu)^* \otimes V)
+\]
+that sends $\Phi \otimes x$ to $\iota(\Phi(x))$,
+where 
+\[
+\iota: \Sym(\Omega_c^\bu \otimes V) \to \Sym((\Omega^\bu)^* \otimes V)
+\]
 

### 2020-10-17 draft.tex
getting caught up in making HKR work, for lots of issues

@@
 
+\owen{This is really turning into a mess.}
+
 \begin{proof}
@@
 
-There is a natural homotopy-locally constant sheaf of cochain complexes $\Omega^\bu \otimes V$ with differential $\d_{dR} + \partial$,
-which is a soft replacement for the locally constant sheaf $V$.
+There is a natural homotopy-locally constant sheaf of cochain complexes $\Omega^\bu$ with differential $\d_{dR}$,
+which is a soft replacement for the locally constant sheaf $\RR$.
+Taking duals, we get a cosheaf.
 In the same way, we define the factorization algebra 

### 2020-10-21 draft.tex
added small reminders about my confusions
attempt at spec seq construction

@@
 
-\subsection{Deformations of $\EE_n$ enveloping algebras}
-It is well-known that the Hochschild cohomology of an associative, or $\EE_1$-algebra, controls its deformations. 
-Precisely, if $A$ is an $\EE_1$-algebra then the shift of its Hochschild cohomology ${\rm Hoch}^\bu (A , A)[1]$ carries a Lie algebra structure (in the homotopical sense). 
-The Maurer--Cartan elements of this dg Lie algebra classify deformations of $A$ as an $\EE_1$-algebra.
-
-Similarly, if $A$ is an $\EE_n$-algebra, the $\EE_n$-center $\fZ_n(A)$ controls deformations of $A$ as $\EE_n$-algebra. 
-Since $\fZ_n(A)$ is an $\EE_{n+1}$-algebra, the shift $\fZ_n(A)[n]$ is equipped with a Lie bracket. 
-Maurer--Cartan elements classify deformations of $A$ as an $\EE_{n}$-algebra.
-
-Using our model for the $\EE_n$-center, we obtain an explicit description 
-of deformations of $\EE_n$-enveloping algebras.
+\subsection{Deformations of enveloping $\EE_n$ algebras}
+It is well-known that the Hochschild cohomology of an associative, or $\EE_1$ algebra, controls its deformations. 
+Precisely, if $A$ is an $\EE_1$ algebra then the shift of its Hochschild cohomology ${\rm Hoch}^\bu (A , A)[1]$ carries a Lie algebra structure (in the homotopical sense). 
+The Maurer--Cartan elements of this dg Lie algebra classify deformations of $A$ as an $\EE_1$ algebra.
+
+Similarly, if $A$ is an $\EE_n$ algebra, the $\EE_n$ center $\fZ_n(A)$ controls deformations of $A$ as $\EE_n$-algebra. 
+Since $\fZ_n(A)$ is an $\EE_{n+1}$ algebra, the shift $\fZ_n(A)[n]$ is equipped with a Lie bracket. 
+Maurer--Cartan elements classify deformations of $A$ as an $\EE_{n}$ algebra.
+
+Using our model for the $\EE_n$ center, we obtain an explicit description 
+of deformations of $\EE_n$ enveloping algebras.
 
@@
 There is a canonical quasi-isomorphism 
-\begin{equation}\label{eqn:def}
+\begin{equation}
+\label{eqn:def}
 \bZ_n(\UU_n \fg) \xto{\simeq} \clies\left(\fg, \Sym(\fg[1-n]) \right) .
@@
 
-\begin{rmk}
 When $n=1$ the quasi-isomorphism of the above proposition produces the well-known quasi-isomorphism
 \[
-{\rm Hoch}^\bu(U \fg , U \fg) \simeq \clie^\bu(\fg , \Sym(\fg)) ,
-\]
-see \cite{LodayCyclicBook}. 
-\end{rmk}
+{\rm Hoch}^\bu(U \fg , U \fg) \simeq \clie^\bu(\fg , \Sym(\fg)).
+\]
+See~\cite{LodayCyclicBook} for discussion of Hochschild (co)homology for such ``almost commutative'' algebras.
 
 %As a corollary of the above proposition, we obtain a concrete description for $\EE_n$-deformations of $\UU_n \fg$ when $\fg$ is an ordinary (strict) Lie algebra. 
-Suppose $\fg$ is an ordinary Lie algebra.
-It is known that if $\fg$ is semi-simple then the $\EE_1$-enveloping algebra $\UU_1 \fg$ is rigid in the sense that it admits no nontrivial deformations. 
-This follows from the above equivalence (\ref{eqn:def}) together with the fact that $H_{\rm Lie}^2(\fg , \Sym(\fg)) = 0$ when $\fg$ is semi-simple by Whitehead's theorem.
+Consider the situation of an ordinary Lie algebra~$\fg$.
+When $\fg$ is semi-simple, the enveloping $\EE_1$ algebra $\UU_1 \fg$ is rigid in the sense that it admits no nontrivial deformations. 
+This claim follows from the above equivalence (\ref{eqn:def}) together with the fact that $H_{\rm Lie}^2(\fg , \Sym(\fg)) = 0$ for $\fg$ is semi-simple by Whitehead's theorem.
 
@@
 
-\owen{I've gotten myself pretty mixed up about this \dots It's fixable but I need to think things through.}
+\owen{I've gotten myself pretty mixed up about this \dots too many duals with infinite dimensional vector spaces, and issues with whether you can base-change a semi-free algebra.}
 
@@
 \owen{We should "compute" the left hand side, borrowing from the GRW paper.}
+
+The left hand side is eminently computable, 
+amounting to a computing relative de Rham cohomology.
+What we really want is a convenient model for the entire factorization algebra whose behavior recovers the pair $(\Gr \frak{Z}_n(\fg), \Gr \UU_n \fg)$.
+Thankfully, it is straightforward to find one, via classic algebraic topology.
+
+For any open subset $V$ in $M$, define
+\[
+\Omega^*_{{\rm rel }}(V) = \{ \alpha \in \Omega^*(V) \, : \, \alpha|_{\partial M} = 0\}.
+\]
+This construction models cohomology relative to the boundary.
+Note that
+\[
+\Omega^*_{{\rm rel }}(U \times [0,\epsilon)) \simeq \Omega^*)_U \otimes \Omega^*_{{\rm rel }}([0,\epsilon)) \simeq 0
+\]
+as the relative cochains $\Omega^*_{{\rm rel }}([0,\epsilon))$ are acyclic.
+
+Consider the prefactorization algebra on $M$ that assigns to the open set $V$, 
+the cochain complex
+\[
+F_{{\rm rel}}(V) =\clies(\Omega^*_{{\rm rel }}(V) \otimes \fg, \Sym(\Omega^*_c(V) \otimes \fg[2])).
+\]
+When $V$ is an open set inside $\mathring{M}$, we find $F_{{\rm rel}}(\mathring{M})$ agrees with  $\Gr \frak{Z}_n(\fg)(V)$.
+When $V$ is a product open $U \times [0,\epsilon)$ along the boundary, we find 
+\[
+F_{{\rm rel}}(V) \simeq \clies(0, \Sym(\Omega^*_c(U) \otimes \fg[1])) \simeq \Sym(\Omega^*_c(U) \otimes \fg[1]) \simeq \Gr \UU_n \fg(U),
+\]
+as desired.
+\owen{Maybe in the second factor I replace $V$ by $V \setminus (V \cap \partial M)$?}
+This construction $F_{{\rm rel}}$ defines, in fact, a factorization algebra by a mild variant of the argument from \owen{cite GRW}.
+
+We thus find
+\[
+\int_{(M,\partial M)} (\Gr \frak{Z}_n(\fg), \Gr \UU_n \fg) \simeq F_{{\rm rel}}(M) =\clies(\Omega^*_{{\rm rel }}(M) \otimes \fg, \Sym(\Omega^*_c(\mathring{M}) \otimes \fg[2])).
+\]
+Let us now focus on the case where $M$ is compact with boundary.
+Then $\Omega^*_c(\mathring{M}) = \Omega^*_{{\rm rel}}(M)$, so
+\[
+\int_{(M,\partial M)} (\Gr \frak{Z}_n(\fg), \Gr \UU_n \fg) 
+\simeq \clies(\Omega^*_{{\rm rel }}(M) \otimes \fg, \Sym(\Omega^*_{{\rm rel}}(M) \otimes \fg[2])),
+\]
+and so it remains to compute relative cohomology.
+
+\owen{revisit and revise}
+
+%By definition~\ref{dfn:constructible1}, we have a model for the pair $(\Gr \frak{Z}_n(\fg), \Gr \UU_n \fg)$.
+%To see this, observe that to an open subset $V$ of the interior $\mathring{M}$, 
+%the factorization algebra assigns
+%\begin{equation}
+%\label{eqn: gr Z}
+%\clies(\Omega^*(V) \otimes \fg, \Sym(\Omega^*_c(V) \otimes \fg[2])).
+%\end{equation}
+%Given an open set $U \subset \partial M$ and a small open neighborhood in $M$ of $U$ such as $U \times [0,\epsilon)$ (depending on a choice of local collar coordinate), 
+%the factorization algebra assigns
+%\[
+%\Sym(\Omega^*_c(U)\otimes \fg[1]),
+%\]
+%up to quasi-isomorphism.
+%
+%What we really want is a convenient model for this entire factorization algebra whose behavior recovers with the values above.
+%Thankfully, it is straightforward to find one, via classic algebraic topology.
+%For any open subset $V$ in $M$, define
+%\[
+%\Omega^*_{{\rm rel }}(V) = \{ \alpha \in \Omega^*(V) \, : \, \alpha|_{\partial M} = 0\}.
+%\]
+%This construction models cohomology relative to the boundary.
+%Note that
+%\[
+%\Omega^*_{{\rm rel }}(U \times [0,\epsilon)) \simeq \Omega^*)_U \otimes \Omega^*_{{\rm rel }}([0,\epsilon)) \simeq 0
+%\]
+%as the relative cochains $\Omega^*_{{\rm rel }}([0,\epsilon))$ are acyclic.
+%
+%Consider the prefactorization algebra on $M$ that assigns to the open set $V$, 
+%the cochain complex
+%\[
+%F_{{\rm rel}}(V) =\clies(\Omega^*_{{\rm rel }}(V) \otimes \fg, \Sym(\Omega^*_c(V) \otimes \fg[2])).
+%\]
+%When $V$ is an open set inside $\mathring{M}$, we find $F_{{\rm rel}}(\mathring{M})$ recovers \eqref{eqn: gr Z} from above.
+%When $V$ is a product open $U \times [0,\epsilon)$ along the boundary, we find 
+%\[
+%F_{{\rm rel}}(V) \simeq \clies(0, \Sym(\Omega^*_c(V) \otimes \fg)) \simeq \Sym(\Omega^*_c(V) \otimes \fg),
+%\]
+%as desired.
 

### 2020-10-22 draft.tex
towards computing the center of CE cochains

@@
 
-The notation $\int_{S^{n-1}}\UU_n\fg$ produces a factorization algebra on $\RR$.
+The construction $\int_{S^{n-1}}\UU_n\fg$ produces a factorization algebra on $\RR$.
 Indeed,
@@
 
-We have thus reduced the situation to familiar dg algebra via the equivalence
+The equivalence
 \[
@@
 \simeq 
-{\rm Mor}_{\LMod_{U(\fg \otimes R_n)}} (\Sym(\fg[1-n]), (\Sym(\fh[1-n]))_f).
-\]
+{\rm Mor}_{\LMod_{U(\fg \otimes R_n)}} (\Sym(\fg[1-n]), (\Sym(\fh[1-n]))_f)
+\]
+thus reduces the situation to familiar dg algebra.
 By the inclusion of the unit $k \hookrightarrow R_n = k \oplus k[1-n]$,
@@
 
-When $n=1$ the quasi-isomorphism of the above proposition produces the well-known quasi-isomorphism
+When $n=1$, the above proposition recovers the well-known quasi-isomorphism
 \[
@@
 %As a corollary of the above proposition, we obtain a concrete description for $\EE_n$-deformations of $\UU_n \fg$ when $\fg$ is an ordinary (strict) Lie algebra. 
-Consider the situation of an ordinary Lie algebra~$\fg$.
+Consider now the situation of an ordinary Lie algebra~$\fg$.
 When $\fg$ is semi-simple, the enveloping $\EE_1$ algebra $\UU_1 \fg$ is rigid in the sense that it admits no nontrivial deformations. 
@@
 For instance, consider the case $n=2$.
+
 \begin{cor}
-Deformations of $\UU_2 \fg$ are in bijective correspondence with the group
+First-order deformations of $\UU_2 \fg$ are in bijective correspondence with
 \[
@@
 \]
+In particular, for $\fg$ simple, the middle two terms vanish and deformations are isomorphic to $k \oplus k$.
 \end{cor}
-
-In particular, when $\fg$ is semisimple the middle two terms in the above corollary vanish and we are left with a two-dimensional space of deformations $H^3_{\rm Lie}(\fg) \oplus \wedge^3 (\fg)^\fg = k \oplus k$.
-\brian{check me}
 
@@
 Such a result is proved by very different methods in~\cite{CalWil, ToenBranes}.
-Now we swiftly describe how to use methods like those in this paper to prove a version of this powerful result.
-
-\owen{I've gotten myself pretty mixed up about this \dots too many duals with infinite dimensional vector spaces, and issues with whether you can base-change a semi-free algebra.}
-
-First, we wish to define ${\rm Poly}_n(A)$ for an arbitrary dg commutative algebra $A$ in a way that gives the ``correct'' derived answer, i.e., the answer up to quasi-isomorphism of dg commutative algebras.
-Concretely, one should replace $A$ by a quasi-isomorphic but better behaved algebra $\widetilde{A}$, 
-such as semi-free resolution or cofibrant replacement with respect to some nice model category structure.
-Then one computes the tangent complex $\TT_{\widetilde{A}}$, i.e., the derived derivations.
-The {\em shifted polyvector fields} of $A$ means
-\[
-{\rm Poly}_n(A) \simeq \Sym_{\widetilde{A}} (\TT_{\widetilde{A}}[-n]),
-\]
-which is again a dg commutative algebra up to quasi-isomorphism.
-
-%Second, we introduce a technical hypothesis  needed to apply our methods.
-%We need an {\em augmented} dg commutative algebra $\epsilon: A \to k$ that admits a semifree resolution of the form $(\Sym(V^\vee), \partial)$, where $V$ is some graded vector space.
-%In other words, we need that the generators can be realized as the graded linear dual of some other graded vector space.
-%We say such an algebra $A$ is of {\em type~($\star$)}.
+Our method offers another approach, pursued in~\cite{GGWZ2}.
+
+\subsection{Koszul duality}
+
+\owen{Also prove that the $\EE_n$ center of $\clies(\fg)$ is also $\clies(\fg, \UU_n \fg)$}
+
+It will be convenient for us to prove a special case of that HKR theorem.
 
 \begin{prp}
-Let $A$ be an augmented dg commutative algebra.
-Then 
-\[
-{\frak Z}_n(A) \simeq {\rm Poly}_n(A).
-\]
-\end{prp}
-
-\owen{This is really turning into a mess.}
-
-\begin{proof}
-We are free to replace $A$ by a semifree resolution $(\Sym(V), \partial)$,
-where $\partial$ sends $V$ to the augmentation ideal $\Sym^{> 0}(V)$.
-Below we will (abusively) use $A$ to denote this semifree resolution,
-as the original $A$ is irrelevant for us.
-Ignoring the differential, we see that our situation resembles our central result for an abelian Lie algebra,
-and so we now mimic the proof of our central result.
-
-There is a natural homotopy-locally constant sheaf of cochain complexes $\Omega^\bu$ with differential $\d_{dR}$,
-which is a soft replacement for the locally constant sheaf $\RR$.
-Taking duals, we get a cosheaf.
-In the same way, we define the factorization algebra 
-\[
-F_A = (\Sym((\Omega^\bu)^* \otimes V ), \d_{dR} + \partial) 
-\]
-which is manifestly commutative and is quasi-isomorphic to $A$ on every disk.
-Hence $F_A$ is a commutative, locally constant factorization algebra that models~$A$.
-
-Similar techniques allow us to construct a factorization algebra modeling the polyvector fields ${\rm Poly}_n(A)$.
-Define
-\[
-Z_A = (\Hom^\bu(\Sym((\Omega^\bu)^* \otimes V), \Sym(\Omega_c^* \otimes V), [\d_{dR} + \partial,-]).
-\]
-Note its similarity to our model $\bZ_\fg$ for the center of~$\bU_n \fg$.
-%There is a canonical shifted Poisson structure here by extending the canonical  pairing
-%\[
-%(\Omega^\bu \otimes V)^* \otimes \Omega^\bu_c \otimes V \to \RR
-%\]
-%arising from the inclusion $\Omega^\bu_c \otimes V \hookrightarrow \Omega^\bu \otimes V$.
-
-Let us verify that 
-\[
-Z_A(D) \simeq {\rm Poly}_n(A)
-\]
-for any open disk $D$.
-Due to the Poincar\'e lemma, we have canonical quasi-isomorphisms $(\Omega^\bu(D))^* \otimes V \xto{\simeq} V$ and $\Omega^\bu_c(D) \otimes V \xto{\simeq} V[-n]$,
-where we view $V$ as simply a graded vector space but the de Rham complexes have the differential $\d_{dR}$.
-(The differential $\partial$ will make its appearance shortly.)
-Thus we have quasi-isomorphisms
-\[
-i: \Sym((\Omega^\bu(D))^* \otimes V) \xto{\simeq} \Sym(V)
-\]
-and 
-\[
-i_c: \Sym(\Omega_c^*(D) \otimes V) \xto{\simeq} \Sym(V[-n]).
-\]
-As $\partial$ acts only on the $V$-factors and not the de Rham factors,
-we can modify all the complexes by adding $\partial$ to the differential.
-Finally, if we fix a quasi-isomorphism 
-\[
-s: \Sym(V) \xto{\simeq} \Sym((\Omega^\bu(D))^* \otimes V),
-\]
-we get a map
-\[
-\begin{array}{ccc}
-Z_A(D) & \to & \Hom^\bu(A,A)\\
-\Phi & \mapsto & i_c \circ \Phi \circ s
-\end{array}
-\]
-that is a quasi-isomorphism.
-(Note that $s$ depends on the disk~$D$. 
-We do not construct a map that intertwines with any structure maps of~$Z_A$.)
-
-We now turn to constructing a map from this factorization algebra $Z_A$ to the center ${\frak Z}_n(A)$.
-The key is to show that $Z_A$ fits into a commuting triangle as in Definition~\ref{D:centralizer},
-because then we know $Z_A$ has a canonical map to~${\frak Z}_n(A)$.
-This action is quite easy to see here: there is a canonical map
-\[
-\Hom^\bu(\Sym((\Omega^\bu)^* \otimes V), \Sym(\Omega_c^* \otimes V) \otimes \Sym((\Omega^\bu)^* \otimes V) \to \Sym((\Omega^\bu)^* \otimes V)
-\]
-that sends $\Phi \otimes x$ to $\iota(\Phi(x))$,
-where 
-\[
-\iota: \Sym(\Omega_c^\bu \otimes V) \to \Sym((\Omega^\bu)^* \otimes V)
-\]
-
-4) Show this putative center fits into the commuting triangle and hence possesses a canonical map to the "true" center
-
-5) Use the Francis-Lurie recognition principle to show this map is a quasi-iso
-\end{proof}
-
-\owen{Also prove that the $\EE_n$ center of $\clies(\fg)$ is also $\clies(\fg, \UU_n \fg)$}
-
-\begin{cor}
 \label{cor: koszul dual to main theorem}
@@
 \[
-{\frak Z}_n(\clies(\fg)) \simeq \clies(\fg, \UU_n \fg).
-\]
-\end{cor}
+{\frak Z}_n(\clies(\fg)) \simeq {\frak Z}_n(\UU_n \fg) \simeq \clies(\fg, \UU_n \fg).
+\]
+\end{prp}
+
+There is a structural feature to observe before we give the proof.
+Note that $\clies(\fg)$ itself arises as a centralizer:
+take the Lie algebra map $z: \fg \to 0$, 
+in which case ${\frak Z}_n(z) \simeq \clies(\fg)$ because $\UU_n(0) \simeq 1$, the unit $\EE_n$ algebra.
+The functoriality of the centralizer construction then tells us that ${\frak Z}_n(\UU_n \fg)$ acts on ${\frak Z}_n(\clies(\fg))$, by considering how the composite Lie algebra map 
+\[
+\fg \xto{\id} \fg \xto{z} 0
+\]
+determines an $\EE_n$ algebra map 
+\[
+\UU_n \fg \xto{\id} \UU_n \fg \xto{z} \UU_n(0) = 1
+\]
+and hence a map of centralizers
+\[
+{\frak Z}_n(\id) \otimes {\frak Z}_n(z) \to {\frak Z}_n(z).
+\]
+But ${\frak Z}_n(\id) = {\frak Z}_n(\fg)$ and ${\frak Z}_n(z) = \cliels(\fg)$.
+In this way, we obtain a canonical map ${\frak Z}_n(\fg) \to {{\frak Z}_n(\clies(\fg))}$.
+We wish to show it is an equivalence.
+
+\begin{proof}
+We use the factorization algebra $\clies(\Omega^* \otimes \fg)$ as is a factorization model for $\clies(\fg)$.
+The idea is 
+\begin{enumerate}
+\item to show that our model $\bZ_n(\fg)$ for the center of $\bU_n \fg$ acts on the factorization algebra $\clies(\Omega^* \otimes \fg)$, and hence we obtain a canonical map $\bZ_n(\fg) \to {\frak Z}_n(\clies(\fg))$; and then
+\item to use the Francis-Lurie recognition principle to verify this map is a quasi-isomorphism.
+\end{enumerate}
+Just before the proof, we explained why this canonical map exists for structural reasons,
+and Theorem~\ref{T:compcentralizer} provides a completely explicit construction of it.
+
+It remains to apply the recognition principle.
+We compute
+\begin{align*}
+\int_{S^{n-1}}\clies(\fg) 
+&\simeq \clies(\Omega^\bu(\RR_{> 0} \times S^{n-1}) \otimes \fg)\\
+&\simeq \clies(H^\bu(S^{n-1}) \otimes \fg)
+\end{align*}
+because $(n-1)$-sphere is formal over the rationals (or reals). 
+This pushforward to the real line $\RR$ is a locally constant factorization algebra,
+which happens to be commutative here.
+As the cohomology of the $(n-1)$-sphere is 
+\[
+R_n = k[\epsilon_{n-1}]/(\epsilon_{n-1}^2),
+\] 
+where $|\epsilon_{n-1}| = n-1$,
+we find that 
+\[
+\int_{S^{n-1}}\clies(\fg) \simeq \clies(\fg \otimes R_n)
+\]
+as commutative algebras.
+
+Consider now the equivalence
+\[
+{\rm Mor}_{\LMod_{\int_{S^{n-1}} \clies(\fg)}}(\clies(\fg), \clies(\fg)) 
+\simeq 
+{\rm Mor}_{\LMod_{\clies(\fg \otimes R_n)}} (\clies(\fg), \clies(\fg)).
+\]
+\owen{I think it's straightforward algebra after this (along the lines of the base change for the other proof), but I'm running out of steam right now.}
+%The augmentation $R_n = k \oplus k[1-n] \to k$,
+%induces a canonical inclusion $i: \clies(\fg) \to \clies(\fg \otimes R_n)$ of dg associative algebras,
+%and so
+%\[
+%k \otimes_{U\fg} U(\fg \otimes R_n) \simeq \Sym(\fg[1-n]).
+%\]
+%Base change along $i$ thus gives rise to an equivalence 
+%\[
+%{\rm Mor}_{\LMod_{U\fg}} (k, (\Sym(\fh[1-n]))_f) \simeq {\rm Mor}_{\LMod_{U(\fg \otimes R_n)}} (\Sym(\fg[1-n]), (\Sym(\fh[1-n]))_f)
+%\]
+%of underlying cochain complexes, i.e. an equivalence after applying the forgetful functor. 
+%The left hand side is modeled by $\clies(\fg,(\Sym(\fh[1-n]))_f)$, 
+%the Lie algebra cochains of $\fg$ with coefficients in~$(\UU_n \fh)_f$, as desired.
+%Hence the map $\theta_{\bf f}$ is a quasi-isomorphism on any disk, as needed.
+\end{proof}
+
+\owen{Add a discussion of Koszul duality. In the abelian case this is really obvious.}
 
@@
 
-Now, when $n$ is odd, we apply the Chevalley restriction theorem to obtain an isomorphism of graded vector spaces
-\[
-\Sym(\fg[1-n])^G \cong \Sym \left(\fh[1-n]\right)^W .
-\]
-
-Similarly, when $n$ is even, we apply the discussion in the paragraph preceding the statement of this proposition 
+Now, when $n$ is odd, we apply the Chevalley restriction theorem to obtain an isomorphism 
+\[
+\Sym(\fg[1-n])^G \cong \Sym \left(\fh[1-n]\right)^W 
+\]
+of graded vector spaces.
+
+Similarly, when $n$ is even, we apply the discussion in the paragraph preceding the statement of this proposition.
 \end{proof}

### 2020-10-22 HKR.tex
notes toward short paper on En HKR

Now we swiftly describe how to use methods like those in this paper to prove a version of this powerful result.

\owen{I've gotten myself pretty mixed up about this \dots too many duals with infinite dimensional vector spaces, and issues with whether you can base-change a semi-free algebra.}

First, we wish to define ${\rm Poly}_n(A)$ for an arbitrary dg commutative algebra $A$ in a way that gives the ``correct'' derived answer, i.e., the answer up to quasi-isomorphism of dg commutative algebras.
Concretely, one should replace $A$ by a quasi-isomorphic but better behaved algebra $\widetilde{A}$, 
such as semi-free resolution or cofibrant replacement with respect to some nice model category structure.
Then one computes the tangent complex $\TT_{\widetilde{A}}$, i.e., the derived derivations.
The {\em shifted polyvector fields} of $A$ means
\[
{\rm Poly}_n(A) \simeq \Sym_{\widetilde{A}} (\TT_{\widetilde{A}}[-n]),
\]
which is again a dg commutative algebra up to quasi-isomorphism.

%Second, we introduce a technical hypothesis  needed to apply our methods.
%We need an {\em augmented} dg commutative algebra $\epsilon: A \to k$ that admits a semifree resolution of the form $(\Sym(V^\vee), \partial)$, where $V$ is some graded vector space.
%In other words, we need that the generators can be realized as the graded linear dual of some other graded vector space.
%We say such an algebra $A$ is of {\em type~($\star$)}.

\begin{prp}
Let $A$ be an augmented dg commutative algebra.
Then 
\[
{\frak Z}_n(A) \simeq {\rm Poly}_n(A).
\]
\end{prp}

\owen{This is really turning into a mess.}

\begin{proof}
We are free to replace $A$ by a semifree resolution $(\Sym(V), \partial)$,
where $\partial$ sends $V$ to the augmentation ideal $\Sym^{> 0}(V)$.
Below we will (abusively) use $A$ to denote this semifree resolution,
as the original $A$ is irrelevant for us.
Ignoring the differential, we see that our situation resembles our central result for an abelian Lie algebra,
and so we now mimic the proof of our central result.

There is a natural homotopy-locally constant sheaf of cochain complexes $\Omega^\bu$ with differential $\d_{dR}$,
which is a soft replacement for the locally constant sheaf $\RR$.
Taking duals, we get a cosheaf.
In the same way, we define the factorization algebra 
\[
F_A = (\Sym((\Omega^\bu)^* \otimes V ), \d_{dR} + \partial) 
\]
which is manifestly commutative and is quasi-isomorphic to $A$ on every disk.
Hence $F_A$ is a commutative, locally constant factorization algebra that models~$A$.

Similar techniques allow us to construct a factorization algebra modeling the polyvector fields ${\rm Poly}_n(A)$.
Define
\[
Z_A = (\Hom^\bu(\Sym((\Omega^\bu)^* \otimes V), \Sym(\Omega_c^* \otimes V), [\d_{dR} + \partial,-]).
\]
Note its similarity to our model $\bZ_\fg$ for the center of~$\bU_n \fg$.
%There is a canonical shifted Poisson structure here by extending the canonical  pairing
%\[
%(\Omega^\bu \otimes V)^* \otimes \Omega^\bu_c \otimes V \to \RR
%\]
%arising from the inclusion $\Omega^\bu_c \otimes V \hookrightarrow \Omega^\bu \otimes V$.

Let us verify that 
\[
Z_A(D) \simeq {\rm Poly}_n(A)
\]
for any open disk $D$.
Due to the Poincar\'e lemma, we have canonical quasi-isomorphisms $(\Omega^\bu(D))^* \otimes V \xto{\simeq} V$ and $\Omega^\bu_c(D) \otimes V \xto{\simeq} V[-n]$,
where we view $V$ as simply a graded vector space but the de Rham complexes have the differential $\d_{dR}$.
(The differential $\partial$ will make its appearance shortly.)
Thus we have quasi-isomorphisms
\[
i: \Sym((\Omega^\bu(D))^* \otimes V) \xto{\simeq} \Sym(V)
\]
and 
\[
i_c: \Sym(\Omega_c^*(D) \otimes V) \xto{\simeq} \Sym(V[-n]).
\]
As $\partial$ acts only on the $V$-factors and not the de Rham factors,
we can modify all the complexes by adding $\partial$ to the differential.
Finally, if we fix a quasi-isomorphism 
\[
s: \Sym(V) \xto{\simeq} \Sym((\Omega^\bu(D))^* \otimes V),
\]
we get a map
\[
\begin{array}{ccc}
Z_A(D) & \to & \Hom^\bu(A,A)\\
\Phi & \mapsto & i_c \circ \Phi \circ s
\end{array}
\]
that is a quasi-isomorphism.
(Note that $s$ depends on the disk~$D$. 
We do not construct a map that intertwines with any structure maps of~$Z_A$.)

We now turn to constructing a map from this factorization algebra $Z_A$ to the center ${\frak Z}_n(A)$.
The key is to show that $Z_A$ fits into a commuting triangle as in Definition~\ref{D:centralizer},
because then we know $Z_A$ has a canonical map to~${\frak Z}_n(A)$.
This action is quite easy to see here: there is a canonical map
\[
\Hom^\bu(\Sym((\Omega^\bu)^* \otimes V), \Sym(\Omega_c^* \otimes V) \otimes \Sym((\Omega^\bu)^* \otimes V) \to \Sym((\Omega^\bu)^* \otimes V)
\]
that sends $\Phi \otimes x$ to $\iota(\Phi(x))$,
where 
\[
\iota: \Sym(\Omega_c^\bu \otimes V) \to \Sym((\Omega^\bu)^* \otimes V)
\]

4) Show this putative center fits into the commuting triangle and hence possesses a canonical map to the "true" center

5) Use the Francis-Lurie recognition principle to show this map is a quasi-iso
\end{proof}

### 2020-10-22 draft.tex
bc

@@
 
-Before stating the definition of this model, we introduce the following variant of the de Rham complex of differential forms on $\RR_{\geq 0}$. 
+Before stating the definition of this model, we introduce the following variants of the de Rham complex of differential forms on $\RR_{\geq 0}$ and compactly supported differential forms.
+
 Let $j : \RR_{>0} \hookrightarrow \RR_{\geq 0}$ be the embedding of the open ray into the closed ray. 
@@
 f \cdot (g \, \d t) = (j^* f) g\, \d t .
+\]
+
+Next, let $\Tilde{\Omega}^{\bu}_{c}(\RR_{\geq 0}) \subset \Omega^{\bu}_{c}(\RR_{\geq 0})$ be the sub dg algebra of compactly supported de Rham forms defined by
+\[
+\Tilde{\Omega}^{\bu}_{c}(\RR_{\geq 0}) = \{\alpha_{0} + \alpha_{1} \d t \; | \; \alpha_{0} (t = 0) = 0 \} .
 \]
@@
 \[
-\bC_n (\fg) (V \times [0,\epsilon)) = \clies\bigg(\fg \otimes \Omega^\bu(V) \Hat{\otimes} \Tilde{\Omega}^\bu([0,\epsilon))  \; , \; \Sym\left(\fg \otimes \Omega^\bu_c (V \times [0,\epsilon))[2] \right) \bigg).
+\bC_n (\fg) (V \times [0,\epsilon)) = \clies\bigg(\fg \otimes \Omega^\bu(V) \Hat{\otimes} \Tilde{\Omega}^\bu([0,\epsilon))  \; , \; \Sym\left(\fg \otimes \Omega^\bu_c (V) \Hat{\otimes} \Tilde{\Omega}_{c}([0,\epsilon))[2] \right) \bigg).
 \]
@@
 \begin{tikzcd}
-\clies \bigg(\fg \otimes \Omega^\bu (U) \; , \; \Sym \left(\fg \otimes \Omega^\bu_c(U) [2] \right) \bigg) \; \otimes \;  \clies\bigg(\fg \otimes \Omega^\bu(V) \otimes \Tilde{\Omega}^\bu([0,\epsilon))  \; , \; \Sym\left(\fg \otimes \Omega^\bu_c (V \times [0,\epsilon))[2] \right) \bigg) \ar[d, "\simeq"] \\
-\clies \bigg(\fg \otimes \left(\Omega^\bu (U) \oplus \Omega^\bu(V) \Hat{\otimes} \Tilde{\Omega}^\bu([0,\epsilon)) \right) \; , \; \Sym \left(\fg \otimes \left(\Omega^\bu_c(U) [2] \oplus \Omega^\bu_c(V \times [0,\epsilon)) [2]\right)\right) \bigg) \ar[d, "i^* \otimes i_*"] \\
-\clies\bigg(\fg \otimes \Omega^\bu(V') \Hat{\otimes} \Tilde{\Omega}^\bu([0,\epsilon'))  \; , \; \Sym\left(\fg \otimes \Omega^\bu_c (V' \times [0,\epsilon'))[2] \right) \bigg).
+\clies \bigg(\fg \otimes \Omega^\bu (U) \; , \; \Sym \left(\fg \otimes \Omega^\bu_c(U) [2] \right) \bigg) \; \otimes \;  \clies\bigg(\fg \otimes \Omega^\bu(V) \otimes \Tilde{\Omega}^\bu([0,\epsilon))  \; , \; \Sym\left(\fg \otimes \Omega^\bu_c (V) \Hat{\otimes} \Tilde{\Omega}_{c}([0,\epsilon))[2] \right) \bigg) \ar[d, "\simeq"] \\
+\clies \bigg(\fg \otimes \left(\Omega^\bu (U) \oplus \Omega^\bu(V) \Hat{\otimes} \Tilde{\Omega}^\bu([0,\epsilon)) \right) \; , \; \Sym \left(\fg \otimes \left(\Omega^\bu_c(U) [2] \oplus \Omega^\bu_c(V) \Hat{\otimes} \Tilde{\Omega}_{c}^{\bu}([0,\epsilon)) [2]\right)\right) \bigg) \ar[d, "i^* \otimes i_*"] \\
+\clies\bigg(\fg \otimes \Omega^\bu(V') \Hat{\otimes} \Tilde{\Omega}^\bu([0,\epsilon'))  \; , \; \Sym\left(\fg \otimes \Omega^\bu_c (V') \Hat{\otimes} \Tilde{\Omega}^{\bu}_{c}([0,\epsilon'))[2] \right) \bigg).
 \end{tikzcd}
@@
 k \otimes \bigg(\fg \otimes \Omega^\bu(V) \Hat{\otimes} \Tilde{\Omega}^\bu([0,\epsilon)) \bigg) \ar[rdd, dotted, "{\{F,G\}}"'] \ar[r, "G \otimes 1"] & 
-\bigg(\fg \otimes \Omega^\bu_c(V \times [0,\epsilon)) [2]\bigg) \otimes \bigg(\fg \otimes \Omega^\bu(V) \Hat{\otimes} \Tilde{\Omega}^\bu([0,\epsilon)) \bigg) \ar[d,"{[\cdot, \cdot] \otimes \wedge}"] \\
+\bigg(\fg \otimes \Omega^\bu_c(V) \Hat{\otimes} \Tilde{\Omega}^{\bu}_{c}([0,\epsilon)) [2]\bigg) \otimes \bigg(\fg \otimes \Omega^\bu(V) \Hat{\otimes} \Tilde{\Omega}^\bu([0,\epsilon)) \bigg) \ar[d,"{[\cdot, \cdot] \otimes \wedge}"] \\
 & \fg \otimes \Omega^\bu(V) \Hat{\otimes} \Tilde{\Omega}^\bu([0,\epsilon)) [2] \ar[d, "F"] \\ & k
@@
 \[
-\bC_n(\fg)^\partial (V) = \clies\bigg(\fg \otimes \Omega^\bu(V) \Hat{\otimes} \Tilde{\Omega}^\bu(\RR_{\geq 0})  \; , \; \Sym\left(\fg \otimes \Omega^\bu_c (V \times \RR_{\geq 0})[2] \right) \bigg) .
+\bC_n(\fg)^\partial (V) = \clies\bigg(\fg \otimes \Omega^\bu(V) \Hat{\otimes} \Tilde{\Omega}^\bu(\RR_{\geq 0})  \; , \; \Sym\left(\fg \otimes \Omega^\bu_c (V) \Hat{\otimes} \Tilde{\Omega}_{c}^{\bu}(\RR_{\geq 0})[2] \right) \bigg) .
 \]
@@
 \begin{tikzcd}
-\clies\bigg(\fg \otimes \Omega^\bu(V) \Hat{\otimes} \Tilde{\Omega}^\bu(\RR_{\geq 0})  \; , \; \Sym\left(\fg \otimes \Omega^\bu_c (V \times \RR_{\geq 0})[2] \right) \bigg) \ar[r, "{{\rm ev}_1}"] & \Sym\left(\fg \otimes \Omega^\bu_c (V \times \RR_{\geq 0})[2] \right) \ar[d, "{\int_{\RR_{\geq 0}}}"] \\ &  \Sym\left(\fg \otimes \Omega^\bu_c (V)[1] \right) .
+\clies\bigg(\fg \otimes \Omega^\bu(V) \Hat{\otimes} \Tilde{\Omega}^\bu(\RR_{\geq 0})  \; , \; \Sym\left(\fg \otimes \Omega^\bu_c (V \times \RR_{\geq 0})[2] \right) \bigg) \ar[r, "{{\rm ev}_1}"] & \Sym\left(\fg \otimes \Omega^\bu_c (V) \Hat{\otimes} \Tilde{\Omega}_{c}^{\bu}(\RR_{\geq 0})[2] \right) \ar[d, "{\int_{\RR_{\geq 0}}}"] \\ &  \Sym\left(\fg \times \Omega^\bu_c (V)[1] \right) .
 \end{tikzcd}

### 2020-11-02 draft.tex
eugene

@@
 
-Following the proof of this proposition, our main thrust is to interpret this result by exhibiting a topological field theory on the $(n+1)$-dimensional manifold with boundary $M \times \RR_{\geq 0}$ whose factorization algebra of classical observables is equivalent to the constructible factorization algebra $\bC_n(\fg)$.
-\brian{improve this pointer}
+Following the proof of this proposition, our main thrust is to interpret this result by exhibiting a topological field theory on the $(n+1)$-dimensional manifold with boundary $M \times \RR_{\geq 0}$ whose factorization algebra of {\em classical} observables is equivalent to the constructible factorization algebra $\bC_n(\fg)$.
+In this sense, the pair $(\bZ_n(\fg), \bU_n(\fg))$ is a model for the quantization of a particular topological field theory on a manifold with boundary.
+
 \owen{Somewhere please mention that the slogan ``quantization commutes with pushforward'' holds for this class of theories.}
+\brian{not sure where you wanted to address this request.}
 
@@
 
-Let $j : \RR_{>0} \hookrightarrow \RR_{\geq 0}$ be the embedding of the open ray into the closed ray. 
 Let $\Tilde{\Omega}^\bu (\RR_{\geq 0})$ be the two-term complex
 \[
-\Omega^0(\RR_{\geq 0}) \xto{j^* \circ \d_{\rm dR}} \Omega^1(\RR_{>0})[-1]  .
-\]
-The dg commutative algebra structure on $\Tilde{\Omega}^\bu (\RR_{\geq 0})$ is defined by the formula
-\[
-f \cdot (g \, \d t) = (j^* f) g\, \d t .
-\]
-
-Next, let $\Tilde{\Omega}^{\bu}_{c}(\RR_{\geq 0}) \subset \Omega^{\bu}_{c}(\RR_{\geq 0})$ be the sub dg algebra of compactly supported de Rham forms defined by
-\[
-\Tilde{\Omega}^{\bu}_{c}(\RR_{\geq 0}) = \{\alpha_{0} + \alpha_{1} \d t \; | \; \alpha_{0} (t = 0) = 0 \} .
-\]
+\{f \in  C^{\infty}(\RR_{\geq 0}) \; | \; f(0) = 0\}  \xto{\d_{\rm dR}} \Omega^1(\RR_{\geq 0})[-1]  .
+\]
+Notice that this is a subcomplex of the full de Rham complex on $\RR_{\geq 0}$.
+In fact, this is a de Rham model for the relative cohomology of the pair $(\RR_{\geq 0}, \partial \RR_{\geq 0} = \{t = 0\})$.
+
+Similarly, let $\Tilde{\Omega}^{\bu}_{c}(\RR_{\geq 0}) \subset \Omega^{\bu}_{c}(\RR_{\geq 0})$ be the subcomplex of compactly supported de Rham forms on $\RR_{\geq 0}$ whose zero form component vanishes at $t = 0$.
+
+Notice that $\Tilde{\Omega}_c^\bu(\RR_{\geq 0})$ (and $\Tilde{\Omega}^\bu_c(\RR_{\geq 0})$) admits the obvious enhancement to a sheaf (cosheaf) of commutative dg algebras on $\RR_{\geq 0}$.
 
@@
 \end{proof}
+
+By Proposition \ref{prp:pair}, the constructible factorization algebra $\bC_n(\fg)$ is the classical limit of the factorization sc-pair $(\bZ_n(\fg), \bU_n(\fg))$.
+Thus, we have shown that the pair $(\bZ_n(\fg), \bU_n(\fg))$ is
+a model for the quantum factorization algebra of observables of topological BF theory on $M \times \RR_{\geq 0}$.
+
+In the ordinary Batalin--Vilkovisky formalism on manifolds without boundary it is the central theme of \cite{CG2} that to any effective family of functionals satisfying the ``quantum master equation'' one can associate a factorization algebra of quantum observables.
+On manifolds with boundary, this approach appears in the work of Rabinovich \cite{EugeneNew}.
+We expect that one can exhibit our constructible factorization algebra as the quantum factorization algebra of observables associated to a Batalin--Vilkovisky quantization of BF theory on $M \times \RR_{\geq 0}$.
 
@@
 \end{document}
+
 We call $\ev_f$ the 

### 2020-11-03 draft.tex
sec 8.1,2,3

@@
 
-Before stating the definition of this model, we introduce the following variants of the de Rham complex of differential forms on $\RR_{\geq 0}$ and compactly supported differential forms.
-
-Let $\Tilde{\Omega}^\bu (\RR_{\geq 0})$ be the two-term complex
+Before stating the definition of this model, we introduce the following variants of the de Rham complex of differential forms on manifolds with boundary.
+
+Suppose $N$ is a manifold with boundary and denote by $i_\partial : \partial N \hookrightarrow N$ the boundary embedding.
+Let $\Omega^{\bu}(N \, | \, \partial N)$ be the subcomplex of de Rham forms $\alpha$ on $N$ with the property that $i_\partial^* \alpha  = 0$.
+For instance, if $N = \RR_{\geq 0}$, then $\Omega^{\bu}(\RR_{\geq 0} \, | \, \{0\})$ is equal to the two-term complex
 \[
@@
 \]
-Notice that this is a subcomplex of the full de Rham complex on $\RR_{\geq 0}$.
-In fact, this is a de Rham model for the relative cohomology of the pair $(\RR_{\geq 0}, \partial \RR_{\geq 0} = \{t = 0\})$.
-
-Similarly, let $\Tilde{\Omega}^{\bu}_{c}(\RR_{\geq 0}) \subset \Omega^{\bu}_{c}(\RR_{\geq 0})$ be the subcomplex of compactly supported de Rham forms on $\RR_{\geq 0}$ whose zero form component vanishes at $t = 0$.
-
-Notice that $\Tilde{\Omega}_c^\bu(\RR_{\geq 0})$ (and $\Tilde{\Omega}^\bu_c(\RR_{\geq 0})$) admits the obvious enhancement to a sheaf (cosheaf) of commutative dg algebras on $\RR_{\geq 0}$.
+The complex $\Omega^\bu(N \, | \, \partial N)$ is a de Rham model for the relative cohomology of the pair $(N, \partial N)$.
+
+Similarly, let $\Omega^{\bu}_{c}(N \, | \, \partial N)$ be the subcomplex of compactly supported de Rham forms $\alpha$ on $N$ with the property that $i_\partial^* \alpha = 0$.
+
+Notice that both $\Omega^\bu(N \, | \, \partial N)$ and its compactly supported version are commutative dg subalgebras of the full de Rham complex.
 
@@
 \[
-\bC_n (\fg) (V \times [0,\epsilon)) = \clies\bigg(\fg \otimes \Omega^\bu(V) \Hat{\otimes} \Tilde{\Omega}^\bu([0,\epsilon))  \; , \; \Sym\left(\fg \otimes \Omega^\bu_c (V) \Hat{\otimes} \Tilde{\Omega}_{c}([0,\epsilon))[2] \right) \bigg).
+    \bC_n (\fg) (V \times [0,\epsilon)) = \clies\bigg(\fg \otimes \Omega^\bu(V \times [0,\epsilon) \, | \, V)  \; , \; \Sym\left(\fg \otimes \Omega^\bu_c (V \times [0,\epsilon) \, | \, V) [2] \right) \bigg)
 \]
@@
 \begin{tikzcd}
-\clies \bigg(\fg \otimes \Omega^\bu (U) \; , \; \Sym \left(\fg \otimes \Omega^\bu_c(U) [2] \right) \bigg) \; \otimes \;  \clies\bigg(\fg \otimes \Omega^\bu(V) \otimes \Tilde{\Omega}^\bu([0,\epsilon))  \; , \; \Sym\left(\fg \otimes \Omega^\bu_c (V) \Hat{\otimes} \Tilde{\Omega}_{c}([0,\epsilon))[2] \right) \bigg) \ar[d, "\simeq"] \\
-\clies \bigg(\fg \otimes \left(\Omega^\bu (U) \oplus \Omega^\bu(V) \Hat{\otimes} \Tilde{\Omega}^\bu([0,\epsilon)) \right) \; , \; \Sym \left(\fg \otimes \left(\Omega^\bu_c(U) [2] \oplus \Omega^\bu_c(V) \Hat{\otimes} \Tilde{\Omega}_{c}^{\bu}([0,\epsilon)) [2]\right)\right) \bigg) \ar[d, "i^* \otimes i_*"] \\
-\clies\bigg(\fg \otimes \Omega^\bu(V') \Hat{\otimes} \Tilde{\Omega}^\bu([0,\epsilon'))  \; , \; \Sym\left(\fg \otimes \Omega^\bu_c (V') \Hat{\otimes} \Tilde{\Omega}^{\bu}_{c}([0,\epsilon'))[2] \right) \bigg).
+\clies \bigg(\fg \otimes \Omega^\bu (U) \; , \; \Sym \left(\fg \otimes \Omega^\bu_c(U) [2] \right) \bigg) \; \otimes \;  \clies\bigg(\fg \otimes \Omega^\bu(V \times [0,\epsilon) \, | \, V) \; , \; \Sym\left(\fg \otimes \Omega^\bu_c (V \times [0,\epsilon) \, | \, V)[2] \right) \bigg) \ar[d, "\simeq"] \\
+\clies \bigg(\fg \otimes \left(\Omega^\bu (U) \oplus \Omega^\bu(V \times [0,\epsilon) \, | \, V \right) \; , \; \Sym \left(\fg \otimes \left(\Omega^\bu_c(U) [2] \oplus \Omega^\bu_c(V \times [0,\epsilon) \, | \, V) [2]\right)\right) \bigg) \ar[d, "i^* \otimes i_*"] \\
+\clies\bigg(\fg \otimes \Omega^\bu(V' \times [0,\epsilon') \, | \, V')  \; , \; \Sym\left(\fg \otimes \Omega^\bu_c (V' \times [0,\epsilon') \, | \, V') [2] \right) \bigg).
 \end{tikzcd}
@@
 \[
-\Omega^\bu (V') \otimes \Tilde{\Omega}^\bu([0,\epsilon)) \xto{j^*}  \Omega^\bu (V') \Hat{\otimes} \Omega^\bu((0,\epsilon)) \cong \Omega^\bu(V \times (0,\epsilon)) \xto{\iota^*} \Omega^\bu(U) .
-\]
+  \Omega^\bu (V \times [0,\epsilon) \, | \, V) \xto{j^*}  \Omega^\bu (V \times (0,\epsilon)) \xto{\iota^*} \Omega^\bu(U)
+\]
+where $j : V \times (0,\epsilon) \hookrightarrow V \times [0,\epsilon)$ is the open embedding.
 This composition provides the version of restriction $\iota^*$ of de Rham forms used in the definition above.
@@
 \[
-{\rm Hom}^\bu\left(\Sym(\fg \otimes \Omega^\bu (V) \otimes \Tilde{\Omega}^\bu ([0,\epsilon))) [1]) \; , \; \Sym \left(\fg \otimes \Omega^\bu_c(V \times [0,\epsilon)) [2] \right) \right)  .
+{\rm Hom}^\bu\left(\Sym(\fg \otimes \Omega^\bu (V \times [0,\epsilon) \, | \, V) [1]) \; , \; \Sym \left(\fg \otimes \Omega^\bu_c(V \times [0,\epsilon) \, | \, V) [2] \right) \right)  .
 \]
@@
 \[
-F : \fg \otimes \Omega^\bu(V) \Hat{\otimes} \Tilde{\Omega}^\bu([0,\epsilon)) [2] \to k
+F : \fg \otimes \Omega^\bu(V \times [0,\epsilon) \, | \, V) [2] \to k
 \]
@@
 \[
-G : k \to \fg \otimes \Omega^\bu_c(V \times [0,\epsilon))[2] .
+G : k \to \fg \otimes \Omega^\bu_c(V \times [0,\epsilon) \, | \, V)[2] .
 \]
@@
 \begin{tikzcd}
-k \otimes \bigg(\fg \otimes \Omega^\bu(V) \Hat{\otimes} \Tilde{\Omega}^\bu([0,\epsilon)) \bigg) \ar[rdd, dotted, "{\{F,G\}}"'] \ar[r, "G \otimes 1"] & 
-\bigg(\fg \otimes \Omega^\bu_c(V) \Hat{\otimes} \Tilde{\Omega}^{\bu}_{c}([0,\epsilon)) [2]\bigg) \otimes \bigg(\fg \otimes \Omega^\bu(V) \Hat{\otimes} \Tilde{\Omega}^\bu([0,\epsilon)) \bigg) \ar[d,"{[\cdot, \cdot] \otimes \wedge}"] \\
-& \fg \otimes \Omega^\bu(V) \Hat{\otimes} \Tilde{\Omega}^\bu([0,\epsilon)) [2] \ar[d, "F"] \\ & k
+k \otimes \bigg(\fg \otimes \Omega^\bu(V \times [0,\epsilon) \, | \, V) \bigg) \ar[rdd, dotted, "{\{F,G\}}"'] \ar[r, "G \otimes 1"] &
+\bigg(\fg \otimes \Omega^\bu_c(V \times [0,\epsilon) \, | \, V) [2]\bigg) \otimes \bigg(\fg \otimes \Omega^\bu(V \times [0,\epsilon) \, | \, V)\bigg)
+\ar[d,"{[\cdot, \cdot] \otimes \wedge}"] \\
+& \fg \otimes \Omega^\bu(V \times [0,\epsilon) \, | \, V) [2] \ar[d, "F"] \\ & k
 \end{tikzcd}
@@
 \[
-\bC_n(\fg)^\partial (V) = \clies\bigg(\fg \otimes \Omega^\bu(V) \Hat{\otimes} \Tilde{\Omega}^\bu(\RR_{\geq 0})  \; , \; \Sym\left(\fg \otimes \Omega^\bu_c (V) \Hat{\otimes} \Tilde{\Omega}_{c}^{\bu}(\RR_{\geq 0})[2] \right) \bigg) .
+  \bC_n(\fg)^\partial (V) = \clies\bigg(\fg \otimes \Omega^\bu(V \times \RR_{\geq 0} \, | \, V) \; , \; \Sym\left(\fg \otimes \Omega^\bu_c (V \times \RR_{\geq 0} \, | \, V)[2] \right) \bigg) .
 \]
@@
 \begin{tikzcd}
-\clies\bigg(\fg \otimes \Omega^\bu(V) \Hat{\otimes} \Tilde{\Omega}^\bu(\RR_{\geq 0})  \; , \; \Sym\left(\fg \otimes \Omega^\bu_c (V \times \RR_{\geq 0})[2] \right) \bigg) \ar[r, "{{\rm ev}_1}"] & \Sym\left(\fg \otimes \Omega^\bu_c (V) \Hat{\otimes} \Tilde{\Omega}_{c}^{\bu}(\RR_{\geq 0})[2] \right) \ar[d, "{\int_{\RR_{\geq 0}}}"] \\ &  \Sym\left(\fg \times \Omega^\bu_c (V)[1] \right) .
+  \clies\bigg((\fg \otimes \Omega^\bu(V \times \RR_{\geq 0} \, | \, V) \; , \; \Sym\left(\fg \otimes \Omega^\bu_c (V \times \RR_{\geq 0})[2] \right) \bigg) \ar[r, "{{\rm ev}_1}"] & \Sym\left(\fg \otimes \Omega^\bu_c (V \times \RR_{\geq 0} \, | V)[2] \right) \ar[d, "{\int_{\RR_{\geq 0}}}"] \\ &  \Sym\left(\fg \otimes \Omega^\bu_c (V)[1] \right) .
 \end{tikzcd}
 \]
-The first map ${\rm ev}_1$ evaluates the unit in $\Sym \left(\fg \otimes \Omega^\bu(V) \Hat{\otimes} \Tilde{\Omega}^\bu(\RR_{\geq 0})\right)$ and the second map is induced by integration along $\RR_{\geq 0}$.
+The first map ${\rm ev}_1$ evaluates the unit in $\Sym \left(\fg \otimes \Omega^\bu(V \times \RR_{\geq 0} \, | \, V)[1]\right)$ and the second map is induced by integration along $\RR_{\geq 0}$.
 It is quick to check that $I^{\partial}$ extends to a map of factorization algebras.
@@
 It is the central theme of \cite{CG1, CG2} that the observables of a {\em perturbative} field theory define the structure of a factorization algebra.
-Moreover, the observables are equipped with the structure of a $\PP_0$ factorization algebra.
+The value of the factorization algebra on an open set $U$ is, by definition, the functionals on the fields restricted to $U$.
+Furthermore, the observables are equipped with the structure of a $\PP_0$ factorization algebra.
 
@@
 \[
-\cL (V \times [0,\epsilon)) = \Omega^\bu (V) \Hat{\otimes} \Tilde{\Omega}^\bu([0,\epsilon)) \otimes \fg \ltimes \Omega^{\bu} (V \times [0,\epsilon)) \otimes \fg^* [n-3] .
+    \cL (V \times [0,\epsilon)) = \Omega^\bu (V \times [0,\epsilon) \, | \, V) \otimes \fg \ltimes \Omega^{\bu} (V \times [0,\epsilon)) \otimes \fg^* [n-3] .
 \]
@@
 \begin{proof}
-\brian{all we need to say is that half-smeared is equivalent to full observables}
-
+  This proposition follows by tracing through some definitions, together with a key fact in functional analysis.
+
+  First, observe that the cochain complex which is {\em linear dual}\footnote{Here, we mean continuous linear dual, taking into account the structure of de Rham forms as a topological vector space.} to the cochain complex $\Omega^\bu (V \times [0,\epsilon)) \otimes \fg^*[n-3]$ is
+  \[
+    \Bar{\Omega}_c^\bu(V \times [0,\epsilon) \, | \, V) \otimes \fg[2].
+  \]
+  Here, the bar in $\Bar{\Omega}_c$ indicates compactly supported distributional differential forms.
+  In words, this is the space of compactly supported distributional de Rham forms $\alpha$ valued in $\fg[2]$ with the property that $i_\partial^* \alpha = 0$.
+  Where, as above, $i_\partial : \partial N \hookrightarrow N$ is the boundary embedding.
+
+  Now, there is a natural inclusion of cochain complexes of the smooth (non-distributional) compactly supported de Rham forms inside of the distributional ones:
+  \begin{equation}\label{eqn:AB}
+    \Omega_c^\bu(V \times [0,\epsilon) \, | \, V) \otimes \fg[2]\Bar{\Omega}_c^\bu(V \times [0,\epsilon) \, | \, V) \otimes \fg[2] .
+  \end{equation}
+  Furthermore, using ellipticity of the de Rham operator we can assert by the Atiyah--Bott lemma \cite{??} that this inclusion is a quasi-isomorphism.
+
+  With this bit of functional analysis out of the way, we observe that the value of the factorization algebra $\clies(\cL)$ on $V \times [0,\epsilon)$ is
+
+  The value of $\clies(\cL)$ on an open set $U$ is
+  \[
+    \clies\bigg(\fg \otimes \Omega^\bu(V \times [0,\epsilon) \, | \, V)  \; , \; \Sym\left(\fg \otimes \Bar{\Omega}^\bu_c (V \times [0,\epsilon) \, | \, V) [2] \right) \bigg) .
+\]
+So, the quasi-isomorphism (\ref{eqn:AB}) induces a quasi-isomorphism
+\[
+  \bC_n(\fg)(V \times [0,\epsilon)) \xto{\simeq} \clies(\cL)(V \times [0,\epsilon)) .
+\]
+
+Checking that $\bC_n(\fg)(U) \to \clies(\cL)(U)$ for open sets of the form $U \subset M \times \RR_{>0}$ is completely similar.
 %Suppose $V \times [0,\epsilon) \subset M \times \RR_{\geq 0}$ is an open set. 
@@
 
-In the ordinary Batalin--Vilkovisky formalism on manifolds without boundary it is the central theme of \cite{CG2} that to any effective family of functionals satisfying the ``quantum master equation'' one can associate a factorization algebra of quantum observables.
-On manifolds with boundary, this approach appears in the work of Rabinovich \cite{EugeneNew}.
+In the ordinary Batalin--Vilkovisky formalism, on manifolds without boundary, it is the central result of \cite{CG2} that to any effective family of functionals satisfying the ``quantum master equation'' one can associate a factorization algebra of quantum observables.
+For manifolds with boundary, this has been developed in the work of Rabinovich \cite{EugeneNew}.
 We expect that one can exhibit our constructible factorization algebra as the quantum factorization algebra of observables associated to a Batalin--Vilkovisky quantization of BF theory on $M \times \RR_{\geq 0}$.
@@
 
-\begin{rmk} Examples
-
-Poisson $\sigma$-model. 
-$B$-model. 
-cite paper with Eugene.
-Kapustin-Witten. 
-\end{rmk}
+%\begin{rmk} Examples
+%Poisson $\sigma$-model.
+%$B$-model.
+%cite paper with Eugene.
+%Kapustin-Witten.
+%\end{rmk}
 

### 2020-11-05 draft.tex
typo
strict

@@
 If the associated graded of a filtered $\EE_n$ algebra is commutative, then it carries the structure of a $\PP_n$ algebra, which is similar to a Poisson algebra except the bracket is of cohomological degree $1-n$.
-There is a similar description of the ``classical limit"  of algebras over the $(n+1)$-dimensional Swiss cheese operad in terms of algebras over a certain two-colored operad $\PP_{[n+1,n]}$, introduced by Safronov \cite{Pavel1, Pavel2}, whose definition we recall below.
-
-\begin{prp} 
-\label{prp:poisson}
-The associated graded pair $({\rm Gr} \; \fZ_n(\fg) , {\rm Gr} \; \UU_n(\fg))$ determines an algebra over the operad $\PP_{[n+1,n]}$. 
-\end{prp}
+In particular, ${\rm Gr} \; \UU_n (\fg)$ has the structure of a $\PP_n$-algebra.
+
+There is a similar description of the ``classical limit"  of algebras over the $(n+1)$-dimensional Swiss cheese operad in terms of algebras over a certain two-colored operad $\PP_{[n+1,n]}$, introduced by Safronov \cite{Pavel1, Pavel2}.
+Using our model, we will see that the pair $({\rm Gr} \; \fZ_n (\fg), {\rm Gr} \; \UU_n(\fg))$ is an algebra over this two-colored operad.
+In particular, this implies that ${\rm Gr} \; \fZ_n (\fg)$ carries the structure of a $\PP_{n+1}$-algebra which ``acts'' on the $\PP_n$-algebra ${\rm Gr} \; \UU_n(\fg)$.
+
+%\begin{prp}
+%\label{prp:poisson}
+%The associated graded pair $({\rm Gr} \; \fZ_n(\fg) , {\rm Gr} \; \UU_n(\fg))$ determines an algebra over the operad $\PP_{[n+1,n]}$.
+%\end{prp}
 
@@
 The associated graded factorization algebras ${\rm Gr} \; \bU_n (\fg)$ and ${\rm Gr} \; \bZ_n(\fg)$ are equipped with Poisson brackets that are compatible with the factorization structure. 
-
-For $k \geq -1$, a {\em $\PP_k$-factorization algebra} is a factorization algebra $\bA$ such that for every open set $U$ the cochain complex $\bA(U)$ is equipped with the structure of a $\PP_k$ algebra.
-Furthermore, we require that the factorization structure maps be compatible with the $\PP_k$ algebra structure.
-
-Theorem \ref{thm:lurie1} combines with the additivity result of \cite{SafronovAdd} to show that there is an equivalence of categories between the category of locally constant $\PP_k$-factorization algebras on $\RR^n$ and $\PP_{n+k}$ algebras.
-
-In light of this, the following lemma implies that ${\rm Gr} \; \bU_n (\fg)$ and ${\rm Gr} \; \bZ_n(\fg)$ determine $\PP_n$ and $\PP_{n+1}$ algebras respectively.
+For the remainder of this section we will assume that $\fg$ is a strict dg Lie algebra so that we can work with strict Poisson brackets
+in the category of dg algebras.
+
+\begin{dfn}
+  A $\PP_m$-algebra is a commutative dg algebra $A$ equipped with a bracket
+  \[
+    \{\cdot , \cdot\} : A \otimes_k A \to A
+  \]
+  which defines a graded Lie bracket on $A[m-1]$ and satisfies the graded Leibniz rule
+  \[
+    \{a, b \cdot c\} = \{a,b\} \cdot c + (-1)^{|b||c|} \{a , c\} \cdot b .
+  \]
+\end{dfn}
+
+A {\em $\PP_m$-factorization algebra} is a factorization algebra $\bA$ such that for every open set $U$ the cochain complex $\bA(U)$ is equipped with the structure of a $\PP_m$ algebra and that the factorization structure maps are compatible with the $\PP_m$-algebra structures.
+In particular, we note that a $\PP_m$-factorization algebra is a commutative factorization algebra.
+
+There is an additivity theorem of Dunn and Lurie for $\EE_n$-algebras, see Theorem ??
+in \cite{LurieHA}, which states an equivalence of $\infty$-categories between the category of $\EE_{n+1}$-algebras and the category of algebras in $\EE_{n}$-algebras.
+Safronov \cite{SafronovAdd} has proven a Poisson version of this result which states that there is an equivalence of $\infty$-categories between the category of $\PP_{n+1}$ algebras and the category of algebras in $\PP_{n}$-algebras.
+
+In light of this result, the following lemma implies that ${\rm Gr} \; \bU_n (\fg)$ and ${\rm Gr} \; \bZ_n(\fg)$ determine $\PP_n$ and $\PP_{n+1}$ algebras respectively.
 
@@
 \begin{proof}
-For any $L_\infty$ algebra $\fh$, the associated graded of the Chevalley--Eilenberg complex ${\rm Gr} \; \cliels {\rm Sym} (\fh [1])$ is equipped with the structure of a $\PP_0$ algebra.
-It is given by the sum of the $L_\infty$-operations $\ell_2 + \ell_3 + \cdots$. 
+For any Lie algebra $\fh$, the associated graded of the Chevalley--Eilenberg complex ${\rm Gr} \; \cliels {\rm Sym} (\fh [1])$ is equipped with the structure of a $\PP_0$ algebra with $\PP_0$-bracket determined by the Lie bracket on $\fh$.
 This observation implies that ${\rm Gr} \; \bU_n (\fg)$ is a $\PP_0$-factorization algebra.
@@
 The definition of this two-colored operad $\PP_{[n+1,n]}$ can be found in~\cite{SafronovCoiso}. 
-A {\em $\PP_{[n+1,n]}$ algebra} consists of a pair $(A,B)$ where $A$ is a $\PP_{n+1}$ algebra and $B$ is a $\PP_n$ algebra that receives an action by $A$.
+Roughly speaking, a {\em $\PP_{[n+1,n]}$ algebra} consists of a pair $(A,B)$ where $A$ is a $\PP_{n+1}$ algebra and $B$ is a $\PP_n$ algebra that receives an action by $A$.
 
 The action of $\bZ_n(\fg)$ on $\bU_n(\fg)$ descends to an action at the level of the associated graded factorization algebras
-Together with Lemma~\ref{lmm:pois1}, we obtain Proposition~\ref{prp:poisson}.
+Together with Lemma~\ref{lmm:pois1}, we see that the associated graded pair is an algebra over $\PP_{[n+1,n]}$.
 
@@
   \begin{equation}\label{eqn:AB}
-    \Omega_c^\bu(V \times [0,\epsilon) \, | \, V) \otimes \fg[2]\Bar{\Omega}_c^\bu(V \times [0,\epsilon) \, | \, V) \otimes \fg[2] .
+    \Omega_c^\bu(V \times [0,\epsilon) \, | \, V) \otimes \fg[2] \hookrightarrow \Bar{\Omega}_c^\bu(V \times [0,\epsilon) \, | \, V) \otimes \fg[2] .
   \end{equation}
